### 2019-12-09 apssamp.tex
Initial Overleaf Import

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.2 distribution.
%   Version 4.2a of REVTeX, December 2014
%
%   Copyright (c) 2014 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.2
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[%
 reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-2}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

%\usepackage[showframe,%Uncomment any one of the following lines to test 
%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
%%text={7in,10in},centering,
%%margin=1.5in,
%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
%%height=10in,a5paper,hmargin={3cm,0.8in},
%]{geometry}

\begin{document}

\preprint{APS/123-QED}

\title{A High Mass Black Hole Search\\with BCR}% Force line breaks with \\
\thanks{A footnote to the article title}%

\author{Ann Author}
 \altaffiliation[Also at ]{Physics Department, XYZ University.}%Lines break automatically or can be forced with \\
\author{Second Author}%
 \email{Second.Author@institution.edu}
\affiliation{%
 Authors' institution and/or address\\
 This line break forced with \textbackslash\textbackslash
}%

\collaboration{MUSO Collaboration}%\noaffiliation

\author{Charlie Author}
 \homepage{http://www.Second.institution.edu/~Charlie.Author}
\affiliation{
 Second institution and/or address\\
 This line break forced% with \\
}%
\affiliation{
 Third institution, the second for Charlie Author
}%
\author{Delta Author}
\affiliation{%
 Authors' institution and/or address\\
 This line break forced with \textbackslash\textbackslash
}%

\collaboration{CLEO Collaboration}%\noaffiliation

\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

\begin{abstract}
An article usually includes an abstract, a concise summary of the work
covered at length in the main body of the article. 
\begin{description}
\item[Usage]
Secondary publications and information retrieval purposes.
\item[Structure]
You may use the \texttt{description} environment to structure your abstract;
use the optional argument of the \verb+\item+ command to give the category of each item. 
\end{description}
\end{abstract}

%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired
\maketitle

%\tableofcontents

\section{\label{sec:level1}First-level heading:\protect\\ The line
break was forced \lowercase{via} \textbackslash\textbackslash}

This sample document demonstrates proper use of REV\TeX~4.2 (and
\LaTeXe) in mansucripts prepared for submission to APS
journals. Further information can be found in the REV\TeX~4.2
documentation included in the distribution or available at
\url{http://journals.aps.org/revtex/}.

When commands are referred to in this example file, they are always
shown with their required arguments, using normal \TeX{} format. In
this format, \verb+#1+, \verb+#2+, etc. stand for required
author-supplied arguments to commands. For example, in
\verb+\section{#1}+ the \verb+#1+ stands for the title text of the
author's section heading, and in \verb+\title{#1}+ the \verb+#1+
stands for the title text of the paper.

Line breaks in section headings at all levels can be introduced using
\textbackslash\textbackslash. A blank input line tells \TeX\ that the
paragraph has ended. Note that top-level section headings are
automatically uppercased. If a specific letter or word should appear in
lowercase instead, you must escape it using \verb+\lowercase{#1}+ as
in the word ``via'' above.

\subsection{\label{sec:level2}Second-level heading: Formatting}

This file may be formatted in either the \texttt{preprint} or
\texttt{reprint} style. \texttt{reprint} format mimics final journal output. 
Either format may be used for submission purposes. \texttt{letter} sized paper should
be used when submitting to APS journals.

\subsubsection{Wide text (A level-3 head)}
The \texttt{widetext} environment will make the text the width of the
full page, as on page~\pageref{eq:wideeq}. (Note the use the
\verb+\pageref{#1}+ command to refer to the page number.) 
\paragraph{Note (Fourth-level head is run in)}
The width-changing commands only take effect in two-column formatting. 
There is no effect if text is in a single column.

\subsection{\label{sec:citeref}Citations and References}
A citation in text uses the command \verb+\cite{#1}+ or
\verb+\onlinecite{#1}+ and refers to an entry in the bibliography. 
An entry in the bibliography is a reference to another document.

\subsubsection{Citations}
Because REV\TeX\ uses the \verb+natbib+ package of Patrick Daly, 
the entire repertoire of commands in that package are available for your document;
see the \verb+natbib+ documentation for further details. Please note that
REV\TeX\ requires version 8.31a or later of \verb+natbib+.

\paragraph{Syntax}
The argument of \verb+\cite+ may be a single \emph{key}, 
or may consist of a comma-separated list of keys.
The citation \emph{key} may contain 
letters, numbers, the dash (-) character, or the period (.) character. 
New with natbib 8.3 is an extension to the syntax that allows for 
a star (*) form and two optional arguments on the citation key itself.
The syntax of the \verb+\cite+ command is thus (informally stated)
\begin{quotation}\flushleft\leftskip1em
\verb+\cite+ \verb+{+ \emph{key} \verb+}+, or\\
\verb+\cite+ \verb+{+ \emph{optarg+key} \verb+}+, or\\
\verb+\cite+ \verb+{+ \emph{optarg+key} \verb+,+ \emph{optarg+key}\ldots \verb+}+,
\end{quotation}\noindent
where \emph{optarg+key} signifies 
\begin{quotation}\flushleft\leftskip1em
\emph{key}, or\\
\texttt{*}\emph{key}, or\\
\texttt{[}\emph{pre}\texttt{]}\emph{key}, or\\
\texttt{[}\emph{pre}\texttt{]}\texttt{[}\emph{post}\texttt{]}\emph{key}, or even\\
\texttt{*}\texttt{[}\emph{pre}\texttt{]}\texttt{[}\emph{post}\texttt{]}\emph{key}.
\end{quotation}\noindent
where \emph{pre} and \emph{post} is whatever text you wish to place 
at the beginning and end, respectively, of the bibliographic reference
(see Ref.~[\onlinecite{witten2001}] and the two under Ref.~[\onlinecite{feyn54}]).
(Keep in mind that no automatic space or punctuation is applied.)
It is highly recommended that you put the entire \emph{pre} or \emph{post} portion 
within its own set of braces, for example: 
\verb+\cite+ \verb+{+ \texttt{[} \verb+{+\emph{text}\verb+}+\texttt{]}\emph{key}\verb+}+.
The extra set of braces will keep \LaTeX\ out of trouble if your \emph{text} contains the comma (,) character.

The star (*) modifier to the \emph{key} signifies that the reference is to be 
merged with the previous reference into a single bibliographic entry, 
a common idiom in APS and AIP articles (see below, Ref.~[\onlinecite{epr}]). 
When references are merged in this way, they are separated by a semicolon instead of 
the period (full stop) that would otherwise appear.

\paragraph{Eliding repeated information}
When a reference is merged, some of its fields may be elided: for example, 
when the author matches that of the previous reference, it is omitted. 
If both author and journal match, both are omitted.
If the journal matches, but the author does not, the journal is replaced by \emph{ibid.},
as exemplified by Ref.~[\onlinecite{epr}]. 
These rules embody common editorial practice in APS and AIP journals and will only
be in effect if the markup features of the APS and AIP Bib\TeX\ styles is employed.

\paragraph{The options of the cite command itself}
Please note that optional arguments to the \emph{key} change the reference in the bibliography, 
not the citation in the body of the document. 
For the latter, use the optional arguments of the \verb+\cite+ command itself:
\verb+\cite+ \texttt{*}\allowbreak
\texttt{[}\emph{pre-cite}\texttt{]}\allowbreak
\texttt{[}\emph{post-cite}\texttt{]}\allowbreak
\verb+{+\emph{key-list}\verb+}+.

\subsubsection{Example citations}
By default, citations are numerical\cite{Beutler1994}.
Author-year citations are used when the journal is RMP. 
To give a textual citation, use \verb+\onlinecite{#1}+: 
Refs.~\onlinecite{[][{, and references therein}]witten2001,Bire82}. 
By default, the \texttt{natbib} package automatically sorts your citations into numerical order and ``compresses'' runs of three or more consecutive numerical citations.
REV\TeX\ provides the ability to automatically change the punctuation when switching between journal styles that provide citations in square brackets and those that use a superscript style instead. This is done through the \texttt{citeautoscript} option. For instance, the journal style \texttt{prb} automatically invokes this option because \textit{Physical 
Review B} uses superscript-style citations. The effect is to move the punctuation, which normally comes after a citation in square brackets, to its proper position before the superscript. 
To illustrate, we cite several together 
\cite{[See the explanation of time travel in ]feyn54,*[The classical relativistic treatment of ][ is a relative classic]epr,witten2001,Berman1983,Davies1998,Bire82}, 
and once again in different order (Refs.~\cite{epr,feyn54,Bire82,Berman1983,witten2001,Davies1998}). 
Note that the citations were both compressed and sorted. Futhermore, running this sample file under the \texttt{prb} option will move the punctuation to the correct place.

When the \verb+prb+ class option is used, the \verb+\cite{#1}+ command
displays the reference's number as a superscript rather than in
square brackets. Note that the location of the \verb+\cite{#1}+
command should be adjusted for the reference style: the superscript
references in \verb+prb+ style must appear after punctuation;
otherwise the reference must appear before any punctuation. This
sample was written for the regular (non-\texttt{prb}) citation style.
The command \verb+\onlinecite{#1}+ in the \texttt{prb} style also
displays the reference on the baseline.

\subsubsection{References}
A reference in the bibliography is specified by a \verb+\bibitem{#1}+ command
with the same argument as the \verb+\cite{#1}+ command.
\verb+\bibitem{#1}+ commands may be crafted by hand or, preferably,
generated by Bib\TeX. 
REV\TeX~4.2 includes Bib\TeX\ style files
\verb+apsrev4-2.bst+, \verb+apsrmp4-2.bst+ appropriate for
\textit{Physical Review} and \textit{Reviews of Modern Physics},
respectively.

\subsubsection{Example references}
This sample file employs the \verb+\bibliography+ command, 
which formats the \texttt{\jobname .bbl} file
and specifies which bibliographic databases are to be used by Bib\TeX\ 
(one of these should be by arXiv convention \texttt{\jobname .bib}).
Running Bib\TeX\ (via \texttt{bibtex \jobname}) 
after the first pass of \LaTeX\ produces the file
\texttt{\jobname .bbl} which contains the automatically formatted
\verb+\bibitem+ commands (including extra markup information via
\verb+\bibinfo+ and \verb+\bibfield+ commands). 
If not using Bib\TeX, you will have to create the \verb+thebibiliography+ environment 
and its \verb+\bibitem+ commands by hand.

Numerous examples of the use of the APS bibliographic entry types appear in the bibliography of this sample document.
You can refer to the \texttt{\jobname .bib} file, 
and compare its information to the formatted bibliography itself.

\subsection{Footnotes}%
Footnotes, produced using the \verb+\footnote{#1}+ command, 
usually integrated into the bibliography alongside the other entries.
Numerical citation styles do this%
\footnote{Automatically placing footnotes into the bibliography requires using BibTeX to compile the bibliography.};
author-year citation styles place the footnote at the bottom of the text column.
Note: due to the method used to place footnotes in the bibliography, 
\emph{you must re-run Bib\TeX\ every time you change any of your document's footnotes}.

\section{Math and Equations}
Inline math may be typeset using the \verb+$+ delimiters. Bold math
symbols may be achieved using the \verb+bm+ package and the
\verb+\bm{#1}+ command it supplies. For instance, a bold $\alpha$ can
be typeset as \verb+$\bm{\alpha}$+ giving $\bm{\alpha}$. Fraktur and
Blackboard (or open face or double struck) characters should be
typeset using the \verb+\mathfrak{#1}+ and \verb+\mathbb{#1}+ commands
respectively. Both are supplied by the \texttt{amssymb} package. For
example, \verb+$\mathbb{R}$+ gives $\mathbb{R}$ and
\verb+$\mathfrak{G}$+ gives $\mathfrak{G}$

In \LaTeX\ there are many different ways to display equations, and a
few preferred ways are noted below. Displayed math will center by
default. Use the class option \verb+fleqn+ to flush equations left.

Below we have numbered single-line equations; this is the most common
type of equation in \textit{Physical Review}:
\begin{eqnarray}
\chi_+(p)\alt{\bf [}2|{\bf p}|(|{\bf p}|+p_z){\bf ]}^{-1/2}
\left(
\begin{array}{c}
|{\bf p}|+p_z\\
px+ip_y
\end{array}\right)\;,
\\
\left\{%
 \openone234567890abc123\alpha\beta\gamma\delta1234556\alpha\beta
 \frac{1\sum^{a}_{b}}{A^2}%
\right\}%
\label{eq:one}.
\end{eqnarray}
Note the open one in Eq.~(\ref{eq:one}).

Not all numbered equations will fit within a narrow column this
way. The equation number will move down automatically if it cannot fit
on the same line with a one-line equation:
\begin{equation}
\left\{
 ab12345678abc123456abcdef\alpha\beta\gamma\delta1234556\alpha\beta
 \frac{1\sum^{a}_{b}}{A^2}%
\right\}.
\end{equation}

When the \verb+\label{#1}+ command is used [cf. input for
Eq.~(\ref{eq:one})], the equation can be referred to in text without
knowing the equation number that \TeX\ will assign to it. Just
use \verb+\ref{#1}+, where \verb+#1+ is the same name that used in
the \verb+\label{#1}+ command.

Unnumbered single-line equations can be typeset
using the \verb+\[+, \verb+\]+ format:
\[g^+g^+ \rightarrow g^+g^+g^+g^+ \dots ~,~~q^+q^+\rightarrow
q^+g^+g^+ \dots ~. \]

\subsection{Multiline equations}

Multiline equations are obtained by using the \verb+eqnarray+
environment.  Use the \verb+\nonumber+ command at the end of each line
to avoid assigning a number:
\begin{eqnarray}
{\cal M}=&&ig_Z^2(4E_1E_2)^{1/2}(l_i^2)^{-1}
\delta_{\sigma_1,-\sigma_2}
(g_{\sigma_2}^e)^2\chi_{-\sigma_2}(p_2)\nonumber\\
&&\times
[\epsilon_jl_i\epsilon_i]_{\sigma_1}\chi_{\sigma_1}(p_1),
\end{eqnarray}
\begin{eqnarray}
\sum \vert M^{\text{viol}}_g \vert ^2&=&g^{2n-4}_S(Q^2)~N^{n-2}
        (N^2-1)\nonumber \\
 & &\times \left( \sum_{i<j}\right)
  \sum_{\text{perm}}
 \frac{1}{S_{12}}
 \frac{1}{S_{12}}
 \sum_\tau c^f_\tau~.
\end{eqnarray}
\textbf{Note:} Do not use \verb+\label{#1}+ on a line of a multiline
equation if \verb+\nonumber+ is also used on that line. Incorrect
cross-referencing will result. Notice the use \verb+\text{#1}+ for
using a Roman font within a math environment.

To set a multiline equation without \emph{any} equation
numbers, use the \verb+\begin{eqnarray*}+,
\verb+\end{eqnarray*}+ format:
\begin{eqnarray*}
\sum \vert M^{\text{viol}}_g \vert ^2&=&g^{2n-4}_S(Q^2)~N^{n-2}
        (N^2-1)\\
 & &\times \left( \sum_{i<j}\right)
 \left(
  \sum_{\text{perm}}\frac{1}{S_{12}S_{23}S_{n1}}
 \right)
 \frac{1}{S_{12}}~.
\end{eqnarray*}

To obtain numbers not normally produced by the automatic numbering,
use the \verb+\tag{#1}+ command, where \verb+#1+ is the desired
equation number. For example, to get an equation number of
(\ref{eq:mynum}),
\begin{equation}
g^+g^+ \rightarrow g^+g^+g^+g^+ \dots ~,~~q^+q^+\rightarrow
q^+g^+g^+ \dots ~. \tag{2.6$'$}\label{eq:mynum}
\end{equation}

\paragraph{A few notes on \texttt{tag}s} 
\verb+\tag{#1}+ requires the \texttt{amsmath} package. 
Place the \verb+\tag{#1}+ command before the \verb+\label{#1}+, if any. 
The numbering produced by \verb+\tag{#1}+ \textit{does not affect} 
the automatic numbering in REV\TeX; 
therefore, the number must be known ahead of time, 
and it must be manually adjusted if other equations are added. 
\verb+\tag{#1}+ works with both single-line and multiline equations. 
\verb+\tag{#1}+ should only be used in exceptional cases---%
do not use it to number many equations in your paper. 
Please note that this feature of the \texttt{amsmath} package
is \emph{not} compatible with the \texttt{hyperref} (6.77u) package.

Enclosing display math within
\verb+\begin{subequations}+ and \verb+\end{subequations}+ will produce
a set of equations that are labeled with letters, as shown in
Eqs.~(\ref{subeq:1}) and (\ref{subeq:2}) below.
You may include any number of single-line and multiline equations,
although it is probably not a good idea to follow one display math
directly after another.
\begin{subequations}
\label{eq:whole}
\begin{eqnarray}
{\cal M}=&&ig_Z^2(4E_1E_2)^{1/2}(l_i^2)^{-1}
(g_{\sigma_2}^e)^2\chi_{-\sigma_2}(p_2)\nonumber\\
&&\times
[\epsilon_i]_{\sigma_1}\chi_{\sigma_1}(p_1).\label{subeq:2}
\end{eqnarray}
\begin{equation}
\left\{
 abc123456abcdef\alpha\beta\gamma\delta1234556\alpha\beta
 \frac{1\sum^{a}_{b}}{A^2}
\right\},\label{subeq:1}
\end{equation}
\end{subequations}
Giving a \verb+\label{#1}+ command directly after the \verb+\begin{subequations}+, 
allows you to reference all the equations in the \texttt{subequations} environment. 
For example, the equations in the preceding subequations environment were
Eqs.~(\ref{eq:whole}).

\subsubsection{Wide equations}
The equation that follows is set in a wide format, i.e., it spans the full page. 
The wide format is reserved for long equations
that cannot easily be set in a single column:
\begin{widetext}
\begin{equation}
{\cal R}^{(\text{d})}=
 g_{\sigma_2}^e
 \left(
   \frac{[\Gamma^Z(3,21)]_{\sigma_1}}{Q_{12}^2-M_W^2}
  +\frac{[\Gamma^Z(13,2)]_{\sigma_1}}{Q_{13}^2-M_W^2}
 \right)
 + x_WQ_e
 \left(
   \frac{[\Gamma^\gamma(3,21)]_{\sigma_1}}{Q_{12}^2-M_W^2}
  +\frac{[\Gamma^\gamma(13,2)]_{\sigma_1}}{Q_{13}^2-M_W^2}
 \right)\;. 
 \label{eq:wideeq}
\end{equation}
\end{widetext}
This is typed to show how the output appears in wide format.
(Incidentally, since there is no blank line between the \texttt{equation} environment above 
and the start of this paragraph, this paragraph is not indented.)

\section{Cross-referencing}
REV\TeX{} will automatically number such things as
sections, footnotes, equations, figure captions, and table captions. 
In order to reference them in text, use the
\verb+\label{#1}+ and \verb+\ref{#1}+ commands. 
To reference a particular page, use the \verb+\pageref{#1}+ command.

The \verb+\label{#1}+ should appear 
within the section heading, 
within the footnote text, 
within the equation, or 
within the table or figure caption. 
The \verb+\ref{#1}+ command
is used in text at the point where the reference is to be displayed.  
Some examples: Section~\ref{sec:level1} on page~\pageref{sec:level1},
Table~\ref{tab:table1},%
\begin{table}[b]%The best place to locate the table environment is directly after its first reference in text
\caption{\label{tab:table1}%
A table that fits into a single column of a two-column layout. 
Note that REV\TeX~4 adjusts the intercolumn spacing so that the table fills the
entire width of the column. Table captions are numbered
automatically. 
This table illustrates left-, center-, decimal- and right-aligned columns,
along with the use of the \texttt{ruledtabular} environment which sets the 
Scotch (double) rules above and below the alignment, per APS style.
}
\begin{ruledtabular}
\begin{tabular}{lcdr}
\textrm{Left\footnote{Note a.}}&
\textrm{Centered\footnote{Note b.}}&
\multicolumn{1}{c}{\textrm{Decimal}}&
\textrm{Right}\\
\colrule
1 & 2 & 3.001 & 4\\
10 & 20 & 30 & 40\\
100 & 200 & 300.0 & 400\\
\end{tabular}
\end{ruledtabular}
\end{table}
and Fig.~\ref{fig:epsart}.%
\begin{figure}[b]
\includegraphics{fig_1}% Here is how to import EPS art
\caption{\label{fig:epsart} A figure caption. The figure captions are
automatically numbered.}
\end{figure}

\section{Floats: Figures, Tables, Videos, etc.}
Figures and tables are usually allowed to ``float'', which means that their
placement is determined by \LaTeX, while the document is being typeset.

Use the \texttt{figure} environment for a figure, the \texttt{table} environment for a table.
In each case, use the \verb+\caption+ command within to give the text of the
figure or table caption along with the \verb+\label+ command to provide
a key for referring to this figure or table.
The typical content of a figure is an image of some kind; 
that of a table is an alignment.%
\begin{figure*}
\includegraphics{fig_2}% Here is how to import EPS art
\caption{\label{fig:wide}Use the figure* environment to get a wide
figure that spans the page in \texttt{twocolumn} formatting.}
\end{figure*}
\begin{table*}
\caption{\label{tab:table3}This is a wide table that spans the full page
width in a two-column layout. It is formatted using the
\texttt{table*} environment. It also demonstates the use of
\textbackslash\texttt{multicolumn} in rows with entries that span
more than one column.}
\begin{ruledtabular}
\begin{tabular}{ccccc}
 &\multicolumn{2}{c}{$D_{4h}^1$}&\multicolumn{2}{c}{$D_{4h}^5$}\\
 Ion&1st alternative&2nd alternative&lst alternative
&2nd alternative\\ \hline
 K&$(2e)+(2f)$&$(4i)$ &$(2c)+(2d)$&$(4f)$ \\
 Mn&$(2g)$\footnote{The $z$ parameter of these positions is $z\sim\frac{1}{4}$.}
 &$(a)+(b)+(c)+(d)$&$(4e)$&$(2a)+(2b)$\\
 Cl&$(a)+(b)+(c)+(d)$&$(2g)$\footnotemark[1]
 &$(4e)^{\text{a}}$\\
 He&$(8r)^{\text{a}}$&$(4j)^{\text{a}}$&$(4g)^{\text{a}}$\\
 Ag& &$(4k)^{\text{a}}$& &$(4h)^{\text{a}}$\\
\end{tabular}
\end{ruledtabular}
\end{table*}

Insert an image using either the \texttt{graphics} or
\texttt{graphix} packages, which define the \verb+\includegraphics{#1}+ command.
(The two packages differ in respect of the optional arguments 
used to specify the orientation, scaling, and translation of the image.) 
To create an alignment, use the \texttt{tabular} environment.

The best place to locate the \texttt{figure} or \texttt{table} environment
is immediately following its first reference in text; this sample document
illustrates this practice for Fig.~\ref{fig:epsart}, which
shows a figure that is small enough to fit in a single column.

In exceptional cases, you will need to move the float earlier in the document, as was done
with Table~\ref{tab:table3}: \LaTeX's float placement algorithms need to know
about a full-page-width float earlier.

Fig.~\ref{fig:wide}
has content that is too wide for a single column,
so the \texttt{figure*} environment has been used.%
\begin{table}[b]
\caption{\label{tab:table4}%
Numbers in columns Three--Five are aligned with the ``d'' column specifier 
(requires the \texttt{dcolumn} package). 
Non-numeric entries (those entries without a ``.'') in a ``d'' column are aligned on the decimal point. 
Use the ``D'' specifier for more complex layouts. }
\begin{ruledtabular}
\begin{tabular}{ccddd}
One&Two&
\multicolumn{1}{c}{\textrm{Three}}&
\multicolumn{1}{c}{\textrm{Four}}&
\multicolumn{1}{c}{\textrm{Five}}\\
%\mbox{Three}&\mbox{Four}&\mbox{Five}\\
\hline
one&two&\mbox{three}&\mbox{four}&\mbox{five}\\
He&2& 2.77234 & 45672. & 0.69 \\
C\footnote{Some tables require footnotes.}
  &C\footnote{Some tables need more than one footnote.}
  & 12537.64 & 37.66345 & 86.37 \\
\end{tabular}
\end{ruledtabular}
\end{table}

The content of a table is typically a \texttt{tabular} environment, 
giving rows of type in aligned columns. 
Column entries separated by \verb+&+'s, and 
each row ends with \textbackslash\textbackslash. 
The required argument for the \texttt{tabular} environment
specifies how data are aligned in the columns. 
For instance, entries may be centered, left-justified, right-justified, aligned on a decimal
point. 
Extra column-spacing may be be specified as well, 
although REV\TeX~4 sets this spacing so that the columns fill the width of the
table. Horizontal rules are typeset using the \verb+\hline+
command. The doubled (or Scotch) rules that appear at the top and
bottom of a table can be achieved enclosing the \texttt{tabular}
environment within a \texttt{ruledtabular} environment. Rows whose
columns span multiple columns can be typeset using the
\verb+\multicolumn{#1}{#2}{#3}+ command (for example, see the first
row of Table~\ref{tab:table3}).%

Tables~\ref{tab:table1}, \ref{tab:table3}, \ref{tab:table4}, and \ref{tab:table2}%
\begin{table}[b]
\caption{\label{tab:table2}
A table with numerous columns that still fits into a single column. 
Here, several entries share the same footnote. 
Inspect the \LaTeX\ input for this table to see exactly how it is done.}
\begin{ruledtabular}
\begin{tabular}{cccccccc}
 &$r_c$ (\AA)&$r_0$ (\AA)&$\kappa r_0$&
 &$r_c$ (\AA) &$r_0$ (\AA)&$\kappa r_0$\\
\hline
Cu& 0.800 & 14.10 & 2.550 &Sn\footnotemark[1]
& 0.680 & 1.870 & 3.700 \\
Ag& 0.990 & 15.90 & 2.710 &Pb\footnotemark[2]
& 0.450 & 1.930 & 3.760 \\
Au& 1.150 & 15.90 & 2.710 &Ca\footnotemark[3]
& 0.750 & 2.170 & 3.560 \\
Mg& 0.490 & 17.60 & 3.200 &Sr\footnotemark[4]
& 0.900 & 2.370 & 3.720 \\
Zn& 0.300 & 15.20 & 2.970 &Li\footnotemark[2]
& 0.380 & 1.730 & 2.830 \\
Cd& 0.530 & 17.10 & 3.160 &Na\footnotemark[5]
& 0.760 & 2.110 & 3.120 \\
Hg& 0.550 & 17.80 & 3.220 &K\footnotemark[5]
&  1.120 & 2.620 & 3.480 \\
Al& 0.230 & 15.80 & 3.240 &Rb\footnotemark[3]
& 1.330 & 2.800 & 3.590 \\
Ga& 0.310 & 16.70 & 3.330 &Cs\footnotemark[4]
& 1.420 & 3.030 & 3.740 \\
In& 0.460 & 18.40 & 3.500 &Ba\footnotemark[5]
& 0.960 & 2.460 & 3.780 \\
Tl& 0.480 & 18.90 & 3.550 & & & & \\
\end{tabular}
\end{ruledtabular}
\footnotetext[1]{Here's the first, from Ref.~\onlinecite{feyn54}.}
\footnotetext[2]{Here's the second.}
\footnotetext[3]{Here's the third.}
\footnotetext[4]{Here's the fourth.}
\footnotetext[5]{And etc.}
\end{table}
show various effects.
A table that fits in a single column employs the \texttt{table}
environment. 
Table~\ref{tab:table3} is a wide table, set with the \texttt{table*} environment. 
Long tables may need to break across pages. 
The most straightforward way to accomplish this is to specify
the \verb+[H]+ float placement on the \texttt{table} or
\texttt{table*} environment. 
However, the \LaTeXe\ package \texttt{longtable} allows headers and footers to be specified for each page of the table. 
A simple example of the use of \texttt{longtable} can be found
in the file \texttt{summary.tex} that is included with the REV\TeX~4
distribution.

There are two methods for setting footnotes within a table (these
footnotes will be displayed directly below the table rather than at
the bottom of the page or in the bibliography). The easiest
and preferred method is just to use the \verb+\footnote{#1}+
command. This will automatically enumerate the footnotes with
lowercase roman letters. However, it is sometimes necessary to have
multiple entries in the table share the same footnote. In this case,
there is no choice but to manually create the footnotes using
\verb+\footnotemark[#1]+ and \verb+\footnotetext[#1]{#2}+.
\texttt{\#1} is a numeric value. Each time the same value for
\texttt{\#1} is used, the same mark is produced in the table. The
\verb+\footnotetext[#1]{#2}+ commands are placed after the \texttt{tabular}
environment. Examine the \LaTeX\ source and output for
Tables~\ref{tab:table1} and \ref{tab:table2}
for examples.

Video~\ref{vid:PRSTPER.4.010101} 
illustrates several features new with REV\TeX4.2,
starting with the \texttt{video} environment, which is in the same category with
\texttt{figure} and \texttt{table}.%
\begin{video}
\href{http://prst-per.aps.org/multimedia/PRSTPER/v4/i1/e010101/e010101_vid1a.mpg}{\includegraphics{vid_1a}}%
 \quad
\href{http://prst-per.aps.org/multimedia/PRSTPER/v4/i1/e010101/e010101_vid1b.mpg}{\includegraphics{vid_1b}}
 \setfloatlink{http://link.aps.org/multimedia/PRSTPER/v4/i1/e010101}%
 \caption{\label{vid:PRSTPER.4.010101}%
  Students explain their initial idea about Newton's third law to a teaching assistant. 
  Clip (a): same force.
  Clip (b): move backwards.
 }%
\end{video}
The \verb+\setfloatlink+ command causes the title of the video to be a hyperlink to the
indicated URL; it may be used with any environment that takes the \verb+\caption+
command.
The \verb+\href+ command has the same significance as it does in the context of
the \texttt{hyperref} package: the second argument is a piece of text to be 
typeset in your document; the first is its hyperlink, a URL.

\textit{Physical Review} style requires that the initial citation of
figures or tables be in numerical order in text, so don't cite
Fig.~\ref{fig:wide} until Fig.~\ref{fig:epsart} has been cited.

\begin{acknowledgments}
We wish to acknowledge the support of the author community in using
REV\TeX{}, offering suggestions and encouragement, testing new versions,
\dots.
\end{acknowledgments}

\appendix

\section{Appendixes}

To start the appendixes, use the \verb+\appendix+ command.
This signals that all following section commands refer to appendixes
instead of regular sections. Therefore, the \verb+\appendix+ command
should be used only once---to setup the section commands to act as
appendixes. Thereafter normal section commands are used. The heading
for a section can be left empty. For example,
\begin{verbatim}
\appendix
\section{}
\end{verbatim}
will produce an appendix heading that says ``APPENDIX A'' and
\begin{verbatim}
\appendix
\section{Background}
\end{verbatim}
will produce an appendix heading that says ``APPENDIX A: BACKGROUND''
(note that the colon is set automatically).

If there is only one appendix, then the letter ``A'' should not
appear. This is suppressed by using the star version of the appendix
command (\verb+\appendix*+ in the place of \verb+\appendix+).

\section{A little more on appendixes}

Observe that this appendix was started by using
\begin{verbatim}
\section{A little more on appendixes}
\end{verbatim}

Note the equation number in an appendix:
\begin{equation}
E=mc^2.
\end{equation}

\subsection{\label{app:subsec}A subsection in an appendix}

You can use a subsection or subsubsection in an appendix. Note the
numbering: we are now in Appendix~\ref{app:subsec}.

Note the equation numbers in this appendix, produced with the
subequations environment:
\begin{subequations}
\begin{eqnarray}
E&=&mc, \label{appa}
\\
E&=&mc^2, \label{appb}
\\
E&\agt& mc^3. \label{appc}
\end{eqnarray}
\end{subequations}
They turn out to be Eqs.~(\ref{appa}), (\ref{appb}), and (\ref{appc}).

% The \nocite command causes all entries in a bibliography to be printed out
% whether or not they are actually referenced in the text. This is appropriate
% for the sample file to show the different styles of references, but authors
% most likely will not want to use it.
\nocite{*}

\bibliography{apssamp}% Produces the bibliography via BibTeX.

\end{document}
%
% ****** End of file apssamp.tex ******

### 2020-04-13 main.tex
Updates from Overleaf

\documentclass[%
 reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-2}

\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{hyperref}% add hypertext capabilities
\usepackage{graphicx} % Include figure files
\graphicspath{{Figures/}} %Setting the graphicspath

\begin{document}

\preprint{APS/123-QED}

\title{A Bayesian search to find \\high-mass black holes using LIGO data}% Force line breaks with \\

\author{Author list TBD}

\date{\today}

\begin{abstract}
The detection of high mass black holes ( $>100$ M${}_\odot$) will shed light on the formation of supermassive black holes and thus galaxy formation. Although LIGO is theoretically sensitive to the merger of binary black holes with total masses up to 500 M${}_\odot$, the largest total mass detected so far is approximately 80 M${}_\odot$. A possible explanation for the absence of high mass events may be due to their misclassification as short-duration instrumental noise transients. Short-duration instrumental transients mimic the short-duration gravitational-wave signals from high-mass binary black hole mergers. Here we demonstrate that a new search method utilising Bayesian inference could be a more sensitive tool for detecting high-mass binary black hole mergers as compared to traditional match-filtering. We have applied this technique on the high-mass triggers during LIGO's second observing run to investigate the possibility of discovering new gravitational-wave signals from an entirely new class of high mass black hole binaries.

\end{abstract}

\maketitle

%\tableofcontents

%%%%%%---SECTIONS---%%%%%%%%%%%%
\section{\label{sec:Introduction}Introduction}

\begin{itemize}
    \item blip glitches and other short duration glitches occur very often
    \item searches have to down-weight short duration foreground triggers because of high occurrence rate of short duration glitches
    \item searches do not use CBC templates -- BCR can improve significance~\cite{BCR1}.
    \item BCR can help give true significance, or $p_{astro}$ of foreground triggers
\end{itemize}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{example-image-a}
    \caption{Some caption.}
    \label{fig:somefig}
\end{figure}

Since the 1970s, there has been an accumulation of evidence for stellar-mass and supermassive black holes. In 2019, the Event Horizon Telescope provided the first visual evidence of the supermassive black hole M87.  As of January 2020, LIGO has confirmed ten binary black hole systems, and more than fifty public binary black hole alerts. These various discoveries have firmly established the existence of stellar-mass black holes, supermassive black holes and binary black hole systems.  Interestingly, there is still no direct evidence for intermediate-mass black holes, the black holes that lie in between stellar-mass and supermassive black hole systems (footnote on indirect measurements). Thus, their existence is still speculative.

If intermediate-mass black holes are present, the gravitational waves emitted from the merger of a binary black hole system with at least one intermediate-mass black hole (up to a mass of 400 Msun) will be detectable by the ground-based gravitational-wave network. According to \citet{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions}, gravitational waves from such systems within the detection of the ground-based detectors should occur at rates of one to up to ten events per year.  Hence it is peculiar that there still has not been a gravitational wave event from such a high-mass system.

One explanation for the absence of a detection may be due to the low merger frequency of the high-mass systems. The ground-based detectors are much less sensitive at lower frequencies due to various noise sources (e.g. thermal, suspension noise). Another difficulty with the low frequencies is the presence of transient short-duration instrumental non-Gaussian features, known as glitches, in the interferometer's recorded data. Some of the short duration glitches can occur as often as a few times every hour. These short-duration glitches are challenging to distinguish from the short-duration gravitational wave signals of high-mass binary black hole.

This paper discusses a novel method to identify and distinguish these high-mass gravitational wave signals from short-duration glitches in gravitational-wave data. It then employs the method on the PyCBC high-mass triggers from O2 and provides frequentistic estimates of the significance of various gravitational-wave candidates and events.

\section{\label{sec:OutlineOfPipelineMethods}Outline of Pipeline Methods}

\begin{itemize}
    \item briefly explain PyCBC search
    \item define triggers
    \item Extract PyCBC foreground, background and software injection trigger's GPS times based on template duration of triggers
    \item analyse the triggers using Bayesian Parameter Estimation to determine $\log{Z_s}$, $\log{Z_g}$ and $\log{Z_n}$
    \item calculate BCR
    \item Remove outlier BCRs using median method
    \item Calculate PDFs
    \item Find $\alpha$ and $\beta$ values such that separation of background and software injection PDFs is maximally apart.
    \item use tuned $\alpha$ and $\beta$ from previous step to calculate BCRs for foreground
    \item calculate the $p_{astro}$ of the foreground events to determine the probability of the trigger being from an astrophysical source. 
\end{itemize}

\section{\label{sec:Analysis}O2 Sub-threshold Event Analysis}
\hyperlink{https://docs.google.com/spreadsheets/d/1hm7lFsYneY8NGbFDr-vH5YYsILrxcTexO9D1AvF1qJo/edit?usp=sharing}{Important triggers spreadsheet}
\begin{itemize}
    \item BCRs of O2 sub-threshold high mass events
    \item BCRs of Princeton group's high-mass  events
\end{itemize}

\section{\label{sec:Conclusion}Conclusion}
Since the 1970s, there has been 
%%%%%%---SECTIONS-END---%%%%%%%%%%%%

%%%%%%---ACKNOWLEDGEMENTS---%%%%%%%%%%%%
\begin{acknowledgments}
helpful comments, OzGrav, LIGO, NSF

\end{acknowledgments}
%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\section{Appendixes}
%%%%%%%%%%%%%%%%%%%%%%%%

\bibliography{high_mass_bib}% Produces the bibliography via BibTeX.

\end{document}
%
% ****** End of file apssamp.tex ******

### 2020-05-13 main.tex
Updates from Overleaf

@@
 In 2019, the Event Horizon Telescope provided the first visual evidence of the supermassive black hole M87.
-As of January 2020, LIGO has confirmed ten binary black hole systems, and more than fifty public binary black hole alerts.
+As of January 2020, LIGO has confirmed ten binary black hole systems, and more than fifty public binary black hole alerts [CITE].
 These various discoveries have firmly established the existence of stellar-mass black holes, supermassive black holes and binary black hole systems.
-Interestingly, there is still no direct evidence for intermediate-mass black holes, the black holes that lie in between stellar-mass and supermassive black hole systems (footnote on indirect measurements).
-Thus, their existence is still speculative.
+Interestingly, there is still no direct evidence for intermediate-mass black holes, the black holes that lie in between stellar-mass and supermassive black hole systems with masses between $10^2-10^6 \text{M}_\odot$.
+Thus, the existence of intermediate-mass black holes is still speculative.
 
-If intermediate-mass black holes are present, the gravitational waves emitted from the merger of a binary black hole system with at least one intermediate-mass black hole (up to a mass of 400 Msun) will be detectable by the ground-based gravitational-wave network.
+If intermediate-mass black holes are present, the gravitational waves emitted from the merger of a binary black hole system with at least one intermediate-mass black hole (up to a mass of $400 \text{M}_\odot$) will be detectable by the ground-based gravitational-wave network.
 According to \citet{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions}, gravitational waves from such systems within the detection of the ground-based detectors should occur at rates of one to up to ten events per year.
-Hence it is peculiar that there still has not been a gravitational wave event from such a high-mass system.
+Hence it is peculiar that LIGO has not detected a gravitational wave event from a system with a total mass greater than $80 \text{M}_\odot$.
 
-One explanation for the absence of a detection may be due to the low merger frequency of the high-mass systems.
+A foreground trigger is a section of LIGO data identified by data searching pipelines to potentially harbour some
+gravitational wave signal (more on triggers in Appendix\textasciitilde\ref{searches}). In the ground-based gravitational wave
+detectors, many spurious instrumental noise events fool the pipelines into considering the noise events as triggers
+(false-positive triggers). These instrumental-triggers are called glitches. Luckily, unlike triggers from astrophysical
+sources, glitches do not often occur at the same time or with the same morphology across the various gravitational wave
+detectors -- they are often \emph{incoherent} amongst detectors. Additionally, these short-duration glitches appear very
+similar to high-mass gravitational-wave signals, making the two challenging to distinguish.
+
+One explanation for the absence of detections may be due to the low merger frequency of the high-mass systems.
 The ground-based detectors are much less sensitive at lower frequencies due to various noise sources (e.g.
@@
 Another difficulty with the low frequencies is the presence of transient short-duration instrumental non-Gaussian features, known as glitches, in the interferometer's recorded data.
-Some of the short duration glitches can occur as often as a few times every hour.
-These short-duration glitches are challenging to distinguish from the short-duration gravitational wave signals of high-mass binary black hole.
+Some of the short duration glitches can occur as often as a few times every hour~\cite{blipGlitches}.
+These short-duration glitches are challenging to distinguish from the short-duration gravitational-wave signals that we expect to see from high-mass binary black holes.
+
+The high occurrence rate of short duration glitches down-weight the significance of short duration LIGO foreground triggers, GPS times marking sections of LIGO data to potentially harbour gravitational wave signals.
 
@@
 It then employs the method on the PyCBC high-mass triggers from O2 and provides frequentistic estimates of the significance of various gravitational-wave candidates and events.
+
+This paper is organized as follows: Section 2 provides an overview of the search
+pipeline and the methods used to detect gravitational waves from compact-object
+binaries in LIGO data. Section 3 gives a description of the developments implemented
+in this pipeline. Section 4 compares the performance of the new pipeline to that of the
+pipeline that analyzed the sixth LIGO science run and Virgo’s second and third science
+runs [27]. Finally, Section 5 summarizes our findings and suggests directions for future
+improvements.
 
@@
 
+\section{Significance of a high-mass Bayesian Search}\label{significance}}
+
+There are two primary motivations for a targeted high-mass search that utilises Bayesian inference. The first is to help
+distinguish gravitataional-waves from high-mass systems from noise-transients, and the second is to try to alleviate the
+discord in the significance of some of the ``quiet'' gravitational wave events between various search pipelines.
+
+\hypertarget{a-better-detection-statistic}{%
+\subsection{A better Detection-statistic}\label{a-better-detection-statistic}}
+
+\hypertarget{gravitational-wave-triggers-and-short-duration-glitches}{%
+\subsubsection{Gravitational-wave triggers and short duration glitches}\label{gravitational-wave-triggers-and-short-duration-glitches}}
+
+A foreground trigger is a section of LIGO data identified by data searching pipelines to potentially harbour some
+gravitational wave signal (more on triggers in Appendix\textasciitilde\ref{searches}). In the ground-based gravitational wave
+detectors, many spurious instrumental noise events fool the pipelines into considering the noise events as triggers
+(false-positive triggers). These instrumental-triggers are called glitches. Luckily, unlike triggers from astrophysical
+sources, glitches do not often occur at the same time or with the same morphology across the various gravitational wave
+detectors -- they are often \emph{incoherent} amongst detectors. Additionally, these short-duration glitches appear very
+similar to high-mass gravitational-wave signals, making the two challenging to distinguish. For example, consider
+Figure\textasciitilde\ref{fig:compareGlitchAndSignal} that compares a plot of a glitch on the left and a plot of a high-mass GW
+candidate on the right.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.45\linewidth]{images/glitch} \includegraphics[width=0.45\linewidth]{images/L1_spectrogram_logy_0}
+
+}
+
+\caption[Comparing glitches to high-mass candidates.]{Spectrogram of a glitch on the left, and a candidate GW trigger on the right.}\label{fig:compareGlitchAndSignal}
+\end{figure}
+
+\hypertarget{assigning-significance-to-gravitational-wave-triggers}{%
+\subsection{Assigning significance to Gravitational-wave triggers}\label{assigning-significance-to-gravitational-wave-triggers}}
+
+The LIGO-Virgo collaboration uses various methods to avoid marking false-positive glitch triggers as gravitational wave
+triggers. One method first involves generating a set of \emph{background triggers}, false-positives picked up from the search
+through artificially\footnote{The artificial gravitational wave data
+  should have no true gravitational waves as it is constructed by applying relative time offsets between the data of different detectors (time offsets longer than the light-travel time between the detectors).} created gravitational
+wave data containing no signals. Then, a detection-statistic value, a value
+that ranks the likelihood of a trigger to originate from a gravitational-wave signal, is calculated for both the
+foreground and background triggers.
+Finally, the background trigger detection-statistic distribution can assign a probability to the \emph{null hypothesis} that the foreground triggers are consistent with the background.
+This null hypothesis probability is obtained by first calculating the cumulative distribution function for the background distribution.
+Placing the foreground event on the background cumulative distribution function provides the \emph{p-value}, or false alarm probability, of the foreground event.
+This p-value is a measure of how significant indicating the foreground event is from the background distribution of false-positives.
+
+For example, consider the
+detection-statistic plot for GW150914, as seen in Figure\textasciitilde\ref{fig:GW150914background}. If the
+foreground triggers are far away from the background trigger distribution, the foreground triggers have low p-values (and are significantly
+different from the background). Hence, the low p-values foreground triggers might originate from astrophysical sources. On the other hand, if the foreground
+triggers fall along with the background distribution with high p-values, the foreground triggers are consistent with the background. Thus,
+they are less likely to originate from astrophysical sources.
+
+\begin{figure}[!h]
+
+{\centering \includegraphics[width=0.75\linewidth]{images/GW150914_background}
+
+}
+
+\caption[Ranking statistic plot for GW150914]{A binary coalescence search displaying a number of candidate GW events (orange markers) and the mean number of background events (black line), taken from \citet{abbott2016observation}.}\label{fig:GW150914background}
+\end{figure}
+
+\hypertarget{a-bayesian-detection-statistic}{%
+\subsection{A Bayesian Detection statistic}\label{a-bayesian-detection-statistic}}
+
+Comparing foreground events to a background distribution is a ``frequentist'' method of assigning significance. It does
+not use the literal meaning of the likelihood -- which is a probability -- or compute the posterior probability of there
+being a signal given data and hypotheses. By using a frequentist method of assigning significance, these searches
+discard the physical meaning of the likelihood. In principle, a Bayesian approach would be able to incorporate this
+information that is lost.
+
+The goal of this PhD's first project is to enhance the significance of high-mass foreground triggers using a Bayesian
+approach and thereby increase the confidence in the detection of gravitational waves from large-mass compact binaries.
+If this work does improve the significance of high-mass triggers, we will increase the likelihood of detecting a
+high-mass black hole system via gravitational waves. The detection statistic we will utilise is the Bayesian Coherence
+Ratio (or BCR), as seen in \citet{bcr_paper}. The BCR is discussed in detail in Appendix\textasciitilde\ref{BayesianCoherenceRatio}. In
+short, The \texttt{BCR} is an odds (evidence ratio) comparing two hypotheses: there's a coherent GW in the data, plus Gaussian
+noise vs there's only incoherent Gaussian noise or a glitch (modeled as a compact binary coalescence) in each detector
+\citep{bcr_paper}.
+
+\hypertarget{a-better-measure-of-significance}{%
+\section{A better measure of significance}\label{a-better-measure-of-significance}}
+
+\hypertarget{gravitational-wave-candidates-with-uncertain-significance}{%
+\subsection{Gravitational wave candidates with uncertain significance}\label{gravitational-wave-candidates-with-uncertain-significance}}
+
+In aLIGO's first two observing runs, eleven gravitational wave events were found in the data by the LIGO-Virgo
+scientific collaboration \citep{abbott2019gwtc}. Since the public release of LIGO's first and second observing run's data,
+several groups have searched the data for gravitational waves independently of LIGO. One particular research group of
+interest is a research team at the Institute for Advanced Study (IAS). The group constructed searches to look for the
+LIGO-confirmed the gravitational wave events detected by the LIGO-Virgo collaboration, and in the process of doing so,
+claim to have discovered several others events \citep{IAS0, IAS1, IAS2}.
+Some of these events have total masses \(>85 M_{\odot}\), which is larger than the average total mass of the LIGO detections.
+Some of these IAS and LIGO events are
+displayed in Table\textasciitilde\ref{tab:O2significancesWObcr} with their p-astro reported by various LIGO and IAS search pipelines.
+
+\begin{table}[t]
+
+\caption[p-astro for various O2 foreground triggers]{\label{tab:O2significancesWObcr}p-astro from seveal detection pipelines for a subset of the O2 foreground triggers.}
+\centering
+\begin{tabular}{llrrrr}
+\toprule
+Event & Catalog & PyCBC & GstLAL & cWB & IAS\\
+\midrule
+GW170104 & GWTC-1 & 1.00 & 1.00 & 1.00 & 0.99\\
+GW170121 & IAS-1 & NA & NA & NA & 0.99\\
+GWC170402 & IAS-2 & NA & 0.09 & NA & 0.68\\
+GW170403 & IAS-1 & NA & NA & NA & 0.56\\
+IMBHC170423 & IMBH-marginal & NA & 0.00 & 1.00 & NA\\
+\addlinespace
+GW170425 & IAS-1 & NA & NA & NA & 0.77\\
+GW170729 & GWTC-1 & 0.52 & 0.98 & 0.94 & NA\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+From this Table\textasciitilde\ref{tab:O2significancesWObcr}, it is evident there is some uncertainty if these events can be considered real
+gravitational-wave events -- are these events significantly different from the background or not? The various pipelines
+have different answers. Our Bayesian search pipeline, as described in the next section, can help us answer this question
+and come to a conclusion about the significance of the events.
+
+\hypertarget{using-the-bcr-to-calculate-significance}{%
+\subsection{Using the BCR to calculate significance}\label{using-the-bcr-to-calculate-significance}}
+
+While the BCR might not increase the significance of some of the gravitational wave candidates, it will provide a more
+accurate measure of their significance. The BCR significance will be more accurate as it is a measure of the probability
+that signals in two or more detectors are \emph{coherent} (signals share exactly the same source properties in the different
+detectors) vs the detectors having \emph{incoherent} glitches/noise. This Bayesian significance might alleviate the discord
+between the significances of specific foreground triggers reported by various search pipelines.
+
+In summary, we will use the BCR to analyse high-mass foreground triggers to help discern signals from glitches and
+provide a better measure of significance for the foreground triggers. For our work, we will initially focus on
+conducting this BCR search on O2 data, and subsequently with a search in O3 data.
+
+\hypertarget{methodology}{%
+\chapter{Methodology}\label{methodology}}
+
+This PhD project intends to provide new methods and insights to studying gravitational waves form high-mass systems.
+Thus far, the project has focused on building up the infrastructure to compare the Bayesian Coherence Ratio of LIGO's
+time-shifted \emph{background} triggers, \emph{foreground} triggers and \emph{software injections}. This chapter describes how we have
+adapted the methods from \citet{bcr_paper} in our implementation.
+
+\hypertarget{selecting-o3-triggers-for-bcr-analysis}{%
+\section{Selecting O3 Triggers for BCR analysis}\label{selecting-o3-triggers-for-bcr-analysis}}
+
+LIGO's third observing run, O3, began on April, 2019, and is going until May 2020 (with a commissioning break during
+October). In the 35 observing weeks since O3 started, based off the \(\sim50\) public alerts for gravitational wave
+candidate triggers, LIGO might have tripled the number of detections during all of the first and second observing runs,
+O1 and O2 \citep{gracedb}. These gravitational wave events are considered candidates, as LIGO is still in the process of vetting the
+candidates (making sure that they are from astrophysical sources rather than terrestrial, spurious noise sources). On
+top of these candidate triggers, there are numerous sub-threshold triggers (triggers that do not have high
+significance).
+
+Ideally, we would like to compute the BCRs for all triggers (foreground and background) produced by LIGO to help improve
+the significance of astrophysically real triggers and decrease the significance of glitches. However, computational
+limitations prevent analysis of all triggers. Instead, we limit the data to several 8-day chunks from O2, selected based
+on the number of foreground triggers identified by \href{https://pycbc.org/}{\texttt{PyCBC}} in the various chunks, as seen in
+Figure\textasciitilde\ref{fig:o2TrigCount}. Currently, we are using O2 data as it is public, whereas O3 data is not. By analyzing O2
+triggers we can publish our results without any restrictions imposed by LIGO.
+
+\begin{figure}[!h]
+
+{\centering \includegraphics[width=0.75\linewidth]{images/O2_unfiltered_trigger_counts}
+
+}
+
+\caption[Count of all triggers in PyCBC O2 search]{Counts of triggers from \texttt{PyCBC}'s search through O2 Data (November 15, 2016 - August 26, 2017).
+Each chunk is roughly 8 days long.
+The background triggers are collected from timesliding each chunk's data to generate a dataset of roughly 3 million years.}\label{fig:o2TrigCount}
+\end{figure}
+
+Additionally, to confine our search to high-mass sources (systems with total masses roughly between 50-500
+\(M_{\odot}\)), we restrict the triggers corresponding to a gravitational wave template with durations less than 454 ms.
+These short duration templates correspond to compact binary coalesences with the parameters presented in
+Table\textasciitilde\ref{tab:parameters} and the search space for these triggers can be visualised in Figure\textasciitilde\ref{fig:templateBank}.
+
+\begin{table}[t]
+
+\caption[BBH parameters corresponding to durations $<454$ ms]{\label{tab:parameters}Template Banks's parameters for templates with duration $<454$ ms.}
+\centering
+\begin{tabular}{lrr}
+\toprule
+  & Minimum & Maximmum\\
+\midrule
+Component Mass 1 $[\text{M}_{\odot}]$ & 31.54 & 491.68\\
+Component Mass 2 $[\text{M}_{\odot}]$ & 1.32 & 121.01\\
+Total Mass $[\text{M}_{\odot}]$ & 56.93 & 496.72\\
+Chirp Mass $[\text{M}_{\odot}]$ & 8.00 & 174.56\\
+Mass Ratio & 0.01 & 0.98\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{figure}[!h]
+
+{\centering \includegraphics[width=0.75\linewidth]{images/template_bank_masses}
+
+}
+
+\caption[High-mass BCR search space.]{The template bank used by \href{https://pycbc.org/}{\texttt{PyCBC}} to search in O2's chunk 14.
+Our search is constrained to the high-mass parameter space enclosed by the dashed line (triggers with diurations \(<45s\).}\label{fig:templateBank}
+\end{figure}
+
+By restricting the \href{https://pycbc.org/}{\texttt{PyCBC}} triggers only based on the template duration, we acquire common (high FAR) and rare (low
+FAR) triggers. It would be straightforward in principle to broaden our template-duration constraint to encompass all
+triggers produced by all the various search pipelines. However, we refrain from doing so to keep our computational costs
+manageable. A plot of the counts of the triggers in O2 after downsampling the triggers based on the template duration
+can be viewed in Figure\textasciitilde\ref{fig:o2FilteredTrigCount}.
+
+\begin{figure}[!h]
+
+{\centering \includegraphics[width=0.75\linewidth]{images/O2_filtered_trigger_counts}
+
+}
+
+\caption[Count of triggers in PyCBC O2 search shorter than 454 ms]{Counts of triggers from \texttt{PyCBC}'s search through O2 Data, filtered to include only the triggers with a duration less than 454 ms}\label{fig:o2FilteredTrigCount}
+\end{figure}
+
+\hypertarget{bcr-analysis-procedure}{%
+\section{BCR Analysis Procedure}\label{bcr-analysis-procedure}}
+
+\hypertarget{computational-setup}{%
+\subsection{Computational setup}\label{computational-setup}}
+
+To compute the evidence making up the BCR (described in Section\textasciitilde\ref{bcrCalculation}), we use \href{https://lscsoft.docs.ligo.org/bilby_pipe/}{\texttt{bilby\_pipe}} to acquire
+the LIGO data in 4s-long data segments containing each trigger (analysis segments) and run the nested-sampling algorithm
+implemented in the \texttt{dynesty} library. We utilise \href{https://lscsoft.docs.ligo.org/bilby_pipe/}{\texttt{bilby\_pipe}} to generate PSDs via Welch's method for each data
+segment by taking 128 seconds of the data before the analysis segment. If the data quality is not marked as `Science
+Mode' for either the PSD or analysis data, then the analysis of that trigger is skipped. Gravitational-wave templates
+are produced using \texttt{IMRPhenomPv2} \footnote{\texttt{IMRPhenomPv2} is a standard phenomenological waveform model constructed in the
+  frequency domain that models the inspiral, merger, and ringdown (IMR) of a compact binary coalescence with aligned spins
+  \citep{khan2016frequency}.}. Although gravitational wave templates that are created from numerical relativity simulations
+incorporate more physics than \texttt{IMRPhenomPv2}, we still use this waveform as it is faster to evaluate than numerical
+relativity models.
+
+\hypertarget{bayesian-parameter-estimation}{%
+\subsection{Bayesian Parameter Estimation}\label{bayesian-parameter-estimation}}
+
+We restrict the priors for Bayesian parameter estimation on the masses such that we only consider signals that are less
+than 454ms in duration, as presented in Table\textasciitilde\ref{tab:parameters}. The spins are set to be aligned with a range from
+{[}0,1{]}. The prior on luminosity distance assigns probability uniformly in comoving volume, with an upper cutoff of 5 Gpc.
+The \href{https://pycbc.org/}{\texttt{PyCBC}} search that originally produced our set of triggers considered a more comprehensive range of masses and
+spins than we do in the BCR computation for this project. To accommodate this, we prescreened the triggers to only allow
+triggers with masses within our priors. The run time on a single trigger using the \href{https://arxiv.org/abs/1904.02180}{\texttt{dynesty}} implementation of nested
+sampling, with \(2,000\) live points and \(100\) walkers is usually between \(0.5-12\) hours (where the speed often depends on
+the SNR of the data segment).
+
+\hypertarget{bcrCalculation}{%
+\subsection{BCR calculation}\label{bcrCalculation}}
+
+The Bayesian coherence ratio (BCR), as seen in \citet{bcr_paper}, is the odds between the hypothesis that the data comprise a
+coherent, compact binary coalescence signal in Gaussian noise (\(\mathcal{H}_S\)), and the hypothesis that they instead
+comprise incoherent instrumental features (\(\mathcal{H}_I\))---meaning each detector has either a glitch in Gaussian noise
+(\(\mathcal{H}_N\)) or pure Gaussian noise (\(\mathcal{H}_G\)). For a network of \(D\) detectors,
+
+\begin{equation}
+\mathrm{BCR} = \frac{\alpha Z^{S}}{\prod_{i=1}^{D}\left[\beta Z_{i}^{G}+(1-\beta) Z_{i}^{N}\right]}\ , \label{eq:bcr}
+\end{equation}
+where \(Z^S\) is the evidence for \(\mathcal{H}_S\), and \(Z^{G}_i\) and
+\(Z^N_i\) are the evidences for \(\mathcal{H}_{Gi}\) and \(\mathcal{H}_{Ni}\),
+in the \(i^{\text{th}}\) detectors. The arbitrary weights \(\alpha\) and \(\beta\)
+parametrize our prior belief in each model:
+
+\begin{itemize}
+\tightlist
+\item
+  \(\alpha = P(\mathcal{H}_S)/P(\mathcal{H}_I)\)
+\item
+  \(\beta = P(\mathcal{H}_{Gi}|\mathcal{H}_I)=1-P(\mathcal{H}_{N}|\mathcal{H}_I)\)
+\end{itemize}
+
+for all \(i\) detectors. As most of the data should be noise, we expect both \(\alpha\) and \(\beta\), to be less than 1.
+These parameters will be tuned to minimize the overlap between the signal and noise trigger populations.
+
+\hypertarget{trigger-sets-for-bcr-analysis}{%
+\subsection{Trigger sets for BCR analysis}\label{trigger-sets-for-bcr-analysis}}
+
+We calculate the BCRs using the procedure described above for three separate trigger sets: background triggers,
+foreground triggers, and software injections. The software injections created using masses, spins and distances that
+span our priors. The software injections are inserted in the O2 data from where the other triggers are retrieved.
+
+We expect the background trigger BCRs to favour the incoherent glitch hypothesis, and the software injection BCRs to
+favour the coherent, compact binary coalescence hypothesis. The foreground trigger BCRs should fall along with the
+background if the foreground trigger is a glitch, and with the software injections if the foreground trigger is a
+gravitational wave candidate. For example, consider Figure\textasciitilde\ref{fig:bcrIfar} that contains a plot of the BCRs for
+several O1 background triggers, foreground triggers, and software injections plotted against iFAR (inverse
+false-alarm-rate). In the figure, some foreground triggers fall along the background distribution, these are discarded
+as glitches. The foreground triggers that fall along the bulk of software injections are considered gravitational wave
+candidates.
+
+\begin{figure}[!h]
+
+{\centering \includegraphics[width=0.75\linewidth]{images/bcr_ifar}
+
+}
+
+\caption[BCR vs iFAR for O1]{BCR versus iFAR distributions from simulated signals (blue), hardware injections (green), GW events (stars) and background triggers (black), taken from \citet{bcr_paper}.}\label{fig:bcrIfar}
+\end{figure}
+
+\hypertarget{making-a-significance-statement}{%
+\subsection{Making a significance statement}\label{making-a-significance-statement}}
+
+After obtaining the BCRs for the foreground triggers, background triggers, and software injections, we can make a
+statement about the significance of foreground events. For example, consider Figure\textasciitilde\ref{fig:bcrCdf} which displays ln
+BCR distributions obtained from our BCR pipeline for aLIGO O2 PyCBC chunk three background triggers and software injections.
+The figure also displays the ln BCR values obtained for four foreground triggers. The two foreground triggers with low
+ln BCRs are confirmed glitches. The rightmost foreground trigger is GW170104, a gravitational wave event confirmed by
+LIGO, and shows much stronger evidence for it being a coherent, compact binary coalescence signal, rather than it being
+an incoherent glitch. The remaining foreground trigger corresponds to a gravitational wave candidate identified by the
+IAS group.
+
+\begin{figure}[!h]
+
+{\centering \includegraphics[width=0.75\linewidth]{images/bcr_cdf}
+
+}
+
+\caption[BCR distribution example]{Histograms represent the survival function (1-CDF) from our selection of 2407 aLIGO O2 PyCBC chunk 3 background triggers (gray) and 648 simulated signals (blue).
+Vertical lines mark the ln BCRs of two glitches (orange and yellow), IAS's GW170121 (pink), and GWTC-1's GW170104 (dark blue).}\label{fig:bcrCdf}
+\end{figure}
+
+Irrespective of the BCR's Bayesian interpretation, we may treat the BCR as a traditional detection statistic to obtain a
+frequentist estimate of the significance of any given foreground event based on the measured background with a p-value.
+The p-value of foreground events can be obtained from the background's survival function. For example, in
+Figure\textasciitilde\ref{fig:bcrCdf}, the p-value for GW170104 is 0.99, denoting that it is significantly different from the bulk
+of the background distribution and hence likely to have astrophysical origins. On the other hand, the p-value for the
+IAS candidate is 0.65, demonstrating that this candidate might be a glitch.
+
+To calculate the p-value, we need first to calculate fits to the BCR probability
+distributions and then tune the BCR's parameters. The following subsections describe these calculations.
+
+\hypertarget{fitting-bcr-data}{%
+\subsubsection{Fitting BCR data}\label{fitting-bcr-data}}
+
+Although the BCR should favour the coherent signal hypothesis for software injections,
+software injections with a very low SNR might not look coherent amongst an ensemble of
+detectors. Hence, software injections are likely to have two probability distributions
+of BCRs, one probability distribution of low BCRs corresponding to the software
+injections that have very low SNRs and another probability distribution of software
+injections with high BCRs. Due to this, we use Gaussian mixture models with two Gaussian
+components to fit our BCR distributions.
+
+\hypertarget{tuning-of-bcr-using-kl-distance}{%
+\subsubsection{Tuning of BCR using KL Distance}\label{tuning-of-bcr-using-kl-distance}}
+
+The BCR has two tunable parameters as described in Section\textasciitilde\ref{bcrCalculation},
+\(\alpha\) and \(\beta\). Altering \(\alpha\) translates the BCR probability distributions for
+the triggers while adjusting \(\beta\) spreads the probability distributions out. Although
+Bayesian hyper-parameter estimation might be able to determine the optimal values for
+these parameters, an easier approach is to manually adjust the parameters for each data
+chunk's BCR distribution. In this study, we manually adjust \(\alpha\) and \(\beta\) to
+maximally separate the BCR distributions for the software injections and background
+triggers.
+
+To calculate the separation between the background and software injection BCR
+distributions, we use the Kullback--Leibler divergence (also called relative entropy, or
+KL divergence) to quantify how different how the background and software injection BCR
+probability distributions are. If the distributions are identical, the KL divergence is
+equal to 0, and the KL divergence increases as the asymmetry between the distributions
+increases. Figure\textasciitilde\ref{fig:klDivGrid} displays a contour plot of O2 Chunk 14's KL
+divergences between the background and software injection triggers for values of
+\(\alpha\) and \(\beta\) ranging from \(1^{-10}\) to \(1\). We select these ranges for \(\alpha\)
+and \(\beta\) as values outside this range will not make physical sense. Note that for a
+fixed value of \(\beta\), the KL divergence stays the same as we alter \(\alpha\). This is
+because \(\alpha\) translates the BCR values, but does not alter the distributions
+themselves.
+
+\begin{figure}[!h]
+
+{\centering \includegraphics[width=0.75\linewidth]{images/kl_divergence_grid}
+
+}
+
+\caption[KL Divergence grid for both BCR tunable parameters]{KL Divergences for O2 Chunk 14's software injection and background trigger BCR probability distributions.
+The red line indicates the \(\alpha\) and \(\beta\) parameters with the maximum KL divergence in this range of \(\alpha\) and \(\beta\).}\label{fig:klDivGrid}
+\end{figure}
+
+Figure\textasciitilde\ref{fig:klDivLine} displays a plot of O2 Chunk 14's KL divergences only as
+\(\beta\) is adjusted for a fixed \(alpha=1^{-6}\). The \(\alpha\) and \(\beta\) are then selected
+based on the combination that results with the maximum KL divergence.
+
+\begin{figure}[!h]
+
+{\centering \includegraphics[width=0.75\linewidth]{images/kl_distance_14}
+
+}
+
+\caption[KL Divergences for one BCR tunable parameter]{KL Divergences for O2 Chunk 14's software injection and background trigger BCR probability distributions with \(alpha=1^{-6}\).}\label{fig:klDivLine}
+\end{figure}
+
+In Chapter\textasciitilde\ref{progress} we present some of the preliminary BCR search results we
+have obtained from the analysis of various O2 data chunks.
+
 \section{\label{sec:Analysis}O2 Sub-threshold Event Analysis}
@@
 \section{\label{sec:Conclusion}Conclusion}
-Since the 1970s, there has been 
+The detection of high mass black holes (\(>100\) M\({}_\odot\)) will shed light on the formation of globular clusters,
+supermassive black holes and thus galaxy formation \citep{lodato2006supermassive, 2018IMBHreview}. LIGO is theoretically
+sensitive to the merger of binary black holes with total masses up to 500 M\({}_\odot\) which are expected to occur at a
+rate of 0-10 yr\(^{-1}\) \citep[\citet{mandel2008rates}]{fregeau2006imbhbRatePrediction}. However, even after \citet{salemi2019search}'s
+targeted match-filter based search for gravitational waves from high-mass black holes the largest total mass detected so
+far is approximately 80 M\({}_\odot\) \citep{abbott2019gwtc}. A possible explanation for the absence of high mass events may be
+due to their misclassification as short-duration instrumental noise transients \citep{blipGlitches}. High-mass mergers have
+very few in-band wave cycles, and hence can easily be mistaken for short-duration instrumental transients. More details
+on the theorised formation channels and merger rates are discussed in Appendix \ref{literature}.
+
+The focus of this PhD is on improving our scientific understanding of these high-mass binary black hole systems. We
+start by developing a targeted search for gravitational waves from high-mass black hole systems. This new targeted
+search utilises Bayesian inference and thus is a more sensitive tool for detecting high-mass binary black hole mergers
+as compared to traditional match-filtering searches. We have applied this technique on the high-mass triggers during
+LIGO's second observing run to investigate the possibility of discovering new gravitational-wave signals from an
+entirely new class of high mass black hole binaries.
 %%%%%%---SECTIONS-END---%%%%%%%%%%%%

### 2020-06-24 main.tex
Committed by TeXstudio

@@
 The detection of high mass black holes ( $>100$ M${}_\odot$) will shed light on the formation of supermassive black holes and thus galaxy formation.
-Although LIGO is theoretically sensitive to the merger of binary black holes with total masses up to 500 M${}_\odot$, the largest total mass detected so far is approximately 80 M${}_\odot$.
+Although LIGO is sensitive to the merger of binary black holes with total masses up to 500 M${}_\odot$, the largest total mass detected so far is approximately 80 M${}_\odot$.
 A possible explanation for the absence of high mass events may be due to their misclassification as short-duration instrumental noise transients.
@@
 
-\begin{itemize}
-    \item blip glitches and other short duration glitches occur very often
-    \item searches have to down-weight short duration foreground triggers because of high occurrence rate of short duration glitches
-    \item searches do not use CBC templates -- BCR can improve significance~\cite{BCR1}.
-    \item BCR can help give true significance, or $p_{astro}$ of foreground triggers
-\end{itemize}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{example-image-a}
-    \caption{Some caption.}
-    \label{fig:somefig}
-\end{figure}
+ LIGO is theoretically
+sensitive to the merger of binary black holes with total masses up to 500 M\({}_\odot\) which are expected to occur at a
+rate of 0-10 yr\(^{-1}\) \citep[\citet{mandel2008rates}]{fregeau2006imbhbRatePrediction}. However, even after \citet{salemi2019search}'s
+targeted match-filter based search for gravitational waves from high-mass black holes the largest total mass detected so
+far is approximately 80 M\({}_\odot\) \citep{abbott2019gwtc}. A possible explanation for the absence of high mass events may be
+due to their misclassification as short-duration instrumental noise transients \citep{blipGlitches}. High-mass mergers have
+very few in-band wave cycles, and hence can easily be mistaken for short-duration instrumental transients.
 
 Since the 1970s, there has been an accumulation of evidence for stellar-mass and supermassive black holes.
-In 2019, the Event Horizon Telescope provided the first visual evidence of the supermassive black hole M87.
-As of January 2020, LIGO has confirmed ten binary black hole systems, and more than fifty public binary black hole alerts [CITE].
+In 2019, the Event Horizon Telescope provided the first visual evidence of the supermassive black hole M87  \cite{m87photo}.
+As of January 2020, LIGO has confirmed ten binary black hole systems, and more than fifty public binary black hole alerts \cite{gw190814}.
 These various discoveries have firmly established the existence of stellar-mass black holes, supermassive black holes and binary black hole systems.
@@
 If intermediate-mass black holes are present, the gravitational waves emitted from the merger of a binary black hole system with at least one intermediate-mass black hole (up to a mass of $400 \text{M}_\odot$) will be detectable by the ground-based gravitational-wave network.
-According to \citet{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions}, gravitational waves from such systems within the detection of the ground-based detectors should occur at rates of one to up to ten events per year.
-Hence it is peculiar that LIGO has not detected a gravitational wave event from a system with a total mass greater than $80 \text{M}_\odot$.
+According to \citet{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions}, gravitational waves from such systems within the detection of the ground-based detectors should occur at a rate of 0-10 yr\(^{-1}\) .
+However, even after \citet{salemi2019search}'s
+targeted match-filter based search for gravitational waves from high-mass black holes the largest total mass detected so
+far is approximately 80 M\({}_\odot\) \citep{abbott2019gwtc}. A possible explanation for the absence of high mass events may be
+due to their misclassification as short-duration instrumental noise transients \citep{blipGlitches}. As demonstrated in ___ High-mass mergers have
+very few in-band wave cycles, and hence can easily be mistaken for short-duration instrumental transients.
 
@@
 
-The focus of this PhD is on improving our scientific understanding of these high-mass binary black hole systems. We
-start by developing a targeted search for gravitational waves from high-mass black hole systems. This new targeted
+We start by developing a targeted search for gravitational waves from high-mass black hole systems. This new targeted
 search utilises Bayesian inference and thus is a more sensitive tool for detecting high-mass binary black hole mergers
@@
 \begin{acknowledgments}
-helpful comments, OzGrav, LIGO, NSF
+Helpful comments, OzGrav, LIGO, NSF
 

### 2020-06-24 main.tex
Committed by TeXstudio

@@
 %floatfix,
-]{revtex4-2}
+]{revtex4}
 
@@
 
- LIGO is theoretically
-sensitive to the merger of binary black holes with total masses up to 500 M\({}_\odot\) which are expected to occur at a
-rate of 0-10 yr\(^{-1}\) \citep[\citet{mandel2008rates}]{fregeau2006imbhbRatePrediction}. However, even after \citet{salemi2019search}'s
-targeted match-filter based search for gravitational waves from high-mass black holes the largest total mass detected so
-far is approximately 80 M\({}_\odot\) \citep{abbott2019gwtc}. A possible explanation for the absence of high mass events may be
-due to their misclassification as short-duration instrumental noise transients \citep{blipGlitches}. High-mass mergers have
-very few in-band wave cycles, and hence can easily be mistaken for short-duration instrumental transients.
-
 Since the 1970s, there has been an accumulation of evidence for stellar-mass and supermassive black holes.
@@
 far is approximately 80 M\({}_\odot\) \citep{abbott2019gwtc}. A possible explanation for the absence of high mass events may be
-due to their misclassification as short-duration instrumental noise transients \citep{blipGlitches}. As demonstrated in ___ High-mass mergers have
+due to their misclassification as short-duration instrumental noise transients \citep{blipGlitches}. As demonstrated in ?? High-mass mergers have
 very few in-band wave cycles, and hence can easily be mistaken for short-duration instrumental transients.
@@
 
-\section{Significance of a high-mass Bayesian Search}\label{significance}}
+\section{Significance of a high-mass Bayesian Search}\label{significance}
 
@@
 \begin{tabular}{llrrrr}
-\toprule
 Event & Catalog & PyCBC & GstLAL & cWB & IAS\\
-\midrule
 GW170104 & GWTC-1 & 1.00 & 1.00 & 1.00 & 0.99\\
@@
 IMBHC170423 & IMBH-marginal & NA & 0.00 & 1.00 & NA\\
-\addlinespace
 GW170425 & IAS-1 & NA & NA & NA & 0.77\\
 GW170729 & GWTC-1 & 0.52 & 0.98 & 0.94 & NA\\
-\bottomrule
 \end{tabular}

### 2020-06-24 main.tex
Committed by TeXstudio

@@
   & Minimum & Maximmum\\
-\midrule
 Component Mass 1 $[\text{M}_{\odot}]$ & 31.54 & 491.68\\
@@
 Mass Ratio & 0.01 & 0.98\\
-\bottomrule
 \end{tabular}

### 2020-06-24 main.tex
Committed by TeXstudio

@@
 Thus, the existence of intermediate-mass black holes is still speculative.
+\\
 
@@
 targeted match-filter based search for gravitational waves from high-mass black holes the largest total mass detected so
-far is approximately 80 M\({}_\odot\) \citep{abbott2019gwtc}. A possible explanation for the absence of high mass events may be
-due to their misclassification as short-duration instrumental noise transients \citep{blipGlitches}. As demonstrated in ?? High-mass mergers have
+far is approximately 80 M\({}_\odot\) \cite{abbott2019gwtc}. A possible explanation for the absence of high mass events may be
+due to their misclassification as short-duration instrumental noise transients \cite{blipGlitches}. As demonstrated in ?? High-mass mergers have
 very few in-band wave cycles, and hence can easily be mistaken for short-duration instrumental transients.
@@
 
-\hypertarget{methodology}{%
-\chapter{Methodology}\label{methodology}}
-
+\section{Methodology}\label{methodology}
 This PhD project intends to provide new methods and insights to studying gravitational waves form high-mass systems.
@@
 \begin{itemize}
-\tightlist
 \item

### 2020-06-24 main.tex
Committed by TeXstudio

@@
 far is approximately 80 M\({}_\odot\) \cite{abbott2019gwtc}. A possible explanation for the absence of high mass events may be
-due to their misclassification as short-duration instrumental noise transients \cite{blipGlitches}. As demonstrated in ?? High-mass mergers have
+due to their misclassification as short-duration instrumental noise transients \cite{blip_glitches}. As demonstrated in ?? High-mass mergers have
 very few in-band wave cycles, and hence can easily be mistaken for short-duration instrumental transients.

### 2020-06-24 main.tex
Committed by TeXstudio

@@
 If intermediate-mass black holes are present, the gravitational waves emitted from the merger of a binary black hole system with at least one intermediate-mass black hole (up to a mass of $400 \text{M}_\odot$) will be detectable by the ground-based gravitational-wave network.
-According to \citet{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions}, gravitational waves from such systems within the detection of the ground-based detectors should occur at a rate of 0-10 yr\(^{-1}\) .
-However, even after \citet{salemi2019search}'s
-targeted match-filter based search for gravitational waves from high-mass black holes the largest total mass detected so
-far is approximately 80 M\({}_\odot\) \cite{abbott2019gwtc}. A possible explanation for the absence of high mass events may be
-due to their misclassification as short-duration instrumental noise transients \cite{blip_glitches}. As demonstrated in ?? High-mass mergers have
+According to \citet{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions}, gravitational waves from such systems should occur at a rate of 0-10 yr\(^{-1}\) .
+However, even after \citet{salemi2019search}'s targeted match-filter based search for gravitational waves from high-mass black holes the largest total mass detected so far is approximately 80 M\({}_\odot\) \cite{abbott2019gwtc}.
+A possible explanation for the absence of high mass events may be
+due to their misclassification as short-duration instrumental noise transients \cite{blip_glitches}.
+
+% PyCBC asks for the 5 citations:
+% http://pycbc.org/pycbc/latest/html/credit.html#searches-for-compact-binary-coalescence
+
+Search algorithms for gravitational waves from coalescing compact binaries, such as PyCBC \cite{pycbc_code}, have tried to account for these short-duration glitches \cite{pycbc_short_duration_transients}.
+At its core, PyCBC performs a matched-filter search for binary merger signals using a bank of gravitational-wave template waveforms \cite{pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5}.
+To account for the short-duration glitches,
+
+ to As demonstrated in \citet{blip_glitches},  High-mass mergers have
 very few in-band wave cycles, and hence can easily be mistaken for short-duration instrumental transients.

### 2020-08-19 main.tex
add introduction

@@
 
+\newcommand{\prior}{{\sc prior}\xspace}
+\newcommand{\bilby}{{\sc Bilby}\xspace}
+\newcommand{\bilbypipe}{{\sc bilby\_pipe}\xspace}
+\newcommand{\bilbypipegdb}{\texttt{bilby\_pipe\_gracedb}\xspace}
+\newcommand{\pbilby}{{\sc pBilby}\xspace}
+\newcommand{\dynesty}{{\sc dynesty}\xspace}
+\newcommand{\cpnest}{{\sc cpnest}\xspace}
+\newcommand{\ptemcee}{{\sc ptemcee}\xspace}
+\newcommand{\gwpy}{{\sc GWpy}\xspace}
+\newcommand{\imrphenomp}{{\sc IMRPhenomPv2}\xspace}
+\newcommand{\pycbc}{{\sc PyCBC}\xspace}
+\newcommand{\msun}{{M${}_\odot$}\xspace}
+
 \begin{document}
@@
 
-\title{A Bayesian search to find \\high-mass black holes using LIGO data}% Force line breaks with \\
+\title{A Bayesian search to find \\high-mass black holes in  LIGO data}% Force line breaks with \\
 
@@
 \begin{abstract}
-The detection of high mass black holes ( $>100$ M${}_\odot$) will shed light on the formation of supermassive black holes and thus galaxy formation.
-Although LIGO is sensitive to the merger of binary black holes with total masses up to 500 M${}_\odot$, the largest total mass detected so far is approximately 80 M${}_\odot$.
+The detection of high mass black holes ( $>100$ \msun) will shed light on the formation of supermassive black holes and thus galaxy formation.
+Although LIGO is sensitive to the merger of binary black holes with total masses up to 500 \msun, the largest total mass detected so far is approximately 80 \msun.
 A possible explanation for the absence of high mass events may be due to their misclassification as short-duration instrumental noise transients.
@@
 In 2019, the Event Horizon Telescope provided the first visual evidence of the supermassive black hole M87  \cite{m87photo}.
-As of January 2020, LIGO has confirmed ten binary black hole systems, and more than fifty public binary black hole alerts \cite{gw190814}.
+As of January 2020, LIGO, Virgo and IAS have confirmed more than a dozen binary black hole systems \cite{GWTC1, IAS0, IAS1, IAS2}.
 These various discoveries have firmly established the existence of stellar-mass black holes, supermassive black holes and binary black hole systems.
-Interestingly, there is still no direct evidence for intermediate-mass black holes, the black holes that lie in between stellar-mass and supermassive black hole systems with masses between $10^2-10^6 \text{M}_\odot$.
+Interestingly, there is still no direct evidence for intermediate-mass black holes, the black holes that lie in between stellar-mass and supermassive black hole systems with masses between $10^2-10^6$ \msun.
 Thus, the existence of intermediate-mass black holes is still speculative.
@@
 
-If intermediate-mass black holes are present, the gravitational waves emitted from the merger of a binary black hole system with at least one intermediate-mass black hole (up to a mass of $400 \text{M}_\odot$) will be detectable by the ground-based gravitational-wave network.
-According to \citet{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions}, gravitational waves from such systems should occur at a rate of 0-10 yr\(^{-1}\) .
-However, even after \citet{salemi2019search}'s targeted match-filter based search for gravitational waves from high-mass black holes the largest total mass detected so far is approximately 80 M\({}_\odot\) \cite{abbott2019gwtc}.
-A possible explanation for the absence of high mass events may be
-due to their misclassification as short-duration instrumental noise transients \cite{blip_glitches}.
+If intermediate-mass black holes are present, the gravitational waves emitted from the merger of a binary black hole system with at least one intermediate-mass black hole (up to a mass of $400$ \msun) will be detectable by the ground-based gravitational-wave network.
+Gravitational waves from such systems should occur at a rate of $0-10\text {yr}^{-1}$ \cite{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions}.
+However, even after conducting a targeted match-filter based search for gravitational waves from intermediate-mass black holes the largest total mass detected so far is approximately $80$ \msun \cite{salemi2019search, abbott2019gwtc}.
+A possible explanation for the absence of intermediate-mass events may be due to their misclassification as short-duration instrumental noise transients \cite{blip_glitches}.
+These glitches can mimic astrophysical signals and hence decrease the significance of true gravitational wave events.
 
+One method to account for glitches while searching for gravitational waves from coalescing compact binaries is by utilising a signal consistency test \cite{pycbc_short_duration_transients} or a signal coherence test amongst a network of detectors \cite{bci, bcr_paper,  bcr_gw151216, bayesian_odds}.
+A signal-coherence test such as the Bayesian coherence ratio (BCR) \cite{bcr_paper} provides an odds ratio comparing the probability that the data contains an astrophysical signal versus the probability that the data contains an incoherent glitch or noise.
+Although an odds ratio, the BCR can be used  as a ranking statistic to calculate the statistical significance of candidate gravitational-wave signals from compact binary coalescences in the detector data \cite{bcr_paper}.
+
+In this paper we utilise the BCR to calculate $p_\text{astro}$, the probability that a signal is of astrophysical origin [cite],  for all the high-mass (systems with total masses in the range of $55-500$ \msun) candidate gravitational-wave signals from compact binary coalescences in the detector data recorded during aLIGO's second observing run (O2).
+We find that (a) our search does not identify any new stellar mass or intermediate mass black holes; (b) all events reported in the GWTC-1, including GW170729 (an event with disputed $p_\text{astro}$ amongst various search pipelines) have high $p_\text{astro}$; and that (c) events
+
+is an odds ratio
+
+presents the method and results from analysing the candidate events with
+
+\section{PyCBC}
 % PyCBC asks for the 5 citations:
@@
 
+ such as \pycbc \cite{pycbc_code} have tried to account for these short-duration glitches \cite{pycbc_short_duration_transients}. 
 Search algorithms for gravitational waves from coalescing compact binaries, such as PyCBC \cite{pycbc_code}, have tried to account for these short-duration glitches \cite{pycbc_short_duration_transients}.

### 2020-08-19 main.tex
add introduction

@@
 The detection of high mass black holes ( $>100$ \msun) will shed light on the formation of supermassive black holes and thus galaxy formation.
-Although LIGO is sensitive to the merger of binary black holes with total masses up to 500 \msun, the largest total mass detected so far is approximately 80 \msun.
+Although LIGO is sensitive to the merger of binary black holes with total masses up to 500 \msun, the largest total mass detected so far is approximately $80$ \msun.
 A possible explanation for the absence of high mass events may be due to their misclassification as short-duration instrumental noise transients.
@@
 If intermediate-mass black holes are present, the gravitational waves emitted from the merger of a binary black hole system with at least one intermediate-mass black hole (up to a mass of $400$ \msun) will be detectable by the ground-based gravitational-wave network.
-Gravitational waves from such systems should occur at a rate of $0-10\text {yr}^{-1}$ \cite{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions}.
+Gravitational waves from such systems should occur at a rate of $0-10\text{yr}^{-1}$ \cite{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions}.
 However, even after conducting a targeted match-filter based search for gravitational waves from intermediate-mass black holes the largest total mass detected so far is approximately $80$ \msun \cite{salemi2019search, abbott2019gwtc}.
@@
 In this paper we utilise the BCR to calculate $p_\text{astro}$, the probability that a signal is of astrophysical origin [cite],  for all the high-mass (systems with total masses in the range of $55-500$ \msun) candidate gravitational-wave signals from compact binary coalescences in the detector data recorded during aLIGO's second observing run (O2).
-We find that (a) our search does not identify any new stellar mass or intermediate mass black holes; (b) all events reported in the GWTC-1, including GW170729 (an event with disputed $p_\text{astro}$ amongst various search pipelines) have high $p_\text{astro}$; and that (c) events
-
-is an odds ratio
-
-presents the method and results from analysing the candidate events with
+We find that (a) our search does not identify any new stellar mass or intermediate mass black holes; (b) high-mass events reported in the GWTC-1, including GW170729 (an event with disputed $p_\text{astro}$ amongst various search pipelines) have high $p_\text{astro}$; and that (c) high-mass events detected from independent groups have low $p_\text{astro}$.
 

### 2020-08-19 main.tex
work on methods

@@
 \newcommand{\pycbc}{{\sc PyCBC}\xspace}
+\newcommand{\bcr}{{\sc BCR}\xspace}
+\newcommand{\pastro}{{$p_\text{astro}$}\xspace}
 \newcommand{\msun}{{M${}_\odot$}\xspace}
-
 \begin{document}
@@
 One method to account for glitches while searching for gravitational waves from coalescing compact binaries is by utilising a signal consistency test \cite{pycbc_short_duration_transients} or a signal coherence test amongst a network of detectors \cite{bci, bcr_paper,  bcr_gw151216, bayesian_odds}.
-A signal-coherence test such as the Bayesian coherence ratio (BCR) \cite{bcr_paper} provides an odds ratio comparing the probability that the data contains an astrophysical signal versus the probability that the data contains an incoherent glitch or noise.
-Although an odds ratio, the BCR can be used  as a ranking statistic to calculate the statistical significance of candidate gravitational-wave signals from compact binary coalescences in the detector data \cite{bcr_paper}.
+A signal-coherence test such as the Bayesian coherence ratio (\bcr) \cite{bcr_paper} provides a Bayesian odds ratio comparing the probability that the data contains an astrophysical signal versus the probability that the data contains an incoherent glitch or noise.
+Although an odds ratio, the \bcr can be used  as a frequentistic \textit{ranking statistic}, ranking the likelihood that a trigger is due to a gravitational-wave signal \cite{bcr_paper}.
+The \bcr as a ranking statistic is much more powerful than a matched-filter SNR as the \bcr incorporates numerous features that may distinguish gravitational waves from noise and demands that signals must be coherent while glitches must be incoherent amongst different detectors.
 
-In this paper we utilise the BCR to calculate $p_\text{astro}$, the probability that a signal is of astrophysical origin [cite],  for all the high-mass (systems with total masses in the range of $55-500$ \msun) candidate gravitational-wave signals from compact binary coalescences in the detector data recorded during aLIGO's second observing run (O2).
-We find that (a) our search does not identify any new stellar mass or intermediate mass black holes; (b) high-mass events reported in the GWTC-1, including GW170729 (an event with disputed $p_\text{astro}$ amongst various search pipelines) have high $p_\text{astro}$; and that (c) high-mass events detected from independent groups have low $p_\text{astro}$.
+In this paper we utilise the \bcr to calculate \pastro, the probability that a signal is of astrophysical origin [cite],  for all the high-mass (systems with total masses in the range of $55-500$ \msun) candidate gravitational-wave signals from compact binary coalescences in the detector data recorded during aLIGO's second observing run (O2).
+We find that (a) our search does not identify any new stellar mass or intermediate mass black holes; (b) high-mass events reported in the GWTC-1, including GW170729 (an event with disputed $p_\text{astro}$ amongst various search pipelines) have high \pastro; and that (c) high-mass events detected from independent groups have low \pastro.
 
-\section{PyCBC}
+\section{Method}
+
 % PyCBC asks for the 5 citations:
 % http://pycbc.org/pycbc/latest/html/credit.html#searches-for-compact-binary-coalescence
+Following \citet{bcr_paper}, the \bcr is an odds ratio of the coherent signal hypotheses $mathcal{H_S}$ and the incoherent instrumental feature hypothesis $mathcal{H_I}$. It is given by
+\begin{equation}
+BCR = \frac{\alpha Z^S}{\Pi^D_{i=1}[\beta Z^G_i + (1-\beta)Z^N_i]}\ .
+\end{equation}
+The numerator is the probability of obtaining a coherent signal, where $Z^S$ is the evidence for $\mathcal{H_S}$ and $\alpha$ is the prior odds for obtaining a signal $\alpha=P(\mathcal{H_S})/P(\mathcal{H_I})$.
+The denominator is the probability of obtaining an incoherent glitch or noise amongst the network of $D$ detectors, where $Z_G_i$ and $Z_N_i$ are the evidence for obtaining a glitch in detector $i$ and the evidence for obtaining just noise in detector $i$.
 
- such as \pycbc \cite{pycbc_code} have tried to account for these short-duration glitches \cite{pycbc_short_duration_transients}. 
-Search algorithms for gravitational waves from coalescing compact binaries, such as PyCBC \cite{pycbc_code}, have tried to account for these short-duration glitches \cite{pycbc_short_duration_transients}.
-At its core, PyCBC performs a matched-filter search for binary merger signals using a bank of gravitational-wave template waveforms \cite{pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5}.
-To account for the short-duration glitches,
+We use a Bayesian framework to calculate the \bcr for high-mass candidate events, simulated signal events and  background events (signal-free events ) supplied by the \pycbc \cite{pycbc_code} search in O2  \cite{pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5}.
+At its core, \pycbc performs a matched-filter search for binary merger signals using a template-bank of gravitational-wave template waveforms to generate triggers.
+For the trigger to be considered a  candidate event by \pycbc, it must be observed between detectors with the same template and with a time of arrival difference less than the gravitational-wave travel time between detectors \cite{pycbc_og0}.
+The simulated signal events are artificially created by injecting signals into the detector data.
+Similarly, \pycbc artificially constructs the background, signal-free, events by applying relative offsets, or time-shifts, between the data of different detectors \cite{pycbc_og0}.
 
- to As demonstrated in \citet{blip_glitches},  High-mass mergers have
-very few in-band wave cycles, and hence can easily be mistaken for short-duration instrumental transients.
+Figure~\ref{fig:templateBank} depicts the \pycbc template bank, the high-mass search space and the candidate events, simulated events and background events from a one-week stretch of \pycbc's search in O2.
 
-A foreground trigger is a section of LIGO data identified by data searching pipelines to potentially harbour some
-gravitational wave signal (more on triggers in Appendix\textasciitilde\ref{searches}). In the ground-based gravitational wave
-detectors, many spurious instrumental noise events fool the pipelines into considering the noise events as triggers
-(false-positive triggers). These instrumental-triggers are called glitches. Luckily, unlike triggers from astrophysical
-sources, glitches do not often occur at the same time or with the same morphology across the various gravitational wave
-detectors -- they are often \emph{incoherent} amongst detectors. Additionally, these short-duration glitches appear very
-similar to high-mass gravitational-wave signals, making the two challenging to distinguish.
+Week long stretches of analysis because noise-non stationary, glitches will occur at different rates depending on state of detectors
 
-One explanation for the absence of detections may be due to the low merger frequency of the high-mass systems.
-The ground-based detectors are much less sensitive at lower frequencies due to various noise sources (e.g.
-thermal, suspension noise).
-Another difficulty with the low frequencies is the presence of transient short-duration instrumental non-Gaussian features, known as glitches, in the interferometer's recorded data.
-Some of the short duration glitches can occur as often as a few times every hour~\cite{blipGlitches}.
-These short-duration glitches are challenging to distinguish from the short-duration gravitational-wave signals that we expect to see from high-mass binary black holes.
-
-The high occurrence rate of short duration glitches down-weight the significance of short duration LIGO foreground triggers, GPS times marking sections of LIGO data to potentially harbour gravitational wave signals.
-
-This paper discusses a novel method to identify and distinguish these high-mass gravitational wave signals from short-duration glitches in gravitational-wave data.
-It then employs the method on the PyCBC high-mass triggers from O2 and provides frequentistic estimates of the significance of various gravitational-wave candidates and events.
-
-This paper is organized as follows: Section 2 provides an overview of the search
-pipeline and the methods used to detect gravitational waves from compact-object
-binaries in LIGO data. Section 3 gives a description of the developments implemented
-in this pipeline. Section 4 compares the performance of the new pipeline to that of the
-pipeline that analyzed the sixth LIGO science run and Virgo’s second and third science
-runs [27]. Finally, Section 5 summarizes our findings and suggests directions for future
-improvements.
-
-\section{\label{sec:OutlineOfPipelineMethods}Outline of Pipeline Methods}
+Dont know the prior odds,
 
@@
 	\item analyse the triggers using Bayesian Parameter Estimation to determine $\log{Z_s}$, $\log{Z_g}$ and $\log{Z_n}$
-    \item calculate BCR
-    \item Remove outlier BCRs using median method
+	\item reweight results to account for uncertainties in PSDs
+	\item Calculate BCR
 	\item Calculate PDFs
@@
 \end{itemize}
+
+\section{\label{sec:OutlineOfPipelineMethods}Outline of Pipeline Methods}
 

### 2020-08-20 main.tex
Updates from Overleaf

--- 2020-08-19 main.tex
@@
 %floatfix,
-]{revtex4}
+]{revtex4-2}
 
@@
 \graphicspath{{Figures/}} %Setting the graphicspath
-
-\newcommand{\prior}{{\sc prior}\xspace}
-\newcommand{\bilby}{{\sc Bilby}\xspace}
-\newcommand{\bilbypipe}{{\sc bilby\_pipe}\xspace}
-\newcommand{\bilbypipegdb}{\texttt{bilby\_pipe\_gracedb}\xspace}
-\newcommand{\pbilby}{{\sc pBilby}\xspace}
-\newcommand{\dynesty}{{\sc dynesty}\xspace}
-\newcommand{\cpnest}{{\sc cpnest}\xspace}
-\newcommand{\ptemcee}{{\sc ptemcee}\xspace}
-\newcommand{\gwpy}{{\sc GWpy}\xspace}
-\newcommand{\imrphenomp}{{\sc IMRPhenomPv2}\xspace}
-\newcommand{\pycbc}{{\sc PyCBC}\xspace}
-\newcommand{\msun}{{M${}_\odot$}\xspace}
 
@@
 \begin{abstract}
-The detection of high mass black holes ( $>100$ \msun) will shed light on the formation of supermassive black holes and thus galaxy formation.
-Although LIGO is sensitive to the merger of binary black holes with total masses up to 500 \msun, the largest total mass detected so far is approximately $80$ \msun.
+The detection of high mass black holes ( $>100$ M${}_\odot$) will shed light on the formation of super-massive black holes and thus galaxy formation.
+Although LIGO is theoretically sensitive to the merger of binary black holes with total masses up to 500 M${}_\odot$, the largest total mass detected so far is approximately 80 M${}_\odot$.
 A possible explanation for the absence of high mass events may be due to their misclassification as short-duration instrumental noise transients.
@@
 
-Since the 1970s, there has been an accumulation of evidence for stellar-mass and supermassive black holes.
-In 2019, the Event Horizon Telescope provided the first visual evidence of the supermassive black hole M87  \cite{m87photo}.
-As of January 2020, LIGO, Virgo and IAS have confirmed more than a dozen binary black hole systems \cite{GWTC1, IAS0, IAS1, IAS2}.
-These various discoveries have firmly established the existence of stellar-mass black holes, supermassive black holes and binary black hole systems.
-Interestingly, there is still no direct evidence for intermediate-mass black holes, the black holes that lie in between stellar-mass and supermassive black hole systems with masses between $10^2-10^6$ \msun.
+\begin{itemize}
+    \item blip glitches and other short duration glitches occur very often
+    \item searches have to down-weight short duration foreground triggers because of high occurrence rate of short duration glitches
+    \item searches do not use CBC templates -- BCR can improve significance~\cite{BCR1}.
+    \item BCR can help give true significance, or $p_{astro}$ of foreground triggers
+\end{itemize}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{example-image-a}
+    \caption{Some caption.}
+    \label{fig:somefig}
+\end{figure}
+
+Since the 1970s, there has been an accumulation of evidence for stellar-mass and super-massive black holes.
+In 2019, the Event Horizon Telescope provided the first visual evidence of the super-massive black hole M87 \cite{event_horizon}.
+As of January 2020, LIGO, Virgo and IAS have confirmed more than a dozen binary black hole systems \cite{GWTC1, IAS_2}.
+These discoveries have established the existence of stellar-mass black holes, super-massive black holes and binary black hole systems.
+Interestingly, there is still no direct evidence for intermediate-mass black holes, the black holes that lie in between stellar-mass and super-massive black hole systems with masses between $10^2-10^6 \text{M}_\odot$.
 Thus, the existence of intermediate-mass black holes is still speculative.
-\\
 
-If intermediate-mass black holes are present, the gravitational waves emitted from the merger of a binary black hole system with at least one intermediate-mass black hole (up to a mass of $400$ \msun) will be detectable by the ground-based gravitational-wave network.
-Gravitational waves from such systems should occur at a rate of $0-10\text{yr}^{-1}$ \cite{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions}.
-However, even after conducting a targeted match-filter based search for gravitational waves from intermediate-mass black holes the largest total mass detected so far is approximately $80$ \msun \cite{salemi2019search, abbott2019gwtc}.
-A possible explanation for the absence of intermediate-mass events may be due to their misclassification as short-duration instrumental noise transients \cite{blip_glitches}.
-These glitches can mimic astrophysical signals and hence decrease the significance of true gravitational wave events.
-
-One method to account for glitches while searching for gravitational waves from coalescing compact binaries is by utilising a signal consistency test \cite{pycbc_short_duration_transients} or a signal coherence test amongst a network of detectors \cite{bci, bcr_paper,  bcr_gw151216, bayesian_odds}.
-A signal-coherence test such as the Bayesian coherence ratio (BCR) \cite{bcr_paper} provides an odds ratio comparing the probability that the data contains an astrophysical signal versus the probability that the data contains an incoherent glitch or noise.
-Although an odds ratio, the BCR can be used  as a ranking statistic to calculate the statistical significance of candidate gravitational-wave signals from compact binary coalescences in the detector data \cite{bcr_paper}.
-
-In this paper we utilise the BCR to calculate $p_\text{astro}$, the probability that a signal is of astrophysical origin [cite],  for all the high-mass (systems with total masses in the range of $55-500$ \msun) candidate gravitational-wave signals from compact binary coalescences in the detector data recorded during aLIGO's second observing run (O2).
-We find that (a) our search does not identify any new stellar mass or intermediate mass black holes; (b) high-mass events reported in the GWTC-1, including GW170729 (an event with disputed $p_\text{astro}$ amongst various search pipelines) have high $p_\text{astro}$; and that (c) high-mass events detected from independent groups have low $p_\text{astro}$.
-
-\section{PyCBC}
-% PyCBC asks for the 5 citations:
-% http://pycbc.org/pycbc/latest/html/credit.html#searches-for-compact-binary-coalescence
-
- such as \pycbc \cite{pycbc_code} have tried to account for these short-duration glitches \cite{pycbc_short_duration_transients}. 
-Search algorithms for gravitational waves from coalescing compact binaries, such as PyCBC \cite{pycbc_code}, have tried to account for these short-duration glitches \cite{pycbc_short_duration_transients}.
-At its core, PyCBC performs a matched-filter search for binary merger signals using a bank of gravitational-wave template waveforms \cite{pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5}.
-To account for the short-duration glitches,
-
- to As demonstrated in \citet{blip_glitches},  High-mass mergers have
-very few in-band wave cycles, and hence can easily be mistaken for short-duration instrumental transients.
+If intermediate-mass black holes are present, the gravitational waves emitted from the merger of a binary black hole system with at least one intermediate-mass black hole (up to a mass of $400 \text{M}_\odot$) will be detectable by the ground-based gravitational-wave network.
+According to \citet{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions}, gravitational waves from such systems within the detection of the ground-based detectors should occur at rates of one to up to ten events per year.
+Hence it is peculiar that LIGO has not detected a gravitational wave event from a system with a total mass greater than $80 \text{M}_\odot$.
 
@@
 There are two primary motivations for a targeted high-mass search that utilises Bayesian inference. The first is to help
-distinguish gravitataional-waves from high-mass systems from noise-transients, and the second is to try to alleviate the
+distinguish gravitational-waves from high-mass systems from noise-transients, and the second is to try to alleviate the
 discord in the significance of some of the ``quiet'' gravitational wave events between various search pipelines.
@@
 
-\caption[Comparing glitches to high-mass candidates.]{Spectrogram of a glitch on the left, and a candidate GW trigger on the right.}\label{fig:compareGlitchAndSignal}
+\caption[Comparing glitches to high-mass candidates.]{Spectogram of a glitch on the left, and a candidate GW trigger on the right.}\label{fig:compareGlitchAndSignal}
 \end{figure}
@@
 short, The \texttt{BCR} is an odds (evidence ratio) comparing two hypotheses: there's a coherent GW in the data, plus Gaussian
-noise vs there's only incoherent Gaussian noise or a glitch (modeled as a compact binary coalescence) in each detector
+noise vs there's only incoherent Gaussian noise or a glitch (modelled as a compact binary coalescence) in each detector
 \citep{bcr_paper}.
@@
 
-\caption[p-astro for various O2 foreground triggers]{\label{tab:O2significancesWObcr}p-astro from seveal detection pipelines for a subset of the O2 foreground triggers.}
+\caption[p-astro for various O2 foreground triggers]{\label{tab:O2significancesWObcr}p-astro from several detection pipelines for a subset of the O2 foreground triggers.}
 \centering
 \begin{tabular}{llrrrr}
-Event & Catalog & PyCBC & GstLAL & cWB & IAS\\
+\toprule
+Event & Catalogue & PyCBC & GstLAL & cWB & IAS\\
+\midrule
 GW170104 & GWTC-1 & 1.00 & 1.00 & 1.00 & 0.99\\
@@
 IMBHC170423 & IMBH-marginal & NA & 0.00 & 1.00 & NA\\
+\addlinespace
 GW170425 & IAS-1 & NA & NA & NA & 0.77\\
 GW170729 & GWTC-1 & 0.52 & 0.98 & 0.94 & NA\\
+\bottomrule
 \end{tabular}
@@
 
-\section{Methodology}\label{methodology}
+\hypertarget{methodology}{%
+\chapter{Methodology}\label{methodology}
+
 This PhD project intends to provide new methods and insights to studying gravitational waves form high-mass systems.
@@
 on the number of foreground triggers identified by \href{https://pycbc.org/}{\texttt{PyCBC}} in the various chunks, as seen in
-Figure\textasciitilde\ref{fig:o2TrigCount}. Currently, we are using O2 data as it is public, whereas O3 data is not. By analyzing O2
+Figure\textasciitilde\ref{fig:o2TrigCount}. Currently, we are using O2 data as it is public, whereas O3 data is not. By analysing O2
 triggers we can publish our results without any restrictions imposed by LIGO.
@@
 \toprule
-  & Minimum & Maximmum\\
+  & Minimum & Maximum\\
+\midrule
 Component Mass 1 $[\text{M}_{\odot}]$ & 31.54 & 491.68\\
@@
 Mass Ratio & 0.01 & 0.98\\
+\bottomrule
 \end{tabular}
@@
 \caption[High-mass BCR search space.]{The template bank used by \href{https://pycbc.org/}{\texttt{PyCBC}} to search in O2's chunk 14.
-Our search is constrained to the high-mass parameter space enclosed by the dashed line (triggers with diurations \(<45s\).}\label{fig:templateBank}
+Our search is constrained to the high-mass parameter space enclosed by the dashed line (triggers with duration \(<45s\).}\label{fig:templateBank}
 \end{figure}
@@
 triggers produced by all the various search pipelines. However, we refrain from doing so to keep our computational costs
-manageable. A plot of the counts of the triggers in O2 after downsampling the triggers based on the template duration
+manageable. A plot of the counts of the triggers in O2 after down-sampling the triggers based on the template duration
 can be viewed in Figure\textasciitilde\ref{fig:o2FilteredTrigCount}.
@@
 The \href{https://pycbc.org/}{\texttt{PyCBC}} search that originally produced our set of triggers considered a more comprehensive range of masses and
-spins than we do in the BCR computation for this project. To accommodate this, we prescreened the triggers to only allow
+spins than we do in the BCR computation for this project. To accommodate this, we screened the triggers to only allow
 triggers with masses within our priors. The run time on a single trigger using the \href{https://arxiv.org/abs/1904.02180}{\texttt{dynesty}} implementation of nested
@@
 in the \(i^{\text{th}}\) detectors. The arbitrary weights \(\alpha\) and \(\beta\)
-parametrize our prior belief in each model:
+parametrise our prior belief in each model:
 
 \begin{itemize}
+\tightlist
 \item
@@
 for all \(i\) detectors. As most of the data should be noise, we expect both \(\alpha\) and \(\beta\), to be less than 1.
-These parameters will be tuned to minimize the overlap between the signal and noise trigger populations.
+These parameters will be tuned to minimise the overlap between the signal and noise trigger populations.
 
@@
 \begin{acknowledgments}
-Helpful comments, OzGrav, LIGO, NSF
+helpful comments, OzGrav, LIGO, NSF
 

### 2020-08-20 main.tex

--- 2020-08-19 main.tex
@@
 \begin{abstract}
+
 The detection of high mass black holes ( $>100$ \msun) will shed light on the formation of supermassive black holes and thus galaxy formation.
@@
 in the \(i^{\text{th}}\) detectors. The arbitrary weights \(\alpha\) and \(\beta\)
-parametrize our prior belief in each model:
+parametrise our prior belief in each model:
 

### 2020-08-20 main.tex
Fix compilation errors

@@
 
+\usepackage{aas_macros}
+
 \usepackage{dcolumn}% Align table columns on decimal point
+\usepackage{booktabs}
+\usepackage{xspace} 
 \usepackage{bm}% bold math
@@
 % http://pycbc.org/pycbc/latest/html/credit.html#searches-for-compact-binary-coalescence
-Following \citet{bcr_paper}, the \bcr is an odds ratio of the coherent signal hypotheses $mathcal{H_S}$ and the incoherent instrumental feature hypothesis $mathcal{H_I}$. It is given by
+Following \citet{bcr_paper}, the \bcr is an odds ratio of the coherent signal hypotheses $\mathcal{H_S}$ and the incoherent instrumental feature hypothesis $\mathcal{H_I}$. It is given by
 \begin{equation}
@@
 The numerator is the probability of obtaining a coherent signal, where $Z^S$ is the evidence for $\mathcal{H_S}$ and $\alpha$ is the prior odds for obtaining a signal $\alpha=P(\mathcal{H_S})/P(\mathcal{H_I})$.
-The denominator is the probability of obtaining an incoherent glitch or noise amongst the network of $D$ detectors, where $Z_G_i$ and $Z_N_i$ are the evidence for obtaining a glitch in detector $i$ and the evidence for obtaining just noise in detector $i$.
+The denominator is the probability of obtaining an incoherent glitch or noise amongst the network of $D$ detectors, where $Z_{Gi}$ and $Z_{Ni}$ are the evidence for obtaining a glitch in detector $i$ and the evidence for obtaining just noise in detector $i$.
 

### 2020-08-20 main.tex
Rory's notes

@@
 \newcommand{\imrphenomp}{{\sc IMRPhenomPv2}\xspace}
+\newcommand{\seob}{{\sc SEOBNRv4PHM}\xspace}
 \newcommand{\pycbc}{{\sc PyCBC}\xspace}
@@
 These glitches can mimic astrophysical signals and hence decrease the significance of true gravitational wave events.
+\\
+
+% Launch into what Bayesain means
+
+% mathced-filter searches do not utilise as much information as present
+% an optimal search would computer a bayesian odds
+% rest of para what a bayesian odds is 
+% typicallly Bayesain a follow up tool
+% no reason why we cnat use for search
+% bayesian search on an entire observing run
 
@@
 The \bcr as a ranking statistic is much more powerful than a matched-filter SNR as the \bcr incorporates numerous features that may distinguish gravitational waves from noise and demands that signals must be coherent while glitches must be incoherent amongst different detectors.
+\\
 
@@
 We find that (a) our search does not identify any new stellar mass or intermediate mass black holes; (b) high-mass events reported in the GWTC-1, including GW170729 (an event with disputed $p_\text{astro}$ amongst various search pipelines) have high \pastro; and that (c) high-mass events detected from independent groups have low \pastro.
+\\
 
-\section{Method}
+The remainder of this paper is structured as follows.
+We outline our analysis methods in Section~\ref{sec:method}.
+We present our results in Section~\ref{sec:result}, and discuss these results in the context of the significance of gravitational wave candidates in Section~\ref{sec:Conclusion}.
+
+\section{Method\label{sec:method}}
 
@@
 % http://pycbc.org/pycbc/latest/html/credit.html#searches-for-compact-binary-coalescence
-Following \citet{bcr_paper}, the \bcr is an odds ratio of the coherent signal hypotheses $\mathcal{H_S}$ and the incoherent instrumental feature hypothesis $\mathcal{H_I}$. It is given by
+Following \citet{bcr_paper}, the \bcr is an odds ratio of the coherent signal hypotheses $\mathcal{H_S}$ and the incoherent instrumental feature hypothesis $\mathcal{H_I}$ for a network of $D$ detectors.
+$\mathcal{H_I}$ states that each $i$th detector has either pure Gaussian noise $\mathcal{H_Ni}$ or a glitch $\mathcal{H_Gi}$.
+The \bcr is given by
 \begin{equation}
-BCR = \frac{\alpha Z^S}{\Pi^D_{i=1}[\beta Z^G_i + (1-\beta)Z^N_i]}\ .
+BCR = \frac{\alpha Z^S}{\Pi^D_{i=1}[\beta Z^G_i + (1-\beta)Z^N_i]}\ ,
 \end{equation}
-The numerator is the probability of obtaining a coherent signal, where $Z^S$ is the evidence for $\mathcal{H_S}$ and $\alpha$ is the prior odds for obtaining a signal $\alpha=P(\mathcal{H_S})/P(\mathcal{H_I})$.
-The denominator is the probability of obtaining an incoherent glitch or noise amongst the network of $D$ detectors, where $Z_{Gi}$ and $Z_{Ni}$ are the evidence for obtaining a glitch in detector $i$ and the evidence for obtaining just noise in detector $i$.
+where $Z^S$, $Z_{Gi}$ and $Z_{Ni}$ are the Bayesian evidences (marginalised likelihoods) for $\mathcal{H_S}$, $\mathcal{H_Ni}$, and $\mathcal{H_Gi}$.
+$\alpha$ and $\beta$, are the prior odds for obtaining a signal $\alpha=P(\mathcal{H_S})/P(\mathcal{H_I})$, the prior odds for obtaining a glitch $\beta=P(\mathcal{H_G})/P(\mathcal{H_I})$.
 
-We use a Bayesian framework to calculate the \bcr for high-mass candidate events, simulated signal events and  background events (signal-free events ) supplied by the \pycbc \cite{pycbc_code} search in O2  \cite{pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5}.
+To calculate the Bayesian evidences $Z^S$, $Z_{Gi}$ and $Z_{Ni}$, we carry out Bayesian inference with \bilby CITE, using \dynesty CITE as our nested sampler.
+
+% We use the publicly available strain data associated with the 10 binary black hole events in GWTC-1.
+We implement the same priors as used in GWTC-1 for almost all parameters.
+The exceptions are eccentricity, which is not included in GWTC-1, and aligned dimensionless component spins, which are only supported in SEOBNRE between −1 and 0.6.
+Our prior on eccentricity is uniform in log10(e) in the range −6 ≤ log10(e) ≤ −0.7.
+Our aligned dimensionless component spin prior is uniform between −0.6 and 0.6.
+Our prior boundaries for cyclic parameters (e.g.
+coalescence phase, right ascension, and declination) are periodic, while our priors for non-cyclic parameters (e.g.
+mass and distance) have reflective boundaries.
+
+% Generating a posterior probability distribution demands many thousands of likelihood calculations, each requiring waveform template evaluation.
+While standard quasi-circular waveform models are fast enough to facilitate reasonable computation times, eccentric waveforms including merger and ringdown physics are not.
+SEOBNRE takes roughly a million times longer to evaluate a GW150914-like signal than aligned-spin quasi-circular waveform model IMRPHENOMD
+
+%  We use nested sampling, introduced by Skilling (2006) and popular for gravitational-wave data analysis due to its handling of high-dimensional spaces (Veitch et al.
+2015).
+For a thorough review of Bayesian inference in the context of gravitational-wave astrophysics, see Thrane & Talbot (2018).
+
+% where μ is our waveform template and σ is the detector noise amplitude spectral density.1 We assume Gaussian noise, using the noise power spectral densities σ2 that were used to produce the GWTC-1 results.
+We neglect calibration uncertainty.
+We generate μ using SEOBNRE (Cao & Han 2017), an effective one-body numerical-relativity waveform model that can produce non-circular waveforms with eccentricities in the range 0 ≤ e ≤ 0.2 at 10 Hz.
+The SEOBNRE waveform model incorporates more complex physics than the waveform used in Lower et al.
+(2018).
+It includes aligned dimensionless component spin magnitudes between −1 and 0.6, and models the merger and ringdown in addition to the inspiral.
+
+% We carry out Bayesian inference with BILBY (Ashton et al.
+2019), using DYNESTY (Speagle 2019) as our nested sampler.
+We use the publicly available strain data associated with the 10 binary black hole events in GWTC-1.
+We implement the same priors as used in GWTC-1 for almost all parameters.
+The exceptions are eccentricity, which is not included in GWTC-1, and aligned dimensionless component spins, which are only supported in SEOBNRE between −1 and 0.6.
+Our prior on eccentricity is uniform in log10(e) in the range −6 ≤ log10(e) ≤ −0.7.
+Our aligned dimensionless component spin prior is uniform between −0.6 and 0.6.
+Our prior boundaries for cyclic parameters (e.g.
+coalescence phase, right ascension, and declination) are periodic, while our priors for non-cyclic parameters (e.g.
+mass and distance) have reflective boundaries.
+
+% Generating a posterior probability distribution demands many thousands of likelihood calculations, each requiring waveform template evaluation.
+While standard quasi-circular waveform models are fast enough to facilitate reasonable computation times, eccentric waveforms including merger and ringdown physics are not.
+SEOBNRE takes roughly a million times longer to evaluate a GW150914-like signal than aligned-spin quasi-circular waveform model IMRPHENOMD
+
+high-mass candidate events, simulated signal events and  background events (signal-free events ) supplied by the \pycbc \cite{pycbc_code} search in O2  \cite{pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5}.
 At its core, \pycbc performs a matched-filter search for binary merger signals using a template-bank of gravitational-wave template waveforms to generate triggers.
@@
 
-\begin{itemize}
-	\item briefly explain PyCBC search
-	\item define triggers
-	\item Extract PyCBC foreground, background and software injection trigger's GPS times based on template duration of triggers
-	\item analyse the triggers using Bayesian Parameter Estimation to determine $\log{Z_s}$, $\log{Z_g}$ and $\log{Z_n}$
-	\item reweight results to account for uncertainties in PSDs
-	\item Calculate BCR
-	\item Calculate PDFs
-	\item Find $\alpha$ and $\beta$ values such that separation of background and software injection PDFs is maximally apart.
-	\item use tuned $\alpha$ and $\beta$ from previous step to calculate BCRs for foreground
-	\item calculate the $p_{astro}$ of the foreground events to determine the probability of the trigger being from an astrophysical source. 
-\end{itemize}
-
-\section{\label{sec:OutlineOfPipelineMethods}Outline of Pipeline Methods}
-
-\section{Significance of a high-mass Bayesian Search}\label{significance}
-
-There are two primary motivations for a targeted high-mass search that utilises Bayesian inference. The first is to help
-distinguish gravitational-waves from high-mass systems from noise-transients, and the second is to try to alleviate the
-discord in the significance of some of the ``quiet'' gravitational wave events between various search pipelines.
-
-\hypertarget{a-better-detection-statistic}{%
-\subsection{A better Detection-statistic}\label{a-better-detection-statistic}}
-
-\hypertarget{gravitational-wave-triggers-and-short-duration-glitches}{%
-\subsubsection{Gravitational-wave triggers and short duration glitches}\label{gravitational-wave-triggers-and-short-duration-glitches}}
-
-A foreground trigger is a section of LIGO data identified by data searching pipelines to potentially harbour some
-gravitational wave signal (more on triggers in Appendix\textasciitilde\ref{searches}). In the ground-based gravitational wave
-detectors, many spurious instrumental noise events fool the pipelines into considering the noise events as triggers
-(false-positive triggers). These instrumental-triggers are called glitches. Luckily, unlike triggers from astrophysical
-sources, glitches do not often occur at the same time or with the same morphology across the various gravitational wave
-detectors -- they are often \emph{incoherent} amongst detectors. Additionally, these short-duration glitches appear very
-similar to high-mass gravitational-wave signals, making the two challenging to distinguish. For example, consider
-Figure\textasciitilde\ref{fig:compareGlitchAndSignal} that compares a plot of a glitch on the left and a plot of a high-mass GW
-candidate on the right.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.45\linewidth]{images/glitch} \includegraphics[width=0.45\linewidth]{images/L1_spectrogram_logy_0}
-
-}
-
-\caption[Comparing glitches to high-mass candidates.]{Spectogram of a glitch on the left, and a candidate GW trigger on the right.}\label{fig:compareGlitchAndSignal}
-\end{figure}
-
-\hypertarget{assigning-significance-to-gravitational-wave-triggers}{%
-\subsection{Assigning significance to Gravitational-wave triggers}\label{assigning-significance-to-gravitational-wave-triggers}}
-
-The LIGO-Virgo collaboration uses various methods to avoid marking false-positive glitch triggers as gravitational wave
-triggers. One method first involves generating a set of \emph{background triggers}, false-positives picked up from the search
-through artificially\footnote{The artificial gravitational wave data
-  should have no true gravitational waves as it is constructed by applying relative time offsets between the data of different detectors (time offsets longer than the light-travel time between the detectors).} created gravitational
-wave data containing no signals. Then, a detection-statistic value, a value
-that ranks the likelihood of a trigger to originate from a gravitational-wave signal, is calculated for both the
-foreground and background triggers.
-Finally, the background trigger detection-statistic distribution can assign a probability to the \emph{null hypothesis} that the foreground triggers are consistent with the background.
-This null hypothesis probability is obtained by first calculating the cumulative distribution function for the background distribution.
-Placing the foreground event on the background cumulative distribution function provides the \emph{p-value}, or false alarm probability, of the foreground event.
-This p-value is a measure of how significant indicating the foreground event is from the background distribution of false-positives.
-
-For example, consider the
-detection-statistic plot for GW150914, as seen in Figure\textasciitilde\ref{fig:GW150914background}. If the
-foreground triggers are far away from the background trigger distribution, the foreground triggers have low p-values (and are significantly
-different from the background). Hence, the low p-values foreground triggers might originate from astrophysical sources. On the other hand, if the foreground
-triggers fall along with the background distribution with high p-values, the foreground triggers are consistent with the background. Thus,
-they are less likely to originate from astrophysical sources.
-
-\begin{figure}[!h]
-
-{\centering \includegraphics[width=0.75\linewidth]{images/GW150914_background}
-
-}
-
-\caption[Ranking statistic plot for GW150914]{A binary coalescence search displaying a number of candidate GW events (orange markers) and the mean number of background events (black line), taken from \citet{abbott2016observation}.}\label{fig:GW150914background}
-\end{figure}
-
-\hypertarget{a-bayesian-detection-statistic}{%
-\subsection{A Bayesian Detection statistic}\label{a-bayesian-detection-statistic}}
-
-Comparing foreground events to a background distribution is a ``frequentist'' method of assigning significance. It does
-not use the literal meaning of the likelihood -- which is a probability -- or compute the posterior probability of there
-being a signal given data and hypotheses. By using a frequentist method of assigning significance, these searches
-discard the physical meaning of the likelihood. In principle, a Bayesian approach would be able to incorporate this
-information that is lost.
-
-The goal of this PhD's first project is to enhance the significance of high-mass foreground triggers using a Bayesian
-approach and thereby increase the confidence in the detection of gravitational waves from large-mass compact binaries.
-If this work does improve the significance of high-mass triggers, we will increase the likelihood of detecting a
-high-mass black hole system via gravitational waves. The detection statistic we will utilise is the Bayesian Coherence
-Ratio (or BCR), as seen in \citet{bcr_paper}. The BCR is discussed in detail in Appendix\textasciitilde\ref{BayesianCoherenceRatio}. In
-short, The \texttt{BCR} is an odds (evidence ratio) comparing two hypotheses: there's a coherent GW in the data, plus Gaussian
-noise vs there's only incoherent Gaussian noise or a glitch (modelled as a compact binary coalescence) in each detector
-\citep{bcr_paper}.
-
-\hypertarget{a-better-measure-of-significance}{%
-\section{A better measure of significance}\label{a-better-measure-of-significance}}
-
-\hypertarget{gravitational-wave-candidates-with-uncertain-significance}{%
-\subsection{Gravitational wave candidates with uncertain significance}\label{gravitational-wave-candidates-with-uncertain-significance}}
-
-In aLIGO's first two observing runs, eleven gravitational wave events were found in the data by the LIGO-Virgo
-scientific collaboration \citep{abbott2019gwtc}. Since the public release of LIGO's first and second observing run's data,
-several groups have searched the data for gravitational waves independently of LIGO. One particular research group of
-interest is a research team at the Institute for Advanced Study (IAS). The group constructed searches to look for the
-LIGO-confirmed the gravitational wave events detected by the LIGO-Virgo collaboration, and in the process of doing so,
-claim to have discovered several others events \citep{IAS0, IAS1, IAS2}.
-Some of these events have total masses \(>85 M_{\odot}\), which is larger than the average total mass of the LIGO detections.
-Some of these IAS and LIGO events are
-displayed in Table\textasciitilde\ref{tab:O2significancesWObcr} with their p-astro reported by various LIGO and IAS search pipelines.
-
-\begin{table}[t]
-
-\caption[p-astro for various O2 foreground triggers]{\label{tab:O2significancesWObcr}p-astro from several detection pipelines for a subset of the O2 foreground triggers.}
-\centering
-\begin{tabular}{llrrrr}
-\toprule
-Event & Catalogue & PyCBC & GstLAL & cWB & IAS\\
-\midrule
-GW170104 & GWTC-1 & 1.00 & 1.00 & 1.00 & 0.99\\
-GW170121 & IAS-1 & NA & NA & NA & 0.99\\
-GWC170402 & IAS-2 & NA & 0.09 & NA & 0.68\\
-GW170403 & IAS-1 & NA & NA & NA & 0.56\\
-IMBHC170423 & IMBH-marginal & NA & 0.00 & 1.00 & NA\\
-GW170425 & IAS-1 & NA & NA & NA & 0.77\\
-GW170729 & GWTC-1 & 0.52 & 0.98 & 0.94 & NA\\
-\end{tabular}
-\end{table}
-
-From this Table\textasciitilde\ref{tab:O2significancesWObcr}, it is evident there is some uncertainty if these events can be considered real
-gravitational-wave events -- are these events significantly different from the background or not? The various pipelines
-have different answers. Our Bayesian search pipeline, as described in the next section, can help us answer this question
-and come to a conclusion about the significance of the events.
-
-\hypertarget{using-the-bcr-to-calculate-significance}{%
-\subsection{Using the BCR to calculate significance}\label{using-the-bcr-to-calculate-significance}}
-
-While the BCR might not increase the significance of some of the gravitational wave candidates, it will provide a more
-accurate measure of their significance. The BCR significance will be more accurate as it is a measure of the probability
-that signals in two or more detectors are \emph{coherent} (signals share exactly the same source properties in the different
-detectors) vs the detectors having \emph{incoherent} glitches/noise. This Bayesian significance might alleviate the discord
-between the significances of specific foreground triggers reported by various search pipelines.
-
-In summary, we will use the BCR to analyse high-mass foreground triggers to help discern signals from glitches and
-provide a better measure of significance for the foreground triggers. For our work, we will initially focus on
-conducting this BCR search on O2 data, and subsequently with a search in O3 data.
-
-\section{Methodology}\label{methodology}
-This PhD project intends to provide new methods and insights to studying gravitational waves form high-mass systems.
-Thus far, the project has focused on building up the infrastructure to compare the Bayesian Coherence Ratio of LIGO's
-time-shifted \emph{background} triggers, \emph{foreground} triggers and \emph{software injections}. This chapter describes how we have
-adapted the methods from \citet{bcr_paper} in our implementation.
-
-\hypertarget{selecting-o3-triggers-for-bcr-analysis}{%
-\section{Selecting O3 Triggers for BCR analysis}\label{selecting-o3-triggers-for-bcr-analysis}}
-
-LIGO's third observing run, O3, began on April, 2019, and is going until May 2020 (with a commissioning break during
-October). In the 35 observing weeks since O3 started, based off the \(\sim50\) public alerts for gravitational wave
-candidate triggers, LIGO might have tripled the number of detections during all of the first and second observing runs,
-O1 and O2 \citep{gracedb}. These gravitational wave events are considered candidates, as LIGO is still in the process of vetting the
-candidates (making sure that they are from astrophysical sources rather than terrestrial, spurious noise sources). On
-top of these candidate triggers, there are numerous sub-threshold triggers (triggers that do not have high
-significance).
-
-Ideally, we would like to compute the BCRs for all triggers (foreground and background) produced by LIGO to help improve
-the significance of astrophysically real triggers and decrease the significance of glitches. However, computational
-limitations prevent analysis of all triggers. Instead, we limit the data to several 8-day chunks from O2, selected based
-on the number of foreground triggers identified by \href{https://pycbc.org/}{\texttt{PyCBC}} in the various chunks, as seen in
-Figure\textasciitilde\ref{fig:o2TrigCount}. Currently, we are using O2 data as it is public, whereas O3 data is not. By analysing O2
-triggers we can publish our results without any restrictions imposed by LIGO.
-
-\begin{figure}[!h]
-
-{\centering \includegraphics[width=0.75\linewidth]{images/O2_unfiltered_trigger_counts}
-
-}
-
-\caption[Count of all triggers in PyCBC O2 search]{Counts of triggers from \texttt{PyCBC}'s search through O2 Data (November 15, 2016 - August 26, 2017).
-Each chunk is roughly 8 days long.
-The background triggers are collected from timesliding each chunk's data to generate a dataset of roughly 3 million years.}\label{fig:o2TrigCount}
-\end{figure}
-
-Additionally, to confine our search to high-mass sources (systems with total masses roughly between 50-500
-\(M_{\odot}\)), we restrict the triggers corresponding to a gravitational wave template with durations less than 454 ms.
-These short duration templates correspond to compact binary coalesences with the parameters presented in
-Table\textasciitilde\ref{tab:parameters} and the search space for these triggers can be visualised in Figure\textasciitilde\ref{fig:templateBank}.
-
-\begin{table}[t]
-
-\caption[BBH parameters corresponding to durations $<454$ ms]{\label{tab:parameters}Template Banks's parameters for templates with duration $<454$ ms.}
-\centering
-\begin{tabular}{lrr}
-\toprule
-  & Minimum & Maximum\\
-\midrule
-Component Mass 1 $[\text{M}_{\odot}]$ & 31.54 & 491.68\\
-Component Mass 2 $[\text{M}_{\odot}]$ & 1.32 & 121.01\\
-Total Mass $[\text{M}_{\odot}]$ & 56.93 & 496.72\\
-Chirp Mass $[\text{M}_{\odot}]$ & 8.00 & 174.56\\
-Mass Ratio & 0.01 & 0.98\\
-\end{tabular}
-\end{table}
-
-\begin{figure}[!h]
-
-{\centering \includegraphics[width=0.75\linewidth]{images/template_bank_masses}
-
-}
-
-\caption[High-mass BCR search space.]{The template bank used by \href{https://pycbc.org/}{\texttt{PyCBC}} to search in O2's chunk 14.
-Our search is constrained to the high-mass parameter space enclosed by the dashed line (triggers with duration \(<45s\).}\label{fig:templateBank}
-\end{figure}
-
-By restricting the \href{https://pycbc.org/}{\texttt{PyCBC}} triggers only based on the template duration, we acquire common (high FAR) and rare (low
-FAR) triggers. It would be straightforward in principle to broaden our template-duration constraint to encompass all
-triggers produced by all the various search pipelines. However, we refrain from doing so to keep our computational costs
-manageable. A plot of the counts of the triggers in O2 after down-sampling the triggers based on the template duration
-can be viewed in Figure\textasciitilde\ref{fig:o2FilteredTrigCount}.
-
-\begin{figure}[!h]
-
-{\centering \includegraphics[width=0.75\linewidth]{images/O2_filtered_trigger_counts}
-
-}
-
-\caption[Count of triggers in PyCBC O2 search shorter than 454 ms]{Counts of triggers from \texttt{PyCBC}'s search through O2 Data, filtered to include only the triggers with a duration less than 454 ms}\label{fig:o2FilteredTrigCount}
-\end{figure}
-
-\hypertarget{bcr-analysis-procedure}{%
-\section{BCR Analysis Procedure}\label{bcr-analysis-procedure}}
-
-\hypertarget{computational-setup}{%
-\subsection{Computational setup}\label{computational-setup}}
-
-To compute the evidence making up the BCR (described in Section\textasciitilde\ref{bcrCalculation}), we use \href{https://lscsoft.docs.ligo.org/bilby_pipe/}{\texttt{bilby\_pipe}} to acquire
-the LIGO data in 4s-long data segments containing each trigger (analysis segments) and run the nested-sampling algorithm
-implemented in the \texttt{dynesty} library. We utilise \href{https://lscsoft.docs.ligo.org/bilby_pipe/}{\texttt{bilby\_pipe}} to generate PSDs via Welch's method for each data
-segment by taking 128 seconds of the data before the analysis segment. If the data quality is not marked as `Science
-Mode' for either the PSD or analysis data, then the analysis of that trigger is skipped. Gravitational-wave templates
-are produced using \texttt{IMRPhenomPv2} \footnote{\texttt{IMRPhenomPv2} is a standard phenomenological waveform model constructed in the
+We use \bilbypipe to both acquire the publicly accessible LIGO data in 4s-long data segments containing each trigger (analysis segments) and to generate PSDs via Welch's method for each data segment by taking 124 seconds of the data before the analysis segment.
+If the data quality is not marked as ``Science Mode'' for either the PSD or analysis data, then the analysis of that trigger is skipped.
+Gravitational-wave templates
+are produced using \imrphenomp \footnote{\texttt{IMRPhenomPv2} is a standard phenomenological waveform model constructed in the
   frequency domain that models the inspiral, merger, and ringdown (IMR) of a compact binary coalescence with aligned spins
-  \citep{khan2016frequency}.}. Although gravitational wave templates that are created from numerical relativity simulations
-incorporate more physics than \texttt{IMRPhenomPv2}, we still use this waveform as it is faster to evaluate than numerical
+  \citep{khan2016frequency}.}. Although gravitational wave templates such as \ created from numerical relativity simulations
+incorporate more physics such as information on higher-order modes, we still use \imrphenomp as it is faster to evaluate than numerical
 relativity models.
@@
 
-\section{\label{sec:Analysis}O2 Sub-threshold Event Analysis}
-\hyperlink{https://docs.google.com/spreadsheets/d/1hm7lFsYneY8NGbFDr-vH5YYsILrxcTexO9D1AvF1qJo/edit?usp=sharing}{Important triggers spreadsheet}
 \begin{itemize}
-    \item BCRs of O2 sub-threshold high mass events
-    \item BCRs of Princeton group's high-mass  events
+	\item briefly explain PyCBC search
+	\item define triggers
+	\item Extract PyCBC foreground, background and software injection trigger's GPS times based on template duration of triggers
+	\item analyse the triggers using Bayesian Parameter Estimation to determine $\log{Z_s}$, $\log{Z_g}$ and $\log{Z_n}$
+	\item reweight results to account for uncertainties in PSDs
+	\item Calculate BCR
+	\item Calculate PDFs
+	\item Find $\alpha$ and $\beta$ values such that separation of background and software injection PDFs is maximally apart.
+	\item use tuned $\alpha$ and $\beta$ from previous step to calculate BCRs for foreground
+	\item calculate the $p_{astro}$ of the foreground events to determine the probability of the trigger being from an astrophysical source. 
 \end{itemize}
+
+In aLIGO's first two observing runs, eleven gravitational wave events were found in the data by the LIGO-Virgo
+scientific collaboration \citep{abbott2019gwtc}. Since the public release of LIGO's first and second observing run's data,
+several groups have searched the data for gravitational waves independently of LIGO. One particular research group of
+interest is a research team at the Institute for Advanced Study (IAS). The group constructed searches to look for the
+LIGO-confirmed the gravitational wave events detected by the LIGO-Virgo collaboration, and in the process of doing so,
+claim to have discovered several others events \citep{IAS0, IAS1, IAS2}.
+Some of these events have total masses \(>85 M_{\odot}\), which is larger than the average total mass of the LIGO detections.
+Some of these IAS and LIGO events are
+displayed in Table\textasciitilde\ref{tab:O2significancesWObcr} with their p-astro reported by various LIGO and IAS search pipelines.
+
+\begin{table}[t]
+
+\caption[p-astro for various O2 foreground triggers]{\label{tab:O2significancesWObcr}p-astro from several detection pipelines for a subset of the O2 foreground triggers.}
+\centering
+\begin{tabular}{llrrrr}
+\toprule
+Event & Catalogue & PyCBC & GstLAL & cWB & IAS\\
+\midrule
+GW170104 & GWTC-1 & 1.00 & 1.00 & 1.00 & 0.99\\
+GW170121 & IAS-1 & NA & NA & NA & 0.99\\
+GWC170402 & IAS-2 & NA & 0.09 & NA & 0.68\\
+GW170403 & IAS-1 & NA & NA & NA & 0.56\\
+IMBHC170423 & IMBH-marginal & NA & 0.00 & 1.00 & NA\\
+GW170425 & IAS-1 & NA & NA & NA & 0.77\\
+GW170729 & GWTC-1 & 0.52 & 0.98 & 0.94 & NA\\
+\end{tabular}
+\end{table}
+
+From this Table\textasciitilde\ref{tab:O2significancesWObcr}, it is evident there is some uncertainty if these events can be considered real
+gravitational-wave events -- are these events significantly different from the background or not? The various pipelines
+have different answers. Our Bayesian search pipeline, as described in the next section, can help us answer this question
+and come to a conclusion about the significance of the events.
+
+\begin{figure}[!h]
+
+{\centering \includegraphics[width=0.75\linewidth]{images/O2_unfiltered_trigger_counts}
+
+}
+
+\caption[Count of all triggers in PyCBC O2 search]{Counts of triggers from \texttt{PyCBC}'s search through O2 Data (November 15, 2016 - August 26, 2017).
+Each chunk is roughly 8 days long.
+The background triggers are collected from timesliding each chunk's data to generate a dataset of roughly 3 million years.}\label{fig:o2TrigCount}
+\end{figure}
+
+\begin{table}[t]
+
+\caption[BBH parameters corresponding to durations $<454$ ms]{\label{tab:parameters}Template Banks's parameters for templates with duration $<454$ ms.}
+\centering
+\begin{tabular}{lrr}
+\toprule
+  & Minimum & Maximum\\
+\midrule
+Component Mass 1 $[\text{M}_{\odot}]$ & 31.54 & 491.68\\
+Component Mass 2 $[\text{M}_{\odot}]$ & 1.32 & 121.01\\
+Total Mass $[\text{M}_{\odot}]$ & 56.93 & 496.72\\
+Chirp Mass $[\text{M}_{\odot}]$ & 8.00 & 174.56\\
+Mass Ratio & 0.01 & 0.98\\
+\end{tabular}
+\end{table}
+
+\begin{figure}[!h]
+
+{\centering \includegraphics[width=0.75\linewidth]{images/template_bank_masses}
+
+}
+
+\caption[High-mass BCR search space.]{The template bank used by \href{https://pycbc.org/}{\texttt{PyCBC}} to search in O2's chunk 14.
+Our search is constrained to the high-mass parameter space enclosed by the dashed line (triggers with duration \(<45s\).}\label{fig:templateBank}
+\end{figure}
 
@@
 due to their misclassification as short-duration instrumental noise transients \citep{blipGlitches}. High-mass mergers have
-very few in-band wave cycles, and hence can easily be mistaken for short-duration instrumental transients. More details
-on the theorised formation channels and merger rates are discussed in Appendix \ref{literature}.
+very few in-band wave cycles, and hence can easily be mistaken for short-duration instrumental transients.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
-\section{Appendixes}
-%%%%%%%%%%%%%%%%%%%%%%%%
-
 \bibliography{high_mass_bib}% Produces the bibliography via BibTeX.

### 2020-08-21 main.tex
improve introduction

@@
 Gravitational waves from such systems should occur at a rate of $0-10\text{yr}^{-1}$ \cite{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions}.
-However, even after conducting a targeted match-filter based search for gravitational waves from intermediate-mass black holes the largest total mass detected so far is approximately $80$ \msun \cite{salemi2019search, abbott2019gwtc}.
-A possible explanation for the absence of intermediate-mass events may be due to their misclassification as short-duration instrumental noise transients \cite{blip_glitches}.
+However, even after conducting a targeted matched-filter based search for gravitational waves from intermediate-mass black holes the largest total mass detected so far is approximately $80$ \msun \cite{salemi2019search, abbott2019gwtc}.
+A possible explanation for the absence of intermediate-mass events may be due to their misclassification as short-duration instrumental noise transients known as glitches \cite{glitch_in_fifth_ligo_run, bayeswave, improving_dq_in_early_runs, ligo_glitch_gw150914, pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
 These glitches can mimic astrophysical signals and hence decrease the significance of true gravitational wave events.
@@
 
-% Launch into what Bayesain means
+One method to account for glitches while searching for gravitational waves from coalescing compact binaries is by utilising an astrophysical Bayesian odds  \cite{bci, BCR1, BCR2, bcr_gw151216, bayesian_odds}.
+A true Bayesian odds calculated without using bootstrap techniques can provide events with a more accurate significance that is agnostic to a specific search strategy \cite{BCR2, bcr_gw151216,  bayesian_odds}.
+Additionally, a Bayesian odds can include information such as if the gravitational wave event's signal is coherent amongst the network of detectors, if the binary system that created the gravitational waves was precessing, and if the gravitational wave signal contains higher-order modes.
+It is because Bayesian methods can incorporate all this physical information about a gravitational wave signal that the LIGO Scientific Collaboration uses these methods to determine the source parameters of gravitational wave events \cite{abbott2016ligo, abbott2019gwtc}.
+This paper demonstrates that the power of Bayesian methods used in parameter estimation can also successfully be used to discriminate between coherent gravitational-wave signals, incoherent glitches, and Gaussian noise in the form of a Bayesian search.
+\\
 
-% mathced-filter searches do not utilise as much information as present
-% an optimal search would computer a bayesian odds
-% rest of para what a bayesian odds is 
-% typicallly Bayesain a follow up tool
-% no reason why we cnat use for search
-% bayesian search on an entire observing run
+ In this paper we utilise a Bayesian method to search for the significant gravitational wave signals from high-mass (systems with total masses in the range of $55-500$ \msun) compact binary coalescences in the detector data recorded during aLIGO's second observing run (O2).
+We find that (a) our search does not identify any unreported stellar mass or intermediate mass black holes; (b) high-mass events reported in the GWTC-1, including GW170729 (an event with disputed $p_\text{astro}$ amongst various search pipelines) have high low significance; and that (c) high-mass events detected from some independent groups have low significance.
+\\
 
-One method to account for glitches while searching for gravitational waves from coalescing compact binaries is by utilising a signal consistency test \cite{pycbc_short_duration_transients} or a signal coherence test amongst a network of detectors \cite{bci, bcr_paper,  bcr_gw151216, bayesian_odds}.
+The remainder of this paper is structured as follows.
+We outline our analysis methods, including details of our Bayesian  in Section~\ref{sec:method}.
+We present our results in Section~\ref{sec:result}, and discuss these results in the context of the significance of gravitational wave candidates in Section~\ref{sec:Conclusion}.
+
+\section{Method\label{sec:method}}
+
+\pastro, the probability that a signal is of astrophysical origin \cite{pastro_1,pastro_2,pastro_3},
+
+a signal consistency test \cite{pycbc_short_duration_transients} or a signal coherence test amongst a network of detectors.
 A signal-coherence test such as the Bayesian coherence ratio (\bcr) \cite{bcr_paper} provides a Bayesian odds ratio comparing the probability that the data contains an astrophysical signal versus the probability that the data contains an incoherent glitch or noise.
@@
 \\
-
- In this paper we utilise the \bcr to calculate \pastro, the probability that a signal is of astrophysical origin [cite],  for all the high-mass (systems with total masses in the range of $55-500$ \msun) candidate gravitational-wave signals from compact binary coalescences in the detector data recorded during aLIGO's second observing run (O2).
-We find that (a) our search does not identify any new stellar mass or intermediate mass black holes; (b) high-mass events reported in the GWTC-1, including GW170729 (an event with disputed $p_\text{astro}$ amongst various search pipelines) have high \pastro; and that (c) high-mass events detected from independent groups have low \pastro.
-\\
-
-The remainder of this paper is structured as follows.
-We outline our analysis methods in Section~\ref{sec:method}.
-We present our results in Section~\ref{sec:result}, and discuss these results in the context of the significance of gravitational wave candidates in Section~\ref{sec:Conclusion}.
-
-\section{Method\label{sec:method}}
 
@@
 
-To calculate the Bayesian evidences $Z^S$, $Z_{Gi}$ and $Z_{Ni}$, we carry out Bayesian inference with \bilby CITE, using \dynesty CITE as our nested sampler.
+To calculate the Bayesian evidences $Z^S$, $Z_{Gi}$ and $Z_{Ni}$, we carry out Bayesian inference with \bilby \cite{bilby}, using \dynesty \cite{dynesty} as our nested sampler.
 

### 2020-08-21 main.tex
update images

@@
 
- In this paper we utilise a Bayesian method to search for the significant gravitational wave signals from high-mass (systems with total masses in the range of $55-500$ \msun) compact binary coalescences in the detector data recorded during aLIGO's second observing run (O2).
+ In this paper we utilise a Bayesian method, called the\bcr \cite{BCR1}, to search for the significant gravitational wave signals from high-mass (systems with total masses in the range of $55-500$ \msun) compact binary coalescences in the detector data recorded during aLIGO's second observing run (O2).
 We find that (a) our search does not identify any unreported stellar mass or intermediate mass black holes; (b) high-mass events reported in the GWTC-1, including GW170729 (an event with disputed $p_\text{astro}$ amongst various search pipelines) have high low significance; and that (c) high-mass events detected from some independent groups have low significance.
@@
 The remainder of this paper is structured as follows.
-We outline our analysis methods, including details of our Bayesian  in Section~\ref{sec:method}.
+We outline our analysis methods, including details of the \bcr in Section~\ref{sec:method}.
 We present our results in Section~\ref{sec:result}, and discuss these results in the context of the significance of gravitational wave candidates in Section~\ref{sec:Conclusion}.
@@
 
+\subsection{The Bayesian Coherence Ratio}
+
 \pastro, the probability that a signal is of astrophysical origin \cite{pastro_1,pastro_2,pastro_3},
 
-a signal consistency test \cite{pycbc_short_duration_transients} or a signal coherence test amongst a network of detectors.
-A signal-coherence test such as the Bayesian coherence ratio (\bcr) \cite{bcr_paper} provides a Bayesian odds ratio comparing the probability that the data contains an astrophysical signal versus the probability that the data contains an incoherent glitch or noise.
-Although an odds ratio, the \bcr can be used  as a frequentistic \textit{ranking statistic}, ranking the likelihood that a trigger is due to a gravitational-wave signal \cite{bcr_paper}.
-The \bcr as a ranking statistic is much more powerful than a matched-filter SNR as the \bcr incorporates numerous features that may distinguish gravitational waves from noise and demands that signals must be coherent while glitches must be incoherent amongst different detectors.
-\\
-
-% PyCBC asks for the 5 citations:
-% http://pycbc.org/pycbc/latest/html/credit.html#searches-for-compact-binary-coalescence
 Following \citet{bcr_paper}, the \bcr is an odds ratio of the coherent signal hypotheses $\mathcal{H_S}$ and the incoherent instrumental feature hypothesis $\mathcal{H_I}$ for a network of $D$ detectors.
-$\mathcal{H_I}$ states that each $i$th detector has either pure Gaussian noise $\mathcal{H_Ni}$ or a glitch $\mathcal{H_Gi}$.
+$\mathcal{H_I}$ states that each $i$th detector has either pure Gaussian noise $\mathcal{H_N}$ or a glitch $\mathcal{H_G}$.
 The \bcr is given by
@@
 \end{equation}
-where $Z^S$, $Z_{Gi}$ and $Z_{Ni}$ are the Bayesian evidences (marginalised likelihoods) for $\mathcal{H_S}$, $\mathcal{H_Ni}$, and $\mathcal{H_Gi}$.
+where $Z^S$, $Z_{Gi}$ and $Z_{Ni}$ are the Bayesian evidences (marginalised likelihoods) for $\mathcal{H_S}$, $\mathcal{H_N}$, and $\mathcal{H_G}$.
 $\alpha$ and $\beta$, are the prior odds for obtaining a signal $\alpha=P(\mathcal{H_S})/P(\mathcal{H_I})$, the prior odds for obtaining a glitch $\beta=P(\mathcal{H_G})/P(\mathcal{H_I})$.
+As the rate of signal and glitches are unknown, these priors $\alpha$ and $\beta$ are tuned to maximize the \bcr distributions for background data (signal-free data) and simulated signals $\cite{BCR1}.
+
+ provides a Bayesian odds ratio comparing the probability that the data contains an astrophysical signal versus the probability that the data contains an incoherent glitch or noise.
+Although an odds ratio, the \bcr can be used  as a frequentistic \textit{ranking statistic}, ranking the likelihood that a trigger is due to a gravitational-wave signal \cite{bcr_paper}.
+The \bcr as a ranking statistic is much more powerful than a matched-filter SNR as the \bcr incorporates numerous features that may distinguish gravitational waves from noise and demands that signals must be coherent while glitches must be incoherent amongst different detectors.
+\\
 
@@
 
+% PyCBC asks for the 5 citations:
+% http://pycbc.org/pycbc/latest/html/credit.html#searches-for-compact-binary-coalescence
 high-mass candidate events, simulated signal events and  background events (signal-free events ) supplied by the \pycbc \cite{pycbc_code} search in O2  \cite{pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5}.

### 2020-08-21 main.tex
Updates from Overleaf

--- 2020-08-20 main.tex
@@
 In 2019, the Event Horizon Telescope provided the first visual evidence of the supermassive black hole M87  \cite{m87photo}.
-As of January 2020, LIGO, Virgo and IAS have confirmed more than a dozen binary black hole systems \cite{GWTC1, IAS0, IAS1, IAS2}.
+As of January 2020, LIGO, Virgo and IAS have confirmed more than a dozen binary black hole systems \cite{GWTC1, IAS0, IAS1, IAS2, pycbc_ogc_2}.
 These various discoveries have firmly established the existence of stellar-mass black holes, supermassive black holes and binary black hole systems.
@@
 However, even after conducting a targeted match-filter based search for gravitational waves from intermediate-mass black holes the largest total mass detected so far is approximately $80$ \msun \cite{salemi2019search, abbott2019gwtc}.
-A possible explanation for the absence of intermediate-mass events may be due to their misclassification as short-duration instrumental noise transients \cite{blip_glitches}.
+A possible explanation for the absence of intermediate-mass events may be due to their misclassification as short-duration instrumental noise transients \cite{gli blip_glitches}.
 These glitches can mimic astrophysical signals and hence decrease the significance of true gravitational wave events.

### 2020-08-21 main.tex
adjust some missing citation keys

--- 2020-08-21 main.tex
@@
 Gravitational waves from such systems should occur at a rate of $0-10\text{yr}^{-1}$ \cite{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions}.
-However, even after conducting a targeted matched-filter based search for gravitational waves from intermediate-mass black holes the largest total mass detected so far is approximately $80$ \msun \cite{salemi2019search, abbott2019gwtc}.
+However, even after conducting a targeted matched-filter based search for gravitational waves from intermediate-mass black holes the largest total mass detected so far is approximately $80$ \msun \cite{imbhbSearch2014, ligo_imbh_search, abbott2019gwtc}.
 A possible explanation for the absence of intermediate-mass events may be due to their misclassification as short-duration instrumental noise transients known as glitches \cite{glitch_in_fifth_ligo_run, bayeswave, improving_dq_in_early_runs, ligo_glitch_gw150914, pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
@@
 
-Following \citet{bcr_paper}, the \bcr is an odds ratio of the coherent signal hypotheses $\mathcal{H_S}$ and the incoherent instrumental feature hypothesis $\mathcal{H_I}$ for a network of $D$ detectors.
+Following \citet{BCR1}, the \bcr is an odds ratio of the coherent signal hypotheses $\mathcal{H_S}$ and the incoherent instrumental feature hypothesis $\mathcal{H_I}$ for a network of $D$ detectors.
 $\mathcal{H_I}$ states that each $i$th detector has either pure Gaussian noise $\mathcal{H_N}$ or a glitch $\mathcal{H_G}$.
@@
 $\alpha$ and $\beta$, are the prior odds for obtaining a signal $\alpha=P(\mathcal{H_S})/P(\mathcal{H_I})$, the prior odds for obtaining a glitch $\beta=P(\mathcal{H_G})/P(\mathcal{H_I})$.
-As the rate of signal and glitches are unknown, these priors $\alpha$ and $\beta$ are tuned to maximize the \bcr distributions for background data (signal-free data) and simulated signals $\cite{BCR1}.
+As the rate of signal and glitches are unknown, these priors $\alpha$ and $\beta$ are tuned to maximise the \bcr distributions for background data (signal-free data) and simulated signals $\cite{BCR1}.
 
  provides a Bayesian odds ratio comparing the probability that the data contains an astrophysical signal versus the probability that the data contains an incoherent glitch or noise.
-Although an odds ratio, the \bcr can be used  as a frequentistic \textit{ranking statistic}, ranking the likelihood that a trigger is due to a gravitational-wave signal \cite{bcr_paper}.
+Although an odds ratio, the \bcr can be used  as a frequentistic \textit{ranking statistic}, ranking the likelihood that a trigger is due to a gravitational-wave signal \cite{BCR}.
 The \bcr as a ranking statistic is much more powerful than a matched-filter SNR as the \bcr incorporates numerous features that may distinguish gravitational waves from noise and demands that signals must be coherent while glitches must be incoherent amongst different detectors.
@@
 
-The Bayesian coherence ratio (BCR), as seen in \citet{bcr_paper}, is the odds between the hypothesis that the data comprise a
+The Bayesian coherence ratio (BCR), as seen in \citet{BCR1}, is the odds between the hypothesis that the data comprise a
 coherent, compact binary coalescence signal in Gaussian noise (\(\mathcal{H}_S\)), and the hypothesis that they instead
@@
 
-\caption[BCR vs iFAR for O1]{BCR versus iFAR distributions from simulated signals (blue), hardware injections (green), GW events (stars) and background triggers (black), taken from \citet{bcr_paper}.}\label{fig:bcrIfar}
+\caption[BCR vs iFAR for O1]{BCR versus iFAR distributions from simulated signals (blue), hardware injections (green), GW events (stars) and background triggers (black), taken from \citet{BCR1}.}\label{fig:bcrIfar}
 \end{figure}

### 2020-08-23 main.tex
add content for method

@@
 \newcommand{\bcr}{{\sc BCR}\xspace}
+\newcommand{\psd}{{\sc $\sigma^2$}\xspace}
 \newcommand{\pastro}{{$p_\text{astro}$}\xspace}
 \newcommand{\msun}{{M${}_\odot$}\xspace}
+
+\newcommand{\av}[1]{\textcolor{orange}{[AV: #1]}}
+\newcommand{\rs}[1]{\textcolor{red}{[RS: #1]}}
+\newcommand{\et}[1]{\textcolor{blue}{[ET: #1]}}
+
 \begin{document}
@@
 
-\pastro, the probability that a signal is of astrophysical origin \cite{pastro_1,pastro_2,pastro_3},
-
 Following \citet{BCR1}, the \bcr is an odds ratio of the coherent signal hypotheses $\mathcal{H_S}$ and the incoherent instrumental feature hypothesis $\mathcal{H_I}$ for a network of $D$ detectors.
@@
 \end{equation}
-where $Z^S$, $Z_{Gi}$ and $Z_{Ni}$ are the Bayesian evidences (marginalised likelihoods) for $\mathcal{H_S}$, $\mathcal{H_N}$, and $\mathcal{H_G}$.
-$\alpha$ and $\beta$, are the prior odds for obtaining a signal $\alpha=P(\mathcal{H_S})/P(\mathcal{H_I})$, the prior odds for obtaining a glitch $\beta=P(\mathcal{H_G})/P(\mathcal{H_I})$.
-As the rate of signal and glitches are unknown, these priors $\alpha$ and $\beta$ are tuned to maximise the \bcr distributions for background data (signal-free data) and simulated signals $\cite{BCR1}.
+where $Z^S$, $Z^G_i $ and $Z^N_i }$ are the Bayesian evidences (marginalised likelihoods) for $\mathcal{H_S}$, $\mathcal{H_N}$, and $\mathcal{H_G}$.
+$\alpha$ and $\beta$, are the prior odds for obtaining a signal $\alpha=P(\mathcal{H_S})/P(\mathcal{H_I})$ and the prior odds for obtaining a glitch $\beta=P(\mathcal{H_G})/P(\mathcal{H_I})$.
+As the rate of signal and glitches are unknown, these priors $\alpha$ and $\beta$ are tuned to maximise the \bcr distributions for background data (signal-free data) and simulated signals \cite{BCR1}.
+\\
+
+We assume that each detector's noise is Gaussian and stationary over the period being analysed \cite{ligo_psd}.
+In practice, we estimate the noise using a noise power spectral density \psd.
+The method of estimating the \psd, along with details on the implementation of our Bayesian inference pipeline is presented in the following section \av{(Not sure if the details on the PSD generation should be here or not...)}.
+Using the \psd, we can write
+\begin{equation}
+Z^N_i =  \frac{1}{2\pi \sigma^2} \text{exp}\left(-\frac{1}{2} \frac{d_i}{\sigma^2} \right) \ ,
+\end{equation}
+for the data $d_i$ in each of the $i$ detectors in a network of $D$ detectors..
+
+We model coherent signal with parameters $\vec{\theta}$ using \imrphenomp $\mu_{\text{IMR}}(\vec{\theta})$.
+For this model to be coherent, the $\vec{\theta}$ must be consistent in each dataset $d_i$ for a network of $D$ detectors.
+Note that $\mu_{\text{IMR}}(\vec{\theta})$ is a phenomenological aligned spin waveform template constructed in the frequency domain that models the in-spiral, merger, and ringdown (IMR) of a compact binary coalescence \citep{khan2016frequency}.
+Although gravitational wave templates such as \seob $\mu_{\text{SEOB}}$ created from numerical relativity simulations incorporate more physics such as information on higher-order modes, we still use $\mu_{\text{IMR}}\vec{\theta}$ as this phenomenological model is faster to evaluate than numerical relativity models.
+Hence, the coherent signal evidence is calculated as
+\begin{equation}
+Z^S = \int \Pi^D_{i=1} \left[\frac{1}{2\pi \sigma^2} \text{exp}\left(\right)-\frac{1}{2} \frac{(d_i-\mu_{\text{IMR}}\vec{\theta})^2}{\sigma^2} \right) \right] \pi(\vec{\theta}) \text{d}\vec{\theta}  \ .
+\end{equation}
+
+\av{Introduce pi before the above}
+
+Finally, as glitches are challenging to model and poorly understood, we utilise a surrogate model for glitches: the glitches are modelled using $\mu_{\text{IMR}}\vec{\theta}$ with uncorrelated  parameters amongst the different detectors such that  $\vec{\theta}_i \neq \vec{\theta}_j$ for two detectors $i$ and $j$ \cite{bci}.
+Modelling glitches with gravitational wave templates captures the worst case scenario for when glitches appear similar to gravitational wave signals.
+Thus, we can write $Z^G_i$ as
+\begin{equation}
+Z^G_i = \int \frac{1}{2\pi \sigma^2} \text{exp}\left(\right)-\frac{1}{2} \frac{(d -\mu_{\text{IMR}}\vec{\theta})^2}{\sigma^2} \right) \pi(\vec{\theta}) \text{d}\vec{\theta}  \ .
+\end{equation}
+
+\hypertarget{bayesian-parameter-estimation}{%
+	\subsection{Bayesian Parameter Estimation}\label{bayesian-parameter-estimation}}
+
+To generate posterior probability distributions and calculate Bayesian evidences for our signal, glitch and noise models, we carry out Bayesian inference with \bilby \cite{bilby}, employing \dynesty \cite{dynesty} as our nested sampler.
+Although nested sampling, an algorithm introduced by \cite{skilling_nested_sampling}, is an estimate of the true Bayesian evidence,
+
+To generate the \psd, we take 31 neighbouring, "off-source", non-overlapping,  $4\ s$  segments of time-series data prior to the data being analysed.
+A Tukey window with a roll off of $0.2\ s$ is applied to each data segment to suppress spectral leakage after which the segments are fast-Fourier transformed and median-averaged to create a \psd.
+This method, like other \psd estimation methods, adds statistical uncertainties to the \psd \cite{psd_student_t}.
+To marginalise over the statistical uncertainty we use the median-likelihood presented by \citet{psd_student_t} to re-weight our posterior samples as a post-processing step and shift our Bayesian Evidence estimations closer to their true astrophysical values.
+
+We restrict the priors for Bayesian parameter estimation on the masses such that we only consider signals that are less
+than 454ms in duration, as presented in Table\textasciitilde\ref{tab:parameters}. The spins are set to be aligned with a range from
+{[}0,1{]}. The prior on luminosity distance assigns probability uniformly in comoving volume, with an upper cutoff of 5 Gpc.
+The \href{https://pycbc.org/}{\texttt{PyCBC}} search that originally produced our set of triggers considered a more comprehensive range of masses and
+spins than we do in the BCR computation for this project. To accommodate this, we screened the triggers to only allow
+triggers with masses within our priors. The run time on a single trigger using the \href{https://arxiv.org/abs/1904.02180}{\texttt{dynesty}} implementation of nested
+sampling, with \(2,000\) live points and \(100\) walkers is usually between \(0.5-12\) hours (where the speed often depends on
+the SNR of the data segment).
+
+we use the noise power spectral densities created with a median-average method by taking 31 neighbouring, "off-source", non-overlapping,  4 second segments of data prior to the data being analysed.
+Before computing the PSD,   prior to fast-Fourier transforming the the windowed time-domain strain before averaging the PSD chunks.As this method does not provide a perfect estimation of the true noise power spectral density  These power spectral densities are ?
+with a studuent-T's distribution to account for ?
+\cite{psd_student_t}.
+
+\pastro, the probability that a signal is of astrophysical origin \cite{pastro_1,pastro_2,pastro_3},
 
@@
 \\
-
-To calculate the Bayesian evidences $Z^S$, $Z_{Gi}$ and $Z_{Ni}$, we carry out Bayesian inference with \bilby \cite{bilby}, using \dynesty \cite{dynesty} as our nested sampler.
 
@@
 Gravitational-wave templates
-are produced using \imrphenomp \footnote{\texttt{IMRPhenomPv2} is a standard phenomenological waveform model constructed in the
-  frequency domain that models the inspiral, merger, and ringdown (IMR) of a compact binary coalescence with aligned spins
-  \citep{khan2016frequency}.}. Although gravitational wave templates such as \ created from numerical relativity simulations
-incorporate more physics such as information on higher-order modes, we still use \imrphenomp as it is faster to evaluate than numerical
-relativity models.
-
-\hypertarget{bayesian-parameter-estimation}{%
-\subsection{Bayesian Parameter Estimation}\label{bayesian-parameter-estimation}}
-
-We restrict the priors for Bayesian parameter estimation on the masses such that we only consider signals that are less
-than 454ms in duration, as presented in Table\textasciitilde\ref{tab:parameters}. The spins are set to be aligned with a range from
-{[}0,1{]}. The prior on luminosity distance assigns probability uniformly in comoving volume, with an upper cutoff of 5 Gpc.
-The \href{https://pycbc.org/}{\texttt{PyCBC}} search that originally produced our set of triggers considered a more comprehensive range of masses and
-spins than we do in the BCR computation for this project. To accommodate this, we screened the triggers to only allow
-triggers with masses within our priors. The run time on a single trigger using the \href{https://arxiv.org/abs/1904.02180}{\texttt{dynesty}} implementation of nested
-sampling, with \(2,000\) live points and \(100\) walkers is usually between \(0.5-12\) hours (where the speed often depends on
-the SNR of the data segment).
-
-\hypertarget{bcrCalculation}{%
-\subsection{BCR calculation}\label{bcrCalculation}}
-
-The Bayesian coherence ratio (BCR), as seen in \citet{BCR1}, is the odds between the hypothesis that the data comprise a
-coherent, compact binary coalescence signal in Gaussian noise (\(\mathcal{H}_S\)), and the hypothesis that they instead
-comprise incoherent instrumental features (\(\mathcal{H}_I\))---meaning each detector has either a glitch in Gaussian noise
-(\(\mathcal{H}_N\)) or pure Gaussian noise (\(\mathcal{H}_G\)). For a network of \(D\) detectors,
-
-\begin{equation}
-\mathrm{BCR} = \frac{\alpha Z^{S}}{\prod_{i=1}^{D}\left[\beta Z_{i}^{G}+(1-\beta) Z_{i}^{N}\right]}\ , \label{eq:bcr}
-\end{equation}
-where \(Z^S\) is the evidence for \(\mathcal{H}_S\), and \(Z^{G}_i\) and
-\(Z^N_i\) are the evidences for \(\mathcal{H}_{Gi}\) and \(\mathcal{H}_{Ni}\),
-in the \(i^{\text{th}}\) detectors. The arbitrary weights \(\alpha\) and \(\beta\)
-parametrise our prior belief in each model:
-
-\begin{itemize}
-\item
-  \(\alpha = P(\mathcal{H}_S)/P(\mathcal{H}_I)\)
-\item
-  \(\beta = P(\mathcal{H}_{Gi}|\mathcal{H}_I)=1-P(\mathcal{H}_{N}|\mathcal{H}_I)\)
-\end{itemize}
-
-for all \(i\) detectors. As most of the data should be noise, we expect both \(\alpha\) and \(\beta\), to be less than 1.
-These parameters will be tuned to minimise the overlap between the signal and noise trigger populations.
+are produced using \imrphenomp.
 
@@
 
-\begin{itemize}
-	\item briefly explain PyCBC search
-	\item define triggers
-	\item Extract PyCBC foreground, background and software injection trigger's GPS times based on template duration of triggers
-	\item analyse the triggers using Bayesian Parameter Estimation to determine $\log{Z_s}$, $\log{Z_g}$ and $\log{Z_n}$
-	\item reweight results to account for uncertainties in PSDs
-	\item Calculate BCR
-	\item Calculate PDFs
-	\item Find $\alpha$ and $\beta$ values such that separation of background and software injection PDFs is maximally apart.
-	\item use tuned $\alpha$ and $\beta$ from previous step to calculate BCRs for foreground
-	\item calculate the $p_{astro}$ of the foreground events to determine the probability of the trigger being from an astrophysical source. 
-\end{itemize}
-
 In aLIGO's first two observing runs, eleven gravitational wave events were found in the data by the LIGO-Virgo

### 2020-08-24 main.tex
Updates from Overleaf

@@
 \documentclass[%
- reprint,
+ %reprint,
 %superscriptaddress,
@@
 %frontmatterverbose, 
-%preprint,
+preprint,
 %preprintnumbers,
@@
 \usepackage{aas_macros}
+\usepackage{amssymb}
+\usepackage{amsmath}
+\usepackage{array}
+\usepackage{graphicx}
+\usepackage{color,units}
+\usepackage[dvipsnames]{xcolor} % for more colours!
+
+\usepackage{lineno}
+\usepackage{xspace}
+\usepackage{dcolumn}
+\usepackage{longtable}
+\usepackage[normalem]{ulem} %% for striking out text
+\usepackage{subfigure}
+\usepackage[T1]{fontenc}
+\usepackage{hyperref}
 
@@
 \graphicspath{{Figures/}} %Setting the graphicspath
+
+                 % Astronomical Journal
 
@@
 \newcommand{\bcr}{{\sc BCR}\xspace}
-\newcommand{\psd}{{\sc $\sigma^2$}\xspace}
+\newcommand{\psd}{{\sc $\sigma^2_i$}\xspace}
 \newcommand{\pastro}{{$p_\text{astro}$}\xspace}
@@
 
- In this paper we utilise a Bayesian method, called the\bcr \cite{BCR1}, to search for the significant gravitational wave signals from high-mass (systems with total masses in the range of $55-500$ \msun) compact binary coalescences in the detector data recorded during aLIGO's second observing run (O2).
+In this paper we utilise a Bayesian method, called the \bcr \cite{BCR1}, to search for the significant gravitational wave signals from high-mass (systems with total masses in the range of $55-500$ \msun) compact binary coalescences in the detector data recorded during aLIGO's second observing run (O2).
 We find that (a) our search does not identify any unreported stellar mass or intermediate mass black holes; (b) high-mass events reported in the GWTC-1, including GW170729 (an event with disputed $p_\text{astro}$ amongst various search pipelines) have high low significance; and that (c) high-mass events detected from some independent groups have low significance.
@@
 
+\av{I have broken this section up into subsections for my convenience, we can remove them later}
+
 \subsection{The Bayesian Coherence Ratio}
@@
 \begin{equation}
-BCR = \frac{\alpha Z^S}{\Pi^D_{i=1}[\beta Z^G_i + (1-\beta)Z^N_i]}\ ,
+BCR = \frac{\alpha Z^S}{\prod\limits^D_{i=1}[\beta Z^G_i + (1-\beta)Z^N_i]}\ ,
 \end{equation}
-where $Z^S$, $Z^G_i $ and $Z^N_i }$ are the Bayesian evidences (marginalised likelihoods) for $\mathcal{H_S}$, $\mathcal{H_N}$, and $\mathcal{H_G}$.
+where $Z^S$, $Z^G_i$ and $Z^N_i$ are the Bayesian evidences (marginalised likelihoods) for $\mathcal{H_S}$, $\mathcal{H_N}$, and $\mathcal{H_G}$.
 $\alpha$ and $\beta$, are the prior odds for obtaining a signal $\alpha=P(\mathcal{H_S})/P(\mathcal{H_I})$ and the prior odds for obtaining a glitch $\beta=P(\mathcal{H_G})/P(\mathcal{H_I})$.
@@
 
+\subsection{Bayesian Evidence Evaluation}
+\subsubsection{Noise Model}
 We assume that each detector's noise is Gaussian and stationary over the period being analysed \cite{ligo_psd}.
-In practice, we estimate the noise using a noise power spectral density \psd.
-The method of estimating the \psd, along with details on the implementation of our Bayesian inference pipeline is presented in the following section \av{(Not sure if the details on the PSD generation should be here or not...)}.
-Using the \psd, we can write
+In practice, we estimate the noise using a noise power spectral density \psd for each of the $i$ detectors.
+\\
+
+To generate the \psd, we take 31 neighbouring, ``off-source'', non-overlapping,  $4\ s$  segments of time-series data prior to the data segment $d_i$ being analysed.
+A Tukey window with a roll off of $0.2\ \text{s}$ is applied to each data segment to suppress spectral leakage after which the segments are fast-Fourier transformed and median-averaged to create a \psd \cite{ligo_psd}.
+This method, like other \psd estimation methods, adds statistical uncertainties to the \psd \cite{psd_student_t}.
+To marginalise over the statistical uncertainty we use the median-likelihood presented by \citet{psd_student_t} as a post-processing step and shift our Bayesian Evidence estimations closer to their true astrophysical values.
+
+Using the \psd, for each data segment $d_i$ in each of the $i$ detectors in a network of $D$ detectors, we can write 
 \begin{equation}
-Z^N_i =  \frac{1}{2\pi \sigma^2} \text{exp}\left(-\frac{1}{2} \frac{d_i}{\sigma^2} \right) \ ,
-\end{equation}
-for the data $d_i$ in each of the $i$ detectors in a network of $D$ detectors..
-
-We model coherent signal with parameters $\vec{\theta}$ using \imrphenomp $\mu_{\text{IMR}}(\vec{\theta})$.
-For this model to be coherent, the $\vec{\theta}$ must be consistent in each dataset $d_i$ for a network of $D$ detectors.
-Note that $\mu_{\text{IMR}}(\vec{\theta})$ is a phenomenological aligned spin waveform template constructed in the frequency domain that models the in-spiral, merger, and ringdown (IMR) of a compact binary coalescence \citep{khan2016frequency}.
-Although gravitational wave templates such as \seob $\mu_{\text{SEOB}}$ created from numerical relativity simulations incorporate more physics such as information on higher-order modes, we still use $\mu_{\text{IMR}}\vec{\theta}$ as this phenomenological model is faster to evaluate than numerical relativity models.
-Hence, the coherent signal evidence is calculated as
-\begin{equation}
-Z^S = \int \Pi^D_{i=1} \left[\frac{1}{2\pi \sigma^2} \text{exp}\left(\right)-\frac{1}{2} \frac{(d_i-\mu_{\text{IMR}}\vec{\theta})^2}{\sigma^2} \right) \right] \pi(\vec{\theta}) \text{d}\vec{\theta}  \ .
+Z^N_i =  \frac{1}{2\pi \sigma^2_i} \text{exp}\left(-\frac{1}{2} \frac{d_i}{\sigma^2_i} \right) .
 \end{equation}
 
-\av{Introduce pi before the above}
+\subsubsection{Coherent Signal Model}
+We model coherent signal using a binary black hole waveform template $\mu(\vec{\theta})$, where the vector $\vec{\theta}$ contains a point in the 15 dimensional space describing precessing binary-black hole mergers.
+For the signal to be coherent, $\vec{\theta}$ must be consistent in each $4\ \text{s}$ data segment $d_i$ for a network of $D$ detectors, Hence, the coherent signal evidence is calculated as
+\begin{equation}
+\label{eq:zs}
+Z^S = \int\limits_{\vec{\theta}} \prod\limits^{D}_{i=1} \left[\frac{1}{2\pi \sigma^2_i} \text{exp}\left(-\frac{1}{2} \frac{(d_i-\mu(\vec{\theta}))^2}{\sigma^2_i} \right) \right] \pi(\vec{\theta}| \mathcal{H_S})\  \text{d}\vec{\theta} \ ,
+\end{equation}
+where $\pi(\theta| \mathcal{H_S})$ is the prior for the parameters in the coherent signal hypothesis.
 
-Finally, as glitches are challenging to model and poorly understood, we utilise a surrogate model for glitches: the glitches are modelled using $\mu_{\text{IMR}}\vec{\theta}$ with uncorrelated  parameters amongst the different detectors such that  $\vec{\theta}_i \neq \vec{\theta}_j$ for two detectors $i$ and $j$ \cite{bci}.
+\subsubsection{Incoherent Glitch Model}
+Finally, as glitches are challenging to model and poorly understood, we utilise a surrogate model for glitches: the glitches are modelled using $\mu(\vec{\theta})$ with uncorrelated  parameters amongst the different detectors such that  $\vec{\theta}_i \neq \vec{\theta}_j$ for two detectors $i$ and $j$ \cite{bci}.
 Modelling glitches with gravitational wave templates captures the worst case scenario for when glitches appear similar to gravitational wave signals.
@@
 \begin{equation}
-Z^G_i = \int \frac{1}{2\pi \sigma^2} \text{exp}\left(\right)-\frac{1}{2} \frac{(d -\mu_{\text{IMR}}\vec{\theta})^2}{\sigma^2} \right) \pi(\vec{\theta}) \text{d}\vec{\theta}  \ .
+\label{eq:zg}
+Z^G_i = \int\limits_{\vec{\theta}} \frac{1}{2\pi \sigma^2_i} \text{exp}\left(-\frac{1}{2} \frac{(d_i -\mu(\vec{\theta}))^2}{\sigma^2_i} \right) \pi(\vec{\theta}| \mathcal{H_G})\  \text{d}\vec{\theta}  \ ,
 \end{equation}
+where $\pi(\theta| \mathcal{H_G})$ is the prior for the parameters in the incoherent glitch hypothesis.
 
-\hypertarget{bayesian-parameter-estimation}{%
-	\subsection{Bayesian Parameter Estimation}\label{bayesian-parameter-estimation}}
+\section{Analysis}\label{sec:Analysis}
 
-To generate posterior probability distributions and calculate Bayesian evidences for our signal, glitch and noise models, we carry out Bayesian inference with \bilby \cite{bilby}, employing \dynesty \cite{dynesty} as our nested sampler.
-Although nested sampling, an algorithm introduced by \cite{skilling_nested_sampling}, is an estimate of the true Bayesian evidence,
+Advanced LIGO's second observing run O2 lasted $38$ weeks \cite{GWOSC}.
+The software package, \pycbc \cite{pycbc_code}, processed the O2 data in 22 chunks (approximately 2 weeks for one chunk) and found several gravitational wave events and some gravitational wave candidates \cite{pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5}.
 
-To generate the \psd, we take 31 neighbouring, "off-source", non-overlapping,  $4\ s$  segments of time-series data prior to the data being analysed.
-A Tukey window with a roll off of $0.2\ s$ is applied to each data segment to suppress spectral leakage after which the segments are fast-Fourier transformed and median-averaged to create a \psd.
-This method, like other \psd estimation methods, adds statistical uncertainties to the \psd \cite{psd_student_t}.
-To marginalise over the statistical uncertainty we use the median-likelihood presented by \citet{psd_student_t} to re-weight our posterior samples as a post-processing step and shift our Bayesian Evidence estimations closer to their true astrophysical values.
+At its core, \pycbc performs a matched-filter search for binary merger signals using a template-bank of gravitational-wave template waveforms to generate triggers.
+For the trigger to be considered a \textbf{candidate trigger} by \pycbc, it must be observed between detectors with the same template and with a time of arrival difference less than the gravitational-wave travel time between detectors \cite{pycbc_og0}.
+To test its search, \pycbc also conducts searches for simulated signals.
+\textbf{Simulated triggers} are artificial triggers created by injecting signals into the detector data.
+These simulated signal studies provides \pycbc with metrics on its sensitivity.
+Finally, to quantify the rareness of candidate events, \pycbc artificially constructs a \textbf{background trigger} set to compare the candidate events against.
+These background triggers are signal-free events, created by applying relative offsets, or time-shifts, between the data of different detectors \cite{pycbc_og0}.
+Note that the time-shifts are greater than the gravitational-wave travel time between detectors.
 
-We restrict the priors for Bayesian parameter estimation on the masses such that we only consider signals that are less
-than 454ms in duration, as presented in Table\textasciitilde\ref{tab:parameters}. The spins are set to be aligned with a range from
-{[}0,1{]}. The prior on luminosity distance assigns probability uniformly in comoving volume, with an upper cutoff of 5 Gpc.
-The \href{https://pycbc.org/}{\texttt{PyCBC}} search that originally produced our set of triggers considered a more comprehensive range of masses and
-spins than we do in the BCR computation for this project. To accommodate this, we screened the triggers to only allow
-triggers with masses within our priors. The run time on a single trigger using the \href{https://arxiv.org/abs/1904.02180}{\texttt{dynesty}} implementation of nested
-sampling, with \(2,000\) live points and \(100\) walkers is usually between \(0.5-12\) hours (where the speed often depends on
-the SNR of the data segment).
+The \pycbc search in O2 produced numerous candidate, simulated and background triggers. For our high-mass study, we screen the triggers to only allow
+triggers with masses within the ranges of the parameters presented in Table\textasciitilde\ref{tab:parameters}.
+Plot of the \pycbc triggers from one chuk  To calculate the \bcr for these triggers, we carry out Bayesian inference with \bilby \cite{bilby}, employing \dynesty \cite{dynesty} as our nested sampler.
+Nested sampling, an algorithm introduced by \cite{skilling_nested_sampling}, provides an estimate of the true Bayesian evidence and is often utilised for parameter estimation within the LIGO collaboration \cite{bilby}.
 
-we use the noise power spectral densities created with a median-average method by taking 31 neighbouring, "off-source", non-overlapping,  4 second segments of data prior to the data being analysed.
-Before computing the PSD,   prior to fast-Fourier transforming the the windowed time-domain strain before averaging the PSD chunks.As this method does not provide a perfect estimation of the true noise power spectral density  These power spectral densities are ?
-with a studuent-T's distribution to account for ?
-\cite{psd_student_t}.
+We restrict the priors for Bayesian inference on the masses to only consider signals shorter than $454 \text{ms}$ in duration, as presented in Table\textasciitilde\ref{tab:parameters}.
+The spins are set to be aligned with a uniform range for the dimensionless spin magnitude from $\left[0,1\right]$.
+The prior on luminosity distance assigns probability uniformly in comoving volume, with an upper cutoff of $5\ \text{Gpc}$.
+We implement the same priors as used in GWTC-1 for the remaining parameters.
+The priors we use for the coherent signal and incoherent glitch hypotheses are identical.\\
+
+The waveform template we utilise is \imrphenomp $\mu_{\text{IMR}}(\vec{\theta})$, a phenomenological waveform template constructed in the frequency domain that models the in-spiral, merger, and ringdown (IMR) of a compact binary coalescence \citep{khan2016frequency}.
+Although gravitational wave templates such as \seob \cite{seob} created from numerical relativity simulations incorporate more physics such as information on higher-order modes, we still use $\mu_{\text{IMR}}(\vec{\theta})$ as it evaluates faster than numerical relativity models.
+
+Finally, we neglect detector calibration uncertainty and acquire data from from the Gravitational Wave Open Science Center \cite{GWOSC}.
+The data we use is the publicly accessible O2 strain data from the Hanford and Livingston detectors.
+To ensure the data is usable we verify that the analysis and PSD data are obtained when the detectors are  in ``Science Mode''.
+The data requisition and quality checks are conducted using \gwpy \cite{}.
+
+For the Bayesian Inference, we use a ? likelihood.... \av{talk about TDP marginalisation, cite Eric and COlms paper}
+
+The run-time for to calculate a single Bayesian evidence after using \dynesty with $1,000$ live points and $100$ walkers is usually between $0.5-12\ \text{hours}$ (where the speed often depends on the SNR of the data segment).
 
@@
 
-% We use the publicly available strain data associated with the 10 binary black hole events in GWTC-1.
-We implement the same priors as used in GWTC-1 for almost all parameters.
-The exceptions are eccentricity, which is not included in GWTC-1, and aligned dimensionless component spins, which are only supported in SEOBNRE between −1 and 0.6.
-Our prior on eccentricity is uniform in log10(e) in the range −6 ≤ log10(e) ≤ −0.7.
-Our aligned dimensionless component spin prior is uniform between −0.6 and 0.6.
-Our prior boundaries for cyclic parameters (e.g.
-coalescence phase, right ascension, and declination) are periodic, while our priors for non-cyclic parameters (e.g.
-mass and distance) have reflective boundaries.
-
-% Generating a posterior probability distribution demands many thousands of likelihood calculations, each requiring waveform template evaluation.
-While standard quasi-circular waveform models are fast enough to facilitate reasonable computation times, eccentric waveforms including merger and ringdown physics are not.
-SEOBNRE takes roughly a million times longer to evaluate a GW150914-like signal than aligned-spin quasi-circular waveform model IMRPHENOMD
-
-%  We use nested sampling, introduced by Skilling (2006) and popular for gravitational-wave data analysis due to its handling of high-dimensional spaces (Veitch et al.
-2015).
-For a thorough review of Bayesian inference in the context of gravitational-wave astrophysics, see Thrane & Talbot (2018).
-
-% where μ is our waveform template and σ is the detector noise amplitude spectral density.1 We assume Gaussian noise, using the noise power spectral densities σ2 that were used to produce the GWTC-1 results.
-We neglect calibration uncertainty.
-We generate μ using SEOBNRE (Cao & Han 2017), an effective one-body numerical-relativity waveform model that can produce non-circular waveforms with eccentricities in the range 0 ≤ e ≤ 0.2 at 10 Hz.
-The SEOBNRE waveform model incorporates more complex physics than the waveform used in Lower et al.
-(2018).
-It includes aligned dimensionless component spin magnitudes between −1 and 0.6, and models the merger and ringdown in addition to the inspiral.
-
-% We carry out Bayesian inference with BILBY (Ashton et al.
-2019), using DYNESTY (Speagle 2019) as our nested sampler.
-We use the publicly available strain data associated with the 10 binary black hole events in GWTC-1.
-We implement the same priors as used in GWTC-1 for almost all parameters.
-The exceptions are eccentricity, which is not included in GWTC-1, and aligned dimensionless component spins, which are only supported in SEOBNRE between −1 and 0.6.
-Our prior on eccentricity is uniform in log10(e) in the range −6 ≤ log10(e) ≤ −0.7.
-Our aligned dimensionless component spin prior is uniform between −0.6 and 0.6.
-Our prior boundaries for cyclic parameters (e.g.
-coalescence phase, right ascension, and declination) are periodic, while our priors for non-cyclic parameters (e.g.
-mass and distance) have reflective boundaries.
-
-% Generating a posterior probability distribution demands many thousands of likelihood calculations, each requiring waveform template evaluation.
-While standard quasi-circular waveform models are fast enough to facilitate reasonable computation times, eccentric waveforms including merger and ringdown physics are not.
-SEOBNRE takes roughly a million times longer to evaluate a GW150914-like signal than aligned-spin quasi-circular waveform model IMRPHENOMD
-
 % PyCBC asks for the 5 citations:
 % http://pycbc.org/pycbc/latest/html/credit.html#searches-for-compact-binary-coalescence
-high-mass candidate events, simulated signal events and  background events (signal-free events ) supplied by the \pycbc \cite{pycbc_code} search in O2  \cite{pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5}.
-At its core, \pycbc performs a matched-filter search for binary merger signals using a template-bank of gravitational-wave template waveforms to generate triggers.
-For the trigger to be considered a  candidate event by \pycbc, it must be observed between detectors with the same template and with a time of arrival difference less than the gravitational-wave travel time between detectors \cite{pycbc_og0}.
-The simulated signal events are artificially created by injecting signals into the detector data.
-Similarly, \pycbc artificially constructs the background, signal-free, events by applying relative offsets, or time-shifts, between the data of different detectors \cite{pycbc_og0}.
+high-mass candidate events, simulated signal events and  background events (signal-free events ) supplied by the \pycbc \cite{pycbc_code} search in O2  \
 
@@
 Dont know the prior odds,
-
-We use \bilbypipe to both acquire the publicly accessible LIGO data in 4s-long data segments containing each trigger (analysis segments) and to generate PSDs via Welch's method for each data segment by taking 124 seconds of the data before the analysis segment.
-If the data quality is not marked as ``Science Mode'' for either the PSD or analysis data, then the analysis of that trigger is skipped.
-Gravitational-wave templates
-are produced using \imrphenomp.
 
@@
 
+\section{\label{sec:Results}Results}
+blah
+
 \section{\label{sec:Conclusion}Conclusion}
@@
 \begin{acknowledgments}
-Helpful comments, OzGrav, LIGO, NSF
+Helpful comments, OzGrav, LIGO, NSF.
+
+This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open Science Center (https://www.gw-openscience.org), a service of LIGO Laboratory, the LIGO Scientific Collaboration and the Virgo Collaboration.
+LIGO is funded by the U.S.
+National Science Foundation.
+Virgo is funded by the French Centre National de Recherche Scientifique (CNRS), the Italian Istituto Nazionale della Fisica Nucleare (INFN) and the Dutch Nikhef, with contributions by Polish and Hungarian institutes.
 

### 2020-09-03 main.tex
Completed analysis section

@@
 \newcommand{\prior}{{\sc prior}\xspace}
-\newcommand{\bilby}{{\sc Bilby}\xspace}
+\newcommand{\bilby}{{\sc \href{https://lscsoft.docs.ligo.org/bilby/}{\texttt{Bilby}}}\xspace}
 \newcommand{\bilbypipe}{{\sc bilby\_pipe}\xspace}
-\newcommand{\bilbypipegdb}{\texttt{bilby\_pipe\_gracedb}\xspace}
 \newcommand{\pbilby}{{\sc pBilby}\xspace}
@@
 \newcommand{\ptemcee}{{\sc ptemcee}\xspace}
-\newcommand{\gwpy}{{\sc GWpy}\xspace}
+\newcommand{\gwpy}{{\sc \href{https://gwpy.github.io/}{\texttt{GWpy}}}\xspace}
 \newcommand{\imrphenomp}{{\sc IMRPhenomPv2}\xspace}
 \newcommand{\seob}{{\sc SEOBNRv4PHM}\xspace}
-\newcommand{\pycbc}{{\sc PyCBC}\xspace}
+\newcommand{\pycbc}{{\sc \href{https://pycbc.org/}{\texttt{PyCBC}}}\xspace}
 \newcommand{\bcr}{{\sc BCR}\xspace}
 \newcommand{\psd}{{\sc $\sigma^2_i$}\xspace}
-\newcommand{\pastro}{{$p_\text{astro}$}\xspace}
-\newcommand{\msun}{{M${}_\odot$}\xspace}
+\newcommand{\pastro}{{\sc $p_\text{astro}$}\xspace}
+\newcommand{\msun}{{\sc M${}_\odot$}\xspace}
+\newcommand{\template}{{\sc $\mu(\vec{\theta})$}\xspace}
+\newcommand{\parameters}{{\sc $\vec{\theta}$}\xspace}
 
@@
 \section{\label{sec:Introduction}Introduction}
-
+\av{Need to edit in light of S190521G paper}
 Since the 1970s, there has been an accumulation of evidence for stellar-mass and supermassive black holes.
@@
 The remainder of this paper is structured as follows.
-We outline our analysis methods, including details of the \bcr in Section~\ref{sec:method}.
-We present our results in Section~\ref{sec:result}, and discuss these results in the context of the significance of gravitational wave candidates in Section~\ref{sec:Conclusion}.
+We outline our methods, including details of the \bcr and the retrieval of our candidate events in Section~\ref{sec:method}.
+We present details on the implementation of our analysis in Section~\ref{sec:Analysis}.
+Finally we present our results in Section~\ref{sec:result}, and discuss these results in the context of the significance of gravitational wave candidates in Section~\ref{sec:Conclusion}.
 
@@
 
-\av{I have broken this section up into subsections for my convenience, we can remove them later}
+\subsection{Triggers for Analysis}
+The LIGO Scientific collaboration runs a number of search pipelines that target gravitational waves from compact binary mergers such as the GstLAL, MBTA, SPIIR and PyCBC searches \cite{abbott2019gwtc}.\\
+
+At its core, the \pycbc \cite{pycbc_code} search performs a matched-filter search for binary merger signals by comparing the data against templates from a gravitational-wave template-bank \cite{pycbc_og6}.
+\pycbc calculates the matched-filter for several different coalescence times and uses numerous templates from the template bank for each section of data being analysed.
+The output of \pycbc's search is a signal-to-noise ratio $\rho$ like statistic, called the \pycbc ranking statistic $\rho_\text{PC}$.
+This statistic is a function of the matched-filter $\rho$, signal-based veto values, intrinsic and extrinsic properties of the apparent signal and other information \cite{pycbc_og6}.
+Whenever a local maximum of $\rho_\text{PC} > \rho_\text{T}$, where $\rho_\text{T}$ is some threshold value, the search pipeline produces a single-detector trigger associated with the detector and time where the data was obtained.\\
+
+For \pycbc to consider a trigger to be a \textbf{candidate trigger}, a trigger from astrophysical origins, the trigger must be observed between detectors with the same template and a time of arrival difference less than the gravitational-wave travel time between detectors \cite{pycbc_og6}.
+To test its search, \pycbc also conducts searches for \textbf{simulated triggers}, artificial triggers manufactured by injecting signals into the detector data.
+These simulated signal studies provides \pycbc with metrics on its search's sensitivity.
+Finally, to quantify the statistical significance of candidate events, \pycbc artificially constructs a \textbf{background trigger} set to compare the candidate events against.
+These background triggers are signal-free events, constructed by applying relative offsets, or time-shifts, between the data of different detectors \cite{pycbc_og6}.
+Note that the time-shifts to generate the background triggers are greater than the gravitational-wave travel time between detectors to ensure that the background triggers are not of astrophysical origins.
+\\
+
+In our work, we demonstrate that the \bcr can be used in a similar way as $\rho_\text{PC}$, as a ranking statistic, to measure the statistical significance of candidate triggers.
+Before we discuss how we use the \bcr as a measure of significance, we introduce the method to calculate the \bcr in the following section.\\
 
@@
 
-Following \citet{BCR1}, the \bcr is an odds ratio of the coherent signal hypotheses $\mathcal{H_S}$ and the incoherent instrumental feature hypothesis $\mathcal{H_I}$ for a network of $D$ detectors.
-$\mathcal{H_I}$ states that each $i$th detector has either pure Gaussian noise $\mathcal{H_N}$ or a glitch $\mathcal{H_G}$.
-The \bcr is given by
+Bayes theorem states that the probability $P(\mathcal{H}|d)$ for a hypothesis $\mathcal{H}$ and data $d$ is
 \begin{equation}
-BCR = \frac{\alpha Z^S}{\prod\limits^D_{i=1}[\beta Z^G_i + (1-\beta)Z^N_i]}\ ,
+    P(\mathcal{H}|d) = \frac{\mathcal{L}(d|\mathcal{H})\pi(\mathcal{H})}{Z}\ , 
 \end{equation}
-where $Z^S$, $Z^G_i$ and $Z^N_i$ are the Bayesian evidences (marginalised likelihoods) for $\mathcal{H_S}$, $\mathcal{H_N}$, and $\mathcal{H_G}$.
-$\alpha$ and $\beta$, are the prior odds for obtaining a signal $\alpha=P(\mathcal{H_S})/P(\mathcal{H_I})$ and the prior odds for obtaining a glitch $\beta=P(\mathcal{H_G})/P(\mathcal{H_I})$.
+where $\mathcal{L}(d|\mathcal{H})$ is the likelihood of the data given
+the hypothesis,  $\pi(\mathcal{H})$ is the prior probability of the hypothesis, and finally, $Z = \sum \mathcal{L}(d|\mathcal{H})  \pi(\mathcal{H})$ is the marginalised likelihood called the evidence.
+To compare two hypotheses $\mathcal{H}_A$ and $\mathcal{H}_B$ with the Bayes theorem one can calculate an odds ratio
+\begin{equation}
+    \mathcal{O}^A_B = \frac{Z^A\ \pi(\mathcal{H}_A)}{Z^B\ \pi(\mathcal{H}_B)}\ ,
+\end{equation}
+where $Z^A$ and $Z^B$ are the evidences for the $\mathcal{H}_A$ and $\mathcal{H}_B$ hypotheses.
+The odds ratio can tell us which of the two hypotheses is more likely.
+For example, if $\mathcal{O}^A_B >> 1$, then this odds ratio indicates that the $\mathcal{H}_A$ is much more likely than $\mathcal{H}_B$.
+\\
+
+The \bcr is a Bayesian odds ratio like the above, of a coherent signal hypotheses $\mathcal{H}_S$ and an incoherent instrumental feature hypothesis $\mathcal{H}_I$ for a network of $D$ detectors.
+$\mathcal{H_I}$ states that each detector $i$ has either pure Gaussian noise $\mathcal{H}_N$ or a glitch $\mathcal{H}_G$.
+Following \citet{BCR1}, the \bcr is given by
+\begin{equation}
+\label{eq:bcr}
+\text{BCR} = \frac{\alpha Z^S}{\prod\limits^D_{i=1} \ [\beta Z^G_i + (1-\beta)Z^N_i]}\ ,
+\end{equation}
+where $Z^S$, $Z^G_i$ and $Z^N_i$ are the Bayesian evidences (marginalised likelihoods) for $\mathcal{H}_S$, $\mathcal{H}_N$, and $\mathcal{H}_G$.
+$\alpha$ and $\beta$, are the prior odds for obtaining a signal $\alpha=P(\mathcal{H}_S)/P(\mathcal{H}_I)$ and the prior odds for obtaining a glitch $\beta=P(\mathcal{H}_G)/P(\mathcal{H}_I)$.
 As the rate of signal and glitches are unknown, these priors $\alpha$ and $\beta$ are tuned to maximise the \bcr distributions for background data (signal-free data) and simulated signals \cite{BCR1}.
@@
 We assume that each detector's noise is Gaussian and stationary over the period being analysed \cite{ligo_psd}.
-In practice, we estimate the noise using a noise power spectral density \psd for each of the $i$ detectors.
-\\
-
-To generate the \psd, we take 31 neighbouring, ``off-source'', non-overlapping,  $4\ s$  segments of time-series data prior to the data segment $d_i$ being analysed.
-A Tukey window with a roll off of $0.2\ \text{s}$ is applied to each data segment to suppress spectral leakage after which the segments are fast-Fourier transformed and median-averaged to create a \psd \cite{ligo_psd}.
-This method, like other \psd estimation methods, adds statistical uncertainties to the \psd \cite{psd_student_t}.
-To marginalise over the statistical uncertainty we use the median-likelihood presented by \citet{psd_student_t} as a post-processing step and shift our Bayesian Evidence estimations closer to their true astrophysical values.
-
+In practice, we estimate the noise using a noise power spectral density (PSD)  \psd.
 Using the \psd, for each data segment $d_i$ in each of the $i$ detectors in a network of $D$ detectors, we can write
 \begin{equation}
-Z^N_i =  \frac{1}{2\pi \sigma^2_i} \text{exp}\left(-\frac{1}{2} \frac{d_i}{\sigma^2_i} \right) .
+\label{eq:zn}
+Z^N_i = \mathcal{N}(d_i) = \frac{1}{2\pi \sigma^2_i} \ \text{exp}\left(-\frac{1}{2} \frac{d_i}{\sigma^2_i} \right) \ ,
 \end{equation}
+where $\mathcal{N}(d_i)$ is a normal distribution with a mean of zero and variance proportional to the \psd.
 
 \subsubsection{Coherent Signal Model}
-We model coherent signal using a binary black hole waveform template $\mu(\vec{\theta})$, where the vector $\vec{\theta}$ contains a point in the 15 dimensional space describing precessing binary-black hole mergers.
-For the signal to be coherent, $\vec{\theta}$ must be consistent in each $4\ \text{s}$ data segment $d_i$ for a network of $D$ detectors, Hence, the coherent signal evidence is calculated as
+We model coherent signal using a binary black hole waveform template \template, where the vector \parameters contains a point in the 15 dimensional space describing precessing binary-black hole mergers.
+For the signal to be coherent, \parameters must be consistent in each $4\ \text{s}$ data segment $d_i$ for a network of $D$ detectors, Hence, the coherent signal evidence is calculated as
 \begin{equation}
 \label{eq:zs}
-Z^S = \int\limits_{\vec{\theta}} \prod\limits^{D}_{i=1} \left[\frac{1}{2\pi \sigma^2_i} \text{exp}\left(-\frac{1}{2} \frac{(d_i-\mu(\vec{\theta}))^2}{\sigma^2_i} \right) \right] \pi(\vec{\theta}| \mathcal{H_S})\  \text{d}\vec{\theta} \ ,
+% Z^S = \int\limits_{\vec{\theta}} \prod\limits^{D}_{i=1} \left[\frac{1}{2\pi \sigma^2_i} \ \text{exp}\left(-\frac{1}{2} \frac{|d_i-\mu(\vec{\theta})|^2}{\sigma^2_i} \right) \right] \pi(\vec{\theta}| \mathcal{H}_S)\  \text{d}\vec{\theta} \ ,
+Z^S = \int\limits_{\vec{\theta}} \prod\limits^{D}_{i=1} \left[ \mathcal{L}(d_i|\mu(\vec{\theta}))\right] \pi(\vec{\theta}| \mathcal{H}_S)\  \text{d}\vec{\theta} \ ,
 \end{equation}
-where $\pi(\theta| \mathcal{H_S})$ is the prior for the parameters in the coherent signal hypothesis.
+where $\pi(\theta| \mathcal{H}_S)$ is the prior for the parameters in the coherent signal hypothesis, and $\mathcal{L}(d_i|\mu(\vec{\theta}))$ is the likelihood for the coherent signal hypothesis that depends on the gravitational wave template \template and its parameters \parameters.
 
 \subsubsection{Incoherent Glitch Model}
-Finally, as glitches are challenging to model and poorly understood, we utilise a surrogate model for glitches: the glitches are modelled using $\mu(\vec{\theta})$ with uncorrelated  parameters amongst the different detectors such that  $\vec{\theta}_i \neq \vec{\theta}_j$ for two detectors $i$ and $j$ \cite{bci}.
-Modelling glitches with gravitational wave templates captures the worst case scenario for when glitches appear similar to gravitational wave signals.
+Finally, as glitches are challenging to model and poorly understood, we utilise a surrogate model for glitches: the glitches are modelled using gravitational wave templates  \template with uncorrelated  parameters amongst the different detectors such that  $\vec{\theta}_i \neq \vec{\theta}_j$ for two detectors $i$ and $j$ \cite{bci}.
+Modelling glitches with \template captures the worst case scenario: when glitches appear similar to gravitational wave signals.
 Thus, we can write $Z^G_i$ as
@@
 \label{eq:zg}
-Z^G_i = \int\limits_{\vec{\theta}} \frac{1}{2\pi \sigma^2_i} \text{exp}\left(-\frac{1}{2} \frac{(d_i -\mu(\vec{\theta}))^2}{\sigma^2_i} \right) \pi(\vec{\theta}| \mathcal{H_G})\  \text{d}\vec{\theta}  \ ,
+% Z^G_i = \int\limits_{\vec{\theta}} \frac{1}{2\pi \sigma^2_i} \ \text{exp}\left(-\frac{1}{2} \frac{|d_i-\mu(\vec{\theta})|^2}{\sigma^2_i} \right) \pi(\vec{\theta}| \mathcal{H}_G)\  \text{d}\vec{\theta}  \ ,
+Z^G_i = \int\limits_{\vec{\theta}} \mathcal{L}(d_i|\mu(\vec{\theta}))\ \pi(\vec{\theta}| \mathcal{H}_G)\  \text{d}\vec{\theta}  \ ,
 \end{equation}
-where $\pi(\theta| \mathcal{H_G})$ is the prior for the parameters in the incoherent glitch hypothesis.
+where $\pi(\theta| \mathcal{H}_G)$ is the prior for the parameters in the incoherent glitch hypothesis.
+
+\subsection{Tuning the BCR}
+
+After calculating the \bcr for a set of background triggers and simulated triggers from as stretch of detector-data, we can compute probability distributions for the background and simulated triggers, $p_b(\text{BCR})$ and $p_s(\text{BCR})$.
+We expect the background trigger and simulated signal \bcr values to favour the incoherent glitch and the coherent signal hypothesis, respectively.
+Ideally these distributions that represent two unique populations should be distinctly separate and have no overlap in their \bcr values.
+The prior odds parameters $\alpha$ and $\beta$ from Eq.~\ref{eq:bcr} help separate the two distributions.
+Altering $\alpha$ translates the \bcr probability distributions while adjusting $\beta$ spreads the distributions.
+Although Bayesian hyper-parameter estimation can determine the optimal values for these parameters, an easier approach is to manually adjust the parameters for each data chunk's \bcr distribution.
+In this study, we manually tune $\alpha$ and $\beta$ to maximally separate the \bcr distributions for the background and simulated triggers.
+\\
+
+To calculate the separation between $p_b(\text{BCR})$ and $p_s(\text{BCR})$, we use the Kullback--Leibler divergence (KL divergence) $D_{KL}$, given by
+\begin{equation}
+    D_{KL}(p_b | p_s) = \sum\limits_{i=1}^N p_b(\text{BCR}_i) \cdot (\log p_b(\text{BCR}_i) - \log p_s(\text{BCR}_i)) \ .
+\end{equation}
+The $D_{KL}=0$ when the distributions are identical and increases as the asymmetry between the distributions increases. \\
+
+We limit our search for the maximum KL-divergence in the $\alpha$ and $\beta$ ranges of $[E-10, E0]$ as values outside this range are nonphysical.
+We set our values for $\alpha$ and $\beta$ to those which provide the highest KL-divergence and can now calculate the \bcr for candidate events present in this stretch of detector-data.
+Note that we conduct the analysis in stretches of data rather than an entire data set as the background may be different at different points of the entire data set.
+
+\subsection{Calculating the Significance of Candidate events}
+With the tuned values of $\alpha$ and $\beta$ we can calculate the \bcr for candidate events.
+As mentioned previously, irrespective of the \bcr's Bayesian interpretation, we treat the \bcr as a traditional detection statistic to obtain a frequentist estimate of the significance of candidate event measured against the background of signal-free data.
+\\
+
+We expect the background trigger \bcr values to favour the incoherent glitch hypothesis (the null hypothesis).
+Candidate event \bcr values will either be statistically insignificant compared to the background triggers, implying the candidate is a glitch, or statistically significant to the background distribution, indicating the possible presence of an astrophysical signal.
+To quantify the level of significance we can calculate a $p\text{-value}$s for the candidate events.
+Here, the $p\text{-value}$ tells us how probable it is for the candidate event to be a glitch.
+Hence, we can use the $p\text{-value}$ to calculate
+\begin{equation}
+    p_\text{astro} = 1 - p\text{-value} \ ,
+\end{equation}
+where \pastro is the probability that a signal is of astrophysical origin \cite{pastro_1,pastro_2,pastro_3}.
 
@@
 
+\subsection{Acquisition of triggers}
 Advanced LIGO's second observing run O2 lasted $38$ weeks \cite{GWOSC}.
-The software package, \pycbc \cite{pycbc_code}, processed the O2 data in 22 chunks (approximately 2 weeks for one chunk) and found several gravitational wave events and some gravitational wave candidates \cite{pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5}.
+The software package, \pycbc \cite{pycbc_code}, processed the O2 data in 22 time-frames (approximately 2 weeks for one time-frames) and found several gravitational wave events and numerous gravitational wave candidates \cite{pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5}.
+Some candidate events were vetoed to be glitches, while others due to their low significance.
+The data is divided into these time-frames because the detector's sensitivity does not stay constant throughout 8 month long observing period.\\
 
-At its core, \pycbc performs a matched-filter search for binary merger signals using a template-bank of gravitational-wave template waveforms to generate triggers.
-For the trigger to be considered a \textbf{candidate trigger} by \pycbc, it must be observed between detectors with the same template and with a time of arrival difference less than the gravitational-wave travel time between detectors \cite{pycbc_og0}.
-To test its search, \pycbc also conducts searches for simulated signals.
-\textbf{Simulated triggers} are artificial triggers created by injecting signals into the detector data.
-These simulated signal studies provides \pycbc with metrics on its sensitivity.
-Finally, to quantify the rareness of candidate events, \pycbc artificially constructs a \textbf{background trigger} set to compare the candidate events against.
-These background triggers are signal-free events, created by applying relative offsets, or time-shifts, between the data of different detectors \cite{pycbc_og0}.
-Note that the time-shifts are greater than the gravitational-wave travel time between detectors.
-
-The \pycbc search in O2 produced numerous candidate, simulated and background triggers. For our high-mass study, we screen the triggers to only allow
-triggers with masses within the ranges of the parameters presented in Table\textasciitilde\ref{tab:parameters}.
-Plot of the \pycbc triggers from one chuk  To calculate the \bcr for these triggers, we carry out Bayesian inference with \bilby \cite{bilby}, employing \dynesty \cite{dynesty} as our nested sampler.
-Nested sampling, an algorithm introduced by \cite{skilling_nested_sampling}, provides an estimate of the true Bayesian evidence and is often utilised for parameter estimation within the LIGO collaboration \cite{bilby}.
-
-We restrict the priors for Bayesian inference on the masses to only consider signals shorter than $454 \text{ms}$ in duration, as presented in Table\textasciitilde\ref{tab:parameters}.
-The spins are set to be aligned with a uniform range for the dimensionless spin magnitude from $\left[0,1\right]$.
-The prior on luminosity distance assigns probability uniformly in comoving volume, with an upper cutoff of $5\ \text{Gpc}$.
-We implement the same priors as used in GWTC-1 for the remaining parameters.
-The priors we use for the coherent signal and incoherent glitch hypotheses are identical.\\
-
-The waveform template we utilise is \imrphenomp $\mu_{\text{IMR}}(\vec{\theta})$, a phenomenological waveform template constructed in the frequency domain that models the in-spiral, merger, and ringdown (IMR) of a compact binary coalescence \citep{khan2016frequency}.
-Although gravitational wave templates such as \seob \cite{seob} created from numerical relativity simulations incorporate more physics such as information on higher-order modes, we still use $\mu_{\text{IMR}}(\vec{\theta})$ as it evaluates faster than numerical relativity models.
-
-Finally, we neglect detector calibration uncertainty and acquire data from from the Gravitational Wave Open Science Center \cite{GWOSC}.
-The data we use is the publicly accessible O2 strain data from the Hanford and Livingston detectors.
-To ensure the data is usable we verify that the analysis and PSD data are obtained when the detectors are  in ``Science Mode''.
-The data requisition and quality checks are conducted using \gwpy \cite{}.
-
-For the Bayesian Inference, we use a ? likelihood.... \av{talk about TDP marginalisation, cite Eric and COlms paper}
-
-The run-time for to calculate a single Bayesian evidence after using \dynesty with $1,000$ live points and $100$ walkers is usually between $0.5-12\ \text{hours}$ (where the speed often depends on the SNR of the data segment).
-
-\pastro, the probability that a signal is of astrophysical origin \cite{pastro_1,pastro_2,pastro_3},
-
- provides a Bayesian odds ratio comparing the probability that the data contains an astrophysical signal versus the probability that the data contains an incoherent glitch or noise.
-Although an odds ratio, the \bcr can be used  as a frequentistic \textit{ranking statistic}, ranking the likelihood that a trigger is due to a gravitational-wave signal \cite{BCR}.
-The \bcr as a ranking statistic is much more powerful than a matched-filter SNR as the \bcr incorporates numerous features that may distinguish gravitational waves from noise and demands that signals must be coherent while glitches must be incoherent amongst different detectors.
+In addition to finding candidate events, \pycbc also manufactured several million background triggers for each time-frames, to quantify the significance of the candidate events when compared to the background for the respective time-frames.
+Finally, to test the search's sensitivity, \pycbc simulated and searched for thousands of artificial signals.
 \\
 
-% PyCBC asks for the 5 citations:
-% http://pycbc.org/pycbc/latest/html/credit.html#searches-for-compact-binary-coalescence
-high-mass candidate events, simulated signal events and  background events (signal-free events ) supplied by the \pycbc \cite{pycbc_code} search in O2  \
-
-Figure~\ref{fig:templateBank} depicts the \pycbc template bank, the high-mass search space and the candidate events, simulated events and background events from a one-week stretch of \pycbc's search in O2.
-
-Week long stretches of analysis because noise-non stationary, glitches will occur at different rates depending on state of detectors
-
-Dont know the prior odds,
-
-\hypertarget{trigger-sets-for-bcr-analysis}{%
-\subsection{Trigger sets for BCR analysis}\label{trigger-sets-for-bcr-analysis}}
-
-We calculate the BCRs using the procedure described above for three separate trigger sets: background triggers,
-foreground triggers, and software injections. The software injections created using masses, spins and distances that
-span our priors. The software injections are inserted in the O2 data from where the other triggers are retrieved.
-
-We expect the background trigger BCRs to favour the incoherent glitch hypothesis, and the software injection BCRs to
-favour the coherent, compact binary coalescence hypothesis. The foreground trigger BCRs should fall along with the
-background if the foreground trigger is a glitch, and with the software injections if the foreground trigger is a
-gravitational wave candidate. For example, consider Figure\textasciitilde\ref{fig:bcrIfar} that contains a plot of the BCRs for
-several O1 background triggers, foreground triggers, and software injections plotted against iFAR (inverse
-false-alarm-rate). In the figure, some foreground triggers fall along the background distribution, these are discarded
-as glitches. The foreground triggers that fall along the bulk of software injections are considered gravitational wave
-candidates.
-
-\begin{figure}[!h]
-
-{\centering \includegraphics[width=0.75\linewidth]{images/bcr_ifar}
-
-}
-
-\caption[BCR vs iFAR for O1]{BCR versus iFAR distributions from simulated signals (blue), hardware injections (green), GW events (stars) and background triggers (black), taken from \citet{BCR1}.}\label{fig:bcrIfar}
-\end{figure}
-
-\hypertarget{making-a-significance-statement}{%
-\subsection{Making a significance statement}\label{making-a-significance-statement}}
-
-After obtaining the BCRs for the foreground triggers, background triggers, and software injections, we can make a
-statement about the significance of foreground events. For example, consider Figure\textasciitilde\ref{fig:bcrCdf} which displays ln
-BCR distributions obtained from our BCR pipeline for aLIGO O2 PyCBC chunk three background triggers and software injections.
-The figure also displays the ln BCR values obtained for four foreground triggers. The two foreground triggers with low
-ln BCRs are confirmed glitches. The rightmost foreground trigger is GW170104, a gravitational wave event confirmed by
-LIGO, and shows much stronger evidence for it being a coherent, compact binary coalescence signal, rather than it being
-an incoherent glitch. The remaining foreground trigger corresponds to a gravitational wave candidate identified by the
-IAS group.
-
-\begin{figure}[!h]
-
-{\centering \includegraphics[width=0.75\linewidth]{images/bcr_cdf}
-
-}
-
-\caption[BCR distribution example]{Histograms represent the survival function (1-CDF) from our selection of 2407 aLIGO O2 PyCBC chunk 3 background triggers (gray) and 648 simulated signals (blue).
-Vertical lines mark the ln BCRs of two glitches (orange and yellow), IAS's GW170121 (pink), and GWTC-1's GW170104 (dark blue).}\label{fig:bcrCdf}
-\end{figure}
-
-Irrespective of the BCR's Bayesian interpretation, we may treat the BCR as a traditional detection statistic to obtain a
-frequentist estimate of the significance of any given foreground event based on the measured background with a p-value.
-The p-value of foreground events can be obtained from the background's survival function. For example, in
-Figure\textasciitilde\ref{fig:bcrCdf}, the p-value for GW170104 is 0.99, denoting that it is significantly different from the bulk
-of the background distribution and hence likely to have astrophysical origins. On the other hand, the p-value for the
-IAS candidate is 0.65, demonstrating that this candidate might be a glitch.
-
-To calculate the p-value, we need first to calculate fits to the BCR probability
-distributions and then tune the BCR's parameters. The following subsections describe these calculations.
-
-\hypertarget{fitting-bcr-data}{%
-\subsubsection{Fitting BCR data}\label{fitting-bcr-data}}
-
-Although the BCR should favour the coherent signal hypothesis for software injections,
-software injections with a very low SNR might not look coherent amongst an ensemble of
-detectors. Hence, software injections are likely to have two probability distributions
-of BCRs, one probability distribution of low BCRs corresponding to the software
-injections that have very low SNRs and another probability distribution of software
-injections with high BCRs. Due to this, we use Gaussian mixture models with two Gaussian
-components to fit our BCR distributions.
-
-\hypertarget{tuning-of-bcr-using-kl-distance}{%
-\subsubsection{Tuning of BCR using KL Distance}\label{tuning-of-bcr-using-kl-distance}}
-
-The BCR has two tunable parameters as described in Section\textasciitilde\ref{bcrCalculation},
-\(\alpha\) and \(\beta\). Altering \(\alpha\) translates the BCR probability distributions for
-the triggers while adjusting \(\beta\) spreads the probability distributions out. Although
-Bayesian hyper-parameter estimation might be able to determine the optimal values for
-these parameters, an easier approach is to manually adjust the parameters for each data
-chunk's BCR distribution. In this study, we manually adjust \(\alpha\) and \(\beta\) to
-maximally separate the BCR distributions for the software injections and background
-triggers.
-
-To calculate the separation between the background and software injection BCR
-distributions, we use the Kullback--Leibler divergence (also called relative entropy, or
-KL divergence) to quantify how different how the background and software injection BCR
-probability distributions are. If the distributions are identical, the KL divergence is
-equal to 0, and the KL divergence increases as the asymmetry between the distributions
-increases. Figure\textasciitilde\ref{fig:klDivGrid} displays a contour plot of O2 Chunk 14's KL
-divergences between the background and software injection triggers for values of
-\(\alpha\) and \(\beta\) ranging from \(1^{-10}\) to \(1\). We select these ranges for \(\alpha\)
-and \(\beta\) as values outside this range will not make physical sense. Note that for a
-fixed value of \(\beta\), the KL divergence stays the same as we alter \(\alpha\). This is
-because \(\alpha\) translates the BCR values, but does not alter the distributions
-themselves.
-
-\begin{figure}[!h]
-
-{\centering \includegraphics[width=0.75\linewidth]{images/kl_divergence_grid}
-
-}
-
-\caption[KL Divergence grid for both BCR tunable parameters]{KL Divergences for O2 Chunk 14's software injection and background trigger BCR probability distributions.
-The red line indicates the \(\alpha\) and \(\beta\) parameters with the maximum KL divergence in this range of \(\alpha\) and \(\beta\).}\label{fig:klDivGrid}
-\end{figure}
-
-Figure\textasciitilde\ref{fig:klDivLine} displays a plot of O2 Chunk 14's KL divergences only as
-\(\beta\) is adjusted for a fixed \(alpha=1^{-6}\). The \(\alpha\) and \(\beta\) are then selected
-based on the combination that results with the maximum KL divergence.
-
-\begin{figure}[!h]
-
-{\centering \includegraphics[width=0.75\linewidth]{images/kl_distance_14}
-
-}
-
-\caption[KL  Divergences for one BCR tunable parameter]{KL Divergences for O2 Chunk 14's software injection and background trigger BCR probability distributions with \(alpha=1^{-6}\).}\label{fig:klDivLine}
-\end{figure}
-
-In Chapter\textasciitilde\ref{progress} we present some of the preliminary BCR search results we
-have obtained from the analysis of various O2 data chunks.
-
-In aLIGO's first two observing runs, eleven gravitational wave events were found in the data by the LIGO-Virgo
-scientific collaboration \citep{abbott2019gwtc}. Since the public release of LIGO's first and second observing run's data,
-several groups have searched the data for gravitational waves independently of LIGO. One particular research group of
-interest is a research team at the Institute for Advanced Study (IAS). The group constructed searches to look for the
-LIGO-confirmed the gravitational wave events detected by the LIGO-Virgo collaboration, and in the process of doing so,
-claim to have discovered several others events \citep{IAS0, IAS1, IAS2}.
-Some of these events have total masses \(>85 M_{\odot}\), which is larger than the average total mass of the LIGO detections.
-Some of these IAS and LIGO events are
-displayed in Table\textasciitilde\ref{tab:O2significancesWObcr} with their p-astro reported by various LIGO and IAS search pipelines.
-
-\begin{table}[t]
-
-\caption[p-astro for various O2 foreground triggers]{\label{tab:O2significancesWObcr}p-astro from several detection pipelines for a subset of the O2 foreground triggers.}
-\centering
-\begin{tabular}{llrrrr}
-\toprule
-Event & Catalogue & PyCBC & GstLAL & cWB & IAS\\
-\midrule
-GW170104 & GWTC-1 & 1.00 & 1.00 & 1.00 & 0.99\\
-GW170121 & IAS-1 & NA & NA & NA & 0.99\\
-GWC170402 & IAS-2 & NA & 0.09 & NA & 0.68\\
-GW170403 & IAS-1 & NA & NA & NA & 0.56\\
-IMBHC170423 & IMBH-marginal & NA & 0.00 & 1.00 & NA\\
-GW170425 & IAS-1 & NA & NA & NA & 0.77\\
-GW170729 & GWTC-1 & 0.52 & 0.98 & 0.94 & NA\\
-\end{tabular}
-\end{table}
-
-From this Table\textasciitilde\ref{tab:O2significancesWObcr}, it is evident there is some uncertainty if these events can be considered real
-gravitational-wave events -- are these events significantly different from the background or not? The various pipelines
-have different answers. Our Bayesian search pipeline, as described in the next section, can help us answer this question
-and come to a conclusion about the significance of the events.
-
-\begin{figure}[!h]
-
-{\centering \includegraphics[width=0.75\linewidth]{images/O2_unfiltered_trigger_counts}
-
-}
-
-\caption[Count of all triggers in PyCBC O2 search]{Counts of triggers from \texttt{PyCBC}'s search through O2 Data (November 15, 2016 - August 26, 2017).
-Each chunk is roughly 8 days long.
-The background triggers are collected from timesliding each chunk's data to generate a dataset of roughly 3 million years.}\label{fig:o2TrigCount}
-\end{figure}
+For our study, we filter the background, simulated and candidate events to  include only high-mass events with masses in the ranges of the parameters presented in Table\textasciitilde\ref{tab:parameters}.
+A plot of the \pycbc triggers from one time-frame, during April 23 - May 8, 2017, is presented in Figure~\ref{fig:templateBank}.
+This figure also depicts the gravitational wave templates used during the search through this time-frame of data.
+\\
 
@@
 }
+% time for chunk 14
+% 1176955218, Apr 23, 2017, 4:00 UTC
+% 1178294418, May 08, 2017, 16:00 UTC
+\caption[High-mass BCR search space.]{The template bank used by \pycbc to search a section of O2 data from $\text{April 23 - May 8, 2017}$.
+Our search is constrained to the high-mass parameter space enclosed by the dashed line.}\label{fig:templateBank}
+\end{figure}
 
-\caption[High-mass BCR search space.]{The template bank used by \href{https://pycbc.org/}{\texttt{PyCBC}} to search in O2's chunk 14.
-Our search is constrained to the high-mass parameter space enclosed by the dashed line (triggers with duration \(<45s\).}\label{fig:templateBank}
+\subsection{Calculating the BCR for triggers}
+To evaluate $Z^S$, $Z^G_i$ and $Z^N_i$ as shown in Eqs.~\ref{eq:zn}-\ref{eq:zg} and calculate the \bcr Eq.~\ref{eq:bcr} for these triggers, we carry out Bayesian inference with \bilby \cite{bilby}, employing \dynesty \cite{dynesty} as our nested sampler.
+Nested sampling, an algorithm introduced by \cite{skilling_nested_sampling}, provides an estimate of the true Bayesian evidence and is often utilised for parameter estimation within the LIGO collaboration \cite{bilby}.\\
+
+The most computationally intensive step during Bayesian inference is the evaluation of the likelihood $\mathcal{L}(d_i|\mu(\vec{\theta}))$.
+To accelerate our analysis, we use a likelihood that explicitly marginalises over coalescence time, phase at coalescence, and luminosity distance (Eq.~80 from \citet{intro_to_gw_bayes}).
+While this marginalised likelihood reduces the run time without introducing errors to our evidence evaluation, it does not generates samples for the marginalised parameters.
+However, these parameter samples can be calculated as a post-processing step \cite{intro_to_gw_bayes}.\\
+
+We set the priors $\pi(\vec{\theta}|\mathcal{H}_S)$ and $\pi(\vec{\theta}|\mathcal{H}_G)$ to be identical.
+These priors restrict signals with mass parameters in the ranges presented in Table\textasciitilde\ref{tab:parameters}.
+The spins are aligned over a uniform range for the dimensionless spin magnitude from $\left[0,1\right]$.
+The luminosity distance prior assigns probability uniformly in comoving volume, with an upper cutoff of $5\ \text{Gpc}$.
+The remaining priors are the same as the those used for in GWTC-1.
+\\
+
+The waveform template we utilise is \imrphenomp, a phenomenological waveform template constructed in the frequency domain that models the in-spiral, merger, and ringdown (IMR) of a compact binary coalescence \citep{khan2016frequency}.
+Although gravitational wave templates such as \seob \cite{seob} created from numerical relativity simulations incorporate more physics such as information on higher-order modes, we still use \imrphenomp as it evaluates faster than numerical relativity models.
+\\
+
+To generate the PSD \psd, we take 31 neighbouring, off-source, non-overlapping,  $4\ s$  segments of time-series data prior to the data segment $d_i$ being analysed.
+A Tukey window with a roll off of $0.2\ \text{s}$ is applied to each data segment to suppress spectral leakage after which the segments are fast-Fourier transformed and median-averaged to create a \psd \cite{ligo_psd}.
+This method, like other \psd estimation methods, adds statistical uncertainties to the \psd \cite{psd_student_t}.
+To marginalise over the statistical uncertainty we use the median-likelihood presented by \citet{psd_student_t} as a post-processing step and shift our Bayesian Evidence estimations closer to their true astrophysical values.
+\\
+
+Finally, we neglect detector calibration uncertainty and acquire data from from the Gravitational Wave Open Science Center \cite{GWOSC}.
+The data we use is the publicly accessible O2 strain data from the Hanford and Livingston detectors.
+To ensure the data is usable we verify that the analysis and PSD data are obtained when the detectors are  in ``Science Mode''.
+The data requisition and quality checks are conducted using \gwpy \cite{gwpy}.
+\\
+
+The run-time to calculate a single Bayesian evidence after using \dynesty with $1,000$ live points and $100$ walkers is usually between $0.5-12\ \text{hours}$ (where the run time often depends on the SNR of the data segment).
+\\
+
+\subsection{Assigning $p_{astro}$ to candidate events}
+
+After the calculating the \bcr for the entire set of high-mass background and simulated triggers, we calculate probability distributions $p_b(\text{BCR})$ and $p_s(\text{BCR})$ for each 2-week time-frame of O2 data.
+These distributions are used to obtain the ``tuned'' prior-odd $\alpha$ and $\beta$ values that maximise $D_{KL}(p_b|p_s)$ for each time-frame of data.
+A plot of the different $D_{KL}(p_b|p_s)$ values obtained for different prior odds for the triggers found between the April 23 - May 8, 2017 time-frame can be seen in Figure~\ref{fig:Dkl}.
+\\
+
+\begin{figure}[!h]
+{\centering \includegraphics[width=0.75\linewidth]{images/kl_divergence_grid.png} }
+\caption[Grid of KL-Distances for different prior odds]{A grid of $D_{KL}(p_b|p_s)$ for different configurations of $\alpha$ and $\beta$, calculated from triggers obtained between $\text{April 23 - May 8, 2017}$.
+The red lines mark $\alpha$ and $\beta$ for the maximum $D_{KL}(p_b|p_s)$.}\label{fig:fig:Dkl}
+\end{figure}
+
+Finally, using the tuned prior odds the \bcr for the candidate events can be calculated.
+Figure~\ref{fig:bcrCdf} shows the \bcr distributions for the background triggers, simulated triggers and candidate events.
+The bulk of the background and simulated trigger distributions are separate but have a slight overlap due to some of the simulated signal's being very faint \av{but the BCR should still be able to find the injections and set them to have high BCRs?
+Could it be that the signals are injected over sketchy-glitch like data?
+How can I verify this?}.
+This suggests that the \bcr can successfully distinguish signals from noise or glitches.
+The vertical lines in Figure~\ref{fig:bcrCdf} displays the \bcr for gravitational wave candidate events.
+On comparing the candidate event \bcr values with the background distribution, we can estimate $p_text{astro}$ values for the candidate events.
+
+\begin{figure}[!h]
+{\centering \includegraphics[width=0.75\linewidth]{images/bcr_cdf} }
+\caption[BCR distribution example]{Histograms represent the survival function (1-CDF) from our selection of $\sim$ 3,000 background triggers (grey) and 648 simulated signals (blue) triggers obtained from \pycbc's search of data from $\text{April 23 - May 8, 2017}$.
+Vertical lines mark the ln BCRs of two glitches (orange and yellow), IAS's GW170121 (pink), and GWTC-1's GW170104 (dark blue).}\label{fig:bcrCdf}
 \end{figure}
@@
 \section{\label{sec:Results}Results}
-blah
+
+In aLIGO's first two observing runs, eleven gravitational wave events were found in the data by the LIGO-Virgo scientific collaboration \citep{abbott2019gwtc}.
+Since the public release of LIGO's first and second observing run's data, several groups have searched the data for gravitational waves independently of LIGO.
+One particular research group of interest is a research team at the Institute for Advanced Study (IAS).
+The group constructed searches to look for the LIGO-confirmed the gravitational wave events detected by the LIGO-Virgo collaboration, and in the process of doing so, claim to have discovered several others events \citep{IAS0, IAS1, IAS2}.
+Some of these events have total masses \(>85 M_{\odot}\), which is larger than the average total mass of the LIGO detections.
+Some of these IAS and LIGO events are displayed in Table\textasciitilde\ref{tab:O2significancesWObcr} with their p-astro reported by various LIGO and IAS search pipelines.\\
+
+\begin{table}[t]
+\caption[p-astro for various O2 foreground triggers]{\label{tab:O2significancesWObcr}p-astro from several detection pipelines for a subset of the O2 foreground triggers.}
+\centering
+\begin{tabular}{llrrrr}
+\toprule
+Event & Catalogue & PyCBC & GstLAL & cWB & IAS\\
+\midrule
+GW170104 & GWTC-1 & 1.00 & 1.00 & 1.00 & 0.99\\
+GW170121 & IAS-1 & NA & NA & NA & 0.99\\
+GWC170402 & IAS-2 & NA & 0.09 & NA & 0.68\\
+GW170403 & IAS-1 & NA & NA & NA & 0.56\\
+IMBHC170423 & IMBH-marginal & NA & 0.00 & 1.00 & NA\\
+GW170425 & IAS-1 & NA & NA & NA & 0.77\\
+GW170729 & GWTC-1 & 0.52 & 0.98 & 0.94 & NA\\
+\end{tabular}
+\end{table}
+
+From this Table\textasciitilde\ref{tab:O2significancesWObcr}, it is evident there is some uncertainty if these events can be considered real gravitational-wave events -- are these events significantly different from the background or not?
+The various pipelines have different answers.
+Our \bcr $p_{astro}$ shows support that the LIGO-VIRGO events come from an astrophysical source, while the candidate events from the IAS group appear to have a lower probability of originating from an astrophysical source.\\
 
 \section{\label{sec:Conclusion}Conclusion}
-The detection of high mass black holes (\(>100\) M\({}_\odot\)) will shed light on the formation of globular clusters,
-supermassive black holes and thus galaxy formation \citep{lodato2006supermassive, 2018IMBHreview}. LIGO is theoretically
-sensitive to the merger of binary black holes with total masses up to 500 M\({}_\odot\) which are expected to occur at a
-rate of 0-10 yr\(^{-1}\) \citep[\citet{mandel2008rates}]{fregeau2006imbhbRatePrediction}. However, even after \citet{salemi2019search}'s
-targeted match-filter based search for gravitational waves from high-mass black holes the largest total mass detected so
-far is approximately 80 M\({}_\odot\) \citep{abbott2019gwtc}. A possible explanation for the absence of high mass events may be
-due to their misclassification as short-duration instrumental noise transients \citep{blipGlitches}. High-mass mergers have
-very few in-band wave cycles, and hence can easily be mistaken for short-duration instrumental transients.
+The detection of high mass black holes $>100$ \msun will shed light on the formation of globular clusters, supermassive black holes and thus galaxy formation \citep{lodato2006supermassive, 2018IMBHreview}.
+LIGO is theoretically
+sensitive to the merger of binary black holes with total masses up to 500 M \msun which are expected to occur at a rate of 0-10 yr\(^{-1}\) \cite{mandel2008rates, fregeau2006imbhbRatePrediction}.
+However, even after \citet{salemi2019search}'s targeted match-filter based search for gravitational waves from high-mass black holes the largest total mass detected so far is approximately 80 \msun \citep{abbott2019gwtc}.
+A possible explanation for the absence of high mass events may be due to their misclassification as short-duration instrumental noise transients \citep{blipGlitches}.
+High-mass mergers have very few in-band wave cycles, and hence can easily be mistaken for short-duration instrumental transients.
+\\
 
-We start by developing a targeted search for gravitational waves from high-mass black hole systems. This new targeted
-search utilises Bayesian inference and thus is a more sensitive tool for detecting high-mass binary black hole mergers
-as compared to traditional match-filtering searches. We have applied this technique on the high-mass triggers during
-LIGO's second observing run to investigate the possibility of discovering new gravitational-wave signals from an
-entirely new class of high mass black hole binaries.
+We start by developing a targeted search for gravitational waves from high-mass black hole systems.
+This new targeted search utilises Bayesian inference and thus is a more sensitive tool for detecting high-mass binary black hole mergers as compared to traditional match-filtering searches.
+We have applied this technique on the high-mass triggers during LIGO's second observing run to investigate the possibility of discovering new gravitational-wave signals from an entirely new class of high mass black hole binaries.
 %%%%%%---SECTIONS-END---%%%%%%%%%%%%
@@
 \begin{acknowledgments}
-Helpful comments, OzGrav, LIGO, NSF.
 

### 2020-09-03 main.tex
complete 1st draft

@@
 We present details on the implementation of our analysis in Section~\ref{sec:Analysis}.
-Finally we present our results in Section~\ref{sec:result}, and discuss these results in the context of the significance of gravitational wave candidates in Section~\ref{sec:Conclusion}.
+Finally we present our results in Section~\ref{sec:Results}, and discuss these results in the context of the significance of gravitational wave candidates in Section~\ref{sec:Conclusion}.
 
@@
 \caption[Grid of KL-Distances for different prior odds]{A grid of $D_{KL}(p_b|p_s)$ for different configurations of $\alpha$ and $\beta$, calculated from triggers obtained between $\text{April 23 - May 8, 2017}$.
-The red lines mark $\alpha$ and $\beta$ for the maximum $D_{KL}(p_b|p_s)$.}\label{fig:fig:Dkl}
+The red lines mark $\alpha$ and $\beta$ for the maximum $D_{KL}(p_b|p_s)$.}\label{fig:Dkl}
 \end{figure}
@@
 The vertical lines in Figure~\ref{fig:bcrCdf} displays the \bcr for gravitational wave candidate events.
-On comparing the candidate event \bcr values with the background distribution, we can estimate $p_text{astro}$ values for the candidate events.
+On comparing the candidate event \bcr values with the background distribution, we can estimate $p_\text{astro}$ values for the candidate events.
 
@@
 \section{\label{sec:Results}Results}
-
+\av{I should use Pratten et al's table + values here}
 In aLIGO's first two observing runs, eleven gravitational wave events were found in the data by the LIGO-Virgo scientific collaboration \citep{abbott2019gwtc}.
@@
 The group constructed searches to look for the LIGO-confirmed the gravitational wave events detected by the LIGO-Virgo collaboration, and in the process of doing so, claim to have discovered several others events \citep{IAS0, IAS1, IAS2}.
-Some of these events have total masses \(>85 M_{\odot}\), which is larger than the average total mass of the LIGO detections.
-Some of these IAS and LIGO events are displayed in Table\textasciitilde\ref{tab:O2significancesWObcr} with their p-astro reported by various LIGO and IAS search pipelines.\\
+Some of these events have total masses $>85$ \msun, which is larger than the average total mass of the LIGO detections.
+Some of these IAS and LIGO events are displayed in Table\textasciitilde\ref{tab:O2significancesWObcr} with their $p_\text{astro}$ reported by various LIGO and IAS search pipelines.\\
 
-\begin{table}[t]
-\caption[p-astro for various O2 foreground triggers]{\label{tab:O2significancesWObcr}p-astro from several detection pipelines for a subset of the O2 foreground triggers.}
+\begin{table}
+\caption[$p_\text{astro}$ for various O2 foreground triggers]{\label{tab:O2significancesWObcr}$p_\text{astro}$ from several detection pipelines for a subset of the O2 foreground triggers.}
 \centering
-\begin{tabular}{llrrrr}
-\toprule
-Event & Catalogue & PyCBC & GstLAL & cWB & IAS\\
-\midrule
-GW170104 & GWTC-1 & 1.00 & 1.00 & 1.00 & 0.99\\
-GW170121 & IAS-1 & NA & NA & NA & 0.99\\
-GWC170402 & IAS-2 & NA & 0.09 & NA & 0.68\\
-GW170403 & IAS-1 & NA & NA & NA & 0.56\\
-IMBHC170423 & IMBH-marginal & NA & 0.00 & 1.00 & NA\\
-GW170425 & IAS-1 & NA & NA & NA & 0.77\\
-GW170729 & GWTC-1 & 0.52 & 0.98 & 0.94 & NA\\
+\begin{tabular}{lllllll} 
+\hline
+\textbf{Event} & \textbf{Catalogue} & \textbf{PyCBC} & \textbf{GstLAL} & \textbf{cWB} & \textbf{IAS} & \textbf{BCR} \\ 
+\hline
+GW170104 & GWTC-1 & 1 & 1 & 1 & 0.99 & 0.99 \\
+GW170121 & IAS-1 & NA & NA & NA & 0.99 & 0.65 \\
+GWC170402 & IAS-2 & NA & 0.086 & NA & 0.68 & 0.33 \\
+GW170403 & IAS-1 & NA & NA & NA & 0.56 & 0.33 \\
+IMBHC170423 & IMBH-marginal & NA & 0.95 & 1 & NA & 0.01 \\
+GW170425 & IAS-1 & NA & NA & NA & 0.77 & 0.36 \\
+GW170502 & Udall et al. & NA & NA & NA & NA & 0.40 \\
+GW170729 & GWTC-1 & 0.52 & 0.98 & 0.94 & NA & 0.98
 \end{tabular}
@@
 The various pipelines have different answers.
-Our \bcr $p_{astro}$ shows support that the LIGO-VIRGO events come from an astrophysical source, while the candidate events from the IAS group appear to have a lower probability of originating from an astrophysical source.\\
+Our \bcr $p_\text{astro}$ shows support that the LIGO-VIRGO events come from an astrophysical source, while the candidate events from the IAS group appear to have a lower probability of originating from an astrophysical source.\\
 
 \section{\label{sec:Conclusion}Conclusion}
+
 The detection of high mass black holes $>100$ \msun will shed light on the formation of globular clusters, supermassive black holes and thus galaxy formation \citep{lodato2006supermassive, 2018IMBHreview}.
-LIGO is theoretically
-sensitive to the merger of binary black holes with total masses up to 500 M \msun which are expected to occur at a rate of 0-10 yr\(^{-1}\) \cite{mandel2008rates, fregeau2006imbhbRatePrediction}.
-However, even after \citet{salemi2019search}'s targeted match-filter based search for gravitational waves from high-mass black holes the largest total mass detected so far is approximately 80 \msun \citep{abbott2019gwtc}.
+LIGO is theoretically sensitive to the merger of binary black holes with total masses up to 500 M \msun which are expected to occur at a rate of 0-10 yr\(^{-1}\) \cite{mandel2008rates, fregeau2006imbhbRatePrediction}.
+However, even after \citet{ligo_imbh_search}'s targeted match-filter based search for gravitational waves from high-mass black holes the largest total mass detected so far is approximately 80 \msun \citep{abbott2019gwtc}.
 A possible explanation for the absence of high mass events may be due to their misclassification as short-duration instrumental noise transients \citep{blipGlitches}.
@@
 
-We start by developing a targeted search for gravitational waves from high-mass black hole systems.
-This new targeted search utilises Bayesian inference and thus is a more sensitive tool for detecting high-mass binary black hole mergers as compared to traditional match-filtering searches.
-We have applied this technique on the high-mass triggers during LIGO's second observing run to investigate the possibility of discovering new gravitational-wave signals from an entirely new class of high mass black hole binaries.
+We have developing a targeted search for gravitational waves from high-mass black hole systems.
+This targeted search utilises Bayesian inference and provides a ranking statistic that contains a lot of physical information about the high-mass systems.
+We have applied this technique on all the high-mass triggers identified by \pycbc during LIGO's second observing run to investigate the possibility of discovering new gravitational-wave signals from high mass black hole binaries.
+Although we were unable to uncover new gravitational waves events, we were able to report high $p_{astro}$ for events already detected by LIGO, and low $p_{astro}$ for some events identified by external pipelines.
 %%%%%%---SECTIONS-END---%%%%%%%%%%%%

### 2020-09-14 main.tex
Rory suggestions

@@
 We have applied this technique on the high-mass triggers during LIGO's second observing run to investigate the possibility of discovering new gravitational-wave signals from an entirely new class of high mass black hole binaries.
+\rs{add sentence describing if we see any new events; add a sentence on our analysis of IAS events}
 
@@
 In 2019, the Event Horizon Telescope provided the first visual evidence of the supermassive black hole M87  \cite{m87photo}.
-As of January 2020, LIGO, Virgo and IAS have confirmed more than a dozen binary black hole systems \cite{GWTC1, IAS0, IAS1, IAS2, pycbc_ogc_2}.
+As of January 2020, LIGO, Virgo and IAS \rs{we should think carefully about how to describe the IAS events here; I think our conclusion is that they're not real} have confirmed more than a dozen binary black hole systems \cite{GWTC1, IAS0, IAS1, IAS2, pycbc_ogc_2}.
 These various discoveries have firmly established the existence of stellar-mass black holes, supermassive black holes and binary black hole systems.
@@
 A true Bayesian odds calculated without using bootstrap techniques can provide events with a more accurate significance that is agnostic to a specific search strategy \cite{BCR2, bcr_gw151216,  bayesian_odds}.
-Additionally, a Bayesian odds can include information such as if the gravitational wave event's signal is coherent amongst the network of detectors, if the binary system that created the gravitational waves was precessing, and if the gravitational wave signal contains higher-order modes.
+Additionally, a Bayesian odds can include more information than is included in current matched filter searches such as if the gravitational wave event's signal is coherent amongst the network of detectors, if the binary system that created the gravitational waves was precessing, and if the gravitational wave signal contains higher-order modes.
 It is because Bayesian methods can incorporate all this physical information about a gravitational wave signal that the LIGO Scientific Collaboration uses these methods to determine the source parameters of gravitational wave events \cite{abbott2016ligo, abbott2019gwtc}.
@@
 We find that (a) our search does not identify any unreported stellar mass or intermediate mass black holes; (b) high-mass events reported in the GWTC-1, including GW170729 (an event with disputed $p_\text{astro}$ amongst various search pipelines) have high low significance; and that (c) high-mass events detected from some independent groups have low significance.
-\\
+\rs{explicitly state that they're the IAS events}\\
 
@@
 \section{Method\label{sec:method}}
-
+\rs{I think you need a synopsis of this section before going into the details; explain that one could in principle apply bayesian methods only, but we don't do that here.
+Instead, we take triggers from pycbc and use bayesian evidences as a ranking statistic etc...}
 \subsection{Triggers for Analysis}
@@
 At its core, the \pycbc \cite{pycbc_code} search performs a matched-filter search for binary merger signals by comparing the data against templates from a gravitational-wave template-bank \cite{pycbc_og6}.
-\pycbc calculates the matched-filter for several different coalescence times and uses numerous templates from the template bank for each section of data being analysed.
-The output of \pycbc's search is a signal-to-noise ratio $\rho$ like statistic, called the \pycbc ranking statistic $\rho_\text{PC}$.
+\sout{\pycbc calculates the matched-filter for several different coalescence times and uses numerous templates from the template bank for each section of data being analysed.} The output of \pycbc's search is a signal-to-noise ratio $\rho$ like statistic, called the \pycbc ranking statistic $\rho_\text{PC}$.
 This statistic is a function of the matched-filter $\rho$, signal-based veto values, intrinsic and extrinsic properties of the apparent signal and other information \cite{pycbc_og6}.
@@
 Finally, to quantify the statistical significance of candidate events, \pycbc artificially constructs a \textbf{background trigger} set to compare the candidate events against.
-These background triggers are signal-free events, constructed by applying relative offsets, or time-shifts, between the data of different detectors \cite{pycbc_og6}.
+These background triggers are signal-free events \rs{not quite: they contain signals, just not coherent ones}, constructed by applying relative offsets, or time-shifts, between the data of different detectors \cite{pycbc_og6}.
 Note that the time-shifts to generate the background triggers are greater than the gravitational-wave travel time between detectors to ensure that the background triggers are not of astrophysical origins.
@@
 \end{equation}
+\rs{see comments from last week on replacing L wiht Z etc...}
 where $\mathcal{L}(d|\mathcal{H})$ is the likelihood of the data given
-the hypothesis,  $\pi(\mathcal{H})$ is the prior probability of the hypothesis, and finally, $Z = \sum \mathcal{L}(d|\mathcal{H})  \pi(\mathcal{H})$ is the marginalised likelihood called the evidence.
+the hypothesis,  $\pi(\mathcal{H})$ is the prior probability of the hypothesis, and finally, $Z = \sum \mathcal{L}(d|\mathcal{H})  \pi(\mathcal{H})$ is the marginalised likelihood called the evidence \av{Rory suggested we use $Z(d|H)$ instead of $L(D|H)$}.
 To compare two hypotheses $\mathcal{H}_A$ and $\mathcal{H}_B$ with the Bayes theorem one can calculate an odds ratio
@@
 We assume that each detector's noise is Gaussian and stationary over the period being analysed \cite{ligo_psd}.
-In practice, we estimate the noise using a noise power spectral density (PSD)  \psd.
+In practice, we estimate the noise variance using the noise power spectral density (PSD)  \psd of the data.
+\rs{NOTE: $\sigma_i^2$ is the noise variance, not the PSD.
+If you compare the likelihood in, e.g., veitch and vecchio to yours you can see how to relate the variance to the PSD and vice versa}.
 Using the \psd, for each data segment $d_i$ in each of the $i$ detectors in a network of $D$ detectors, we can write
@@
 Altering $\alpha$ translates the \bcr probability distributions while adjusting $\beta$ spreads the distributions.
-Although Bayesian hyper-parameter estimation can determine the optimal values for these parameters, an easier approach is to manually adjust the parameters for each data chunk's \bcr distribution.
+Although Bayesian hyper-parameter estimation can determine the optimal values for these parameters, an easier approach is to manually adjust the parameters for each data chunk's \rs{have you introduced the idea of the pycbc chunk yet?}  \bcr distribution.
 In this study, we manually tune $\alpha$ and $\beta$ to maximally separate the \bcr distributions for the background and simulated triggers.
@@
 The waveform template we utilise is \imrphenomp, a phenomenological waveform template constructed in the frequency domain that models the in-spiral, merger, and ringdown (IMR) of a compact binary coalescence \citep{khan2016frequency}.
-Although gravitational wave templates such as \seob \cite{seob} created from numerical relativity simulations incorporate more physics such as information on higher-order modes, we still use \imrphenomp as it evaluates faster than numerical relativity models.
+Although gravitational wave templates such as \seob \cite{seob} created from numerical relativity simulations incorporate more physics such as information on higher-order modes, we still use \imrphenomp as it evaluates faster than numerical relativity models \rs{NOTE: SOEOB is not a NR waveform.
+It's just tuned to NR}.
 \\
 
-To generate the PSD \psd, we take 31 neighbouring, off-source, non-overlapping,  $4\ s$  segments of time-series data prior to the data segment $d_i$ being analysed.
+To generate the PSD \psd \rs{see comment about difference between the psd and the noise variance}, we take 31 neighbouring, off-source, non-overlapping,  $4\ s$  segments of time-series data prior to the data segment $d_i$ being analysed.
 A Tukey window with a roll off of $0.2\ \text{s}$ is applied to each data segment to suppress spectral leakage after which the segments are fast-Fourier transformed and median-averaged to create a \psd \cite{ligo_psd}.
@@
 After the calculating the \bcr for the entire set of high-mass background and simulated triggers, we calculate probability distributions $p_b(\text{BCR})$ and $p_s(\text{BCR})$ for each 2-week time-frame of O2 data.
-These distributions are used to obtain the ``tuned'' prior-odd $\alpha$ and $\beta$ values that maximise $D_{KL}(p_b|p_s)$ for each time-frame of data.
-A plot of the different $D_{KL}(p_b|p_s)$ values obtained for different prior odds for the triggers found between the April 23 - May 8, 2017 time-frame can be seen in Figure~\ref{fig:Dkl}.
-\\
-
-\begin{figure}[!h]
-{\centering \includegraphics[width=0.75\linewidth]{images/kl_divergence_grid.png} }
-\caption[Grid of KL-Distances for different prior odds]{A grid of $D_{KL}(p_b|p_s)$ for different configurations of $\alpha$ and $\beta$, calculated from triggers obtained between $\text{April 23 - May 8, 2017}$.
-The red lines mark $\alpha$ and $\beta$ for the maximum $D_{KL}(p_b|p_s)$.}\label{fig:Dkl}
-\end{figure}
+These distributions are used to obtain the ``tuned'' prior-odd $\alpha$ and $\beta$ values that maximise $D_{KL}(p_b|p_s)$ for each time-frame of data.\\
 
@@
 Could it be that the signals are injected over sketchy-glitch like data?
-How can I verify this?}.
+How can I verify this?} \rs{you expect that some genuine signals will be reported as a glitch or noise, e.g., an odds of 1/10 means that you expect that 1 time out of ten a signal is mis classified a noise, and vice versa.
+You can get a signal at any bayes factor}.
 This suggests that the \bcr can successfully distinguish signals from noise or glitches.
@@
 \begin{table}
-\caption[$p_\text{astro}$ for various O2 foreground triggers]{\label{tab:O2significancesWObcr}$p_\text{astro}$ from several detection pipelines for a subset of the O2 foreground triggers.}
+\caption[\rs{Put BCR first and put a box around it, indicating that this is the new results that people should focus on}$p_\text{astro}$ for various O2 foreground triggers]{\label{tab:O2significancesWObcr}$p_\text{astro}$ from several detection pipelines for a subset of the O2 foreground triggers.}
 \centering
@@
 
-From this Table\textasciitilde\ref{tab:O2significancesWObcr}, it is evident there is some uncertainty if these events can be considered real gravitational-wave events -- are these events significantly different from the background or not?
+From \sout{this} Table\textasciitilde\ref{tab:O2significancesWObcr}, it is evident there is some uncertainty if these events can be considered real gravitational-wave events -- are these events significantly different from the background or not?
 The various pipelines have different answers.
@@
 
-The detection of high mass black holes $>100$ \msun will shed light on the formation of globular clusters, supermassive black holes and thus galaxy formation \citep{lodato2006supermassive, 2018IMBHreview}.
+\rs{lead with something specific to your work; what did you find/learn?
+how can it be extended?
+what does it imply for high mass BBH?
+How do the reported BCRs on interesting events compare to other bayesian measures of significance/odds?
+etc...It might be useful to take a look at some of the pycbc search papers for how to summarize results from a search}The detection of high mass black holes $>100$ \msun will shed light on the formation of globular clusters, supermassive black holes and thus galaxy formation \citep{lodato2006supermassive, 2018IMBHreview}.
 LIGO is theoretically sensitive to the merger of binary black holes with total masses up to 500 M \msun which are expected to occur at a rate of 0-10 yr\(^{-1}\) \cite{mandel2008rates, fregeau2006imbhbRatePrediction}.

### 2020-09-14 commit_work.sh
Deploying to master from  @ 90da49b43a37cc37926d116eaea46b16dd4f1dee 🚀

@@ -1,2 +1,0 @@
-#!bin/bash
-git commit -am "autosave %date%-%time:~0,8%"

### 2020-09-14 commit_work.sh
Revert "Deploying to master from  @ 90da49b43a37cc37926d116eaea46b16dd4f1dee 🚀"
This reverts commit 2f14df0f3d8f735f58d2d3136f5ac11cbf306316.

@@ -1,0 +1,2 @@
+#!bin/bash
+git commit -am "autosave %date%-%time:~0,8%"

### 2021-01-05 main.tex
Updates from Overleaf
incorporating rory's suggestions

@@
 %frontmatterverbose, 
-preprint,
+% preprint,
 %preprintnumbers,
@@
 %floatfix,
+twocolumn
 ]{revtex4}
@@
 
-\newcommand{\prior}{{\sc prior}\xspace}
 \newcommand{\bilby}{{\sc \href{https://lscsoft.docs.ligo.org/bilby/}{\texttt{Bilby}}}\xspace}
@@
 \newcommand{\pycbc}{{\sc \href{https://pycbc.org/}{\texttt{PyCBC}}}\xspace}
-\newcommand{\bcr}{{\sc BCR}\xspace}
-\newcommand{\psd}{{\sc $\sigma^2_i$}\xspace}
-\newcommand{\pastro}{{\sc $p_\text{astro}$}\xspace}
-\newcommand{\msun}{{\sc M${}_\odot$}\xspace}
-\newcommand{\template}{{\sc $\mu(\vec{\theta})$}\xspace}
-\newcommand{\parameters}{{\sc $\vec{\theta}$}\xspace}
+% MATH COMMANDS 
+\newcommand{\mathcmd}[1]{{\sc \relax\ifmmode#1\else $#1$\fi}\xspace}
+\newcommand{\bcr}{\mathcmd{\rho_\text{B}}}
+\newcommand{\pycbcstat}{\mathcmd{\rho_\text{PC}}}
+\newcommand{\snr}{\mathcmd{\rho}}
+\newcommand{\psd}{\mathcmd{P(f)}}
+\newcommand{\msun}{\mathcmd{\text{M}_\odot}}
+\newcommand{\parameters}{\mathcmd{\vec{\theta}}}
+\newcommand{\prior}{\mathcmd{\pi(\parameters)}}
+\newcommand{\template}{\mathcmd{\mu(\parameters)}}
+
+\newcommand{\pastro}{\relax\ifmmode{p_\text{astro}}\else $p_\text{astro}$\fi\xspace}
+\newcommand{\pval}{\relax\ifmmode{\text{p-value}}\else $\text{p-value}$\fi\xspace}
 
@@
 
-\preprint{APS/123-QED}
+\preprint{\textcolor[rgb]{0.00,0.50,0.75}{{\input{.githash.txt}}}}
 
-\title{A Bayesian search to find \\high-mass black holes in LIGO data}% Force line breaks with \\
+\title{A Bayesian search to find \\high-mass black holes in LIGO data}
 
@@
 
-The detection of high mass black holes ( $>100$ \msun) will shed light on the formation of supermassive black holes and thus galaxy formation.
-Although LIGO is sensitive to the merger of binary black holes with total masses up to 500 \msun, the largest total mass detected so far is approximately $80$ \msun.
-A possible explanation for the absence of high mass events may be due to their misclassification as short-duration instrumental noise transients.
-Short-duration instrumental transients mimic the short-duration gravitational-wave signals from high-mass binary black hole mergers.
-Here we demonstrate that a new search method utilising Bayesian inference could be a more sensitive tool for detecting high-mass binary black hole mergers as compared to traditional match-filtering.
-We have applied this technique on the high-mass triggers during LIGO's second observing run to investigate the possibility of discovering new gravitational-wave signals from an entirely new class of high mass black hole binaries.
-\rs{add sentence describing if we see any new events; add a sentence on our analysis of IAS events}
+The detection of intermediate mass black holes ( $10^2-10^6$~\msun) will shed light on the formation of supermassive black holes and thus galaxy formation.
+Although LIGO is sensitive to the merger of binary black holes with total masses up to $500$~\msun, only 1 of their 50 detections have a total mass $>100$~\msun.
+A possible explanation for the absence of intermediate mass events may be due to their misclassification as short-duration instrumental noise transients.
+Short-duration instrumental transients mimic the short-duration gravitational-wave signals from intermediate mass binary black hole mergers.
+Here we demonstrate that a search method utilising Bayesian inference could be a more sensitive tool for detecting high-mass binary black hole mergers (systems with a total mass $>55$~\msun) as compared to traditional match-filtering.
+We have applied this technique on the high-mass triggers during LIGO's second observing run to investigate the possibility of discovering new gravitational-wave signals from high mass black hole binaries, and to re-calculate the significance of high-mass candidate events.
+Although our search does not discover new candidate events, it does alter the significance of candidates identified by various search pipelines.
 
@@
 
-%\tableofcontents
-
 %%%%%%---SECTIONS---%%%%%%%%%%%%
 \section{\label{sec:Introduction}Introduction}
-\av{Need to edit in light of S190521G paper}
 Since the 1970s, there has been an accumulation of evidence for stellar-mass and supermassive black holes.
-In 2019, the Event Horizon Telescope provided the first visual evidence of the supermassive black hole M87  \cite{m87photo}.
-As of January 2020, LIGO, Virgo and IAS \rs{we should think carefully about how to describe the IAS events here; I think our conclusion is that they're not real} have confirmed more than a dozen binary black hole systems \cite{GWTC1, IAS0, IAS1, IAS2, pycbc_ogc_2}.
+In April 2019, the Event Horizon Telescope provided the first visual evidence of the supermassive black hole M87 \cite{m87photo}.
+As of November 2020, the LIGO Scientific Collaboration has confirmed $\sim50$ binary black hole systems and listed numerous candidate events \cite{GWTC1, GWTC2, IAS0, IAS1, IAS2, pycbc_ogc_2}.
 These various discoveries have firmly established the existence of stellar-mass black holes, supermassive black holes and binary black hole systems.
-Interestingly, there is still no direct evidence for intermediate-mass black holes, the black holes that lie in between stellar-mass and supermassive black hole systems with masses between $10^2-10^6$ \msun.
-Thus, the existence of intermediate-mass black holes is still speculative.
-\\
+Until recently, there was no definitive evidence for intermediate-mass black holes, the black holes that lie in between stellar-mass and supermassive black hole systems with masses between $10^2-10^6\ \msun$.
+This changed with the detection of GW190521, a unique gravitational wave event that lead to the formation of a black hole with a mass  $142\ \msun$, the first direct discovery of an intermediate mass black hole.
+Although this is the first gravitational wave that has l;ead to the discovery of a black hole with a mass of $>100\ \msun$, ground based gravitational wave detectors are sensitive to gravitational waves from even more massive systems, up to a systems with a total mass of $400\ \msun$.
+Gravitation waves from systems with masses $>100\ \msun$ systems should occur at a rate of $0-10\text{yr}^{-1}$ \cite{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions,ligo_imbh_search}.
 
-If intermediate-mass black holes are present, the gravitational waves emitted from the merger of a binary black hole system with at least one intermediate-mass black hole (up to a mass of $400$ \msun) will be detectable by the ground-based gravitational-wave network.
-Gravitational waves from such systems should occur at a rate of $0-10\text{yr}^{-1}$ \cite{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions}.
-However, even after conducting a targeted matched-filter based search for gravitational waves from intermediate-mass black holes the largest total mass detected so far is approximately $80$ \msun \cite{imbhbSearch2014, ligo_imbh_search, abbott2019gwtc}.
+However, even after conducting a targeted matched-filter based search for gravitational waves from intermediate-mass black holes the largest total mass detected so far is approximately $80\ \msun$ \cite{imbhbSearch2014, ligo_imbh_search, abbott2019gwtc}.
 A possible explanation for the absence of intermediate-mass events may be due to their misclassification as short-duration instrumental noise transients known as glitches \cite{glitch_in_fifth_ligo_run, bayeswave, improving_dq_in_early_runs, ligo_glitch_gw150914, pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
 These glitches can mimic astrophysical signals and hence decrease the significance of true gravitational wave events.
-\\
 
@@
 This paper demonstrates that the power of Bayesian methods used in parameter estimation can also successfully be used to discriminate between coherent gravitational-wave signals, incoherent glitches, and Gaussian noise in the form of a Bayesian search.
-\\
 
-In this paper we utilise a Bayesian method, called the \bcr \cite{BCR1}, to search for the significant gravitational wave signals from high-mass (systems with total masses in the range of $55-500$ \msun) compact binary coalescences in the detector data recorded during aLIGO's second observing run (O2).
-We find that (a) our search does not identify any unreported stellar mass or intermediate mass black holes; (b) high-mass events reported in the GWTC-1, including GW170729 (an event with disputed $p_\text{astro}$ amongst various search pipelines) have high low significance; and that (c) high-mass events detected from some independent groups have low significance.
-\rs{explicitly state that they're the IAS events}\\
+In this paper we utilise a Bayesian method, called the Bayesian Coherence Ratio \bcr \cite{BCR1}, to search for the significant gravitational wave signals from high-mass (systems with total masses in the range of $55-500\ \msun$) compact binary coalescences in the detector data recorded during aLIGO's second observing run (O2).
+We find that (a) our search does not identify any unreported stellar mass or intermediate mass black holes; (b) high-mass events reported in the GWTC-1, including GW170729 (an event with disputed \pastro amongst various search pipelines) have high significance; \av{and that (c) high-mass events detected from the IAS groups have low significance.
+}
 
@@
 \section{Method\label{sec:method}}
-\rs{I think you need a synopsis of this section before going into the details; explain that one could in principle apply bayesian methods only, but we don't do that here.
-Instead, we take triggers from pycbc and use bayesian evidences as a ranking statistic etc...}
+The gravitational wave community uses Bayesian inference to perform parameter estimation and model selection.
+In this work, we utilise Bayesian inference to calculate the significance of high-mass candidate events in O2 by using the \bcr as a ranking statistic, taking a step forward to building a unified Bayesian framework to search for candidates and estimate their parameters.
+
+Although a dedicated Bayesian search for gravitational waves, as presented by ~\cite{BCR2}, does not require noise estimation using empirical methods, this Bayesian significance ranking technique utilises \textit{time-slides}.
+To perform time-slides, the data from independent observatories are time-shifted by amounts greater than the light-travel time between the two detectors.
+Each unique time-slide amount creates an artificial signal-free ``background'' data set.
+When gravitational-wave search pipelines scan these background data sets for gravitational wave events, they can find candidate triggers, even though the background data set should not contain coherent astrophysical signals.
+These candidate triggers in background data are labelled background triggers, while coherent triggers obtained in non-time-slid data are labelled candidate triggers.
+
+Calculating the \bcr ranking statistic for each background trigger builds a background \bcr distribution.
+With a background distribution,  it is possible to assign a statistical significance of how likely a candidate trigger, detected by the search pipelines over non-time slid data, is due to a gravitational wave signal.
+
+This section discusses (a) the method to retrieve triggers, and (b) the \bcr and how it is utilised as a ranking statistic to calculate the significance of candidate triggers.
+
 \subsection{Triggers for Analysis}
-The LIGO Scientific collaboration runs a number of search pipelines that target gravitational waves from compact binary mergers such as the GstLAL, MBTA, SPIIR and PyCBC searches \cite{abbott2019gwtc}.\\
 
-At its core, the \pycbc \cite{pycbc_code} search performs a matched-filter search for binary merger signals by comparing the data against templates from a gravitational-wave template-bank \cite{pycbc_og6}.
-\sout{\pycbc calculates the matched-filter for several different coalescence times and uses numerous templates from the template bank for each section of data being analysed.} The output of \pycbc's search is a signal-to-noise ratio $\rho$ like statistic, called the \pycbc ranking statistic $\rho_\text{PC}$.
-This statistic is a function of the matched-filter $\rho$, signal-based veto values, intrinsic and extrinsic properties of the apparent signal and other information \cite{pycbc_og6}.
-Whenever a local maximum of $\rho_\text{PC} > \rho_\text{T}$, where $\rho_\text{T}$ is some threshold value, the search pipeline produces a single-detector trigger associated with the detector and time where the data was obtained.\\
+The LIGO Scientific collaboration operates several search pipelines that scan for gravitational waves from compact binary mergers such as \texttt{GstLAL}, \texttt{MBTA}, \texttt{SPIIR} and \pycbc \cite{abbott2019gwtc}.
 
-For \pycbc to consider a trigger to be a \textbf{candidate trigger}, a trigger from astrophysical origins, the trigger must be observed between detectors with the same template and a time of arrival difference less than the gravitational-wave travel time between detectors \cite{pycbc_og6}.
+The output of \pycbc's search is a list of candidate trigger times and their corresponding \pycbc ranking statistic \pycbcstat.
+The \pycbcstat statistic is akin to the matched-filter signal-to-noise ratio \snr.
+However, unlike \snr, \pycbcstat includes some information on the candidate signal's intrinsic and extrinsic properties and other information that feeds into determining if the signal can have astrophysical origins \cite{pycbc_og6}.
+The additional physical information incorporated in \pycbcstat makes it a more accurate measure of significance than the standard \snr.
+
+Whenever a local maximum of $\pycbcstat > \snr_\text{T}$, where $\snr_\text{T}$ is some threshold value, the search pipeline produces a single-detector trigger associated with the detector and time where the apparent signal in the data has its merger.
+
+For \pycbc to consider a trigger to be a \textbf{candidate trigger}, a trigger from astrophysical origins, the trigger must be observed between detectors with the same template and a time of arrival difference less than the gravitational-wave travel time \cite{pycbc_og6}.
 To test its search, \pycbc also conducts searches for \textbf{simulated triggers}, artificial triggers manufactured by injecting signals into the detector data.
-These simulated signal studies provides \pycbc with metrics on its search's sensitivity.
-Finally, to quantify the statistical significance of candidate events, \pycbc artificially constructs a \textbf{background trigger} set to compare the candidate events against.
-These background triggers are signal-free events \rs{not quite: they contain signals, just not coherent ones}, constructed by applying relative offsets, or time-shifts, between the data of different detectors \cite{pycbc_og6}.
-Note that the time-shifts to generate the background triggers are greater than the gravitational-wave travel time between detectors to ensure that the background triggers are not of astrophysical origins.
+These simulated signal studies provide \pycbc with metrics on its search's sensitivity.
+Finally, to quantify the statistical significance of candidate events, \pycbc artificially constructs a \textbf{background trigger} set to compare against the candidate events.
+These background triggers are coherent signal-free events, constructed by applying relative offsets, or time-slides, between the data of different detectors \cite{pycbc_og6}.
+Note that the time-slides to generate the background triggers are greater than the gravitational-wave travel time between detectors to ensure that the background triggers are not of astrophysical origins.
 \\
 
-In our work, we demonstrate that the \bcr can be used in a similar way as $\rho_\text{PC}$, as a ranking statistic, to measure the statistical significance of candidate triggers.
-Before we discuss how we use the \bcr as a measure of significance, we introduce the method to calculate the \bcr in the following section.\\
+Our work demonstrates that the \bcr can be used in the same way as \pycbcstat to measure candidate triggers' statistical significance.
+The \bcr can be a powerful ranking statistic as the \bcr incorporates information of not only all possible binary black hole systems that might have merged to produce the trigger but also the various incoherent glitches that might cause a false-detection.
+
+Before we discuss how we use the \bcr as a measure of significance, we introduce the method to calculate the \bcr in the following section.
 
@@
 
-Bayes theorem states that the probability $P(\mathcal{H}|d)$ for a hypothesis $\mathcal{H}$ and data $d$ is
+Bayes theorem states that the posterior probability distribution $p(\parameters|d,\mathcal{H})$ for data $d$ and a vector of parameters \parameters that describe a model which quantifies a hypothesis $\mathcal{H}$, is given by
 \begin{equation}
-    P(\mathcal{H}|d) = \frac{\mathcal{L}(d|\mathcal{H})\pi(\mathcal{H})}{Z}\ , 
+p(\parameters|d,\mathcal{H}) = \frac{\mathcal{L}(d|\parameters, \mathcal{H}) \ \pi(\parameters | \mathcal{H})}{\mathcal{Z}(d|\mathcal{H})}\ , 
 \end{equation}
-\rs{see comments from last week on replacing L wiht Z etc...}
-where $\mathcal{L}(d|\mathcal{H})$ is the likelihood of the data given
-the hypothesis,  $\pi(\mathcal{H})$ is the prior probability of the hypothesis, and finally, $Z = \sum \mathcal{L}(d|\mathcal{H})  \pi(\mathcal{H})$ is the marginalised likelihood called the evidence \av{Rory suggested we use $Z(d|H)$ instead of $L(D|H)$}.
+where $\mathcal{L}(d|\parameters, \mathcal{H})$ is the likelihood of the data given the parameters \parameters and the hypothesis, $\pi(\parameters | \mathcal{H})$ is the prior probability of the parameters, and finally,
+\begin{equation}
+    \mathcal{Z}(d|\mathcal{H}) = \int\limits_{\parameters} \ \mathcal{L}(d|\parameters,\mathcal{H}) \ \pi(\parameters | \mathcal{H}) \ d\parameters
+\end{equation} is the likelihood after marginalising over the parameters \parameters.
 To compare two hypotheses $\mathcal{H}_A$ and $\mathcal{H}_B$ with the Bayes theorem one can calculate an odds ratio
 \begin{equation}
-    \mathcal{O}^A_B = \frac{Z^A\ \pi(\mathcal{H}_A)}{Z^B\ \pi(\mathcal{H}_B)}\ ,
+    \mathcal{O}^A_B = \frac{\mathcal{Z}^A\ \pi(\parameters^A)}{\mathcal{Z}^B\ \pi(\parameters^B)}\ ,
 \end{equation}
-where $Z^A$ and $Z^B$ are the evidences for the $\mathcal{H}_A$ and $\mathcal{H}_B$ hypotheses.
+where $\mathcal{Z}^A$ and $\mathcal{Z}^B$ are the shorthand for the evidences  $\mathcal{Z}(d|\mathcal{H}_A)$ and $\mathcal{Z}(d|\mathcal{H}_B)$.
 The odds ratio can tell us which of the two hypotheses is more likely.
-For example, if $\mathcal{O}^A_B >> 1$, then this odds ratio indicates that the $\mathcal{H}_A$ is much more likely than $\mathcal{H}_B$.
-\\
+For example, if $\mathcal{O}^A_B >> 1$, then this odds ratio indicates that the $\mathcal{H}_A$ describes the data much better than $\mathcal{H}_B$.
 
@@
 \label{eq:bcr}
-\text{BCR} = \frac{\alpha Z^S}{\prod\limits^D_{i=1} \ [\beta Z^G_i + (1-\beta)Z^N_i]}\ ,
+\bcr = \frac{\alpha Z^S}{\prod\limits^D_{i=1} \ [\beta Z^G_i + (1-\beta)Z^N_i]}\ ,
 \end{equation}
@@
 As the rate of signal and glitches are unknown, these priors $\alpha$ and $\beta$ are tuned to maximise the \bcr distributions for background data (signal-free data) and simulated signals \cite{BCR1}.
-\\
 
@@
 We assume that each detector's noise is Gaussian and stationary over the period being analysed \cite{ligo_psd}.
-In practice, we estimate the noise variance using the noise power spectral density (PSD)  \psd of the data.
-\rs{NOTE: $\sigma_i^2$ is the noise variance, not the PSD.
-If you compare the likelihood in, e.g., veitch and vecchio to yours you can see how to relate the variance to the PSD and vice versa}.
+In practice, we assume that the noise has a mean of zero that the noise variance $\sigma^2$ is proportional to the noise power spectral density (PSD) \psd of the data.
 Using the \psd, for each data segment $d_i$ in each of the $i$ detectors in a network of $D$ detectors, we can write
@@
 \label{eq:zn}
-Z^N_i = \mathcal{N}(d_i) = \frac{1}{2\pi \sigma^2_i} \ \text{exp}\left(-\frac{1}{2} \frac{d_i}{\sigma^2_i} \right) \ ,
+Z^N_i = \mathcal{N}(d_i) = \frac{1}{2\pi \psd_i} \ \text{exp}\left(-\frac{1}{2} \frac{d_i}{\psd_i} \right) \ ,
 \end{equation}
-where $\mathcal{N}(d_i)$ is a normal distribution with a mean of zero and variance proportional to the \psd.
+where $\mathcal{N}(d_i)$ is a normal distribution with $\mu=0$ and $\sigma^2\sim \psd$.
 
@@
 \label{eq:zs}
-% Z^S = \int\limits_{\vec{\theta}} \prod\limits^{D}_{i=1} \left[\frac{1}{2\pi \sigma^2_i} \ \text{exp}\left(-\frac{1}{2} \frac{|d_i-\mu(\vec{\theta})|^2}{\sigma^2_i} \right) \right] \pi(\vec{\theta}| \mathcal{H}_S)\  \text{d}\vec{\theta} \ ,
-Z^S = \int\limits_{\vec{\theta}} \prod\limits^{D}_{i=1} \left[ \mathcal{L}(d_i|\mu(\vec{\theta}))\right] \pi(\vec{\theta}| \mathcal{H}_S)\  \text{d}\vec{\theta} \ ,
+Z^S = \int\limits_{\parameters} \prod\limits^{D}_{i=1} \left[ \mathcal{L}(d_i|\template)\right] \pi(\parameters | \mathcal{H}_S)\  \text{d}\parameters \ ,
 \end{equation}
-where $\pi(\theta| \mathcal{H}_S)$ is the prior for the parameters in the coherent signal hypothesis, and $\mathcal{L}(d_i|\mu(\vec{\theta}))$ is the likelihood for the coherent signal hypothesis that depends on the gravitational wave template \template and its parameters \parameters.
+where $\pi(\parameters| \mathcal{H}_S)$ is the prior for the parameters in the coherent signal hypothesis, and $\mathcal{L}(d_i|\template))$ is the likelihood for the coherent signal hypothesis that depends on the gravitational wave template \template and its parameters \parameters.
 
 \subsubsection{Incoherent Glitch Model}
-Finally, as glitches are challenging to model and poorly understood, we utilise a surrogate model for glitches: the glitches are modelled using gravitational wave templates  \template with uncorrelated  parameters amongst the different detectors such that  $\vec{\theta}_i \neq \vec{\theta}_j$ for two detectors $i$ and $j$ \cite{bci}.
+Finally, as glitches are challenging to model and poorly understood, we utilise a surrogate model for glitches: the glitches are modelled using gravitational wave templates  \template with uncorrelated  parameters amongst the different detectors such that  $\parameters_i \neq \parameters_j$ for two detectors $i$ and $j$ \cite{bci}.
 Modelling glitches with \template captures the worst case scenario: when glitches appear similar to gravitational wave signals.
@@
 \label{eq:zg}
-% Z^G_i = \int\limits_{\vec{\theta}} \frac{1}{2\pi \sigma^2_i} \ \text{exp}\left(-\frac{1}{2} \frac{|d_i-\mu(\vec{\theta})|^2}{\sigma^2_i} \right) \pi(\vec{\theta}| \mathcal{H}_G)\  \text{d}\vec{\theta}  \ ,
-Z^G_i = \int\limits_{\vec{\theta}} \mathcal{L}(d_i|\mu(\vec{\theta}))\ \pi(\vec{\theta}| \mathcal{H}_G)\  \text{d}\vec{\theta}  \ ,
+Z^G_i = \int\limits_{\parameters} \mathcal{L}(d_i|\template))\ \pi(\parameters| \mathcal{H}_G)\  \text{d}\parameters  \ ,
 \end{equation}
@@
 
-After calculating the \bcr for a set of background triggers and simulated triggers from as stretch of detector-data, we can compute probability distributions for the background and simulated triggers, $p_b(\text{BCR})$ and $p_s(\text{BCR})$.
+After calculating the \bcr for a set of background triggers and simulated triggers from as stretch of detector-data (a data chunk), we can compute probability distributions for the background and simulated triggers, $p_b(\bcr)$ and $p_s(\bcr)$.
 We expect the background trigger and simulated signal \bcr values to favour the incoherent glitch and the coherent signal hypothesis, respectively.
@@
 Altering $\alpha$ translates the \bcr probability distributions while adjusting $\beta$ spreads the distributions.
-Although Bayesian hyper-parameter estimation can determine the optimal values for these parameters, an easier approach is to manually adjust the parameters for each data chunk's \rs{have you introduced the idea of the pycbc chunk yet?}  \bcr distribution.
-In this study, we manually tune $\alpha$ and $\beta$ to maximally separate the \bcr distributions for the background and simulated triggers.
-\\
+Although Bayesian hyper-parameter estimation can determine the optimal values for $\alpha$ and $\beta$, an easier approach is to adjust the parameters for each data chunk's \bcr distribution.
+In this study, we tune $\alpha$ and $\beta$ to maximally separate the \bcr distributions for the background and simulated triggers.
 
-To calculate the separation between $p_b(\text{BCR})$ and $p_s(\text{BCR})$, we use the Kullback--Leibler divergence (KL divergence) $D_{KL}$, given by
+To calculate the separation between $p_b(\bcr)$ and $p_s(\bcr)$, we use the Kullback--Leibler divergence (KL divergence) $D_{KL}$, given by
 \begin{equation}
-    D_{KL}(p_b | p_s) = \sum\limits_{i=1}^N p_b(\text{BCR}_i) \cdot (\log p_b(\text{BCR}_i) - \log p_s(\text{BCR}_i)) \ .
+    D_{KL}(p_b | p_s) = \sum\limits_{i=1}^N p_b(\bcr^i) \cdot (\log p_b(\bcr^i) - \log p_s(\bcr^i) \ .
 \end{equation}
-The $D_{KL}=0$ when the distributions are identical and increases as the asymmetry between the distributions increases. \\
+The $D_{KL}=0$ when the distributions are identical and increases as the asymmetry between the distributions increases.
 
 We limit our search for the maximum KL-divergence in the $\alpha$ and $\beta$ ranges of $[E-10, E0]$ as values outside this range are nonphysical.
-We set our values for $\alpha$ and $\beta$ to those which provide the highest KL-divergence and can now calculate the \bcr for candidate events present in this stretch of detector-data.
-Note that we conduct the analysis in stretches of data rather than an entire data set as the background may be different at different points of the entire data set.
+We set our values for $\alpha$ and $\beta$ to those which provide the highest KL-divergence and calculate the \bcr for candidate events present in this data chunk.
+Note that we conduct the analysis in data chunks of a few days rather than an entire data set of a few months as the background may be different at different points of the entire data set.
 
@@
 As mentioned previously, irrespective of the \bcr's Bayesian interpretation, we treat the \bcr as a traditional detection statistic to obtain a frequentist estimate of the significance of candidate event measured against the background of signal-free data.
-\\
 
@@
 Candidate event \bcr values will either be statistically insignificant compared to the background triggers, implying the candidate is a glitch, or statistically significant to the background distribution, indicating the possible presence of an astrophysical signal.
-To quantify the level of significance we can calculate a $p\text{-value}$s for the candidate events.
-Here, the $p\text{-value}$ tells us how probable it is for the candidate event to be a glitch.
-Hence, we can use the $p\text{-value}$ to calculate
+To quantify the level of significance we can calculate a \pval for the candidate events.
+Here, the \pval tells us how probable it is for the candidate event to be a glitch.
+Hence, we can use the  \pval to calculate
 \begin{equation}
-    p_\text{astro} = 1 - p\text{-value} \ ,
+    \pastro = 1 -  \pval \ ,
 \end{equation}
@@
 Some candidate events were vetoed to be glitches, while others due to their low significance.
-The data is divided into these time-frames because the detector's sensitivity does not stay constant throughout 8 month long observing period.\\
+The data is divided into these time-frames because the detector's sensitivity does not stay constant throughout 8 month long observing period.
 
@@
 Finally, to test the search's sensitivity, \pycbc simulated and searched for thousands of artificial signals.
-\\
 
-For our study, we filter the background, simulated and candidate events to  include only high-mass events with masses in the ranges of the parameters presented in Table\textasciitilde\ref{tab:parameters}.
+For our study, we filter the background, simulated and candidate events to  include only high-mass events with masses in the ranges of the parameters presented in Table~\ref{tab:parameters}.
 A plot of the \pycbc triggers from one time-frame, during April 23 - May 8, 2017, is presented in Figure~\ref{fig:templateBank}.
 This figure also depicts the gravitational wave templates used during the search through this time-frame of data.
-\\
 
@@
 
-\caption[BBH parameters corresponding to durations $<454$ ms]{\label{tab:parameters}Template Banks's parameters for templates with duration $<454$ ms.}
+\caption[BBH parameters corresponding to duration $<454$ ms]{\label{tab:parameters}Template Banks's parameters for templates with duration $<454$ ms.}
 \centering
@@
 \midrule
-Component Mass 1 $[\text{M}_{\odot}]$ & 31.54 & 491.68\\
-Component Mass 2 $[\text{M}_{\odot}]$ & 1.32 & 121.01\\
-Total Mass $[\text{M}_{\odot}]$ & 56.93 & 496.72\\
-Chirp Mass $[\text{M}_{\odot}]$ & 8.00 & 174.56\\
+Component Mass 1 [\msun] & 31.54 & 491.68\\
+Component Mass 2 [\msun] & 1.32 & 121.01\\
+Total Mass [\msun] & 56.93 & 496.72\\
+Chirp Mass [\msun] & 8.00 & 174.56\\
 Mass Ratio & 0.01 & 0.98\\
@@
 To evaluate $Z^S$, $Z^G_i$ and $Z^N_i$ as shown in Eqs.~\ref{eq:zn}-\ref{eq:zg} and calculate the \bcr Eq.~\ref{eq:bcr} for these triggers, we carry out Bayesian inference with \bilby \cite{bilby}, employing \dynesty \cite{dynesty} as our nested sampler.
-Nested sampling, an algorithm introduced by \cite{skilling_nested_sampling}, provides an estimate of the true Bayesian evidence and is often utilised for parameter estimation within the LIGO collaboration \cite{bilby}.\\
+Nested sampling, an algorithm introduced by \cite{skilling_nested_sampling}, provides an estimate of the true Bayesian evidence and is often utilised for parameter estimation within the LIGO collaboration \cite{bilby}.
 
-The most computationally intensive step during Bayesian inference is the evaluation of the likelihood $\mathcal{L}(d_i|\mu(\vec{\theta}))$.
+The most computationally intensive step during Bayesian inference is the evaluation of the likelihood $\mathcal{L}(d_i|\template)$.
 To accelerate our analysis, we use a likelihood that explicitly marginalises over coalescence time, phase at coalescence, and luminosity distance (Eq.~80 from \citet{intro_to_gw_bayes}).
 While this marginalised likelihood reduces the run time without introducing errors to our evidence evaluation, it does not generates samples for the marginalised parameters.
-However, these parameter samples can be calculated as a post-processing step \cite{intro_to_gw_bayes}.\\
+However, these parameter samples can be calculated as a post-processing step \cite{intro_to_gw_bayes}.
 
-We set the priors $\pi(\vec{\theta}|\mathcal{H}_S)$ and $\pi(\vec{\theta}|\mathcal{H}_G)$ to be identical.
-These priors restrict signals with mass parameters in the ranges presented in Table\textasciitilde\ref{tab:parameters}.
+We set the priors $\pi(\parameters|\mathcal{H}_S)$ and $\pi(\parameters|\mathcal{H}_G)$ to be identical.
+These priors restrict signals with mass parameters in the ranges presented in Table~\ref{tab:parameters}.
 The spins are aligned over a uniform range for the dimensionless spin magnitude from $\left[0,1\right]$.
@@
 The remaining priors are the same as the those used for in GWTC-1.
-\\
 
 The waveform template we utilise is \imrphenomp, a phenomenological waveform template constructed in the frequency domain that models the in-spiral, merger, and ringdown (IMR) of a compact binary coalescence \citep{khan2016frequency}.
-Although gravitational wave templates such as \seob \cite{seob} created from numerical relativity simulations incorporate more physics such as information on higher-order modes, we still use \imrphenomp as it evaluates faster than numerical relativity models \rs{NOTE: SOEOB is not a NR waveform.
-It's just tuned to NR}.
-\\
+Although gravitational wave templates such as \seob \cite{seob} which incorporate more physics, such as information on higher-order modes, we still use \imrphenomp as it is inexpensive compared to waveforms fitted
+against numerical-relativity simulations.
 
-To generate the PSD \psd \rs{see comment about difference between the psd and the noise variance}, we take 31 neighbouring, off-source, non-overlapping,  $4\ s$  segments of time-series data prior to the data segment $d_i$ being analysed.
-A Tukey window with a roll off of $0.2\ \text{s}$ is applied to each data segment to suppress spectral leakage after which the segments are fast-Fourier transformed and median-averaged to create a \psd \cite{ligo_psd}.
-This method, like other \psd estimation methods, adds statistical uncertainties to the \psd \cite{psd_student_t}.
+To generate the PSD, we take 31 neighbouring, off-source, non-overlapping,  4-second  segments of time-series data prior to the data segment $d_i$ being analysed.
+A Tukey window with a roll off of 0.2-seconds is applied to each data segment to suppress spectral leakage after which the segments are fast-Fourier transformed and median-averaged to create a PSD \cite{ligo_psd}.
+This method, like other PSD estimation methods, adds statistical uncertainties to the PSD \cite{psd_student_t}.
 To marginalise over the statistical uncertainty we use the median-likelihood presented by \citet{psd_student_t} as a post-processing step and shift our Bayesian Evidence estimations closer to their true astrophysical values.
-\\
 
@@
 The data requisition and quality checks are conducted using \gwpy \cite{gwpy}.
-\\
 
 The run-time to calculate a single Bayesian evidence after using \dynesty with $1,000$ live points and $100$ walkers is usually between $0.5-12\ \text{hours}$ (where the run time often depends on the SNR of the data segment).
-\\
 
-\subsection{Assigning $p_{astro}$ to candidate events}
+\subsection{Assigning \pastro to candidate events}
 
-After the calculating the \bcr for the entire set of high-mass background and simulated triggers, we calculate probability distributions $p_b(\text{BCR})$ and $p_s(\text{BCR})$ for each 2-week time-frame of O2 data.
-These distributions are used to obtain the ``tuned'' prior-odd $\alpha$ and $\beta$ values that maximise $D_{KL}(p_b|p_s)$ for each time-frame of data.\\
+After the calculating the \bcr for the entire set of high-mass background and simulated triggers, we calculate probability distributions $p_b(\bcr)$ and $p_s(\bcr)$ for each 2-week time-frame of O2 data.
+These distributions are used to obtain the ``tuned'' prior-odd $\alpha$ and $\beta$ values that maximise $D_{KL}(p_b|p_s)$ for each time-frame of data.
 
@@
 Figure~\ref{fig:bcrCdf} shows the \bcr distributions for the background triggers, simulated triggers and candidate events.
-The bulk of the background and simulated trigger distributions are separate but have a slight overlap due to some of the simulated signal's being very faint \av{but the BCR should still be able to find the injections and set them to have high BCRs?
-Could it be that the signals are injected over sketchy-glitch like data?
-How can I verify this?} \rs{you expect that some genuine signals will be reported as a glitch or noise, e.g., an odds of 1/10 means that you expect that 1 time out of ten a signal is mis classified a noise, and vice versa.
-You can get a signal at any bayes factor}.
+The bulk of the background and simulated trigger distributions are separate but have a slight overlap due to some of the simulated signal's being very faint.
 This suggests that the \bcr can successfully distinguish signals from noise or glitches.
 The vertical lines in Figure~\ref{fig:bcrCdf} displays the \bcr for gravitational wave candidate events.
-On comparing the candidate event \bcr values with the background distribution, we can estimate $p_\text{astro}$ values for the candidate events.
+On comparing the candidate event \bcr values with the background distribution, we can estimate \pastro values for the candidate events.
 
@@
 The group constructed searches to look for the LIGO-confirmed the gravitational wave events detected by the LIGO-Virgo collaboration, and in the process of doing so, claim to have discovered several others events \citep{IAS0, IAS1, IAS2}.
-Some of these events have total masses $>85$ \msun, which is larger than the average total mass of the LIGO detections.
-Some of these IAS and LIGO events are displayed in Table\textasciitilde\ref{tab:O2significancesWObcr} with their $p_\text{astro}$ reported by various LIGO and IAS search pipelines.\\
+Some of these events have total masses $>85\ \msun$, which is larger than the average total mass of the LIGO detections.
+Some of these IAS and LIGO events are displayed in Table~\ref{tab:O2significancesWObcr} with their \pastro reported by various LIGO and IAS search pipelines.
 
-\begin{table}
-\caption[\rs{Put BCR first and put a box around it, indicating that this is the new results that people should focus on}$p_\text{astro}$ for various O2 foreground triggers]{\label{tab:O2significancesWObcr}$p_\text{astro}$ from several detection pipelines for a subset of the O2 foreground triggers.}
+\begin{table*}
+\caption[\rs{Put BCR first and put a box around it, indicating that this is the new results that people should focus on}\pastro for various O2 foreground triggers]{\label{tab:O2significancesWObcr}\pastro from several detection pipelines for a subset of the O2 foreground triggers.}
+
 \centering
@@
 \end{tabular}
-\end{table}
+\end{table*}
 
-From \sout{this} Table\textasciitilde\ref{tab:O2significancesWObcr}, it is evident there is some uncertainty if these events can be considered real gravitational-wave events -- are these events significantly different from the background or not?
+From Table~\ref{tab:O2significancesWObcr}, it is evident there is some uncertainty if these events can be considered real gravitational-wave events -- are these events significantly different from the background or not?
 The various pipelines have different answers.
-Our \bcr $p_\text{astro}$ shows support that the LIGO-VIRGO events come from an astrophysical source, while the candidate events from the IAS group appear to have a lower probability of originating from an astrophysical source.\\
+Our \bcr \pastro shows support that the LIGO-VIRGO events come from an astrophysical source, while the candidate events from the IAS group appear to have a lower probability of originating from an astrophysical source.
 
 \section{\label{sec:Conclusion}Conclusion}
+
+\av{Although a true Bayesian search for gravitational waves, as presented by ~\cite{BCR2}, does not require noise estimation using empirical methods, this Bayesian framework utilises 'time-slides'}
 
@@
 etc...It might be useful to take a look at some of the pycbc search papers for how to summarize results from a search}The detection of high mass black holes $>100$ \msun will shed light on the formation of globular clusters, supermassive black holes and thus galaxy formation \citep{lodato2006supermassive, 2018IMBHreview}.
-LIGO is theoretically sensitive to the merger of binary black holes with total masses up to 500 M \msun which are expected to occur at a rate of 0-10 yr\(^{-1}\) \cite{mandel2008rates, fregeau2006imbhbRatePrediction}.
+LIGO is theoretically sensitive to the merger of binary black holes with total masses up to $500\ \msun$ which are expected to occur at a rate of 0-10 yr\(^{-1}\) \cite{mandel2008rates, fregeau2006imbhbRatePrediction}.
 However, even after \citet{ligo_imbh_search}'s targeted match-filter based search for gravitational waves from high-mass black holes the largest total mass detected so far is approximately 80 \msun \citep{abbott2019gwtc}.
@@
 High-mass mergers have very few in-band wave cycles, and hence can easily be mistaken for short-duration instrumental transients.
-\\
 

### 2021-01-18 authors.tex
Updates from Overleaf

%------ affiliation shortcuts
\newcommand{\SPAno}{1}
\newcommand{\OzGravMonashno}{2}
\newcommand{\CITno}{3}
\newcommand{\MITno}{4}
\newcommand{\Kavlino}{5}

%--------------------------
\newcommand{\SPA}{School of Physics and Astronomy, Monash University, Clayton VIC 3800, Australia}
\newcommand{\OzGravMonash}{OzGrav: The ARC Centre of Excellence for Gravitational Wave Discovery, Clayton VIC 3800, Australia}
\newcommand{\MIT}{LIGO Laboratory, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
\newcommand{\Kavli}{Department of Physics and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, \\ 77 Massachusetts Ave, Cambridge, MA 02139, USA}
\newcommand{\CIT}{LIGO Laboratory, California Institute of Technology, Pasadena, CA 91125, USA}
\author{
\parbox{\textwidth}{
A.~Vajpeyi$^{\SPAno,\OzGravMonashno}$, %ORCID:0000-0002-4146-1132
R.~Smith$^{\SPAno,\OzGravMonashno}$, %ORCID:0000-0001-8516-3324
E.~Thrane$^{\SPAno,\OzGravMonashno}$, %0000-0002-4418-3895
G.~Ashton$^{\SPAno,\OzGravMonashno}$, %ORCID:0000-0001-7288-2231 
J.~Kanner$^\CITno$, 
T.~Alford$^\CITno$, 
L.~Xiao$^\CITno$, %0000-0003-2703-449X
M.~Isi$^{\MITno,\Kavlino}$, %0000-0001-8040-9807
S.~Garza$^\CITno$, 
}\vspace{0.2cm}\\
$^1$\SPA\\
$^2$\OzGravMonash\\
$^3$\CIT\\
$^4$\MIT\\
$^5$\Kavli\\
}

### 2021-01-18 main.tex
Updates from Overleaf

@@
 %preprintnumbers,
-%nofootinbib,
+ nofootinbib,
 %nobibnotes,
@@
  twocolumn
-]{revtex4}
+]{revtex4-2}
 
@@
 \usepackage{array}
-\usepackage{graphicx}
 \usepackage{color,units}
 \usepackage[dvipsnames]{xcolor} % for more colours!
-
 \usepackage{lineno}
-\usepackage{xspace}
 \usepackage{dcolumn}
@@
 \usepackage[T1]{fontenc}
-\usepackage{hyperref}
-
-\usepackage{dcolumn}% Align table columns on decimal point
+\usepackage[breaklinks]{hyperref}
 \usepackage{booktabs}
@@
 \usepackage{bm}% bold math
-\usepackage{hyperref}% add hypertext capabilities
 \usepackage{graphicx} % Include figure files
-\graphicspath{{Figures/}} %Setting the graphicspath
+\graphicspath{{images/}} %Setting the graphicspath
 
-                 % Astronomical Journal
-
+% Keywords
 \newcommand{\bilby}{{\sc \href{https://lscsoft.docs.ligo.org/bilby/}{\texttt{Bilby}}}\xspace}
@@
 \newcommand{\seob}{{\sc SEOBNRv4PHM}\xspace}
+\newcommand{\gstlal}{{\sc GstLAL}\xspace}
 \newcommand{\pycbc}{{\sc \href{https://pycbc.org/}{\texttt{PyCBC}}}\xspace}
-% MATH COMMANDS 
+
+% math keywords 
+\newcommand{\fancytext}[1]{{\relax\ifmmode#1\else $#1$\fi}\xspace}
 \newcommand{\mathcmd}[1]{{\sc \relax\ifmmode#1\else $#1$\fi}\xspace}
-\newcommand{\bcr}{\mathcmd{\rho_\text{B}}}
+\newcommand{\bcr}{\mathcmd{\rho_\text{BCR}}}
 \newcommand{\pycbcstat}{\mathcmd{\rho_\text{PC}}}
@@
 \newcommand{\template}{\mathcmd{\mu(\parameters)}}
+\newcommand{\fap}{\mathcmd{\text{FAP}}}
 
-\newcommand{\pastro}{\relax\ifmmode{p_\text{astro}}\else $p_\text{astro}$\fi\xspace}
-\newcommand{\pval}{\relax\ifmmode{\text{p-value}}\else $\text{p-value}$\fi\xspace}
+\newcommand{\pastro}{\fancytext{p_\text{astro}}}
+\newcommand{\pastrobcr}{\fancytext{p_\text{astro}^{\text{BCR}}}}
+\newcommand{\pastroext}{\fancytext{p_\text{astro}^{\text{ext}}}}
+\newcommand{\pval}{\fancytext{\text{p-value}}}
+% Table settings
+\renewcommand{\aboverulesep}{0pt}
+\renewcommand{\belowrulesep}{0pt}
+% \setlength\cellspacetoplimit{2pt}
+% \setlength\cellspacebottomlimit{2pt}
 
+\newcolumntype{C}{>{\centering\arraybackslash}X}
+\newcolumntype{L}{>{\arraybackslash}X}
+
+% Aesthetic colours
+\definecolor{dodgerblue}{HTML}{1E90FF}
+\definecolor{viennared}{HTML}{DA0A14}
+\definecolor{ctorange}{HTML}{FF6C0C}
+\definecolor{wales}{HTML}{ff0038}
+\definecolor{benettongreen}{HTML}{009421}
+\definecolor{valenciacfred}{HTML}{ee3524}
+\definecolor{barcelonafcgold}{HTML}{edbb00}
+\definecolor{jam}{HTML}{A50B5E}
+\definecolor{austriawien}{HTML}{441678}
+\definecolor{italia90green}{HTML}{009966}
+\definecolor{ferrarired}{HTML}{ff2800}
+\definecolor{gray}{HTML}{F0F0F0}
+\definecolor{LightCyan}{rgb}{0.88,1,1}
+\newcolumntype{a}{>{\columncolor{gray}}c}
+\newcolumntype{b}{>{\columncolor{white}}c}
+
+% author comments
 \newcommand{\av}[1]{\textcolor{orange}{[AV: #1]}}
@@
 
+% %%% AFFILIATIONS
+% %------ affiliation shortcuts
+% \newcommand{\SPAno}{1}
+% \newcommand{\OzGravMonashno}{2}
+% \newcommand{\CITno}{3}
+% \newcommand{\MITno}{4}
+% \newcommand{\Kavlino}{5}
+
+% %--------------------------
+% \newcommand{\SPA}{School of Physics and Astronomy, Monash University, Clayton VIC 3800, Australia}
+% \newcommand{\OzGravMonash}{OzGrav: The ARC Centre of Excellence for Gravitational Wave Discovery, Clayton VIC 3800, Australia}
+% \newcommand{\MIT}{LIGO Laboratory, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
+% \newcommand{\Kavli}{Department of Physics and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, \\ 77 Massachusetts Ave, Cambridge, MA 02139, USA}
+% \newcommand{\CIT}{LIGO Laboratory, California Institute of Technology, Pasadena, CA 91125, USA}
+% %%%
+
 \begin{document}
 
-\preprint{\textcolor[rgb]{0.00,0.50,0.75}{{\input{.githash.txt}}}}
+\title{A Bayesian ranking statistic to find \\high-mass black holes in LIGO data}
 
-\title{A Bayesian search to find \\high-mass black holes in LIGO data}
-
-\author{Author list TBD}
+% \author{Author list TBD}
+\input{authors}
 
@@
 \begin{abstract}
-
 The detection of intermediate mass black holes ( $10^2-10^6$~\msun) will shed light on the formation of supermassive black holes and thus galaxy formation.
@@
 Although our search does not discover new candidate events, it does alter the significance of candidates identified by various search pipelines.
-
 \end{abstract}
@@
 \section{\label{sec:Introduction}Introduction}
+
 Since the 1970s, there has been an accumulation of evidence for stellar-mass and supermassive black holes.
-In April 2019, the Event Horizon Telescope provided the first visual evidence of the supermassive black hole M87 \cite{m87photo}.
-As of November 2020, the LIGO Scientific Collaboration has confirmed $\sim50$ binary black hole systems and listed numerous candidate events \cite{GWTC1, GWTC2, IAS0, IAS1, IAS2, pycbc_ogc_2}.
+In April 2019, the Event Horizon Telescope provided the first visual evidence of the supermassive black hole M87~\cite{m87photo}.
+As of November 2020, the LIGO Scientific Collaboration has confirmed $\sim50$ binary black hole systems and listed numerous candidate events~\cite{GWTC1, GWTC2, gracedb}.
+Additionally, since the public release of LIGO's first and second observing run's data (O1 and O2), several external groups, such as \pycbc~\cite{pycbc_code} and a research team at the Institute for Advanced Study (IAS)~\cite{IAS0, IAS1, IAS2}, have independently searched and identified additional binary black hole gravitational wave candidates.
 These various discoveries have firmly established the existence of stellar-mass black holes, supermassive black holes and binary black hole systems.
+
 Until recently, there was no definitive evidence for intermediate-mass black holes, the black holes that lie in between stellar-mass and supermassive black hole systems with masses between $10^2-10^6\ \msun$.
-This changed with the detection of GW190521, a unique gravitational wave event that lead to the formation of a black hole with a mass  $142\ \msun$, the first direct discovery of an intermediate mass black hole.
-Although this is the first gravitational wave that has l;ead to the discovery of a black hole with a mass of $>100\ \msun$, ground based gravitational wave detectors are sensitive to gravitational waves from even more massive systems, up to a systems with a total mass of $400\ \msun$.
-Gravitation waves from systems with masses $>100\ \msun$ systems should occur at a rate of $0-10\text{yr}^{-1}$ \cite{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions,ligo_imbh_search}.
+This changed with the detection of GW190521, a unique gravitational wave event that lead to the formation of a black hole with a mass  $142\ \msun$, the first confirmed direct discovery of an intermediate mass black hole~\cite{gw190521}.
+Although this is the first gravitational wave that has lead to the discovery of a black hole with a mass in the intermediate range, ground based gravitational wave detectors are sensitive to gravitational waves from even more massive systems, up to a systems with a total mass of $400\ \msun$.
+\av{double check the following -- is this the most recent rate quote?} Additionally, gravitation waves from systems with masses greater than $100\ \msun$ systems should occur at a rate of $0-10\text{yr}^{-1}$~\cite{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions,ligo_imbh_search}.
+Hence, we should have detected gravitational waves from more intermediate-mass systems, and potentially one event from O2.
 
-However, even after conducting a targeted matched-filter based search for gravitational waves from intermediate-mass black holes the largest total mass detected so far is approximately $80\ \msun$ \cite{imbhbSearch2014, ligo_imbh_search, abbott2019gwtc}.
-A possible explanation for the absence of intermediate-mass events may be due to their misclassification as short-duration instrumental noise transients known as glitches \cite{glitch_in_fifth_ligo_run, bayeswave, improving_dq_in_early_runs, ligo_glitch_gw150914, pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
+However, even after conducting a targeted matched-filter based search for gravitational waves from intermediate-mass black holes in O2's data, the largest total mass detected so far is approximately $80\ \msun$~\cite{GWTC1,imbhbSearch2014, ligo_imbh_search}.
+A possible explanation for the absence of intermediate-mass events may be due to their misclassification as short-duration instrumental noise transients known as glitches~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
 These glitches can mimic astrophysical signals and hence decrease the significance of true gravitational wave events.
 
-One method to account for glitches while searching for gravitational waves from coalescing compact binaries is by utilising an astrophysical Bayesian odds  \cite{bci, BCR1, BCR2, bcr_gw151216, bayesian_odds}.
-A true Bayesian odds calculated without using bootstrap techniques can provide events with a more accurate significance that is agnostic to a specific search strategy \cite{BCR2, bcr_gw151216,  bayesian_odds}.
-Additionally, a Bayesian odds can include more information than is included in current matched filter searches such as if the gravitational wave event's signal is coherent amongst the network of detectors, if the binary system that created the gravitational waves was precessing, and if the gravitational wave signal contains higher-order modes.
-It is because Bayesian methods can incorporate all this physical information about a gravitational wave signal that the LIGO Scientific Collaboration uses these methods to determine the source parameters of gravitational wave events \cite{abbott2016ligo, abbott2019gwtc}.
-This paper demonstrates that the power of Bayesian methods used in parameter estimation can also successfully be used to discriminate between coherent gravitational-wave signals, incoherent glitches, and Gaussian noise in the form of a Bayesian search.
+One method to account for glitches while searching for gravitational waves from coalescing compact binaries is by utilising an astrophysical Bayesian odds~\cite{bci, BCR1, BCR2, bcr_gw151216, bayesian_odds}.
+A true Bayesian odds calculated without using bootstrap techniques can provide events with a more accurate significance that is agnostic to a specific search strategy~\cite{BCR2, bcr_gw151216,  bayesian_odds}.
 
-In this paper we utilise a Bayesian method, called the Bayesian Coherence Ratio \bcr \cite{BCR1}, to search for the significant gravitational wave signals from high-mass (systems with total masses in the range of $55-500\ \msun$) compact binary coalescences in the detector data recorded during aLIGO's second observing run (O2).
-We find that (a) our search does not identify any unreported stellar mass or intermediate mass black holes; (b) high-mass events reported in the GWTC-1, including GW170729 (an event with disputed \pastro amongst various search pipelines) have high significance; \av{and that (c) high-mass events detected from the IAS groups have low significance.
-}
+Additionally, Bayesian odds can include comprehensive astrophysical information in its calculation.
+For example, a Bayesian odds to help detect gravitational-wave candidates can incorporate information on if an event's binary system was precessing and if the signal contains higher-order modes and is coherent amongst various detectors.
+Because of the possibility of Bayesian methods to incorporate detailed physical information about a gravitational wave signal, the LIGO Scientific Collaboration uses Bayesian methods to determine the source parameters of gravitational wave events~\cite{abbott2016ligo, GWTC1}.
+This paper demonstrates that the power of Bayesian methods used in parameter estimation can also discriminate between coherent gravitational-wave signals, incoherent glitches, and Gaussian noise in the form of a Bayesian odds, utilised as a ranking statistic.
+
+In this paper we utilise a Bayesian method, called the Bayesian Coherence Ratio \bcr~\cite{BCR1}, to rank the candidate gravitational wave signals from high-mass compact binary coalescences (systems with total masses in the range of $55-500\ \msun$) in the detector data recorded during O2.
+Although the \bcr, utilising bootstrap techniques, does not provide the true Bayesian odds, it provides a more astrophysical measure of the significance of candidate events than a traditional match-filter significance.
+
+We find that (a) high-mass events reported in the GWTC-1, including GW170729 (an event with disputed \pastro amongst various search pipelines) have high significance; (b) high-mass events detected from the IAS group have differing levels of significance; and that (c) our ranking statistic does not identify any intermediate mass black holes, but does identify an unreported stellar mass binary black hole candidate, GWC170222.
 
@@
 
-Although a dedicated Bayesian search for gravitational waves, as presented by ~\cite{BCR2}, does not require noise estimation using empirical methods, this Bayesian significance ranking technique utilises \textit{time-slides}.
-To perform time-slides, the data from independent observatories are time-shifted by amounts greater than the light-travel time between the two detectors.
-Each unique time-slide amount creates an artificial signal-free ``background'' data set.
-When gravitational-wave search pipelines scan these background data sets for gravitational wave events, they can find candidate triggers, even though the background data set should not contain coherent astrophysical signals.
-These candidate triggers in background data are labelled background triggers, while coherent triggers obtained in non-time-slid data are labelled candidate triggers.
+Although a dedicated Bayesian search for gravitational waves, as presented by ~\citet{BCR2}, does not require noise estimation using empirical methods, this Bayesian significance ranking technique utilises \textit{time-slides}.
+To perform time-slides, data from independent observatories are time-shifted by amounts greater than the light-travel time between the two detectors.
+Each unique time-slide amount creates an artificial signal-free `background' data set.
+When search pipelines scan these background data sets for gravitational wave events, they can find \textit{triggers}\footnotemark, even though the background data set should not contain coherent astrophysical signals.
+These triggers in background data are labelled background triggers, while coherent triggers obtained in non-time-slid data are labelled candidate triggers.
+
+\footnotetext{\textit{Triggers} are points in time when the matched-filter SNR is greater than a threshold value for a given gravitational wave template~\cite{pycbc_og1}.}
 
@@
 
-The LIGO Scientific collaboration operates several search pipelines that scan for gravitational waves from compact binary mergers such as \texttt{GstLAL}, \texttt{MBTA}, \texttt{SPIIR} and \pycbc \cite{abbott2019gwtc}.
+The LIGO Scientific collaboration operates several search pipelines that scan for gravitational waves from compact binary mergers such as \texttt{GstLAL}, \texttt{MBTA}, \texttt{SPIIR} and \pycbc~\cite{GWTC1}.
 
@@
 The \pycbcstat statistic is akin to the matched-filter signal-to-noise ratio \snr.
-However, unlike \snr, \pycbcstat includes some information on the candidate signal's intrinsic and extrinsic properties and other information that feeds into determining if the signal can have astrophysical origins \cite{pycbc_og6}.
+However, unlike \snr, \pycbcstat includes some information on the candidate signal's intrinsic and extrinsic properties and other information that feeds into determining if the signal can have astrophysical origins~\cite{pycbc_og6}.
 The additional physical information incorporated in \pycbcstat makes it a more accurate measure of significance than the standard \snr.
 
-Whenever a local maximum of $\pycbcstat > \snr_\text{T}$, where $\snr_\text{T}$ is some threshold value, the search pipeline produces a single-detector trigger associated with the detector and time where the apparent signal in the data has its merger.
+Whenever a local maximum of $\pycbcstat > \snr_\text{T}$, where $\snr_\text{T}$ is some threshold value, the search pipeline produces a single-detector trigger associated with the detector and time where the apparent signal in the data has its merger~\cite{pycbc_og6}.
 
-For \pycbc to consider a trigger to be a \textbf{candidate trigger}, a trigger from astrophysical origins, the trigger must be observed between detectors with the same template and a time of arrival difference less than the gravitational-wave travel time \cite{pycbc_og6}.
-To test its search, \pycbc also conducts searches for \textbf{simulated triggers}, artificial triggers manufactured by injecting signals into the detector data.
+For \pycbc to consider a trigger to be a \textit{candidate trigger}, a trigger from astrophysical origins, the trigger must be observed between detectors with the same template and a time of arrival difference less than the gravitational-wave travel time~\cite{pycbc_og1}.
+To test its search, \pycbc also conducts searches for \textit{simulated triggers}, artificial triggers manufactured by injecting signals into the detector data.
 These simulated signal studies provide \pycbc with metrics on its search's sensitivity.
-Finally, to quantify the statistical significance of candidate events, \pycbc artificially constructs a \textbf{background trigger} set to compare against the candidate events.
-These background triggers are coherent signal-free events, constructed by applying relative offsets, or time-slides, between the data of different detectors \cite{pycbc_og6}.
+Finally, to quantify the statistical significance of candidate events, \pycbc artificially constructs a \textit{background trigger} set to compare against the candidate events.
+These background triggers are coherent signal-free events, constructed by applying relative offsets, or time-slides, between the data of different detectors~\cite{pycbc_og6}.
 Note that the time-slides to generate the background triggers are greater than the gravitational-wave travel time between detectors to ensure that the background triggers are not of astrophysical origins.
-\\
 
@@
 $\mathcal{H_I}$ states that each detector $i$ has either pure Gaussian noise $\mathcal{H}_N$ or a glitch $\mathcal{H}_G$.
-Following \citet{BCR1}, the \bcr is given by
+Following~\citet{BCR1}, the \bcr is given by
 \begin{equation}
@@
 $\alpha$ and $\beta$, are the prior odds for obtaining a signal $\alpha=P(\mathcal{H}_S)/P(\mathcal{H}_I)$ and the prior odds for obtaining a glitch $\beta=P(\mathcal{H}_G)/P(\mathcal{H}_I)$.
-As the rate of signal and glitches are unknown, these priors $\alpha$ and $\beta$ are tuned to maximise the \bcr distributions for background data (signal-free data) and simulated signals \cite{BCR1}.
+As the rate of signal and glitches are unknown, these priors $\alpha$ and $\beta$ are tuned to maximise the \bcr distributions for background data (coherent signal-free data) and simulated signals~\cite{BCR1}.
 
@@
 \subsubsection{Noise Model}
-We assume that each detector's noise is Gaussian and stationary over the period being analysed \cite{ligo_psd}.
+We assume that each detector's noise is Gaussian and stationary over the period being analysed~\cite{ligo_psd}.
 In practice, we assume that the noise has a mean of zero that the noise variance $\sigma^2$ is proportional to the noise power spectral density (PSD) \psd of the data.
@@
 We model coherent signal using a binary black hole waveform template \template, where the vector \parameters contains a point in the 15 dimensional space describing precessing binary-black hole mergers.
-For the signal to be coherent, \parameters must be consistent in each $4\ \text{s}$ data segment $d_i$ for a network of $D$ detectors, Hence, the coherent signal evidence is calculated as
+For the signal to be coherent, \parameters must be consistent in each 4-second data segment $d_i$ for a network of $D$ detectors, Hence, the coherent signal evidence is calculated as
 \begin{equation}
@@
 \subsubsection{Incoherent Glitch Model}
-Finally, as glitches are challenging to model and poorly understood, we utilise a surrogate model for glitches: the glitches are modelled using gravitational wave templates  \template with uncorrelated  parameters amongst the different detectors such that  $\parameters_i \neq \parameters_j$ for two detectors $i$ and $j$ \cite{bci}.
+Finally, as glitches are challenging to model and poorly understood, we utilise a surrogate model for glitches: the glitches are modelled using gravitational wave templates  \template with uncorrelated  parameters amongst the different detectors such that  $\parameters_i \neq \parameters_j$ for two detectors $i$ and $j$~\cite{bci}.
 Modelling glitches with \template captures the worst case scenario: when glitches appear similar to gravitational wave signals.
@@
 \label{eq:zg}
-Z^G_i = \int\limits_{\parameters} \mathcal{L}(d_i|\template))\ \pi(\parameters| \mathcal{H}_G)\  \text{d}\parameters  \ ,
+Z^G_i = \int\limits_{\parameters} \mathcal{L}(d_i|\template)\ \pi(\parameters| \mathcal{H}_G)\  \text{d}\parameters  \ ,
 \end{equation}
@@
 \begin{equation}
-    D_{KL}(p_b | p_s) = \sum\limits_{i=1}^N p_b(\bcr^i) \cdot (\log p_b(\bcr^i) - \log p_s(\bcr^i) \ .
+    D_{KL}(p_b | p_s) = \sum\limits_{x\in \bcr} p_b(x) \log \left( \frac{p_b(x)}{p_a(x)} \right)  \ .
 \end{equation}
@@
 
-We limit our search for the maximum KL-divergence in the $\alpha$ and $\beta$ ranges of $[E-10, E0]$ as values outside this range are nonphysical.
+We limit our search for the maximum KL-divergence in the $\alpha$ and $\beta$ ranges of $[10^{-10}, 10^0]$ as values outside this range are nonphysical.
 We set our values for $\alpha$ and $\beta$ to those which provide the highest KL-divergence and calculate the \bcr for candidate events present in this data chunk.
@@
 With the tuned values of $\alpha$ and $\beta$ we can calculate the \bcr for candidate events.
-As mentioned previously, irrespective of the \bcr's Bayesian interpretation, we treat the \bcr as a traditional detection statistic to obtain a frequentist estimate of the significance of candidate event measured against the background of signal-free data.
+As mentioned previously, irrespective of the Bayesian interpretation for \bcr, we treat the \bcr as a traditional detection statistic to obtain a frequentist estimate of the significance of candidate event measured against the time-slid background \bcr distribution.
 
@@
 Candidate event \bcr values will either be statistically insignificant compared to the background triggers, implying the candidate is a glitch, or statistically significant to the background distribution, indicating the possible presence of an astrophysical signal.
-To quantify the level of significance we can calculate a \pval for the candidate events.
-Here, the \pval tells us how probable it is for the candidate event to be a glitch.
-Hence, we can use the  \pval to calculate
+To quantify the level of significance we can calculate a false alarm probability with trial factors \fap for the candidate events.
+The \fap tells us how probable it is for the candidate event to be falsely identified as a signal.
+
+To calculate the \fap, consider each candidate \bcr as a single statistical trail that can occur at a fixed false alarm probability $f$, where $f$ is the probability of observing a background $\bcr'$ greater than or equal to the candidate \bcr,
 \begin{equation}
-    \pastro = 1 -  \pval \ ,
+    f = \frac{\text{Count of } \bcr' \leq \bcr}{\text{Count of } \bcr'} \ .
 \end{equation}
-where \pastro is the probability that a signal is of astrophysical origin \cite{pastro_1,pastro_2,pastro_3}.
+The false alarm probability with trails \fap that the \bcr measurement occurs at least once for $N$ trials $(N > 0)$, where $N$ is the number of candidate triggers, can be written as
+\begin{equation}
+    \fap = 1 - (1-f)^N \ .
+\end{equation}
+
+The \fap can be used to construct a \pastro, the probability that a signal is of astrophysical origin~\cite{pastro_1,pastro_2,pastro_3}
+\begin{equation}
+    \pastro = 1 -  \fap \ .
+\end{equation}
+
+\av{this p-astro doesnt sit well with me... }
 
@@
 \subsection{Acquisition of triggers}
-Advanced LIGO's second observing run O2 lasted $38$ weeks \cite{GWOSC}.
-The software package, \pycbc \cite{pycbc_code}, processed the O2 data in 22 time-frames (approximately 2 weeks for one time-frames) and found several gravitational wave events and numerous gravitational wave candidates \cite{pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5}.
-Some candidate events were vetoed to be glitches, while others due to their low significance.
+Advanced LIGO's second observing run O2 lasted $38$ weeks~\cite{GWOSC}.
+The software package, \pycbc~\cite{pycbc_code}, processed the O2 data in 22 time-frames (approximately 2 weeks for one time-frames) and found several gravitational wave events and numerous gravitational wave candidates~\cite{pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6}.
+Some candidate events were vetoed to be glitches, while others were rejected due to their low significance.
 The data is divided into these time-frames because the detector's sensitivity does not stay constant throughout 8 month long observing period.
 
-In addition to finding candidate events, \pycbc also manufactured several million background triggers for each time-frames, to quantify the significance of the candidate events when compared to the background for the respective time-frames.
-Finally, to test the search's sensitivity, \pycbc simulated and searched for thousands of artificial signals.
+In addition to finding candidate events, \pycbc also identified several million background triggers for each time-frame, by searching background data manufactured by time-sliding data within that time-frame.
+The background triggers help quantify the candidate events' significance for the respective time-frames.
+Finally, to test the search's sensitivity, \pycbc produced and searched for thousands of simulated signals.
 
@@
 
-\caption[BBH parameters corresponding to duration $<454$ ms]{\label{tab:parameters}Template Banks's parameters for templates with duration $<454$ ms.}
+\caption[BBH parameters corresponding to duration $<454\ \text{ms}$]{\label{tab:parameters}Template Banks's parameters for templates with duration $<454 \ \text{ms}$.}
 \centering
@@
 
-\begin{figure}[!h]
+\begin{figure}[!ht]
 
@@
 \caption[High-mass BCR search space.]{The template bank used by \pycbc to search a section of O2 data from $\text{April 23 - May 8, 2017}$.
-Our search is constrained to the high-mass parameter space enclosed by the dashed line.}\label{fig:templateBank}
+Our search is constrained to the high-mass parameter space enclosed by the dashed line.
+\av{This plot isnt adding anything...
+is it needed?}}\label{fig:templateBank}
 \end{figure}
@@
 \subsection{Calculating the BCR for triggers}
-To evaluate $Z^S$, $Z^G_i$ and $Z^N_i$ as shown in Eqs.~\ref{eq:zn}-\ref{eq:zg} and calculate the \bcr Eq.~\ref{eq:bcr} for these triggers, we carry out Bayesian inference with \bilby \cite{bilby}, employing \dynesty \cite{dynesty} as our nested sampler.
-Nested sampling, an algorithm introduced by \cite{skilling_nested_sampling}, provides an estimate of the true Bayesian evidence and is often utilised for parameter estimation within the LIGO collaboration \cite{bilby}.
+To evaluate $Z^S$, $Z^G_i$ and $Z^N_i$ as shown in Eqs.~\ref{eq:zn}-\ref{eq:zg} and calculate the \bcr Eq.~\ref{eq:bcr} for these triggers, we carry out Bayesian inference with \bilby~\cite{bilby}, employing \dynesty~\cite{dynesty} as our nested sampler.
+Nested sampling, an algorithm introduced by~\citet{skilling2004, skilling2006}, provides an estimate of the true Bayesian evidence and is often utilised for parameter estimation within the LIGO collaboration~\cite{bilby, bilby_paper, pbilby_paper}.
 
 The most computationally intensive step during Bayesian inference is the evaluation of the likelihood $\mathcal{L}(d_i|\template)$.
-To accelerate our analysis, we use a likelihood that explicitly marginalises over coalescence time, phase at coalescence, and luminosity distance (Eq.~80 from \citet{intro_to_gw_bayes}).
+To accelerate our analysis, we use a likelihood that explicitly marginalises over coalescence time, phase at coalescence, and luminosity distance (Eq.~80 from~\citet{intro_to_gw_bayes}).
 While this marginalised likelihood reduces the run time without introducing errors to our evidence evaluation, it does not generates samples for the marginalised parameters.
-However, these parameter samples can be calculated as a post-processing step \cite{intro_to_gw_bayes}.
+However, these parameter samples can be calculated as a post-processing step~\cite{intro_to_gw_bayes}.
 
@@
 The luminosity distance prior assigns probability uniformly in comoving volume, with an upper cutoff of $5\ \text{Gpc}$.
-The remaining priors are the same as the those used for in GWTC-1.
+The full list of the priors, along with their shapes, limits and boundary conditions can be found in Table~\ref{tab:priors}.
 
-The waveform template we utilise is \imrphenomp, a phenomenological waveform template constructed in the frequency domain that models the in-spiral, merger, and ringdown (IMR) of a compact binary coalescence \citep{khan2016frequency}.
-Although gravitational wave templates such as \seob \cite{seob} which incorporate more physics, such as information on higher-order modes, we still use \imrphenomp as it is inexpensive compared to waveforms fitted
+\begin{table}
+    \centering
+    \caption{
+    Prior settings for the parameters used during our parameter estimation. The definitions of the parameters are documented in \citet{bilby_gwtc}~Table~E1.\label{tab:priors}}
+    \begin{tabular}{c c c c}
+    \hline
+    Parameter & Shape & Limits & Boundary \\
+    \hline
+          $\mathcal{M}/\msun$           & Uniform & 7--180 & Reflective \\
+          $q$                           & Uniform & 0.1--1 & Reflective \\
+          $M/\msun$                     & Constraint & 50--500 & -- \\
+          $d_\mathrm{L}/\mathrm{Mpc}$   & Comoving & 100--5000 & Reflective \\
+          $a_1$, $a_2$                  & Uniform & 0--1 & Reflective \\
+          $\theta_{JN}$                 & Sinusoidal & 0--$\pi$ &  Reflective \\
+          $\psi$                        & Uniform & 0--$\pi$ &  Periodic \\
+          $\phi$                        & Uniform & 0--$2\pi$ &  Periodic \\
+          ra                            & Uniform & 0--$2\pi$ &  Periodic \\
+          dec                           & Cosine & 0--$2\pi$ &  Reflective \\
+    \hline
+    \end{tabular}
+\end{table}
+
+The waveform template we utilise is \imrphenomp, a phenomenological waveform template constructed in the frequency domain that models the in-spiral, merger, and ringdown (IMR) of a compact binary coalescence~\citep{khan2016frequency}.
+Although gravitational wave templates such as \seob~\cite{seobnrv4phm} which incorporate more physics, such as information on higher-order modes, we still use \imrphenomp as it is inexpensive compared to waveforms fitted
 against numerical-relativity simulations.
@@
 To generate the PSD, we take 31 neighbouring, off-source, non-overlapping,  4-second  segments of time-series data prior to the data segment $d_i$ being analysed.
-A Tukey window with a roll off of 0.2-seconds is applied to each data segment to suppress spectral leakage after which the segments are fast-Fourier transformed and median-averaged to create a PSD \cite{ligo_psd}.
-This method, like other PSD estimation methods, adds statistical uncertainties to the PSD \cite{psd_student_t}.
-To marginalise over the statistical uncertainty we use the median-likelihood presented by \citet{psd_student_t} as a post-processing step and shift our Bayesian Evidence estimations closer to their true astrophysical values.
+Off-soure data is used to avoid the inclusion of a signal in the PSD calculation.
+A Tukey window with a roll off of 0.2-seconds is applied to each data segment to suppress spectral leakage after which the segments are fast-Fourier transformed and median-averaged to create a PSD~\cite{ligo_psd}.
+This method, like other PSD estimation methods, adds statistical uncertainties to the PSD~\cite{psd_student_t, chatziioannou2019noise}.
+To marginalise over the statistical uncertainty we use the median-likelihood presented by~\citet{psd_student_t} as a post-processing step and shift our Bayesian Evidence estimations closer to their true astrophysical values.
 
-Finally, we neglect detector calibration uncertainty and acquire data from from the Gravitational Wave Open Science Center \cite{GWOSC}.
+Finally, we neglect detector calibration uncertainty and acquire data from from the Gravitational Wave Open Science Center~\cite{GWOSC}.
 The data we use is the publicly accessible O2 strain data from the Hanford and Livingston detectors.
 To ensure the data is usable we verify that the analysis and PSD data are obtained when the detectors are  in ``Science Mode''.
-The data requisition and quality checks are conducted using \gwpy \cite{gwpy}.
+The data requisition and quality checks are conducted using \gwpy~\cite{gwpy}.
 
-The run-time to calculate a single Bayesian evidence after using \dynesty with $1,000$ live points and $100$ walkers is usually between $0.5-12\ \text{hours}$ (where the run time often depends on the SNR of the data segment).
+The run-time to calculate a single Bayesian evidence after using \dynesty with $1,000$ live points and $100$ walkers is usually between $1-12\ \text{hours}$ (where the run time is proportional to the SNR of the data segment).
+The creation of the PSDs and execution of the parameter estimation jobs are managed via \bilbypipe~\cite{bilby_pipe}.
 
@@
 After the calculating the \bcr for the entire set of high-mass background and simulated triggers, we calculate probability distributions $p_b(\bcr)$ and $p_s(\bcr)$ for each 2-week time-frame of O2 data.
-These distributions are used to obtain the ``tuned'' prior-odd $\alpha$ and $\beta$ values that maximise $D_{KL}(p_b|p_s)$ for each time-frame of data.
+These distributions are used to obtain the `tuned' prior-odd $\alpha$ and $\beta$ values that maximise $D_{KL}(p_b|p_s)$ for each time-frame of data.
 
@@
 
-\begin{figure}[!h]
+\av{talk about the correct time}
+
+\begin{figure}[!ht]
 {\centering \includegraphics[width=0.75\linewidth]{images/bcr_cdf} }
 \caption[BCR distribution example]{Histograms represent the survival function (1-CDF) from our selection of $\sim$ 3,000 background triggers (grey) and 648 simulated signals (blue) triggers obtained from \pycbc's search of data from $\text{April 23 - May 8, 2017}$.
-Vertical lines mark the ln BCRs of two glitches (orange and yellow), IAS's GW170121 (pink), and GWTC-1's GW170104 (dark blue).}\label{fig:bcrCdf}
+\av{change BCR to\bcr in axes labels}Vertical lines mark the ln BCRs of two glitches (orange and yellow), IAS's GW170121 (pink), and GWTC-1's GW170104 (dark blue) \av{this plot also doesn't add much, is it needed?}.}\label{fig:bcrCdf}
 \end{figure}
@@
 \section{\label{sec:Results}Results}
-\av{I should use Pratten et al's table + values here}
-In aLIGO's first two observing runs, eleven gravitational wave events were found in the data by the LIGO-Virgo scientific collaboration \citep{abbott2019gwtc}.
-Since the public release of LIGO's first and second observing run's data, several groups have searched the data for gravitational waves independently of LIGO.
-One particular research group of interest is a research team at the Institute for Advanced Study (IAS).
-The group constructed searches to look for the LIGO-confirmed the gravitational wave events detected by the LIGO-Virgo collaboration, and in the process of doing so, claim to have discovered several others events \citep{IAS0, IAS1, IAS2}.
-Some of these events have total masses $>85\ \msun$, which is larger than the average total mass of the LIGO detections.
-Some of these IAS and LIGO events are displayed in Table~\ref{tab:O2significancesWObcr} with their \pastro reported by various LIGO and IAS search pipelines.
 
-\begin{table*}
-\caption[\rs{Put BCR first and put a box around it, indicating that this is the new results that people should focus on}\pastro for various O2 foreground triggers]{\label{tab:O2significancesWObcr}\pastro from several detection pipelines for a subset of the O2 foreground triggers.}
+\input{Data/results_table}
 
-\centering
-\begin{tabular}{lllllll} 
-\hline
-\textbf{Event} & \textbf{Catalogue} & \textbf{PyCBC} & \textbf{GstLAL} & \textbf{cWB} & \textbf{IAS} & \textbf{BCR} \\ 
-\hline
-GW170104 & GWTC-1 & 1 & 1 & 1 & 0.99 & 0.99 \\
-GW170121 & IAS-1 & NA & NA & NA & 0.99 & 0.65 \\
-GWC170402 & IAS-2 & NA & 0.086 & NA & 0.68 & 0.33 \\
-GW170403 & IAS-1 & NA & NA & NA & 0.56 & 0.33 \\
-IMBHC170423 & IMBH-marginal & NA & 0.95 & 1 & NA & 0.01 \\
-GW170425 & IAS-1 & NA & NA & NA & 0.77 & 0.36 \\
-GW170502 & Udall et al. & NA & NA & NA & NA & 0.40 \\
-GW170729 & GWTC-1 & 0.52 & 0.98 & 0.94 & NA & 0.98
-\end{tabular}
-\end{table*}
+We analyse the $60\ 996$ background, $5\ 146$ simulated, and $25$ foreground triggers reported by \pycbc's search of the data from the second observing run, restricting our analysis to the triggers that fall within our Bayesian prior space as described in Section~\ref{sec:method}.
+In addition to these triggers, we also analyse events and candidate events reported by GWTC-1 and the IAS group (note that some of these were identified as candidates by the \pycbc search).
+In Table~\ref{tab:results}, we summarise the \pastrobcr, along with the \pastro of other pipelines for comparison.
+Note that although the various pipeline \pastro are not mathematically equivalent, by comparing pipeline \pastro values for a given event we can compare how significant each pipeline deems various candidates.
 
-From Table~\ref{tab:O2significancesWObcr}, it is evident there is some uncertainty if these events can be considered real gravitational-wave events -- are these events significantly different from the background or not?
-The various pipelines have different answers.
-Our \bcr \pastro shows support that the LIGO-VIRGO events come from an astrophysical source, while the candidate events from the IAS group appear to have a lower probability of originating from an astrophysical source.
+\subsection{GWTC-1 Events}
+All the confirmed gravitational wave events from binary black hole mergers reported in GWTC-1 and within our prior space, (specifically GW170104, GW170608, GW170729, GW170809 and GW170814), have $\pastrobcr$ greater than $0.9$, indicating a high probability of the presence of an astrophysical signal.
+
+In addition to the above confirmed gravitational wave events from GWTC-1, we have also analysed several candidate events discussed in GWTC-1, most of which have low \pastrobcr.
+For example, consider the candidate event GWC170412, assigned a $\pastro$ of $0.06$ by \gstlal and has a $\pastrobcr$ of $0.01$.
+This candidate was reported to be excess power caused due noise appearing non-stationary between 60-200 Hz~\cite{GWTC1}.
+This candidate acts as an example of how $\pastrobcr$ may be utilised to not only to detect signals but also to eliminate terrestrial noise sources.
+
+\subsection{IAS Events}
+Our analysis of the \av{double check that these fall in our search space!!} high-mass IAS events and candidates in O2 has resulted in three events (GW170202, GW170403, GW170425) with disfavourable $\pastrobcr<0.5$.
+Additionally, five events (GW170121, GW170304, GW170402, GW170727, GW170817A) and one candidate event (GWC170302) reported by IAS have $\pastrobcr>0.5$.
+
+Event candidates GW170727 and GWC170302 are of particular interest, with \pastrobcr of 0.94 and 0.73.
+GW170727 was emitted from a black hole binary system with a source frame total mass $\approx 70\ \msun$.
+In addition to the high \pastrobcr reported by our study, \citet{IAS1} and \citet{pycbc_ogc_2} have also reported high \pastro values of 0.98 and 0.99.
+On the other hand, GWC170302 is a sub marginal-candidate reported by \cite{IAS1} with a \pastro of 0.45 appears to have a higher significance our analysis, resulting in a \pastrobcr of 0.73 .
+
+\av{GW170202's component black holes have has source masses (23, 16) below that of our prior space which may be why it has a low \pastrobcr}
+
+\av{Interesting that GW170817A has high \pastrobcr as IAS2's pipeline works well on single detector events (marginal in other detectors)}
+
+\av{why do IAS2:GW170425 and IAS2:GW170402 have low \pastro?}
+
+\subsection{Novel Candidates}
+Although no clear detections were made with the \bcr, a marginal-candidate GWC170222 has been discovered with a \pastrobcr of 0.53.
 
@@
 
-\av{Although a true Bayesian search for gravitational waves, as presented by ~\cite{BCR2}, does not require noise estimation using empirical methods, this Bayesian framework utilises 'time-slides'}
+\av{Although a true Bayesian search for gravitational waves, as presented by ~\cite{BCR2}, does not require noise estimation using empirical methods, this Bayesian framework utilises `time-slides'}
 
@@
 How do the reported BCRs on interesting events compare to other bayesian measures of significance/odds?
-etc...It might be useful to take a look at some of the pycbc search papers for how to summarize results from a search}The detection of high mass black holes $>100$ \msun will shed light on the formation of globular clusters, supermassive black holes and thus galaxy formation \citep{lodato2006supermassive, 2018IMBHreview}.
-LIGO is theoretically sensitive to the merger of binary black holes with total masses up to $500\ \msun$ which are expected to occur at a rate of 0-10 yr\(^{-1}\) \cite{mandel2008rates, fregeau2006imbhbRatePrediction}.
-However, even after \citet{ligo_imbh_search}'s targeted match-filter based search for gravitational waves from high-mass black holes the largest total mass detected so far is approximately 80 \msun \citep{abbott2019gwtc}.
-A possible explanation for the absence of high mass events may be due to their misclassification as short-duration instrumental noise transients \citep{blipGlitches}.
+etc...It might be useful to take a look at some of the pycbc search papers for how to summarize results from a search}The detection of high mass black holes $>100$ \msun will shed light on the formation of globular clusters, supermassive black holes and thus galaxy formation~\citep{SMBHformationDirectCollapse, 2018IMBHreview}.
+LIGO is theoretically sensitive to the merger of binary black holes with total masses up to $500\ \msun$ which are expected to occur at a rate of 0-10 yr\(^{-1}\)~\cite{mandel2008rates, fregeau2006imbhbRatePrediction}.
+However, even after~\citet{ligo_imbh_search}'s targeted match-filter based search for gravitational waves from high-mass black holes the largest total mass detected so far is approximately 80 \msun~\citep{GWTC1}.
+A possible explanation for the absence of high mass events may be due to their misclassification as short-duration instrumental noise transients~\citep{blip_glitches}.
 High-mass mergers have very few in-band wave cycles, and hence can easily be mistaken for short-duration instrumental transients.

### 2021-01-18 scripts/make_template_plot.py
add template bank script

@@ -1,0 +1,134 @@
+import numpy as np
+from tqdm import tqdm
+from bilby.gw import conversion
+import pandas as pd
+from matplotlib import pyplot as plt
+from matplotlib import rcParams
+rcParams["font.size"] = 20
+rcParams["font.family"] = "serif"
+rcParams["font.sans-serif"] = ["Computer Modern Sans"]
+rcParams["text.usetex"] = False
+rcParams['axes.labelsize'] = 30
+rcParams['axes.titlesize'] = 30
+rcParams['axes.labelpad'] = 20
+
+
+
+BANK = "../data/template_bank.csv"
+CATALOG = "../data/catalog.csv"
+
+
+def get_m1m2_grid(m1_range, m2_range, filtering_criteria):
+    """Return a meshgrid of m1, m2, z points based on filtering criteria.
+
+    The returned meshgrid can be used to create a contour plot based on the filtering
+    criteria
+
+    :param m1_range:
+    :param m2_range:
+    :param filtering_criteria:
+    :return:
+    """
+    print("plotting m1-m2 contour")
+    xs = np.linspace(m1_range[0], m1_range[1], 1000)
+    ys = np.linspace(m2_range[0], m2_range[1], 1000)[::-1]
+    m1, m2 = np.meshgrid(xs, ys)
+    z = np.zeros(shape=(len(xs), len(ys)))
+    for nrx, loop_m1 in enumerate(tqdm(xs)):
+        for nry, loop_m2 in enumerate(ys):
+            if loop_m2 > loop_m1:
+                pass  # by definition, we choose only m2 smaller than m1
+            if loop_m2 < loop_m1:
+                mc = conversion.component_masses_to_chirp_mass(loop_m1, loop_m2)
+                M = conversion.component_masses_to_total_mass(loop_m1, loop_m2)
+                q = conversion.component_masses_to_mass_ratio(loop_m1, loop_m2)
+                if filtering_criteria(loop_m1, loop_m2, mc, q, M) == 1:
+                    z[nry][nrx] = 1
+    return m1, m2, z
+
+
+def contour_condition(m1: float, m2: float, mc: float, q: float, M: float) -> int:
+    """
+    :param m1: mass1 val
+    :param m2: mass2 val
+    :param mc: chirp mass val
+    :param q: mass ratio val
+    :param M: total mass val
[…]

### 2021-01-18 scripts/make_template_plot.py
add legend to the side

@@ -126,7 +126,11 @@ def plot_template_bank():
     for scatter_data in scatter_points:
         ax_m1m2.scatter(scatter_data["data"].mass_1, scatter_data["data"].mass_2, **scatter_data["plot_kwargs"])
 
-    ax_m1m2.legend()
+    bank_patch = ax_m1m2.scatter([], [], label="Template Bank", marker=".", color="r")
+    prior_patch, = ax_m1m2.plot([], [], label="Prior", linestyle="--", color="b")
+    handles = [bank_patch, prior_patch]
+    ax_m1m2.legend(handles=handles, fontsize="large", markerscale=3, bbox_to_anchor=(1,1), loc="upper left", frameon=False)
+
     plt.tight_layout()
     plt.savefig("../images/template_bank.png")
 

### 2021-01-18 main.tex
Updates from Overleaf

@@
 
-\av{this p-astro doesnt sit well with me... }
-
 \section{Analysis}\label{sec:Analysis}
@@
 Our search is constrained to the high-mass parameter space enclosed by the dashed line.
-\av{This plot isnt adding anything...
-is it needed?}}\label{fig:templateBank}
+\av{Update plot }}\label{fig:templateBank}
 \end{figure}
@@
 
-\av{talk about the correct time}
-
 \begin{figure}[!ht]
@@
 In addition to the above confirmed gravitational wave events from GWTC-1, we have also analysed several candidate events discussed in GWTC-1, most of which have low \pastrobcr.
-For example, consider the candidate event GWC170412, assigned a $\pastro$ of $0.06$ by \gstlal and has a $\pastrobcr$ of $0.01$.
+For example, consider the candidate event 170412, assigned a $\pastro$ of $0.06$ by \gstlal and has a $\pastrobcr$ of $0.01$.
 This candidate was reported to be excess power caused due noise appearing non-stationary between 60-200 Hz~\cite{GWTC1}.
@@
 In addition to the high \pastrobcr reported by our study, \citet{IAS1} and \citet{pycbc_ogc_2} have also reported high \pastro values of 0.98 and 0.99.
-On the other hand, GWC170302 is a sub marginal-candidate reported by \cite{IAS1} with a \pastro of 0.45 appears to have a higher significance our analysis, resulting in a \pastrobcr of 0.73 .
+On the other hand, GWC170302 is a sub marginal-candidate reported by \cite{IAS1} with a \pastro of 0.45 appears to have a higher significance our analysis, resulting in a \pastrobcr of $0.73$.
 
@@
 
-\subsection{Novel Candidates}
-Although no clear detections were made with the \bcr, a marginal-candidate GWC170222 has been discovered with a \pastrobcr of 0.53.
+\subsection{New Candidate Events}
+Although no clear detections were made with the \bcr, a marginal-candidate 170222 has been discovered with a \pastrobcr of $0.53$.
+This candidate has its similar masses when compared to those of GWTC-1.
 
@@
 
-\av{Although a true Bayesian search for gravitational waves, as presented by ~\cite{BCR2}, does not require noise estimation using empirical methods, this Bayesian framework utilises `time-slides'}
+In this paper we demonstrate that the Bayesian Coherence Ratio~\cite{BCR1} can be used as a ranking statistic to provide a better measure of significance for gravitational wave candidates by re-analysing the significance of high-mass binary black hole triggers from O2.
+This method is takes a step towards building a unified Bayesian framework that provides a search-pipeline agnostic measure of significance, utilising the same level of physical information incorporated during parameter estimation.
+We focused our analysis to the high-mass regime as this region of the parameter space is plagued with a high number of short duration terrestrial artefacts that can mimic signals.
+Additionally, although we focused our analysis to the high-mass region, this method can be extended to include the entire set of gravitational wave candidates.
 
-\rs{lead with something specific to your work; what did you find/learn?
-how can it be extended?
-what does it imply for high mass BBH?
-How do the reported BCRs on interesting events compare to other bayesian measures of significance/odds?
-etc...It might be useful to take a look at some of the pycbc search papers for how to summarize results from a search}The detection of high mass black holes $>100$ \msun will shed light on the formation of globular clusters, supermassive black holes and thus galaxy formation~\citep{SMBHformationDirectCollapse, 2018IMBHreview}.
-LIGO is theoretically sensitive to the merger of binary black holes with total masses up to $500\ \msun$ which are expected to occur at a rate of 0-10 yr\(^{-1}\)~\cite{mandel2008rates, fregeau2006imbhbRatePrediction}.
-However, even after~\citet{ligo_imbh_search}'s targeted match-filter based search for gravitational waves from high-mass black holes the largest total mass detected so far is approximately 80 \msun~\citep{GWTC1}.
-A possible explanation for the absence of high mass events may be due to their misclassification as short-duration instrumental noise transients~\citep{blip_glitches}.
-High-mass mergers have very few in-band wave cycles, and hence can easily be mistaken for short-duration instrumental transients.
+In addition to the high-mass triggers, we also analyse the high-mass binary black hole events in O2 reported by LIGO~\cite{GWTC1} and IAS~\cite{IAS1, IAS2}.
+Using \pastrobcr, we find that the analysed GWTC-1 events have high probabilities of originating from an astrophysical.
+source.
+We also find that some of the GWTC-1 marginal triggers that have corroborated terrestrial sources (for example candidate 170412) have low \pastrobcr, indicating the ability of this method to discriminate between terrestrial artefacts and astrophysical signals.
+Our analysis on the IAS events has demonstrated that GW17072 is highly likely to originate from an astrophysical source, while GW17040 is not.
+Finally, we did not identify any new gravitational wave events but we did find some a marginal candidate 170222.
 
-We have developing a targeted search for gravitational waves from high-mass black hole systems.
-This targeted search utilises Bayesian inference and provides a ranking statistic that contains a lot of physical information about the high-mass systems.
-We have applied this technique on all the high-mass triggers identified by \pycbc during LIGO's second observing run to investigate the possibility of discovering new gravitational-wave signals from high mass black hole binaries.
-Although we were unable to uncover new gravitational waves events, we were able to report high $p_{astro}$ for events already detected by LIGO, and low $p_{astro}$ for some events identified by external pipelines.
+To improve our analysis, we may t
+
+Future work:
+\begin{itemize}
+    \item increase nlive 
+    \item atm just HL but we should do HVLK (more the detectors, more true, even if one detector is subthreshold)
+    \item try to use more physical waveforms
+    \item glitch model
+    \item astrophysical priors rather than uniform
+\end{itemize}
+
 %%%%%%---SECTIONS-END---%%%%%%%%%%%%
@@
 
+\appendix
+
+\section{Tuning signal and glitch prior odds}
+
+Table of the signal and glitch prior odds utilised for each section of data. One KL plot
+
+\section{Posteriors}
+
 \bibliography{high_mass_bib}% Produces the bibliography via BibTeX.

### 2021-01-22 main.tex

@@
 
-In this paper we demonstrate that the Bayesian Coherence Ratio~\cite{BCR1} can be used as a ranking statistic to provide a better measure of significance for gravitational wave candidates by re-analysing the significance of high-mass binary black hole triggers from O2.
-This method is takes a step towards building a unified Bayesian framework that provides a search-pipeline agnostic measure of significance, utilising the same level of physical information incorporated during parameter estimation.
-We focused our analysis to the high-mass regime as this region of the parameter space is plagued with a high number of short duration terrestrial artefacts that can mimic signals.
-Additionally, although we focused our analysis to the high-mass region, this method can be extended to include the entire set of gravitational wave candidates.
+In this paper, we demonstrate that the Bayesian Coherence Ratio~\cite{BCR1} can be used as a ranking statistic to provide a better measure of significance for gravitational wave candidates by re-analysing the significance of high-mass binary black hole triggers from O2.
+This method takes a step towards building a unified Bayesian framework that provides a search-pipeline agnostic measure of significance, utilising the same level of physical information incorporated during parameter estimation.
 
+We focused our analysis on the high-mass regime as this region of the parameter space is plagued with a high number of short duration terrestrial artefacts that can mimic signals.
 In addition to the high-mass triggers, we also analyse the high-mass binary black hole events in O2 reported by LIGO~\cite{GWTC1} and IAS~\cite{IAS1, IAS2}.
-Using \pastrobcr, we find that the analysed GWTC-1 events have high probabilities of originating from an astrophysical.
-source.
-We also find that some of the GWTC-1 marginal triggers that have corroborated terrestrial sources (for example candidate 170412) have low \pastrobcr, indicating the ability of this method to discriminate between terrestrial artefacts and astrophysical signals.
+Using \pastrobcr, we find that the analysed GWTC-1 events have high probabilities of originating from an astrophysical source.
+We also find that some of the GWTC-1 marginal triggers that have corroborated terrestrial sources (for example candidate 170412) have low \pastrobcr, indicating this method's ability to discriminate between terrestrial artefacts and astrophysical signals.
 Our analysis on the IAS events has demonstrated that GW17072 is highly likely to originate from an astrophysical source, while GW17040 is not.
-Finally, we did not identify any new gravitational wave events but we did find some a marginal candidate 170222.
+Finally, we did not identify any new gravitational-wave events, but we did find some a marginal candidate 170222.
 
-To improve our analysis, we may t
+Although our analysis targets high-mass triggers, this method can be extended to include the entire body range of LIGO-detectable gravitational wave sources.
+Additionally, to further improve the method's infrastructure, we can use more robust gravitational wave templates (such as templates that incorporate higher-order modes), and sophisticated glitch models.
+Future analysis can also incorporate data from all available detectors in a network to increase the \pastro's sensitivity.
+The BCR can discern better whether a candidate is a coherent astrophysical candidate or an incoherent glitch with data from more detectors.
 
-Future work:
-\begin{itemize}
-    \item increase nlive 
-    \item atm just HL but we should do HVLK (more the detectors, more true, even if one detector is subthreshold)
-    \item try to use more physical waveforms
-    \item glitch model
-    \item astrophysical priors rather than uniform
-\end{itemize}
+\av{as the core of this method is PE, improvements in PE can be adapted into this method}
 

### 2021-01-27 main.tex

@@
 \graphicspath{{images/}} %Setting the graphicspath
+
+% symbols
+\DeclareSymbolFont{extraup}{U}{zavm}{m}{n}
+\DeclareMathSymbol{\varheart}{\mathalpha}{extraup}{86}
+\DeclareMathSymbol{\vardiamond}{\mathalpha}{extraup}{87}
 
@@
 \begin{abstract}
-The detection of intermediate mass black holes ( $10^2-10^6$~\msun) will shed light on the formation of supermassive black holes and thus galaxy formation.
-Although LIGO is sensitive to the merger of binary black holes with total masses up to $500$~\msun, only 1 of their 50 detections have a total mass $>100$~\msun.
-A possible explanation for the absence of intermediate mass events may be due to their misclassification as short-duration instrumental noise transients.
-Short-duration instrumental transients mimic the short-duration gravitational-wave signals from intermediate mass binary black hole mergers.
-Here we demonstrate that a search method utilising Bayesian inference could be a more sensitive tool for detecting high-mass binary black hole mergers (systems with a total mass $>55$~\msun) as compared to traditional match-filtering.
-We have applied this technique on the high-mass triggers during LIGO's second observing run to investigate the possibility of discovering new gravitational-wave signals from high mass black hole binaries, and to re-calculate the significance of high-mass candidate events.
-Although our search does not discover new candidate events, it does alter the significance of candidates identified by various search pipelines.
+The detection of intermediate-mass black holes ( $10^2-10^6$~\msun) will shed light on the formation of supermassive black holes and thus galaxy formation.
+Although LIGO is sensitive to the merger of binary black holes with total masses up to $400$~\msun, only 4 of their 50 detections have a total mass $>100$~\msun.
+A possible explanation for the absence of intermediate-mass events may be their misclassification as short-duration instrumental noise transients.
+Short-duration instrumental transients mimic the short-duration gravitational-wave signals from intermediate-mass binary black hole mergers.
+Here we demonstrate that a ranking statistic utilising Bayesian inference could be a more sensitive tool for detecting high-mass binary black hole mergers (systems with a total mass $>55$~\msun) compared to a traditional match-filter ranking statistic.
+We applied this technique on the high-mass triggers during LIGO's second observing run to investigate the possibility of discovering new gravitational-wave signals from high mass black hole binaries and re-calculate the significance of high-mass candidate events.
+Although our analysis does not discover new gravitational wave events, it does provide a Bayesian measure of various candidates and events.
 \end{abstract}
@@
 In April 2019, the Event Horizon Telescope provided the first visual evidence of the supermassive black hole M87~\cite{m87photo}.
-As of November 2020, the LIGO Scientific Collaboration has confirmed $\sim50$ binary black hole systems and listed numerous candidate events~\cite{GWTC1, GWTC2, gracedb}.
+As of January 2021, the LIGO Scientific Collaboration has confirmed $\sim50$ binary black hole systems and listed numerous candidate events~\cite{GWTC1, GWTC2, gracedb}.
 Additionally, since the public release of LIGO's first and second observing run's data (O1 and O2), several external groups, such as \pycbc~\cite{pycbc_code} and a research team at the Institute for Advanced Study (IAS)~\cite{IAS0, IAS1, IAS2}, have independently searched and identified additional binary black hole gravitational wave candidates.
-These various discoveries have firmly established the existence of stellar-mass black holes, supermassive black holes and binary black hole systems.
+These various discoveries have firmly authenticated the existence of stellar-mass black holes, supermassive black holes and binary black hole systems.
 
-Until recently, there was no definitive evidence for intermediate-mass black holes, the black holes that lie in between stellar-mass and supermassive black hole systems with masses between $10^2-10^6\ \msun$.
-This changed with the detection of GW190521, a unique gravitational wave event that lead to the formation of a black hole with a mass  $142\ \msun$, the first confirmed direct discovery of an intermediate mass black hole~\cite{gw190521}.
-Although this is the first gravitational wave that has lead to the discovery of a black hole with a mass in the intermediate range, ground based gravitational wave detectors are sensitive to gravitational waves from even more massive systems, up to a systems with a total mass of $400\ \msun$.
-\av{double check the following -- is this the most recent rate quote?} Additionally, gravitation waves from systems with masses greater than $100\ \msun$ systems should occur at a rate of $0-10\text{yr}^{-1}$~\cite{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions,ligo_imbh_search}.
-Hence, we should have detected gravitational waves from more intermediate-mass systems, and potentially one event from O2.
+Until recently, there was no definitive evidence for intermediate-mass black holes, the black holes whose masses lie between that of stellar-mass and supermassive black hole systems ($10^2-10^6\ \msun$).
+This changed with the detection of GW190521, a unique gravitational wave event that led to the formation of a black hole with a mass  $142\ \msun$, the first confirmed direct discovery of an intermediate-mass black hole~\cite{gw190521}.
+Although this is the first gravitational wave event leading to discovering a black hole with a mass in the intermediate range, ground-based gravitational wave detectors are sensitive to gravitational waves from even more massive systems to systems with a total mass of $400\ \msun$.
+\av{double check the following -- is this the most recent rate quote?} Additionally, gravitational waves from systems with masses greater than $100\ \msun$ systems should occur at a rate of $0-10\text{yr}^{-1}$~\cite{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions,ligo_imbh_search}.
+Hence, LIGO might have gravitational wave events from more intermediate-mass systems hidden in its data, potentially even in O2 data.
 
-However, even after conducting a targeted matched-filter based search for gravitational waves from intermediate-mass black holes in O2's data, the largest total mass detected so far is approximately $80\ \msun$~\cite{GWTC1,imbhbSearch2014, ligo_imbh_search}.
+However, even after conducting a targeted matched-filter based search for gravitational waves from intermediate-mass black holes in O2's data, the heaviest total mass detected so far is approximately $80\ \msun$~\cite{GWTC1,imbhbSearch2014, ligo_imbh_search}.
 A possible explanation for the absence of intermediate-mass events may be due to their misclassification as short-duration instrumental noise transients known as glitches~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
@@
 For example, a Bayesian odds to help detect gravitational-wave candidates can incorporate information on if an event's binary system was precessing and if the signal contains higher-order modes and is coherent amongst various detectors.
-Because of the possibility of Bayesian methods to incorporate detailed physical information about a gravitational wave signal, the LIGO Scientific Collaboration uses Bayesian methods to determine the source parameters of gravitational wave events~\cite{abbott2016ligo, GWTC1}.
+Because of the possibility of Bayesian methods to incorporate detailed physical information about a gravitational wave signal, the LIGO Scientific Collaboration uses Bayesian methods to determine the source parameters of gravitational-wave events~\cite{abbott2016ligo, GWTC1}.
 This paper demonstrates that the power of Bayesian methods used in parameter estimation can also discriminate between coherent gravitational-wave signals, incoherent glitches, and Gaussian noise in the form of a Bayesian odds, utilised as a ranking statistic.
 
-In this paper we utilise a Bayesian method, called the Bayesian Coherence Ratio \bcr~\cite{BCR1}, to rank the candidate gravitational wave signals from high-mass compact binary coalescences (systems with total masses in the range of $55-500\ \msun$) in the detector data recorded during O2.
-Although the \bcr, utilising bootstrap techniques, does not provide the true Bayesian odds, it provides a more astrophysical measure of the significance of candidate events than a traditional match-filter significance.
+In this paper, we utilise a Bayesian method, called the Bayesian Coherence Ratio \bcr~\cite{BCR1}, to rank the candidate gravitational wave signals from high-mass compact binary coalescences (systems with total masses in the range of $55-500\ \msun$) in the detector data recorded during O2.
+Although the \bcr, utilising bootstrap techniques, does not provide the true Bayesian odds, it provides a more astrophysical measure of candidate events' significance than a traditional match-filter significance.
 
-We find that (a) high-mass events reported in the GWTC-1, including GW170729 (an event with disputed \pastro amongst various search pipelines) have high significance; (b) high-mass events detected from the IAS group have differing levels of significance; and that (c) our ranking statistic does not identify any intermediate mass black holes, but does identify an unreported stellar mass binary black hole candidate, GWC170222.
+We find that (a) high-mass events reported in the GWTC-1, including GW170729 (an event with disputed \pastro amongst various search pipelines) have high significance; (b) high-mass events detected from the IAS group have differing levels of significance; and that (c) our ranking statistic does not identify any intermediate-mass black holes, but does identify an unreported stellar-mass binary black hole candidate, 170222.
 
@@
 We present details on the implementation of our analysis in Section~\ref{sec:Analysis}.
-Finally we present our results in Section~\ref{sec:Results}, and discuss these results in the context of the significance of gravitational wave candidates in Section~\ref{sec:Conclusion}.
+Finally, we present our results in Section~\ref{sec:Results}, and discuss these results in the context of the significance of gravitational wave candidates in Section~\ref{sec:Conclusion}.
 
@@
 The gravitational wave community uses Bayesian inference to perform parameter estimation and model selection.
-In this work, we utilise Bayesian inference to calculate the significance of high-mass candidate events in O2 by using the \bcr as a ranking statistic, taking a step forward to building a unified Bayesian framework to search for candidates and estimate their parameters.
+In this work, we utilise Bayesian inference to calculate the significance of high-mass candidate events in O2 by using the \bcr as a ranking statistic, taking a step toward building a unified Bayesian framework to search for candidates and estimate their parameters.
 
@@
 
-\footnotetext{\textit{Triggers} are points in time when the matched-filter SNR is greater than a threshold value for a given gravitational wave template~\cite{pycbc_og1}.}
+\footnotetext{\textit{Triggers} are points in time when the matched-filter SNR is larger than a threshold value for a given gravitational wave template~\cite{pycbc_og1}.}
 
@@
 
-Whenever a local maximum of $\pycbcstat > \snr_\text{T}$, where $\snr_\text{T}$ is some threshold value, the search pipeline produces a single-detector trigger associated with the detector and time where the apparent signal in the data has its merger~\cite{pycbc_og6}.
+Whenever a local maximum of $\pycbcstat > \snr_\text{T}$, where $\snr_\text{T}$ is some threshold value, the \pycbc search pipeline produces a single-detector trigger associated with the detector and time where the apparent signal in the data has its merger~\cite{pycbc_og6}.
 
-For \pycbc to consider a trigger to be a \textit{candidate trigger}, a trigger from astrophysical origins, the trigger must be observed between detectors with the same template and a time of arrival difference less than the gravitational-wave travel time~\cite{pycbc_og1}.
+For \pycbc to consider a trigger to be a \textit{candidate trigger}, a trigger that may be from astrophysical origins, the trigger must be observed between detectors with the same template and a time of arrival difference less than the gravitational-wave travel time~\cite{pycbc_og1}.
 To test its search, \pycbc also conducts searches for \textit{simulated triggers}, artificial triggers manufactured by injecting signals into the detector data.
@@
 These background triggers are coherent signal-free events, constructed by applying relative offsets, or time-slides, between the data of different detectors~\cite{pycbc_og6}.
-Note that the time-slides to generate the background triggers are greater than the gravitational-wave travel time between detectors to ensure that the background triggers are not of astrophysical origins.
+The time-slides to generate the background triggers are greater than the gravitational-wave travel time between detectors to ensure that the background triggers are not of astrophysical origins.
 
@@
 We expect the background trigger and simulated signal \bcr values to favour the incoherent glitch and the coherent signal hypothesis, respectively.
-Ideally these distributions that represent two unique populations should be distinctly separate and have no overlap in their \bcr values.
+Ideally, these distributions representing two unique populations should be distinctly separate and have no overlap in their \bcr values.
 The prior odds parameters $\alpha$ and $\beta$ from Eq.~\ref{eq:bcr} help separate the two distributions.
@@
 Candidate event \bcr values will either be statistically insignificant compared to the background triggers, implying the candidate is a glitch, or statistically significant to the background distribution, indicating the possible presence of an astrophysical signal.
-To quantify the level of significance we can calculate a false alarm probability with trial factors \fap for the candidate events.
-The \fap tells us how probable it is for the candidate event to be falsely identified as a signal.
+To quantify the significance level, we can calculate a false alarm probability with trial factors \fap for the candidate events.
+The \fap is the probability that a candidate event originating from a non-astrophysical source can be is falsely identified as a signal.
 
@@
 Some candidate events were vetoed to be glitches, while others were rejected due to their low significance.
-The data is divided into these time-frames because the detector's sensitivity does not stay constant throughout 8 month long observing period.
+The data is divided into these time-frames because the detector's sensitivity does not stay constant throughout the eight-month-long observing period.
 
@@
 
-The most computationally intensive step during Bayesian inference is the evaluation of the likelihood $\mathcal{L}(d_i|\template)$.
+The most computationally intensive step during Bayesian inference is evaluating the likelihood $\mathcal{L}(d_i|\template)$.
 To accelerate our analysis, we use a likelihood that explicitly marginalises over coalescence time, phase at coalescence, and luminosity distance (Eq.~80 from~\citet{intro_to_gw_bayes}).
@@
 The luminosity distance prior assigns probability uniformly in comoving volume, with an upper cutoff of $5\ \text{Gpc}$.
-The full list of the priors, along with their shapes, limits and boundary conditions can be found in Table~\ref{tab:priors}.
+The full list of the priors, along with their shapes, limits and boundary conditions are documented in Table~\ref{tab:priors}.
 
@@
 The waveform template we utilise is \imrphenomp, a phenomenological waveform template constructed in the frequency domain that models the in-spiral, merger, and ringdown (IMR) of a compact binary coalescence~\citep{khan2016frequency}.
-Although gravitational wave templates such as \seob~\cite{seobnrv4phm} which incorporate more physics, such as information on higher-order modes, we still use \imrphenomp as it is inexpensive compared to waveforms fitted
-against numerical-relativity simulations.
+Although gravitational wave templates such as \seob~\cite{seobnrv4phm} which incorporate more physics, such as information on higher-order modes, we still use \imrphenomp as it is inexpensive compared to waveforms fitted against numerical-relativity simulations.
 
-To generate the PSD, we take 31 neighbouring, off-source, non-overlapping,  4-second  segments of time-series data prior to the data segment $d_i$ being analysed.
-Off-soure data is used to avoid the inclusion of a signal in the PSD calculation.
-A Tukey window with a roll off of 0.2-seconds is applied to each data segment to suppress spectral leakage after which the segments are fast-Fourier transformed and median-averaged to create a PSD~\cite{ligo_psd}.
-This method, like other PSD estimation methods, adds statistical uncertainties to the PSD~\cite{psd_student_t, chatziioannou2019noise}.
-To marginalise over the statistical uncertainty we use the median-likelihood presented by~\citet{psd_student_t} as a post-processing step and shift our Bayesian Evidence estimations closer to their true astrophysical values.
+We take 31 neighbouring, off-source, non-overlapping,  4-second  segments of time-series data before the analysis data segment $d_i$ to generate the PSD.
+We use off-source to avoid the inclusion of a signal in the PSD calculation.
+A Tukey window with 0.2-second roll-offs is applied to each data segment to suppress spectral leakage after which the segments are fast-Fourier transformed and median-averaged to create a PSD~\cite{ligo_psd}.
+Like other PSD estimation methods, this method adds statistical uncertainties to the PSD~\cite{psd_student_t, chatziioannou2019noise}.
+To marginalise over the statistical uncertainty, we use the median-likelihood presented by~\citet{psd_student_t} as a post-processing step and shift our Bayesian Evidence estimations closer to their astrophysical values.
 
 Finally, we neglect detector calibration uncertainty and acquire data from from the Gravitational Wave Open Science Center~\cite{GWOSC}.
-The data we use is the publicly accessible O2 strain data from the Hanford and Livingston detectors.
-To ensure the data is usable we verify that the analysis and PSD data are obtained when the detectors are  in ``Science Mode''.
-The data requisition and quality checks are conducted using \gwpy~\cite{gwpy}.
+The data we use is the publicly accessible O2 strain data from the Hanford and Livingston detectors, recorded while the detectors are in ``Science Mode''.
+We obtain the data using \gwpy~\cite{gwpy}.
 
 The run-time to calculate a single Bayesian evidence after using \dynesty with $1,000$ live points and $100$ walkers is usually between $1-12\ \text{hours}$ (where the run time is proportional to the SNR of the data segment).
-The creation of the PSDs and execution of the parameter estimation jobs are managed via \bilbypipe~\cite{bilby_pipe}.
+\bilbypipe orchestrates the creation of the PSDs and execution of the parameter estimation jobs~\cite{bilby_pipe}.
 
 \subsection{Assigning \pastro to candidate events}
-
 After the calculating the \bcr for the entire set of high-mass background and simulated triggers, we calculate probability distributions $p_b(\bcr)$ and $p_s(\bcr)$ for each 2-week time-frame of O2 data.
@@
 Figure~\ref{fig:bcrCdf} shows the \bcr distributions for the background triggers, simulated triggers and candidate events.
-The bulk of the background and simulated trigger distributions are separate but have a slight overlap due to some of the simulated signal's being very faint.
-This suggests that the \bcr can successfully distinguish signals from noise or glitches.
+The bulk of the background and simulated trigger distributions are separate but slightly overlap due to some of the simulated signal's being very faint.
+The separation suggests that the \bcr can successfully distinguish signals from noise or glitches.
 The vertical lines in Figure~\ref{fig:bcrCdf} displays the \bcr for gravitational wave candidate events.
@@
 \input{Data/results_table}
-
 We analyse the $60\ 996$ background, $5\ 146$ simulated, and $25$ foreground triggers reported by \pycbc's search of the data from the second observing run, restricting our analysis to the triggers that fall within our Bayesian prior space as described in Section~\ref{sec:method}.
@@
 In Table~\ref{tab:results}, we summarise the \pastrobcr, along with the \pastro of other pipelines for comparison.
-Note that although the various pipeline \pastro are not mathematically equivalent, by comparing pipeline \pastro values for a given event we can compare how significant each pipeline deems various candidates.
+Note that although the various pipeline \pastro are not mathematically equivalent, by comparing pipeline \pastro values for a given event, we can compare how significant each pipeline deems various candidates.
 
@@
 This candidate was reported to be excess power caused due noise appearing non-stationary between 60-200 Hz~\cite{GWTC1}.
-This candidate acts as an example of how $\pastrobcr$ may be utilised to not only to detect signals but also to eliminate terrestrial noise sources.
+This candidate acts as an example of how $\pastrobcr$ may be utilised  to eliminate terrestrial noise sources, in addition to detecting signals
 
 \subsection{IAS Events}
-Our analysis of the \av{double check that these fall in our search space!!} high-mass IAS events and candidates in O2 has resulted in three events (GW170202, GW170403, GW170425) with disfavourable $\pastrobcr<0.5$.
-Additionally, five events (GW170121, GW170304, GW170402, GW170727, GW170817A) and one candidate event (GWC170302) reported by IAS have $\pastrobcr>0.5$.
+Our analysis of the \av{double check that these fall in our search space!!} high-mass IAS events and candidates in O2 has resulted in three events with disfavourable $\pastrobcr<0.5$ (GW170202, GW170403, GW170425).
+On the other hand, five events (GW170121, GW170304, GW170402, GW170727, GW170817A) and one candidate event (170302) reported by IAS have $\pastrobcr>0.5$.
 
-Event candidates GW170727 and GWC170302 are of particular interest, with \pastrobcr of 0.94 and 0.73.
+GW170727 and 170302 are of particular interest, with \pastrobcr of 0.94 and 0.73.
 GW170727 was emitted from a black hole binary system with a source frame total mass $\approx 70\ \msun$.
-In addition to the high \pastrobcr reported by our study, \citet{IAS1} and \citet{pycbc_ogc_2} have also reported high \pastro values of 0.98 and 0.99.
-On the other hand, GWC170302 is a sub marginal-candidate reported by \cite{IAS1} with a \pastro of 0.45 appears to have a higher significance our analysis, resulting in a \pastrobcr of $0.73$.
+In addition to the high \pastrobcr reported by our study, \citet{IAS1} and \citet{pycbc_ogc_2} have also reported high \pastro values of 0.98 and 0.99, making it a viable gravitational-wave event candidate.
+Similarly, the sub-marginal-candidate 170302 reported by \cite{IAS1} with a \pastro of 0.45 appears to have a higher significance from our analysis, resulting in a \pastrobcr of $0.73$.
 
-\av{GW170202's component black holes have has source masses (23, 16) below that of our prior space which may be why it has a low \pastrobcr}
+\av{GW170202's component black holes have source masses (23, 16) below that of our prior space which may be why it has a low \pastrobcr}
 
@@
 \subsection{New Candidate Events}
-Although no clear detections were made with the \bcr, a marginal-candidate 170222 has been discovered with a \pastrobcr of $0.53$.
+Although no clear detections are made with the \bcr, a marginal-candidate 170222 has been discovered with a \pastrobcr of $0.53$.
 This candidate has its similar masses when compared to those of GWTC-1.
+The other candidates with \pastrobcr
 

### 2021-01-28 main.tex

@@
 \newcommand{\pastrobcr}{\fancytext{p_\text{astro}^{\text{BCR}}}}
+\newcommand{\untunedpastrobcr}{\fancytext{p_\text{astro}^{\text{BCR}\prime}}}
 \newcommand{\pastroext}{\fancytext{p_\text{astro}^{\text{ext}}}}
@@
 \input{Data/results_table}
-We analyse the $60\ 996$ background, $5\ 146$ simulated, and $25$ foreground triggers reported by \pycbc's search of the data from the second observing run, restricting our analysis to the triggers that fall within our Bayesian prior space as described in Section~\ref{sec:method}.
+We analyse the $60\ 996$ background, $5\ 146$ simulated, and $25$ candidate triggers reported by \pycbc's search of the data from the second observing run, restricting our analysis to the triggers that fall within our Bayesian prior space as described in Section~\ref{sec:method}.
 In addition to these triggers, we also analyse events and candidate events reported by GWTC-1 and the IAS group (note that some of these were identified as candidates by the \pycbc search).
@@
 Note that although the various pipeline \pastro are not mathematically equivalent, by comparing pipeline \pastro values for a given event, we can compare how significant each pipeline deems various candidates.
+The $\alpha$ and $\beta$ values utilised for each time-frame of O2 are reported in Appendix~\ref{apdx:alphabeta}
 
@@
 \subsection{IAS Events}
-Our analysis of the \av{double check that these fall in our search space!!} high-mass IAS events and candidates in O2 has resulted in three events with disfavourable $\pastrobcr<0.5$ (GW170202, GW170403, GW170425).
-On the other hand, five events (GW170121, GW170304, GW170402, GW170727, GW170817A) and one candidate event (170302) reported by IAS have $\pastrobcr>0.5$.
+Our analysis of the high-mass IAS events and candidates in O2 has resulted in three events with disfavourable $\pastrobcr<0.5$ (GWC170402, GW170403, GW170425), and four events and one candidate with $\pastrobcr\geq0.5$ (GW170121, 170302, GW170304, GW170727, GW170817A).
 
-GW170727 and 170302 are of particular interest, with \pastrobcr of 0.94 and 0.73.
+GWC170402, detected by \citet{IAS2}, is reported to have a signal that is not described well by waveforms for circular binaries with aligned spins.
+Hence, we might have received a low \pastrobcr due to our usage of \imrphenomp, a waveform that does not account for eccentricity.
+Additionally, the search conducted by \citet{IAS2} was a single-detector search.
+Our ranking statistic relies on the signal to appear coherent, even if just faintly coherent, amongst the various detectors to have a high \pastrobcr.
+Hence, the lack of coherence and the non-eccentric waveform may be the leading factors for a low \pastro.
+GW170403 and GW170425 which have $\pastrobcr<0.35$ also have low  \pastro reported by \citet{pycbc_ogc_2},  suggesting that these events may have been false alarms.
+
+From the candidates with $\pastrobcr>0.5$, GW170727 and 170302 are of particular interest, with \pastrobcr of $0.92$ and $0.63$.
 GW170727 was emitted from a black hole binary system with a source frame total mass $\approx 70\ \msun$.
 In addition to the high \pastrobcr reported by our study, \citet{IAS1} and \citet{pycbc_ogc_2} have also reported high \pastro values of 0.98 and 0.99, making it a viable gravitational-wave event candidate.
-Similarly, the sub-marginal-candidate 170302 reported by \cite{IAS1} with a \pastro of 0.45 appears to have a higher significance from our analysis, resulting in a \pastrobcr of $0.73$.
+Similarly, the sub-marginal-candidate 170302 reported by \cite{IAS1} with a \pastro of 0.45 appears to have a higher significance from our analysis, resulting in a \pastrobcr of $0.63$.
 
-\av{GW170202's component black holes have source masses (23, 16) below that of our prior space which may be why it has a low \pastrobcr}
-
-\av{Interesting that GW170817A has high \pastrobcr as IAS2's pipeline works well on single detector events (marginal in other detectors)}
-
-\av{why do IAS2:GW170425 and IAS2:GW170402 have low \pastro?}
+% \av{Interesting that GW170817A has high \pastrobcr as IAS2's pipeline works well on single detector events (marginal in other detectors)}
 
 \subsection{New Candidate Events}
-Although no clear detections are made with the \bcr, a marginal-candidate 170222 has been discovered with a \pastrobcr of $0.53$.
+Although no clear detections are made with the \bcr, a marginal-candidate 170222 has been discovered with a $\pastrobcr\sim0.5$.
 This candidate has its similar masses when compared to those of GWTC-1.
-The other candidates with \pastrobcr
+The remaining coherent trigger candidates all have $\pastrobcr\ll0.5$ making them unlikely to originate from astrophysical sources.
 
@@
 Additionally, to further improve the method's infrastructure, we can use more robust gravitational wave templates (such as templates that incorporate higher-order modes), and sophisticated glitch models.
-Future analysis can also incorporate data from all available detectors in a network to increase the \pastro's sensitivity.
+Future analysis can also incorporate data from all available detectors in a network to increase the sensitivity of \pastrobcr.
 The BCR can discern better whether a candidate is a coherent astrophysical candidate or an incoherent glitch with data from more detectors.
@@
 
-\section{Tuning signal and glitch prior odds}
+\section{Tuned prior odds}\label{apdx:alphabeta}
 
-Table of the signal and glitch prior odds utilised for each section of data. One KL plot
+O2 lasted several months over which the detector's sensitivity varied.
+Hence, a part of our analysis entailed tuning the prior odds for obtaining a signal and a glitch, $\alpha$ and $\beta$, as described in Section~\ref{sec:method}.
+Table~\ref{tab:priorodds} presents the signal and glitch prior odds utilised for each time-frame of O2 data.
+\input{Data/alpha_beta_table}
 
-\section{Posteriors}
+Tuning the prior odds can dramatically affect the \pastrobcr.
+For example, consider Table~\ref{tab:tuningresults}, which reports tuned \pastrobcr and un-tuned \untunedpastrobcr (where $\alpha=1$ and $\beta=1$) for various high-mass events and candidates.
+By tuning the prior odds, the \pastrobcr for some IAS events (for example, GW170403 and GW170817A) can change by more than 0.5, resulting in a candidate being promoted/demotion of candidate significance.
+\input{Data/tuning_results_table}
 

### 2021-01-28 scripts/make_template_plot.py
add accepted events

@@ -1,9 +1,10 @@
 import numpy as np
-from tqdm import tqdm
-from bilby.gw import conversion
 import pandas as pd
+from bilby.gw import conversion
 from matplotlib import pyplot as plt
 from matplotlib import rcParams
+from tqdm import tqdm
+
 rcParams["font.size"] = 20
 rcParams["font.family"] = "serif"
 rcParams["font.sans-serif"] = ["Computer Modern Sans"]
@@ -11,8 +12,6 @@ rcParams["text.usetex"] = False
 rcParams['axes.labelsize'] = 30
 rcParams['axes.titlesize'] = 30
 rcParams['axes.labelpad'] = 20
-
-
 
 BANK = "../data/template_bank.csv"
 CATALOG = "../data/catalog.csv"
@@ -57,52 +56,65 @@ def contour_condition(m1: float, m2: float, mc: float, q: float, M: float) -> in
     :return: 1 if above parameters inside criteria (defined in function), otherwise 0
     """
     if (
-        31 <= m1 <= 491
-        and 1.32 <= m2 <= 121
-        and 0.01 <= q <= 0.98
-        and 8 <= mc <= 174
-        and 56 <= M <= 496
+            31 <= m1 <= 491
+            and 1.32 <= m2 <= 121
+            and 0.01 <= q <= 0.98
+            and 8 <= mc <= 174
+            and 56 <= M <= 496
     ):
         return 1
     else:
         return 0
 
-    
-    
+
+def get_event_status(catalogue_df):
+    data = []
+    for rowid, event in catalogue_df.iterrows():
+        m1 = event.mass_1_source
+        m2 = event.mass_2_source
+        mc = conversion.component_masses_to_chirp_mass(m1, m2)
+        M = conversion.component_masses_to_total_mass(m1, m2)
+        q = conversion.component_masses_to_mass_ratio(m1, m2)
+        data.append({'event': event.commonName,
+                     'catalog': event["catalog.shortName"],
+                     'in_prior': contour_condition(m1, m2, mc, q, M) == 1,
+                     'm1_source': m1,
+                     'm2_source': m2,
+                     'M': M
+                     })
+    return pd.DataFrame(data)
+
+
 def plot_template_bank():
[…]

### 2021-01-28 main.tex
adjust language

@@
 For example, consider Table~\ref{tab:tuningresults}, which reports tuned \pastrobcr and un-tuned \untunedpastrobcr (where $\alpha=1$ and $\beta=1$) for various high-mass events and candidates.
-By tuning the prior odds, the \pastrobcr for some IAS events (for example, GW170403 and GW170817A) can change by more than 0.5, resulting in a candidate being promoted/demotion of candidate significance.
+By tuning the prior odds, the \pastrobcr for some IAS events (for example, GW170403 and GW170817A) can change by more than 0.5, resulting in the promotion/demotion of a candidate's significance.
 \input{Data/tuning_results_table}

### 2021-01-28 scripts/make_template_plot.py

@@ -168,23 +168,3 @@ def main():
 
 if __name__ == "__main__":
     main()
-
-
-2017-01-22  & 1.00E+00 & 2.33E-02 \\
-2017-02-03  & 4.09E-10 & 6.25E-01 \\
-2017-02-12  & 1.76E-08 & 9.54E-02 \\
-2017-02-20  & 6.55E-10 & 2.22E-03 \\
-2017-02-28  & 1.00E-10 & 5.96E-02 \\
-2017-03-10  & 2.56E-10 & 2.44E-01 \\
-2017-03-18  & 1.60E-10 & 1.00E+00 \\
-2017-03-27  & 4.29E-09 & 2.22E-03 \\
-2017-04-04  & 1.00E+00 & 2.33E-02 \\
-2017-04-14  & 1.05E-09 & 2.44E-01 \\
-2017-04-23  & 2.68E-09 & 1.46E-02 \\
-2017-05-08  & 1.00E+00 & 2.44E-01 \\
-2017-06-18  & 2.81E-08 & 2.22E-03 \\
-2017-06-30  & 6.55E-10 & 1.53E-01 \\
-2017-07-15  & 1.05E-09 & 9.54E-02 \\
-2017-07-27  & 1.00E+00 & 4.29E-09 \\
-2017-08-05  & 2.12E-04 & 3.73E-02 \\
-2017-08-13  & 2.81E-08 & 1.39E-03 \\

### 2021-01-28 main.tex
Updates from Overleaf

@@
 For example, consider Table~\ref{tab:tuningresults}, which reports tuned \pastrobcr and un-tuned \untunedpastrobcr (where $\alpha=1$ and $\beta=1$) for various high-mass events and candidates.
-By tuning the prior odds, the \pastrobcr for some IAS events (for example, GW170403 and GW170817A) can change by more than 0.5, resulting in the promotion/demotion of a candidate's significance.
+By tuning the prior odds, the \pastrobcr for some IAS events (for example, GW170403 and GW170817A) can change by more than 0.5, resulting in the candidate being promoted/demotion of candidate significance.
 \input{Data/tuning_results_table}

### 2021-01-28 scripts/make_bcr_cdf.py
add plotting scripts

@@ -1,26 +1,61 @@
-# -*- coding: utf-8 -*-
-"""Module one liner
+from bcr_pipeline.post_processing.bcr_plotting.main_analysis_plots import \
+    pack_plotting_data
+from bcr_pipeline.post_processing.bcr_plotting.make_ranking_stat_probability_plot import (
+    _add_rank_pdf, add_foreground_events_to_plot)
+from matplotlib import pyplot as plt
+from matplotlib import rcParams
+from matplotlib.lines import Line2D
 
-This module does what....
+rcParams["font.size"] = 30
+rcParams["font.family"] = "serif"
+rcParams["font.sans-serif"] = ["Computer Modern Sans"]
+rcParams["text.usetex"] = True
+rcParams['axes.labelsize'] = 30
+rcParams['xtick.labelsize'] = 25
+rcParams['ytick.labelsize'] = 25
+rcParams['axes.titlesize'] = 30
+rcParams['axes.labelpad'] = 10
 
-Example usage:
-
-"""
-import numpy as np
-import matplotlib.pyplot as plt
+BANK = "../data/template_bank.csv"
+INJECTION = "../data/chunk21_res/injection_res.csv"
+BACKGROUND = "../data/chunk21_res/background_res.csv"
+FOREGROUND = "../data/chunk21_res/foreground_res.csv"
+CATALOG = "../data/catalog.csv"
 
 
 def plot():
-    """Plots a scatter plot."""
-    sample_x = np.random.normal(4, 0.1, 500)
-    sample_y = np.random.normal(4, 0.1, 500)
-    fig, ax = plt.subplots()
-    ax.plot(sample_x, sample_y, '.')
-    fig.show()
+    plot_data = pack_plotting_data(
+        foreground_csv=FOREGROUND,
+        background_csv=BACKGROUND,
+        injection_csv=INJECTION,
+        rank='lnBCR',
+        alpha=1.0e-6,
+        beta=1.0e-4,
+    )
+    xrange = dict(min=-15, max=30)
+    fig, ax_cdf = plt.subplots(nrows=1, ncols=1, figsize=(7, 5))
+    cdf_data = _add_rank_pdf(plot_data, xrange, ax_cdf, cdf=True)
+    add_foreground_events_to_plot(ax_cdf, plot_data['foreground']['df'],
+                                  x_vals=cdf_data['bins'],
+                                  y_vals=cdf_data['background_counts'],
[…]

### 2021-01-28 scripts/make_template_plot.py

@@ -14,6 +14,9 @@ rcParams['axes.titlesize'] = 30
 rcParams['axes.labelpad'] = 20
 
 BANK = "../data/template_bank.csv"
+INJECTION = "../data/chunk14/injection_triggers.csv"
+BACKGROUND = "../data/chunk14/background_triggers.csv"
+FOREGROUND = "../data/chunk14/foreground_triggers.csv"
 CATALOG = "../data/catalog.csv"
 
 
@@ -56,11 +59,11 @@ def contour_condition(m1: float, m2: float, mc: float, q: float, M: float) -> in
     :return: 1 if above parameters inside criteria (defined in function), otherwise 0
     """
     if (
-            31 <= m1 <= 491
-            and 1.32 <= m2 <= 121
-            and 0.01 <= q <= 0.98
-            and 8 <= mc <= 174
-            and 56 <= M <= 496
+            26 <= m1 <= 500
+            and 1.1 <= m2 <= 115
+            and 0.01 <= q <= 0.99
+            and 7 <= mc <= 166
+            and 47 <= M <= 500
     ):
         return 1
     else:
@@ -87,20 +90,45 @@ def get_event_status(catalogue_df):
 
 def plot_template_bank():
     template_bank = pd.read_csv(BANK, index_col=0)
+    foreground = pd.read_csv(FOREGROUND, index_col=False)
+    background = pd.read_csv(BACKGROUND, index_col=False)
+    injection = pd.read_csv(INJECTION, index_col=False)
+
+    print(injection[['mass_1', 'mass_2', 'mass_total', 'mass_chirp', 'mass_ratio']].describe().transpose()[['min','max']])
+    print(background[['mass_1', 'mass_2', 'mass_total', 'mass_chirp',
+                     'mass_ratio']].describe().transpose()[['min','max']])
 
     scatter_points = [
         # TEMPLATE BANK
         dict(
             data=template_bank,
             plot_kwargs=dict(
-                color="pink", s=0.5, marker=".", alpha=0.1, label="Template Bank"
+                color="pink", s=0.2, marker=".", alpha=0.2, label="Template Bank"
             ),
         ),
         # ALL CATALOGUE EVENTS
+        # dict(
+        #     data=pd.DataFrame(dict(mass_1=catalogs_df.mass_1_source,
+        #                            mass_2=catalogs_df.mass_2_source)),
+        #     plot_kwargs=dict(color="skyblue", s=5, marker="o", label="Catalogue Events"),
+        # ),
         dict(
[…]

### 2021-01-28 scripts/make_bcr_cdf.py
add cdf changes

@@ -1,7 +1,7 @@
 from bcr_pipeline.post_processing.bcr_plotting.main_analysis_plots import \
     pack_plotting_data
 from bcr_pipeline.post_processing.bcr_plotting.make_ranking_stat_probability_plot import (
-    _add_rank_pdf, add_foreground_events_to_plot)
+    _add_rank_pdf)
 from matplotlib import pyplot as plt
 from matplotlib import rcParams
 from matplotlib.lines import Line2D
@@ -35,19 +35,44 @@ def plot():
     xrange = dict(min=-15, max=30)
     fig, ax_cdf = plt.subplots(nrows=1, ncols=1, figsize=(7, 5))
     cdf_data = _add_rank_pdf(plot_data, xrange, ax_cdf, cdf=True)
-    add_foreground_events_to_plot(ax_cdf, plot_data['foreground']['df'],
-                                  x_vals=cdf_data['bins'],
-                                  y_vals=cdf_data['background_counts'],
-                                  make_annotation=False,
-                                  plot_x=False)
     ax_cdf.set_ylim(0, 1)
     ax_cdf.set_ylabel('1-CDF', fontsize="x-large")
     ax_cdf.set_xlabel(r'$\rho_{\mathrm{BCR}}$', fontsize="x-large")
-    labels = ["Background Triggers", "Simulated Triggers", "GW170814", "GW170817A"]
-    colors = ["#d8d8d8", "#daf0f8", "#0173b2", "#e9b457"]
-    custom_lines = [Line2D([0], [0], color=c, lw=4) for c in colors]
-    l = ax_cdf.legend(custom_lines, labels, fontsize="large",
-                      bbox_to_anchor=(1, 1), loc="upper left", frameon=False)
+
+
+    for idx, x_in_q in plot_data['foreground']['df'].iterrows():
+        c = 'orange'
+        xval = x_in_q["data"]
+        event_txt = x_in_q["trigger_label"].split(":")[1]
+        ax_cdf.axvline(x=xval, color=c)
+        ax_cdf.annotate(
+            event_txt, xy=(xval, 1), ha='left', va='top', rotation=-90,
+            color="#ff8c00", fontweight="extra bold", fontfamily='sans-serif')
+
+    # add_foreground_events_to_plot(ax_cdf, plot_data['foreground']['df'],
+    #                               x_vals=cdf_data['bins'],
+    #                               y_vals=cdf_data['background_counts'],
[…]

### 2021-01-28 scripts/make_bcr_cdf.py
make plots pretty

@@ -6,15 +6,32 @@ from matplotlib import pyplot as plt
 from matplotlib import rcParams
 from matplotlib.lines import Line2D
 
+
 rcParams["font.size"] = 30
 rcParams["font.family"] = "serif"
 rcParams["font.sans-serif"] = ["Computer Modern Sans"]
 rcParams["text.usetex"] = True
 rcParams['axes.labelsize'] = 30
-rcParams['xtick.labelsize'] = 25
-rcParams['ytick.labelsize'] = 25
 rcParams['axes.titlesize'] = 30
 rcParams['axes.labelpad'] = 10
+rcParams['axes.linewidth'] = 2.5
+rcParams['axes.edgecolor'] = 'black'
+rcParams['xtick.labelsize'] = 25
+rcParams['xtick.major.size'] = 10.0
+rcParams['xtick.minor.size'] = 5.0
+rcParams['ytick.labelsize'] = 25
+rcParams['ytick.major.size'] = 10.0
+rcParams['ytick.minor.size'] = 5.0
+plt.rcParams['xtick.direction'] = 'in'
+plt.rcParams['ytick.direction'] = 'in'
+plt.rcParams['xtick.minor.width'] = 1
+plt.rcParams['xtick.major.width'] = 3
+plt.rcParams['ytick.minor.width'] = 1
+plt.rcParams['ytick.major.width'] = 2.5
+plt.rcParams['xtick.top'] = True
+plt.rcParams['ytick.right'] = True
+
+
 
 BANK = "../data/template_bank.csv"
 INJECTION = "../data/chunk21_res/injection_res.csv"
@@ -46,7 +63,7 @@ def plot():
         event_txt = x_in_q["trigger_label"].split(":")[1]
         ax_cdf.axvline(x=xval, color=c)
         ax_cdf.annotate(
-            event_txt, xy=(xval, 1), ha='left', va='top', rotation=-90,
+            event_txt, xy=(xval, 0.95), ha='left', va='top', rotation=-90,
             color="#ff8c00", fontweight="extra bold", fontfamily='sans-serif')
 
     # add_foreground_events_to_plot(ax_cdf, plot_data['foreground']['df'],
@@ -73,7 +90,7 @@ def plot():
     frame = l.get_frame()
     frame.set_linewidth(0)
 
-    fname = '../images/bcr_cdf.png'
+    fname = '../images/bcr_cdf_smaller_legend.png'
[…]

### 2021-01-28 scripts/make_template_plot.py

@@ -5,13 +5,29 @@ from matplotlib import pyplot as plt
 from matplotlib import rcParams
 from tqdm import tqdm
 
-rcParams["font.size"] = 20
+rcParams["font.size"] = 30
 rcParams["font.family"] = "serif"
 rcParams["font.sans-serif"] = ["Computer Modern Sans"]
-rcParams["text.usetex"] = False
+rcParams["text.usetex"] = True
 rcParams['axes.labelsize'] = 30
 rcParams['axes.titlesize'] = 30
-rcParams['axes.labelpad'] = 20
+rcParams['axes.labelpad'] = 10
+rcParams['axes.linewidth'] = 2.5
+rcParams['axes.edgecolor'] = 'black'
+rcParams['xtick.labelsize'] = 25
+rcParams['xtick.major.size'] = 10.0
+rcParams['xtick.minor.size'] = 5.0
+rcParams['ytick.labelsize'] = 25
+rcParams['ytick.major.size'] = 10.0
+rcParams['ytick.minor.size'] = 5.0
+plt.rcParams['xtick.direction'] = 'in'
+plt.rcParams['ytick.direction'] = 'in'
+plt.rcParams['xtick.minor.width'] = 1
+plt.rcParams['xtick.major.width'] = 3
+plt.rcParams['ytick.minor.width'] = 1
+plt.rcParams['ytick.major.width'] = 2.5
+plt.rcParams['xtick.top'] = True
+plt.rcParams['ytick.right'] = True
 
 BANK = "../data/template_bank.csv"
 INJECTION = "../data/chunk14/injection_triggers.csv"
@@ -141,7 +157,7 @@ def plot_template_bank():
     m2_range = [1, 200]
 
     fig, ax_m1m2 = plt.subplots(nrows=1, ncols=1,
-                                figsize=(12, 6))  # 3, 2
+                                figsize=(13, 6))  # 3, 2
 
     axis_label_kwargs = dict(fontsize="x-large")
 
@@ -154,7 +170,7 @@ def plot_template_bank():
     ax_m1m2.set_xscale("log")
 
     # set scale limits
-    ax_m1m2.set_xlim(m1_range[0], m1_range[1])
+    ax_m1m2.set_xlim(m1_range[0], m1_range[1]+100)
     ax_m1m2.set_ylim(m2_range[0], m2_range[1])
 
     # contour line
@@ -169,7 +185,7 @@ def plot_template_bank():
                         **scatter_data["plot_kwargs"])
 
[…]

### 2021-01-28 scripts/make_bcr_cdf.py
adjust xlabel for cdf

@@ -54,7 +54,7 @@ def plot():
     cdf_data = _add_rank_pdf(plot_data, xrange, ax_cdf, cdf=True)
     ax_cdf.set_ylim(0, 1)
     ax_cdf.set_ylabel('1-CDF', fontsize="x-large")
-    ax_cdf.set_xlabel(r'$\rho_{\mathrm{BCR}}$', fontsize="x-large")
+    ax_cdf.set_xlabel(r'ln $\rho_{\mathrm{BCR}}$', fontsize="x-large")
 
 
     for idx, x_in_q in plot_data['foreground']['df'].iterrows():

### 2021-01-28 scripts/make_template_plot.py
adjust trigger label

@@ -186,7 +186,7 @@ def plot_template_bank():
 
     bank_patch = ax_m1m2.scatter([], [], label="Template Bank", marker=".", color="pink")
     prior_patch, = ax_m1m2.plot([], [], label="Prior", linestyle="--", color="k")
-    fg_patch = ax_m1m2.scatter([], [], label="Foreground Triggers", marker="s", color="orange")
+    fg_patch = ax_m1m2.scatter([], [], label="Candidate Triggers", marker="s", color="orange")
     bg_patch = ax_m1m2.scatter([], [], label="Background Triggers", marker=".", color="gray")
     inj_patch = ax_m1m2.scatter([], [], label="Simulated Triggers", marker=".", color="skyblue")
     handles = [bank_patch, prior_patch, fg_patch, bg_patch, inj_patch]

### 2021-01-28 main.tex
add plotting scripts
Updates from Overleaf

--- 2021-01-28 main.tex
@@
 This changed with the detection of GW190521, a unique gravitational wave event that led to the formation of a black hole with a mass  $142\ \msun$, the first confirmed direct discovery of an intermediate-mass black hole~\cite{gw190521}.
-Although this is the first gravitational wave event leading to discovering a black hole with a mass in the intermediate range, ground-based gravitational wave detectors are sensitive to gravitational waves from even more massive systems to systems with a total mass of $400\ \msun$.
-\av{double check the following -- is this the most recent rate quote?} Additionally, gravitational waves from systems with masses greater than $100\ \msun$ systems should occur at a rate of $0-10\text{yr}^{-1}$~\cite{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions,ligo_imbh_search}.
-Hence, LIGO might have gravitational wave events from more intermediate-mass systems hidden in its data, potentially even in O2 data.
+Although this is the first gravitational wave event leading to discovering a black hole with a mass in the intermediate range, ground-based gravitational wave detectors are sensitive to gravitational waves from even more massive systems to systems with a total mass of $400\ \msun$~\cite{GWTC1}.
+Additionally, gravitational waves from systems with masses greater than $100\ \msun$ systems should occur at a rate of $0-10\text{yr}^{-1}$~\cite{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions,ligo_imbh_search}.
+\av{this is surely outdated...
+get more recent rate quote} Hence, LIGO might have gravitational wave events from more intermediate-mass systems hidden in its data, potentially even in O2 data.
 
@@
 
-\begin{figure}[!ht]
+\begin{figure*}[!ht]
 
-{\centering \includegraphics[width=0.75\linewidth]{images/template_bank_masses}
+{\centering \includegraphics[width=0.75\linewidth]{images/template_bank.png}
 
@@
 % 1178294418, May 08, 2017, 16:00 UTC
-\caption[High-mass BCR search space.]{The template bank used by \pycbc to search a section of O2 data from $\text{April 23 - May 8, 2017}$.
+\caption[High-mass BCR search space.]{The template bank (pink) used by \pycbc to search a section of O2 data from $\text{April 23 - May 8, 2017}$.
 Our search is constrained to the high-mass parameter space enclosed by the dashed line.
-\av{Update plot }}\label{fig:templateBank}
-\end{figure}
+The candidate, background and simulated triggers detected in this region of the parameter space during this period are plotted in orange, grey and blue respectively.
+}\label{fig:templateBank}
+\end{figure*}
 
@@
 \begin{figure}[!ht]
-{\centering \includegraphics[width=0.75\linewidth]{images/bcr_cdf} }
-\caption[BCR distribution example]{Histograms represent the survival function (1-CDF) from our selection of $\sim$ 3,000 background triggers (grey) and 648 simulated signals (blue) triggers obtained from \pycbc's search of data from $\text{April 23 - May 8, 2017}$.
-\av{change BCR to\bcr in axes labels}Vertical lines mark the ln BCRs of two glitches (orange and yellow), IAS's GW170121 (pink), and GWTC-1's GW170104 (dark blue) \av{this plot also doesn't add much, is it needed?}.}\label{fig:bcrCdf}
+{\centering \includegraphics[width=0.75\linewidth]{images/bcr_cdf_smaller_legend.png} }
+\caption[BCR distribution example]{Histograms represent the survival function (1-CDF) from our high-mass selection of background triggers (grey) and simulated signals (blue) triggers obtained from \pycbc's search of data from $\text{August 13 - 21, 2017}$.
+Vertical lines mark the $\text{ln}\ \bcr$ of IAS's GW170817 and GWTC-1's GW170814.}\label{fig:bcrCdf}
 \end{figure}
@@
 Table~\ref{tab:priorodds} presents the signal and glitch prior odds utilised for each time-frame of O2 data.
+\av{note: havent tuned all chunks yet -- and tbh the 'tuning' could be better, atm brute force searching a 2d log-spce grid}
 \input{Data/alpha_beta_table}
@@
 By tuning the prior odds, the \pastrobcr for some IAS events (for example, GW170403 and GW170817A) can change by more than 0.5, resulting in the promotion/demotion of a candidate's significance.
+
 \input{Data/tuning_results_table}

### 2021-02-10 authors.tex
Updates from Overleaf

@@
 G.~Ashton$^{\SPAno,\OzGravMonashno}$, %ORCID:0000-0001-7288-2231 
+T.~Alford$^\CITno$, 
+S.~Garza$^\CITno$,
+M.~Isi$^{\MITno,\Kavlino}$, %0000-0001-8040-9807
 J.~Kanner$^\CITno$, 
-T.~Alford$^\CITno$, 
-L.~Xiao$^\CITno$, %0000-0003-2703-449X
-M.~Isi$^{\MITno,\Kavlino}$, %0000-0001-8040-9807
-S.~Garza$^\CITno$, 
+T.J.~Massinger$^\CITno$,
+L.~Xiao$^\CITno$ %0000-0003-2703-449X
 }\vspace{0.2cm}\\

### 2021-03-10 authors.tex

--- 2021-01-18 authors.tex
@@
 
-%--------------------------
-\newcommand{\SPA}{School of Physics and Astronomy, Monash University, Clayton VIC 3800, Australia}
-\newcommand{\OzGravMonash}{OzGrav: The ARC Centre of Excellence for Gravitational Wave Discovery, Clayton VIC 3800, Australia}
-\newcommand{\MIT}{LIGO Laboratory, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
-\newcommand{\Kavli}{Department of Physics and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, \\ 77 Massachusetts Ave, Cambridge, MA 02139, USA}
-\newcommand{\CIT}{LIGO Laboratory, California Institute of Technology, Pasadena, CA 91125, USA}
-\author{
-\parbox{\textwidth}{
-A.~Vajpeyi$^{\SPAno,\OzGravMonashno}$, %ORCID:0000-0002-4146-1132
-R.~Smith$^{\SPAno,\OzGravMonashno}$, %ORCID:0000-0001-8516-3324
-E.~Thrane$^{\SPAno,\OzGravMonashno}$, %0000-0002-4418-3895
-G.~Ashton$^{\SPAno,\OzGravMonashno}$, %ORCID:0000-0001-7288-2231 
-J.~Kanner$^\CITno$, 
-T.~Alford$^\CITno$, 
-L.~Xiao$^\CITno$, %0000-0003-2703-449X
-M.~Isi$^{\MITno,\Kavlino}$, %0000-0001-8040-9807
-S.~Garza$^\CITno$, 
-}\vspace{0.2cm}\\
-$^1$\SPA\\
-$^2$\OzGravMonash\\
-$^3$\CIT\\
-$^4$\MIT\\
-$^5$\Kavli\\
-}
+% %--------------------------
+% \newcommand{\SPA}{School of Physics and Astronomy, Monash University, Clayton VIC 3800, Australia}
+% \newcommand{\OzGravMonash}{OzGrav: The ARC Centre of Excellence for Gravitational Wave Discovery, Clayton VIC 3800, Australia}
+% \newcommand{\MIT}{LIGO Laboratory, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
+% \newcommand{\Kavli}{Department of Physics and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, \\ 77 Massachusetts Ave, Cambridge, MA 02139, USA}
+% \newcommand{\CIT}{LIGO Laboratory, California Institute of Technology, Pasadena, CA 91125, USA}
+
+% \author{
+% \parbox{\textwidth}{
+% A.~Vajpeyi$^{\SPAno,\OzGravMonashno}$, %ORCID:0000-0002-4146-1132
+% R.~Smith$^{\SPAno,\OzGravMonashno}$, %ORCID:0000-0001-8516-3324
+% E.~Thrane$^{\SPAno,\OzGravMonashno}$, %0000-0002-4418-3895
+% G.~Ashton$^{\SPAno,\OzGravMonashno}$, %ORCID:0000-0001-7288-2231 
+% T.~Alford$^\CITno$, 
+% S.~Garza$^\CITno$,
+% M.~Isi$^{\MITno,\Kavlino}$, %0000-0001-8040-9807
+% J.~Kanner$^\CITno$, 
+% T.J.~Massinger$^\CITno$,
+% L.~Xiao$^\CITno$ %0000-0003-2703-449X
+% }\vspace{0.2cm}\\
+% $^1$\SPA\\
+% $^2$\OzGravMonash\\
+% $^3$\CIT\\
+% $^4$\MIT\\
+% $^5$\Kavli\\
+% }
+
+\author[\SPAno,\OzGravMonashno]{A.~Vajpeyi}
+\author[\SPAno,\OzGravMonashno]{R.~Smith}
+\author[\SPAno,\OzGravMonashno]{E.~Thrane}
+\author[\SPAno,\OzGravMonashno]{G.~Ashton}
+\author[\CITno]{T.~Alford}
+\author[\CITno]{S.~Garza}
+\author[\MITno, \Kavlino]{M.~Isi}
+\author[\CITno]{J.~Kanner}
+\author[\CITno]{T.J.~Massinger}
+\author[\CITno]{L.~Xiao}
+
+\affil[\SPAno]{School of Physics and Astronomy, Monash University, Clayton VIC 3800, Australia}
+\affil[\OzGravMonashno]{OzGrav: The ARC Centre of Excellence for Gravitational Wave Discovery, Clayton VIC 3800, Australia}
+\affil[\MITno]{LIGO Laboratory, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
+\affil[\Kavlino]{Department of Physics and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, \\ 77 Massachusetts Ave, Cambridge, MA 02139, USA}
+\affil[\CITno]{LIGO Laboratory, California Institute of Technology, Pasadena, CA 91125, USA}

### 2021-03-10 main.tex

@@
 \usepackage{graphicx} % Include figure files
+% \usepackage{authblk}
+
 \graphicspath{{images/}} %Setting the graphicspath
@@
 
-\title{A Bayesian ranking statistic to find \\high-mass black holes in LIGO data}
+\title{A Bayesian ranking statistic to find high-mass black holes in LIGO--Virgo data}
 
-% \author{Author list TBD}
-\input{authors}
+% \input{authors}
+%\author[1]{Test}
+%\affil[1]{Test Affil}
 
@@
 The detection of intermediate-mass black holes ( $10^2-10^6$~\msun) will shed light on the formation of supermassive black holes and thus galaxy formation.
-Although LIGO is sensitive to the merger of binary black holes with total masses up to $400$~\msun, only 4 of their 50 detections have a total mass $>100$~\msun.
+Although LIGO is sensitive to the merger of binary black holes with total masses up to $400$~\msun, only 4 of their 50 detections have a total mass $>100$~\msun with >95\% credibility.
 A possible explanation for the absence of intermediate-mass events may be their misclassification as short-duration instrumental noise transients.
 Short-duration instrumental transients mimic the short-duration gravitational-wave signals from intermediate-mass binary black hole mergers.
-Here we demonstrate that a ranking statistic utilising Bayesian inference could be a more sensitive tool for detecting high-mass binary black hole mergers (systems with a total mass $>55$~\msun) compared to a traditional match-filter ranking statistic.
-We applied this technique on the high-mass triggers during LIGO's second observing run to investigate the possibility of discovering new gravitational-wave signals from high mass black hole binaries and re-calculate the significance of high-mass candidate events.
-Although our analysis does not discover new gravitational wave events, it does provide a Bayesian measure of various candidates and events.
+\et{I think the preceding text is misleading.
+We make it sound like we expect a uniform distribution of total mass, and so it's a surprising that we don't see IMBH.
+However, in reality, it is theoretically challenging to make IMBH.
+You need an exceptionally massive progenitor star to avoid pair instability supernova.
+Or, maybe you can make IMBH from hierarchical mergers or accretion.
+No one expects them to be common, but they are  interesting because of their connection to supermassive black holes.
+I suggest rewriting the preceding text to explain how IMBH might form and why they are interesting to look for.}
+Here we demonstrate a ranking statistic utilising Bayesian inference for the detection of high-mass binary black hole mergers (with a total mass $>55$~\msun).
+\et{Claims of beating matched filtering not yet borne out.} We apply this technique on the high-mass triggers during LIGO's second observing run to search for previously unresolved gravitational-wave signals from high-mass binary black holes.
+Our analysis does not discover new gravitational-wave events.
+However, we find support for some previously identified borderline detections.
+\et{Don't oversell Bayesian measure since our method is only semi-Bayesian.}
 \end{abstract}
@@
 %%%%%%---SECTIONS---%%%%%%%%%%%%
+\section{New Intro}
+In the 1960s, X-ray and optical observations from the Cyg-X1 binary star system led to the discovery of the first stellar-mass black hole~\cite{}.
+Shortly afterwards, in 1974, kinematic measurements of stars near the center of our galaxy demonstrated the presence of a supermassive black hole of mass $10^6\ \text{M}_{\odot}$ -- Sag A$^*$~\cite{}.
+These two detections firmly established the existence of stellar-mass
+black holes $\text{M}_\text{BH} < 10^{2} \ \text{M}_{\odot}$ and
+supermassive black holes, $\text{M}_\text{BH} > 10^{5} \ \text{M}_{\odot}$ in our universe.
+Since then, astronomers accumulated more definitive evidence for stellar-mass and supermassive black holes.
+However, a gap in between the mass-ranges of these two categories began to form: there is a deficiency of black holes in the intermediate-mass range $10^{2} - 10^{5}\ \text{M}_{\odot}$.
+These intermediate-mass black holes must have existed to form the supermassive black holes detected to exist in the early universe~\cite{}.
+However, we only have a handful of candidates and one confirmed intermediate-mass black hole~\cite{}.
+The study and discovery of intermediate-mass black holes will help bridge the gap and provide a pathway to forming supermassive black holes.
+
+Intermediate-mass black holes may form various scenarios ranging from hierarchical mergers of stellar-mass black holes to large metal-free stars' direct collapse.
+Hierarchical mergers in active galactic nuclei migration-traps, globular and stellar clusters may be a feasible method for black holes to accumulate mass and reach the intermediate-mass range.
+However, when black holes merge, they can receive recoil-kicks up to $\sim$2,500 km/s.
+Hence, the merger remnants require their recoil kick to be less than its environment's escape velocity to undergo successive mergers.
+This tight constraint makes hierarchical mergers a challenging scenario.
+
+Another pathway to form intermediate-mass black involves the direct collapse of massive, metal-free Population III stars.
+Typically, massive stars $> 100 \ \msun$ can eject more than half of their mass in the form of radiatively driven stellar winds.
+However, at zero metallicity, mass loss through stellar winds is negligible (Kudritzki 2000).
+Hence,  Population III stars have the opportunity to complete their life-cycles without losing a significant portion of their mass.
+Moreover, Population III stars with masses above $230 \ \msun$ will avoid electron-positron pair-instability.
+Consequently, oxygen and silicon burning will not drive an explosion, allowing the star to undergo a complete collapse to leave behind an intermediate-mass black hole remnant with a mass of $120-280 \ \msun$, dependant on the initial star mass (Bond et al.
+1984).
+The intermediate-mass black holes that form as remnants of these large Population III stars may exist today in clusters located at the galaxies' bulges.
+If these bulges contain intermediate-mass black holes, they could also provide evidence for Population III stars' existence.
+
+As there is inadequate observational evidence for intermediate-mass black holes, it is challenging to state which formation path is favoured.
+However, the observational work does allude to the existence of intermediate-mass black holes.
+The search for intermediate-mass black holes is underway using direct kinematic measurements, reverberation mapping, studying luminosity from low-luminous active galactic nuclei and Ultraluminous X-ray Sources.
+
+Dynamic measurements of individual sources orbiting an intermediate-mass black hole is that the sphere of influence too small to resolve motions.
+Can only be used on close sources.
+The issue with reverberation mapping and the other EM spectra, cant be sure of anisotropic emission, non-linear emission.
+large uncertainties.
+\url{https://iopscience.iop.org/article/10.3847/2041-8213/ab745b}
+
+The most promising avenues to find $100−1000\ \msun$ black holes are either to identify stellar binaries, which are expected to be common or to detect them in gravitational radiation.
+Ground-based gravitational wave limits on the low end of this mass regime are continuing to improve.
+
+LIGO found 190521, can find more if we are more sensitive, and if we can better harness data
+
 \section{\label{sec:Introduction}Introduction}
@@
 As of January 2021, the LIGO Scientific Collaboration has confirmed $\sim50$ binary black hole systems and listed numerous candidate events~\cite{GWTC1, GWTC2, gracedb}.
-Additionally, since the public release of LIGO's first and second observing run's data (O1 and O2), several external groups, such as \pycbc~\cite{pycbc_code} and a research team at the Institute for Advanced Study (IAS)~\cite{IAS0, IAS1, IAS2}, have independently searched and identified additional binary black hole gravitational wave candidates.
-These various discoveries have firmly authenticated the existence of stellar-mass black holes, supermassive black holes and binary black hole systems.
+Additionally, since the public release of LIGO's first and second observing run's data (O1 and O2), search pipelines such as \pycbc~\cite{pycbc_code} and a research team at the Institute for Advanced Study (IAS)~\cite{IAS0, IAS1, IAS2}, have independently identified additional binary black hole gravitational wave candidates.
 
-Until recently, there was no definitive evidence for intermediate-mass black holes, the black holes whose masses lie between that of stellar-mass and supermassive black hole systems ($10^2-10^6\ \msun$).
+\et{Add a paragraph here discussing basic ideas in IMBH theory.
+Explain why the are not easy to make.
+Discuss scenarios by which they can be made.
+Discuss the role they may play in the formation of supermassive BH.
+Then, we transition to the next paragraph about observational evidence.}
+
+Until recently, there was no definitive evidence for intermediate-mass black holes with a mass in between the range of stellar-mass and supermassive black holes ($10^2-10^6\ \msun$). 
+\et{There have been numerous claims of IMBH detection.
+The previous sentence is correct that there are no \textit{definitive} detections before GW190521, but the paragraph is misleading by omission.
+Insert here an exhaustive review of previous IMBH detection claims, noting who made the claim, the mass, and the method.}
 This changed with the detection of GW190521, a unique gravitational wave event that led to the formation of a black hole with a mass  $142\ \msun$, the first confirmed direct discovery of an intermediate-mass black hole~\cite{gw190521}.
-Although this is the first gravitational wave event leading to discovering a black hole with a mass in the intermediate range, ground-based gravitational wave detectors are sensitive to gravitational waves from even more massive systems to systems with a total mass of $400\ \msun$~\cite{GWTC1}.
-Additionally, gravitational waves from systems with masses greater than $100\ \msun$ systems should occur at a rate of $0-10\text{yr}^{-1}$~\cite{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions,ligo_imbh_search}.
-\av{this is surely outdated...
-get more recent rate quote} Hence, LIGO might have gravitational wave events from more intermediate-mass systems hidden in its data, potentially even in O2 data.
+Although this is the first gravitational-wave observation of an IMBH, ground-based gravitational wave detectors are sensitive to gravitational waves from even more massive systems with a total mass of up to $400\ \msun$~\cite{GWTC1}.
 
-However, even after conducting a targeted matched-filter based search for gravitational waves from intermediate-mass black holes in O2's data, the heaviest total mass detected so far is approximately $80\ \msun$~\cite{GWTC1,imbhbSearch2014, ligo_imbh_search}.
+\et{The following paragraph tries to solve a problem that doesn't exist: as noted in comments above, the absence of GWs from IMBH is not surprising.
+Delete or rewrite if you want to emphasise the difficulty in IMBH detection.}
 A possible explanation for the absence of intermediate-mass events may be due to their misclassification as short-duration instrumental noise transients known as glitches~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
@@
 
-One method to account for glitches while searching for gravitational waves from coalescing compact binaries is by utilising an astrophysical Bayesian odds~\cite{bci, BCR1, BCR2, bcr_gw151216, bayesian_odds}.
-A true Bayesian odds calculated without using bootstrap techniques can provide events with a more accurate significance that is agnostic to a specific search strategy~\cite{BCR2, bcr_gw151216,  bayesian_odds}.
-
-Additionally, Bayesian odds can include comprehensive astrophysical information in its calculation.
-For example, a Bayesian odds to help detect gravitational-wave candidates can incorporate information on if an event's binary system was precessing and if the signal contains higher-order modes and is coherent amongst various detectors.
-Because of the possibility of Bayesian methods to incorporate detailed physical information about a gravitational wave signal, the LIGO Scientific Collaboration uses Bayesian methods to determine the source parameters of gravitational-wave events~\cite{abbott2016ligo, GWTC1}.
-This paper demonstrates that the power of Bayesian methods used in parameter estimation can also discriminate between coherent gravitational-wave signals, incoherent glitches, and Gaussian noise in the form of a Bayesian odds, utilised as a ranking statistic.
-
+One method to account for glitches while searching for gravitational waves from coalescing compact binaries is by utilising the astrophysical Bayesian odds~\cite{bci, BCR1, BCR2, bcr_gw151216, bayesian_odds}.
+A true Bayesian odds, calculated without using bootstrap techniques, can provide more accurate estimate of significance that does note depend on the search pipeline~\cite{BCR2, bcr_gw151216,  bayesian_odds}.
 In this paper, we utilise a Bayesian method, called the Bayesian Coherence Ratio \bcr~\cite{BCR1}, to rank the candidate gravitational wave signals from high-mass compact binary coalescences (systems with total masses in the range of $55-500\ \msun$) in the detector data recorded during O2.
 Although the \bcr, utilising bootstrap techniques, does not provide the true Bayesian odds, it provides a more astrophysical measure of candidate events' significance than a traditional match-filter significance.
+\et{This pitch, that the method is ``a more astrophysical measure'' is unconvincing.
+(What does that even mean?) Chat with RS/ET to come up with a better pitch built around the idea that the detection statistic is built on Bayesian inferences results, and that it's a step toward fully Bayesian detection.}
 
-We find that (a) high-mass events reported in the GWTC-1, including GW170729 (an event with disputed \pastro amongst various search pipelines) have high significance; (b) high-mass events detected from the IAS group have differing levels of significance; and that (c) our ranking statistic does not identify any intermediate-mass black holes, but does identify an unreported stellar-mass binary black hole candidate, 170222.
+We find that (a) high-mass events reported in the GWTC-1, including GW170729 (the least significant event in GWTC-1) have high significance; (b) high-mass events detected from the IAS group have differing levels of significance; \et{differing from what?
+edit this passage to state more clearly that we find statistical support for some of their candidates, but not for others} and that (c) our ranking statistic does not identify any intermediate-mass black holes, but does identify an unreported stellar-mass binary black hole candidate, 170222 \et{State statistical significance.}.
 
 The remainder of this paper is structured as follows.
-We outline our methods, including details of the \bcr and the retrieval of our candidate events in Section~\ref{sec:method}.
+We outline our methods, including details of our ranking statistic and the retrieval of our candidate events in Section~\ref{sec:method}.
 We present details on the implementation of our analysis in Section~\ref{sec:Analysis}.
-Finally, we present our results in Section~\ref{sec:Results}, and discuss these results in the context of the significance of gravitational wave candidates in Section~\ref{sec:Conclusion}.
+Finally, we present our results in Section~\ref{sec:Results}, and discuss these results in the context of the significance of gravitational-wave candidates in Section~\ref{sec:Conclusion}.
+
+\subsection{Notes for motivation}
+\begin{itemize}
+    \item if truly Bayesian -- then its more astrophysical 
+    \item we're focused on odds -- but using it as a ranking statistic
+    \item GOAL: look for an IMBH, not to perfect the statistic     
+    \item  detection statistic that is based on a Bayesian approach -- a different way of looking for IMBHs, in place of matched-filter
+    \item normal statistic -- is maximum likelihood appraach (highest SNR), this one marginalises over all the templates -- closer to an "odds" like goal
+    \item this is NOT BCR2, this is a ranking statistic 
+    \item between Isi et al and Ashton et al,  more like Ashton and not matched filtering 
+    \item we didnt do a full Ashton because (no need to argue why we didnt do this)
+    \item whats out there, where does this fit into lit, what are we doing vs not doing 
+    \item  reproduced all these other results 
+    \item new in this paper: using Bayesian coherence (an ingredient in Ashton et al) and looking for NEW signals in triggers, the PRatten et al looks at all the catalogued triggers. 
+\end{itemize}
+
+\begin{itemize}
+    \item  IMBH signals look a lot like glitches
+    \item  We compute \bcr which needs $\alpha$ $\beta$
+    \item  We don't know the true probability $P(\mathcal{H}_S), P(\mathcal{H}_I)$ 
+    \item hence we cannot take \bcr at face value because we dont know the true distributions of the above
+    \item Studying p(\bcr| d=background) p(\bcr| d=signals) gives us confidence to discriminate between signals and glitches
+    \item  we "rank" the BCR of foreground triggers based on that of background triggers which allows us to compute a frequentist estimator for its significance.
+\end{itemize}
+
+\section{New Method\label{sec:method}}
+
+The gravitational wave community uses Bayesian inference to perform parameter estimation and model selection.
+This work utilises Bayesian inference to calculate the significance of high-mass candidate triggers\footnote{\textit{Trigger:} point in time when the matched-filter SNR is larger than a threshold value for a given gravitational wave template~\cite{pycbc_og1}.
+\textit{Candidate Trigger:} trigger that may be from astrophysical origins.} in LIGO's second observing run.
+We calculate the significance of triggers using the Bayesian Coherence Ratio~\cite{BCR1}, \bcr, as a ranking statistic, a step toward building a unified Bayesian framework to search for candidates and estimate their parameters.
+
+\subsection{The Bayesian Coherence Ratio}
+
+Bayes theorem states that the posterior probability distribution $p(\parameters|d,\mathcal{H})$ for data $d$ and a vector of parameters \parameters that describe a model which quantifies a hypothesis $\mathcal{H}$, is given by
+\begin{equation}
+p(\parameters|d,\mathcal{H}) = \frac{\mathcal{L}(d|\parameters, \mathcal{H}) \ \pi(\parameters | \mathcal{H})}{\mathcal{Z}(d|\mathcal{H})}\ , 
+\end{equation}
+where $\mathcal{L}(d|\parameters, \mathcal{H})$ is the likelihood of the data given the parameters \parameters and the hypothesis, $\pi(\parameters | \mathcal{H})$ is the prior probability of the parameters, and finally,
+\begin{equation}
+    \mathcal{Z}(d|\mathcal{H}) = \int\limits_{\parameters} \ \mathcal{L}(d|\parameters,\mathcal{H}) \ \pi(\parameters | \mathcal{H}) \ d\parameters
+\end{equation} is the likelihood after marginalising over the parameters \parameters.
+To compare two hypotheses $\mathcal{H}_A$ and $\mathcal{H}_B$ with the Bayes theorem one can calculate an odds ratio
+\begin{equation}
+    \mathcal{O}^A_B = \frac{\mathcal{Z}^A\ \pi(\parameters^A)}{\mathcal{Z}^B\ \pi(\parameters^B)}\ ,
+\end{equation}
+where $\mathcal{Z}^A$ and $\mathcal{Z}^B$ are the shorthand for the evidences  $\mathcal{Z}(d|\mathcal{H}_A)$ and $\mathcal{Z}(d|\mathcal{H}_B)$.
+The odds ratio can tell us which of the two hypotheses is more likely.
+For example, if $\mathcal{O}^A_B >> 1$, then this odds ratio indicates that the $\mathcal{H}_A$ describes the data much better than $\mathcal{H}_B$.
+
+The \bcr is a Bayesian odds ratio like the above, of a coherent signal hypotheses $\mathcal{H}_S$ and an incoherent instrumental feature hypothesis $\mathcal{H}_I$ for a network of $D$ detectors.
+$\mathcal{H_I}$ states that each detector $i$ has either pure stationary Gaussian noise $\mathcal{H}_N$ or Gaussian noise and an incoherent noise transient (glitch).
+Taking $\mathcal{H}_G$, $Z^S$, $Z^G_i$ and $Z^N_i$ as the Bayesian evidences (marginalised likelihoods) for $\mathcal{H}_S$, $\mathcal{H}_N$, and $\mathcal{H}_G$, the \bcr is given by
+\begin{equation}
+\label{eq:bcr}
+\bcr = \frac{\alpha Z^S}{\prod\limits^D_{i=1} \ [\beta Z^G_i + (1-\beta)Z^N_i]}\ ,
+\end{equation}
+where $\alpha$ and $\beta$ are the prior-odds of obtaining a signal or a glitch from a stretch of data. The prior-odds can be defined more explicitly as 
+\begin{itemize}
+    \item $\alpha=P(\mathcal{H}_S)/P(\mathcal{H}_I)$, the prior-odds for obtaining a coherent signal versus an incoherent instrumental feature.
+    \item $\beta=P(\mathcal{H}_G| \mathcal{H}_I)$, the prior odds for obtaining a glitch assuming there is an incoherent instrumental feature.
+\end{itemize}
+
+When $\mathcal{H}_S$ and $\mathcal{H}_I$ are precisely described and the correct prior-odds are known, the \bcr is a Bayesian odds-ratio.
+As an odds-ratio, the \bcr is the optimal discriminator between coherent signals and incoherent instrumental features.
+However, as the priors-odds are unknown, it is invalid to use the \bcr as an odds-ratio.
+Instead of interpreting the \bcr as a Bayesian odds-ratio, it can be used as a ranking statistic.
+Using the \bcr as a ranking statistic we can obtain a frequentist significance of a candidate trigger \bcr measured against a {background trigger}\footnote{\textit{Background Triggers}: triggers that do not contain a coherent gravitational wave signal.} \bcr distribution.
+
+When using the \bcr as a detection statistic, the physical interpretation of the prior-odds is lost.
+Hence, the prior-odds are empirically tuned to maximise the separation between the \bcr distributions for background triggers (expected to favour the $\mathcal{H}_I$ hypothesis) and {simulated triggers}\footnote{\textit{Simulated Triggers}: artificial triggers manufactured by injecting signals into the detector data.} (expected to favour the $\mathcal{H}_S$ hypothesis).
+Increasing the separation between the two distributions can improve ability of the \bcr to discriminate candidate events as coherent signals or incoherent instrumental features.
+The tuning process is described in detail in Appendix~\ref{sec:tuning-prior-odds}.
+
+\subsection{Calculating the Significance of Candidate events}
+Candidate trigger \bcr values are either statistically insignificant compared to the background \bcr distribution, implying the candidate is more probable to be an incoherent instrumental feature (the $\mathcal{H}_I$ hypothesis), or statistically significant to the background distribution, indicating the possible presence of an astrophysical signal (the $\mathcal{H}_S$ hypothesis).
+A false alarm probability with trial factors \fap for the candidate triggers can quantify the significance.
+The \fap is the probability that a candidate trigger originating from a non-astrophysical source can be is falsely identified as a signal.
+
+To calculate the \fap, each candidate \bcr is considered as a single statistical trail that can occur at a fixed false alarm probability $f$, where $f$ is the probability of observing a background \bcr greater than or equal to the candidate \bcr,
+\begin{equation}
+    f = \frac{\text{Count of } \bcr' \leq \bcr}{\text{Count of } \bcr'} \ .
+\end{equation}
+The false alarm probability with trails \fap that the \bcr measurement occurs at least once for $N$ trials $(N > 0)$, where $N$ is the number of candidate triggers is
+\begin{equation}
+    \fap = 1 - (1-f)^N \ .
+\end{equation}
+
+Finally, the \fap can be used to construct a \pastro, the probability that a signal is of astrophysical origin~\cite{pastro_1,pastro_2,pastro_3}
+\begin{equation}
+    \pastro = 1 -  \fap \ .
+\end{equation}
+
+\subsection{Triggers for Analysis}
+
+The LIGO Scientific collaboration operates several search pipelines that scan for gravitational waves from compact binary mergers such as \texttt{GstLAL}, \texttt{MBTA}, \texttt{SPIIR} and \pycbc~\cite{GWTC1}.
+
+The output of \pycbc's search is a list of candidate trigger times and their corresponding \pycbc ranking statistic \pycbcstat.
+The \pycbcstat statistic is akin to the matched-filter signal-to-noise ratio \snr.
+However, unlike \snr, \pycbcstat includes some information on the candidate signal's intrinsic and extrinsic properties and other information that feeds into determining if the signal can have astrophysical origins~\cite{pycbc_og6}.
+The additional physical information incorporated in \pycbcstat makes it a more accurate measure of significance than the standard \snr.
+
+Whenever a local maximum of $\pycbcstat > \snr_\text{T}$, where $\snr_\text{T}$ is some threshold value, the \pycbc search pipeline produces a single-detector trigger associated with the detector and time where the apparent signal in the data has its merger~\cite{pycbc_og6}.
+
+For \pycbc to consider a trigger to be a candidate trigger, a trigger that may be from astrophysical origins, the trigger must be observed between detectors with the same template and a time of arrival difference less than the gravitational-wave travel time~\cite{pycbc_og1}.
+To test its pipeline's sensitivity, \pycbc also conducts searches for simulated triggers.
+Finally, to quantify the statistical significance of candidate events, \pycbc artificially constructs background triggers to compare against the candidate events.
+These background triggers are coherent signal-free events, constructed by applying relative offsets, or time-slides, between the data of different detectors~\cite{pycbc_og6}.
+The time-slides to generate the background triggers are greater than the gravitational-wave travel time between detectors to ensure that the background triggers are not of astrophysical origins.
+
+Our work demonstrates that the \bcr can be used in the same way as \pycbcstat to measure candidate triggers' statistical significance.
+The \bcr can be a powerful ranking statistic as the \bcr incorporates information of not only all possible binary black hole systems that might have merged to produce the trigger but also the various incoherent glitches that might cause a false-detection.
 
 \section{Method\label{sec:method}}
+
+\rs{I like the idea of the general intro: I suggest saying that you'll begin by introducing the Bayesian formalism, then defning the BCR, then discussing how we construct a ranking statistic using foreground and background.
+As it stands, there's a lot of discussion about how the BCR differs to other searches, and some technical details, but you haven't yet said what it *is*.
+Before talking about how the BCR differs from other searches etc.., I think there needs to be a description of what it is and where it comes from.
+(essentially describing everything up to the current eq.
+4).
+This sets up the framework, and you can then talk about why we construct it for both foreground and background to get a ranking statistic.
+}.
 The gravitational wave community uses Bayesian inference to perform parameter estimation and model selection.
@@
 
+\rs{Suggest revisiting the rest of this intro to section 2 after moving the discussion of Bayes theorem and the BCR.}
 Although a dedicated Bayesian search for gravitational waves, as presented by ~\citet{BCR2}, does not require noise estimation using empirical methods, this Bayesian significance ranking technique utilises \textit{time-slides}.
@@
 \subsection{Triggers for Analysis}
-
+\rs{I suggest moving this section to after you define the BCR and the need to estimate its significance empirically}
 The LIGO Scientific collaboration operates several search pipelines that scan for gravitational waves from compact binary mergers such as \texttt{GstLAL}, \texttt{MBTA}, \texttt{SPIIR} and \pycbc~\cite{GWTC1}.
@@
 The \bcr is a Bayesian odds ratio like the above, of a coherent signal hypotheses $\mathcal{H}_S$ and an incoherent instrumental feature hypothesis $\mathcal{H}_I$ for a network of $D$ detectors.
-$\mathcal{H_I}$ states that each detector $i$ has either pure Gaussian noise $\mathcal{H}_N$ or a glitch $\mathcal{H}_G$.
+$\mathcal{H_I}$ states that each detector $i$ has either pure stationary Gaussian noise $\mathcal{H}_N$ or an incoherent noise transient (glitch) $\mathcal{H}_G$.
 Following~\citet{BCR1}, the \bcr is given by
@@
 $\alpha$ and $\beta$, are the prior odds for obtaining a signal $\alpha=P(\mathcal{H}_S)/P(\mathcal{H}_I)$ and the prior odds for obtaining a glitch $\beta=P(\mathcal{H}_G)/P(\mathcal{H}_I)$.
+\rs{In the case that these hypotheses are exhaustive and mutually exclusive, $\rho_{BCR}$ is the optimal discriminator between signals, glitches or noise.}
+
+\rs{I suggest taking a pause here and talking about how we plan to use the BCR.
+You can recycle a lot of information from Isi+.
+A *key* point is that IMBH signals look a lot like glitches and we computing $\rho_{BCR}$ and we don't want to make a guess at a distribution for glitches and signals in this mass space (because we don't really know anything!) Looking at how the BCR is distributed for the background can give us some confidence that we construct a good discriminator between background and foreground
+So, we don't take it at face value because we don't think we have a good model for the signal and/or glitch distribution.
+Thus, we "rank" the BCR of foreground triggers based on that of background triggers which allows us to compute a frequentist estimator for its significance.
+I suggest moving the current section II.E to be directly after this subsection.
+Note that you don't need to say where background triggers come from yet -- it suffices to say that background triggers are just data known to contain no coherent GW signals.
+}
 As the rate of signal and glitches are unknown, these priors $\alpha$ and $\beta$ are tuned to maximise the \bcr distributions for background data (coherent signal-free data) and simulated signals~\cite{BCR1}.
@@
 \subsubsection{Noise Model}
+\rs{I suggest moving this subsection to an appendix}
 We assume that each detector's noise is Gaussian and stationary over the period being analysed~\cite{ligo_psd}.
@@
 
+\section{Bayesian Evidence Evaluation}
+\subsection{Noise Model}
+\rs{I suggest moving this subsection to an appendix}
+We assume that each detector's noise is Gaussian and stationary over the period being analysed~\cite{ligo_psd}.
+In practice, we assume that the noise has a mean of zero that the noise variance $\sigma^2$ is proportional to the noise power spectral density (PSD) \psd of the data.
+Using the \psd, for each data segment $d_i$ in each of the $i$ detectors in a network of $D$ detectors, we can write
+\begin{equation}
+\label{eq:zn}
+Z^N_i = \mathcal{N}(d_i) = \frac{1}{2\pi \psd_i} \ \text{exp}\left(-\frac{1}{2} \frac{d_i}{\psd_i} \right) \ ,
+\end{equation}
+where $\mathcal{N}(d_i)$ is a normal distribution with $\mu=0$ and $\sigma^2\sim \psd$.
+
+\subsection{Coherent Signal Model}
+We model coherent signal using a binary black hole waveform template \template, where the vector \parameters contains a point in the 15 dimensional space describing precessing binary-black hole mergers.
+For the signal to be coherent, \parameters must be consistent in each 4-second data segment $d_i$ for a network of $D$ detectors, Hence, the coherent signal evidence is calculated as
+\begin{equation}
+\label{eq:zs}
+Z^S = \int\limits_{\parameters} \prod\limits^{D}_{i=1} \left[ \mathcal{L}(d_i|\template)\right] \pi(\parameters | \mathcal{H}_S)\  \text{d}\parameters \ ,
+\end{equation}
+where $\pi(\parameters| \mathcal{H}_S)$ is the prior for the parameters in the coherent signal hypothesis, and $\mathcal{L}(d_i|\template))$ is the likelihood for the coherent signal hypothesis that depends on the gravitational wave template \template and its parameters \parameters.
+
+\subsection{Incoherent Glitch Model}
+Finally, as glitches are challenging to model and poorly understood, we follow \citet{bci} and utilise a surrogate model for glitches: the glitches are modelled using gravitational wave templates  \template with uncorrelated  parameters amongst the different detectors such that  $\parameters_i \neq \parameters_j$ for two detectors $i$ and $j$~\cite{bci}.
+Modelling glitches with \template captures the worst case scenario: when glitches are identical to gravitational wave signals (excluding coherent signals).
+Thus, we can write $Z^G_i$ as
+\begin{equation}
+\label{eq:zg}
+Z^G_i = \int\limits_{\parameters} \mathcal{L}(d_i|\template)\ \pi(\parameters| \mathcal{H}_G)\  \text{d}\parameters  \ ,
+\end{equation}
+where $\pi(\theta| \mathcal{H}_G)$ is the prior for the parameters in the incoherent glitch hypothesis.
+
+\section{Tuning the prior-odds}\label{sec:tuning-prior-odds}
+
+After calculating the \bcr for a set of background triggers and simulated triggers from as stretch of detector-data (a data chunk), we can compute probability distributions for the background and simulated triggers, $p_b(\bcr)$ and $p_s(\bcr)$.
+We expect the background trigger and simulated signal \bcr values to favour the incoherent glitch and the coherent signal hypothesis, respectively.
+Ideally, these distributions representing two unique populations should be distinctly separate and have no overlap in their \bcr values.
+The prior odds parameters $\alpha$ and $\beta$ from Eq.~\ref{eq:bcr} help separate the two distributions.
+Altering $\alpha$ translates the \bcr probability distributions while adjusting $\beta$ spreads the distributions.
+Although Bayesian hyper-parameter estimation can determine the optimal values for $\alpha$ and $\beta$, an easier approach is to adjust the parameters for each data chunk's \bcr distribution.
+In this study, we tune $\alpha$ and $\beta$ to maximally separate the \bcr distributions for the background and simulated triggers.
+
+To calculate the separation between $p_b(\bcr)$ and $p_s(\bcr)$, we use the Kullback--Leibler divergence (KL divergence) $D_{KL}$, given by
+\begin{equation}
+    D_{KL}(p_b | p_s) = \sum\limits_{x\in \bcr} p_b(x) \log \left( \frac{p_b(x)}{p_a(x)} \right)  \ .
+\end{equation}
+The $D_{KL}=0$ when the distributions are identical and increases as the asymmetry between the distributions increases.
+
+We limit our search for the maximum KL-divergence in the $\alpha$ and $\beta$ ranges of $[10^{-10}, 10^0]$ as values outside this range are nonphysical.
+We set our values for $\alpha$ and $\beta$ to those which provide the highest KL-divergence and calculate the \bcr for candidate events present in this data chunk.
+Note that we conduct the analysis in data chunks of a few days rather than an entire data set of a few months as the background may be different at different points of the entire data set.
+
 \section{Tuned prior odds}\label{apdx:alphabeta}

### 2021-03-10 main.tex
Updates from Overleaf

@@
 % author comments
-\newcommand{\av}[1]{\textcolor{orange}{[AV: #1]}}
+\newcommand{\avi}[1]{\textcolor{orange}{[AV: #1]}}
 \newcommand{\rs}[1]{\textcolor{red}{[RS: #1]}}
@@
 
-\subsection{Notes for motivation}
-\begin{itemize}
-    \item if truly Bayesian -- then its more astrophysical 
-    \item we're focused on odds -- but using it as a ranking statistic
-    \item GOAL: look for an IMBH, not to perfect the statistic     
-    \item  detection statistic that is based on a Bayesian approach -- a different way of looking for IMBHs, in place of matched-filter
-    \item normal statistic -- is maximum likelihood appraach (highest SNR), this one marginalises over all the templates -- closer to an "odds" like goal
-    \item this is NOT BCR2, this is a ranking statistic 
-    \item between Isi et al and Ashton et al,  more like Ashton and not matched filtering 
-    \item we didnt do a full Ashton because (no need to argue why we didnt do this)
-    \item whats out there, where does this fit into lit, what are we doing vs not doing 
-    \item  reproduced all these other results 
-    \item new in this paper: using Bayesian coherence (an ingredient in Ashton et al) and looking for NEW signals in triggers, the PRatten et al looks at all the catalogued triggers. 
-\end{itemize}
-
-\begin{itemize}
-    \item  IMBH signals look a lot like glitches
-    \item  We compute \bcr which needs $\alpha$ $\beta$
-    \item  We don't know the true probability $P(\mathcal{H}_S), P(\mathcal{H}_I)$ 
-    \item hence we cannot take \bcr at face value because we dont know the true distributions of the above
-    \item Studying p(\bcr| d=background) p(\bcr| d=signals) gives us confidence to discriminate between signals and glitches
-    \item  we "rank" the BCR of foreground triggers based on that of background triggers which allows us to compute a frequentist estimator for its significance.
-\end{itemize}
-
-\section{New Method\label{sec:method}}
+\section{Method\label{sec:method}}
 
@@
 
-\section{Method\label{sec:method}}
-
-\rs{I like the idea of the general intro: I suggest saying that you'll begin by introducing the Bayesian formalism, then defning the BCR, then discussing how we construct a ranking statistic using foreground and background.
-As it stands, there's a lot of discussion about how the BCR differs to other searches, and some technical details, but you haven't yet said what it *is*.
-Before talking about how the BCR differs from other searches etc.., I think there needs to be a description of what it is and where it comes from.
-(essentially describing everything up to the current eq.
-4).
-This sets up the framework, and you can then talk about why we construct it for both foreground and background to get a ranking statistic.
-}.
-The gravitational wave community uses Bayesian inference to perform parameter estimation and model selection.
-In this work, we utilise Bayesian inference to calculate the significance of high-mass candidate events in O2 by using the \bcr as a ranking statistic, taking a step toward building a unified Bayesian framework to search for candidates and estimate their parameters.
-
-\rs{Suggest revisiting the rest of this intro to section 2 after moving the discussion of Bayes theorem and the BCR.}
-Although a dedicated Bayesian search for gravitational waves, as presented by ~\citet{BCR2}, does not require noise estimation using empirical methods, this Bayesian significance ranking technique utilises \textit{time-slides}.
-To perform time-slides, data from independent observatories are time-shifted by amounts greater than the light-travel time between the two detectors.
-Each unique time-slide amount creates an artificial signal-free `background' data set.
-When search pipelines scan these background data sets for gravitational wave events, they can find \textit{triggers}\footnotemark, even though the background data set should not contain coherent astrophysical signals.
-These triggers in background data are labelled background triggers, while coherent triggers obtained in non-time-slid data are labelled candidate triggers.
-
-\footnotetext{\textit{Triggers} are points in time when the matched-filter SNR is larger than a threshold value for a given gravitational wave template~\cite{pycbc_og1}.}
-
-Calculating the \bcr ranking statistic for each background trigger builds a background \bcr distribution.
-With a background distribution,  it is possible to assign a statistical significance of how likely a candidate trigger, detected by the search pipelines over non-time slid data, is due to a gravitational wave signal.
-
-This section discusses (a) the method to retrieve triggers, and (b) the \bcr and how it is utilised as a ranking statistic to calculate the significance of candidate triggers.
-
-\subsection{Triggers for Analysis}
-\rs{I suggest moving this section to after you define the BCR and the need to estimate its significance empirically}
-The LIGO Scientific collaboration operates several search pipelines that scan for gravitational waves from compact binary mergers such as \texttt{GstLAL}, \texttt{MBTA}, \texttt{SPIIR} and \pycbc~\cite{GWTC1}.
-
-The output of \pycbc's search is a list of candidate trigger times and their corresponding \pycbc ranking statistic \pycbcstat.
-The \pycbcstat statistic is akin to the matched-filter signal-to-noise ratio \snr.
-However, unlike \snr, \pycbcstat includes some information on the candidate signal's intrinsic and extrinsic properties and other information that feeds into determining if the signal can have astrophysical origins~\cite{pycbc_og6}.
-The additional physical information incorporated in \pycbcstat makes it a more accurate measure of significance than the standard \snr.
-
-Whenever a local maximum of $\pycbcstat > \snr_\text{T}$, where $\snr_\text{T}$ is some threshold value, the \pycbc search pipeline produces a single-detector trigger associated with the detector and time where the apparent signal in the data has its merger~\cite{pycbc_og6}.
-
-For \pycbc to consider a trigger to be a \textit{candidate trigger}, a trigger that may be from astrophysical origins, the trigger must be observed between detectors with the same template and a time of arrival difference less than the gravitational-wave travel time~\cite{pycbc_og1}.
-To test its search, \pycbc also conducts searches for \textit{simulated triggers}, artificial triggers manufactured by injecting signals into the detector data.
-These simulated signal studies provide \pycbc with metrics on its search's sensitivity.
-Finally, to quantify the statistical significance of candidate events, \pycbc artificially constructs a \textit{background trigger} set to compare against the candidate events.
-These background triggers are coherent signal-free events, constructed by applying relative offsets, or time-slides, between the data of different detectors~\cite{pycbc_og6}.
-The time-slides to generate the background triggers are greater than the gravitational-wave travel time between detectors to ensure that the background triggers are not of astrophysical origins.
-
-Our work demonstrates that the \bcr can be used in the same way as \pycbcstat to measure candidate triggers' statistical significance.
-The \bcr can be a powerful ranking statistic as the \bcr incorporates information of not only all possible binary black hole systems that might have merged to produce the trigger but also the various incoherent glitches that might cause a false-detection.
-
-Before we discuss how we use the \bcr as a measure of significance, we introduce the method to calculate the \bcr in the following section.
-
-\subsection{The Bayesian Coherence Ratio}
-
-Bayes theorem states that the posterior probability distribution $p(\parameters|d,\mathcal{H})$ for data $d$ and a vector of parameters \parameters that describe a model which quantifies a hypothesis $\mathcal{H}$, is given by
-\begin{equation}
-p(\parameters|d,\mathcal{H}) = \frac{\mathcal{L}(d|\parameters, \mathcal{H}) \ \pi(\parameters | \mathcal{H})}{\mathcal{Z}(d|\mathcal{H})}\ , 
-\end{equation}
-where $\mathcal{L}(d|\parameters, \mathcal{H})$ is the likelihood of the data given the parameters \parameters and the hypothesis, $\pi(\parameters | \mathcal{H})$ is the prior probability of the parameters, and finally,
-\begin{equation}
-    \mathcal{Z}(d|\mathcal{H}) = \int\limits_{\parameters} \ \mathcal{L}(d|\parameters,\mathcal{H}) \ \pi(\parameters | \mathcal{H}) \ d\parameters
-\end{equation} is the likelihood after marginalising over the parameters \parameters.
-To compare two hypotheses $\mathcal{H}_A$ and $\mathcal{H}_B$ with the Bayes theorem one can calculate an odds ratio
-\begin{equation}
-    \mathcal{O}^A_B = \frac{\mathcal{Z}^A\ \pi(\parameters^A)}{\mathcal{Z}^B\ \pi(\parameters^B)}\ ,
-\end{equation}
-where $\mathcal{Z}^A$ and $\mathcal{Z}^B$ are the shorthand for the evidences  $\mathcal{Z}(d|\mathcal{H}_A)$ and $\mathcal{Z}(d|\mathcal{H}_B)$.
-The odds ratio can tell us which of the two hypotheses is more likely.
-For example, if $\mathcal{O}^A_B >> 1$, then this odds ratio indicates that the $\mathcal{H}_A$ describes the data much better than $\mathcal{H}_B$.
-
-The \bcr is a Bayesian odds ratio like the above, of a coherent signal hypotheses $\mathcal{H}_S$ and an incoherent instrumental feature hypothesis $\mathcal{H}_I$ for a network of $D$ detectors.
-$\mathcal{H_I}$ states that each detector $i$ has either pure stationary Gaussian noise $\mathcal{H}_N$ or an incoherent noise transient (glitch) $\mathcal{H}_G$.
-Following~\citet{BCR1}, the \bcr is given by
-\begin{equation}
-\label{eq:bcr}
-\bcr = \frac{\alpha Z^S}{\prod\limits^D_{i=1} \ [\beta Z^G_i + (1-\beta)Z^N_i]}\ ,
-\end{equation}
-where $Z^S$, $Z^G_i$ and $Z^N_i$ are the Bayesian evidences (marginalised likelihoods) for $\mathcal{H}_S$, $\mathcal{H}_N$, and $\mathcal{H}_G$.
-$\alpha$ and $\beta$, are the prior odds for obtaining a signal $\alpha=P(\mathcal{H}_S)/P(\mathcal{H}_I)$ and the prior odds for obtaining a glitch $\beta=P(\mathcal{H}_G)/P(\mathcal{H}_I)$.
-\rs{In the case that these hypotheses are exhaustive and mutually exclusive, $\rho_{BCR}$ is the optimal discriminator between signals, glitches or noise.}
-
-\rs{I suggest taking a pause here and talking about how we plan to use the BCR.
-You can recycle a lot of information from Isi+.
-A *key* point is that IMBH signals look a lot like glitches and we computing $\rho_{BCR}$ and we don't want to make a guess at a distribution for glitches and signals in this mass space (because we don't really know anything!) Looking at how the BCR is distributed for the background can give us some confidence that we construct a good discriminator between background and foreground
-So, we don't take it at face value because we don't think we have a good model for the signal and/or glitch distribution.
-Thus, we "rank" the BCR of foreground triggers based on that of background triggers which allows us to compute a frequentist estimator for its significance.
-I suggest moving the current section II.E to be directly after this subsection.
-Note that you don't need to say where background triggers come from yet -- it suffices to say that background triggers are just data known to contain no coherent GW signals.
-}
-As the rate of signal and glitches are unknown, these priors $\alpha$ and $\beta$ are tuned to maximise the \bcr distributions for background data (coherent signal-free data) and simulated signals~\cite{BCR1}.
-
-\subsection{Bayesian Evidence Evaluation}
-\subsubsection{Noise Model}
-\rs{I suggest moving this subsection to an appendix}
-We assume that each detector's noise is Gaussian and stationary over the period being analysed~\cite{ligo_psd}.
-In practice, we assume that the noise has a mean of zero that the noise variance $\sigma^2$ is proportional to the noise power spectral density (PSD) \psd of the data.
-Using the \psd, for each data segment $d_i$ in each of the $i$ detectors in a network of $D$ detectors, we can write
-\begin{equation}
-\label{eq:zn}
-Z^N_i = \mathcal{N}(d_i) = \frac{1}{2\pi \psd_i} \ \text{exp}\left(-\frac{1}{2} \frac{d_i}{\psd_i} \right) \ ,
-\end{equation}
-where $\mathcal{N}(d_i)$ is a normal distribution with $\mu=0$ and $\sigma^2\sim \psd$.
-
-\subsubsection{Coherent Signal Model}
-We model coherent signal using a binary black hole waveform template \template, where the vector \parameters contains a point in the 15 dimensional space describing precessing binary-black hole mergers.
-For the signal to be coherent, \parameters must be consistent in each 4-second data segment $d_i$ for a network of $D$ detectors, Hence, the coherent signal evidence is calculated as
-\begin{equation}
-\label{eq:zs}
-Z^S = \int\limits_{\parameters} \prod\limits^{D}_{i=1} \left[ \mathcal{L}(d_i|\template)\right] \pi(\parameters | \mathcal{H}_S)\  \text{d}\parameters \ ,
-\end{equation}
-where $\pi(\parameters| \mathcal{H}_S)$ is the prior for the parameters in the coherent signal hypothesis, and $\mathcal{L}(d_i|\template))$ is the likelihood for the coherent signal hypothesis that depends on the gravitational wave template \template and its parameters \parameters.
-
-\subsubsection{Incoherent Glitch Model}
-Finally, as glitches are challenging to model and poorly understood, we utilise a surrogate model for glitches: the glitches are modelled using gravitational wave templates  \template with uncorrelated  parameters amongst the different detectors such that  $\parameters_i \neq \parameters_j$ for two detectors $i$ and $j$~\cite{bci}.
-Modelling glitches with \template captures the worst case scenario: when glitches appear similar to gravitational wave signals.
-Thus, we can write $Z^G_i$ as
-\begin{equation}
-\label{eq:zg}
-Z^G_i = \int\limits_{\parameters} \mathcal{L}(d_i|\template)\ \pi(\parameters| \mathcal{H}_G)\  \text{d}\parameters  \ ,
-\end{equation}
-where $\pi(\theta| \mathcal{H}_G)$ is the prior for the parameters in the incoherent glitch hypothesis.
-
-\subsection{Tuning the BCR}
-
-After calculating the \bcr for a set of background triggers and simulated triggers from as stretch of detector-data (a data chunk), we can compute probability distributions for the background and simulated triggers, $p_b(\bcr)$ and $p_s(\bcr)$.
-We expect the background trigger and simulated signal \bcr values to favour the incoherent glitch and the coherent signal hypothesis, respectively.
-Ideally, these distributions representing two unique populations should be distinctly separate and have no overlap in their \bcr values.
-The prior odds parameters $\alpha$ and $\beta$ from Eq.~\ref{eq:bcr} help separate the two distributions.
-Altering $\alpha$ translates the \bcr probability distributions while adjusting $\beta$ spreads the distributions.
-Although Bayesian hyper-parameter estimation can determine the optimal values for $\alpha$ and $\beta$, an easier approach is to adjust the parameters for each data chunk's \bcr distribution.
-In this study, we tune $\alpha$ and $\beta$ to maximally separate the \bcr distributions for the background and simulated triggers.
-
-To calculate the separation between $p_b(\bcr)$ and $p_s(\bcr)$, we use the Kullback--Leibler divergence (KL divergence) $D_{KL}$, given by
-\begin{equation}
-    D_{KL}(p_b | p_s) = \sum\limits_{x\in \bcr} p_b(x) \log \left( \frac{p_b(x)}{p_a(x)} \right)  \ .
-\end{equation}
-The $D_{KL}=0$ when the distributions are identical and increases as the asymmetry between the distributions increases.
-
-We limit our search for the maximum KL-divergence in the $\alpha$ and $\beta$ ranges of $[10^{-10}, 10^0]$ as values outside this range are nonphysical.
-We set our values for $\alpha$ and $\beta$ to those which provide the highest KL-divergence and calculate the \bcr for candidate events present in this data chunk.
-Note that we conduct the analysis in data chunks of a few days rather than an entire data set of a few months as the background may be different at different points of the entire data set.
-
-\subsection{Calculating the Significance of Candidate events}
-With the tuned values of $\alpha$ and $\beta$ we can calculate the \bcr for candidate events.
-As mentioned previously, irrespective of the Bayesian interpretation for \bcr, we treat the \bcr as a traditional detection statistic to obtain a frequentist estimate of the significance of candidate event measured against the time-slid background \bcr distribution.
-
-We expect the background trigger \bcr values to favour the incoherent glitch hypothesis (the null hypothesis).
-Candidate event \bcr values will either be statistically insignificant compared to the background triggers, implying the candidate is a glitch, or statistically significant to the background distribution, indicating the possible presence of an astrophysical signal.
-To quantify the significance level, we can calculate a false alarm probability with trial factors \fap for the candidate events.
-The \fap is the probability that a candidate event originating from a non-astrophysical source can be is falsely identified as a signal.
-
-To calculate the \fap, consider each candidate \bcr as a single statistical trail that can occur at a fixed false alarm probability $f$, where $f$ is the probability of observing a background $\bcr'$ greater than or equal to the candidate \bcr,
-\begin{equation}
-    f = \frac{\text{Count of } \bcr' \leq \bcr}{\text{Count of } \bcr'} \ .
-\end{equation}
-The false alarm probability with trails \fap that the \bcr measurement occurs at least once for $N$ trials $(N > 0)$, where $N$ is the number of candidate triggers, can be written as
-\begin{equation}
-    \fap = 1 - (1-f)^N \ .
-\end{equation}
-
-The \fap can be used to construct a \pastro, the probability that a signal is of astrophysical origin~\cite{pastro_1,pastro_2,pastro_3}
-\begin{equation}
-    \pastro = 1 -  \fap \ .
-\end{equation}
-
 \section{Analysis}\label{sec:Analysis}
@@
 Advanced LIGO's second observing run O2 lasted $38$ weeks~\cite{GWOSC}.
-The software package, \pycbc~\cite{pycbc_code}, processed the O2 data in 22 time-frames (approximately 2 weeks for one time-frames) and found several gravitational wave events and numerous gravitational wave candidates~\cite{pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6}.
+The software package, \pycbc~\cite{pycbc_code}, was used by LIGO to process the O2 data in 22 time-frames (approximately 2 weeks for one time-frame) and found several gravitational wave events and numerous gravitational wave candidates~\cite{pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6}.
 Some candidate events were vetoed to be glitches, while others were rejected due to their low significance.
@@
 
-\caption[BBH parameters corresponding to duration $<454\ \text{ms}$]{\label{tab:parameters}Template Banks's parameters for templates with duration $<454 \ \text{ms}$.}
+\caption[BBH parameters corresponding to duration $<454\ \text{ms}$]{\label{tab:parameters}High-mass parameter space (parameters corresponding to signals with durations $<454 \ \text{ms}$). }
 \centering
@@
 The candidate, background and simulated triggers detected in this region of the parameter space during this period are plotted in orange, grey and blue respectively.
-}\label{fig:templateBank}
+\avi{Should I remove the `template bank' and only display the various triggers?}}\label{fig:templateBank}
 \end{figure*}
@@
 \subsection{Calculating the BCR for triggers}
-To evaluate $Z^S$, $Z^G_i$ and $Z^N_i$ as shown in Eqs.~\ref{eq:zn}-\ref{eq:zg} and calculate the \bcr Eq.~\ref{eq:bcr} for these triggers, we carry out Bayesian inference with \bilby~\cite{bilby}, employing \dynesty~\cite{dynesty} as our nested sampler.
+To evaluate $Z^S$, $Z^G_i$ and $Z^N_i$ and calculate the \bcr Eq.~\ref{eq:bcr} for triggers, we carry out Bayesian inference with \bilby~\cite{bilby, bilby_pipe}, employing \dynesty~\cite{dynesty} as our nested sampler.
 Nested sampling, an algorithm introduced by~\citet{skilling2004, skilling2006}, provides an estimate of the true Bayesian evidence and is often utilised for parameter estimation within the LIGO collaboration~\cite{bilby, bilby_paper, pbilby_paper}.
@@
 The waveform template we utilise is \imrphenomp, a phenomenological waveform template constructed in the frequency domain that models the in-spiral, merger, and ringdown (IMR) of a compact binary coalescence~\citep{khan2016frequency}.
-Although gravitational wave templates such as \seob~\cite{seobnrv4phm} which incorporate more physics, such as information on higher-order modes, we still use \imrphenomp as it is inexpensive compared to waveforms fitted against numerical-relativity simulations.
+Although there exist gravitational wave templates such as \seob~\cite{seobnrv4phm} which incorporate more physics, such as information on higher-order modes, we use \imrphenomp as it is computationally inexpensive compared to others.
 
@@
 Like other PSD estimation methods, this method adds statistical uncertainties to the PSD~\cite{psd_student_t, chatziioannou2019noise}.
-To marginalise over the statistical uncertainty, we use the median-likelihood presented by~\citet{psd_student_t} as a post-processing step and shift our Bayesian Evidence estimations closer to their astrophysical values.
+To marginalise over the statistical uncertainty, we use the median-likelihood presented by~\citet{psd_student_t} as a post-processing step.
+\avi{Greg would like me to discuss the effect of the PSD marginalization in more detail}
 
@@
 
-The run-time to calculate a single Bayesian evidence after using \dynesty with $1,000$ live points and $100$ walkers is usually between $1-12\ \text{hours}$ (where the run time is proportional to the SNR of the data segment).
-\bilbypipe orchestrates the creation of the PSDs and execution of the parameter estimation jobs~\cite{bilby_pipe}.
-
 \subsection{Assigning \pastro to candidate events}
 After the calculating the \bcr for the entire set of high-mass background and simulated triggers, we calculate probability distributions $p_b(\bcr)$ and $p_s(\bcr)$ for each 2-week time-frame of O2 data.
-These distributions are used to obtain the `tuned' prior-odd $\alpha$ and $\beta$ values that maximise $D_{KL}(p_b|p_s)$ for each time-frame of data.
+These distributions are used to `tune' prior-odd $\alpha$ and $\beta$ values.
 
-Finally, using the tuned prior odds the \bcr for the candidate events can be calculated.
+Using the tuned prior odds the \bcr for the candidate events can be calculated.
 Figure~\ref{fig:bcrCdf} shows the \bcr distributions for the background triggers, simulated triggers and candidate events.
@@
 \input{Data/results_table}
-We analyse the $60\ 996$ background, $5\ 146$ simulated, and $25$ candidate triggers reported by \pycbc's search of the data from the second observing run, restricting our analysis to the triggers that fall within our Bayesian prior space as described in Section~\ref{sec:method}.
+We analyse the $60\ 996$ background, $5\ 146$ simulated, and $25$ candidate triggers reported by \pycbc's search on the data from LIGO's second observing run, restricting our analysis to the triggers that fall within our mass-space as described in Section~\ref{sec:method}.
 In addition to these triggers, we also analyse events and candidate events reported by GWTC-1 and the IAS group (note that some of these were identified as candidates by the \pycbc search).
 In Table~\ref{tab:results}, we summarise the \pastrobcr, along with the \pastro of other pipelines for comparison.
-Note that although the various pipeline \pastro are not mathematically equivalent, by comparing pipeline \pastro values for a given event, we can compare how significant each pipeline deems various candidates.
-The $\alpha$ and $\beta$ values utilised for each time-frame of O2 are reported in Appendix~\ref{apdx:alphabeta}
+Although the various pipeline \pastro are not mathematically equivalent, by comparing pipeline \pastro values for a given candidate, we can compare how significant each pipeline deems various candidates.
+The $\alpha$ and $\beta$ values utilised for each time-frame are reported in Appendix~\ref{apdx:alphabeta}.
 
@@
 
-In addition to the above confirmed gravitational wave events from GWTC-1, we have also analysed several candidate events discussed in GWTC-1, most of which have low \pastrobcr.
+In addition to the above confirmed gravitational wave events from GWTC-1, we have also analysed several candidate events from GWTC-1, most of which have low \pastrobcr.
 For example, consider the candidate event 170412, assigned a $\pastro$ of $0.06$ by \gstlal and has a $\pastrobcr$ of $0.01$.
 This candidate was reported to be excess power caused due noise appearing non-stationary between 60-200 Hz~\cite{GWTC1}.
-This candidate acts as an example of how $\pastrobcr$ may be utilised  to eliminate terrestrial noise sources, in addition to detecting signals
+This candidate acts as an example of how $\pastrobcr$ may be utilised to eliminate candidates originating from terrestrial noise sources.
 
@@
 Our ranking statistic relies on the signal to appear coherent, even if just faintly coherent, amongst the various detectors to have a high \pastrobcr.
-Hence, the lack of coherence and the non-eccentric waveform may be the leading factors for a low \pastro.
+The lack of coherence and the non-eccentric waveform may be the leading factors for a low \pastro.
 GW170403 and GW170425 which have $\pastrobcr<0.35$ also have low  \pastro reported by \citet{pycbc_ogc_2},  suggesting that these events may have been false alarms.
@@
 The remaining coherent trigger candidates all have $\pastrobcr\ll0.5$ making them unlikely to originate from astrophysical sources.
+\avi{wjat more can I say about this?}
 
@@
 Virgo is funded by the French Centre National de Recherche Scientifique (CNRS), the Italian Istituto Nazionale della Fisica Nucleare (INFN) and the Dutch Nikhef, with contributions by Polish and Hungarian institutes.
+
+Thank Stuart Anderson, CIT
 
@@
 Table~\ref{tab:priorodds} presents the signal and glitch prior odds utilised for each time-frame of O2 data.
-\av{note: havent tuned all chunks yet -- and tbh the 'tuning' could be better, atm brute force searching a 2d log-spce grid}
+\avi{note: havent tuned all chunks yet -- and tbh the 'tuning' could be better, atm brute force searching a 2d log-spce grid}
 \input{Data/alpha_beta_table}

### 2021-03-13 main.tex
Updates from Overleaf

@@
 
-The most promising avenues to find $100−1000\ \msun$ black holes are either to identify stellar binaries, which are expected to be common or to detect them in gravitational radiation.
-Ground-based gravitational wave limits on the low end of this mass regime are continuing to improve.
+The most promising avenues to find $100-1000 Msun$ black holes are either to identify stellar binaries, which are expected to be common or to detect them in gravitational radiation.
+Ground based gravitational-wave limits on the low end of this mass regime are continuing to improve.
 
@@
 As of January 2021, the LIGO Scientific Collaboration has confirmed $\sim50$ binary black hole systems and listed numerous candidate events~\cite{GWTC1, GWTC2, gracedb}.
-Additionally, since the public release of LIGO's first and second observing run's data (O1 and O2), search pipelines such as \pycbc~\cite{pycbc_code} and a research team at the Institute for Advanced Study (IAS)~\cite{IAS0, IAS1, IAS2}, have independently identified additional binary black hole gravitational wave candidates.
+Additionally, since the public release of LIGO's first and second observing run's data (O1 and O2), search pipelines such as \pycbc~\cite{pycbc_code} and a research team at the Institute for Advanced Study (IAS)~\cite{IAS0, IAS1, IAS2}, have independently identified additional binary black hole gravitational-wave candidates.
 
@@
 Insert here an exhaustive review of previous IMBH detection claims, noting who made the claim, the mass, and the method.}
-This changed with the detection of GW190521, a unique gravitational wave event that led to the formation of a black hole with a mass  $142\ \msun$, the first confirmed direct discovery of an intermediate-mass black hole~\cite{gw190521}.
-Although this is the first gravitational-wave observation of an IMBH, ground-based gravitational wave detectors are sensitive to gravitational waves from even more massive systems with a total mass of up to $400\ \msun$~\cite{GWTC1}.
+This changed with the detection of GW190521, a unique gravitational-wave event that led to the formation of a black hole with a mass  $142\ \msun$, the first confirmed direct discovery of an intermediate-mass black hole~\cite{gw190521}.
+Although this is the first gravitational-wave observation of an IMBH, ground-based gravitational-wave detectors are sensitive to gravitational-waves from even more massive systems with a total mass of up to $400\ \msun$~\cite{GWTC1}.
 
@@
 A possible explanation for the absence of intermediate-mass events may be due to their misclassification as short-duration instrumental noise transients known as glitches~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
-These glitches can mimic astrophysical signals and hence decrease the significance of true gravitational wave events.
+These glitches can mimic astrophysical signals and hence decrease the significance of true gravitational-wave events.
 
-One method to account for glitches while searching for gravitational waves from coalescing compact binaries is by utilising the astrophysical Bayesian odds~\cite{bci, BCR1, BCR2, bcr_gw151216, bayesian_odds}.
+One method to account for glitches while searching for gravitational-waves from coalescing compact binaries (CBCs) is by utilising the astrophysical Bayesian odds~\cite{bci, BCR1, BCR2, bcr_gw151216, bayesian_odds}.
 A true Bayesian odds, calculated without using bootstrap techniques, can provide more accurate estimate of significance that does note depend on the search pipeline~\cite{BCR2, bcr_gw151216,  bayesian_odds}.
-In this paper, we utilise a Bayesian method, called the Bayesian Coherence Ratio \bcr~\cite{BCR1}, to rank the candidate gravitational wave signals from high-mass compact binary coalescences (systems with total masses in the range of $55-500\ \msun$) in the detector data recorded during O2.
+In this paper, we utilise a Bayesian method, called the Bayesian Coherence Ratio \bcr~\cite{BCR1}, to rank the candidate gravitational-wave signals from high-mass compact binary coalescences (systems with total masses in the range of $55-500\ \msun$) in the detector data recorded during O2.
 Although the \bcr, utilising bootstrap techniques, does not provide the true Bayesian odds, it provides a more astrophysical measure of candidate events' significance than a traditional match-filter significance.
@@
 
-The gravitational wave community uses Bayesian inference to perform parameter estimation and model selection.
-This work utilises Bayesian inference to calculate the significance of high-mass candidate triggers\footnote{\textit{Trigger:} point in time when the matched-filter SNR is larger than a threshold value for a given gravitational wave template~\cite{pycbc_og1}.
-\textit{Candidate Trigger:} trigger that may be from astrophysical origins.} in LIGO's second observing run.
-We calculate the significance of triggers using the Bayesian Coherence Ratio~\cite{BCR1}, \bcr, as a ranking statistic, a step toward building a unified Bayesian framework to search for candidates and estimate their parameters.
+The standard framework to identify CBC gravitational-wave signals hidden in data is by quantifying the significance of candidates with null-hypothesis significance testing.
+In this framework, the candidates' ranking statistic is compared against a background distribution in a frequentist approach.
+On the other hand, the standard framework for performing parameter estimation and model selection in gravitational-wave astronomy is Bayesian inference.
+This work utilises Bayesian inference to calculate the Bayesian Coherence odds-ratio~\cite{BCR1}, \bcr, of high-mass candidates in LIGO's second observing run.
+We use the \bcr not as an odds-ratio but instead as a ranking statistic, a step toward building a unified Bayesian framework to search for candidates and estimate their parameters.
 
@@
 \end{equation} is the likelihood after marginalising over the parameters \parameters.
-To compare two hypotheses $\mathcal{H}_A$ and $\mathcal{H}_B$ with the Bayes theorem one can calculate an odds ratio
+To compare two hypotheses $\mathcal{H}_A$ and $\mathcal{H}_B$ with the Bayes theorem one can calculate an odds-ratio
 \begin{equation}
@@
 where $\mathcal{Z}^A$ and $\mathcal{Z}^B$ are the shorthand for the evidences  $\mathcal{Z}(d|\mathcal{H}_A)$ and $\mathcal{Z}(d|\mathcal{H}_B)$.
-The odds ratio can tell us which of the two hypotheses is more likely.
+The odds-ratio can tell us which of the two hypotheses is more likely.
 For example, if $\mathcal{O}^A_B >> 1$, then this odds ratio indicates that the $\mathcal{H}_A$ describes the data much better than $\mathcal{H}_B$.
 
-The \bcr is a Bayesian odds ratio like the above, of a coherent signal hypotheses $\mathcal{H}_S$ and an incoherent instrumental feature hypothesis $\mathcal{H}_I$ for a network of $D$ detectors.
+The \bcr is a Bayesian odds-ratio like the above, of a coherent signal hypotheses $\mathcal{H}_S$ and an incoherent instrumental feature hypothesis $\mathcal{H}_I$ (the null-hypotheses) for a network of $D$ detectors.
 $\mathcal{H_I}$ states that each detector $i$ has either pure stationary Gaussian noise $\mathcal{H}_N$ or Gaussian noise and an incoherent noise transient (glitch).
@@
     \item $\alpha=P(\mathcal{H}_S)/P(\mathcal{H}_I)$, the prior-odds for obtaining a coherent signal versus an incoherent instrumental feature.
-    \item $\beta=P(\mathcal{H}_G| \mathcal{H}_I)$, the prior odds for obtaining a glitch assuming there is an incoherent instrumental feature.
+    \item $\beta=P(\mathcal{H}_G| \mathcal{H}_I)$, the prior-odds for obtaining a glitch assuming there is an incoherent instrumental feature.
 \end{itemize}
@@
 As an odds-ratio, the \bcr is the optimal discriminator between coherent signals and incoherent instrumental features.
-However, as the priors-odds are unknown, it is invalid to use the \bcr as an odds-ratio.
+However, as the priors-odds are unknown, it is invalid to use the \bcr as an odds-ratio to make an informed decision about whether a candidate is from an astrophysical or terrestrial source.
 Instead of interpreting the \bcr as a Bayesian odds-ratio, it can be used as a ranking statistic.
-Using the \bcr as a ranking statistic we can obtain a frequentist significance of a candidate trigger \bcr measured against a {background trigger}\footnote{\textit{Background Triggers}: triggers that do not contain a coherent gravitational wave signal.} \bcr distribution.
+Using the \bcr as a ranking statistic we can obtain a frequentist significance of a candidate \bcr-value measured against a background \bcr distribution.
 
 When using the \bcr as a detection statistic, the physical interpretation of the prior-odds is lost.
-Hence, the prior-odds are empirically tuned to maximise the separation between the \bcr distributions for background triggers (expected to favour the $\mathcal{H}_I$ hypothesis) and {simulated triggers}\footnote{\textit{Simulated Triggers}: artificial triggers manufactured by injecting signals into the detector data.} (expected to favour the $\mathcal{H}_S$ hypothesis).
+Hence, the prior-odds are empirically tuned to maximise the separation between the \bcr distribution of the background (expected to favour the $\mathcal{H}_I$ hypothesis) and the \bcr distribution of artificially manufactured simulated signals (expected to favour the $\mathcal{H}_S$ hypothesis).
 Increasing the separation between the two distributions can improve ability of the \bcr to discriminate candidate events as coherent signals or incoherent instrumental features.
@@
 
-\subsection{Calculating the Significance of Candidate events}
-Candidate trigger \bcr values are either statistically insignificant compared to the background \bcr distribution, implying the candidate is more probable to be an incoherent instrumental feature (the $\mathcal{H}_I$ hypothesis), or statistically significant to the background distribution, indicating the possible presence of an astrophysical signal (the $\mathcal{H}_S$ hypothesis).
-A false alarm probability with trial factors \fap for the candidate triggers can quantify the significance.
-The \fap is the probability that a candidate trigger originating from a non-astrophysical source can be is falsely identified as a signal.
+\subsection{Calculating the Significance of Candidates}
+Candidate \bcr-values are either statistically insignificant compared to the background \bcr distribution, implying the candidate is more probable to be an incoherent instrumental feature (the $\mathcal{H}_I$ null-hypothesis), or statistically significant to the background distribution, indicating the possible presence of an astrophysical signal (the $\mathcal{H}_S$ hypothesis).
+A false alarm probability with trial factors, \fap, for the candidate \bcr-values can quantify the significance.
+The \fap is the probability that a candidate originating from a non-astrophysical source can be is falsely identified as a signal.
 
-To calculate the \fap, each candidate \bcr is considered as a single statistical trail that can occur at a fixed false alarm probability $f$, where $f$ is the probability of observing a background \bcr greater than or equal to the candidate \bcr,
+To calculate the \fap, each candidate \bcr is considered a single statistical trail that can occur at a fixed false alarm probability $f$, where $f$ is the probability of observing a background \bcr greater than or equal to the candidate \bcr,
 \begin{equation}
@@
 
-\subsection{Triggers for Analysis}
+\subsection{Data for Analysis}
+\avi{Probably need a better section label...}
+The LIGO Scientific collaboration operates several search pipelines that scan for gravitational-waves from compact binary mergers such as \texttt{GstLAL}, \texttt{MBTA}, \texttt{SPIIR} and \pycbc~\cite{GWTC1}.
+The output of \pycbc's search is a list of times and their corresponding \pycbc ranking statistic \pycbcstat values.
+The \pycbcstat ranking-statistic is akin to the matched-filter signal-to-noise ratio \snr.
+However, unlike \snr, \pycbcstat includes candidate signal's intrinsic and extrinsic properties and other information that feeds into determining if the signal can have astrophysical origins~\cite{pycbc_og6}.
+Whenever a local maximum of $\pycbcstat > \snr_\text{T}$, where $\snr_\text{T}$ is some predetermined threshold value, the \pycbc search pipeline produces a single-detector \textit{trigger} associated with the detector and time where the apparent signal in the data has its merger~\cite{pycbc_og6}.
 
-The LIGO Scientific collaboration operates several search pipelines that scan for gravitational waves from compact binary mergers such as \texttt{GstLAL}, \texttt{MBTA}, \texttt{SPIIR} and \pycbc~\cite{GWTC1}.
-
-The output of \pycbc's search is a list of candidate trigger times and their corresponding \pycbc ranking statistic \pycbcstat.
-The \pycbcstat statistic is akin to the matched-filter signal-to-noise ratio \snr.
-However, unlike \snr, \pycbcstat includes some information on the candidate signal's intrinsic and extrinsic properties and other information that feeds into determining if the signal can have astrophysical origins~\cite{pycbc_og6}.
-The additional physical information incorporated in \pycbcstat makes it a more accurate measure of significance than the standard \snr.
-
-Whenever a local maximum of $\pycbcstat > \snr_\text{T}$, where $\snr_\text{T}$ is some threshold value, the \pycbc search pipeline produces a single-detector trigger associated with the detector and time where the apparent signal in the data has its merger~\cite{pycbc_og6}.
-
-For \pycbc to consider a trigger to be a candidate trigger, a trigger that may be from astrophysical origins, the trigger must be observed between detectors with the same template and a time of arrival difference less than the gravitational-wave travel time~\cite{pycbc_og1}.
-To test its pipeline's sensitivity, \pycbc also conducts searches for simulated triggers.
-Finally, to quantify the statistical significance of candidate events, \pycbc artificially constructs background triggers to compare against the candidate events.
+When \pycbc observes a trigger between detectors with coincident parameters and a time of arrival difference less than the gravitational-wave travel time between detectors, the trigger is labelled a \textit{candidate event trigger}, a trigger that may be from astrophysical origins~\cite{pycbc_og1}.
+To test the pipeline's sensitivity \pycbc also conducts searches for \textit{simulated triggers}, artificial triggers manufactured by injecting signals into the detector data.
+Finally, to quantify the statistical significance of candidate triggers, \pycbc artificially constructs \textit{background triggers} to compare against the candidate events.
 These background triggers are coherent signal-free events, constructed by applying relative offsets, or time-slides, between the data of different detectors~\cite{pycbc_og6}.
-The time-slides to generate the background triggers are greater than the gravitational-wave travel time between detectors to ensure that the background triggers are not of astrophysical origins.
+The background trigger's \pycbcstat distribution is used to calculate the candidate trigger's significance,  using null-hypothesis significance testing, under the assumption that all candidate event triggers are due to noise.
 
 Our work demonstrates that the \bcr can be used in the same way as \pycbcstat to measure candidate triggers' statistical significance.
-The \bcr can be a powerful ranking statistic as the \bcr incorporates information of not only all possible binary black hole systems that might have merged to produce the trigger but also the various incoherent glitches that might cause a false-detection.
+The \bcr can be a powerful ranking statistic as it incorporates information of not only all possible binary black hole systems that might have merged to produce the trigger but also the various incoherent glitches that might cause a false-detection.
 
@@
 Advanced LIGO's second observing run O2 lasted $38$ weeks~\cite{GWOSC}.
-The software package, \pycbc~\cite{pycbc_code}, was used by LIGO to process the O2 data in 22 time-frames (approximately 2 weeks for one time-frame) and found several gravitational wave events and numerous gravitational wave candidates~\cite{pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6}.
+The software package, \pycbc~\cite{pycbc_code}, was used by LIGO to process the O2 data in 22 time-frames (approximately 2 weeks for one time-frame) and found several gravitational-wave events and numerous gravitational-wave candidates~\cite{pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6}.
 Some candidate events were vetoed to be glitches, while others were rejected due to their low significance.
@@
 A plot of the \pycbc triggers from one time-frame, during April 23 - May 8, 2017, is presented in Figure~\ref{fig:templateBank}.
-This figure also depicts the gravitational wave templates used during the search through this time-frame of data.
+This figure also depicts the gravitational-wave templates used during the search through this time-frame of data.
 
@@
 The waveform template we utilise is \imrphenomp, a phenomenological waveform template constructed in the frequency domain that models the in-spiral, merger, and ringdown (IMR) of a compact binary coalescence~\citep{khan2016frequency}.
-Although there exist gravitational wave templates such as \seob~\cite{seobnrv4phm} which incorporate more physics, such as information on higher-order modes, we use \imrphenomp as it is computationally inexpensive compared to others.
+Although there exist gravitational-wave templates such as \seob~\cite{seobnrv4phm} which incorporate more physics, such as information on higher-order modes, we use \imrphenomp as it is computationally inexpensive compared to others.
 
@@
 
-Finally, we neglect detector calibration uncertainty and acquire data from from the Gravitational Wave Open Science Center~\cite{GWOSC}.
+Finally, we neglect detector calibration uncertainty and acquire data from from the gravitational-wave Open Science Center~\cite{GWOSC}.
 The data we use is the publicly accessible O2 strain data from the Hanford and Livingston detectors, recorded while the detectors are in ``Science Mode''.
@@
 The separation suggests that the \bcr can successfully distinguish signals from noise or glitches.
-The vertical lines in Figure~\ref{fig:bcrCdf} displays the \bcr for gravitational wave candidate events.
+The vertical lines in Figure~\ref{fig:bcrCdf} displays the \bcr for gravitational-wave candidate events.
 On comparing the candidate event \bcr values with the background distribution, we can estimate \pastro values for the candidate events.
@@
 \subsection{GWTC-1 Events}
-All the confirmed gravitational wave events from binary black hole mergers reported in GWTC-1 and within our prior space, (specifically GW170104, GW170608, GW170729, GW170809 and GW170814), have $\pastrobcr$ greater than $0.9$, indicating a high probability of the presence of an astrophysical signal.
+All the confirmed gravitational-wave events from binary black hole mergers reported in GWTC-1 and within our prior space, (specifically GW170104, GW170608, GW170729, GW170809 and GW170814), have $\pastrobcr$ greater than $0.9$, indicating a high probability of the presence of an astrophysical signal.
 
-In addition to the above confirmed gravitational wave events from GWTC-1, we have also analysed several candidate events from GWTC-1, most of which have low \pastrobcr.
+In addition to the above confirmed gravitational-wave events from GWTC-1, we have also analysed several candidate events from GWTC-1, most of which have low \pastrobcr.
 For example, consider the candidate event 170412, assigned a $\pastro$ of $0.06$ by \gstlal and has a $\pastrobcr$ of $0.01$.
@@
 
-In this paper, we demonstrate that the Bayesian Coherence Ratio~\cite{BCR1} can be used as a ranking statistic to provide a better measure of significance for gravitational wave candidates by re-analysing the significance of high-mass binary black hole triggers from O2.
+In this paper, we demonstrate that the Bayesian Coherence Ratio~\cite{BCR1} can be used as a ranking statistic to provide a better measure of significance for gravitational-wave candidates by re-analysing the significance of high-mass binary black hole triggers from O2.
 This method takes a step towards building a unified Bayesian framework that provides a search-pipeline agnostic measure of significance, utilising the same level of physical information incorporated during parameter estimation.
@@
 
-Although our analysis targets high-mass triggers, this method can be extended to include the entire body range of LIGO-detectable gravitational wave sources.
-Additionally, to further improve the method's infrastructure, we can use more robust gravitational wave templates (such as templates that incorporate higher-order modes), and sophisticated glitch models.
+Although our analysis targets high-mass triggers, this method can be extended to include the entire body range of LIGO-detectable gravitational-wave sources.
+Additionally, to further improve the method's infrastructure, we can use more robust gravitational-wave templates (such as templates that incorporate higher-order modes), and sophisticated glitch models.
 Future analysis can also incorporate data from all available detectors in a network to increase the sensitivity of \pastrobcr.
@@
 
-\av{as the core of this method is PE, improvements in PE can be adapted into this method}
+\avi{as the core of this method is PE, improvements in PE can be adapted into this method}
 
@@
 Thank Stuart Anderson, CIT
+
+ We greatly appreciate the contributions of all these computing allocations.
+All pe performed for this study including test runs and failed simulations used about 2.5M core-hours which under the assumption of 30W per core-hour and a CO2 intensity of electricity of ~ 600 kg CO2 per MWh amounts to a carbon footprint of~ 45t of CO2.
 
@@
 \end{equation}
-where $\pi(\parameters| \mathcal{H}_S)$ is the prior for the parameters in the coherent signal hypothesis, and $\mathcal{L}(d_i|\template))$ is the likelihood for the coherent signal hypothesis that depends on the gravitational wave template \template and its parameters \parameters.
+where $\pi(\parameters| \mathcal{H}_S)$ is the prior for the parameters in the coherent signal hypothesis, and $\mathcal{L}(d_i|\template))$ is the likelihood for the coherent signal hypothesis that depends on the gravitational-wave template \template and its parameters \parameters.
 
 \subsection{Incoherent Glitch Model}
-Finally, as glitches are challenging to model and poorly understood, we follow \citet{bci} and utilise a surrogate model for glitches: the glitches are modelled using gravitational wave templates  \template with uncorrelated  parameters amongst the different detectors such that  $\parameters_i \neq \parameters_j$ for two detectors $i$ and $j$~\cite{bci}.
-Modelling glitches with \template captures the worst case scenario: when glitches are identical to gravitational wave signals (excluding coherent signals).
+Finally, as glitches are challenging to model and poorly understood, we follow \citet{bci} and utilise a surrogate model for glitches: the glitches are modelled using gravitational-wave templates  \template with uncorrelated  parameters amongst the different detectors such that  $\parameters_i \neq \parameters_j$ for two detectors $i$ and $j$~\cite{bci}.
+Modelling glitches with \template captures the worst case scenario: when glitches are identical to gravitational-wave signals (excluding coherent signals).
 Thus, we can write $Z^G_i$ as

### 2021-03-15 main.tex

@@
 %%%%%%---SECTIONS---%%%%%%%%%%%%
-\section{New Intro}
+\section{Introduction}
 In the 1960s, X-ray and optical observations from the Cyg-X1 binary star system led to the discovery of the first stellar-mass black hole~\cite{}.
-Shortly afterwards, in 1974, kinematic measurements of stars near the center of our galaxy demonstrated the presence of a supermassive black hole of mass $10^6\ \text{M}_{\odot}$ -- Sag A$^*$~\cite{}.
+Shortly afterwards, in 1974, kinematic measurements of stars near the center of our galaxy demonstrated the presence of a supermassive black hole of mass $10^6\ \msun$ -- Sag A$^*$~\cite{}.
 These two detections firmly established the existence of stellar-mass
-black holes $\text{M}_\text{BH} < 10^{2} \ \text{M}_{\odot}$ and
-supermassive black holes, $\text{M}_\text{BH} > 10^{5} \ \text{M}_{\odot}$ in our universe.
+black holes $\text{M}_\text{BH} < 10^{2} \ \msun$ and
+supermassive black holes, $\text{M}_\text{BH} > 10^{5} \ \msun$ in our universe.
 Since then, astronomers accumulated more definitive evidence for stellar-mass and supermassive black holes.
@@
 
-Intermediate-mass black holes may form various scenarios ranging from hierarchical mergers of stellar-mass black holes to large metal-free stars' direct collapse.
-Hierarchical mergers in active galactic nuclei migration-traps, globular and stellar clusters may be a feasible method for black holes to accumulate mass and reach the intermediate-mass range.
+The two main proposed formation channels for Intermediate-mass black holes are the light-seed and the heavy-seed channels.
+The light-seed channel involves dynamic interactions of low-mass seeds, e.g.
+hierarchical mergers of stellar-mass black holes, runaway collisions of stars.
+The heavy-seed channel involves the direct collapse of high-mass seeds, e.g.
+the direct collapse of giant metal-free Population III stars or early protogalaxies' collapse.
+Although promising pathways, there are challenging obstacles both scenarios must overcome to pathways that can form intermediate-mass black holes.
+
+Hierarchical mergers in active galactic nuclei migration-traps, globular and stellar clusters may be a feasible light-seed method for black holes to accumulate mass and reach the intermediate-mass range.
 However, when black holes merge, they can receive recoil-kicks up to $\sim$2,500 km/s.
@@
 This tight constraint makes hierarchical mergers a challenging scenario.
-
-Another pathway to form intermediate-mass black involves the direct collapse of massive, metal-free Population III stars.
+One proposed heave-seed pathway involves the direct collapse of massive, metal-free Population III stars.
 Typically, massive stars $> 100 \ \msun$ can eject more than half of their mass in the form of radiatively driven stellar winds.
-However, at zero metallicity, mass loss through stellar winds is negligible (Kudritzki 2000).
+However, at zero metallicity, mass loss through stellar winds is negligible \cite{Kudritzki 2000}.
 Hence,  Population III stars have the opportunity to complete their life-cycles without losing a significant portion of their mass.
 Moreover, Population III stars with masses above $230 \ \msun$ will avoid electron-positron pair-instability.
-Consequently, oxygen and silicon burning will not drive an explosion, allowing the star to undergo a complete collapse to leave behind an intermediate-mass black hole remnant with a mass of $120-280 \ \msun$, dependant on the initial star mass (Bond et al.
-1984).
-The intermediate-mass black holes that form as remnants of these large Population III stars may exist today in clusters located at the galaxies' bulges.
-If these bulges contain intermediate-mass black holes, they could also provide evidence for Population III stars' existence.
+Consequently, oxygen and silicon burning will not drive an explosion, allowing the star to undergo a complete collapse to leave behind an intermediate-mass black hole remnant with a mass of $120-280 \ \msun$, dependant on the initial star mass \cite{Bond et al.
+1984}.
+Hence, the formation of intermediate-mass black holes from Population III stars is directly proportional to the fraction of Population III stars with masses above $230 \ \msun$, a fraction that is still uncertain~\cite{Coleman Miller, Formation Scenarios for Intermediate-Mass Black Holes}.
 
-As there is inadequate observational evidence for intermediate-mass black holes, it is challenging to state which formation path is favoured.
-However, the observational work does allude to the existence of intermediate-mass black holes.
-The search for intermediate-mass black holes is underway using direct kinematic measurements, reverberation mapping, studying luminosity from low-luminous active galactic nuclei and Ultraluminous X-ray Sources.
+% - Bridge between light-seed and heavy-seed formation and observation
+% - Although IMBH gap isnt completly filled, observational work conducted in the past 20 years points to the existence of intermediate-mass black holes .
 
-Dynamic measurements of individual sources orbiting an intermediate-mass black hole is that the sphere of influence too small to resolve motions.
-Can only be used on close sources.
-The issue with reverberation mapping and the other EM spectra, cant be sure of anisotropic emission, non-linear emission.
-large uncertainties.
-\url{https://iopscience.iop.org/article/10.3847/2041-8213/ab745b}
+% - To prove the existence of IMBH we need to measure their BH's masses
+% - We can measure mass by two main methods: direct kinematic, emission (reverberation mapping, luminosity, gw)
+% - Discuss Candidates
+% - LIGO a good way. 190521g uncertain
+% - Challenges of IMBH from ground-based
+% - THUS We need a better way to discriminate between glitches and high-mass signals -- BCR!
 
-The most promising avenues to find $100-1000 Msun$ black holes are either to identify stellar binaries, which are expected to be common or to detect them in gravitational radiation.
-Ground based gravitational-wave limits on the low end of this mass regime are continuing to improve.
+To prove the existence of intermediate-mass black holes, the scientific community needs to measure the mass of a black hole inside the IMBH range.
+However, measuring the mass of black holes can be challenging.
 
-LIGO found 190521, can find more if we are more sensitive, and if we can better harness data
+It is possible to measure the mass of nearby supermassive black holes (such as Sag A) by directly observing the dynamic motion of stars nearby the supermassive black hole.
+However, this dynamic measurement method is challenging to utilise for IMBHs as their sphere of influence is too small to resolve motions.
+Additionally, dynamic-measurements that have alluded to IMBH candidates, e.g.
+the candidate at the centre of the globular cluster 47 Tucanae \cite{kiziltan 2017}, can also be attributed to simpler models without a central IMBH \cite{freire 2017}.
 
-\section{\label{sec:Introduction}Introduction}
+In a similar vein, although the M-$\sigma$ and M-L relations (relations between the spheroidal bulge of a galaxy's velocity dispersion $\sigma$,  luminosity L, and its central black hole's mass M) can estimate the mass of supermassive black holes  \cite{Ferrarese & Merritt 2000 and Gebhardt et al.
+2000}, it cannot accurately estimate the mass of IMBHs.
+The M-$\sigma$ and M-L relations are not calibrated for low-mass galaxies that might host an IMBH as its central black hole \cite{J.
+E.
+Greene and L.
+C.
+Ho The Mass Function of Active Black Holes in the Local Universe, E.
+C.
+Moran, K.
+Shahinyan, H.
+R.
+Sugarman, D.
+O.
+Vélez and M.
+Eracleous Black Holes At the Centers of Nearby Dwarf Galaxies}.
+Table 2 of ~\citet{mercuza} displays a list of IMBH candidates found with these relations.
 
-Since the 1970s, there has been an accumulation of evidence for stellar-mass and supermassive black holes.
-In April 2019, the Event Horizon Telescope provided the first visual evidence of the supermassive black hole M87~\cite{m87photo}.
-As of January 2021, the LIGO Scientific Collaboration has confirmed $\sim50$ binary black hole systems and listed numerous candidate events~\cite{GWTC1, GWTC2, gracedb}.
-Additionally, since the public release of LIGO's first and second observing run's data (O1 and O2), search pipelines such as \pycbc~\cite{pycbc_code} and a research team at the Institute for Advanced Study (IAS)~\cite{IAS0, IAS1, IAS2}, have independently identified additional binary black hole gravitational-wave candidates.
+Another method to estimate large black hole masses is reverberation mapping, which estimates black hole virial masses by studying their nearby gasses' velocities \cite{reverberation mapping}.
+Reverberation mapping has shown to estimate both supermassive black hole and IMBH virial masses successfully.
+However, this method fails to measure the systematic uncertainties on the low-mass IMBH masses ~\cite{}.
+Additionally, cloud-variability and the possibility of anisotropic emission deride the credibility of IMBH candidates found with reverberation mapping.
 
-\et{Add a paragraph here discussing basic ideas in IMBH theory.
-Explain why the are not easy to make.
-Discuss scenarios by which they can be made.
-Discuss the role they may play in the formation of supermassive BH.
-Then, we transition to the next paragraph about observational evidence.}
+The most promising IMBH candidates found with electromagnetic-spectra are Ultra-Luminous X-ray sources (with luminosities $> 10^{39} \text{erg s}^{-1}$).
+While stellar mass black holes are too small to generate such luminosities with Eddington accretion, Intermediate mass black holes can accrete at rates large enough to account for the high luminosities \cite{}.
+The drawback to this approach is the assumption that super-Eddington accretion is impossible and that X-ray emission from the sources is isotropic.
 
-Until recently, there was no definitive evidence for intermediate-mass black holes with a mass in between the range of stellar-mass and supermassive black holes ($10^2-10^6\ \msun$). 
-\et{There have been numerous claims of IMBH detection.
-The previous sentence is correct that there are no \textit{definitive} detections before GW190521, but the paragraph is misleading by omission.
-Insert here an exhaustive review of previous IMBH detection claims, noting who made the claim, the mass, and the method.}
-This changed with the detection of GW190521, a unique gravitational-wave event that led to the formation of a black hole with a mass  $142\ \msun$, the first confirmed direct discovery of an intermediate-mass black hole~\cite{gw190521}.
-Although this is the first gravitational-wave observation of an IMBH, ground-based gravitational-wave detectors are sensitive to gravitational-waves from even more massive systems with a total mass of up to $400\ \msun$~\cite{GWTC1}.
+Finally, another channel to measure BH masses is from gravitational waves.
+Identifying GW from mergers of compact binaries.
+Ground-based gravitational-wave limits on the low end of this mass regime are continuing to improve.
+LIGO found 190521, can find more if we are more sensitive, and can better harness data.
 
-\et{The following paragraph tries to solve a problem that doesn't exist: as noted in comments above, the absence of GWs from IMBH is not surprising.
-Delete or rewrite if you want to emphasise the difficulty in IMBH detection.}
-A possible explanation for the absence of intermediate-mass events may be due to their misclassification as short-duration instrumental noise transients known as glitches~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
+IMBH hard to find as very similar to short-duration instrumental noise transients known as glitches~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
 These glitches can mimic astrophysical signals and hence decrease the significance of true gravitational-wave events.
@@
 In this paper, we utilise a Bayesian method, called the Bayesian Coherence Ratio \bcr~\cite{BCR1}, to rank the candidate gravitational-wave signals from high-mass compact binary coalescences (systems with total masses in the range of $55-500\ \msun$) in the detector data recorded during O2.
-Although the \bcr, utilising bootstrap techniques, does not provide the true Bayesian odds, it provides a more astrophysical measure of candidate events' significance than a traditional match-filter significance.
-\et{This pitch, that the method is ``a more astrophysical measure'' is unconvincing.
-(What does that even mean?) Chat with RS/ET to come up with a better pitch built around the idea that the detection statistic is built on Bayesian inferences results, and that it's a step toward fully Bayesian detection.}
+Although the \bcr, utilising bootstrap techniques, does not provide the true Bayesian odds,  it utilizes Bayesian evidences which describe the explicit probability of data under the hypothesis that it contains coherent signals vs incoherent glitches.
 
@@
 Candidate \bcr-values are either statistically insignificant compared to the background \bcr distribution, implying the candidate is more probable to be an incoherent instrumental feature (the $\mathcal{H}_I$ null-hypothesis), or statistically significant to the background distribution, indicating the possible presence of an astrophysical signal (the $\mathcal{H}_S$ hypothesis).
-A false alarm probability with trial factors, \fap, for the candidate \bcr-values can quantify the significance.
+A false alarm probability with trial factors, \fap, for the candidate \bcr-value can quantify the significance.
 The \fap is the probability that a candidate originating from a non-astrophysical source can be is falsely identified as a signal.
 
-To calculate the \fap, each candidate \bcr is considered a single statistical trail that can occur at a fixed false alarm probability $f$, where $f$ is the probability of observing a background \bcr greater than or equal to the candidate \bcr,
+To calculate the \fap, each candidate \bcr is considered a single statistical trail that can occur at a fixed false alarm probability $f$, where $f$ is the probability of observing a background $\bcr'$ greater than or equal to the candidate \bcr,
 \begin{equation}
@@
 
-\caption[BBH parameters corresponding to duration $<454\ \text{ms}$]{\label{tab:parameters}High-mass parameter space (parameters corresponding to signals with durations $<454 \ \text{ms}$). }
+\caption[BBH parameters correspond to duration $<454\ \text{ms}$]{\label{tab:parameters}High-mass parameter space (parameters correspond to signals with durations $<454 \ \text{ms}$). }
 \centering
@@
 \subsection{Calculating the BCR for triggers}
+\avi{Sat 13th: Just realised that some parts of this dont make sense without the material present in Apdx~\ref{sec:bayesianEvidEval}}...
 To evaluate $Z^S$, $Z^G_i$ and $Z^N_i$ and calculate the \bcr Eq.~\ref{eq:bcr} for triggers, we carry out Bayesian inference with \bilby~\cite{bilby, bilby_pipe}, employing \dynesty~\cite{dynesty} as our nested sampler.
@@
     \hline
-    Parameter & Shape & Limits & Boundary \\
+    Parameter & Shape & Limits \\
     \hline
-          $\mathcal{M}/\msun$           & Uniform & 7--180 & Reflective \\
-          $q$                           & Uniform & 0.1--1 & Reflective \\
-          $M/\msun$                     & Constraint & 50--500 & -- \\
-          $d_\mathrm{L}/\mathrm{Mpc}$   & Comoving & 100--5000 & Reflective \\
-          $a_1$, $a_2$                  & Uniform & 0--1 & Reflective \\
-          $\theta_{JN}$                 & Sinusoidal & 0--$\pi$ &  Reflective \\
-          $\psi$                        & Uniform & 0--$\pi$ &  Periodic \\
-          $\phi$                        & Uniform & 0--$2\pi$ &  Periodic \\
-          ra                            & Uniform & 0--$2\pi$ &  Periodic \\
-          dec                           & Cosine & 0--$2\pi$ &  Reflective \\
+          $\mathcal{M}/\msun$           & Uniform & 7--180  \\
+          $q$                           & Uniform & 0.1--1  \\
+          $M/\msun$                     & Constraint & 50--500  \\
+          $d_\mathrm{L}/\mathrm{Mpc}$   & Comoving & 100--5000  \\
+          $a_1$, $a_2$                  & Uniform & 0--1  \\
+          $\theta_{JN}$                 & Sinusoidal & 0--$\pi$  \\
+          $\psi$                        & Uniform & 0--$\pi$  \\
+          $\phi$                        & Uniform & 0--$2\pi$  \\
+          ra                            & Uniform & 0--$2\pi$  \\
+          dec                           & Cosine & 0--$2\pi$  \\
     \hline
@@
 \begin{figure}[!ht]
-{\centering \includegraphics[width=0.75\linewidth]{images/bcr_cdf_smaller_legend.png} }
+{\centering \includegraphics[width=0.85\linewidth]{images/bcr_cdf_smaller_legend.png} }
 \caption[BCR distribution example]{Histograms represent the survival function (1-CDF) from our high-mass selection of background triggers (grey) and simulated signals (blue) triggers obtained from \pycbc's search of data from $\text{August 13 - 21, 2017}$.
@@
 
-\section{Bayesian Evidence Evaluation}
+\section{Bayesian Evidence Evaluation}\label{sec:bayesianEvidEval}
 \subsection{Noise Model}
-\rs{I suggest moving this subsection to an appendix}
 We assume that each detector's noise is Gaussian and stationary over the period being analysed~\cite{ligo_psd}.
@@
 Table~\ref{tab:priorodds} presents the signal and glitch prior odds utilised for each time-frame of O2 data.
-\avi{note: havent tuned all chunks yet -- and tbh the 'tuning' could be better, atm brute force searching a 2d log-spce grid}
 \input{Data/alpha_beta_table}

### 2021-03-18 main.tex
Updates from Overleaf

@@
 \section{Introduction}
-In the 1960s, X-ray and optical observations from the Cyg-X1 binary star system led to the discovery of the first stellar-mass black hole~\cite{}.
-Shortly afterwards, in 1974, kinematic measurements of stars near the center of our galaxy demonstrated the presence of a supermassive black hole of mass $10^6\ \msun$ -- Sag A$^*$~\cite{}.
-These two detections firmly established the existence of stellar-mass
-black holes $\text{M}_\text{BH} < 10^{2} \ \msun$ and
-supermassive black holes, $\text{M}_\text{BH} > 10^{5} \ \msun$ in our universe.
-Since then, astronomers accumulated more definitive evidence for stellar-mass and supermassive black holes.
-However, a gap in between the mass-ranges of these two categories began to form: there is a deficiency of black holes in the intermediate-mass range $10^{2} - 10^{5}\ \text{M}_{\odot}$.
-These intermediate-mass black holes must have existed to form the supermassive black holes detected to exist in the early universe~\cite{}.
-However, we only have a handful of candidates and one confirmed intermediate-mass black hole~\cite{}.
-The study and discovery of intermediate-mass black holes will help bridge the gap and provide a pathway to forming supermassive black holes.
+In the 1970s, X-ray and optical observations from the Cyg-X1 binary star system led to the discovery of the first stellar-mass black hole~\cite{Webster:1972:Natur}.
+Two years later, in 1974, radio observation of our galaxy center demonstrated the presence of a supermassive black hole -- Sgr A$^*$~\cite{Balick:1974:ApJ}.
+In the half-century since then, astronomers accumulated more definitive evidence that have established the  existence of stellar-mass black holes $\text{M}_\text{BH} < 10^{2} \ \msun$ and supermassive black holes, $\text{M}_\text{BH} > 10^{5} \ \msun$ in our universe (e.g.
+~\cite{Ghez:1998:ApJ, Genzel:2010:RvMP, Abbott:2019:PhRvX, EventHorizonTelescopeCollaboration:2019:ApJL, Abbott:2020:arXiv}).
+However, a gap in between the mass-ranges of these two categories has formed: there is a deficiency of observational evidence for black holes in the intermediate-mass range $10^{2} - 10^{5}\ \text{M}_{\odot}$.
+These intermediate-mass black holes must have existed to form the supermassive black holes detected to exist in the early universe~\cite{Banados:2018:Natur}.
+However, we only have a handful of promising candidates~\cite{Greene:2004:ApJ, Graham:2013:ApJ, Mezcua:2017:IJMPD, Koliopanos:2017:mbhe, Lin:2020:ApJL, Greene:2020:ARA&A}, and one confirmed intermediate-mass black hole, the remnant of the gravitational wave event GW190521 with a mass of $142^{+28}_{-16}\ \msun$~\cite{Abbott:2020:PhRvL}.
+The concrete discovery of more intermediate-mass black holes will bridge the observational gap and illuminate our understanding of galaxy and supermassive black hole formation.
 
@@
 The light-seed channel involves dynamic interactions of low-mass seeds, e.g.
-hierarchical mergers of stellar-mass black holes, runaway collisions of stars.
+hierarchical mergers of stellar-mass black holes~\cite{}, runaway collisions of stars~\cite{}.
 The heavy-seed channel involves the direct collapse of high-mass seeds, e.g.
-the direct collapse of giant metal-free Population III stars or early protogalaxies' collapse.
+the direct collapse of giant metal-free Population III stars~\cite{}, early protogalaxies' collapse~\cite{}.
 Although promising pathways, there are challenging obstacles both scenarios must overcome to pathways that can form intermediate-mass black holes.
@@
 Hierarchical mergers in active galactic nuclei migration-traps, globular and stellar clusters may be a feasible light-seed method for black holes to accumulate mass and reach the intermediate-mass range.
-However, when black holes merge, they can receive recoil-kicks up to $\sim$2,500 km/s.
+\rory{\sout{However, when black holes merge, they can receive recoil-kicks up to $\sim$2,500 km/s~\cite{}.
 Hence, the merger remnants require their recoil kick to be less than its environment's escape velocity to undergo successive mergers.
-This tight constraint makes hierarchical mergers a challenging scenario.
+This tight constraint makes hierarchical mergers a challenging scenario.}
+
 One proposed heave-seed pathway involves the direct collapse of massive, metal-free Population III stars.
-Typically, massive stars $> 100 \ \msun$ can eject more than half of their mass in the form of radiatively driven stellar winds.
+Typically, massive stars $> 100 \ \msun$ can eject more than half of their mass in the form of radiatively driven stellar winds~\cite{}.
 However, at zero metallicity, mass loss through stellar winds is negligible \cite{Kudritzki 2000}.
-Hence,  Population III stars have the opportunity to complete their life-cycles without losing a significant portion of their mass.
+Consequently,  Population III stars have the opportunity to complete their life-cycles without losing a significant portion of their mass.
 Moreover, Population III stars with masses above $230 \ \msun$ will avoid electron-positron pair-instability.
-Consequently, oxygen and silicon burning will not drive an explosion, allowing the star to undergo a complete collapse to leave behind an intermediate-mass black hole remnant with a mass of $120-280 \ \msun$, dependant on the initial star mass \cite{Bond et al.
+Therefore, oxygen and silicon burning will not drive an explosion, allowing the star to undergo a complete collapse to leave behind an intermediate-mass black hole remnant with a mass of $120-280 \ \msun$, dependant on the initial star mass \cite{Bond et al.
 1984}.
-Hence, the formation of intermediate-mass black holes from Population III stars is directly proportional to the fraction of Population III stars with masses above $230 \ \msun$, a fraction that is still uncertain~\cite{Coleman Miller, Formation Scenarios for Intermediate-Mass Black Holes}.
+As the fraction of Population III stars with masses above $230 \ \msun$ is uncertain, the number of expected intermediate-mass black holes from these stars is also ambiguous~\cite{Coleman Miller, Formation Scenarios for Intermediate-Mass Black Holes}.
 
-% - Bridge between light-seed and heavy-seed formation and observation
-% - Although IMBH gap isnt completly filled, observational work conducted in the past 20 years points to the existence of intermediate-mass black holes .
-
-% - To prove the existence of IMBH we need to measure their BH's masses
-% - We can measure mass by two main methods: direct kinematic, emission (reverberation mapping, luminosity, gw)
-% - Discuss Candidates
-% - LIGO a good way. 190521g uncertain
-% - Challenges of IMBH from ground-based
-% - THUS We need a better way to discriminate between glitches and high-mass signals -- BCR!
-
-To prove the existence of intermediate-mass black holes, the scientific community needs to measure the mass of a black hole inside the IMBH range.
+To verify and determine details on which formation channel is favoured, a catalog of observed intermediate-black holes and their masses is required.
 However, measuring the mass of black holes can be challenging.
 
-It is possible to measure the mass of nearby supermassive black holes (such as Sag A) by directly observing the dynamic motion of stars nearby the supermassive black hole.
-However, this dynamic measurement method is challenging to utilise for IMBHs as their sphere of influence is too small to resolve motions.
-Additionally, dynamic-measurements that have alluded to IMBH candidates, e.g.
-the candidate at the centre of the globular cluster 47 Tucanae \cite{kiziltan 2017}, can also be attributed to simpler models without a central IMBH \cite{freire 2017}.
+\rory{\sout{It is possible to measure the mass of nearby supermassive black holes by directly observing the dynamic motion of stars nearby the supermassive black hole (such as Sgr A$^*$~).
+However, this dynamic measurement method is challenging to utilise for  intermediate-mass black holes as their sphere of influence is too small to resolve motions~\cite{}.
+Additionally, dynamic-measurements that have alluded to  intermediate-mass candidates, e.g.
+the candidate at the centre of the globular cluster 47 Tucanae~\cite{kiziltan 2017}, can also be attributed to simpler models without a central  intermediate-mass black hole~\cite{freire 2017}.
+}}
 
-In a similar vein, although the M-$\sigma$ and M-L relations (relations between the spheroidal bulge of a galaxy's velocity dispersion $\sigma$,  luminosity L, and its central black hole's mass M) can estimate the mass of supermassive black holes  \cite{Ferrarese & Merritt 2000 and Gebhardt et al.
-2000}, it cannot accurately estimate the mass of IMBHs.
-The M-$\sigma$ and M-L relations are not calibrated for low-mass galaxies that might host an IMBH as its central black hole \cite{J.
+\rory{\sout{In a similar vein, although the M-$\sigma$ and M-L relations (relations between the spheroidal bulge of a galaxy's velocity dispersion $\sigma$,  luminosity L, and its central black hole's mass M) can estimate the mass of supermassive black holes~\cite{Ferrarese & Merritt 2000 and Gebhardt et al.
+2000}, they cannot accurately estimate the intermediate-masses.
+The M-$\sigma$ and M-L relations are not calibrated for low-mass galaxies that might host an central intermediate-mass black hole~\cite{J.
 E.
@@
 Eracleous Black Holes At the Centers of Nearby Dwarf Galaxies}.
-Table 2 of ~\citet{mercuza} displays a list of IMBH candidates found with these relations.
+Table 2 of~\citet{mercuza} displays a list of intermediate-mass candidates found with these relations.
+}}
 
-Another method to estimate large black hole masses is reverberation mapping, which estimates black hole virial masses by studying their nearby gasses' velocities \cite{reverberation mapping}.
-Reverberation mapping has shown to estimate both supermassive black hole and IMBH virial masses successfully.
-However, this method fails to measure the systematic uncertainties on the low-mass IMBH masses ~\cite{}.
-Additionally, cloud-variability and the possibility of anisotropic emission deride the credibility of IMBH candidates found with reverberation mapping.
+\rory{\sout{Another method to estimate large black hole masses is with reverberation mapping, which estimates black hole virial masses by studying their nearby gasses' velocities~\cite{reverberation mapping}.
+Reverberation mapping has shown to estimate both supermassive black hole and intermediate-mass black hole virial masses successfully.
+However, this method fails to measure the systematic uncertainties on the lower-end of the intermediate-mass spectrum~\cite{}.
+Additionally, cloud-variability and the possibility of anisotropic emission deride the credibility of intermediate-mass candidates found with reverberation mapping~\cite{}.
+}}
 
-The most promising IMBH candidates found with electromagnetic-spectra are Ultra-Luminous X-ray sources (with luminosities $> 10^{39} \text{erg s}^{-1}$).
-While stellar mass black holes are too small to generate such luminosities with Eddington accretion, Intermediate mass black holes can accrete at rates large enough to account for the high luminosities \cite{}.
-The drawback to this approach is the assumption that super-Eddington accretion is impossible and that X-ray emission from the sources is isotropic.
+The most promising intermediate-mass candidates found with electromagnetic-spectra are Ultra-Luminous X-ray sources with luminosities $> 10^{39} \text{erg s}^{-1}$ (e.g.
+HLX-X1)~\cite{}.
+\rory{\sout{While stellar mass black holes are too small to generate such luminosities with Eddington accretion, intermediate mass black holes can accrete at rates large enough to account for the high luminosities~\cite{}.
+However, some argue that some stellar mass black holes may exceed the Eddington limit~\cite{}, and others argue that the X-ray emission might be from a collimated jet leading to an inaccurate mass calculation~\cite{}.}}
 
-Finally, another channel to measure BH masses is from gravitational waves.
-Identifying GW from mergers of compact binaries.
-Ground-based gravitational-wave limits on the low end of this mass regime are continuing to improve.
-LIGO found 190521, can find more if we are more sensitive, and can better harness data.
+\Finally, \rory{\sout{another channel to measure black hole masses is by identifying}} Gravitational waves from compact binaries coalesces (CBCs) \rory{are clean channels to measure BH masses} \rory{\sout{ inferring their source parameters~\cite{}.}} Mergers involving either a binary system with at least one intermediate-mass component, or a system whose merger results in an intermediate-mass remnant will have large initial total masses $\text{M}_{T}$.
+As a binary's $\text{M}_{T}$ is associated with its merger frequency, $f\sim \text{M}_T^-1$, systems with large $\text{M}_{T}$ have very low merger frequencies $f < 100\ \text{Hz}$.
+Hence, ground based gravitational wave detectors ($\sim 10 - 1000\ \text{Hz}$) are sensitive to the last milliseconds of merging systems with $100 \msun < \text{M}_{T} < 500 \msun$, while space-based detectors ($\sim 0.1 - 10\ \text{Hz}$) can study the full signals of merging systems with $10^4 \msun < \text{M}_{T} < 10^7 \msun$.
 
-IMBH hard to find as very similar to short-duration instrumental noise transients known as glitches~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
-These glitches can mimic astrophysical signals and hence decrease the significance of true gravitational-wave events.
+Because of high-total mass systems' short-durations in ground-based gravitational wave data steams, handling data quality is critical to their detection.
+The low-frequency ranges of ground-based observatories are plagued with incoherent non-stationary terrestrial artefacts, called glitches~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
+Some glitches, similar to signals from high total mass mergers, last for a fraction of a second, making them difficult to distinguish from the signals.
+These glitches that mimic astrophysical signals can severely decrease the confidence in detection of true gravitational-waves from high total mass mergers.
 
-One method to account for glitches while searching for gravitational-waves from coalescing compact binaries (CBCs) is by utilising the astrophysical Bayesian odds~\cite{bci, BCR1, BCR2, bcr_gw151216, bayesian_odds}.
+Although a significant fraction of the glitches can be removed by testing them for coherence amongst various ground based detectors and performing matched-filtering, these methods are insufficient to remove all the glitches.
+One method to account for more glitches while searching for high total mass CBC gravitational-waves is by utilising the astrophysical Bayesian odds~\cite{bci, BCR1, BCR2, bcr_gw151216, bayesian_odds}.
 A true Bayesian odds, calculated without using bootstrap techniques, can provide more accurate estimate of significance that does note depend on the search pipeline~\cite{BCR2, bcr_gw151216,  bayesian_odds}.
@@
 Although the \bcr, utilising bootstrap techniques, does not provide the true Bayesian odds,  it utilizes Bayesian evidences which describe the explicit probability of data under the hypothesis that it contains coherent signals vs incoherent glitches.
+
+\avi{Need to discuss IAS, PyCBC etc here as well}
 
@@
 $\mathcal{H_I}$ states that each detector $i$ has either pure stationary Gaussian noise $\mathcal{H}_N$ or Gaussian noise and an incoherent noise transient (glitch).
-Taking $\mathcal{H}_G$, $Z^S$, $Z^G_i$ and $Z^N_i$ as the Bayesian evidences (marginalised likelihoods) for $\mathcal{H}_S$, $\mathcal{H}_N$, and $\mathcal{H}_G$, the \bcr is given by
+Taking $Z^S$, $Z^G_i$ and $Z^N_i$ as the Bayesian evidences (marginalised likelihoods, definitions in Appendix~\ref{apdx} for $\mathcal{H}_S$, $\mathcal{H}_N$, and $\mathcal{H}_G$, the \bcr is given by
 \begin{equation}
@@
 The remaining coherent trigger candidates all have $\pastrobcr\ll0.5$ making them unlikely to originate from astrophysical sources.
-\avi{wjat more can I say about this?}
+
+\avi{mass and spin estimates, is it a vanilla bbh}
 
 \section{\label{sec:Conclusion}Conclusion}
+
+% Gravitational waves from intermediate-mass black holes will Current ground-based gravitational-wave observatories like LIGO can probe the lower-end of the intermediate-mass range, u, while future space based detectors will be able to study the mergers of large limits on the low end of this mass regime are continuing to improve.
+LIGO found 190521, can find more if we are more sensitive, and can better harness data.
+
+% Most of what we know about intermediate mass black holes so far has been informed from electromagnetic observations.
+Gravitational waves provide a complementary lens to study these massive objects.
+In the future, LISA will fill in this gap, but we can begin now with LIGO...
+In this paper, we
 

### 2021-03-29 scripts/make_bcr_cdf.py
add scripts for plotting

@@ -5,11 +5,24 @@ from bcr_pipeline.post_processing.bcr_plotting.make_ranking_stat_probability_plo
 from matplotlib import pyplot as plt
 from matplotlib import rcParams
 from matplotlib.lines import Line2D
+from matplotlib.ticker import (MultipleLocator,
+                               FormatStrFormatter,
+                               AutoMinorLocator)
+import matplotlib.font_manager
+from matplotlib import rc
+
+# matplotlib.font_manager.findfont("font.sans-serif", rebuild_if_missing=False)
+all_fonts = matplotlib.font_manager.findSystemFonts()
+print(f"Avail fonts: {all_fonts}")
+
+font_path = "/Users/avaj0001/Library/Fonts/ScopeOn-Regular.ttf"
+# prop = matplotlib.font_manager.FontProperties(fname=font_path)
 
 
+rc('text.latex', preamble=r'\usepackage{cmbright}')
 rcParams["font.size"] = 30
-rcParams["font.family"] = "serif"
-rcParams["font.sans-serif"] = ["Computer Modern Sans"]
+rcParams["font.family"] = "sans-serif"
+# rcParams["font.sans-serif"] = ["/Users/avaj0001/Library/Fonts/ScopeOn-Regular.ttf"]
 rcParams["text.usetex"] = True
 rcParams['axes.labelsize'] = 30
 rcParams['axes.titlesize'] = 30
@@ -53,7 +66,7 @@ def plot():
     fig, ax_cdf = plt.subplots(nrows=1, ncols=1, figsize=(7, 5))
     cdf_data = _add_rank_pdf(plot_data, xrange, ax_cdf, cdf=True)
     ax_cdf.set_ylim(0, 1)
-    ax_cdf.set_ylabel('1-CDF', fontsize="x-large")
+    ax_cdf.set_ylabel('Survival Probability', fontsize="x-large")
     ax_cdf.set_xlabel(r'ln $\rho_{\mathrm{BCR}}$', fontsize="x-large")
 
 
@@ -64,7 +77,7 @@ def plot():
         ax_cdf.axvline(x=xval, color=c)
         ax_cdf.annotate(
             event_txt, xy=(xval, 0.95), ha='left', va='top', rotation=-90,
-            color="#ff8c00", fontweight="extra bold", fontfamily='sans-serif')
+            color="#ff8c00", fontweight="extra bold")
 
     # add_foreground_events_to_plot(ax_cdf, plot_data['foreground']['df'],
[…]

### 2021-03-29 scripts/make_events_plot.py

@@ -1,0 +1,111 @@
+import matplotlib.pyplot as plt
+import matplotlib.ticker
+import numpy as np
+import pandas as pd
+from matplotlib import rcParams
+from matplotlib.patches import Patch
+from matplotlib.patches import Polygon
+import matplotlib.font_manager
+from matplotlib import rc
+
+# matplotlib.font_manager.findfont("font.sans-serif", rebuild_if_missing=False)
+all_fonts = matplotlib.font_manager.findSystemFonts()
+print(f"Avail fonts: {all_fonts}")
+
+rc('text.latex', preamble=r'\usepackage{cmbright}')
+
+rcParams["font.size"] = 34
+rcParams["font.family"] = "serif"
+rcParams["font.sans-serif"] = ["Computer Modern Sans"]
+rcParams["text.usetex"] = True
+rcParams['axes.labelsize'] = 60
+rcParams['axes.titlesize'] = 50
+rcParams['axes.labelpad'] = 10
+rcParams['axes.linewidth'] = 5
+rcParams['axes.edgecolor'] = 'black'
+rcParams['xtick.labelsize'] = 38
+rcParams['ytick.labelsize'] = 38
+rcParams['ytick.major.size'] = 20.0
+rcParams['ytick.minor.size'] = 10
+rcParams['xtick.major.size'] = 20.0
+rcParams['xtick.minor.size'] = 10
+rcParams['ytick.major.pad'] = 10
+rcParams['ytick.minor.pad'] = 10
+rcParams['xtick.major.pad'] = 10
+rcParams['xtick.minor.pad'] = 10
+
+plt.rcParams['xtick.minor.width'] = 5
+plt.rcParams['xtick.major.width'] = 5
+plt.rcParams['ytick.minor.width'] = 5
+plt.rcParams['ytick.major.width'] = 5
+plt.rcParams['xtick.direction'] = 'in'
+plt.rcParams['ytick.direction'] = 'in'
+plt.rcParams['xtick.top'] = True
+plt.rcParams['ytick.right'] = True
+
+COLS = {"LVK":"tab:purple", "IAS":"tab:pink", "LVK Candidates":"tab:orange"}
+
+
+def plot_masses(catalog_df):
+    df = catalog_df.copy()
+    df = df.replace("GWTC-1-confident", "LVK")
+    df = df.replace("GWTC-2", "LVK")
[…]

### 2021-03-29 main.tex

@@
 Hierarchical mergers in active galactic nuclei migration-traps, globular and stellar clusters may be a feasible light-seed method for black holes to accumulate mass and reach the intermediate-mass range.
-\rory{\sout{However, when black holes merge, they can receive recoil-kicks up to $\sim$2,500 km/s~\cite{}.
+\rs{\sout{However, when black holes merge, they can receive recoil-kicks up to $\sim$2,500 km/s~\cite{}.
 Hence, the merger remnants require their recoil kick to be less than its environment's escape velocity to undergo successive mergers.
@@
 
-\rory{\sout{It is possible to measure the mass of nearby supermassive black holes by directly observing the dynamic motion of stars nearby the supermassive black hole (such as Sgr A$^*$~).
+\rs{\sout{It is possible to measure the mass of nearby supermassive black holes by directly observing the dynamic motion of stars nearby the supermassive black hole (such as Sgr A$^*$~).
 However, this dynamic measurement method is challenging to utilise for  intermediate-mass black holes as their sphere of influence is too small to resolve motions~\cite{}.
@@
 
-\rory{\sout{In a similar vein, although the M-$\sigma$ and M-L relations (relations between the spheroidal bulge of a galaxy's velocity dispersion $\sigma$,  luminosity L, and its central black hole's mass M) can estimate the mass of supermassive black holes~\cite{Ferrarese & Merritt 2000 and Gebhardt et al.
+\rs{\sout{In a similar vein, although the M-$\sigma$ and M-L relations (relations between the spheroidal bulge of a galaxy's velocity dispersion $\sigma$,  luminosity L, and its central black hole's mass M) can estimate the mass of supermassive black holes~\cite{Ferrarese & Merritt 2000 and Gebhardt et al.
 2000}, they cannot accurately estimate the intermediate-masses.
@@
 
-\rory{\sout{Another method to estimate large black hole masses is with reverberation mapping, which estimates black hole virial masses by studying their nearby gasses' velocities~\cite{reverberation mapping}.
+\rs{\sout{Another method to estimate large black hole masses is with reverberation mapping, which estimates black hole virial masses by studying their nearby gasses' velocities~\cite{reverberation mapping}.
 Reverberation mapping has shown to estimate both supermassive black hole and intermediate-mass black hole virial masses successfully.
@@
 HLX-X1)~\cite{}.
-\rory{\sout{While stellar mass black holes are too small to generate such luminosities with Eddington accretion, intermediate mass black holes can accrete at rates large enough to account for the high luminosities~\cite{}.
+\rs{\sout{While stellar mass black holes are too small to generate such luminosities with Eddington accretion, intermediate mass black holes can accrete at rates large enough to account for the high luminosities~\cite{}.
 However, some argue that some stellar mass black holes may exceed the Eddington limit~\cite{}, and others argue that the X-ray emission might be from a collimated jet leading to an inaccurate mass calculation~\cite{}.}}
 
-\Finally, \rory{\sout{another channel to measure black hole masses is by identifying}} Gravitational waves from compact binaries coalesces (CBCs) \rory{are clean channels to measure BH masses} \rory{\sout{ inferring their source parameters~\cite{}.}} Mergers involving either a binary system with at least one intermediate-mass component, or a system whose merger results in an intermediate-mass remnant will have large initial total masses $\text{M}_{T}$.
+\Finally, \rs{\sout{another channel to measure black hole masses is by identifying}} Gravitational waves from compact binaries coalesces (CBCs) \rs{are clean channels to measure BH masses} \rs{\sout{ inferring their source parameters~\cite{}.}} Mergers involving either a binary system with at least one intermediate-mass component, or a system whose merger results in an intermediate-mass remnant will have large initial total masses $\text{M}_{T}$.
 As a binary's $\text{M}_{T}$ is associated with its merger frequency, $f\sim \text{M}_T^-1$, systems with large $\text{M}_{T}$ have very low merger frequencies $f < 100\ \text{Hz}$.

### 2021-03-29 main.tex

@@
 \section{Introduction}
-In the 1970s, X-ray and optical observations from the Cyg-X1 binary star system led to the discovery of the first stellar-mass black hole~\cite{Webster:1972:Natur}.
-Two years later, in 1974, radio observation of our galaxy center demonstrated the presence of a supermassive black hole -- Sgr A$^*$~\cite{Balick:1974:ApJ}.
-In the half-century since then, astronomers accumulated more definitive evidence that have established the  existence of stellar-mass black holes $\text{M}_\text{BH} < 10^{2} \ \msun$ and supermassive black holes, $\text{M}_\text{BH} > 10^{5} \ \msun$ in our universe (e.g.
-~\cite{Ghez:1998:ApJ, Genzel:2010:RvMP, Abbott:2019:PhRvX, EventHorizonTelescopeCollaboration:2019:ApJL, Abbott:2020:arXiv}).
-However, a gap in between the mass-ranges of these two categories has formed: there is a deficiency of observational evidence for black holes in the intermediate-mass range $10^{2} - 10^{5}\ \text{M}_{\odot}$.
-These intermediate-mass black holes must have existed to form the supermassive black holes detected to exist in the early universe~\cite{Banados:2018:Natur}.
+Since the 1970s, there has been a steady accumulation of evidence for stellar mass ($\text{M}_\text{BH} < 10^{2} \ \msun$) and supermassive black holes ($\text{M}_\text{BH} > 10^{5} \ \msun$)~cite{Webster:1972:Natur, Balick:1974:ApJ, Ghez:1998:ApJ, Genzel:2010:RvMP, Abbott:2019:PhRvX, EventHorizonTelescopeCollaboration:2019:ApJL, Abbott:2020:arXiv}.
+However, there is a deficiency of observational evidence for black holes in the intermediate-mass range $10^{2} - 10^{5}\ \text{M}_{\odot}$.
+Given the existence of supermassive black holes detected in the early universe, it is likely for intermediate-mass black holes to have also existed~\cite{Banados:2018:Natur}.
 However, we only have a handful of promising candidates~\cite{Greene:2004:ApJ, Graham:2013:ApJ, Mezcua:2017:IJMPD, Koliopanos:2017:mbhe, Lin:2020:ApJL, Greene:2020:ARA&A}, and one confirmed intermediate-mass black hole, the remnant of the gravitational wave event GW190521 with a mass of $142^{+28}_{-16}\ \msun$~\cite{Abbott:2020:PhRvL}.
@@
 Hence, the merger remnants require their recoil kick to be less than its environment's escape velocity to undergo successive mergers.
-This tight constraint makes hierarchical mergers a challenging scenario.}
+This tight constraint makes hierarchical mergers a challenging scenario.}}
 
@@
 In this framework, the candidates' ranking statistic is compared against a background distribution in a frequentist approach.
-On the other hand, the standard framework for performing parameter estimation and model selection in gravitational-wave astronomy is Bayesian inference.
+\rs{add a sentence describing what the ranking stats are for the different pipelines (key words: matched filtering, SNR etc...) and add citations!} On the other hand, the standard framework for performing parameter estimation and model selection in gravitational-wave astronomy is Bayesian inference.
 This work utilises Bayesian inference to calculate the Bayesian Coherence odds-ratio~\cite{BCR1}, \bcr, of high-mass candidates in LIGO's second observing run.
@@
 Our analysis of the high-mass IAS events and candidates in O2 has resulted in three events with disfavourable $\pastrobcr<0.5$ (GWC170402, GW170403, GW170425), and four events and one candidate with $\pastrobcr\geq0.5$ (GW170121, 170302, GW170304, GW170727, GW170817A).
+\rs{suggest an additional sentence comparing the numbers with greater/less than 0.5 to the numbers that IAS find.}
 
-GWC170402, detected by \citet{IAS2}, is reported to have a signal that is not described well by waveforms for circular binaries with aligned spins.
+GWC170402, detected by \citet{IAS2}, is reported to have a signal that is not described well by waveforms for circular binaries with aligned spins \rs{what does "not well described" mean?}.
 Hence, we might have received a low \pastrobcr due to our usage of \imrphenomp, a waveform that does not account for eccentricity.

### 2021-03-29 main.tex
Updates from Overleaf

@@
 Moreover, Population III stars with masses above $230 \ \msun$ will avoid electron-positron pair-instability.
-Therefore, oxygen and silicon burning will not drive an explosion, allowing the star to undergo a complete collapse to leave behind an intermediate-mass black hole remnant with a mass of $120-280 \ \msun$, dependant on the initial star mass \cite{Bond et al.
+Therefore, oxygen and silicon burning will not drive an explosion, allowing the star to undergo a complete collapse to leave behind an intermediate-mass black hole remnant with a mass of $120-280 \ \msun$, dependent on the initial star mass \cite{Bond et al.
 1984}.
@@
 Additionally, dynamic-measurements that have alluded to  intermediate-mass candidates, e.g.
-the candidate at the centre of the globular cluster 47 Tucanae~\cite{kiziltan 2017}, can also be attributed to simpler models without a central  intermediate-mass black hole~\cite{freire 2017}.
+the candidate at the center of the globular cluster 47 Tucanae~\cite{kiziltan 2017}, can also be attributed to simpler models without a central  intermediate-mass black hole~\cite{freire 2017}.
 }}
@@
 Although a significant fraction of the glitches can be removed by testing them for coherence amongst various ground based detectors and performing matched-filtering, these methods are insufficient to remove all the glitches.
-One method to account for more glitches while searching for high total mass CBC gravitational-waves is by utilising the astrophysical Bayesian odds~\cite{bci, BCR1, BCR2, bcr_gw151216, bayesian_odds}.
+One method to account for more glitches while searching for high total mass CBC gravitational-waves is by utilizing the astrophysical Bayesian odds~\cite{bci, BCR1, BCR2, bcr_gw151216, bayesian_odds}.
 A true Bayesian odds, calculated without using bootstrap techniques, can provide more accurate estimate of significance that does note depend on the search pipeline~\cite{BCR2, bcr_gw151216,  bayesian_odds}.
-In this paper, we utilise a Bayesian method, called the Bayesian Coherence Ratio \bcr~\cite{BCR1}, to rank the candidate gravitational-wave signals from high-mass compact binary coalescences (systems with total masses in the range of $55-500\ \msun$) in the detector data recorded during O2.
-Although the \bcr, utilising bootstrap techniques, does not provide the true Bayesian odds,  it utilizes Bayesian evidences which describe the explicit probability of data under the hypothesis that it contains coherent signals vs incoherent glitches.
+In this paper, we utilize a Bayesian method, called the Bayesian Coherence Ratio \bcr~\cite{BCR1}, to rank the candidate gravitational-wave signals from high-mass compact binary coalescences (systems with total masses in the range of $55-500\ \msun$) in the detector data recorded during O2.
+Although the \bcr, utilizing bootstrap techniques, does not provide the true Bayesian odds,  it utilizes Bayesian evidences which describe the explicit probability of data under the hypothesis that it contains coherent signals vs incoherent glitches.
 
@@
 \rs{add a sentence describing what the ranking stats are for the different pipelines (key words: matched filtering, SNR etc...) and add citations!} On the other hand, the standard framework for performing parameter estimation and model selection in gravitational-wave astronomy is Bayesian inference.
-This work utilises Bayesian inference to calculate the Bayesian Coherence odds-ratio~\cite{BCR1}, \bcr, of high-mass candidates in LIGO's second observing run.
+This work utilizes Bayesian inference to calculate the Bayesian Coherence odds-ratio~\cite{BCR1}, \bcr, of high-mass candidates in LIGO's second observing run.
 We use the \bcr not as an odds-ratio but instead as a ranking statistic, a step toward building a unified Bayesian framework to search for candidates and estimate their parameters.
@@
     \mathcal{Z}(d|\mathcal{H}) = \int\limits_{\parameters} \ \mathcal{L}(d|\parameters,\mathcal{H}) \ \pi(\parameters | \mathcal{H}) \ d\parameters
-\end{equation} is the likelihood after marginalising over the parameters \parameters.
+\end{equation} is the likelihood after marginalizing over the parameters \parameters.
 To compare two hypotheses $\mathcal{H}_A$ and $\mathcal{H}_B$ with the Bayes theorem one can calculate an odds-ratio
@@
 For our study, we filter the background, simulated and candidate events to include only high-mass events with masses in the ranges of the parameters presented in Table~\ref{tab:parameters}.
-A plot of the \pycbc triggers from one time-frame, during April 23 - May 8, 2017, is presented in Figure~\ref{fig:templateBank}.
+A plot of the \pycbc triggers from one time-frame, during April 23 - May 8, 2017, is presented in Fig.~\ref{fig:templateBank}.
 This figure also depicts the gravitational-wave templates used during the search through this time-frame of data.
@@
 To evaluate $Z^S$, $Z^G_i$ and $Z^N_i$ and calculate the \bcr Eq.~\ref{eq:bcr} for triggers, we carry out Bayesian inference with \bilby~\cite{bilby, bilby_pipe}, employing \dynesty~\cite{dynesty} as our nested sampler.
-Nested sampling, an algorithm introduced by~\citet{skilling2004, skilling2006}, provides an estimate of the true Bayesian evidence and is often utilised for parameter estimation within the LIGO collaboration~\cite{bilby, bilby_paper, pbilby_paper}.
+Nested sampling, an algorithm introduced by~\citet{skilling2004, skilling2006}, provides an estimate of the true Bayesian evidence and is often utilized for parameter estimation within the LIGO collaboration~\cite{bilby, bilby_paper, pbilby_paper}.
 
 The most computationally intensive step during Bayesian inference is evaluating the likelihood $\mathcal{L}(d_i|\template)$.
-To accelerate our analysis, we use a likelihood that explicitly marginalises over coalescence time, phase at coalescence, and luminosity distance (Eq.~80 from~\citet{intro_to_gw_bayes}).
-While this marginalised likelihood reduces the run time without introducing errors to our evidence evaluation, it does not generates samples for the marginalised parameters.
+To accelerate our analysis, we use a likelihood that explicitly marginalizes over coalescence time, phase at coalescence, and luminosity distance (Eq.~80 from~\citet{intro_to_gw_bayes}).
+While this marginalized likelihood reduces the run time without introducing errors to our evidence evaluation, it does not generates samples for the marginalized parameters.
 However, these parameter samples can be calculated as a post-processing step~\cite{intro_to_gw_bayes}.
@@
 
-The waveform template we utilise is \imrphenomp, a phenomenological waveform template constructed in the frequency domain that models the in-spiral, merger, and ringdown (IMR) of a compact binary coalescence~\citep{khan2016frequency}.
+The waveform template we utilize is \imrphenomp, a phenomenological waveform template constructed in the frequency domain that models the in-spiral, merger, and ring-down (IMR) of a compact binary coalescence~\citep{khan2016frequency}.
 Although there exist gravitational-wave templates such as \seob~\cite{seobnrv4phm} which incorporate more physics, such as information on higher-order modes, we use \imrphenomp as it is computationally inexpensive compared to others.
 
-We take 31 neighbouring, off-source, non-overlapping,  4-second  segments of time-series data before the analysis data segment $d_i$ to generate the PSD.
+We take 31 neighboring, off-source, non-overlapping,  4-second  segments of time-series data before the analysis data segment $d_i$ to generate the PSD.
 We use off-source to avoid the inclusion of a signal in the PSD calculation.
@@
 Like other PSD estimation methods, this method adds statistical uncertainties to the PSD~\cite{psd_student_t, chatziioannou2019noise}.
-To marginalise over the statistical uncertainty, we use the median-likelihood presented by~\citet{psd_student_t} as a post-processing step.
+To marginalize over the statistical uncertainty, we use the median-likelihood presented by~\citet{psd_student_t} as a post-processing step.
 \avi{Greg would like me to discuss the effect of the PSD marginalization in more detail}
+
+We take 31 neighboring off-source non-overlapping  4-second  segments of time-series data before the analysis data segment $d_i$ to generate the PSD.
+A Tukey window with a 0.2-second roll-off is applied to each data segment to suppress spectral leakage.
+After this  the segments are fast-Fourier transformed and median-averaged to create a PSD~\cite{ligo_psd}.
+Like other PSD estimation methods, this method adds statistical uncertainties to the PSD~\cite{psd_student_t, chatziioannou2019noise, Biscoveanu:2020:PhRvD}.
+To marginalize over the statistical uncertainty, we use the median-likelihood presented by~\citet{psd_student_t} as a post-processing step.
+We find that this post-processing step improves the search efficiency by $x\%$ the details of this calculation are presented in the Appendix~\ref{sec:psd-marginalization}.
 
@@
 Using the tuned prior odds the \bcr for the candidate events can be calculated.
-Figure~\ref{fig:bcrCdf} shows the \bcr distributions for the background triggers, simulated triggers and candidate events.
+Fig.~\ref{fig:bcrCdf} shows the \bcr distributions for the background triggers, simulated triggers and candidate events.
 The bulk of the background and simulated trigger distributions are separate but slightly overlap due to some of the simulated signal's being very faint.
 The separation suggests that the \bcr can successfully distinguish signals from noise or glitches.
-The vertical lines in Figure~\ref{fig:bcrCdf} displays the \bcr for gravitational-wave candidate events.
+The vertical lines in Fig.~\ref{fig:bcrCdf} displays the \bcr for gravitational-wave candidate events.
 On comparing the candidate event \bcr values with the background distribution, we can estimate \pastro values for the candidate events.
@@
 \caption[BCR distribution example]{Histograms represent the survival function (1-CDF) from our high-mass selection of background triggers (grey) and simulated signals (blue) triggers obtained from \pycbc's search of data from $\text{August 13 - 21, 2017}$.
-Vertical lines mark the $\text{ln}\ \bcr$ of IAS's GW170817 and GWTC-1's GW170814.}\label{fig:bcrCdf}
+Vertical lines mark the $\text{ln}\ \bcr$ of IAS's GW170817A and GWTC-1's GW170814.}\label{fig:bcrCdf}
 \end{figure}
@@
 \input{Data/results_table}
-We analyse the $60\ 996$ background, $5\ 146$ simulated, and $25$ candidate triggers reported by \pycbc's search on the data from LIGO's second observing run, restricting our analysis to the triggers that fall within our mass-space as described in Section~\ref{sec:method}.
-In addition to these triggers, we also analyse events and candidate events reported by GWTC-1 and the IAS group (note that some of these were identified as candidates by the \pycbc search).
+We analyse the $60,996$ background, $5,146$ simulated, and $25$ candidate triggers reported by \pycbc's search on the data from LIGO's second observing run, restricting our analysis to the triggers that fall within our mass-space as described in Section~\ref{sec:method}.We also analyse events and candidate events reported by GWTC-1 and the IAS group (note: some of these were identified as candidates by the \pycbc search).
 In Table~\ref{tab:results}, we summarise the \pastrobcr, along with the \pastro of other pipelines for comparison.
@@
 
+\section{Marginalizing over PSD statistical uncertainties}\label{sec:psd-marginalization}
+To generate the results in Fig.~\ref{fig:bcrCdf}, we applied a post-processing step to marginalize the uncertainty in the PSD.
+In Fig.~\ref{fig:bcrCdfUnmarginalized}, we show the results if this post-processing step is not applied.
+Clearly, marginalizing over uncertainty in the PSD yields an improvement in the separation of the noise and signal distributions.
+Quantitatively, this results in a reduction in the rate of false alarms from X to Y and a reduction in the rate of false positives from X to Y in the August 13 - 21, 2017 time-frame of data.
+For the entirety of O2 PSD marginalisation resulted in a reduction of X, or an $x\%$ improvement in search efficency.
+
+\begin{figure}[!ht]
+{\centering \includegraphics[width=0.85\linewidth]{images/bcr_cdf_smaller_legend.png} }
+\caption[BCR distribution example]{This plot is analogous to Fig.~\ref{fig:bcrCdf}, but without using the post-processing step to marginalize over PSD statistical uncertainties.
+Without the post-processing step, there is a greater overlap between the background (grey) and foreground (blue) survival functions.
+For more details about this plot, refer to the caption of Fig.~\ref{fig:bcrCdf}.}\label{fig:bcrCdfUnmarginalized}
+\end{figure}
+
 \section{Tuned prior odds}\label{apdx:alphabeta}

### 2021-04-08 main.tex
Updates from Overleaf

@@
 \section{Introduction}
-Since the 1970s, there has been a steady accumulation of evidence for stellar mass ($\text{M}_\text{BH} < 10^{2} \ \msun$) and supermassive black holes ($\text{M}_\text{BH} > 10^{5} \ \msun$)~cite{Webster:1972:Natur, Balick:1974:ApJ, Ghez:1998:ApJ, Genzel:2010:RvMP, Abbott:2019:PhRvX, EventHorizonTelescopeCollaboration:2019:ApJL, Abbott:2020:arXiv}.
+Since the 1970s, there has been a steady accumulation of evidence for stellar mass ($\text{M}_\text{BH} < 10^{2} \ \msun$) and supermassive black holes ($\text{M}_\text{BH} > 10^{5} \ \msun$)~\cite{Webster:1972:Natur, Balick:1974:ApJ, Ghez:1998:ApJ, Genzel:2010:RvMP, Abbott:2019:PhRvX, EventHorizonTelescopeCollaboration:2019:ApJL, Abbott:2020:arXiv}.
 However, there is a deficiency of observational evidence for black holes in the intermediate-mass range $10^{2} - 10^{5}\ \text{M}_{\odot}$.
-Given the existence of supermassive black holes detected in the early universe, it is likely for intermediate-mass black holes to have also existed~\cite{Banados:2018:Natur}.
-However, we only have a handful of promising candidates~\cite{Greene:2004:ApJ, Graham:2013:ApJ, Mezcua:2017:IJMPD, Koliopanos:2017:mbhe, Lin:2020:ApJL, Greene:2020:ARA&A}, and one confirmed intermediate-mass black hole, the remnant of the gravitational wave event GW190521 with a mass of $142^{+28}_{-16}\ \msun$~\cite{Abbott:2020:PhRvL}.
+Astronomers have detected a handful of intermediate-masses candidates using reverberation mapping, taking direct kinematic measurements, applying  M-$\sigma$ and M-L relations, and also studying  X-ray luminosity and spectra~\cite{Greene:2004:ApJ, Graham:2013:ApJ, Mezcua:2017:IJMPD, Koliopanos:2017:mbhe, Lin:2020:ApJL, Greene:2020:ARA&A}.
+However, these observations are highly uncertain and can be attributed to sources without intermediate-mass black holes~\cite{kiziltan2017, freire2017}.
+In the last few years, astronomers have found definitive evidence for two intermediate-mass black holes, (i) the $142^{+28}_{-16}\ \msun$ remnant observed from the gravitational wave event GW190521~\cite{Abbott:2020:PhRvL}, and the $5.5^{+1.7}_{-0.9}\times10^{4}\ \msun$ black hole identified from gravitational lensing in the light curve of GRB950830~\cite{paynter_evidence_2021}.
 The concrete discovery of more intermediate-mass black holes will bridge the observational gap and illuminate our understanding of galaxy and supermassive black hole formation.
+Additionally, a catalog of observed intermediate-mass black holes can act as probes to their formation environments, such as in the accretion disks of active galactic nuclei~\cite{}, the centers of dense stellar clusters~\cite{}, and even Population-III stars~\cite{}.
 
-The two main proposed formation channels for Intermediate-mass black holes are the light-seed and the heavy-seed channels.
-The light-seed channel involves dynamic interactions of low-mass seeds, e.g.
-hierarchical mergers of stellar-mass black holes~\cite{}, runaway collisions of stars~\cite{}.
-The heavy-seed channel involves the direct collapse of high-mass seeds, e.g.
-the direct collapse of giant metal-free Population III stars~\cite{}, early protogalaxies' collapse~\cite{}.
-Although promising pathways, there are challenging obstacles both scenarios must overcome to pathways that can form intermediate-mass black holes.
+% Given the existence of supermassive black holes detected in the early universe, it is likely for intermediate-mass black holes to have also existed~\cite{Banados:2018:Natur}.
+However, we only have a handful of promising candidates~\cite{Greene:2004:ApJ, Graham:2013:ApJ, Mezcua:2017:IJMPD, Koliopanos:2017:mbhe, Lin:2020:ApJL, Greene:2020:ARA&A}, and two confirmed intermediate-mass black holes, (i) the $142^{+28}_{-16}\ \msun$ remnant observed from the gravitational wave event GW190521~\cite{Abbott:2020:PhRvL}, and the $5.5^{+1.7}_{-0.9}\times10^{4}\ \msun$ black hole identified from gravitational lensing in the light curve of GRB950830~\cite{paynter_evidence_2021}.
+The concrete discovery of more intermediate-mass black holes will bridge the observational gap and illuminate our understanding of galaxy and supermassive black hole formation.
+Additionally, a catalog of observed intermediate-mass black holes can act as probes to their formation environments, such as in the accretion disks of active galactic nuclei~\cite{}, the centers of dense stellar clusters~\cite{}, and even Population-III stars~\cite{}.
 
-Hierarchical mergers in active galactic nuclei migration-traps, globular and stellar clusters may be a feasible light-seed method for black holes to accumulate mass and reach the intermediate-mass range.
-\rs{\sout{However, when black holes merge, they can receive recoil-kicks up to $\sim$2,500 km/s~\cite{}.
-Hence, the merger remnants require their recoil kick to be less than its environment's escape velocity to undergo successive mergers.
-This tight constraint makes hierarchical mergers a challenging scenario.}}
+% However, measuring the mass of black holes can be challenging. Several observational techniques to identify intermediate mass black holes
 
-One proposed heave-seed pathway involves the direct collapse of massive, metal-free Population III stars.
-Typically, massive stars $> 100 \ \msun$ can eject more than half of their mass in the form of radiatively driven stellar winds~\cite{}.
-However, at zero metallicity, mass loss through stellar winds is negligible \cite{Kudritzki 2000}.
-Consequently,  Population III stars have the opportunity to complete their life-cycles without losing a significant portion of their mass.
-Moreover, Population III stars with masses above $230 \ \msun$ will avoid electron-positron pair-instability.
-Therefore, oxygen and silicon burning will not drive an explosion, allowing the star to undergo a complete collapse to leave behind an intermediate-mass black hole remnant with a mass of $120-280 \ \msun$, dependent on the initial star mass \cite{Bond et al.
-1984}.
-As the fraction of Population III stars with masses above $230 \ \msun$ is uncertain, the number of expected intermediate-mass black holes from these stars is also ambiguous~\cite{Coleman Miller, Formation Scenarios for Intermediate-Mass Black Holes}.
-
-To verify and determine details on which formation channel is favoured, a catalog of observed intermediate-black holes and their masses is required.
-However, measuring the mass of black holes can be challenging.
-
-\rs{\sout{It is possible to measure the mass of nearby supermassive black holes by directly observing the dynamic motion of stars nearby the supermassive black hole (such as Sgr A$^*$~).
-However, this dynamic measurement method is challenging to utilise for  intermediate-mass black holes as their sphere of influence is too small to resolve motions~\cite{}.
+% It is possible to measure the mass of nearby supermassive black holes by directly observing the dynamic motion of stars nearby the supermassive black hole (such as Sgr A$^*$~).
+However, this dynamic measurement method is challenging to utilize for  intermediate-mass black holes as their sphere of influence is too small to resolve motions~\cite{}.
 Additionally, dynamic-measurements that have alluded to  intermediate-mass candidates, e.g.
-the candidate at the center of the globular cluster 47 Tucanae~\cite{kiziltan 2017}, can also be attributed to simpler models without a central  intermediate-mass black hole~\cite{freire 2017}.
+the candidate at the center of the globular cluster 47 Tucanae~\cite{kiziltan2017}, can also be attributed to simpler models without a central intermediate-mass black hole~\cite{freire 2017}.
 }}
 
-\rs{\sout{In a similar vein, although the M-$\sigma$ and M-L relations (relations between the spheroidal bulge of a galaxy's velocity dispersion $\sigma$,  luminosity L, and its central black hole's mass M) can estimate the mass of supermassive black holes~\cite{Ferrarese & Merritt 2000 and Gebhardt et al.
+% \rs{\sout{In a similar vein, although the M-$\sigma$ and M-L relations (relations between the spheroidal bulge of a galaxy's velocity dispersion $\sigma$,  luminosity L, and its central black hole's mass M) can estimate the mass of supermassive black holes~\cite{Ferrarese & Merritt 2000 and Gebhardt et al.
 2000}, they cannot accurately estimate the intermediate-masses.
@@
 
-\rs{\sout{Another method to estimate large black hole masses is with reverberation mapping, which estimates black hole virial masses by studying their nearby gasses' velocities~\cite{reverberation mapping}.
+% \rs{\sout{Another method to estimate large black hole masses is with reverberation mapping, which estimates black hole virial masses by studying their nearby gasses' velocities~\cite{reverberation mapping}.
 Reverberation mapping has shown to estimate both supermassive black hole and intermediate-mass black hole virial masses successfully.
@@
 
-The most promising intermediate-mass candidates found with electromagnetic-spectra are Ultra-Luminous X-ray sources with luminosities $> 10^{39} \text{erg s}^{-1}$ (e.g.
+% The most promising intermediate-mass candidates found with electromagnetic-spectra are Ultra-Luminous X-ray sources with luminosities $> 10^{39} \text{erg s}^{-1}$ (e.g.
 HLX-X1)~\cite{}.
@@
 
-\Finally, \rs{\sout{another channel to measure black hole masses is by identifying}} Gravitational waves from compact binaries coalesces (CBCs) \rs{are clean channels to measure BH masses} \rs{\sout{ inferring their source parameters~\cite{}.}} Mergers involving either a binary system with at least one intermediate-mass component, or a system whose merger results in an intermediate-mass remnant will have large initial total masses $\text{M}_{T}$.
-As a binary's $\text{M}_{T}$ is associated with its merger frequency, $f\sim \text{M}_T^-1$, systems with large $\text{M}_{T}$ have very low merger frequencies $f < 100\ \text{Hz}$.
-Hence, ground based gravitational wave detectors ($\sim 10 - 1000\ \text{Hz}$) are sensitive to the last milliseconds of merging systems with $100 \msun < \text{M}_{T} < 500 \msun$, while space-based detectors ($\sim 0.1 - 10\ \text{Hz}$) can study the full signals of merging systems with $10^4 \msun < \text{M}_{T} < 10^7 \msun$.
+Gravitational waves from compact binaries coalesces (CBCs) are clean channels to measure BH masses.
+Mergers involving either a binary system with at least one intermediate-mass component, or a system whose merger results in an intermediate-mass remnant will have large initial total masses $\text{M}_{T}$.
+As a binary's $\text{M}_{T}$ is associated with its merger frequency, $f\sim \text{M}_{T}^{-1}$, systems with large $\text{M}_{T}$ have very low merger frequencies $f < 100\ \text{Hz}$.
+Hence, ground based gravitational wave detectors ($\sim 10 - 1000\ \text{Hz}$) are sensitive to the last milliseconds of merging systems with $100 \msun < \text{M}_{T} < 400 \msun$~\cite{}, while space-based detectors ($\sim 0.1 - 10\ \text{Hz}$) can study the full signals of merging systems with $10^4 \msun < \text{M}_{T} < 10^7 \msun$~\cite{}.
 
@@
 After calculating the \bcr for a set of background triggers and simulated triggers from as stretch of detector-data (a data chunk), we can compute probability distributions for the background and simulated triggers, $p_b(\bcr)$ and $p_s(\bcr)$.
-We expect the background trigger and simulated signal \bcr values to favour the incoherent glitch and the coherent signal hypothesis, respectively.
+We expect the background trigger and simulated signal \bcr values to favor the incoherent glitch and the coherent signal hypothesis, respectively.
 Ideally, these distributions representing two unique populations should be distinctly separate and have no overlap in their \bcr values.
@@
 Clearly, marginalizing over uncertainty in the PSD yields an improvement in the separation of the noise and signal distributions.
-Quantitatively, this results in a reduction in the rate of false alarms from X to Y and a reduction in the rate of false positives from X to Y in the August 13 - 21, 2017 time-frame of data.
-For the entirety of O2 PSD marginalisation resulted in a reduction of X, or an $x\%$ improvement in search efficency.
+Quantitatively, at a threshold $\bcr_T=0$ the post-processing step results in a reduction in the number of background $\bcr > \bcr_T$ from $60.7\%$ to $25.28\%$ in the August 13 - 21, 2017 time-frame of data.
+For the entirety of O2 PSD marginalization resulted in a $49.26\%$ improvement in search efficiency.
 

### 2021-04-08 scripts/make_bcr_cdf.py
ad orig dataset

@@ -1,15 +1,13 @@
+import matplotlib.font_manager
 from bcr_pipeline.post_processing.bcr_plotting.main_analysis_plots import \
     pack_plotting_data
 from bcr_pipeline.post_processing.bcr_plotting.make_ranking_stat_probability_plot import (
     _add_rank_pdf)
 from matplotlib import pyplot as plt
+from matplotlib import rc
 from matplotlib import rcParams
 from matplotlib.lines import Line2D
-from matplotlib.ticker import (MultipleLocator,
-                               FormatStrFormatter,
-                               AutoMinorLocator)
-import matplotlib.font_manager
-from matplotlib import rc
+from matplotlib.ticker import (FormatStrFormatter)
 
 # matplotlib.font_manager.findfont("font.sans-serif", rebuild_if_missing=False)
 all_fonts = matplotlib.font_manager.findSystemFonts()
@@ -44,20 +42,38 @@ plt.rcParams['ytick.major.width'] = 2.5
 plt.rcParams['xtick.top'] = True
 plt.rcParams['ytick.right'] = True
 
-
-
 BANK = "../data/template_bank.csv"
-INJECTION = "../data/chunk21_res/injection_res.csv"
-BACKGROUND = "../data/chunk21_res/background_res.csv"
-FOREGROUND = "../data/chunk21_res/foreground_res.csv"
+INJECTION_REW = "../data/chunk21_res/injection_res.csv"
+BACKGROUND_REW = "../data/chunk21_res/background_res.csv"
+FOREGROUND_REW = "../data/chunk21_res/foreground_res.csv"
+INJECTION_ORIG = "../data/chunk21_orig/injection.csv"
+BACKGROUND_ORIG = "../data/chunk21_orig/background.csv"
+FOREGROUND_ORIG = "../data/chunk21_orig/foreground.csv"
+INJECTION="INJECTION"
+BACKGROUND="BACKGROUND"
+FOREGROUND="FOREGROUND"
+
+DATA = dict(
+    orig=dict(
+        INJECTION=INJECTION_ORIG,
+        BACKGROUND=BACKGROUND_ORIG,
+        FOREGROUND=FOREGROUND_ORIG,
+    ),
+    reweighted=dict(
+        INJECTION=INJECTION_REW,
+        BACKGROUND=BACKGROUND_REW,
+        FOREGROUND=FOREGROUND_REW,
+    ),
+)
+
 CATALOG = "../data/catalog.csv"
 
 
-def plot():
+def plot(data_type='orig', add_legend=False):
[…]

### 2021-04-08 scripts/make_bcr_cdf.py
remo0ve grid

@@ -25,7 +25,7 @@ rcParams["text.usetex"] = True
 rcParams['axes.labelsize'] = 30
 rcParams['axes.titlesize'] = 30
 rcParams['axes.labelpad'] = 10
-rcParams['axes.linewidth'] = 2.5
+rcParams['axes.linewidth'] = 3
 rcParams['axes.edgecolor'] = 'black'
 rcParams['xtick.labelsize'] = 25
 rcParams['xtick.major.size'] = 10.0
@@ -105,6 +105,7 @@ def plot(data_type='orig', add_legend=False):
     # colors = ["#d8d8d8", "#daf0f8", "#0173b2", "#e9b457"]
     # custom_lines = [Line2D([0], [0], color=c, lw=4) for c in colors]
     # l = ax_cdf.legend(custom_lines, labels, **lg_kwargs)
+    ax_cdf.grid(False)
     bbox_extra_artists = []
     if add_legend:
         lg_kwargs = dict(fontsize="small", loc="lower right",

### 2021-04-08 main.tex
Updates from Overleaf

@@
 \begin{figure}[!ht]
-{\centering \includegraphics[width=0.85\linewidth]{images/bcr_cdf_smaller_legend.png} }
+{\centering \includegraphics[width=0.85\linewidth]{images/reweighted_bcr_cdf_smaller_legend.png} }
 \caption[BCR distribution example]{Histograms represent the survival function (1-CDF) from our high-mass selection of background triggers (grey) and simulated signals (blue) triggers obtained from \pycbc's search of data from $\text{August 13 - 21, 2017}$.
@@
 \begin{figure}[!ht]
-{\centering \includegraphics[width=0.85\linewidth]{images/bcr_cdf_smaller_legend.png} }
+{\centering \includegraphics[width=0.85\linewidth]{images/orig_bcr_cdf_smaller_legend.png} }
 \caption[BCR distribution example]{This plot is analogous to Fig.~\ref{fig:bcrCdf}, but without using the post-processing step to marginalize over PSD statistical uncertainties.

### 2021-04-15 authors.tex
edits for v2

--- 2021-01-18 authors.tex
@@
 %------ affiliation shortcuts
-\newcommand{\SPAno}{1}
-\newcommand{\OzGravMonashno}{2}
-\newcommand{\CITno}{3}
-\newcommand{\MITno}{4}
-\newcommand{\Kavlino}{5}
+\newcommand{\SPAno}{School of Physics and Astronomy, Monash University, Clayton VIC 3800, Australia}
+\newcommand{\OzGravMonashno}{OzGrav: The ARC Centre of Excellence for Gravitational Wave Discovery, Clayton VIC 3800, Australia}
+\newcommand{\CITno}{LIGO Laboratory, California Institute of Technology, Pasadena, CA 91125, USA}
+\newcommand{\MITno}{LIGO Laboratory, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
+\newcommand{\Kavlino}{Department of Physics and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, 77 Massachusetts Ave, Cambridge, MA 02139, USA}
 
-%--------------------------
-\newcommand{\SPA}{School of Physics and Astronomy, Monash University, Clayton VIC 3800, Australia}
-\newcommand{\OzGravMonash}{OzGrav: The ARC Centre of Excellence for Gravitational Wave Discovery, Clayton VIC 3800, Australia}
-\newcommand{\MIT}{LIGO Laboratory, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
-\newcommand{\Kavli}{Department of Physics and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, \\ 77 Massachusetts Ave, Cambridge, MA 02139, USA}
-\newcommand{\CIT}{LIGO Laboratory, California Institute of Technology, Pasadena, CA 91125, USA}
-\author{
-\parbox{\textwidth}{
-A.~Vajpeyi$^{\SPAno,\OzGravMonashno}$, %ORCID:0000-0002-4146-1132
-R.~Smith$^{\SPAno,\OzGravMonashno}$, %ORCID:0000-0001-8516-3324
-E.~Thrane$^{\SPAno,\OzGravMonashno}$, %0000-0002-4418-3895
-G.~Ashton$^{\SPAno,\OzGravMonashno}$, %ORCID:0000-0001-7288-2231 
-J.~Kanner$^\CITno$, 
-T.~Alford$^\CITno$, 
-L.~Xiao$^\CITno$, %0000-0003-2703-449X
-M.~Isi$^{\MITno,\Kavlino}$, %0000-0001-8040-9807
-S.~Garza$^\CITno$, 
-}\vspace{0.2cm}\\
-$^1$\SPA\\
-$^2$\OzGravMonash\\
-$^3$\CIT\\
-$^4$\MIT\\
-$^5$\Kavli\\
-}
+\author{A.~Vajpeyi}
+\affiliation{\SPAno}
+\affiliation{\OzGravMonashno}
+\author{R.~Smith}
+\affiliation{\SPAno}
+\affiliation{\OzGravMonashno}
+\author{E.~Thrane}
+\affiliation{\SPAno}
+\affiliation{\OzGravMonashno}
+\author{G.~Ashton}
+\affiliation{\SPAno}
+\affiliation{\OzGravMonashno}
+\author{T.~Alford}
+\affiliation{\CITno}
+\author{S.~Garza}
+\affiliation{\CITno}
+\author{M.~Isi}
+\affiliation{\MITno}
+\affiliation{\Kavlino}
+\author{J.~Kanner}
+\affiliation{\CITno}
+\author{T.J.~Massinger}
+\affiliation{\CITno}
+\author{L.~Xiao}
+\affiliation{\CITno}
+
+% \affiliation[\OzGravMonashno]{}
+% \affiliation[\MITno]}
+% \affiliation[\Kavlino]{}
+% \affiliation[\CITno]{}

### 2021-04-15 main.tex
edits for v2

@@
 %floatfix,
- twocolumn
+ twocolumn,
+ superscriptaddress
 ]{revtex4-2}
@@
 \newcommand{\gstlal}{{\sc GstLAL}\xspace}
+\newcommand{\cwb}{{\sc cWB}\xspace}
 \newcommand{\pycbc}{{\sc \href{https://pycbc.org/}{\texttt{PyCBC}}}\xspace}
+
+\newcommand{\GWTC}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2019PhRvX...9c1040A/abstract}{\texttt{GWTC-1}}}\xspace}
+\newcommand{\OGC}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2020ApJ...891..123N/abstract}{\texttt{2-OGC}}}\xspace}
+\newcommand{\IAS}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2020PhRvD.101h3030V/abstract}{\texttt{IAS}}}\xspace}
 
@@
 \newcommand{\avi}[1]{\textcolor{orange}{[AV: #1]}}
+\newcommand{\greg}[1]{\textcolor{purple}{[Greg: #1]}}
 \newcommand{\rs}[1]{\textcolor{red}{[RS: #1]}}
@@
 
-% %%% AFFILIATIONS
-% %------ affiliation shortcuts
-% \newcommand{\SPAno}{1}
-% \newcommand{\OzGravMonashno}{2}
-% \newcommand{\CITno}{3}
-% \newcommand{\MITno}{4}
-% \newcommand{\Kavlino}{5}
-
-% %--------------------------
-% \newcommand{\SPA}{School of Physics and Astronomy, Monash University, Clayton VIC 3800, Australia}
-% \newcommand{\OzGravMonash}{OzGrav: The ARC Centre of Excellence for Gravitational Wave Discovery, Clayton VIC 3800, Australia}
-% \newcommand{\MIT}{LIGO Laboratory, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
-% \newcommand{\Kavli}{Department of Physics and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, \\ 77 Massachusetts Ave, Cambridge, MA 02139, USA}
-% \newcommand{\CIT}{LIGO Laboratory, California Institute of Technology, Pasadena, CA 91125, USA}
-% %%%
-
 \begin{document}
 
-\title{A Bayesian ranking statistic to find high-mass black holes in LIGO--Virgo data}
+\title{A search for high-mass black holes in data from the second LIGO observing run using a Bayesian ranking-statistic}
 
-% \input{authors}
-%\author[1]{Test}
-%\affil[1]{Test Affil}
+\input{authors}
 
@@
 \begin{abstract}
-The detection of intermediate-mass black holes ( $10^2-10^6$~\msun) will shed light on the formation of supermassive black holes and thus galaxy formation.
-Although LIGO is sensitive to the merger of binary black holes with total masses up to $400$~\msun, only 4 of their 50 detections have a total mass $>100$~\msun with >95\% credibility.
-A possible explanation for the absence of intermediate-mass events may be their misclassification as short-duration instrumental noise transients.
-Short-duration instrumental transients mimic the short-duration gravitational-wave signals from intermediate-mass binary black hole mergers.
-\et{I think the preceding text is misleading.
-We make it sound like we expect a uniform distribution of total mass, and so it's a surprising that we don't see IMBH.
-However, in reality, it is theoretically challenging to make IMBH.
-You need an exceptionally massive progenitor star to avoid pair instability supernova.
-Or, maybe you can make IMBH from hierarchical mergers or accretion.
-No one expects them to be common, but they are  interesting because of their connection to supermassive black holes.
-I suggest rewriting the preceding text to explain how IMBH might form and why they are interesting to look for.}
-Here we demonstrate a ranking statistic utilising Bayesian inference for the detection of high-mass binary black hole mergers (with a total mass $>55$~\msun).
-\et{Claims of beating matched filtering not yet borne out.} We apply this technique on the high-mass triggers during LIGO's second observing run to search for previously unresolved gravitational-wave signals from high-mass binary black holes.
-Our analysis does not discover new gravitational-wave events.
-However, we find support for some previously identified borderline detections.
-\et{Don't oversell Bayesian measure since our method is only semi-Bayesian.}
+The detection of an intermediate-mass black hole population ($10^2-10^6$~\msun) will provide probes to their formation environments (e.g., disks of active galactic nuclei, globular clusters) and illuminate a potential pathway to produce supermassive black holes.
+Numerous methods to search for $10^4-10^6\ \msun$ intermediate-mass black holes exist, while the primary method to find $10^2-10^3\ \msun$ is by identifying gravitational-waves emitted from the merger of stellar binaries.
+Theoretically, ground-based gravitational-wave detectors are sensitive to such mergers and have found one $142^{+28}_{-16}\ \msun$ intermediate-mass black hole.
+In reality, ground-based detectors are plagued with short-duration instrumental transients that mimic the gravitational-wave signals from mergers capable of producing intermediate-mass black holes.
+Here we demonstrate a ranking statistic utilizing Bayesian inference to detect high-mass binary black hole mergers (with a total mass $>55$~\msun).
+We apply this technique to the high-mass triggers during LIGO's second observing run to search for previously unresolved gravitational-wave signals from high-mass binary black holes.
+Our analysis does not discover new intermediate-mass black holes.
+However, we find support for some previously identified borderline stellar-mass binary black hole detections and gravitational-wave detections made externally from the LIGO-Virgo-KAGRA collaboration.
 \end{abstract}
@@
 \section{Introduction}
-Since the 1970s, there has been a steady accumulation of evidence for stellar mass ($\text{M}_\text{BH} < 10^{2} \ \msun$) and supermassive black holes ($\text{M}_\text{BH} > 10^{5} \ \msun$)~\cite{Webster:1972:Natur, Balick:1974:ApJ, Ghez:1998:ApJ, Genzel:2010:RvMP, Abbott:2019:PhRvX, EventHorizonTelescopeCollaboration:2019:ApJL, Abbott:2020:arXiv}.
-However, there is a deficiency of observational evidence for black holes in the intermediate-mass range $10^{2} - 10^{5}\ \text{M}_{\odot}$.
-Astronomers have detected a handful of intermediate-masses candidates using reverberation mapping, taking direct kinematic measurements, applying  M-$\sigma$ and M-L relations, and also studying  X-ray luminosity and spectra~\cite{Greene:2004:ApJ, Graham:2013:ApJ, Mezcua:2017:IJMPD, Koliopanos:2017:mbhe, Lin:2020:ApJL, Greene:2020:ARA&A}.
-However, these observations are highly uncertain and can be attributed to sources without intermediate-mass black holes~\cite{kiziltan2017, freire2017}.
-In the last few years, astronomers have found definitive evidence for two intermediate-mass black holes, (i) the $142^{+28}_{-16}\ \msun$ remnant observed from the gravitational wave event GW190521~\cite{Abbott:2020:PhRvL}, and the $5.5^{+1.7}_{-0.9}\times10^{4}\ \msun$ black hole identified from gravitational lensing in the light curve of GRB950830~\cite{paynter_evidence_2021}.
-The concrete discovery of more intermediate-mass black holes will bridge the observational gap and illuminate our understanding of galaxy and supermassive black hole formation.
-Additionally, a catalog of observed intermediate-mass black holes can act as probes to their formation environments, such as in the accretion disks of active galactic nuclei~\cite{}, the centers of dense stellar clusters~\cite{}, and even Population-III stars~\cite{}.
+Since the 1970s, there has been a steady accumulation of evidence for stellar mass ($\text{M}_\text{BH} < 10^{2} \ \msun$) and supermassive black holes ($\text{M}_\text{BH} > 10^{6} \ \msun$)~\cite{Webster:1972:Natur, Balick:1974:ApJ, Ghez:1998:ApJ, Genzel:2010:RvMP, Abbott:2019:PhRvX, EventHorizonTelescopeCollaboration:2019:ApJL, Abbott:2020:arXiv}.
+However, there is a deficiency of observational evidence for black holes in the intermediate-mass range $10^{2} - 10^{6}\ \msun$.
+The discovery of an intermediate-mass black hole population will bridge this observational gap, probe intermediate-mass formation environments (e.g.
+accretion disks of active galactic nuclei~\cite{Tagawa:2021:ApJ, Li:2021:arXiv, Samsing:2020:arXiv, Tagawa:2020:ApJ, Ishibashi:2020:A&A, Grobner:2020:A&A, Yang:2019:PhRvL, McKernan:2019:ApJL, Yang:2019:ApJ, McKernan:2018:ApJ, Bellovary:2016:ApJL, McKernan:2014:MNRAS, McKernan:2012:MNRAS}, the centers of dense stellar clusters~\cite{Banerjee:2021:MNRASa, Zevin:2021:ApJ,Mapelli:2021:arXiv,Weatherford:2021:ApJL, Bouffanais:2021:arXiv, Ballone:2021:MNRAS, Kumamoto:2021:arXiv, Banerjee:2021:MNRASb, Martinez:2020:ApJ, Romero-Shaw:2020:ApJL, Anagnostou:2020:PASA}, Population-III stars~\cite{Toubiana:2021:PhRvL, Farrell:2021:MNRAS, Safarzadeh:2020:ApJL, Liu:2020:MNRAS, Inayoshi:2017:MNRAS}), and illuminate our understanding of supermassive black hole formation~\cite{Askar:2021:MNRAS, ArcaSedda:2019:arXiv, Amaro-Seoane:2007:CQGra, Gurkan:2006:ApJL}.
+A variety of techniques have been employed to search for $10^{4} - 10^{6}\ \msun$ intermediate mass candidates (reverberation mapping~\cite{Peterson:2014:SSRv}, direct kinematic measurements~\cite{Schodel:2002:Natur, Kiziltan:2017:Natur}, applying macroscopic galaxy to black hole mass scaling relations (M$_{BH}$-$\sigma$ and M$_{BH}$-L relations)~\cite{Graham:2013:ApJ, Wevers:2017:MNRAS}, studying  X-ray luminosity and spectra~\cite{Greene:2004:ApJ, Lin:2020:ApJL}, gravitational lensing of light curves~\cite{paynter_evidence_2021}, and others~\cite{Greene:2020:ARA&A, Koliopanos:2017:mbhe, Mezcua:2017:IJMPD})).
+However, these observational techniques are challenging to use for intermediate mass black holes, due to their small sphere of influence.
+Additionally, some candidates discovered with these techniques can be attributed to sources without intermediate-mass black holes (e.g.
+clusters of stellar-mass black holes~\cite{Ridolfi:2016:MNRAS, Freire:2017:MNRAS}, anisotropic emission from neutron stars~\cite{Israel:2017:MNRAS, RodriguezCastillo:2020:ApJ}), while others have high uncertainties due to the observational techniques utilized~\cite{Greene:2020:ARA&A}.
+Compact binaries coalesces (CBCs) can provide unambiguous gravitational wave signals for intermediate-mass candidates (e.g.
+the $142^{+28}_{-16}\ \msun$ remnant observed from the gravitational wave event GW190521~\cite{Abbott:2020:PhRvL}), and ground-based detectors can probe the lower-end $10^{2} - 10^{3}\ \msun$ of the intermediate mass range.
+Mergers involving either a binary system with at least one intermediate-mass component, or a system whose merger results in an intermediate-mass remnant will have large total masses $\text{M}_{T}$.
+As a binary's $\text{M}_{T}$ is associated with its gravitational-wave merger frequency, $f\sim \text{M}_{T}^{-1}$, systems with large $\text{M}_{T}$ have very low merger frequencies $f < 100\ \text{Hz}$.
+Hence, ground based gravitational wave detectors ($\sim 10^1 - 10^3\ \text{Hz}$) are sensitive to the last milliseconds of merging systems with $100 \msun < \text{M}_{T} < 400 \msun$~\cite{LIGOScientificCollaboration:2015:CQGra, Martynov:2016:PhRvD, Moore_2014}, while space-based detectors ($\sim 10^{-2} - 10^1\ \text{Hz}$) can study the full signals of merging systems with $10^4 \msun < \text{M}_{T} < 10^7 \msun$~\cite{ Moore_2014, Lu:2019:PhRvD}.
 
-% Given the existence of supermassive black holes detected in the early universe, it is likely for intermediate-mass black holes to have also existed~\cite{Banados:2018:Natur}.
+Because of high-total mass systems' short-durations in ground-based gravitational wave data steams, handling data quality is critical to their detection.
+The low-frequency ranges of ground-based observatories are plagued with incoherent non-stationary terrestrial artifacts, called \textit{glitches}~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
+Some glitches, similar to signals from high total mass mergers, last for a fraction of a second, making them difficult to distinguish from the signals.
+These glitches that mimic astrophysical signals can severely decrease the confidence in detection of true gravitational-waves from high total mass mergers.
+
+Although a significant fraction of the glitches can be removed by testing them for coherence amongst various ground based detectors and performing matched-filtering, these methods are insufficient to remove all the glitches~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
+One method to account for more glitches while searching for high total mass CBC gravitational-waves is by utilizing a Bayesian odds~\cite{bci, kanner2016leveraging, BCR1, BCR2, bcr_gw151216, bayesian_odds}.
+In this paper, we utilize a Bayesian method, called the Bayesian Coherence Odds-Ratio \bcr~\cite{BCR1}, to rank the candidate gravitational-wave signals from high-mass compact binary coalescences (systems with total masses in the range of $55-500\ \msun$) in the detector data recorded during O2.
+The \bcr used in this study is a bootstrap-Bayesian odds computed using Bayesian evidences that describe the explicit probability of data under the hypothesis that the data contains coherent signals vs incoherent glitches, and empirically calculated prior-odds that describe how likely each hypotheses is.
+The high-mass candidate \bcr values are then used to calculate the probability that the candidate is of astrophysical origins, \pastrobcr.
+Finally, if the candidate has a \pastro reported by the the LIGO-Virgo-KAGRA (LVK) collaboration in \GWTC~\cite{GWTC1}, the \pycbc-team~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6, pycbc_single_det, pycbc_ogc_2}, by the Institute of Advanced study's team (IAS)~\cite{IAS0, IAS1, IAS2}, or by \citet{bayesian_odds}, we compare their \pastro with the \pastrobcr.
+
+We find that (a) high-mass events reported in the \GWTC, including GW170729 (the heaviest event in \GWTC) are very statistically significant $\pastrobcr>0.9$; (b) three out of the eight \IAS events and candidates have $\pastrobcr>0.5$, corroborating \IAS's detection claims for those events (GW170304, GW170727, GW170817A), and that (c) our ranking statistic does not identify any new intermediate-mass black holes, but does identify an unreported marginal stellar-mass binary black hole candidate, 170222 with $\pastrobcr\sim0.5$.
+
+The remainder of this paper is structured as follows.
+We outline our methods, including details of our ranking statistic and the retrieval of our candidate in Section~\ref{sec:method}.
+We present details on the implementation of our analysis in Section~\ref{sec:Analysis}.
+Finally, we present our results in Section~\ref{sec:Results}, and discuss these results in the context of the significance of gravitational-wave candidates in Section~\ref{sec:Conclusion}.
+
+\section{Method\label{sec:method}}
+
+The standard framework to identify CBC gravitational-wave signals hidden in data is by quantifying the significance of candidates with null-hypothesis significance testing~\cite{GWTC1, GWTC2}.
+In this framework, the candidates' ranking statistic is compared against a background distribution in a frequentist approach.
+The independent matched-filter searches, e.g.
+\pycbc~\cite{pycbc_og4} and \gstlal~\cite{sachdev2019gstlal}, and the coherent burst search \cwb~\cite{cwb} used by LVK to search for signals in gravitational-wave data all use ranking statistics in such a manner~\cite{GWTC1}.
+Both \pycbc and \gstlal's ranking statistic incorporate information of the relative likelihood that the data contains a coherent-signal versus just noise, while \cwb's ranking statistic uses the information of coherent energy present in the network of detectors~\cite{GWTC1}.
+
+In a similar vein, this work utilizes Bayesian inference to calculate the Bayesian Coherence Odds-Ratio~\cite{BCR1}, \bcr, of high-mass candidates in LIGO's second observing run.
+We use the \bcr not as an odds-ratio but instead as a ranking statistic.
+
+\subsection{The Bayesian Coherence Odds-Ratio}
+
+Bayes theorem states that the posterior probability distribution $p(\parameters|d,\mathcal{H})$ for data $d$ and a vector of parameters \parameters that describe a model which quantifies a hypothesis $\mathcal{H}$, is given by
+\begin{equation}
+p(\parameters|d,\mathcal{H}) = \frac{\mathcal{L}(d|\parameters, \mathcal{H}) \ \pi(\parameters | \mathcal{H})}{\mathcal{Z}(d|\mathcal{H})}\ , 
+\end{equation}
+where $\mathcal{L}(d|\parameters, \mathcal{H})$ is the likelihood of the data given the parameters \parameters and the hypothesis, $\pi(\parameters | \mathcal{H})$ is the prior probability of the parameters, and finally,
+\begin{equation}
+    \mathcal{Z}(d|\mathcal{H}) = \int\limits_{\parameters} \ \mathcal{L}(d|\parameters,\mathcal{H}) \ \pi(\parameters | \mathcal{H}) \ d\parameters
+\end{equation} is the likelihood after marginalizing over the parameters \parameters.
+To compare two hypotheses $\mathcal{H}_A$ and $\mathcal{H}_B$ with the Bayes theorem one can calculate an odds-ratio
+\begin{equation}
+    \mathcal{O}^A_B = \frac{\mathcal{Z}^A\ \pi(\parameters | \mathcal{H_A})}{\mathcal{Z}^B\ \pi(\parameters | \mathcal{H_B})}\ ,
+\end{equation}
+where $\{\mathcal{Z}^A, \mathcal{Z}^B\}$ are shorthand for the evidences $\{\mathcal{Z}(d|\mathcal{H}_A), \mathcal{Z}(d|\mathcal{H}_B)\}$ and $\{\pi(\parameters | \mathcal{H_A}), \pi(\parameters | \mathcal{H_B})\}$ are the prior-odds for each hypotheses.
+The odds-ratio can tell us which of the two hypotheses is more likely.
+For example, if $\mathcal{O}^A_B >> 1$, then this odds ratio indicates that the $\mathcal{H}_A$ describes the data much better than $\mathcal{H}_B$.
+
+The \bcr is a Bayesian odds-ratio like the above, of a coherent signal hypotheses $\mathcal{H}_S$ and an incoherent instrumental feature hypothesis $\mathcal{H}_I$ (the null-hypotheses) for a network of $D$ detectors.
+$\mathcal{H_I}$ states that each detector $i$ has either pure stationary Gaussian noise $\mathcal{H}_N$ or Gaussian noise and an incoherent noise transient (glitch) $\mathcal{H}_G$.
+Taking $Z^S$, $Z^G_i$ and $Z^N_i$ as the Bayesian evidences (defined in Appendix~\ref{sec:bayesianEvidEval}) for $\mathcal{H}_S$, $\mathcal{H}_N$, and $\mathcal{H}_G$, the \bcr is given by
+\begin{equation}
+\label{eq:bcr}
+\bcr = \frac{P^S Z^S}{\prod\limits^D_{i=1} \ [P^G Z^G_i + (1-P^G)Z^N_i]}\ ,
+\end{equation}
+where $P^S$ and $P^G$ are the prior-odds of obtaining a signal or a glitch from a stretch of data. The prior-odds can be defined more explicitly as 
+\begin{itemize}
+    \item $P^S=P(\mathcal{H}_S)/P(\mathcal{H}_I)$, the prior-odds for obtaining a coherent signal versus an incoherent instrumental feature.
+    \item $P^G=P(\mathcal{H}_G| \mathcal{H}_I)$, the prior-odds for obtaining a glitch assuming there is an incoherent instrumental feature.
+\end{itemize}
+
+When $\mathcal{H}_S$ and $\mathcal{H}_I$ are precisely described and the correct prior-odds are known, the \bcr is a Bayesian odds-ratio.
+As an odds-ratio, the \bcr is the optimal discriminator between coherent signals and incoherent instrumental features.
+However, as the priors-odds are unknown, it is invalid to use the \bcr as an odds-ratio to make an informed decision about whether a candidate is from an astrophysical or terrestrial source.
+Instead of interpreting the \bcr as a Bayesian odds-ratio, it can be used as a ranking statistic.
+Using the \bcr as a ranking statistic we can obtain a frequentist significance of a candidate \bcr-value measured against a background \bcr distribution.
+
+When using the \bcr as a detection statistic, the physical interpretation of the prior-odds is lost.
+Hence, the prior-odds are empirically tuned to maximize the separation between the \bcr distribution of the background (expected to favor the $\mathcal{H}_I$ hypothesis) and the \bcr distribution of artificially manufactured simulated signals (expected to favor the $\mathcal{H}_S$ hypothesis).
+Increasing the separation between the two distributions can improve ability of the \bcr to discriminate candidate events as coherent signals or incoherent instrumental features.
+The tuning process is described in detail in Appendix~\ref{sec:tuning-prior-odds}.
+
+\subsection{Estimation of astrophysical signal probability}
+Candidate \bcr-values are either statistically insignificant compared to the background \bcr distribution, implying the candidate is more probable to be an incoherent instrumental feature (the $\mathcal{H}_I$ null-hypothesis), or statistically significant to the background distribution, indicating the possible presence of an astrophysical signal (the $\mathcal{H}_S$ hypothesis).
+A false alarm probability with trial factors, \fap, for the candidate \bcr-value can quantify the significance.
+The \fap is the probability that a candidate originating from a non-astrophysical source can be falsely identified as a signal.
+
+To calculate the \fap, each candidate \bcr is considered a single statistical trial that can occur at a fixed false alarm probability $f$, where $f$ is the probability of observing a background $\bcr'$ greater than or equal to the candidate \bcr,
+\begin{equation}
+    f = \frac{\text{Count of } \bcr' \leq \bcr}{\text{Count of } \bcr'} \ .
+\end{equation}
+The false alarm probability with trials \fap that the \bcr measurement occurs at least once for $N$ trials $(N > 0)$, where $N$ is the number of candidate triggers is
+\begin{equation}
+    \fap = 1 - (1-f)^N \ .
+\end{equation}
+
+Finally, the \fap can be used to construct a \pastro, the probability that a signal is of astrophysical origin~\cite{pastro_1,pastro_2,pastro_3}
+\begin{equation}
+    \pastro = 1 -  \fap \ .
+\end{equation}
+
+\avi{
+Talk about the differences in pastro calculation ~\cite{Farr:2015:PhRvD, Gaebel:2019:MNRAS,Galaudage:2020:PhRvD}
+}
+
+\greg{This needs more explanation and discussion.
+I know that in the Gaebel paper~\cite{Gaebel:2019:MNRAS}, they make the connection (they don't in FGMC~\cite{Farr:2015:PhRvD}).
+But, effectively the FAP is the p-value, the probability that the event arose from the background noise alone.
+Taking 1-FAP as identifying a real signal can be hugely problematic (Wikipedia has its own page on it \url{https://en.wikipedia.org/wiki/Misuse_of_p-values}).
+In this case, it is a reasonable thing to do, because you are saying "anything which rings up our detection statistic is astrophysical by virtue that it is coherent".
+But, that needs to be spelled out.
+Also, it may be useful to say that the p-astro calculated from, say, PyCBC/GSTLAL are not 1-FAP, but instead apply the FGMC population approach.}
+
+\subsection{Data for Analysis}
+The LIGO Scientific collaboration operates several search pipelines that scan for gravitational-waves from compact binary mergers such as \gstlal~\cite{sachdev2019gstlal}, \texttt{MBTAOnline}~\cite{MBTA}, \texttt{SPIIR}~\cite{spiir} and \pycbc~\cite{pycbc_og4}.
+The output of \pycbc's search is a list of times and their corresponding \pycbc ranking statistic \pycbcstat values.
+The \pycbcstat ranking-statistic is akin to the matched-filter signal-to-noise ratio \snr.
+However, unlike \snr, \pycbcstat includes candidate signal's intrinsic and extrinsic properties and other information that feeds into determining if the signal can have astrophysical origins~\cite{pycbc_og6}.
+Whenever a local maximum of $\pycbcstat > \snr_\text{T}$, where $\snr_\text{T}$ is some predetermined threshold value, the \pycbc search pipeline produces a single-detector \textit{trigger} associated with the detector and time $t_c$ where the apparent signal in the data has its merger~\cite{pycbc_og6}.
+
+When \pycbc observes a trigger between detectors with coincident parameters and a time of arrival difference less than the gravitational-wave travel time between detectors, the trigger is labeled a \textit{candidate event trigger}, a trigger that may be from astrophysical origins~\cite{pycbc_og1}.
+To test the pipeline's sensitivity \pycbc also conducts searches for \textit{simulated triggers}, artificial triggers manufactured by injecting signals into the detector data.
+Finally, to quantify the statistical significance of candidate triggers, \pycbc artificially constructs \textit{background triggers} to compare against the candidate events.
+These background triggers are coherent signal-free events, constructed by applying relative offsets, or time-slides, between the data of different detectors~\cite{pycbc_og6}.
+The background trigger's \pycbcstat distribution is used to calculate the candidate trigger's significance,  using null-hypothesis significance testing, under the assumption that all candidate event triggers are due to noise.
+
+Our work demonstrates that the \bcr can be used in the same way as \pycbcstat to measure candidate triggers' statistical significance.
+The \bcr can be a powerful ranking statistic as it incorporates information of not only all possible binary black hole systems that might have merged to produce the trigger but also the various incoherent glitches that might cause a false-detection.
+
+\section{Analysis}\label{sec:Analysis}
+
+\subsection{Acquisition of triggers}
+Advanced LIGO's second observing run O2 lasted $38$ weeks~\cite{GWOSC}.
+The software package, \pycbc~\cite{pycbc_code}, was used by LVK to process the O2 data in 22 time-frames (approximately 2 weeks per frame) and found several gravitational-wave events and numerous gravitational-wave candidates~\cite{pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6}.
+Some candidate events were vetoed to be glitches, while others were rejected due to their low significance.
+The data are divided into these time-frames because the detector's sensitivity does not stay constant throughout the eight-month-long observing period.
+
+In addition to finding candidate events, \pycbc also identified several million background triggers for each time-frame, by searching background data manufactured by time-sliding data within that time-frame.
+The background triggers help quantify the candidate events' significance for the respective time-frames.
+Finally, to test the search's sensitivity, \pycbc produced and searched for thousands of simulated signals.
+
+For our study, we filter the \pycbc background, simulated and candidate triggers to include only high-mass triggers with masses in the ranges of the parameters presented in Table~\ref{tab:parameters}.
+A plot of the \pycbc triggers from one time-frame, during April 23 - May 8, 2017, is presented in Fig.~\ref{fig:templateBank}.
+This figure also depicts the gravitational-wave templates used during the search through this time-frame of data.
+
+\begin{table}[t]
+
+\caption[BBH parameters correspond to duration $<454\ \text{ms}$]{\label{tab:parameters}High-mass parameter space (parameters correspond to signals with durations $<454 \ \text{ms}$). }
+\centering
+\begin{tabular}{lrr}
+\toprule
+  & Minimum & Maximum\\
+\midrule
+Component Mass 1 [\msun] & 31.54 & 491.68\\
+Component Mass 2 [\msun] & 1.32 & 121.01\\
+Total Mass [\msun] & 56.93 & 496.72\\
+Chirp Mass [\msun] & 8.00 & 174.56\\
+Mass Ratio & 0.01 & 0.98\\
+\end{tabular}
+\end{table}
+
+\begin{figure*}[!ht]
+
+{\centering \includegraphics[width=0.75\linewidth]{images/template_bank.png}
+
+}
+% time for chunk 14
+% 1176955218, Apr 23, 2017, 4:00 UTC
+% 1178294418, May 08, 2017, 16:00 UTC
+\caption[High-mass BCR search space.]{The template bank (pink) used by \pycbc to search a section of O2 data from $\text{April 23 - May 8, 2017}$.
+Our search is constrained to the high-mass parameter space enclosed by the dashed line.
+The candidate, background and simulated triggers detected in this region of the parameter space during this period are plotted in orange, gray and blue respectively.}\label{fig:templateBank}
+\end{figure*}
+
+\subsection{Calculating the BCR for triggers}
+To evaluate $Z^S$, $Z^G_i$ and $Z^N_i$ and calculate the \bcr Eq.~\ref{eq:bcr} for triggers, we carry out Bayesian inference with \bilby~\cite{bilby, bilby_pipe}, employing \dynesty~\cite{dynesty} as our nested sampler.
+Nested sampling, an algorithm introduced by~\citet{skilling2004, skilling2006}, provides an estimate of the true Bayesian evidence and is often utilized for parameter estimation within the LIGO collaboration~\cite{bilby, bilby_paper, pbilby_paper}.
+
+The most computationally intensive step during Bayesian inference is evaluating the likelihood $\mathcal{L}(d_i|\template)$.
+To accelerate our analysis, we use a likelihood that explicitly marginalizes over coalescence time, phase at coalescence, and luminosity distance (Eq.~80 from~\citet{intro_to_gw_bayes}).
+While this marginalized likelihood reduces the run time without introducing errors to our evidence evaluation, it does not generates samples for the marginalized parameters.
+However, these parameter samples can be calculated as a post-processing step~\cite{intro_to_gw_bayes}.
+
+We set the priors $\pi(\parameters|\mathcal{H}_S)$ and $\pi(\parameters|\mathcal{H}_G)$ to be identical.
+These priors restrict signals with mass parameters in the ranges presented in Table~\ref{tab:parameters}.
+The spins are aligned over a uniform range for the dimensionless spin magnitude from $\left[0,1\right]$.
+The luminosity distance prior assigns probability uniformly in comoving volume, with an upper cutoff of $5\ \text{Gpc}$.
+The full list of the priors, along with their shapes, limits and boundary conditions are documented in Table~\ref{tab:priors}.
+
+\begin{table}
+    \centering
+    \caption{
+    Prior settings for the parameters used during our parameter estimation.
+The definitions of the parameters are documented in \citet{bilby_gwtc}~Table~E1.\label{tab:priors}}.
+The trigger time $t_c$ is obtained from the data products of \pycbc's O2 search.
+    \begin{tabular}{c c c c}
+    \hline
+    Parameter & Shape & Limits \\
+    \hline
+          $\mathcal{M}/\msun$           & Uniform & 7--180  \\
+          $q$                           & Uniform & 0.1--1  \\
+          $M/\msun$                     & Constraint & 50--500  \\
+          $d_\mathrm{L}/\mathrm{Mpc}$   & Comoving & 100--5000  \\
+          $a_1$, $a_2$                  & Uniform & 0--1  \\
+          $\theta_{JN}$                 & Sinusoidal & 0--$\pi$  \\
+          $\psi$                        & Uniform & 0--$\pi$  \\
+          $\phi$                        & Uniform & 0--$2\pi$  \\
+          ra                            & Uniform & 0--$2\pi$  \\
+          dec                           & Cosine & 0--$2\pi$  \\
+          $t_c/\mathrm{s}$              & Uniform & $t_c\pm0.1$  \\
+    \hline
+    \end{tabular}
+\end{table}
+
+The waveform template we utilize is \imrphenomp, a phenomenological waveform template constructed in the frequency domain that models the in-spiral, merger, and ring-down (IMR) of a compact binary coalescence~\citep{khan2016frequency}.
+Although there exist gravitational-wave templates such as \seob~\cite{seobnrv4phm} which incorporate more physics, such as information on higher-order modes, we use \imrphenomp as it is computationally inexpensive compared to others.
+
+We take 31 neighboring, off-source, non-overlapping, 4-second segments of time-series data before the analysis data segment $d_i$ to generate the PSD.
+We use off-source to avoid the inclusion of a signal in the PSD calculation.
+A Tukey window with 0.2-second roll-offs is applied to each data segment to suppress spectral leakage after which the segments are fast-Fourier transformed and median-averaged to create a PSD~\cite{ligo_psd}.
+Like other PSD estimation methods, this method adds statistical uncertainties to the PSD~\cite{psd_student_t, chatziioannou2019noise}.
+To marginalize over the statistical uncertainty, we use the median-likelihood presented by~\citet{psd_student_t} as a post-processing step.
+
+We take 31 neighboring off-source non-overlapping  4-second  segments of time-series data before the analysis data segment $d_i$ to generate the PSD.
+A Tukey window with a 0.2-second roll-off is applied to each data segment to suppress spectral leakage.
+After this  the segments are fast-Fourier transformed and median-averaged to create a PSD~\cite{ligo_psd}.
+Like other PSD estimation methods, this method adds statistical uncertainties to the PSD~\cite{psd_student_t, chatziioannou2019noise, Biscoveanu:2020:PhRvD}.
+To marginalize over the statistical uncertainty, we use the median-likelihood presented by~\citet{psd_student_t} as a post-processing step.
+We find that this post-processing step improves the search efficiency by $49.26\%$ the details of this calculation are presented in the Appendix~\ref{sec:psd-marginalization}.
+
+Finally, we neglect detector calibration uncertainty and acquire data from from the gravitational-wave Open Science Center~\cite{GWOSC}.
+The data we use are the publicly accessible O2 strain data from the Hanford and Livingston detectors, recorded while the detectors are in ``Science Mode''.
+We obtain the data using \gwpy~\cite{gwpy}.
+
+\subsection{Assigning \pastro to candidate events}
+After the calculating the \bcr for the entire set of high-mass background and simulated triggers, we calculate probability distributions $p_b(\bcr)$ and $p_s(\bcr)$ for each 2-week time-frame of O2 data.
+These distributions are used to `tune' prior-odd $P^S$ and $P^G$ values.
+
+Using the tuned prior odds the \bcr for the candidate events can be calculated.
+Fig.~\ref{fig:bcrCdf} shows the \bcr distributions for the background triggers, simulated triggers and candidate events.
+The bulk of the background and simulated trigger distributions are separate but slightly overlap due to some of the simulated signal's being very faint.
+The separation suggests that the \bcr can successfully distinguish signals from noise or glitches.
+The vertical lines in Fig.~\ref{fig:bcrCdf} displays the \bcr for gravitational-wave candidate events.
+On comparing the candidate event \bcr values with the background distribution, we can estimate \pastro values for the candidate events.
+
+\begin{figure}[!ht]
+{\centering \includegraphics[width=0.85\linewidth]{images/reweighted_bcr_cdf_smaller_legend.png} }
+\caption[BCR distribution example]{Histograms represent the survival function (1-CDF) from our high-mass selection of background triggers (gray) and simulated signals (blue) triggers obtained from \pycbc's search of data from $\text{August 13 - 21, 2017}$.
+Vertical lines mark the $\text{ln}\ \bcr$ of \IAS's GW170817A and \GWTC's GW170814.}\label{fig:bcrCdf}
+\end{figure}
+
+\section{\label{sec:Results}Results}
+
+\input{Data/results_table}
+We analyze the $60,996$ background, $5,146$ simulated, and $25$ candidate triggers reported by \pycbc's search on the data from LIGO's second observing run, restricting our analysis to the triggers that fall within our mass-space as described in Section~\ref{sec:method}.We also analyze events and candidate events reported by \GWTC and the IAS group (note: some of these were identified as candidates by the \pycbc search).
+In Table~\ref{tab:results}, we summaries the \pastrobcr, along with the \pastro of other pipelines for comparison.
+Although the various pipeline \pastro are not mathematically equivalent, by comparing pipeline \pastro values for a given candidate, we can compare how significant each pipeline deems various candidates.
+The $P^S$ and $P^G$ values utilized for each time-frame are reported in Appendix~\ref{apdx:alphabeta}.
+
+\subsection{GWTC-1 Events}
+All the confirmed gravitational-wave events from binary black hole mergers reported in \GWTC and within our prior space, (specifically GW170104, GW170608, GW170729, GW170809 and GW170814), have $\pastrobcr>0.9$, indicating a high probability of the presence of an astrophysical signal.
+
+In addition to the above confirmed gravitational-wave events from \GWTC, we have also analyzed several candidate events from \GWTC, most of which have low \pastrobcr.
+For example, consider the candidate event 170412, assigned a $\pastro$ of $0.06$ by \gstlal and has a $\pastrobcr$ of $0.01$.
+This candidate was reported to be excess power caused due noise appearing non-stationary between 60-200 Hz~\cite{GWTC1}.
+This candidate acts as an example of how $\pastrobcr$ may be utilized to eliminate candidates originating from terrestrial noise sources.
+
+\subsection{IAS Events}
+Our analysis of the high-mass IAS events and candidates in O2 has resulted in three events with disfavored $\pastrobcr<0.5$ (GWC170402, GW170403, GW170425), and four events and one candidate with $\pastrobcr\geq0.5$ (GW170121, 170302, GW170304, GW170727, GW170817A).
+While GW170727 and GW170817A's \pastrobcr are similar to the \pastro reported from IAS (the differences between the \pastro from \bcr and IAS is $|\Delta \pastro|<0.1$), the remaining candidates have opposing \pastro values (with $|\Delta \pastro| > 0.15$).
+
+GWC170402, detected by \citet{IAS2}, is reported to originate from a binary with non-zero eccentricity~\cite{IAS2}.
+Hence, we might have received a low \pastrobcr due to our usage of \imrphenomp, a waveform that does not account for eccentricity.
+Additionally, the search conducted by \citet{IAS2} was a single-detector search.
+Our ranking statistic relies on the signal to appear coherent, even if just faintly coherent, amongst the various detectors to have a high \pastrobcr.
+The lack of coherence and the non-eccentric waveform may be the leading factors for a low \pastro.
+GW170403 and GW170425 which have $\pastrobcr<0.35$ also have low  \pastro reported by \citet{pycbc_ogc_2},  suggesting that these events may have been false alarms.
+
+From the candidates with $\pastrobcr>0.5$, GW170727 and 170302 are of particular interest, with \pastrobcr of $0.92$ and $0.63$.
+GW170727 was emitted from a black hole binary system with a source frame total mass $\approx 70\ \msun$.
+In addition to the high \pastrobcr reported by our study, \citet{IAS1} and \citet{pycbc_ogc_2} have also reported high \pastro values of 0.98 and 0.99, making it a viable gravitational-wave event candidate.
+Similarly, the sub-marginal-candidate 170302 reported by \cite{IAS1} with a \pastro of 0.45 appears to have a higher significance from our analysis, resulting in a \pastrobcr of $0.63$.
+
+\subsection{New Candidate Events}
+Although no clear detections are made with the \bcr, a marginal-candidate 170222 has been discovered with a $\pastrobcr\sim0.5$.
+This candidate has an SNR$\sim7.7$, low spin magnitudes and source-frame component masses of ${47.16}_{-5.77}^{+8.00}, {35.50}_{-6.35}^{+5.79}$, making it one of the heavier black-hole mergers from O2 and \GWTC.
+This candidate may be of interest as one component black hole may lie in the pair-instability mass gap ($55^{+10}_{-10}-148^{+13}_{-12}\msun$)~\cite{Woosley:2021:arXiv, Heger:2002:ApJ}.
+More details on the candidate are presented in Appendix~\ref{apdx:170222}.
+The remaining coherent trigger candidates all have $\pastrobcr\ll0.5$ making them unlikely to originate from astrophysical sources.
+
+\section{\label{sec:Conclusion}Conclusion}
+
+Until 2016, a majority of intermediate-mass black hole candidates were from electromagnetic observations.
+The dawn of gravitational waves astronomy has provided a new lens to identify and study these massive objects -- from the mergers of heavy black holes' gravitational wave emission.
+In the future, space-based gravitational wave detectors will uncover black holes in the upper end of the intermediate-mass range.
+In the present ground-based gravitational-wave observatories can probe the lower-end of the intermediate-mass range.
+However, many short-duration terrestrial artifacts that mimic intermediate-mass gravitational-wave signals plague ground-based detectors, making intermediate-mass detection challenging.
+
+In this paper, we demonstrate that the Bayesian Coherence Odds-Ratio \bcr~\cite{BCR1} can be used as a ranking statistic to provide a measure of significance for gravitational wave signals originating from CBCs with total masses between $55\msun$ and $400\msun$, a range that includes intermediate-mass black holes.
+To compute the \bcr for candidates, we utilize Bayesian inference to explicitly calculate the probability of data under various hypotheses (the hypotheses that the data contains a coherent signal, just noise, or an incoherent glitch).
+This Bayesian ranking method takes a step towards building a unified Bayesian framework that provides a search-pipeline agnostic measure of significance for candidates and estimates their parameters, utilizing the same level of physical information incorporated during detected parameter estimation studies.
+
+In our study, we analyze high-mass candidates detected by \pycbc, the high-mass binary black hole events in O2 reported in \GWTC~\cite{GWTC1} and by the \IAS-team~\cite{IAS1, IAS2}.
+Using \pastrobcr, we find that the high-mass \GWTC events have high probabilities of originating from an astrophysical source.
+We also find that some of the \GWTC marginal triggers that have corroborated terrestrial sources (for example, candidate 170412) have low \pastrobcr, indicating this method's ability to discriminate between terrestrial artifacts and astrophysical signals.
+Our analysis on the high-mass \IAS events demonstrates that GW17072 is likely to originate from an astrophysical source, while GW17040 is not.
+Finally, we do not identify any new gravitational-wave events, but we find a new marginal binary-black hole merger candidate, 170222.
+
+Although our analysis targets high-mass triggers, this method can be extended to include the entire range of LIGO-detectable gravitational-wave sources.
+Additionally, to further improve the method's infrastructure, we can use more robust gravitational-wave templates (such as templates that incorporate higher-order modes and orbital precession) and sophisticated glitch models.
+Future analysis can also incorporate data from all available detectors in a network to increase the sensitivity of \pastrobcr.
+
+\greg{If the search is better at identifying high-mass black holes and has not found any..
+doesn't this mean we can better constraint their population properties?
+Do we know how much (if at all) this method outperforms current searches?
+This question may be stretching the scope of the paper, but I wondered if you had some thoughts.}
+
+\avi{
+\begin{itemize}
+    \item Unlike for stellar-mass BBH, there are still alot of uncertainties for IMBH formation scenarios. Hence, upper limits would be challenging to calculate
+    \item We would require to do more robust simulation studies to see what would fall in/outside our detection threshold, to put constraints on population properties and study the search's sensitivity
+\end{itemize}
+}
+
+%%%%%%---SECTIONS-END---%%%%%%%%%%%%
+
+%%%%%%---ACKNOWLEDGMENTS---%%%%%%%%%%%%
+\begin{acknowledgments}
+
+The author gratefully thank the \pycbc team for providing the gravitational-wave foreground, background and simulated triggers from \pycbc's search of O2's data.
+We also warmly thank Ian Harry and Thomas Dent for answering questions about the \pycbc search's data products.
+\avi{double check with Stuart what CIT's energy source is}
+
+We thank Stuart Anderson for assistance with accommodating this analysis which was performed on the California Institute of Technology computing cluster.
+All analyses (inclusive of test and failed analyses) performed for this study used $~1.3\mathrm{M}$ core-hours, amounting to a carbon footprint of $~167\ \mathrm{t}$ of CO$^2$ (using the US average electricity source emissions of $0.429\ \text{kg/kWh}$~\cite{greenhouse} and $0.3\ \text{kWh}$ for each CPU).
+
+This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open Science Center (https://www.gw-openscience.org), a service of LIGO Laboratory, the LIGO Scientific Collaboration and the Virgo Collaboration.
+LIGO is funded by the U.S.
+National Science Foundation.
+Virgo is funded by the French Centre National de Recherche Scientifique (CNRS), the Italian Istituto Nazionale della Fisica Nucleare (INFN) and the Dutch Nikhef, with contributions by Polish and Hungarian institutes.
+
+\end{acknowledgments}
+%%%%%%%%%%%%%%%%%%%%%%%%
+
+\appendix
+
+\section{Bayesian Evidence Evaluation}\label{sec:bayesianEvidEval}
+\subsection{Noise Model}
+We assume that each detector's noise is Gaussian and stationary over the period being analyzed~\cite{ligo_psd}.
+In practice, we assume that the noise has a mean of zero that the noise variance $\sigma^2$ is proportional to the noise power spectral density (PSD) \psd of the data.
+Using the \psd, for each frequency-domain data segment $d_i$ in each of the $i$ detectors in a network of $D$ detectors, we can write
+\begin{equation}
+\label{eq:zn}
+Z^N_i = \mathcal{N}(d_i|\mu=0,\sigma^2=\psd),
+\end{equation}
+where $\mathcal{N}$ is a normal distribution.
+
+\subsection{Coherent Signal Model}
+We model coherent signals using a binary black hole waveform template \template, where the vector \parameters contains a point in the 12 dimensional space describing aligned-spin binary-black hole mergers.
+For the signal to be coherent, \parameters must be consistent in each 4-second data segment $d_i$ for a network of $D$ detectors.
+Hence, the coherent signal evidence is calculated as
+\begin{equation}
+\label{eq:zs}
+Z^S = \int\limits_{\parameters} \prod\limits^{D}_{i=1} \left[ \mathcal{L}(d_i|\template)\right] \pi(\parameters | \mathcal{H}_S)\  \text{d}\parameters \ ,
+\end{equation}
+where $\pi(\parameters| \mathcal{H}_S)$ is the prior for the parameters in the coherent signal hypothesis, and $\mathcal{L}(d_i|\template)$ is the likelihood for the coherent signal hypothesis that depends on the gravitational-wave template \template and its parameters \parameters.
+
+\subsection{Incoherent Glitch Model}
+Finally, as glitches are challenging to model and poorly understood, we follow \citet{bci} and utilise a surrogate model for glitches: the glitches are modeled using gravitational-wave templates  \template with uncorrelated  parameters amongst the different detectors such that  $\parameters_i \neq \parameters_j$ for two detectors $i$ and $j$~\cite{bci}.
+Modelling glitches with \template captures the worst case scenario: when glitches are identical to gravitational-wave signals (excluding coherent signals).
+Thus, we can write $Z^G_i$ as
+\begin{equation}
+\label{eq:zg}
+Z^G_i = \int\limits_{\parameters} \mathcal{L}(d_i|\template)\ \pi(\parameters| \mathcal{H}_G)\  \text{d}\parameters  \ ,
+\end{equation}
+where $\pi(\theta| \mathcal{H}_G)$ is the prior for the parameters in the incoherent glitch hypothesis.
+
+\section{Tuning the prior-odds}\label{sec:tuning-prior-odds}
+
+After calculating the \bcr for a set of background triggers and simulated triggers from as stretch of detector-data (a data chunk), we can compute probability distributions for the background and simulated triggers, $p_b(\bcr)$ and $p_s(\bcr)$.
+We expect the background trigger and simulated signal \bcr values to favor the incoherent glitch and the coherent signal hypothesis, respectively.
+Ideally, these distributions representing two unique populations should be distinctly separate and have no overlap in their \bcr values.
+The prior odds parameters $P^S$ and $P^G$ from Eq.~\ref{eq:bcr} help separate the two distributions.
+Altering $P^S$ translates the \bcr probability distributions while adjusting $P^G$ spreads the distributions.
+Although Bayesian hyper-parameter estimation can determine the optimal values for $P^S$ and $P^G$, an easier approach is to adjust the parameters for each data chunk's \bcr distribution.
+In this study, we tune $P^S$ and $P^G$ to maximally separate the \bcr distributions for the background and simulated triggers.
+
+To calculate the separation between $p_b(\bcr)$ and $p_s(\bcr)$, we use the Kullback--Leibler divergence (KL divergence) $D_{KL}$, given by
+\begin{equation}
+    D_{KL}(p_b | p_s) = \sum\limits_{x\in \bcr} p_b(x) \log \left( \frac{p_b(x)}{p_a(x)} \right)  \ .
+\end{equation}
+The $D_{KL}=0$ when the distributions are identical and increases as the asymmetry between the distributions increases.
+
+We limit our search for the maximum KL-divergence in the $P^S$ and $P^G$ ranges of $[10^{-10}, 10^0]$.
+We set our values for $P^S$ and $P^G$ to those which provide the highest KL-divergence and calculate the \bcr for candidate events present in this data chunk.
+Note that we conduct the analysis in data chunks of a few days rather than an entire data set of a few months as the background may be different at different points of the entire data set.
+
+\section{Marginalizing over PSD statistical uncertainties}\label{sec:psd-marginalization}
+To generate the results in Fig.~\ref{fig:bcrCdf}, we applied a post-processing step to marginalize the uncertainty in the PSD.
+In Fig.~\ref{fig:bcrCdfUnmarginalized}, we show the results if this post-processing step is not applied.
+Clearly, marginalizing over uncertainty in the PSD yields an improvement in the separation of the noise and signal distributions.
+Quantitatively, at a threshold $\bcr^T=0$ the post-processing step results in a reduction in the number of background $\bcr > \bcr^T$ from $60.7\%$ to $25.28\%$ in the August 13 - 21, 2017 time-frame of data.
+For the entirety of O2 PSD marginalization resulted in a $49.26\%$ improvement in search efficiency.
+
+\begin{figure}[!ht]
+{\centering \includegraphics[width=0.85\linewidth]{images/orig_bcr_cdf_smaller_legend.png} }
+\caption[BCR distribution example]{This plot is analogous to Fig.~\ref{fig:bcrCdf}, but without using the post-processing step to marginalize over PSD statistical uncertainties.
+Without the post-processing step, there is a greater overlap between the background (gray) and foreground (blue) survival functions.
+For more details about this plot, refer to the caption of Fig.~\ref{fig:bcrCdf}.}\label{fig:bcrCdfUnmarginalized}
+\end{figure}
+
+\section{Tuned prior odds}\label{apdx:alphabeta}
+
+O2 lasted several months over which the detector's sensitivity varied.
+Hence, a part of our analysis entailed tuning the prior odds for obtaining a signal and a glitch, $P^S$ and $P^G$, as described in Section~\ref{sec:method}.
+Table~\ref{tab:priorodds} presents the signal and glitch prior odds utilized for each time-frame of O2 data.
+\input{Data/alpha_beta_table}
+
+Tuning the prior odds can dramatically affect the \pastrobcr.
+For example, consider Table~\ref{tab:tuningresults}, which reports tuned \pastrobcr and un-tuned \untunedpastrobcr (where $P^S=1$ and $P^G=1$) for various high-mass events and candidates.
+By tuning the prior odds, the \pastrobcr for some IAS events (for example, GW170403 and GW170817A) can change by more than 0.5, resulting in the promotion/demotion of a candidate's significance.
+
+\input{Data/tuning_results_table}
+
+\section{A closer look at 170222}\label{apdx:170222}
+PyCBC found in chunk7, with template, corresponds to parameters Xyz. Our parameters state that it is xyz.
+Put in corner, write notes from
+
+% \section{EXTRA INTRO MATERIAL}
+
+% Given the existence of supermassive black holes detected in the early universe, it is likely for intermediate-mass black holes to have also existed~\cite{Banados:2018:Natur, Askar et al  2020,}.
 However, we only have a handful of promising candidates~\cite{Greene:2004:ApJ, Graham:2013:ApJ, Mezcua:2017:IJMPD, Koliopanos:2017:mbhe, Lin:2020:ApJL, Greene:2020:ARA&A}, and two confirmed intermediate-mass black holes, (i) the $142^{+28}_{-16}\ \msun$ remnant observed from the gravitational wave event GW190521~\cite{Abbott:2020:PhRvL}, and the $5.5^{+1.7}_{-0.9}\times10^{4}\ \msun$ black hole identified from gravitational lensing in the light curve of GRB950830~\cite{paynter_evidence_2021}.
@@
 
-Gravitational waves from compact binaries coalesces (CBCs) are clean channels to measure BH masses.
-Mergers involving either a binary system with at least one intermediate-mass component, or a system whose merger results in an intermediate-mass remnant will have large initial total masses $\text{M}_{T}$.
-As a binary's $\text{M}_{T}$ is associated with its merger frequency, $f\sim \text{M}_{T}^{-1}$, systems with large $\text{M}_{T}$ have very low merger frequencies $f < 100\ \text{Hz}$.
-Hence, ground based gravitational wave detectors ($\sim 10 - 1000\ \text{Hz}$) are sensitive to the last milliseconds of merging systems with $100 \msun < \text{M}_{T} < 400 \msun$~\cite{}, while space-based detectors ($\sim 0.1 - 10\ \text{Hz}$) can study the full signals of merging systems with $10^4 \msun < \text{M}_{T} < 10^7 \msun$~\cite{}.
-
-Because of high-total mass systems' short-durations in ground-based gravitational wave data steams, handling data quality is critical to their detection.
-The low-frequency ranges of ground-based observatories are plagued with incoherent non-stationary terrestrial artefacts, called glitches~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
-Some glitches, similar to signals from high total mass mergers, last for a fraction of a second, making them difficult to distinguish from the signals.
-These glitches that mimic astrophysical signals can severely decrease the confidence in detection of true gravitational-waves from high total mass mergers.
-
-Although a significant fraction of the glitches can be removed by testing them for coherence amongst various ground based detectors and performing matched-filtering, these methods are insufficient to remove all the glitches.
-One method to account for more glitches while searching for high total mass CBC gravitational-waves is by utilizing the astrophysical Bayesian odds~\cite{bci, BCR1, BCR2, bcr_gw151216, bayesian_odds}.
-A true Bayesian odds, calculated without using bootstrap techniques, can provide more accurate estimate of significance that does note depend on the search pipeline~\cite{BCR2, bcr_gw151216,  bayesian_odds}.
-In this paper, we utilize a Bayesian method, called the Bayesian Coherence Ratio \bcr~\cite{BCR1}, to rank the candidate gravitational-wave signals from high-mass compact binary coalescences (systems with total masses in the range of $55-500\ \msun$) in the detector data recorded during O2.
-Although the \bcr, utilizing bootstrap techniques, does not provide the true Bayesian odds,  it utilizes Bayesian evidences which describe the explicit probability of data under the hypothesis that it contains coherent signals vs incoherent glitches.
-
-\avi{Need to discuss IAS, PyCBC etc here as well}
-
-We find that (a) high-mass events reported in the GWTC-1, including GW170729 (the least significant event in GWTC-1) have high significance; (b) high-mass events detected from the IAS group have differing levels of significance; \et{differing from what?
-edit this passage to state more clearly that we find statistical support for some of their candidates, but not for others} and that (c) our ranking statistic does not identify any intermediate-mass black holes, but does identify an unreported stellar-mass binary black hole candidate, 170222 \et{State statistical significance.}.
-
-The remainder of this paper is structured as follows.
-We outline our methods, including details of our ranking statistic and the retrieval of our candidate events in Section~\ref{sec:method}.
-We present details on the implementation of our analysis in Section~\ref{sec:Analysis}.
-Finally, we present our results in Section~\ref{sec:Results}, and discuss these results in the context of the significance of gravitational-wave candidates in Section~\ref{sec:Conclusion}.
-
-\section{Method\label{sec:method}}
-
-The standard framework to identify CBC gravitational-wave signals hidden in data is by quantifying the significance of candidates with null-hypothesis significance testing.
-In this framework, the candidates' ranking statistic is compared against a background distribution in a frequentist approach.
-\rs{add a sentence describing what the ranking stats are for the different pipelines (key words: matched filtering, SNR etc...) and add citations!} On the other hand, the standard framework for performing parameter estimation and model selection in gravitational-wave astronomy is Bayesian inference.
-This work utilizes Bayesian inference to calculate the Bayesian Coherence odds-ratio~\cite{BCR1}, \bcr, of high-mass candidates in LIGO's second observing run.
-We use the \bcr not as an odds-ratio but instead as a ranking statistic, a step toward building a unified Bayesian framework to search for candidates and estimate their parameters.
-
-\subsection{The Bayesian Coherence Ratio}
-
-Bayes theorem states that the posterior probability distribution $p(\parameters|d,\mathcal{H})$ for data $d$ and a vector of parameters \parameters that describe a model which quantifies a hypothesis $\mathcal{H}$, is given by
-\begin{equation}
-p(\parameters|d,\mathcal{H}) = \frac{\mathcal{L}(d|\parameters, \mathcal{H}) \ \pi(\parameters | \mathcal{H})}{\mathcal{Z}(d|\mathcal{H})}\ , 
-\end{equation}
-where $\mathcal{L}(d|\parameters, \mathcal{H})$ is the likelihood of the data given the parameters \parameters and the hypothesis, $\pi(\parameters | \mathcal{H})$ is the prior probability of the parameters, and finally,
-\begin{equation}
-    \mathcal{Z}(d|\mathcal{H}) = \int\limits_{\parameters} \ \mathcal{L}(d|\parameters,\mathcal{H}) \ \pi(\parameters | \mathcal{H}) \ d\parameters
-\end{equation} is the likelihood after marginalizing over the parameters \parameters.
-To compare two hypotheses $\mathcal{H}_A$ and $\mathcal{H}_B$ with the Bayes theorem one can calculate an odds-ratio
-\begin{equation}
-    \mathcal{O}^A_B = \frac{\mathcal{Z}^A\ \pi(\parameters^A)}{\mathcal{Z}^B\ \pi(\parameters^B)}\ ,
-\end{equation}
-where $\mathcal{Z}^A$ and $\mathcal{Z}^B$ are the shorthand for the evidences  $\mathcal{Z}(d|\mathcal{H}_A)$ and $\mathcal{Z}(d|\mathcal{H}_B)$.
-The odds-ratio can tell us which of the two hypotheses is more likely.
-For example, if $\mathcal{O}^A_B >> 1$, then this odds ratio indicates that the $\mathcal{H}_A$ describes the data much better than $\mathcal{H}_B$.
-
-The \bcr is a Bayesian odds-ratio like the above, of a coherent signal hypotheses $\mathcal{H}_S$ and an incoherent instrumental feature hypothesis $\mathcal{H}_I$ (the null-hypotheses) for a network of $D$ detectors.
-$\mathcal{H_I}$ states that each detector $i$ has either pure stationary Gaussian noise $\mathcal{H}_N$ or Gaussian noise and an incoherent noise transient (glitch).
-Taking $Z^S$, $Z^G_i$ and $Z^N_i$ as the Bayesian evidences (marginalised likelihoods, definitions in Appendix~\ref{apdx} for $\mathcal{H}_S$, $\mathcal{H}_N$, and $\mathcal{H}_G$, the \bcr is given by
-\begin{equation}
-\label{eq:bcr}
-\bcr = \frac{\alpha Z^S}{\prod\limits^D_{i=1} \ [\beta Z^G_i + (1-\beta)Z^N_i]}\ ,
-\end{equation}
-where $\alpha$ and $\beta$ are the prior-odds of obtaining a signal or a glitch from a stretch of data. The prior-odds can be defined more explicitly as 
-\begin{itemize}
-    \item $\alpha=P(\mathcal{H}_S)/P(\mathcal{H}_I)$, the prior-odds for obtaining a coherent signal versus an incoherent instrumental feature.
-    \item $\beta=P(\mathcal{H}_G| \mathcal{H}_I)$, the prior-odds for obtaining a glitch assuming there is an incoherent instrumental feature.
-\end{itemize}
-
-When $\mathcal{H}_S$ and $\mathcal{H}_I$ are precisely described and the correct prior-odds are known, the \bcr is a Bayesian odds-ratio.
-As an odds-ratio, the \bcr is the optimal discriminator between coherent signals and incoherent instrumental features.
-However, as the priors-odds are unknown, it is invalid to use the \bcr as an odds-ratio to make an informed decision about whether a candidate is from an astrophysical or terrestrial source.
-Instead of interpreting the \bcr as a Bayesian odds-ratio, it can be used as a ranking statistic.
-Using the \bcr as a ranking statistic we can obtain a frequentist significance of a candidate \bcr-value measured against a background \bcr distribution.
-
-When using the \bcr as a detection statistic, the physical interpretation of the prior-odds is lost.
-Hence, the prior-odds are empirically tuned to maximise the separation between the \bcr distribution of the background (expected to favour the $\mathcal{H}_I$ hypothesis) and the \bcr distribution of artificially manufactured simulated signals (expected to favour the $\mathcal{H}_S$ hypothesis).
-Increasing the separation between the two distributions can improve ability of the \bcr to discriminate candidate events as coherent signals or incoherent instrumental features.
-The tuning process is described in detail in Appendix~\ref{sec:tuning-prior-odds}.
-
-\subsection{Calculating the Significance of Candidates}
-Candidate \bcr-values are either statistically insignificant compared to the background \bcr distribution, implying the candidate is more probable to be an incoherent instrumental feature (the $\mathcal{H}_I$ null-hypothesis), or statistically significant to the background distribution, indicating the possible presence of an astrophysical signal (the $\mathcal{H}_S$ hypothesis).
-A false alarm probability with trial factors, \fap, for the candidate \bcr-value can quantify the significance.
-The \fap is the probability that a candidate originating from a non-astrophysical source can be is falsely identified as a signal.
-
-To calculate the \fap, each candidate \bcr is considered a single statistical trail that can occur at a fixed false alarm probability $f$, where $f$ is the probability of observing a background $\bcr'$ greater than or equal to the candidate \bcr,
-\begin{equation}
-    f = \frac{\text{Count of } \bcr' \leq \bcr}{\text{Count of } \bcr'} \ .
-\end{equation}
-The false alarm probability with trails \fap that the \bcr measurement occurs at least once for $N$ trials $(N > 0)$, where $N$ is the number of candidate triggers is
-\begin{equation}
-    \fap = 1 - (1-f)^N \ .
-\end{equation}
-
-Finally, the \fap can be used to construct a \pastro, the probability that a signal is of astrophysical origin~\cite{pastro_1,pastro_2,pastro_3}
-\begin{equation}
-    \pastro = 1 -  \fap \ .
-\end{equation}
-
-\subsection{Data for Analysis}
-\avi{Probably need a better section label...}
-The LIGO Scientific collaboration operates several search pipelines that scan for gravitational-waves from compact binary mergers such as \texttt{GstLAL}, \texttt{MBTA}, \texttt{SPIIR} and \pycbc~\cite{GWTC1}.
-The output of \pycbc's search is a list of times and their corresponding \pycbc ranking statistic \pycbcstat values.
-The \pycbcstat ranking-statistic is akin to the matched-filter signal-to-noise ratio \snr.
-However, unlike \snr, \pycbcstat includes candidate signal's intrinsic and extrinsic properties and other information that feeds into determining if the signal can have astrophysical origins~\cite{pycbc_og6}.
-Whenever a local maximum of $\pycbcstat > \snr_\text{T}$, where $\snr_\text{T}$ is some predetermined threshold value, the \pycbc search pipeline produces a single-detector \textit{trigger} associated with the detector and time where the apparent signal in the data has its merger~\cite{pycbc_og6}.
-
-When \pycbc observes a trigger between detectors with coincident parameters and a time of arrival difference less than the gravitational-wave travel time between detectors, the trigger is labelled a \textit{candidate event trigger}, a trigger that may be from astrophysical origins~\cite{pycbc_og1}.
-To test the pipeline's sensitivity \pycbc also conducts searches for \textit{simulated triggers}, artificial triggers manufactured by injecting signals into the detector data.
-Finally, to quantify the statistical significance of candidate triggers, \pycbc artificially constructs \textit{background triggers} to compare against the candidate events.
-These background triggers are coherent signal-free events, constructed by applying relative offsets, or time-slides, between the data of different detectors~\cite{pycbc_og6}.
-The background trigger's \pycbcstat distribution is used to calculate the candidate trigger's significance,  using null-hypothesis significance testing, under the assumption that all candidate event triggers are due to noise.
-
-Our work demonstrates that the \bcr can be used in the same way as \pycbcstat to measure candidate triggers' statistical significance.
-The \bcr can be a powerful ranking statistic as it incorporates information of not only all possible binary black hole systems that might have merged to produce the trigger but also the various incoherent glitches that might cause a false-detection.
-
-\section{Analysis}\label{sec:Analysis}
-
-\subsection{Acquisition of triggers}
-Advanced LIGO's second observing run O2 lasted $38$ weeks~\cite{GWOSC}.
-The software package, \pycbc~\cite{pycbc_code}, was used by LIGO to process the O2 data in 22 time-frames (approximately 2 weeks for one time-frame) and found several gravitational-wave events and numerous gravitational-wave candidates~\cite{pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6}.
-Some candidate events were vetoed to be glitches, while others were rejected due to their low significance.
-The data is divided into these time-frames because the detector's sensitivity does not stay constant throughout the eight-month-long observing period.
-
-In addition to finding candidate events, \pycbc also identified several million background triggers for each time-frame, by searching background data manufactured by time-sliding data within that time-frame.
-The background triggers help quantify the candidate events' significance for the respective time-frames.
-Finally, to test the search's sensitivity, \pycbc produced and searched for thousands of simulated signals.
-
-For our study, we filter the background, simulated and candidate events to include only high-mass events with masses in the ranges of the parameters presented in Table~\ref{tab:parameters}.
-A plot of the \pycbc triggers from one time-frame, during April 23 - May 8, 2017, is presented in Fig.~\ref{fig:templateBank}.
-This figure also depicts the gravitational-wave templates used during the search through this time-frame of data.
-
-\begin{table}[t]
-
-\caption[BBH parameters correspond to duration $<454\ \text{ms}$]{\label{tab:parameters}High-mass parameter space (parameters correspond to signals with durations $<454 \ \text{ms}$). }
-\centering
-\begin{tabular}{lrr}
-\toprule
-  & Minimum & Maximum\\
-\midrule
-Component Mass 1 [\msun] & 31.54 & 491.68\\
-Component Mass 2 [\msun] & 1.32 & 121.01\\
-Total Mass [\msun] & 56.93 & 496.72\\
-Chirp Mass [\msun] & 8.00 & 174.56\\
-Mass Ratio & 0.01 & 0.98\\
-\end{tabular}
-\end{table}
-
-\begin{figure*}[!ht]
-
-{\centering \includegraphics[width=0.75\linewidth]{images/template_bank.png}
-
-}
-% time for chunk 14
-% 1176955218, Apr 23, 2017, 4:00 UTC
-% 1178294418, May 08, 2017, 16:00 UTC
-\caption[High-mass BCR search space.]{The template bank (pink) used by \pycbc to search a section of O2 data from $\text{April 23 - May 8, 2017}$.
-Our search is constrained to the high-mass parameter space enclosed by the dashed line.
-The candidate, background and simulated triggers detected in this region of the parameter space during this period are plotted in orange, grey and blue respectively.
-\avi{Should I remove the `template bank' and only display the various triggers?}}\label{fig:templateBank}
-\end{figure*}
-
-\subsection{Calculating the BCR for triggers}
-\avi{Sat 13th: Just realised that some parts of this dont make sense without the material present in Apdx~\ref{sec:bayesianEvidEval}}...
-To evaluate $Z^S$, $Z^G_i$ and $Z^N_i$ and calculate the \bcr Eq.~\ref{eq:bcr} for triggers, we carry out Bayesian inference with \bilby~\cite{bilby, bilby_pipe}, employing \dynesty~\cite{dynesty} as our nested sampler.
-Nested sampling, an algorithm introduced by~\citet{skilling2004, skilling2006}, provides an estimate of the true Bayesian evidence and is often utilized for parameter estimation within the LIGO collaboration~\cite{bilby, bilby_paper, pbilby_paper}.
-
-The most computationally intensive step during Bayesian inference is evaluating the likelihood $\mathcal{L}(d_i|\template)$.
-To accelerate our analysis, we use a likelihood that explicitly marginalizes over coalescence time, phase at coalescence, and luminosity distance (Eq.~80 from~\citet{intro_to_gw_bayes}).
-While this marginalized likelihood reduces the run time without introducing errors to our evidence evaluation, it does not generates samples for the marginalized parameters.
-However, these parameter samples can be calculated as a post-processing step~\cite{intro_to_gw_bayes}.
-
-We set the priors $\pi(\parameters|\mathcal{H}_S)$ and $\pi(\parameters|\mathcal{H}_G)$ to be identical.
-These priors restrict signals with mass parameters in the ranges presented in Table~\ref{tab:parameters}.
-The spins are aligned over a uniform range for the dimensionless spin magnitude from $\left[0,1\right]$.
-The luminosity distance prior assigns probability uniformly in comoving volume, with an upper cutoff of $5\ \text{Gpc}$.
-The full list of the priors, along with their shapes, limits and boundary conditions are documented in Table~\ref{tab:priors}.
-
-\begin{table}
-    \centering
-    \caption{
-    Prior settings for the parameters used during our parameter estimation. The definitions of the parameters are documented in \citet{bilby_gwtc}~Table~E1.\label{tab:priors}}
-    \begin{tabular}{c c c c}
-    \hline
-    Parameter & Shape & Limits \\
-    \hline
-          $\mathcal{M}/\msun$           & Uniform & 7--180  \\
-          $q$                           & Uniform & 0.1--1  \\
-          $M/\msun$                     & Constraint & 50--500  \\
-          $d_\mathrm{L}/\mathrm{Mpc}$   & Comoving & 100--5000  \\
-          $a_1$, $a_2$                  & Uniform & 0--1  \\
-          $\theta_{JN}$                 & Sinusoidal & 0--$\pi$  \\
-          $\psi$                        & Uniform & 0--$\pi$  \\
-          $\phi$                        & Uniform & 0--$2\pi$  \\
-          ra                            & Uniform & 0--$2\pi$  \\
-          dec                           & Cosine & 0--$2\pi$  \\
-    \hline
-    \end{tabular}
-\end{table}
-
-The waveform template we utilize is \imrphenomp, a phenomenological waveform template constructed in the frequency domain that models the in-spiral, merger, and ring-down (IMR) of a compact binary coalescence~\citep{khan2016frequency}.
-Although there exist gravitational-wave templates such as \seob~\cite{seobnrv4phm} which incorporate more physics, such as information on higher-order modes, we use \imrphenomp as it is computationally inexpensive compared to others.
-
-We take 31 neighboring, off-source, non-overlapping,  4-second  segments of time-series data before the analysis data segment $d_i$ to generate the PSD.
-We use off-source to avoid the inclusion of a signal in the PSD calculation.
-A Tukey window with 0.2-second roll-offs is applied to each data segment to suppress spectral leakage after which the segments are fast-Fourier transformed and median-averaged to create a PSD~\cite{ligo_psd}.
-Like other PSD estimation methods, this method adds statistical uncertainties to the PSD~\cite{psd_student_t, chatziioannou2019noise}.
-To marginalize over the statistical uncertainty, we use the median-likelihood presented by~\citet{psd_student_t} as a post-processing step.
-\avi{Greg would like me to discuss the effect of the PSD marginalization in more detail}
-
-We take 31 neighboring off-source non-overlapping  4-second  segments of time-series data before the analysis data segment $d_i$ to generate the PSD.
-A Tukey window with a 0.2-second roll-off is applied to each data segment to suppress spectral leakage.
-After this  the segments are fast-Fourier transformed and median-averaged to create a PSD~\cite{ligo_psd}.
-Like other PSD estimation methods, this method adds statistical uncertainties to the PSD~\cite{psd_student_t, chatziioannou2019noise, Biscoveanu:2020:PhRvD}.
-To marginalize over the statistical uncertainty, we use the median-likelihood presented by~\citet{psd_student_t} as a post-processing step.
-We find that this post-processing step improves the search efficiency by $x\%$ the details of this calculation are presented in the Appendix~\ref{sec:psd-marginalization}.
-
-Finally, we neglect detector calibration uncertainty and acquire data from from the gravitational-wave Open Science Center~\cite{GWOSC}.
-The data we use is the publicly accessible O2 strain data from the Hanford and Livingston detectors, recorded while the detectors are in ``Science Mode''.
-We obtain the data using \gwpy~\cite{gwpy}.
-
-\subsection{Assigning \pastro to candidate events}
-After the calculating the \bcr for the entire set of high-mass background and simulated triggers, we calculate probability distributions $p_b(\bcr)$ and $p_s(\bcr)$ for each 2-week time-frame of O2 data.
-These distributions are used to `tune' prior-odd $\alpha$ and $\beta$ values.
-
-Using the tuned prior odds the \bcr for the candidate events can be calculated.
-Fig.~\ref{fig:bcrCdf} shows the \bcr distributions for the background triggers, simulated triggers and candidate events.
-The bulk of the background and simulated trigger distributions are separate but slightly overlap due to some of the simulated signal's being very faint.
-The separation suggests that the \bcr can successfully distinguish signals from noise or glitches.
-The vertical lines in Fig.~\ref{fig:bcrCdf} displays the \bcr for gravitational-wave candidate events.
-On comparing the candidate event \bcr values with the background distribution, we can estimate \pastro values for the candidate events.
-
-\begin{figure}[!ht]
-{\centering \includegraphics[width=0.85\linewidth]{images/reweighted_bcr_cdf_smaller_legend.png} }
-\caption[BCR distribution example]{Histograms represent the survival function (1-CDF) from our high-mass selection of background triggers (grey) and simulated signals (blue) triggers obtained from \pycbc's search of data from $\text{August 13 - 21, 2017}$.
-Vertical lines mark the $\text{ln}\ \bcr$ of IAS's GW170817A and GWTC-1's GW170814.}\label{fig:bcrCdf}
-\end{figure}
-
-\section{\label{sec:Results}Results}
-
-\input{Data/results_table}
-We analyse the $60,996$ background, $5,146$ simulated, and $25$ candidate triggers reported by \pycbc's search on the data from LIGO's second observing run, restricting our analysis to the triggers that fall within our mass-space as described in Section~\ref{sec:method}.We also analyse events and candidate events reported by GWTC-1 and the IAS group (note: some of these were identified as candidates by the \pycbc search).
-In Table~\ref{tab:results}, we summarise the \pastrobcr, along with the \pastro of other pipelines for comparison.
-Although the various pipeline \pastro are not mathematically equivalent, by comparing pipeline \pastro values for a given candidate, we can compare how significant each pipeline deems various candidates.
-The $\alpha$ and $\beta$ values utilised for each time-frame are reported in Appendix~\ref{apdx:alphabeta}.
-
-\subsection{GWTC-1 Events}
-All the confirmed gravitational-wave events from binary black hole mergers reported in GWTC-1 and within our prior space, (specifically GW170104, GW170608, GW170729, GW170809 and GW170814), have $\pastrobcr$ greater than $0.9$, indicating a high probability of the presence of an astrophysical signal.
-
-In addition to the above confirmed gravitational-wave events from GWTC-1, we have also analysed several candidate events from GWTC-1, most of which have low \pastrobcr.
-For example, consider the candidate event 170412, assigned a $\pastro$ of $0.06$ by \gstlal and has a $\pastrobcr$ of $0.01$.
-This candidate was reported to be excess power caused due noise appearing non-stationary between 60-200 Hz~\cite{GWTC1}.
-This candidate acts as an example of how $\pastrobcr$ may be utilised to eliminate candidates originating from terrestrial noise sources.
-
-\subsection{IAS Events}
-Our analysis of the high-mass IAS events and candidates in O2 has resulted in three events with disfavourable $\pastrobcr<0.5$ (GWC170402, GW170403, GW170425), and four events and one candidate with $\pastrobcr\geq0.5$ (GW170121, 170302, GW170304, GW170727, GW170817A).
-\rs{suggest an additional sentence comparing the numbers with greater/less than 0.5 to the numbers that IAS find.}
-
-GWC170402, detected by \citet{IAS2}, is reported to have a signal that is not described well by waveforms for circular binaries with aligned spins \rs{what does "not well described" mean?}.
-Hence, we might have received a low \pastrobcr due to our usage of \imrphenomp, a waveform that does not account for eccentricity.
-Additionally, the search conducted by \citet{IAS2} was a single-detector search.
-Our ranking statistic relies on the signal to appear coherent, even if just faintly coherent, amongst the various detectors to have a high \pastrobcr.
-The lack of coherence and the non-eccentric waveform may be the leading factors for a low \pastro.
-GW170403 and GW170425 which have $\pastrobcr<0.35$ also have low  \pastro reported by \citet{pycbc_ogc_2},  suggesting that these events may have been false alarms.
-
-From the candidates with $\pastrobcr>0.5$, GW170727 and 170302 are of particular interest, with \pastrobcr of $0.92$ and $0.63$.
-GW170727 was emitted from a black hole binary system with a source frame total mass $\approx 70\ \msun$.
-In addition to the high \pastrobcr reported by our study, \citet{IAS1} and \citet{pycbc_ogc_2} have also reported high \pastro values of 0.98 and 0.99, making it a viable gravitational-wave event candidate.
-Similarly, the sub-marginal-candidate 170302 reported by \cite{IAS1} with a \pastro of 0.45 appears to have a higher significance from our analysis, resulting in a \pastrobcr of $0.63$.
-
-% \av{Interesting that GW170817A has high \pastrobcr as IAS2's pipeline works well on single detector events (marginal in other detectors)}
-
-\subsection{New Candidate Events}
-Although no clear detections are made with the \bcr, a marginal-candidate 170222 has been discovered with a $\pastrobcr\sim0.5$.
-This candidate has its similar masses when compared to those of GWTC-1.
-The remaining coherent trigger candidates all have $\pastrobcr\ll0.5$ making them unlikely to originate from astrophysical sources.
-
-\avi{mass and spin estimates, is it a vanilla bbh}
-
-\section{\label{sec:Conclusion}Conclusion}
-
-% Gravitational waves from intermediate-mass black holes will Current ground-based gravitational-wave observatories like LIGO can probe the lower-end of the intermediate-mass range, u, while future space based detectors will be able to study the mergers of large limits on the low end of this mass regime are continuing to improve.
-LIGO found 190521, can find more if we are more sensitive, and can better harness data.
-
-% Most of what we know about intermediate mass black holes so far has been informed from electromagnetic observations.
-Gravitational waves provide a complementary lens to study these massive objects.
-In the future, LISA will fill in this gap, but we can begin now with LIGO...
-In this paper, we
-
-In this paper, we demonstrate that the Bayesian Coherence Ratio~\cite{BCR1} can be used as a ranking statistic to provide a better measure of significance for gravitational-wave candidates by re-analysing the significance of high-mass binary black hole triggers from O2.
-This method takes a step towards building a unified Bayesian framework that provides a search-pipeline agnostic measure of significance, utilising the same level of physical information incorporated during parameter estimation.
-
-We focused our analysis on the high-mass regime as this region of the parameter space is plagued with a high number of short duration terrestrial artefacts that can mimic signals.
-In addition to the high-mass triggers, we also analyse the high-mass binary black hole events in O2 reported by LIGO~\cite{GWTC1} and IAS~\cite{IAS1, IAS2}.
-Using \pastrobcr, we find that the analysed GWTC-1 events have high probabilities of originating from an astrophysical source.
-We also find that some of the GWTC-1 marginal triggers that have corroborated terrestrial sources (for example candidate 170412) have low \pastrobcr, indicating this method's ability to discriminate between terrestrial artefacts and astrophysical signals.
-Our analysis on the IAS events has demonstrated that GW17072 is highly likely to originate from an astrophysical source, while GW17040 is not.
-Finally, we did not identify any new gravitational-wave events, but we did find some a marginal candidate 170222.
-
-Although our analysis targets high-mass triggers, this method can be extended to include the entire body range of LIGO-detectable gravitational-wave sources.
-Additionally, to further improve the method's infrastructure, we can use more robust gravitational-wave templates (such as templates that incorporate higher-order modes), and sophisticated glitch models.
-Future analysis can also incorporate data from all available detectors in a network to increase the sensitivity of \pastrobcr.
-The BCR can discern better whether a candidate is a coherent astrophysical candidate or an incoherent glitch with data from more detectors.
-
-\avi{as the core of this method is PE, improvements in PE can be adapted into this method}
-
-%%%%%%---SECTIONS-END---%%%%%%%%%%%%
-
-%%%%%%---ACKNOWLEDGEMENTS---%%%%%%%%%%%%
-\begin{acknowledgments}
-
-This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open Science Center (https://www.gw-openscience.org), a service of LIGO Laboratory, the LIGO Scientific Collaboration and the Virgo Collaboration.
-LIGO is funded by the U.S.
-National Science Foundation.
-Virgo is funded by the French Centre National de Recherche Scientifique (CNRS), the Italian Istituto Nazionale della Fisica Nucleare (INFN) and the Dutch Nikhef, with contributions by Polish and Hungarian institutes.
-
-Thank Stuart Anderson, CIT
-
- We greatly appreciate the contributions of all these computing allocations.
-All pe performed for this study including test runs and failed simulations used about 2.5M core-hours which under the assumption of 30W per core-hour and a CO2 intensity of electricity of ~ 600 kg CO2 per MWh amounts to a carbon footprint of~ 45t of CO2.
-
-\end{acknowledgments}
-%%%%%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
-\section{Bayesian Evidence Evaluation}\label{sec:bayesianEvidEval}
-\subsection{Noise Model}
-We assume that each detector's noise is Gaussian and stationary over the period being analysed~\cite{ligo_psd}.
-In practice, we assume that the noise has a mean of zero that the noise variance $\sigma^2$ is proportional to the noise power spectral density (PSD) \psd of the data.
-Using the \psd, for each data segment $d_i$ in each of the $i$ detectors in a network of $D$ detectors, we can write
-\begin{equation}
-\label{eq:zn}
-Z^N_i = \mathcal{N}(d_i) = \frac{1}{2\pi \psd_i} \ \text{exp}\left(-\frac{1}{2} \frac{d_i}{\psd_i} \right) \ ,
-\end{equation}
-where $\mathcal{N}(d_i)$ is a normal distribution with $\mu=0$ and $\sigma^2\sim \psd$.
-
-\subsection{Coherent Signal Model}
-We model coherent signal using a binary black hole waveform template \template, where the vector \parameters contains a point in the 15 dimensional space describing precessing binary-black hole mergers.
-For the signal to be coherent, \parameters must be consistent in each 4-second data segment $d_i$ for a network of $D$ detectors, Hence, the coherent signal evidence is calculated as
-\begin{equation}
-\label{eq:zs}
-Z^S = \int\limits_{\parameters} \prod\limits^{D}_{i=1} \left[ \mathcal{L}(d_i|\template)\right] \pi(\parameters | \mathcal{H}_S)\  \text{d}\parameters \ ,
-\end{equation}
-where $\pi(\parameters| \mathcal{H}_S)$ is the prior for the parameters in the coherent signal hypothesis, and $\mathcal{L}(d_i|\template))$ is the likelihood for the coherent signal hypothesis that depends on the gravitational-wave template \template and its parameters \parameters.
-
-\subsection{Incoherent Glitch Model}
-Finally, as glitches are challenging to model and poorly understood, we follow \citet{bci} and utilise a surrogate model for glitches: the glitches are modelled using gravitational-wave templates  \template with uncorrelated  parameters amongst the different detectors such that  $\parameters_i \neq \parameters_j$ for two detectors $i$ and $j$~\cite{bci}.
-Modelling glitches with \template captures the worst case scenario: when glitches are identical to gravitational-wave signals (excluding coherent signals).
-Thus, we can write $Z^G_i$ as
-\begin{equation}
-\label{eq:zg}
-Z^G_i = \int\limits_{\parameters} \mathcal{L}(d_i|\template)\ \pi(\parameters| \mathcal{H}_G)\  \text{d}\parameters  \ ,
-\end{equation}
-where $\pi(\theta| \mathcal{H}_G)$ is the prior for the parameters in the incoherent glitch hypothesis.
-
-\section{Tuning the prior-odds}\label{sec:tuning-prior-odds}
-
-After calculating the \bcr for a set of background triggers and simulated triggers from as stretch of detector-data (a data chunk), we can compute probability distributions for the background and simulated triggers, $p_b(\bcr)$ and $p_s(\bcr)$.
-We expect the background trigger and simulated signal \bcr values to favor the incoherent glitch and the coherent signal hypothesis, respectively.
-Ideally, these distributions representing two unique populations should be distinctly separate and have no overlap in their \bcr values.
-The prior odds parameters $\alpha$ and $\beta$ from Eq.~\ref{eq:bcr} help separate the two distributions.
-Altering $\alpha$ translates the \bcr probability distributions while adjusting $\beta$ spreads the distributions.
-Although Bayesian hyper-parameter estimation can determine the optimal values for $\alpha$ and $\beta$, an easier approach is to adjust the parameters for each data chunk's \bcr distribution.
-In this study, we tune $\alpha$ and $\beta$ to maximally separate the \bcr distributions for the background and simulated triggers.
-
-To calculate the separation between $p_b(\bcr)$ and $p_s(\bcr)$, we use the Kullback--Leibler divergence (KL divergence) $D_{KL}$, given by
-\begin{equation}
-    D_{KL}(p_b | p_s) = \sum\limits_{x\in \bcr} p_b(x) \log \left( \frac{p_b(x)}{p_a(x)} \right)  \ .
-\end{equation}
-The $D_{KL}=0$ when the distributions are identical and increases as the asymmetry between the distributions increases.
-
-We limit our search for the maximum KL-divergence in the $\alpha$ and $\beta$ ranges of $[10^{-10}, 10^0]$ as values outside this range are nonphysical.
-We set our values for $\alpha$ and $\beta$ to those which provide the highest KL-divergence and calculate the \bcr for candidate events present in this data chunk.
-Note that we conduct the analysis in data chunks of a few days rather than an entire data set of a few months as the background may be different at different points of the entire data set.
-
-\section{Marginalizing over PSD statistical uncertainties}\label{sec:psd-marginalization}
-To generate the results in Fig.~\ref{fig:bcrCdf}, we applied a post-processing step to marginalize the uncertainty in the PSD.
-In Fig.~\ref{fig:bcrCdfUnmarginalized}, we show the results if this post-processing step is not applied.
-Clearly, marginalizing over uncertainty in the PSD yields an improvement in the separation of the noise and signal distributions.
-Quantitatively, at a threshold $\bcr_T=0$ the post-processing step results in a reduction in the number of background $\bcr > \bcr_T$ from $60.7\%$ to $25.28\%$ in the August 13 - 21, 2017 time-frame of data.
-For the entirety of O2 PSD marginalization resulted in a $49.26\%$ improvement in search efficiency.
-
-\begin{figure}[!ht]
-{\centering \includegraphics[width=0.85\linewidth]{images/orig_bcr_cdf_smaller_legend.png} }
-\caption[BCR distribution example]{This plot is analogous to Fig.~\ref{fig:bcrCdf}, but without using the post-processing step to marginalize over PSD statistical uncertainties.
-Without the post-processing step, there is a greater overlap between the background (grey) and foreground (blue) survival functions.
-For more details about this plot, refer to the caption of Fig.~\ref{fig:bcrCdf}.}\label{fig:bcrCdfUnmarginalized}
-\end{figure}
-
-\section{Tuned prior odds}\label{apdx:alphabeta}
-
-O2 lasted several months over which the detector's sensitivity varied.
-Hence, a part of our analysis entailed tuning the prior odds for obtaining a signal and a glitch, $\alpha$ and $\beta$, as described in Section~\ref{sec:method}.
-Table~\ref{tab:priorodds} presents the signal and glitch prior odds utilised for each time-frame of O2 data.
-\input{Data/alpha_beta_table}
-
-Tuning the prior odds can dramatically affect the \pastrobcr.
-For example, consider Table~\ref{tab:tuningresults}, which reports tuned \pastrobcr and un-tuned \untunedpastrobcr (where $\alpha=1$ and $\beta=1$) for various high-mass events and candidates.
-By tuning the prior odds, the \pastrobcr for some IAS events (for example, GW170403 and GW170817A) can change by more than 0.5, resulting in the promotion/demotion of a candidate's significance.
-
-\input{Data/tuning_results_table}
-
 \bibliography{high_mass_bib}% Produces the bibliography via BibTeX.

### 2021-04-15 scripts/plot_corners.py
add new posterior images

@@ -1,0 +1,90 @@
+import bilby
+from matplotlib import rcParams
+
+
+def set_matplotlib_style_settings():
+    major, minor = 7, 3
+    linewidth = 1.5
+    rcParams["font.size"] = 30
+    rcParams["font.family"] = "serif"
+    rcParams["font.sans-serif"] = ["Computer Modern Sans"]
+    rcParams["text.usetex"] = True
+    rcParams['axes.labelsize'] = 30
+    rcParams['axes.titlesize'] = 30
+    rcParams['axes.labelpad'] = 10
+    rcParams['axes.linewidth'] = linewidth
+    rcParams['axes.edgecolor'] = 'black'
+    rcParams['xtick.labelsize'] = 25
+    rcParams['ytick.labelsize'] = 25
+    rcParams['xtick.direction'] = 'in'
+    rcParams['ytick.direction'] = 'in'
+    rcParams['xtick.major.size'] = major
+    rcParams['xtick.minor.size'] = minor
+    rcParams['ytick.major.size'] = major
+    rcParams['ytick.minor.size'] = minor
+    rcParams['xtick.minor.width'] = linewidth
+    rcParams['xtick.major.width'] = linewidth
+    rcParams['ytick.minor.width'] = linewidth
+    rcParams['ytick.major.width'] = linewidth
+    rcParams['xtick.top'] = True
+    rcParams['ytick.right'] = True
+    rcParams['axes.grid'] = False
+    rcParams["axes.titlepad"] = 8
+
+
+PARAMS = dict(
+    chi_eff=dict(latex_label=r"$\chi_{eff}$", range=(-0.8, 0.8)),
+    chi_p=dict(latex_label=r"$\chi_{p}$", range=(0, 1)),
+    chi_1=dict(latex_label=r"$\chi_1$", range=(0, 1)),
+    cos_tilt_1=dict(latex_label=r"$\cos(t1)$", range=(-1, 1)),
+    cos_tilt_2=dict(latex_label=r"$\cos(t2)$", range=(-1, 1)),
+    cos_theta_12=dict(latex_label=r"$\cos \theta_{12}$", range=(-1, 1)),
+    tilt_1=dict(latex_label=r"$tilt_{1}$", range=(0, np.pi)),
+    remnant_kick_mag=dict(latex_label=r'$|\vec{v}_k|\ $km/s', range=(0, 3000)),
+    chirp_mass=dict(latex_label=r"$M_{c}$", range=(5, 200)),
[…]

### 2021-04-15 main.tex
complete v2

@@
 \avi{
-Talk about the differences in pastro calculation ~\cite{Farr:2015:PhRvD, Gaebel:2019:MNRAS,Galaudage:2020:PhRvD}
+The pastro calculation may need some more discussion.
+Taking pastro = 1-FAP as identifying a real signal can be hugely problematic: \url{https://en.wikipedia.org/wiki/Misuse_of_p-values}, even though its ok in this case.
+Maybe the following papers have something that can help motivate this ~\cite{Farr:2015:PhRvD, Gaebel:2019:MNRAS,Galaudage:2020:PhRvD}
 }
-
-\greg{This needs more explanation and discussion.
-I know that in the Gaebel paper~\cite{Gaebel:2019:MNRAS}, they make the connection (they don't in FGMC~\cite{Farr:2015:PhRvD}).
-But, effectively the FAP is the p-value, the probability that the event arose from the background noise alone.
-Taking 1-FAP as identifying a real signal can be hugely problematic (Wikipedia has its own page on it \url{https://en.wikipedia.org/wiki/Misuse_of_p-values}).
-In this case, it is a reasonable thing to do, because you are saying "anything which rings up our detection statistic is astrophysical by virtue that it is coherent".
-But, that needs to be spelled out.
-Also, it may be useful to say that the p-astro calculated from, say, PyCBC/GSTLAL are not 1-FAP, but instead apply the FGMC population approach.}
 
@@
     Prior settings for the parameters used during our parameter estimation.
-The definitions of the parameters are documented in \citet{bilby_gwtc}~Table~E1.\label{tab:priors}}.
+The definitions of the parameters are documented in \citet{bilby_gwtc}~Table~E1.
 The trigger time $t_c$ is obtained from the data products of \pycbc's O2 search.
+\label{tab:priors}}
     \begin{tabular}{c c c c}
@@
 Although no clear detections are made with the \bcr, a marginal-candidate 170222 has been discovered with a $\pastrobcr\sim0.5$.
-This candidate has an SNR$\sim7.7$, low spin magnitudes and source-frame component masses of ${47.16}_{-5.77}^{+8.00}, {35.50}_{-6.35}^{+5.79}$, making it one of the heavier black-hole mergers from O2 and \GWTC.
+This candidate has an SNR$\sim7.7$, low spin magnitudes and source-frame component masses of $({47.16}_{-5.77}^{+8.00}, {35.50}_{-6.35}^{+5.79}) \msun$, making it one of the heavier black-hole mergers from O2 and \GWTC.
 This candidate may be of interest as one component black hole may lie in the pair-instability mass gap ($55^{+10}_{-10}-148^{+13}_{-12}\msun$)~\cite{Woosley:2021:arXiv, Heger:2002:ApJ}.
@@
 
-\greg{If the search is better at identifying high-mass black holes and has not found any..
-doesn't this mean we can better constraint their population properties?
-Do we know how much (if at all) this method outperforms current searches?
-This question may be stretching the scope of the paper, but I wondered if you had some thoughts.}
+\greg{can we better constraint their population properties? Do we know how much (if at all) this method outperforms current searches?}
 
-\avi{
-\begin{itemize}
-    \item Unlike for stellar-mass BBH, there are still alot of uncertainties for IMBH formation scenarios. Hence, upper limits would be challenging to calculate
-    \item We would require to do more robust simulation studies to see what would fall in/outside our detection threshold, to put constraints on population properties and study the search's sensitivity
-\end{itemize}
+\avi{Unlike for stellar-mass BBH, there are still alot of uncertainties for IMBH formation scenarios.
+Hence, upper limits would be challenging to calculate.
+Additionally, we would require to do more robust simulation studies to see what would fall in/outside our detection threshold, to put constraints on population properties and study the search's sensitivity
 }
@@
 \section{A closer look at 170222}\label{apdx:170222}
-PyCBC found in chunk7, with template, corresponds to parameters Xyz. Our parameters state that it is xyz.
-Put in corner, write notes from
+PyCBC found the candidate 170222 with $\mathcal{M}_c=49.46$ and $q=0.68$, values that fall within our uncertainty limits.
+Some of the posteriors that were produced as a by-product of our \bcr calculation can be viewed in Fig.~\ref{fig:170222}.
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}
+        \centering
+        \includegraphics[width=0.45\linewidth]{170222_prior_posterior.png}
+    \end{subfigure}
+    ~ 
+    \begin{subfigure}
+        \centering
+        \includegraphics[width=0.45\linewidth]{170222_source_posterior.png}
+    \end{subfigure}
+    \caption{Posterior distributions for some parameters of 170222, comparing posteriors in orange and prior probability density functions to the one-dimensional marginal distributions in green. 
+    Left: Posterior probability distributions for 4 of the 11 search parameters.
+Sections of the prior probability density functions used for analysis are displayed in green in one-dimensional marginal distributions plots.
+    Right: Posterior probability distributions for some inferred parameters.
+    \label{fig:170222}}
+\end{figure*}
 

### 2021-04-15 main.tex
done with minor read-through edits

@@
 \newcommand{\bilby}{{\sc \href{https://lscsoft.docs.ligo.org/bilby/}{\texttt{Bilby}}}\xspace}
-\newcommand{\bilbypipe}{{\sc bilby\_pipe}\xspace}
-\newcommand{\pbilby}{{\sc pBilby}\xspace}
-\newcommand{\dynesty}{{\sc dynesty}\xspace}
+\newcommand{\bilbypipe}{{\sc \texttt{bilby\_pipe}}\xspace}
+\newcommand{\dynesty}{{\sc \texttt{dynesty}}\xspace}
 \newcommand{\cpnest}{{\sc cpnest}\xspace}
@@
 \newcommand{\seob}{{\sc SEOBNRv4PHM}\xspace}
+
 \newcommand{\gstlal}{{\sc GstLAL}\xspace}
 \newcommand{\cwb}{{\sc cWB}\xspace}
-\newcommand{\pycbc}{{\sc \href{https://pycbc.org/}{\texttt{PyCBC}}}\xspace}
+\newcommand{\pycbc}{{\sc \href{https://pycbc.org/}{{PyCBC}}}\xspace}
 
-\newcommand{\GWTC}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2019PhRvX...9c1040A/abstract}{\texttt{GWTC-1}}}\xspace}
-\newcommand{\OGC}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2020ApJ...891..123N/abstract}{\texttt{2-OGC}}}\xspace}
-\newcommand{\IAS}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2020PhRvD.101h3030V/abstract}{\texttt{IAS}}}\xspace}
+\newcommand{\GWTC}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2019PhRvX...9c1040A/abstract}{{GWTC-1}}}\xspace}
+\newcommand{\OGC}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2020ApJ...891..123N/abstract}{{2-OGC}}}\xspace}
+\newcommand{\IAS}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2020PhRvD.101h3030V/abstract}{{IAS}}}\xspace}
 
@@
 Our analysis does not discover new intermediate-mass black holes.
-However, we find support for some previously identified borderline stellar-mass binary black hole detections and gravitational-wave detections made externally from the LIGO-Virgo-KAGRA collaboration.
+However, we find support for some stellar mass binary black holes unreported in GWTC-1.
 \end{abstract}
@@
 Compact binaries coalesces (CBCs) can provide unambiguous gravitational wave signals for intermediate-mass candidates (e.g.
-the $142^{+28}_{-16}\ \msun$ remnant observed from the gravitational wave event GW190521~\cite{Abbott:2020:PhRvL}), and ground-based detectors can probe the lower-end $10^{2} - 10^{3}\ \msun$ of the intermediate mass range.
+the $142^{+28}_{-16}\ \msun$ remnant observed from the gravitational wave event GW190521~\cite{Abbott:2020:PhRvL}).
+Ground-based gravitational wave detectors can probe the lower-end $10^{2} - 10^{3}\ \msun$ of the intermediate mass range.
+
 Mergers involving either a binary system with at least one intermediate-mass component, or a system whose merger results in an intermediate-mass remnant will have large total masses $\text{M}_{T}$.
@@
 The high-mass candidate \bcr values are then used to calculate the probability that the candidate is of astrophysical origins, \pastrobcr.
-Finally, if the candidate has a \pastro reported by the the LIGO-Virgo-KAGRA (LVK) collaboration in \GWTC~\cite{GWTC1}, the \pycbc-team~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6, pycbc_single_det, pycbc_ogc_2}, by the Institute of Advanced study's team (IAS)~\cite{IAS0, IAS1, IAS2}, or by \citet{bayesian_odds}, we compare their \pastro with the \pastrobcr.
+Finally, if the candidate has a \pastro reported by the the LIGO-Virgo-KAGRA (LVK) collaboration in \GWTC~\cite{GWTC1}, the \pycbc-team~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6, pycbc_single_det, pycbc_ogc_2}, by the Institute of Advanced study's team (\IAS)~\cite{IAS0, IAS1, IAS2}, or by \citet{bayesian_odds}, we compare their \pastro with the \pastrobcr.
 
@@
 The remainder of this paper is structured as follows.
-We outline our methods, including details of our ranking statistic and the retrieval of our candidate in Section~\ref{sec:method}.
+We outline our methods, including details of our ranking statistic and the retrieval of our candidates in Section~\ref{sec:method}.
 We present details on the implementation of our analysis in Section~\ref{sec:Analysis}.
@@
 \pycbc~\cite{pycbc_og4} and \gstlal~\cite{sachdev2019gstlal}, and the coherent burst search \cwb~\cite{cwb} used by LVK to search for signals in gravitational-wave data all use ranking statistics in such a manner~\cite{GWTC1}.
-Both \pycbc and \gstlal's ranking statistic incorporate information of the relative likelihood that the data contains a coherent-signal versus just noise, while \cwb's ranking statistic uses the information of coherent energy present in the network of detectors~\cite{GWTC1}.
+Both \pycbc and \gstlal's ranking statistic incorporate information of the relative likelihood that the data contains a coherent signal versus just noise.
+In contrast, \cwb's ranking statistic uses the information of coherent energy present in the network of detectors~\cite{GWTC1}.
 
@@
 \begin{equation}
-    \mathcal{Z}(d|\mathcal{H}) = \int\limits_{\parameters} \ \mathcal{L}(d|\parameters,\mathcal{H}) \ \pi(\parameters | \mathcal{H}) \ d\parameters
+    \mathcal{Z}(d|\mathcal{H}) = \int\limits_{\parameters} \ \mathcal{L}(d|\parameters,\mathcal{H}) \ \pi(\parameters | \mathcal{H}) \ d\parameters\ ,
 \end{equation} is the likelihood after marginalizing over the parameters \parameters.
@@
 \end{equation}
-where $\{\mathcal{Z}^A, \mathcal{Z}^B\}$ are shorthand for the evidences $\{\mathcal{Z}(d|\mathcal{H}_A), \mathcal{Z}(d|\mathcal{H}_B)\}$ and $\{\pi(\parameters | \mathcal{H_A}), \pi(\parameters | \mathcal{H_B})\}$ are the prior-odds for each hypotheses.
-The odds-ratio can tell us which of the two hypotheses is more likely.
-For example, if $\mathcal{O}^A_B >> 1$, then this odds ratio indicates that the $\mathcal{H}_A$ describes the data much better than $\mathcal{H}_B$.
+where  $\{\pi(\parameters | \mathcal{H_A}), \pi(\parameters | \mathcal{H_B})\}$ are the prior-odds for each hypothesis and $\{\mathcal{Z}^A, \mathcal{Z}^B\}$ are shorthand for the evidences $\{\mathcal{Z}(d|\mathcal{H}_A), \mathcal{Z}(d|\mathcal{H}_B)\}$.
+The odds-ratio can quantify which of the two hypotheses is more likely.
+For example, if $\mathcal{O}^A_B >> 1$, then the odds are in favor of the $\mathcal{H}_A$ hypotheses.
 
@@
     \item $P^S=P(\mathcal{H}_S)/P(\mathcal{H}_I)$, the prior-odds for obtaining a coherent signal versus an incoherent instrumental feature.
-    \item $P^G=P(\mathcal{H}_G| \mathcal{H}_I)$, the prior-odds for obtaining a glitch assuming there is an incoherent instrumental feature.
+    \item $P^G=P(\mathcal{H}_G| \mathcal{H}_I)$, the probability of obtaining a glitch assuming there is an incoherent instrumental feature.
 \end{itemize}
@@
 To evaluate $Z^S$, $Z^G_i$ and $Z^N_i$ and calculate the \bcr Eq.~\ref{eq:bcr} for triggers, we carry out Bayesian inference with \bilby~\cite{bilby, bilby_pipe}, employing \dynesty~\cite{dynesty} as our nested sampler.
-Nested sampling, an algorithm introduced by~\citet{skilling2004, skilling2006}, provides an estimate of the true Bayesian evidence and is often utilized for parameter estimation within the LIGO collaboration~\cite{bilby, bilby_paper, pbilby_paper}.
+Nested sampling, an algorithm introduced by~\citet{skilling2004, skilling2006}, provides an estimate of the Bayesian evidence and is often utilized for parameter estimation within the LIGO collaboration~\cite{bilby, bilby_paper, pbilby_paper}.
 
@@
 
-We take 31 neighboring, off-source, non-overlapping, 4-second segments of time-series data before the analysis data segment $d_i$ to generate the PSD.
-We use off-source to avoid the inclusion of a signal in the PSD calculation.
-A Tukey window with 0.2-second roll-offs is applied to each data segment to suppress spectral leakage after which the segments are fast-Fourier transformed and median-averaged to create a PSD~\cite{ligo_psd}.
-Like other PSD estimation methods, this method adds statistical uncertainties to the PSD~\cite{psd_student_t, chatziioannou2019noise}.
-To marginalize over the statistical uncertainty, we use the median-likelihood presented by~\citet{psd_student_t} as a post-processing step.
-
 We take 31 neighboring off-source non-overlapping  4-second  segments of time-series data before the analysis data segment $d_i$ to generate the PSD.
@@
 
-Finally, we neglect detector calibration uncertainty and acquire data from from the gravitational-wave Open Science Center~\cite{GWOSC}.
+Finally, we acquire data from from the gravitational-wave Open Science Center~\cite{GWOSC}.
 The data we use are the publicly accessible O2 strain data from the Hanford and Livingston detectors, recorded while the detectors are in ``Science Mode''.
@@
 After the calculating the \bcr for the entire set of high-mass background and simulated triggers, we calculate probability distributions $p_b(\bcr)$ and $p_s(\bcr)$ for each 2-week time-frame of O2 data.
-These distributions are used to `tune' prior-odd $P^S$ and $P^G$ values.
+These distributions are used to `tune' prior-odd $P^S$ and $P^G$ values as described in Appendix~\ref{apdx:tuning-prior-odds}.
 
@@
 \input{Data/results_table}
-We analyze the $60,996$ background, $5,146$ simulated, and $25$ candidate triggers reported by \pycbc's search on the data from LIGO's second observing run, restricting our analysis to the triggers that fall within our mass-space as described in Section~\ref{sec:method}.We also analyze events and candidate events reported by \GWTC and the IAS group (note: some of these were identified as candidates by the \pycbc search).
-In Table~\ref{tab:results}, we summaries the \pastrobcr, along with the \pastro of other pipelines for comparison.
+We analyze the $60,996$ background, $5,146$ simulated, and $25$ candidate triggers reported by \pycbc's search on the data from LIGO's second observing run, restricting our analysis to the triggers that fall within our mass-space as described in Section~\ref{sec:method}.We also analyze events and candidate events reported by \GWTC and the \IAS group (note: some of these were identified as candidates by the \pycbc search).
+Table~\ref{tab:results} summaries the \pastrobcr, along with the \pastro of other pipelines for comparison.
 Although the various pipeline \pastro are not mathematically equivalent, by comparing pipeline \pastro values for a given candidate, we can compare how significant each pipeline deems various candidates.
@@
 \subsection{GWTC-1 Events}
-All the confirmed gravitational-wave events from binary black hole mergers reported in \GWTC and within our prior space, (specifically GW170104, GW170608, GW170729, GW170809 and GW170814), have $\pastrobcr>0.9$, indicating a high probability of the presence of an astrophysical signal.
+All the confirmed gravitational-wave events from binary black hole mergers reported in \GWTC and within our prior space, (specifically GW170104, GW170608, GW170729, GW170809 and GW170814), have $\pastrobcr>0.9$, indicating a high probability of an astrophysical signal.
 
@@
 In the future, space-based gravitational wave detectors will uncover black holes in the upper end of the intermediate-mass range.
-In the present ground-based gravitational-wave observatories can probe the lower-end of the intermediate-mass range.
+In the present, ground-based gravitational-wave observatories can probe the lower-end of the intermediate-mass range.
 However, many short-duration terrestrial artifacts that mimic intermediate-mass gravitational-wave signals plague ground-based detectors, making intermediate-mass detection challenging.
@@
 We also find that some of the \GWTC marginal triggers that have corroborated terrestrial sources (for example, candidate 170412) have low \pastrobcr, indicating this method's ability to discriminate between terrestrial artifacts and astrophysical signals.
-Our analysis on the high-mass \IAS events demonstrates that GW17072 is likely to originate from an astrophysical source, while GW17040 is not.
+Our analysis of the high-mass \IAS events demonstrates that GW170121, GW170727, and GW170817A are likely to originate from astrophysical sources, while GWC170402, GW170402, and GW170425  are not.
 Finally, we do not identify any new gravitational-wave events, but we find a new marginal binary-black hole merger candidate, 170222.
@@
 
-\greg{can we better constraint their population properties? Do we know how much (if at all) this method outperforms current searches?}
+% \greg{can we better constraint their population properties? Do we know how much (if at all) this method outperforms current searches?}
 
-\avi{Unlike for stellar-mass BBH, there are still alot of uncertainties for IMBH formation scenarios.
+% \avi{Unlike for stellar-mass BBH, there are still alot of uncertainties for IMBH formation scenarios.
 Hence, upper limits would be challenging to calculate.
 Additionally, we would require to do more robust simulation studies to see what would fall in/outside our detection threshold, to put constraints on population properties and study the search's sensitivity
-}
+% }
 
@@
 We also warmly thank Ian Harry and Thomas Dent for answering questions about the \pycbc search's data products.
-\avi{double check with Stuart what CIT's energy source is}
 
@@
 
-\section{Tuning the prior-odds}\label{sec:tuning-prior-odds}
+\section{Tuning the prior-odds}\label{apdx:tuning-prior-odds}
 

### 2021-05-26 main.tex

@@
 \newcommand{\cwb}{{\sc cWB}\xspace}
+\newcommand{\spiir}{{\sc SPIIR}\xspace}
+\newcommand{\mbta}{{\sc MBTAOnline}\xspace}
 \newcommand{\pycbc}{{\sc \href{https://pycbc.org/}{{PyCBC}}}\xspace}
@@
 \newcommand{\msun}{\mathcmd{\text{M}_\odot}}
+\newcommand{\mtot}{\mathcmd{M}}
 \newcommand{\parameters}{\mathcmd{\vec{\theta}}}
@@
 Numerous methods to search for $10^4-10^6\ \msun$ intermediate-mass black holes exist, while the primary method to find $10^2-10^3\ \msun$ is by identifying gravitational-waves emitted from the merger of stellar binaries.
-Theoretically, ground-based gravitational-wave detectors are sensitive to such mergers and have found one $142^{+28}_{-16}\ \msun$ intermediate-mass black hole.
-In reality, ground-based detectors are plagued with short-duration instrumental transients that mimic the gravitational-wave signals from mergers capable of producing intermediate-mass black holes.
+Ground-based gravitational-wave detectors are in principle sensitive to such mergers and have found one $142^{+28}_{-16}\ \msun$ intermediate-mass black hole.
+In reality, ground-based detectors are plagued with short-duration instrumental transients that mimic the gravitational-wave signals from mergers capable of producing intermediate-mass black holes, making their detection difficult.
 Here we demonstrate a ranking statistic utilizing Bayesian inference to detect high-mass binary black hole mergers (with a total mass $>55$~\msun).
@@
 \section{Introduction}
-Since the 1970s, there has been a steady accumulation of evidence for stellar mass ($\text{M}_\text{BH} < 10^{2} \ \msun$) and supermassive black holes ($\text{M}_\text{BH} > 10^{6} \ \msun$)~\cite{Webster:1972:Natur, Balick:1974:ApJ, Ghez:1998:ApJ, Genzel:2010:RvMP, Abbott:2019:PhRvX, EventHorizonTelescopeCollaboration:2019:ApJL, Abbott:2020:arXiv}.
-However, there is a deficiency of observational evidence for black holes in the intermediate-mass range $10^{2} - 10^{6}\ \msun$.
+Since the 1970s, there has been a steady accumulation of evidence for stellar mass ($M_\text{BH} < 10^{2} \ \msun$) and supermassive black holes ($M_\text{BH} > 10^{6} \ \msun$)~\cite{Webster:1972:Natur, Balick:1974:ApJ, Ghez:1998:ApJ, Genzel:2010:RvMP, Abbott:2019:PhRvX, EventHorizonTelescopeCollaboration:2019:ApJL, Abbott:2020:arXiv}.
+However, there is a deficiency of observational evidence for black holes in the `intermediate-mass' range $10^{2} - 10^{6}\ \msun$.
 The discovery of an intermediate-mass black hole population will bridge this observational gap, probe intermediate-mass formation environments (e.g.
 accretion disks of active galactic nuclei~\cite{Tagawa:2021:ApJ, Li:2021:arXiv, Samsing:2020:arXiv, Tagawa:2020:ApJ, Ishibashi:2020:A&A, Grobner:2020:A&A, Yang:2019:PhRvL, McKernan:2019:ApJL, Yang:2019:ApJ, McKernan:2018:ApJ, Bellovary:2016:ApJL, McKernan:2014:MNRAS, McKernan:2012:MNRAS}, the centers of dense stellar clusters~\cite{Banerjee:2021:MNRASa, Zevin:2021:ApJ,Mapelli:2021:arXiv,Weatherford:2021:ApJL, Bouffanais:2021:arXiv, Ballone:2021:MNRAS, Kumamoto:2021:arXiv, Banerjee:2021:MNRASb, Martinez:2020:ApJ, Romero-Shaw:2020:ApJL, Anagnostou:2020:PASA}, Population-III stars~\cite{Toubiana:2021:PhRvL, Farrell:2021:MNRAS, Safarzadeh:2020:ApJL, Liu:2020:MNRAS, Inayoshi:2017:MNRAS}), and illuminate our understanding of supermassive black hole formation~\cite{Askar:2021:MNRAS, ArcaSedda:2019:arXiv, Amaro-Seoane:2007:CQGra, Gurkan:2006:ApJL}.
-A variety of techniques have been employed to search for $10^{4} - 10^{6}\ \msun$ intermediate mass candidates (reverberation mapping~\cite{Peterson:2014:SSRv}, direct kinematic measurements~\cite{Schodel:2002:Natur, Kiziltan:2017:Natur}, applying macroscopic galaxy to black hole mass scaling relations (M$_{BH}$-$\sigma$ and M$_{BH}$-L relations)~\cite{Graham:2013:ApJ, Wevers:2017:MNRAS}, studying  X-ray luminosity and spectra~\cite{Greene:2004:ApJ, Lin:2020:ApJL}, gravitational lensing of light curves~\cite{paynter_evidence_2021}, and others~\cite{Greene:2020:ARA&A, Koliopanos:2017:mbhe, Mezcua:2017:IJMPD})).
-However, these observational techniques are challenging to use for intermediate mass black holes, due to their small sphere of influence.
+A variety of techniques have been employed to search for $10^{4} - 10^{6}\ \msun$ intermediate mass candidates (reverberation mapping~\cite{Peterson:2014:SSRv}, direct kinematic measurements~\cite{Schodel:2002:Natur, Kiziltan:2017:Natur}, applying macroscopic galaxy to black hole mass scaling relations ($M_{BH}$-$\sigma$ and $M_{BH}$-L relations)~\cite{Graham:2013:ApJ, Wevers:2017:MNRAS}, studying  X-ray luminosity and spectra~\cite{Greene:2004:ApJ, Lin:2020:ApJL}, gravitational lensing of light curves~\cite{paynter_evidence_2021}, and others~\cite{Greene:2020:ARA&A, Koliopanos:2017:mbhe, Mezcua:2017:IJMPD})).
+However, these observational techniques are challenging to use for intermediate mass black holes due to their small sphere of influence compared to super-massive black holes~\cite{Mezcua:2017:IJMPD}.
 Additionally, some candidates discovered with these techniques can be attributed to sources without intermediate-mass black holes (e.g.
 clusters of stellar-mass black holes~\cite{Ridolfi:2016:MNRAS, Freire:2017:MNRAS}, anisotropic emission from neutron stars~\cite{Israel:2017:MNRAS, RodriguezCastillo:2020:ApJ}), while others have high uncertainties due to the observational techniques utilized~\cite{Greene:2020:ARA&A}.
-Compact binaries coalesces (CBCs) can provide unambiguous gravitational wave signals for intermediate-mass candidates (e.g.
+
+Compact binaries coalescences (CBCs) can provide unambiguous gravitational-wave signals for intermediate-mass candidates (e.g.
 the $142^{+28}_{-16}\ \msun$ remnant observed from the gravitational wave event GW190521~\cite{Abbott:2020:PhRvL}).
 Ground-based gravitational wave detectors can probe the lower-end $10^{2} - 10^{3}\ \msun$ of the intermediate mass range.
-
-Mergers involving either a binary system with at least one intermediate-mass component, or a system whose merger results in an intermediate-mass remnant will have large total masses $\text{M}_{T}$.
-As a binary's $\text{M}_{T}$ is associated with its gravitational-wave merger frequency, $f\sim \text{M}_{T}^{-1}$, systems with large $\text{M}_{T}$ have very low merger frequencies $f < 100\ \text{Hz}$.
+ As a binary's total mass $\text{M}_{T}$ is associated with its gravitational-wave merger frequency, $f\sim \text{M}_{T}^{-1}$, systems with large $\text{M}_{T}$ have very low merger frequencies $f < 100\ \text{Hz}$.
 Hence, ground based gravitational wave detectors ($\sim 10^1 - 10^3\ \text{Hz}$) are sensitive to the last milliseconds of merging systems with $100 \msun < \text{M}_{T} < 400 \msun$~\cite{LIGOScientificCollaboration:2015:CQGra, Martynov:2016:PhRvD, Moore_2014}, while space-based detectors ($\sim 10^{-2} - 10^1\ \text{Hz}$) can study the full signals of merging systems with $10^4 \msun < \text{M}_{T} < 10^7 \msun$~\cite{ Moore_2014, Lu:2019:PhRvD}.
 
-Because of high-total mass systems' short-durations in ground-based gravitational wave data steams, handling data quality is critical to their detection.
-The low-frequency ranges of ground-based observatories are plagued with incoherent non-stationary terrestrial artifacts, called \textit{glitches}~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
+Because of the short-duration of intermediate-mass gravitational-wave signals in ground-based detector data steams, handling data quality is critical to their detection.
+The low-frequency ranges of ground-based observatories are plagued with non-stationary terrestrial artifacts, called \textit{glitches}~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
 Some glitches, similar to signals from high total mass mergers, last for a fraction of a second, making them difficult to distinguish from the signals.
-These glitches that mimic astrophysical signals can severely decrease the confidence in detection of true gravitational-waves from high total mass mergers.
+These glitches that mimic astrophysical signals can severely decrease the confidence in detection of true gravitational-waves from high total mass mergers~\cite{pycbc_short_duration_transients}.
 
@@
 The \bcr used in this study is a bootstrap-Bayesian odds computed using Bayesian evidences that describe the explicit probability of data under the hypothesis that the data contains coherent signals vs incoherent glitches, and empirically calculated prior-odds that describe how likely each hypotheses is.
-The high-mass candidate \bcr values are then used to calculate the probability that the candidate is of astrophysical origins, \pastrobcr.
+\rs{Need to add another couple of sentences describing what is unique about this work.
+For instance, we study both foreground \textit{and} background events (which is the first time anyone's done a large-scale Bayesian analysis on background data).
+Suggest using this format: ``We highlight a number of innovations unique to this work.
+First...''} The high-mass candidate \bcr values are then used to calculate the probability that the candidate is of astrophysical origins, \pastrobcr.
 Finally, if the candidate has a \pastro reported by the the LIGO-Virgo-KAGRA (LVK) collaboration in \GWTC~\cite{GWTC1}, the \pycbc-team~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6, pycbc_single_det, pycbc_ogc_2}, by the Institute of Advanced study's team (\IAS)~\cite{IAS0, IAS1, IAS2}, or by \citet{bayesian_odds}, we compare their \pastro with the \pastrobcr.
@@
 
-The standard framework to identify CBC gravitational-wave signals hidden in data is by quantifying the significance of candidates with null-hypothesis significance testing~\cite{GWTC1, GWTC2}.
+The standard framework to identify CBC gravitational-wave signals in data is by quantifying the significance of candidates with null-hypothesis significance testing~\cite{GWTC1, GWTC2}.
 In this framework, the candidates' ranking statistic is compared against a background distribution in a frequentist approach.
 The independent matched-filter searches, e.g.
-\pycbc~\cite{pycbc_og4} and \gstlal~\cite{sachdev2019gstlal}, and the coherent burst search \cwb~\cite{cwb} used by LVK to search for signals in gravitational-wave data all use ranking statistics in such a manner~\cite{GWTC1}.
+\pycbc~\cite{pycbc_og4}, \spiir~\cite{spiir} and \gstlal~\cite{sachdev2019gstlal}, and the coherent burst search \cwb~\cite{cwb} used by LVK to search for signals in gravitational-wave data all use ranking statistics in such a manner~\cite{GWTC1}.
 Both \pycbc and \gstlal's ranking statistic incorporate information of the relative likelihood that the data contains a coherent signal versus just noise.
@@
 
-In a similar vein, this work utilizes Bayesian inference to calculate the Bayesian Coherence Odds-Ratio~\cite{BCR1}, \bcr, of high-mass candidates in LIGO's second observing run.
-We use the \bcr not as an odds-ratio but instead as a ranking statistic.
+Bayesian inference offers an alternative means to rank the significance of candidate events by computing the odds that the data contain a transient gravitational-wave signal vs.
+instrumental glitches or noise~\cite{BCR1}.
+This method relies on accurate models for the signal and glitch morphologies and populations~\cite{BCR1}.
+In principle, Bayesian odds is the optimal method for hypothesis testing~\cite{BCR2}.
+Much of its power comes from the Bayesian ``evidence'': a marginalized likelihood.
+The evidence is the correct likelihood of having obtained the data given a hypothesis.
+However, due to the high computational cost to calculate the evidence, it is not explicitly used in current matched filter searches.
+Here, we explore a middle-ground hybrid between frequentist matched filtered searches and Bayesian odds.
+We compute Bayesian evidences for foreground and background data under the assumption that they either contain coherent gravitational-wave signals, noise, or glitches.
+However, instead of computing true Bayesian odds, we use the evidences to form a bootstrapped distribution for the odds of foreground and background events to form a frequentist ranking statistic.
 
@@
 \begin{equation}
-    \mathcal{O}^A_B = \frac{\mathcal{Z}^A\ \pi(\parameters | \mathcal{H_A})}{\mathcal{Z}^B\ \pi(\parameters | \mathcal{H_B})}\ ,
+    \mathcal{O}^A_B = \frac{\mathcal{Z}^A\ \pi^A}{\mathcal{Z}^B\ \pi^B}\ ,
 \end{equation}
-where  $\{\pi(\parameters | \mathcal{H_A}), \pi(\parameters | \mathcal{H_B})\}$ are the prior-odds for each hypothesis and $\{\mathcal{Z}^A, \mathcal{Z}^B\}$ are shorthand for the evidences $\{\mathcal{Z}(d|\mathcal{H}_A), \mathcal{Z}(d|\mathcal{H}_B)\}$.
+where  $\{\pi^A, \pi^B\}$ are the prior-odds for each hypothesis and $\{\mathcal{Z}^A, \mathcal{Z}^B\}$ are shorthand for the evidences $\{\mathcal{Z}(d|\mathcal{H}_A), \mathcal{Z}(d|\mathcal{H}_B)\}$.
 The odds-ratio can quantify which of the two hypotheses is more likely.
@@
 \label{eq:bcr}
-\bcr = \frac{P^S Z^S}{\prod\limits^D_{i=1} \ [P^G Z^G_i + (1-P^G)Z^N_i]}\ ,
+\mathcal{O}_{\mathrm{BCR}} = \frac{P^S Z^S}{\prod\limits^D_{i=1} \ [P^G Z^G_i + (1-P^G)Z^N_i]}\ ,
 \end{equation}
+
 where $P^S$ and $P^G$ are the prior-odds of obtaining a signal or a glitch from a stretch of data. The prior-odds can be defined more explicitly as 
@@
 \end{itemize}
+
+\begin{equation}
+\label{eq:bcr}
+\bcr = \frac{\hat{\pi}^S Z^S}{\prod\limits^D_{i=1} \ [\hat{\pi}^G Z^G_i + (1-\hat{\pi}^G)Z^N_i]}\ ,
+\end{equation}
+
+\avi{Ranking statistic \bcr is like an estimator of what $\mathcal{O}_{\mathrm{BCR}}$ is}
 
@@
 
+\avi{Eric, can you take a look at this section about the FAP p-astro?}
 \avi{
@@
 \subsection{Data for Analysis}
-The LIGO Scientific collaboration operates several search pipelines that scan for gravitational-waves from compact binary mergers such as \gstlal~\cite{sachdev2019gstlal}, \texttt{MBTAOnline}~\cite{MBTA}, \texttt{SPIIR}~\cite{spiir} and \pycbc~\cite{pycbc_og4}.
+
+\rs{Rory: Suggest a bit more preable here, something like ``To build a ranking statistic from $\rho$ we need to compute its distribution for foreground and background events.
+The number of background events in a typical search is very large, however we can manage the number of background triggers by focusing on a specific mass range.
+Background triggers are generated by search pipelines...}
+
+The LIGO Scientific collaboration operates several search pipelines that scan for gravitational-waves from compact binary mergers such as \gstlal~\cite{sachdev2019gstlal}, \mbta~\cite{MBTA}, \spiir~\cite{spiir} and \pycbc~\cite{pycbc_og4}.
 The output of \pycbc's search is a list of times and their corresponding \pycbc ranking statistic \pycbcstat values.
@@
 
-When \pycbc observes a trigger between detectors with coincident parameters and a time of arrival difference less than the gravitational-wave travel time between detectors, the trigger is labeled a \textit{candidate event trigger}, a trigger that may be from astrophysical origins~\cite{pycbc_og1}.
+\pycbc produces three categories of triggers: 
+\begin{itemize}
+    \item \textit{Candidate event trigger}: a trigger observed with coincident parameters amongst a network of detectors. 
+    \item \textit{Simulated trigger}: a trigger detected from an artificially manufactured signal injected into detector data.  
+    \item \textit{Background trigger}: a trigger obtained from incoherent signal-free background data (data manufactured by applying relative offsets, or time-slides, between the data of different detectors~\cite{pycbc_og6}).
+\end{itemize}
+
+% \rs{Rory: suggest cutting most or all of this paragraph.
+We don't need to explain how pycbc works in detail.
+A reference to the relevant paper is sufficient.
+The key point is that a pipeline produces them for us} When \pycbc observes a trigger between detectors with coincident parameters and a time of arrival difference less than the gravitational-wave travel time between detectors, the trigger is labeled a \textit{candidate event trigger}, a trigger that may be from astrophysical origins~\cite{pycbc_og1}.
 To test the pipeline's sensitivity \pycbc also conducts searches for \textit{simulated triggers}, artificial triggers manufactured by injecting signals into the detector data.
@@
 
-Our work demonstrates that the \bcr can be used in the same way as \pycbcstat to measure candidate triggers' statistical significance.
+Our work demonstrates that the \bcr can be used measure candidate triggers' statistical significance.
 The \bcr can be a powerful ranking statistic as it incorporates information of not only all possible binary black hole systems that might have merged to produce the trigger but also the various incoherent glitches that might cause a false-detection.
@@
 To accelerate our analysis, we use a likelihood that explicitly marginalizes over coalescence time, phase at coalescence, and luminosity distance (Eq.~80 from~\citet{intro_to_gw_bayes}).
-While this marginalized likelihood reduces the run time without introducing errors to our evidence evaluation, it does not generates samples for the marginalized parameters.
-However, these parameter samples can be calculated as a post-processing step~\cite{intro_to_gw_bayes}.
 
-We set the priors $\pi(\parameters|\mathcal{H}_S)$ and $\pi(\parameters|\mathcal{H}_G)$ to be identical.
+We set the priors $\pi(\parameters|\mathcal{H}_S)$ and $\pi(\parameters|\mathcal{H}_G)$ to be identical which reflects our ignorance of the distribution of the population properties of signals and signal-like glitches.
 These priors restrict signals with mass parameters in the ranges presented in Table~\ref{tab:parameters}.
@@
 
-We take 31 neighboring off-source non-overlapping  4-second  segments of time-series data before the analysis data segment $d_i$ to generate the PSD.
-A Tukey window with a 0.2-second roll-off is applied to each data segment to suppress spectral leakage.
+To generate the PSD, we take 31 neighboring off-source non-overlapping  4-second  segments of time-series data before the analysis data segment $d_i$.
+To suppress spectral leakage, a Tukey window with a 0.2-second roll-off is applied to each data segment .
 After this the segments are fast-Fourier transformed and median-averaged to create a PSD~\cite{ligo_psd}.
@@
 
-Finally, we acquire data from from the gravitational-wave Open Science Center~\cite{GWOSC}.
+Finally, we acquire the foreground, background and data in which we inject simulated signals into, from from the gravitational-wave Open Science Center~\cite{GWOSC}.
 The data we use are the publicly accessible O2 strain data from the Hanford and Livingston detectors, recorded while the detectors are in ``Science Mode''.
@@
 \subsection{Assigning \pastro to candidate events}
-After the calculating the \bcr for the entire set of high-mass background and simulated triggers, we calculate probability distributions $p_b(\bcr)$ and $p_s(\bcr)$ for each 2-week time-frame of O2 data.
+After the calculating the \bcr for the entire set of high-mass background and simulated triggers, we calculate the background and simulated \bcr probability distributions for each 2-week time-frame of O2 data.
 These distributions are used to `tune' prior-odd $P^S$ and $P^G$ values as described in Appendix~\ref{apdx:tuning-prior-odds}.
@@
 \caption[BCR distribution example]{Histograms represent the survival function (1-CDF) from our high-mass selection of background triggers (gray) and simulated signals (blue) triggers obtained from \pycbc's search of data from $\text{August 13 - 21, 2017}$.
-Vertical lines mark the $\text{ln}\ \bcr$ of \IAS's GW170817A and \GWTC's GW170814.}\label{fig:bcrCdf}
+Vertical lines mark the $\text{ln}\ \bcr$ of \IAS's GW170817A and \GWTC's GW170814.
+\avi{Adjust to have same fonts as other plots} }\label{fig:bcrCdf}
 \end{figure}
@@
 Sections of the prior probability density functions used for analysis are displayed in green in one-dimensional marginal distributions plots.
-    Right: Posterior probability distributions for some inferred parameters.
+    Right: Posterior probability distributions for some inferred parameters. \avi{Right plot labels being cut off. Should i plot prior-samples on the right? }
     \label{fig:170222}}

### 2021-05-26 scripts/__init__.py
update plots

@@ -1,0 +1,26 @@
+# -*- coding: utf-8 -*-
+"""Module one liner
+
+This module does what....
+
+Example usage:
+
+"""
+import numpy as np
+import matplotlib.pyplot as plt
+
+
+def plot():
+    """Plots a scatter plot."""
+    sample_x = np.random.normal(4, 0.1, 500)
+    sample_y = np.random.normal(4, 0.1, 500)
+    fig, ax = plt.subplots()
+    ax.plot(sample_x, sample_y, '.')
+    fig.show()
+
+
+def main(): 
+    plot()
+
+if __name__ == "__main__":
+    main()

### 2021-05-26 Data/corner_data/download_data.sh
uopdate plots

@@ -1,0 +1,2 @@
+scp avi.vajpeyi@ldas-pcdev3.ligo.caltech.edu:/hdfs/user/avi.vajpeyi/out_O2_BCRs/chunk7/pe_outdir/out_foreground/result/bcr_O2_chunk7_foreground_data1_1171814476-971924_analysis_H1L1_dynesty_result.json data/corner_data/170222_result.json
+scp avi.vajpeyi@ldas-pcdev3.ligo.caltech.edu:/home/avi.vajpeyi/projects/bcr_pipeline/bcr_pipeline/priors/454ns.prior data/corner_data/454ns.prior

### 2021-05-26 make_plots.sh

@@ -1,0 +1,3 @@
+python scripts/plot_corners.py
+python scripts/make_template_plot.py
+python scripts/make_bcr_cdf.py

### 2021-05-26 scripts/__init__.py

@@ -1,26 +1,0 @@
-# -*- coding: utf-8 -*-
-"""Module one liner
-
-This module does what....
-
-Example usage:
-
-"""
-import numpy as np
-import matplotlib.pyplot as plt
-
-
-def plot():
-    """Plots a scatter plot."""
-    sample_x = np.random.normal(4, 0.1, 500)
-    sample_y = np.random.normal(4, 0.1, 500)
-    fig, ax = plt.subplots()
-    ax.plot(sample_x, sample_y, '.')
-    fig.show()
-
-
-def main(): 
-    plot()
-
-if __name__ == "__main__":
-    main()

### 2021-05-26 scripts/make_bcr_cdf.py

@@ -1,57 +1,32 @@
-import matplotlib.font_manager
-from bcr_pipeline.post_processing.bcr_plotting.main_analysis_plots import \
-    pack_plotting_data
+"""
+Script to plot CDFs (reweighted and original)
+"""
+import logging.config
+
+from bcr_pipeline.post_processing.bcr_plotting.main_analysis_plots import (
+    pack_plotting_data,
+)
 from bcr_pipeline.post_processing.bcr_plotting.make_ranking_stat_probability_plot import (
-    _add_rank_pdf)
+    _add_rank_pdf,
+)
 from matplotlib import pyplot as plt
-from matplotlib import rc
-from matplotlib import rcParams
 from matplotlib.lines import Line2D
-from matplotlib.ticker import (FormatStrFormatter)
+from matplotlib.ticker import FormatStrFormatter
+from settings import set_matplotlib_style_settings
 
-# matplotlib.font_manager.findfont("font.sans-serif", rebuild_if_missing=False)
-all_fonts = matplotlib.font_manager.findSystemFonts()
-print(f"Avail fonts: {all_fonts}")
+logging.config.dictConfig({'version': 1, 'disable_existing_loggers': True})
 
-font_path = "/Users/avaj0001/Library/Fonts/ScopeOn-Regular.ttf"
-# prop = matplotlib.font_manager.FontProperties(fname=font_path)
+set_matplotlib_style_settings()
 
-
-rc('text.latex', preamble=r'\usepackage{cmbright}')
-rcParams["font.size"] = 30
-rcParams["font.family"] = "sans-serif"
-# rcParams["font.sans-serif"] = ["/Users/avaj0001/Library/Fonts/ScopeOn-Regular.ttf"]
-rcParams["text.usetex"] = True
-rcParams['axes.labelsize'] = 30
-rcParams['axes.titlesize'] = 30
-rcParams['axes.labelpad'] = 10
-rcParams['axes.linewidth'] = 3
-rcParams['axes.edgecolor'] = 'black'
-rcParams['xtick.labelsize'] = 25
-rcParams['xtick.major.size'] = 10.0
-rcParams['xtick.minor.size'] = 5.0
-rcParams['ytick.labelsize'] = 25
-rcParams['ytick.major.size'] = 10.0
-rcParams['ytick.minor.size'] = 5.0
-plt.rcParams['xtick.direction'] = 'in'
-plt.rcParams['ytick.direction'] = 'in'
-plt.rcParams['xtick.minor.width'] = 1
[…]

### 2021-05-26 scripts/make_events_plot.py

@@ -1,49 +1,18 @@
+"""
+Script to plot known events (not used in paper but useful for presentations)
+"""
+import matplotlib.font_manager
 import matplotlib.pyplot as plt
 import matplotlib.ticker
-import numpy as np
 import pandas as pd
-from matplotlib import rcParams
 from matplotlib.patches import Patch
 from matplotlib.patches import Polygon
-import matplotlib.font_manager
-from matplotlib import rc
 
-# matplotlib.font_manager.findfont("font.sans-serif", rebuild_if_missing=False)
-all_fonts = matplotlib.font_manager.findSystemFonts()
-print(f"Avail fonts: {all_fonts}")
+from settings import set_matplotlib_style_settings, logger
 
-rc('text.latex', preamble=r'\usepackage{cmbright}')
+set_matplotlib_style_settings()
 
-rcParams["font.size"] = 34
-rcParams["font.family"] = "serif"
-rcParams["font.sans-serif"] = ["Computer Modern Sans"]
-rcParams["text.usetex"] = True
-rcParams['axes.labelsize'] = 60
-rcParams['axes.titlesize'] = 50
-rcParams['axes.labelpad'] = 10
-rcParams['axes.linewidth'] = 5
-rcParams['axes.edgecolor'] = 'black'
-rcParams['xtick.labelsize'] = 38
-rcParams['ytick.labelsize'] = 38
-rcParams['ytick.major.size'] = 20.0
-rcParams['ytick.minor.size'] = 10
-rcParams['xtick.major.size'] = 20.0
-rcParams['xtick.minor.size'] = 10
-rcParams['ytick.major.pad'] = 10
-rcParams['ytick.minor.pad'] = 10
-rcParams['xtick.major.pad'] = 10
-rcParams['xtick.minor.pad'] = 10
-
-plt.rcParams['xtick.minor.width'] = 5
-plt.rcParams['xtick.major.width'] = 5
-plt.rcParams['ytick.minor.width'] = 5
-plt.rcParams['ytick.major.width'] = 5
-plt.rcParams['xtick.direction'] = 'in'
-plt.rcParams['ytick.direction'] = 'in'
-plt.rcParams['xtick.top'] = True
-plt.rcParams['ytick.right'] = True
-
-COLS = {"LVK":"tab:purple", "IAS":"tab:pink", "LVK Candidates":"tab:orange"}
[…]

### 2021-05-26 scripts/make_template_plot.py

@@ -1,39 +1,20 @@
+"""
+Module to plot "template_bank.png"
+"""
 import numpy as np
 import pandas as pd
 from bilby.gw import conversion
 from matplotlib import pyplot as plt
-from matplotlib import rcParams
+from settings import set_matplotlib_style_settings
 from tqdm import tqdm
 
-rcParams["font.size"] = 30
-rcParams["font.family"] = "serif"
-rcParams["font.sans-serif"] = ["Computer Modern Sans"]
-rcParams["text.usetex"] = True
-rcParams['axes.labelsize'] = 30
-rcParams['axes.titlesize'] = 30
-rcParams['axes.labelpad'] = 10
-rcParams['axes.linewidth'] = 2.5
-rcParams['axes.edgecolor'] = 'black'
-rcParams['xtick.labelsize'] = 25
-rcParams['xtick.major.size'] = 10.0
-rcParams['xtick.minor.size'] = 5.0
-rcParams['ytick.labelsize'] = 25
-rcParams['ytick.major.size'] = 10.0
-rcParams['ytick.minor.size'] = 5.0
-plt.rcParams['xtick.direction'] = 'in'
-plt.rcParams['ytick.direction'] = 'in'
-plt.rcParams['xtick.minor.width'] = 1
-plt.rcParams['xtick.major.width'] = 3
-plt.rcParams['ytick.minor.width'] = 1
-plt.rcParams['ytick.major.width'] = 2.5
-plt.rcParams['xtick.top'] = True
-plt.rcParams['ytick.right'] = True
 
-BANK = "../data/template_bank.csv"
-INJECTION = "../data/chunk14/injection_triggers.csv"
-BACKGROUND = "../data/chunk14/background_triggers.csv"
-FOREGROUND = "../data/chunk14/foreground_triggers.csv"
-CATALOG = "../data/catalog.csv"
+
+BANK = "data/template_bank.csv"
+INJECTION = "data/chunk14/injection_triggers.csv"
+BACKGROUND = "data/chunk14/background_triggers.csv"
+FOREGROUND = "data/chunk14/foreground_triggers.csv"
+CATALOG = "data/catalog.csv"
 
 
 def get_m1m2_grid(m1_range, m2_range, filtering_criteria):
@@ -47,7 +28,6 @@ def get_m1m2_grid(m1_range, m2_range, filtering_criteria):
     :param filtering_criteria:
     :return:
     """
[…]

### 2021-05-26 scripts/plot_corners.py

@@ -1,90 +1,67 @@
+"""
+Script to plot "170222_prior_posterior.png" and "170222_source_posterior.png"
+"""
+
 import bilby
-from matplotlib import rcParams
+import numpy as np
+from settings import set_matplotlib_style_settings
 
-
-def set_matplotlib_style_settings():
-    major, minor = 7, 3
-    linewidth = 1.5
-    rcParams["font.size"] = 30
-    rcParams["font.family"] = "serif"
-    rcParams["font.sans-serif"] = ["Computer Modern Sans"]
-    rcParams["text.usetex"] = True
-    rcParams['axes.labelsize'] = 30
-    rcParams['axes.titlesize'] = 30
-    rcParams['axes.labelpad'] = 10
-    rcParams['axes.linewidth'] = linewidth
-    rcParams['axes.edgecolor'] = 'black'
-    rcParams['xtick.labelsize'] = 25
-    rcParams['ytick.labelsize'] = 25
-    rcParams['xtick.direction'] = 'in'
-    rcParams['ytick.direction'] = 'in'
-    rcParams['xtick.major.size'] = major
-    rcParams['xtick.minor.size'] = minor
-    rcParams['ytick.major.size'] = major
-    rcParams['ytick.minor.size'] = minor
-    rcParams['xtick.minor.width'] = linewidth
-    rcParams['xtick.major.width'] = linewidth
-    rcParams['ytick.minor.width'] = linewidth
-    rcParams['ytick.major.width'] = linewidth
-    rcParams['xtick.top'] = True
-    rcParams['ytick.right'] = True
-    rcParams['axes.grid'] = False
-    rcParams["axes.titlepad"] = 8
-
-
-PARAMS = dict(
-    chi_eff=dict(latex_label=r"$\chi_{eff}$", range=(-0.8, 0.8)),
-    chi_p=dict(latex_label=r"$\chi_{p}$", range=(0, 1)),
-    chi_1=dict(latex_label=r"$\chi_1$", range=(0, 1)),
-    cos_tilt_1=dict(latex_label=r"$\cos(t1)$", range=(-1, 1)),
-    cos_tilt_2=dict(latex_label=r"$\cos(t2)$", range=(-1, 1)),
-    cos_theta_12=dict(latex_label=r"$\cos \theta_{12}$", range=(-1, 1)),
[…]

### 2021-05-26 scripts/settings.py

@@ -1,0 +1,29 @@
+from matplotlib import rcParams
+
+
+def set_matplotlib_style_settings(major=7, minor=3, linewidth=1.5, grid=False):
+    rcParams["font.size"] = 30
+    rcParams["font.family"] = "serif"
+    rcParams["font.sans-serif"] = ["Computer Modern Sans"]
+    rcParams["text.usetex"] = True
+    rcParams["axes.labelsize"] = 30
+    rcParams["axes.titlesize"] = 30
+    rcParams["axes.labelpad"] = 10
+    rcParams["axes.linewidth"] = linewidth
+    rcParams["axes.edgecolor"] = "black"
+    rcParams["xtick.labelsize"] = 25
+    rcParams["ytick.labelsize"] = 25
+    rcParams["xtick.direction"] = "in"
+    rcParams["ytick.direction"] = "in"
+    rcParams["xtick.major.size"] = major
+    rcParams["xtick.minor.size"] = minor
+    rcParams["ytick.major.size"] = major
+    rcParams["ytick.minor.size"] = minor
+    rcParams["xtick.minor.width"] = linewidth
+    rcParams["xtick.major.width"] = linewidth
+    rcParams["ytick.minor.width"] = linewidth
+    rcParams["ytick.major.width"] = linewidth
+    rcParams["xtick.top"] = True
+    rcParams["ytick.right"] = True
+    rcParams["axes.grid"] = grid
+    rcParams["axes.titlepad"] = 8

### 2021-05-26 scripts/plot_corners.py
add priors

@@ -33,9 +33,14 @@ PARAMS = dict(
 
 
 def plot_result_corner(r, parameters, fname, prior=None):
+
+    plt_range = [PARAMS[p]["range"] for p in parameters]
+    if prior:
+        plt_range = [(prior[p].minimum, prior[p].maximum) for p in parameters]
+
     fig = r.plot_corner(
         parameters=parameters, priors=prior,
-        range=[PARAMS[p]["range"] for p in parameters],
+        range=plt_range,
         labels=[PARAMS[p]["latex_label"] for p in parameters],
         color="tab:orange", label_kwargs=dict(fontsize=35, labelpad=12), labelpad=0.05,
         title_kwargs=dict(fontsize=25, pad=12), save=False

### 2021-05-26 main.tex

@@
 \caption[BCR distribution example]{Histograms represent the survival function (1-CDF) from our high-mass selection of background triggers (gray) and simulated signals (blue) triggers obtained from \pycbc's search of data from $\text{August 13 - 21, 2017}$.
-Vertical lines mark the $\text{ln}\ \bcr$ of \IAS's GW170817A and \GWTC's GW170814.
-\avi{Adjust to have same fonts as other plots} }\label{fig:bcrCdf}
+Vertical lines mark the $\text{ln}\ \bcr$ of \IAS's GW170817A and \GWTC's GW170814.}\label{fig:bcrCdf}
 \end{figure}
@@
     \end{subfigure}
-    \caption{Posterior distributions for some parameters of 170222, comparing posteriors in orange and prior probability density functions to the one-dimensional marginal distributions in green. 
+    \caption{Posterior distributions for some parameters of 170222. 
     Left: Posterior probability distributions for 4 of the 11 search parameters.
 Sections of the prior probability density functions used for analysis are displayed in green in one-dimensional marginal distributions plots.
-    Right: Posterior probability distributions for some inferred parameters. \avi{Right plot labels being cut off. Should i plot prior-samples on the right? }
+    Right: Posterior probability distributions for some inferred parameters. \avi{Should i plot prior-samples on the right? }
     \label{fig:170222}}

### 2021-05-26 scripts/plot_corners.py
update corner

@@ -14,6 +14,7 @@ set_matplotlib_style_settings()
 PARAMS = dict(
     chi_eff=dict(latex_label=r"$\mathbf{\chi_{eff}}$", range=(-0.8, 0.8)),
     chi_p=dict(latex_label=r"$\mathbf{\chi_{p}}$", range=(0, 1)),
+    a_1=dict(latex_label=r"$\mathbf{a_1}$", range=(0, 1)),
     chi_1=dict(latex_label=r"$\mathbf{\chi_1}$", range=(-1, 1)),
     cos_tilt_1=dict(latex_label=r"$\mathbf{\cos(t1)}$", range=(-1, 1)),
     cos_tilt_2=dict(latex_label=r"$\mathbf{\cos(t2)}$", range=(-1, 1)),
@@ -61,7 +62,7 @@ def main():
     )
     plot_result_corner(
         r,
-        parameters=["chirp_mass", "mass_ratio", "chi_1", "luminosity_distance"],
+        parameters=["chirp_mass", "mass_ratio", "a_1", "luminosity_distance"],
         fname="images/170222_prior_posterior.png",
         prior=prior
 

### 2021-05-28 main.tex
Updates from Overleaf
add todos

@@
 \newcommand{\bcr}{\mathcmd{\rho_\text{BCR}}}
+\newcommand{\bcrodds}{\mathcmd{\mathcal{O}_{\mathrm{BCR}}}}
 \newcommand{\pycbcstat}{\mathcmd{\rho_\text{PC}}}
@@
 
-\title{A search for high-mass black holes in data from the second LIGO observing run using a Bayesian ranking-statistic}
+\title{A Bayesian ranking-statistic for binary black holes mergers in the second LIGO observing run}
 
@@
 Ground-based gravitational-wave detectors are in principle sensitive to such mergers and have found one $142^{+28}_{-16}\ \msun$ intermediate-mass black hole.
-In reality, ground-based detectors are plagued with short-duration instrumental transients that mimic the gravitational-wave signals from mergers capable of producing intermediate-mass black holes, making their detection difficult.
-Here we demonstrate a ranking statistic utilizing Bayesian inference to detect high-mass binary black hole mergers (with a total mass $>55$~\msun).
-We apply this technique to the high-mass triggers during LIGO's second observing run to search for previously unresolved gravitational-wave signals from high-mass binary black holes.
+In reality, ground-based detector data contain numerous short-duration instrumental transients that mimic the gravitational-wave signals from mergers capable of producing intermediate-mass black holes, making intermediate-mass merger detection challenging.
+Here we demonstrate a ranking statistic utilizing Bayesian inference to detect binary black hole mergers with a total mass $>55$~\msun.
+\avi{Say why it improves on prev techniques}.
+We apply this technique to candidate events with total masses $>55$~\msun during LIGO's second observing run to search for previously unresolved gravitational-wave signals from this heavy category of binary black holes.
 Our analysis does not discover new intermediate-mass black holes.
-However, we find support for some stellar mass binary black holes unreported in GWTC-1.
+However, we find support for some stellar-mass binary black holes unreported in GWTC-1.
 \end{abstract}
@@
 Additionally, some candidates discovered with these techniques can be attributed to sources without intermediate-mass black holes (e.g.
-clusters of stellar-mass black holes~\cite{Ridolfi:2016:MNRAS, Freire:2017:MNRAS}, anisotropic emission from neutron stars~\cite{Israel:2017:MNRAS, RodriguezCastillo:2020:ApJ}), while others have high uncertainties due to the observational techniques utilized~\cite{Greene:2020:ARA&A}.
+clusters of stellar-mass black holes~\cite{Ridolfi:2016:MNRAS, Freire:2017:MNRAS}, anisotropic emission from neutron stars~\cite{Israel:2017:MNRAS, RodriguezCastillo:2020:ApJ}), while others have high uncertainties intrinsic to the observational techniques~\cite{Greene:2020:ARA&A}.
 
@@
 the $142^{+28}_{-16}\ \msun$ remnant observed from the gravitational wave event GW190521~\cite{Abbott:2020:PhRvL}).
-Ground-based gravitational wave detectors can probe the lower-end $10^{2} - 10^{3}\ \msun$ of the intermediate mass range.
- As a binary's total mass $\text{M}_{T}$ is associated with its gravitational-wave merger frequency, $f\sim \text{M}_{T}^{-1}$, systems with large $\text{M}_{T}$ have very low merger frequencies $f < 100\ \text{Hz}$.
-Hence, ground based gravitational wave detectors ($\sim 10^1 - 10^3\ \text{Hz}$) are sensitive to the last milliseconds of merging systems with $100 \msun < \text{M}_{T} < 400 \msun$~\cite{LIGOScientificCollaboration:2015:CQGra, Martynov:2016:PhRvD, Moore_2014}, while space-based detectors ($\sim 10^{-2} - 10^1\ \text{Hz}$) can study the full signals of merging systems with $10^4 \msun < \text{M}_{T} < 10^7 \msun$~\cite{ Moore_2014, Lu:2019:PhRvD}.
-
-Because of the short-duration of intermediate-mass gravitational-wave signals in ground-based detector data steams, handling data quality is critical to their detection.
-The low-frequency ranges of ground-based observatories are plagued with non-stationary terrestrial artifacts, called \textit{glitches}~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
-Some glitches, similar to signals from high total mass mergers, last for a fraction of a second, making them difficult to distinguish from the signals.
-These glitches that mimic astrophysical signals can severely decrease the confidence in detection of true gravitational-waves from high total mass mergers~\cite{pycbc_short_duration_transients}.
+As a binary's total mass $\text{M}_{T}$ is associated with its gravitational-wave merger frequency, $f\sim \text{M}_{T}^{-1}$,  ground based gravitational wave detectors ($f\sim 10^1 - 10^3\ \text{Hz}$) are sensitive to the last milliseconds of merging systems with $100 \msun < \text{M}_{T} < 400 \msun$~\cite{LIGOScientificCollaboration:2015:CQGra, Martynov:2016:PhRvD, Moore_2014}, while space-based detectors ($f \sim 10^{-2} - 10^1\ \text{Hz}$) can study the full signals of merging systems with $10^4 \msun < \text{M}_{T} < 10^7 \msun$~\cite{ Moore_2014, Lu:2019:PhRvD}.
+Because of the short-duration of intermediate-mass gravitational-wave signals in ground-based detector data streams, handling data quality is critical to their detection.
+The low-frequency ranges of ground-based observatories data-streams have numerous non-stationary terrestrial artifacts, called \textit{glitches}~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
+Like signals from intermediate mass mergers, some glitches last for a fraction of a second, making them difficult to distinguish from the signals.
+These glitches that mimic astrophysical signals can severely decrease the confidence in detection of true gravitational-waves from black hole mergers with total masses $>55$~\msun ~\cite{pycbc_short_duration_transients}.
 
 Although a significant fraction of the glitches can be removed by testing them for coherence amongst various ground based detectors and performing matched-filtering, these methods are insufficient to remove all the glitches~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
-One method to account for more glitches while searching for high total mass CBC gravitational-waves is by utilizing a Bayesian odds~\cite{bci, kanner2016leveraging, BCR1, BCR2, bcr_gw151216, bayesian_odds}.
-In this paper, we utilize a Bayesian method, called the Bayesian Coherence Odds-Ratio \bcr~\cite{BCR1}, to rank the candidate gravitational-wave signals from high-mass compact binary coalescences (systems with total masses in the range of $55-500\ \msun$) in the detector data recorded during O2.
-The \bcr used in this study is a bootstrap-Bayesian odds computed using Bayesian evidences that describe the explicit probability of data under the hypothesis that the data contains coherent signals vs incoherent glitches, and empirically calculated prior-odds that describe how likely each hypotheses is.
-\rs{Need to add another couple of sentences describing what is unique about this work.
-For instance, we study both foreground \textit{and} background events (which is the first time anyone's done a large-scale Bayesian analysis on background data).
-Suggest using this format: ``We highlight a number of innovations unique to this work.
-First...''} The high-mass candidate \bcr values are then used to calculate the probability that the candidate is of astrophysical origins, \pastrobcr.
+One method to account for more glitches while searching for CBC gravitational-waves is to rely on a Bayesian odds~\cite{bci, kanner2016leveraging, BCR1, BCR2, bcr_gw151216, bayesian_odds}.
+In this paper, we rank O2's candidate gravitational-wave signals from $55-500\ \msun$ total mass systems using a Bayesian method called the Bayesian Coherence Odds-Ratio \bcr~\cite{BCR1}.
+\avi{Should explain: whats the advantage of this?
+Why is it useful for triggers with $M_T>55\msun$?} The \bcr used in this study is a bootstrap-Bayesian odds calculated using the probability of data under the hypothesis that the data contains coherent signals vs.
+incoherent glitches and empirically calculated prior-odds that describe how likely each hypothesis is.
+After computing the candidate \bcr values, we calculate the candidate's probability of astrophysical origins, \pastrobcr.
 Finally, if the candidate has a \pastro reported by the the LIGO-Virgo-KAGRA (LVK) collaboration in \GWTC~\cite{GWTC1}, the \pycbc-team~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6, pycbc_single_det, pycbc_ogc_2}, by the Institute of Advanced study's team (\IAS)~\cite{IAS0, IAS1, IAS2}, or by \citet{bayesian_odds}, we compare their \pastro with the \pastrobcr.
+We highlight several innovations unique to this work.
+First, we use our Bayesian framework to analyze all candidate signals and background triggers (incoherent signal-free data) with total masses above $> 55 \msun$ in O2.
+Second, we empirically tune prior-odds for finding a signal or a glitch in O2 using \bcr distributions for background triggers and simulated signals.
+Finally,  we use the tuned-\bcr background distribution to compute how significant candidate signals are from the background.
 
-We find that (a) high-mass events reported in the \GWTC, including GW170729 (the heaviest event in \GWTC) are very statistically significant $\pastrobcr>0.9$; (b) three out of the eight \IAS events and candidates have $\pastrobcr>0.5$, corroborating \IAS's detection claims for those events (GW170304, GW170727, GW170817A), and that (c) our ranking statistic does not identify any new intermediate-mass black holes, but does identify an unreported marginal stellar-mass binary black hole candidate, 170222 with $\pastrobcr\sim0.5$.
+We find that (a) high-mass events reported in the \GWTC, including GW170729 (the heaviest event in \GWTC) are very statistically significant $\pastrobcr>0.9$; (b) three out of the eight \IAS events and candidates have $\pastrobcr>0.5$, corroborating \IAS's detection claims for those events (GW170304, GW170727, GW170817A); and that (c) our ranking statistic does not identify any new intermediate-mass black holes, but does identify an unreported marginal stellar-mass binary black hole candidate, 170222 with $\pastrobcr\sim0.5$ \avi{Need to doublecheck that this wasnt in the PyCBC sub-threshold paper}.
 
@@
 
-The standard framework to identify CBC gravitational-wave signals in data is by quantifying the significance of candidates with null-hypothesis significance testing~\cite{GWTC1, GWTC2}.
+The standard framework to identify CBC gravitational-wave signals in data is to quantify the significance of candidates with null-hypothesis significance testing~\cite{GWTC1, GWTC2}.
 In this framework, the candidates' ranking statistic is compared against a background distribution in a frequentist approach.
@@
 \pycbc~\cite{pycbc_og4}, \spiir~\cite{spiir} and \gstlal~\cite{sachdev2019gstlal}, and the coherent burst search \cwb~\cite{cwb} used by LVK to search for signals in gravitational-wave data all use ranking statistics in such a manner~\cite{GWTC1}.
-Both \pycbc and \gstlal's ranking statistic incorporate information of the relative likelihood that the data contains a coherent signal versus just noise.
+\avi{Holdup: isnt GSTLAL's method a bootstrapped-Bayesian method?} Both \pycbc and \gstlal's ranking statistic incorporate information of the relative likelihood that the data contains a coherent signal versus just noise.
 In contrast, \cwb's ranking statistic uses the information of coherent energy present in the network of detectors~\cite{GWTC1}.
 
+\avi{I discuss the benefits of the BCR here...}
 Bayesian inference offers an alternative means to rank the significance of candidate events by computing the odds that the data contain a transient gravitational-wave signal vs.
@@
 
-Bayes theorem states that the posterior probability distribution $p(\parameters|d,\mathcal{H})$ for data $d$ and a vector of parameters \parameters that describe a model which quantifies a hypothesis $\mathcal{H}$, is given by
+Bayes' theorem states that the posterior probability distribution $p(\parameters|d,\mathcal{H})$ for data $d$ and a vector of parameters \parameters that describe a model which quantifies a hypothesis $\mathcal{H}$, is given by
 \begin{equation}
@@
 \end{equation} is the likelihood after marginalizing over the parameters \parameters.
-To compare two hypotheses $\mathcal{H}_A$ and $\mathcal{H}_B$ with the Bayes theorem one can calculate an odds-ratio
+To compare two hypotheses $\mathcal{H}_A$ and $\mathcal{H}_B$ through Bayes' theorem one can calculate an odds-ratio
 \begin{equation}
@@
 
-The \bcr is a Bayesian odds-ratio like the above, of a coherent signal hypotheses $\mathcal{H}_S$ and an incoherent instrumental feature hypothesis $\mathcal{H}_I$ (the null-hypotheses) for a network of $D$ detectors.
+The \bcrodds quantity is a Bayesian odds-ratio like the above, of a coherent signal hypotheses $\mathcal{H}_S$ and an incoherent instrumental feature hypothesis $\mathcal{H}_I$ (the null-hypotheses) for a network of $D$ detectors.
 $\mathcal{H_I}$ states that each detector $i$ has either pure stationary Gaussian noise $\mathcal{H}_N$ or Gaussian noise and an incoherent noise transient (glitch) $\mathcal{H}_G$.
-Taking $Z^S$, $Z^G_i$ and $Z^N_i$ as the Bayesian evidences (defined in Appendix~\ref{sec:bayesianEvidEval}) for $\mathcal{H}_S$, $\mathcal{H}_N$, and $\mathcal{H}_G$, the \bcr is given by
+Taking $Z^S$, $Z^G_i$ and $Z^N_i$ as the Bayesian evidences (defined in Appendix~\ref{sec:bayesianEvidEval}) for $\mathcal{H}_S$, $\mathcal{H}_N$, and $\mathcal{H}_G$, \bcrodds is given by
 \begin{equation}
 \label{eq:bcr}
-\mathcal{O}_{\mathrm{BCR}} = \frac{P^S Z^S}{\prod\limits^D_{i=1} \ [P^G Z^G_i + (1-P^G)Z^N_i]}\ ,
+\bcrodds = \frac{\pi^S Z^S}{\prod\limits^D_{i=1} \ [\pi^G Z^G_i + (1-\pi^G)Z^N_i]}\ ,
 \end{equation}
 
-where $P^S$ and $P^G$ are the prior-odds of obtaining a signal or a glitch from a stretch of data. The prior-odds can be defined more explicitly as 
+where $\pi^S$ and $\pi^G$ are the prior-odds of obtaining a signal or a glitch from a stretch of data. The prior-odds can be defined more explicitly as 
 \begin{itemize}
-    \item $P^S=P(\mathcal{H}_S)/P(\mathcal{H}_I)$, the prior-odds for obtaining a coherent signal versus an incoherent instrumental feature.
-    \item $P^G=P(\mathcal{H}_G| \mathcal{H}_I)$, the probability of obtaining a glitch assuming there is an incoherent instrumental feature.
+    \item $\pi^S=\pi(\mathcal{H}_S)/\pi(\mathcal{H}_I)$, the prior-odds for obtaining a coherent signal versus an incoherent instrumental feature.
+    \item $\pi^G=\pi(\mathcal{H}_G| \mathcal{H}_I)$, the probability of obtaining a glitch assuming there is an incoherent instrumental feature.
 \end{itemize}
 
+When $\mathcal{H}_S$ and $\mathcal{H}_I$ are precisely described and the prior-odds represent our true beliefs, the \bcrodds is a Bayesian odds-ratio.
+As an odds-ratio, the \bcrodds is the optimal discriminator between coherent signals and incoherent instrumental features.
+However, as the priors-odds are unknown, we \textit{tune} values for prior-odds, $\hat{\pi}^S$ and $\hat{\pi}^G$, to estimate \bcrodds with a ranking statistic, \bcr, given by
 \begin{equation}
 \label{eq:bcr}
-\bcr = \frac{\hat{\pi}^S Z^S}{\prod\limits^D_{i=1} \ [\hat{\pi}^G Z^G_i + (1-\hat{\pi}^G)Z^N_i]}\ ,
+\bcr = \frac{\hat{\pi}^S Z^S}{\prod\limits^D_{i=1} \ [\hat{\pi}^G Z^G_i + (1-\hat{\pi}^G)Z^N_i]}\ .
 \end{equation}
 
-\avi{Ranking statistic \bcr is like an estimator of what $\mathcal{O}_{\mathrm{BCR}}$ is}
-
-When $\mathcal{H}_S$ and $\mathcal{H}_I$ are precisely described and the correct prior-odds are known, the \bcr is a Bayesian odds-ratio.
-As an odds-ratio, the \bcr is the optimal discriminator between coherent signals and incoherent instrumental features.
-However, as the priors-odds are unknown, it is invalid to use the \bcr as an odds-ratio to make an informed decision about whether a candidate is from an astrophysical or terrestrial source.
+In the limit where the estimated prior-odds equal the true prior-odds, $\bcr\to\bcrodds$.
+However, as we are uncertain what the true prior-odds are, it is invalid to use the \bcr as an odds-ratio to make an informed decision about whether a candidate is from an astrophysical or terrestrial source.
 Instead of interpreting the \bcr as a Bayesian odds-ratio, it can be used as a ranking statistic.
@@
 
-When using the \bcr as a detection statistic, the physical interpretation of the prior-odds is lost.
-Hence, the prior-odds are empirically tuned to maximize the separation between the \bcr distribution of the background (expected to favor the $\mathcal{H}_I$ hypothesis) and the \bcr distribution of artificially manufactured simulated signals (expected to favor the $\mathcal{H}_S$ hypothesis).
+When using the \bcr as a detection statistic, the prior-odds are empirically tuned to maximize the separation between the \bcr distribution of the background (expected to favor the $\mathcal{H}_I$ hypothesis) and the \bcr distribution of artificially manufactured simulated signals (expected to favor the $\mathcal{H}_S$ hypothesis).
 Increasing the separation between the two distributions can improve ability of the \bcr to discriminate candidate events as coherent signals or incoherent instrumental features.
-The tuning process is described in detail in Appendix~\ref{sec:tuning-prior-odds}.
+The tuning process is further described in Appendix~\ref{apdx:tuning-prior-odds}.
 
 \subsection{Estimation of astrophysical signal probability}
-Candidate \bcr-values are either statistically insignificant compared to the background \bcr distribution, implying the candidate is more probable to be an incoherent instrumental feature (the $\mathcal{H}_I$ null-hypothesis), or statistically significant to the background distribution, indicating the possible presence of an astrophysical signal (the $\mathcal{H}_S$ hypothesis).
-A false alarm probability with trial factors, \fap, for the candidate \bcr-value can quantify the significance.
+Candidate \bcr-values are either statistically insignificant compared to the background \bcr distribution, implying the candidate is more probable to be an incoherent instrumental feature (the $\mathcal{H}_I$ null-hypothesis), or statistically significant relative to the background distribution, indicating the possible presence of an astrophysical signal (the $\mathcal{H}_S$ hypothesis).
+A false alarm probability with trial factors \avi{(need to define a trial factor)}, \fap, for the candidate \bcr-value can quantify the significance.
 The \fap is the probability that a candidate originating from a non-astrophysical source can be falsely identified as a signal.
@@
 \end{equation}
-The false alarm probability with trials \fap that the \bcr measurement occurs at least once for $N$ trials $(N > 0)$, where $N$ is the number of candidate triggers is
+The false alarm probability with trials \fap that the \bcr measurement occurs at least once for $N$ trials $(N > 0)$, where $N$ is the number of candidate signals, is \avi{(This is very convoluted)}
 \begin{equation}
@@
 
-\rs{Rory: Suggest a bit more preable here, something like ``To build a ranking statistic from $\rho$ we need to compute its distribution for foreground and background events.
-The number of background events in a typical search is very large, however we can manage the number of background triggers by focusing on a specific mass range.
-Background triggers are generated by search pipelines...}
-
-The LIGO Scientific collaboration operates several search pipelines that scan for gravitational-waves from compact binary mergers such as \gstlal~\cite{sachdev2019gstlal}, \mbta~\cite{MBTA}, \spiir~\cite{spiir} and \pycbc~\cite{pycbc_og4}.
+To rank candidate event \bcr-values we need to compute a background \bcr distribution.
+We can obtain the background data needed from the LIGO Scientific collaboration's search pipelines that scan for gravitational-waves from compact binary mergers such as \gstlal~\cite{sachdev2019gstlal}, \mbta~\cite{MBTA}, \spiir~\cite{spiir} and \pycbc~\cite{pycbc_og4}.
 The output of \pycbc's search is a list of times and their corresponding \pycbc ranking statistic \pycbcstat values.
-The \pycbcstat ranking-statistic is akin to the matched-filter signal-to-noise ratio \snr.
-However, unlike \snr, \pycbcstat includes candidate signal's intrinsic and extrinsic properties and other information that feeds into determining if the signal can have astrophysical origins~\cite{pycbc_og6}.
 Whenever a local maximum of $\pycbcstat > \snr_\text{T}$, where $\snr_\text{T}$ is some predetermined threshold value, the \pycbc search pipeline produces a single-detector \textit{trigger} associated with the detector and time $t_c$ where the apparent signal in the data has its merger~\cite{pycbc_og6}.
-
 \pycbc produces three categories of triggers:
@@
 
-% \rs{Rory: suggest cutting most or all of this paragraph.
-We don't need to explain how pycbc works in detail.
-A reference to the relevant paper is sufficient.
-The key point is that a pipeline produces them for us} When \pycbc observes a trigger between detectors with coincident parameters and a time of arrival difference less than the gravitational-wave travel time between detectors, the trigger is labeled a \textit{candidate event trigger}, a trigger that may be from astrophysical origins~\cite{pycbc_og1}.
-To test the pipeline's sensitivity \pycbc also conducts searches for \textit{simulated triggers}, artificial triggers manufactured by injecting signals into the detector data.
-Finally, to quantify the statistical significance of candidate triggers, \pycbc artificially constructs \textit{background triggers} to compare against the candidate events.
-These background triggers are coherent signal-free events, constructed by applying relative offsets, or time-slides, between the data of different detectors~\cite{pycbc_og6}.
-The background trigger's \pycbcstat distribution is used to calculate the candidate trigger's significance,  using null-hypothesis significance testing, under the assumption that all candidate event triggers are due to noise.
+After obtaining these triggers from \pycbc, we can calculate the trigger's \bcr-values and use them to measure candidate triggers' statistical significance.
+The \bcr can be a powerful ranking statistic as it incorporates information of not only all possible binary black hole systems that might have merged to produce the trigger but also the various incoherent glitches that might cause a false-detection~\cite{BCR1}.
 
-Our work demonstrates that the \bcr can be used measure candidate triggers' statistical significance.
-The \bcr can be a powerful ranking statistic as it incorporates information of not only all possible binary black hole systems that might have merged to produce the trigger but also the various incoherent glitches that might cause a false-detection.
+\avi{Should I mention that we need \pycbc  as a pre-selection step to computing? }
 
@@
 Finally, to test the search's sensitivity, \pycbc produced and searched for thousands of simulated signals.
+\avi{Do i need to contextualize this choice more, ie talk about what would happen if I chose a narrower range?}
 
-For our study, we filter the \pycbc background, simulated and candidate triggers to include only high-mass triggers with masses in the ranges of the parameters presented in Table~\ref{tab:parameters}.
+For our study, we filter the \pycbc background, simulated and candidate triggers to include only triggers in the ranges of the parameters presented in Table~\ref{tab:parameters}.
+Filtering triggers to this region focuses our analysis to binary black hole mergers with total masses above $> 55 \msun$.
+This corresponds to binary systems with signal durations $<454 \ \text{ms}$, signals which may be mistaken for short-duration glitches.
 A plot of the \pycbc triggers from one time-frame, during April 23 - May 8, 2017, is presented in Fig.~\ref{fig:templateBank}.
-This figure also depicts the gravitational-wave templates used during the search through this time-frame of data.
+This figure also depicts the gravitational-wave templates used by \pycbc's search through this time-frame of data.
 
@@
 
-\caption[BBH parameters correspond to duration $<454\ \text{ms}$]{\label{tab:parameters}High-mass parameter space (parameters correspond to signals with durations $<454 \ \text{ms}$). }
+\caption[BBH parameters correspond to duration $<454\ \text{ms}$]{\label{tab:parameters}Trigger-selection parameter space (parameters correspond to signals with durations $<454 \ \text{ms}$). }
 \centering
@@
 % 1178294418, May 08, 2017, 16:00 UTC
-\caption[High-mass BCR search space.]{The template bank (pink) used by \pycbc to search a section of O2 data from $\text{April 23 - May 8, 2017}$.
-Our search is constrained to the high-mass parameter space enclosed by the dashed line.
+\caption[ BCR search space.]{The template bank (pink) used by \pycbc to search a section of O2 data from $\text{April 23 - May 8, 2017}$.
+Our search is constrained to the parameter space enclosed by the dashed line.
 The candidate, background and simulated triggers detected in this region of the parameter space during this period are plotted in orange, gray and blue respectively.}\label{fig:templateBank}
@@
 The waveform template we utilize is \imrphenomp, a phenomenological waveform template constructed in the frequency domain that models the in-spiral, merger, and ring-down (IMR) of a compact binary coalescence~\citep{khan2016frequency}.
-Although there exist gravitational-wave templates such as \seob~\cite{seobnrv4phm} which incorporate more physics, such as information on higher-order modes, we use \imrphenomp as it is computationally inexpensive compared to others.
+Although there exist gravitational-wave templates such as IMRPhenomPv3HM, NRSur7dq4, \seob~\cite{seobnrv4phm} (and others) which incorporate more physics, such as information on higher-order modes, we use \imrphenomp as it is computationally inexpensive compared to others.
 
@@
 \subsection{Assigning \pastro to candidate events}
-After the calculating the \bcr for the entire set of high-mass background and simulated triggers, we calculate the background and simulated \bcr probability distributions for each 2-week time-frame of O2 data.
-These distributions are used to `tune' prior-odd $P^S$ and $P^G$ values as described in Appendix~\ref{apdx:tuning-prior-odds}.
+After calculating the \bcr for the entire set of background and simulated triggers, we calculate the background and simulated \bcr probability distributions for each 2-week time-frame of O2 data.
+These distributions are used to `tune' prior-odd $\hat{\pi}^S$ and $\hat{\pi}^G$ values as described in Appendix~\ref{apdx:tuning-prior-odds}.
 
-Using the tuned prior odds the \bcr for the candidate events can be calculated.
+Using the tuned prior-odds the \bcr for the candidate events can be calculated.
 Fig.~\ref{fig:bcrCdf} shows the \bcr distributions for the background triggers, simulated triggers and candidate events.
@@
 {\centering \includegraphics[width=0.85\linewidth]{images/reweighted_bcr_cdf_smaller_legend.png} }
-\caption[BCR distribution example]{Histograms represent the survival function (1-CDF) from our high-mass selection of background triggers (gray) and simulated signals (blue) triggers obtained from \pycbc's search of data from $\text{August 13 - 21, 2017}$.
+\caption[BCR distribution example]{Histograms represent the survival function (1-CDF) from our selection of background triggers (gray) and simulated signals (blue) triggers obtained from \pycbc's search of data from $\text{August 13 - 21, 2017}$.
 Vertical lines mark the $\text{ln}\ \bcr$ of \IAS's GW170817A and \GWTC's GW170814.}\label{fig:bcrCdf}
@@
 Although the various pipeline \pastro are not mathematically equivalent, by comparing pipeline \pastro values for a given candidate, we can compare how significant each pipeline deems various candidates.
-The $P^S$ and $P^G$ values utilized for each time-frame are reported in Appendix~\ref{apdx:alphabeta}.
+The $\hat{\pi}^S$ and $\hat{\pi}^G$ values utilized for each time-frame are reported in Appendix~\ref{apdx:alphabeta}.
 
@@
 \subsection{IAS Events}
-Our analysis of the high-mass IAS events and candidates in O2 has resulted in three events with disfavored $\pastrobcr<0.5$ (GWC170402, GW170403, GW170425), and four events and one candidate with $\pastrobcr\geq0.5$ (GW170121, 170302, GW170304, GW170727, GW170817A).
+Our analysis of the IAS events and candidates with $M_T>55\ \msun$ in O2 has resulted in three events with disfavored $\pastrobcr<0.5$ (GWC170402, GW170403, GW170425), and four events and one candidate with $\pastrobcr\geq0.5$ (GW170121, 170302, GW170304, GW170727, GW170817A).
 While GW170727 and GW170817A's \pastrobcr are similar to the \pastro reported from IAS (the differences between the \pastro from \bcr and IAS is $|\Delta \pastro|<0.1$), the remaining candidates have opposing \pastro values (with $|\Delta \pastro| > 0.15$).
@@
 GWC170402, detected by \citet{IAS2}, is reported to originate from a binary with non-zero eccentricity~\cite{IAS2}.
-Hence, we might have received a low \pastrobcr due to our usage of \imrphenomp, a waveform that does not account for eccentricity.
+Hence, we might have computed a low \pastrobcr due to our usage of \imrphenomp, a waveform that does not account for eccentricity.
 Additionally, the search conducted by \citet{IAS2} was a single-detector search.
@@
 Until 2016, a majority of intermediate-mass black hole candidates were from electromagnetic observations.
-The dawn of gravitational waves astronomy has provided a new lens to identify and study these massive objects -- from the mergers of heavy black holes' gravitational wave emission.
+The dawn of gravitational wave astronomy has provided a new lens to identify and study these massive objects -- from the mergers of heavy black holes' gravitational wave emission.
 In the future, space-based gravitational wave detectors will uncover black holes in the upper end of the intermediate-mass range.
@@
 
-In our study, we analyze high-mass candidates detected by \pycbc, the high-mass binary black hole events in O2 reported in \GWTC~\cite{GWTC1} and by the \IAS-team~\cite{IAS1, IAS2}.
-Using \pastrobcr, we find that the high-mass \GWTC events have high probabilities of originating from an astrophysical source.
+In our study, we analyze O2 binary-black hole events and candidates with $M_T > 55 \msun$ reported by the \pycbc search~\cite{pycbc_ogc_2}, the \IAS-team~\cite{IAS1, IAS2} and those reported in \GWTC~\cite{GWTC1}.
+Using \pastrobcr, we find that the \GWTC events have high probabilities of originating from an astrophysical source.
 We also find that some of the \GWTC marginal triggers that have corroborated terrestrial sources (for example, candidate 170412) have low \pastrobcr, indicating this method's ability to discriminate between terrestrial artifacts and astrophysical signals.
-Our analysis of the high-mass \IAS events demonstrates that GW170121, GW170727, and GW170817A are likely to originate from astrophysical sources, while GWC170402, GW170402, and GW170425  are not.
+Our analysis of the \IAS events demonstrates that GW170121, GW170727, and GW170817A are likely to originate from astrophysical sources, while GWC170402, GW170402, and GW170425  are not.
 Finally, we do not identify any new gravitational-wave events, but we find a new marginal binary-black hole merger candidate, 170222.
 
-Although our analysis targets high-mass triggers, this method can be extended to include the entire range of LIGO-detectable gravitational-wave sources.
+Although our analysis targets triggers with $M_T > 55 \msun$, this method can be extended to include the entire range of LIGO-detectable gravitational-wave sources.
 Additionally, to further improve the method's infrastructure, we can use more robust gravitational-wave templates (such as templates that incorporate higher-order modes and orbital precession) and sophisticated glitch models.
@@
 \subsection{Incoherent Glitch Model}
-Finally, as glitches are challenging to model and poorly understood, we follow \citet{bci} and utilise a surrogate model for glitches: the glitches are modeled using gravitational-wave templates  \template with uncorrelated  parameters amongst the different detectors such that  $\parameters_i \neq \parameters_j$ for two detectors $i$ and $j$~\cite{bci}.
-Modelling glitches with \template captures the worst case scenario: when glitches are identical to gravitational-wave signals (excluding coherent signals).
+Finally, as glitches are challenging to model and poorly understood, we follow \citet{bci} and utilize a surrogate model for glitches: the glitches are modeled using gravitational-wave templates  \template with uncorrelated  parameters amongst the different detectors such that  $\parameters_i \neq \parameters_j$ for two detectors $i$ and $j$~\cite{bci}.
+Modeling glitches with \template captures the worst case scenario: when glitches are identical to gravitational-wave signals (excluding coherent signals).
 Thus, we can write $Z^G_i$ as
@@
 Ideally, these distributions representing two unique populations should be distinctly separate and have no overlap in their \bcr values.
-The prior odds parameters $P^S$ and $P^G$ from Eq.~\ref{eq:bcr} help separate the two distributions.
-Altering $P^S$ translates the \bcr probability distributions while adjusting $P^G$ spreads the distributions.
-Although Bayesian hyper-parameter estimation can determine the optimal values for $P^S$ and $P^G$, an easier approach is to adjust the parameters for each data chunk's \bcr distribution.
-In this study, we tune $P^S$ and $P^G$ to maximally separate the \bcr distributions for the background and simulated triggers.
+The prior odds parameters $\hat{\pi}^S$ and $\hat{\pi}^G$ from Eq.~\ref{eq:bcr} help separate the two distributions.
+Altering $\hat{\pi}^S$ translates the \bcr probability distributions while adjusting $\hat{\pi}^G$ spreads the distributions (refer to Appendix A of \citet{BCR1}).
+Although Bayesian hyper-parameter estimation can determine the optimal values for $\hat{\pi}^S$ and $\hat{\pi}^G$, an easier approach is to adjust the parameters for each data chunk's \bcr distribution.
+In this study, we tune $\hat{\pi}^S$ and $\hat{\pi}^G$ to maximally separate the \bcr distributions for the background and simulated triggers.
 
@@
 
-We limit our search for the maximum KL-divergence in the $P^S$ and $P^G$ ranges of $[10^{-10}, 10^0]$.
-We set our values for $P^S$ and $P^G$ to those which provide the highest KL-divergence and calculate the \bcr for candidate events present in this data chunk.
+We limit our search for the maximum KL-divergence in the $\hat{\pi}^S$ and $\hat{\pi}^G$ ranges of $[10^{-10}, 10^0]$.
+We set our values for $\hat{\pi}^S$ and $\hat{\pi}^G$ to those which provide the highest KL-divergence and calculate the \bcr for candidate events present in this data chunk.
 Note that we conduct the analysis in data chunks of a few days rather than an entire data set of a few months as the background may be different at different points of the entire data set.
@@
 O2 lasted several months over which the detector's sensitivity varied.
-Hence, a part of our analysis entailed tuning the prior odds for obtaining a signal and a glitch, $P^S$ and $P^G$, as described in Section~\ref{sec:method}.
+Hence, a part of our analysis entailed tuning the prior odds for obtaining a signal and a glitch, $\hat{\pi}^S$ and $\hat{\pi}^G$, as described in Section~\ref{sec:method}.
 Table~\ref{tab:priorodds} presents the signal and glitch prior odds utilized for each time-frame of O2 data.
@@
 Tuning the prior odds can dramatically affect the \pastrobcr.
-For example, consider Table~\ref{tab:tuningresults}, which reports tuned \pastrobcr and un-tuned \untunedpastrobcr (where $P^S=1$ and $P^G=1$) for various high-mass events and candidates.
+For example, consider Table~\ref{tab:tuningresults}, which reports tuned \pastrobcr and un-tuned \untunedpastrobcr (where $\hat{\pi}^S=1$ and $\hat{\pi}^G=1$) for various events and candidates.
 By tuning the prior odds, the \pastrobcr for some IAS events (for example, GW170403 and GW170817A) can change by more than 0.5, resulting in the promotion/demotion of a candidate's significance.
@@
     \end{subfigure}
-    \caption{Posterior distributions for some parameters of 170222. 
-    Left: Posterior probability distributions for 4 of the 11 search parameters.
-Sections of the prior probability density functions used for analysis are displayed in green in one-dimensional marginal distributions plots.
-    Right: Posterior probability distributions for some inferred parameters. \avi{Should i plot prior-samples on the right? }
+    \caption{Posterior distributions for 8 parameters of 170222. 
+    Left: Posterior probability distributions for 4 of the 12 search parameters in orange.
+The prior probability density functions used for analysis are displayed in green in one-dimensional marginal distributions plots.
+    Right: Posterior probability distributions for 4 inferred parameters in orange.
     \label{fig:170222}}

### 2021-05-28 main.tex
complete draft

@@
 \newcommand{\gwpy}{{\sc \href{https://gwpy.github.io/}{\texttt{GWpy}}}\xspace}
-\newcommand{\imrphenomp}{{\sc IMRPhenomPv2}\xspace}
-\newcommand{\seob}{{\sc SEOBNRv4PHM}\xspace}
+
+\newcommand{\imrphenomp}{{\sc \texttt{IMRPhenomPv2}}\xspace}
+\newcommand{\seob}{{\sc \texttt{SEOBNRv4PHM}}\xspace}
+\newcommand{\nrsur}{{\sc \texttt{NRSur7dq4}}\xspace}
+\newcommand{\imrxhm}{{\sc \texttt{IMRPhenomXPHM}}\xspace}
 
@@
 Here we demonstrate a ranking statistic utilizing Bayesian inference to detect binary black hole mergers with a total mass $>55$~\msun.
-\avi{Say why it improves on prev techniques}.
 We apply this technique to candidate events with total masses $>55$~\msun during LIGO's second observing run to search for previously unresolved gravitational-wave signals from this heavy category of binary black holes.
@@
 \end{abstract}
+
+% \avi{Say why it improves on prev techniques}
 
@@
 
-Although a significant fraction of the glitches can be removed by testing them for coherence amongst various ground based detectors and performing matched-filtering, these methods are insufficient to remove all the glitches~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
-One method to account for more glitches while searching for CBC gravitational-waves is to rely on a Bayesian odds~\cite{bci, kanner2016leveraging, BCR1, BCR2, bcr_gw151216, bayesian_odds}.
-In this paper, we rank O2's candidate gravitational-wave signals from $55-500\ \msun$ total mass systems using a Bayesian method called the Bayesian Coherence Odds-Ratio \bcr~\cite{BCR1}.
-\avi{Should explain: whats the advantage of this?
-Why is it useful for triggers with $M_T>55\msun$?} The \bcr used in this study is a bootstrap-Bayesian odds calculated using the probability of data under the hypothesis that the data contains coherent signals vs.
+Although a significant fraction of the glitches can be discriminated by testing them for coherence amongst various ground based detectors and performing matched-filtering, these methods are insufficient to identify all glitches~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
+One method to discriminate more glitches while searching for CBC gravitational-waves is to rely on a Bayesian odds~\cite{bci, kanner2016leveraging, BCR1, BCR2, bcr_gw151216, bayesian_odds}.
+Utilising Bayesian odds is the optimal method for discriminating glitches from signals~\cite{BCR2}.
+In this paper, we rank O2's candidate gravitational-wave signals from $55-500\ \msun$ total mass systems using a Bayesian method called the Bayesian Coherence Ratio \bcr~\cite{BCR1}.
+The \bcr used in this study is a bootstrap-Bayesian odds that estimates the true Bayesian odds.
+The \bcr is calculated using the probability of data under the hypothesis that the data contains coherent signals vs.
 incoherent glitches and empirically calculated prior-odds that describe how likely each hypothesis is.
@@
 
-We find that (a) high-mass events reported in the \GWTC, including GW170729 (the heaviest event in \GWTC) are very statistically significant $\pastrobcr>0.9$; (b) three out of the eight \IAS events and candidates have $\pastrobcr>0.5$, corroborating \IAS's detection claims for those events (GW170304, GW170727, GW170817A); and that (c) our ranking statistic does not identify any new intermediate-mass black holes, but does identify an unreported marginal stellar-mass binary black hole candidate, 170222 with $\pastrobcr\sim0.5$ \avi{Need to doublecheck that this wasnt in the PyCBC sub-threshold paper}.
+We find that (a) high-mass events reported in the \GWTC, including GW170729 (the heaviest event in \GWTC) are very statistically significant $\pastrobcr>0.9$; (b) three out of the eight \IAS events and candidates have $\pastrobcr>0.5$, corroborating \IAS's detection claims for those events (GW170304, GW170727, GW170817A); and that (c) our ranking statistic does not identify any new intermediate-mass black holes, but does identify an unreported marginal stellar-mass binary black hole candidate, 170222 with $\pastrobcr\sim0.5$ %\avi{Need to doublecheck that this wasnt in the PyCBC sub-threshold paper}.
 
@@
 The standard framework to identify CBC gravitational-wave signals in data is to quantify the significance of candidates with null-hypothesis significance testing~\cite{GWTC1, GWTC2}.
-In this framework, the candidates' ranking statistic is compared against a background distribution in a frequentist approach.
+In this framework, the candidates' ranking statistic is compared against a background distribution.
 The independent matched-filter searches, e.g.
 \pycbc~\cite{pycbc_og4}, \spiir~\cite{spiir} and \gstlal~\cite{sachdev2019gstlal}, and the coherent burst search \cwb~\cite{cwb} used by LVK to search for signals in gravitational-wave data all use ranking statistics in such a manner~\cite{GWTC1}.
-\avi{Holdup: isnt GSTLAL's method a bootstrapped-Bayesian method?} Both \pycbc and \gstlal's ranking statistic incorporate information of the relative likelihood that the data contains a coherent signal versus just noise.
+Both \pycbc and \gstlal's ranking statistic incorporate information of the relative likelihood that the data contains a coherent signal versus just noise.
 In contrast, \cwb's ranking statistic uses the information of coherent energy present in the network of detectors~\cite{GWTC1}.
 
-\avi{I discuss the benefits of the BCR here...}
 Bayesian inference offers an alternative means to rank the significance of candidate events by computing the odds that the data contain a transient gravitational-wave signal vs.
@@
 Candidate \bcr-values are either statistically insignificant compared to the background \bcr distribution, implying the candidate is more probable to be an incoherent instrumental feature (the $\mathcal{H}_I$ null-hypothesis), or statistically significant relative to the background distribution, indicating the possible presence of an astrophysical signal (the $\mathcal{H}_S$ hypothesis).
-A false alarm probability with trial factors \avi{(need to define a trial factor)}, \fap, for the candidate \bcr-value can quantify the significance.
-The \fap is the probability that a candidate originating from a non-astrophysical source can be falsely identified as a signal.
-
-To calculate the \fap, each candidate \bcr is considered a single statistical trial that can occur at a fixed false alarm probability $f$, where $f$ is the probability of observing a background $\bcr'$ greater than or equal to the candidate \bcr,
+A false alarm probability with trial factors, \fap, for the candidate \bcr-value can quantify the significance.
+The \fap for a \bcr-value is the probability that a candidate originating from a non-astrophysical source can be falsely identified as a signal once in $N$ trials, and is given by
+\begin{equation}
+    \fap = 1 - (1-f)^N \ ,
+\end{equation}
+where $f$ is the probability of observing a background $\bcr'$ greater than or equal to the candidate \bcr,
 \begin{equation}
     f = \frac{\text{Count of } \bcr' \leq \bcr}{\text{Count of } \bcr'} \ .
-\end{equation}
-The false alarm probability with trials \fap that the \bcr measurement occurs at least once for $N$ trials $(N > 0)$, where $N$ is the number of candidate signals, is \avi{(This is very convoluted)}
-\begin{equation}
-    \fap = 1 - (1-f)^N \ .
 \end{equation}
@@
 
-\avi{Should I mention that we need \pycbc  as a pre-selection step to computing? }
+% \avi{Should I mention that we need \pycbc  as a pre-selection step to computing? }
 
@@
 Finally, to test the search's sensitivity, \pycbc produced and searched for thousands of simulated signals.
-\avi{Do i need to contextualize this choice more, ie talk about what would happen if I chose a narrower range?}
+% \avi{Do i need to contextualize this choice more, ie talk about what would happen if I chose a narrower range?}
 
@@
 % 1178294418, May 08, 2017, 16:00 UTC
-\caption[ BCR search space.]{The template bank (pink) used by \pycbc to search a section of O2 data from $\text{April 23 - May 8, 2017}$.
+\caption[ BCR search space.]{The templates (pink) used by \pycbc to search a section of O2 data from $\text{April 23 - May 8, 2017}$.
 Our search is constrained to the parameter space enclosed by the dashed line.
@@
 The waveform template we utilize is \imrphenomp, a phenomenological waveform template constructed in the frequency domain that models the in-spiral, merger, and ring-down (IMR) of a compact binary coalescence~\citep{khan2016frequency}.
-Although there exist gravitational-wave templates such as IMRPhenomPv3HM, NRSur7dq4, \seob~\cite{seobnrv4phm} (and others) which incorporate more physics, such as information on higher-order modes, we use \imrphenomp as it is computationally inexpensive compared to others.
+Although there exist gravitational-wave templates such as \imrxhm~\cite{imrphenompxhm}, \nrsur~\cite{nrsur7dq4} and \seob~\cite{seobnrv4phm} which incorporate more physics, such as information on higher-order modes, we use \imrphenomp as it is computationally inexpensive compared to others.
 

### 2021-05-28 main.tex
adjust plot and labels

@@
     \caption{Posterior distributions for 8 parameters of 170222. 
-    Left: Posterior probability distributions for 4 of the 12 search parameters in orange.
-The prior probability density functions used for analysis are displayed in green in one-dimensional marginal distributions plots.
-    Right: Posterior probability distributions for 4 inferred parameters in orange.
+    Left: Posterior probability distributions for 4 of the 12 search parameters.
+    Right: Posterior probability distributions for 4 derived parameters.
     \label{fig:170222}}

### 2021-05-28 scripts/make_template_plot.py

@@ -98,7 +98,7 @@ def plot_template_bank():
         dict(
             data=template_bank,
             plot_kwargs=dict(
-                color="pink", s=0.2, marker=".", alpha=0.2, label="Template Bank"
+                color="pink", s=0.2, marker=".", alpha=0.2, label="Templates"
             ),
         ),
         dict(
@@ -164,7 +164,7 @@ def plot_template_bank():
         )
 
     bank_patch = ax_m1m2.scatter(
-        [], [], label="Template Bank", marker=".", color="pink"
+        [], [], label="Templates", marker=".", color="pink"
     )
     (prior_patch,) = ax_m1m2.plot([], [], label="Prior", linestyle="--", color="k")
     fg_patch = ax_m1m2.scatter(

### 2021-05-28 scripts/plot_corners.py

@@ -21,7 +21,7 @@ PARAMS = dict(
     cos_theta_12=dict(latex_label=r"$\mathbf{\cos \theta_{12}}$", range=(-1, 1)),
     tilt_1=dict(latex_label=r"$tilt_{1}$", range=(0, np.pi)),
     remnant_kick_mag=dict(latex_label=r"$|\vec{v}_k|\ $km/s", range=(0, 3000)),
-    chirp_mass=dict(latex_label=r"$\mathbf{M_{c}}$", range=(5, 100)),
+    chirp_mass=dict(latex_label=r"$\mathbf{M_{c}}$", range=(20, 80)),
     mass_1_source=dict(latex_label=r"$\mathbf{m_1^{source}}$", range=(25, 80)),
     mass_2_source=dict(latex_label=r"$\mathbf{m_2^{source}}$", range=(15, 60)),
     luminosity_distance=dict(latex_label="$\mathbf{d_L}$", range=(50, 4000)),
@@ -31,10 +31,7 @@ PARAMS = dict(
 )
 
 
-
-
 def plot_result_corner(r, parameters, fname, prior=None):
-
     plt_range = [PARAMS[p]["range"] for p in parameters]
     if prior:
         plt_range = [(prior[p].minimum, prior[p].maximum) for p in parameters]
@@ -64,7 +61,7 @@ def main():
         r,
         parameters=["chirp_mass", "mass_ratio", "a_1", "luminosity_distance"],
         fname="images/170222_prior_posterior.png",
-        prior=prior
+        prior=None
 
     )
 

### 2021-05-28 scripts/plot_corners.py
remove bolds

@@ -5,29 +5,54 @@ Script to plot "170222_prior_posterior.png" and "170222_source_posterior.png"
 import bilby
 import numpy as np
 from settings import set_matplotlib_style_settings
+import matplotlib
+import matplotlib.pyplot as plt
+
+plt.rc('text', usetex=True)
+plt.rc('text.latex', preamble=r'\usepackage{amsmath}')
+
 
 RES_PATH = "data/corner_data/170222_result.json"
 PRIOR = "data/corner_data/454ns.prior"
 
 set_matplotlib_style_settings()
 
+# PARAMS = dict(
+#     chi_eff=dict(latex_label=r"$\pmb{\chi_{eff}}$", range=(-0.8, 0.8)),
+#     chi_p=dict(latex_label=r"$\pmb{\chi_{p}}$", range=(0, 1)),
+#     a_1=dict(latex_label=r"$\pmb{a_1}$", range=(0, 1)),
+#     chi_1=dict(latex_label=r"$\pmb{\chi_1}$", range=(-1, 1)),
+#     cos_tilt_1=dict(latex_label=r"$\pmb{\cos(t1)}$", range=(-1, 1)),
+#     cos_tilt_2=dict(latex_label=r"$\pmb{\cos(t2)}$", range=(-1, 1)),
+#     cos_theta_12=dict(latex_label=r"$\pmb{\cos \theta_{12}}$", range=(-1, 1)),
+#     tilt_1=dict(latex_label=r"$tilt_{1}$", range=(0, np.pi)),
+#     remnant_kick_mag=dict(latex_label=r"$|\vec{v}_k|\ $km/s", range=(0, 3000)),
+#     chirp_mass=dict(latex_label=r"$\pmb{M_{c}}$", range=(20, 80)),
+#     mass_1_source=dict(latex_label=r"$\pmb{m_1^{}\ [M_\odot]}$", range=(25, 80)),
+#     mass_2_source=dict(latex_label=r"$\pmb{m_2^{}\ [M_\odot]}$", range=(15, 60)),
+#     luminosity_distance=dict(latex_label="$\pmb{d_L}\ \\bm{[Mpc]}$", range=(50, 4000)),
+#     log_snr=dict(latex_label="$\\rm{log}_{10}\ \\rho$)", range=(-1, 3)),
+#     redshift=dict(latex_label=r"$\pmb{z}$", range=(0, 1)),
[…]

### 2021-06-07 main.tex
incorporating erics suggestions

@@
 
-\title{A Bayesian ranking-statistic for binary black holes mergers in the second LIGO observing run}
+\title{A search for intermediate mass black holes mergers in the \\second LIGO--Virgo observing run with the Bayes Coherence Ratio}
 
@@
 \begin{abstract}
-The detection of an intermediate-mass black hole population ($10^2-10^6$~\msun) will provide probes to their formation environments (e.g., disks of active galactic nuclei, globular clusters) and illuminate a potential pathway to produce supermassive black holes.
-Numerous methods to search for $10^4-10^6\ \msun$ intermediate-mass black holes exist, while the primary method to find $10^2-10^3\ \msun$ is by identifying gravitational-waves emitted from the merger of stellar binaries.
-Ground-based gravitational-wave detectors are in principle sensitive to such mergers and have found one $142^{+28}_{-16}\ \msun$ intermediate-mass black hole.
-In reality, ground-based detector data contain numerous short-duration instrumental transients that mimic the gravitational-wave signals from mergers capable of producing intermediate-mass black holes, making intermediate-mass merger detection challenging.
-Here we demonstrate a ranking statistic utilizing Bayesian inference to detect binary black hole mergers with a total mass $>55$~\msun.
-We apply this technique to candidate events with total masses $>55$~\msun during LIGO's second observing run to search for previously unresolved gravitational-wave signals from this heavy category of binary black holes.
-Our analysis does not discover new intermediate-mass black holes.
-However, we find support for some stellar-mass binary black holes unreported in GWTC-1.
+The detection of an intermediate-mass black hole population ($10^2-10^6$~\msun) will provide clues to their formation environments (e.g., disks of active galactic nuclei, globular clusters) and illuminate a potential pathway to produce supermassive black holes.
+Ground-based gravitational-wave detectors are in principle sensitive to such mergers and have been used to detect one $142^{+28}_{-16}\ \msun$ intermediate-mass black hole formation event.
+Ground-based detector data contain numerous short-duration noise transients that can mimic the gravitational-wave signals from merging intermediate-mass black holes, limiting the sensitivity of searches.
+Here we demonstrate a Bayesian-inspired ranking statistic to detect binary black hole mergers with a total mass $\gtrsim55$~\msun.
+We use this statistic to identify candidate events with total masses $>55$~\msun using data from LIGO's second observing run.
+Our analysis does not yield evidence for new intermediate-mass black holes.
+However, we find support for some stellar-mass binary black holes not reported in the first LIGO--Virgo gravitational-wave transient catalog, GWTC-1.
 \end{abstract}
@@
 Since the 1970s, there has been a steady accumulation of evidence for stellar mass ($M_\text{BH} < 10^{2} \ \msun$) and supermassive black holes ($M_\text{BH} > 10^{6} \ \msun$)~\cite{Webster:1972:Natur, Balick:1974:ApJ, Ghez:1998:ApJ, Genzel:2010:RvMP, Abbott:2019:PhRvX, EventHorizonTelescopeCollaboration:2019:ApJL, Abbott:2020:arXiv}.
-However, there is a deficiency of observational evidence for black holes in the `intermediate-mass' range $10^{2} - 10^{6}\ \msun$.
+However, there is a deficiency of observational evidence for black holes in the intermediate-mass range $10^{2} - 10^{6}\ \msun$.
 The discovery of an intermediate-mass black hole population will bridge this observational gap, probe intermediate-mass formation environments (e.g.
 accretion disks of active galactic nuclei~\cite{Tagawa:2021:ApJ, Li:2021:arXiv, Samsing:2020:arXiv, Tagawa:2020:ApJ, Ishibashi:2020:A&A, Grobner:2020:A&A, Yang:2019:PhRvL, McKernan:2019:ApJL, Yang:2019:ApJ, McKernan:2018:ApJ, Bellovary:2016:ApJL, McKernan:2014:MNRAS, McKernan:2012:MNRAS}, the centers of dense stellar clusters~\cite{Banerjee:2021:MNRASa, Zevin:2021:ApJ,Mapelli:2021:arXiv,Weatherford:2021:ApJL, Bouffanais:2021:arXiv, Ballone:2021:MNRAS, Kumamoto:2021:arXiv, Banerjee:2021:MNRASb, Martinez:2020:ApJ, Romero-Shaw:2020:ApJL, Anagnostou:2020:PASA}, Population-III stars~\cite{Toubiana:2021:PhRvL, Farrell:2021:MNRAS, Safarzadeh:2020:ApJL, Liu:2020:MNRAS, Inayoshi:2017:MNRAS}), and illuminate our understanding of supermassive black hole formation~\cite{Askar:2021:MNRAS, ArcaSedda:2019:arXiv, Amaro-Seoane:2007:CQGra, Gurkan:2006:ApJL}.
-A variety of techniques have been employed to search for $10^{4} - 10^{6}\ \msun$ intermediate mass candidates (reverberation mapping~\cite{Peterson:2014:SSRv}, direct kinematic measurements~\cite{Schodel:2002:Natur, Kiziltan:2017:Natur}, applying macroscopic galaxy to black hole mass scaling relations ($M_{BH}$-$\sigma$ and $M_{BH}$-L relations)~\cite{Graham:2013:ApJ, Wevers:2017:MNRAS}, studying  X-ray luminosity and spectra~\cite{Greene:2004:ApJ, Lin:2020:ApJL}, gravitational lensing of light curves~\cite{paynter_evidence_2021}, and others~\cite{Greene:2020:ARA&A, Koliopanos:2017:mbhe, Mezcua:2017:IJMPD})).
+
+A variety of techniques have been employed to search for $10^{4} - 10^{6}\ \msun$ intermediate mass candidates including reverberation mapping~\cite{Peterson:2014:SSRv}, direct kinematic measurements~\cite{Schodel:2002:Natur, Kiziltan:2017:Natur}, applying macroscopic galaxy to black hole mass scaling relations ($M_{BH}$-$\sigma$ and $M_{BH}$-L relations)~\cite{Graham:2013:ApJ, Wevers:2017:MNRAS}, studying  X-ray luminosity and spectra~\cite{Greene:2004:ApJ, Lin:2020:ApJL}, gravitational lensing of gamma-ray burst light curves~\cite{paynter_evidence_2021}, and others~\cite{Greene:2020:ARA&A, Koliopanos:2017:mbhe, Mezcua:2017:IJMPD}).
 However, these observational techniques are challenging to use for intermediate mass black holes due to their small sphere of influence compared to super-massive black holes~\cite{Mezcua:2017:IJMPD}.
-Additionally, some candidates discovered with these techniques can be attributed to sources without intermediate-mass black holes (e.g.
-clusters of stellar-mass black holes~\cite{Ridolfi:2016:MNRAS, Freire:2017:MNRAS}, anisotropic emission from neutron stars~\cite{Israel:2017:MNRAS, RodriguezCastillo:2020:ApJ}), while others have high uncertainties intrinsic to the observational techniques~\cite{Greene:2020:ARA&A}.
+Additionally, some IMBH candidates can be attributed to sources other than intermediate-mass black holes (e.g., clusters of stellar-mass black holes~\cite{Ridolfi:2016:MNRAS, Freire:2017:MNRAS}, anisotropic emission from neutron stars~\cite{Israel:2017:MNRAS, RodriguezCastillo:2020:ApJ}), while others have high uncertainties intrinsic to the observational techniques~\cite{Greene:2020:ARA&A}.
+\et{Consider replacing previous sentence that says none of the current IMBH candidates are widely accepted within the astronomical community as unambiguous.}
 
-Compact binaries coalescences (CBCs) can provide unambiguous gravitational-wave signals for intermediate-mass candidates (e.g.
-the $142^{+28}_{-16}\ \msun$ remnant observed from the gravitational wave event GW190521~\cite{Abbott:2020:PhRvL}).
-As a binary's total mass $\text{M}_{T}$ is associated with its gravitational-wave merger frequency, $f\sim \text{M}_{T}^{-1}$,  ground based gravitational wave detectors ($f\sim 10^1 - 10^3\ \text{Hz}$) are sensitive to the last milliseconds of merging systems with $100 \msun < \text{M}_{T} < 400 \msun$~\cite{LIGOScientificCollaboration:2015:CQGra, Martynov:2016:PhRvD, Moore_2014}, while space-based detectors ($f \sim 10^{-2} - 10^1\ \text{Hz}$) can study the full signals of merging systems with $10^4 \msun < \text{M}_{T} < 10^7 \msun$~\cite{ Moore_2014, Lu:2019:PhRvD}.
-Because of the short-duration of intermediate-mass gravitational-wave signals in ground-based detector data streams, handling data quality is critical to their detection.
-The low-frequency ranges of ground-based observatories data-streams have numerous non-stationary terrestrial artifacts, called \textit{glitches}~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
-Like signals from intermediate mass mergers, some glitches last for a fraction of a second, making them difficult to distinguish from the signals.
-These glitches that mimic astrophysical signals can severely decrease the confidence in detection of true gravitational-waves from black hole mergers with total masses $>55$~\msun ~\cite{pycbc_short_duration_transients}.
+Compact binary coalescences (CBCs) can provide unambiguous gravitational-wave signals for intermediate-mass candidates (e.g., the $142^{+28}_{-16}\ \msun$ remnant observed from the gravitational wave event GW190521~\cite{Abbott:2020:PhRvL}).
+As a binary's total mass $\text{M}_{T}$ is associated with its gravitational-wave merger frequency, $f\sim \text{M}_{T}^{-1}$,  ground-based gravitational-wave detectors ($f\sim 10^1 - 10^3\ \text{Hz}$) are sensitive to the last milliseconds of merging systems with $100 \msun < \text{M}_{T} < 400 \msun$~\cite{LIGOScientificCollaboration:2015:CQGra, Martynov:2016:PhRvD, Moore_2014}, while space-based detectors ($f \sim 10^{-2} - 10^1\ \text{Hz}$) can study the full signals of merging systems with $10^4 \msun < \text{M}_{T} < 10^7 \msun$~\cite{ Moore_2014, Lu:2019:PhRvD}.
+Because of the short-duration of intermediate-mass gravitational-wave signals in ground-based detectors, data quality is critical for their detection.
+Gravitational-wave data is characterized by numerous non-stationary terrestrial artifacts called \textit{glitches}~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
+Like signals from intermediate mass mergers, most glitches last for a fraction of a second, making them difficult to distinguish from astrophysical signals.
+These glitches can decrease the sensitivity of searches for binary black hole mergers with total masses $>55$~\msun ~\cite{pycbc_short_duration_transients}.
 
-Although a significant fraction of the glitches can be discriminated by testing them for coherence amongst various ground based detectors and performing matched-filtering, these methods are insufficient to identify all glitches~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
-One method to discriminate more glitches while searching for CBC gravitational-waves is to rely on a Bayesian odds~\cite{bci, kanner2016leveraging, BCR1, BCR2, bcr_gw151216, bayesian_odds}.
-Utilising Bayesian odds is the optimal method for discriminating glitches from signals~\cite{BCR2}.
-In this paper, we rank O2's candidate gravitational-wave signals from $55-500\ \msun$ total mass systems using a Bayesian method called the Bayesian Coherence Ratio \bcr~\cite{BCR1}.
-The \bcr used in this study is a bootstrap-Bayesian odds that estimates the true Bayesian odds.
-The \bcr is calculated using the probability of data under the hypothesis that the data contains coherent signals vs.
-incoherent glitches and empirically calculated prior-odds that describe how likely each hypothesis is.
-After computing the candidate \bcr values, we calculate the candidate's probability of astrophysical origins, \pastrobcr.
-Finally, if the candidate has a \pastro reported by the the LIGO-Virgo-KAGRA (LVK) collaboration in \GWTC~\cite{GWTC1}, the \pycbc-team~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6, pycbc_single_det, pycbc_ogc_2}, by the Institute of Advanced study's team (\IAS)~\cite{IAS0, IAS1, IAS2}, or by \citet{bayesian_odds}, we compare their \pastro with the \pastrobcr.
-We highlight several innovations unique to this work.
-First, we use our Bayesian framework to analyze all candidate signals and background triggers (incoherent signal-free data) with total masses above $> 55 \msun$ in O2.
-Second, we empirically tune prior-odds for finding a signal or a glitch in O2 using \bcr distributions for background triggers and simulated signals.
-Finally,  we use the tuned-\bcr background distribution to compute how significant candidate signals are from the background.
+Although a significant fraction of the glitches can be identified by testing them for coherence amongst two or more detectors and performing matched-filtering, these methods are insufficient to identify all glitches~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
+One method to discriminate more glitches while searching for CBC is the Bayesian odds~\cite{bci, kanner2016leveraging, BCR1, BCR2, bcr_gw151216, bayesian_odds}.
+\et{Need sentence here saying we are inspired by the Bayesian odds to develop a ranking statistic that incorporates some of the ideas used in the odds.} In this paper, we rank O2's candidate gravitational-wave signals from $55-500\ \msun$ (\et{lab frame}) total mass systems using a ranking statistic called the Bayesian Coherence Ratio \bcr~\cite{BCR1}.
+\et{I deleted some text here going into detail about the BCR; save for method section.} For each candidate, we calculate the probability of astrophysical origin, \pastrobcr and compare to candidate events reported by other authors including the LIGO-Virgo-KAGRA (LVK) collaboration in \GWTC~\cite{GWTC1}, the \pycbc-team~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6, pycbc_single_det, pycbc_ogc_2}, by the Institute of Advanced study's team (\IAS)~\cite{IAS0, IAS1, IAS2}, or by \citet{bayesian_odds}.
+\et{Deleted several sentences here about innovations that I think are in the weeds.}
 
-We find that (a) high-mass events reported in the \GWTC, including GW170729 (the heaviest event in \GWTC) are very statistically significant $\pastrobcr>0.9$; (b) three out of the eight \IAS events and candidates have $\pastrobcr>0.5$, corroborating \IAS's detection claims for those events (GW170304, GW170727, GW170817A); and that (c) our ranking statistic does not identify any new intermediate-mass black holes, but does identify an unreported marginal stellar-mass binary black hole candidate, 170222 with $\pastrobcr\sim0.5$ %\avi{Need to doublecheck that this wasnt in the PyCBC sub-threshold paper}.
+We find that (a) high-mass events reported in the \GWTC, including GW170729 (the heaviest event in \GWTC) are very statistically significant $\pastrobcr>0.9$; (b) three out of the eight \IAS events and candidates have $\pastrobcr>0.5$, corroborating \IAS's detection claims for GW170304, GW170727, and GW170817A; and that (c) our ranking statistic does not identify any new intermediate-mass black holes, but does identify an unreported marginal stellar-mass binary black hole candidate, 170222 with $\pastrobcr\sim0.5$.
+%\avi{Need to doublecheck that this wasnt in the PyCBC sub-threshold paper}.
 
@@
 In this framework, the candidates' ranking statistic is compared against a background distribution.
-The independent matched-filter searches, e.g.
-\pycbc~\cite{pycbc_og4}, \spiir~\cite{spiir} and \gstlal~\cite{sachdev2019gstlal}, and the coherent burst search \cwb~\cite{cwb} used by LVK to search for signals in gravitational-wave data all use ranking statistics in such a manner~\cite{GWTC1}.
-Both \pycbc and \gstlal's ranking statistic incorporate information of the relative likelihood that the data contains a coherent signal versus just noise.
+The independent matched-filter searches, e.g., \pycbc~\cite{pycbc_og4}, \spiir~\cite{spiir} and \gstlal~\cite{sachdev2019gstlal}, and Coherent WaveBurst~\cite{cwb} used by LVK to search for signals in gravitational-wave data all use ranking statistics in such a manner~\cite{GWTC1}.
+Both \pycbc and \gstlal's ranking statistic incorporate information about the relative likelihood that the data contains a coherent signal versus noise.
 In contrast, \cwb's ranking statistic uses the information of coherent energy present in the network of detectors~\cite{GWTC1}.
 
-Bayesian inference offers an alternative means to rank the significance of candidate events by computing the odds that the data contain a transient gravitational-wave signal vs.
-instrumental glitches or noise~\cite{BCR1}.
-This method relies on accurate models for the signal and glitch morphologies and populations~\cite{BCR1}.
+Bayesian inference offers an alternative means to rank the significance of candidate events by computing the odds that the data contain a transient gravitational-wave signal versus instrumental glitches~\cite{BCR1}.
+This method relies on accurate models for the signal and glitch morphologies~\cite{BCR1}.
 In principle, Bayesian odds is the optimal method for hypothesis testing~\cite{BCR2}.
-Much of its power comes from the Bayesian ``evidence'': a marginalized likelihood.
-The evidence is the correct likelihood of having obtained the data given a hypothesis.
-However, due to the high computational cost to calculate the evidence, it is not explicitly used in current matched filter searches.
-Here, we explore a middle-ground hybrid between frequentist matched filtered searches and Bayesian odds.
-We compute Bayesian evidences for foreground and background data under the assumption that they either contain coherent gravitational-wave signals, noise, or glitches.
-However, instead of computing true Bayesian odds, we use the evidences to form a bootstrapped distribution for the odds of foreground and background events to form a frequentist ranking statistic.
+Much of its power comes from the Bayesian evidence, the likelihood of the data given a hypothesis.
+However, the evidence is not used in current matched filter searches.
+Here, we explore a hybrid frequentist/Bayesian ranking statistic that makes use of the Bayesian evidence.
+We compute the Bayesian evidence under the assumption that they either contain a coherent gravitational-wave signal, noise, or a glitch.
+However, instead of computing true Bayesian odds, we use the evidences as a ranking statistic.
+We form a bootstrapped distribution of the evidence for simulated foreground and background events in order to form a frequentist ranking statistic.
 
-\subsection{The Bayesian Coherence Odds-Ratio}
+\subsection{Formalism}
 
@@
 However, as the priors-odds are unknown, we \textit{tune} values for prior-odds, $\hat{\pi}^S$ and $\hat{\pi}^G$, to estimate \bcrodds with a ranking statistic, \bcr, given by
+\et{I would remove everything in this subsection before this point.
+Save it for your dissertation if you want, but I don't think we need to review Bayesian basics here.
+Instead, just begin by saying that we implement the BCR, which is given by Eq.~\ref{eq:rho_bcr} with suitable references to the previous BCR papers.
+The motivation for the BCR can be summarised in a single sentence.}
 \begin{equation}
-\label{eq:bcr}
+\label{eq:rho_bcr}
 \bcr = \frac{\hat{\pi}^S Z^S}{\prod\limits^D_{i=1} \ [\hat{\pi}^G Z^G_i + (1-\hat{\pi}^G)Z^N_i]}\ .
 \end{equation}
-
+\et{Rewrite the remaining paragraphs to explain that how the BCR relates to the odds with just a few sentences, avoiding equations.}
 In the limit where the estimated prior-odds equal the true prior-odds, $\bcr\to\bcrodds$.
@@
 \subsection{Estimation of astrophysical signal probability}
+\et{Above, I propose to cut the previous subsection way back.
+I think this subsection can be cut way back too and combined with the previous subsection.
+Once we have finished talking about $\rho_\text{BCR}$, we can just state that we use time-shifted data to generate distributions of $\rho_\text{BCR}$ for noise, which we use to calculate a single-event false alarm probability = the fraction of triggers with a $\rho_\text{BCR}$ at least that big.
+(The thing we are currently calling $f$ is a single-event false alarm probability, so we should call it that and give it a better variable name like $p_1$.) Then comment that we consider $N$ triggers so we also calculate a false-alarm probability with trial factors, which is given by the current Eq.~6.
+(I suggest you call the false alarm probability with trial factors $p_N$ to avoid confusion.) The text should say how $N$ is determined.
+I agree that $p_\text{astro} = 1-p_N$ is too sloppy to do in a paper.
+(The reason we are using FAP is because there was not appetite to calculate the distribution of $\rho_\text{BCR}$ for a plausible signal distribution, which is necessary to get an actual $p_\text{astro}$.) At this late stage, I think the best thing to do is just say that we are going to report $1-p_N$ alongside $p_\text{astro}$ values even though they are apples and oranges.
+While it's sloppy to compare them directly, they \textit{are} both indicators of significance.
+Moreover, different groups make different assumptions about the signal distribution, and so the different $p_\text{astro}$ values are sort of already different fruit; see Shanika's paper.
+We can explain all this and say we're going to put everything into one table anyway.
+However, the least bad thing to do is to report $p_N$ without calling it $p_\text{astro}$.
+I think most referees can live with that.}
 Candidate \bcr-values are either statistically insignificant compared to the background \bcr distribution, implying the candidate is more probable to be an incoherent instrumental feature (the $\mathcal{H}_I$ null-hypothesis), or statistically significant relative to the background distribution, indicating the possible presence of an astrophysical signal (the $\mathcal{H}_S$ hypothesis).
@@
 
-\subsection{Data for Analysis}
+\subsection{Background estimation}
 
-To rank candidate event \bcr-values we need to compute a background \bcr distribution.
-We can obtain the background data needed from the LIGO Scientific collaboration's search pipelines that scan for gravitational-waves from compact binary mergers such as \gstlal~\cite{sachdev2019gstlal}, \mbta~\cite{MBTA}, \spiir~\cite{spiir} and \pycbc~\cite{pycbc_og4}.
-The output of \pycbc's search is a list of times and their corresponding \pycbc ranking statistic \pycbcstat values.
+To rank candidate event \bcr values we compute a background \bcr distribution.
+We use time-shifted background data from \pycbc~\cite{pycbc_og4}.
+\et{Add sentence here explaining what time-shifting is and why it is used.} The output of \pycbc's search is a list of times and their corresponding \pycbc ranking statistic \pycbcstat values.
 Whenever a local maximum of $\pycbcstat > \snr_\text{T}$, where $\snr_\text{T}$ is some predetermined threshold value, the \pycbc search pipeline produces a single-detector \textit{trigger} associated with the detector and time $t_c$ where the apparent signal in the data has its merger~\cite{pycbc_og6}.
-\pycbc produces three categories of triggers:
-\begin{itemize}
-    \item \textit{Candidate event trigger}: a trigger observed with coincident parameters amongst a network of detectors. 
-    \item \textit{Simulated trigger}: a trigger detected from an artificially manufactured signal injected into detector data.  
-    \item \textit{Background trigger}: a trigger obtained from incoherent signal-free background data (data manufactured by applying relative offsets, or time-slides, between the data of different detectors~\cite{pycbc_og6}).
-\end{itemize}
-
-After obtaining these triggers from \pycbc, we can calculate the trigger's \bcr-values and use them to measure candidate triggers' statistical significance.
-The \bcr can be a powerful ranking statistic as it incorporates information of not only all possible binary black hole systems that might have merged to produce the trigger but also the various incoherent glitches that might cause a false-detection~\cite{BCR1}.
-
+For each \pycbc background trigger, we calculate \bcr.
 % \avi{Should I mention that we need \pycbc  as a pre-selection step to computing? }
+\et{I think this section can be cut way back too.
+(I've deleted a bunch of stuff w track changes.) I don't think we need to get into the three types of triggers; just focus on background triggers.
+I would move this discussion into a single subsection along with IIA and IIB.
+I would cover this stuff \textit{before}getting into FAP calculation.
+That way, we already have introduced the distribution of $\rho_\text{BCR}$; it will be more clear what we are talking about.}
 
@@
 To accelerate our analysis, we use a likelihood that explicitly marginalizes over coalescence time, phase at coalescence, and luminosity distance (Eq.~80 from~\citet{intro_to_gw_bayes}).
+\et{I think that IIIa and IIb should probably be shrunken and merged so that Section III does not have any subsections (IIC can be deleted; see below).
+The way to cut these sections down is to stick to just \textit{describing what was done} rather than trying to add a lot of explanation.
+(Explaining what PyCBC does and why is particularly excessive, IMO.) Just cut out anything that is not part of a recipe to reproduce the analysis.}
 
@@
 These distributions are used to `tune' prior-odd $\hat{\pi}^S$ and $\hat{\pi}^G$ values as described in Appendix~\ref{apdx:tuning-prior-odds}.
+\et{This subsection discusses formalism (how the analysis works) and so it feels out of place in Section III, which is about the details of the implementation.
+I would delete this subsection entirely and just add a sentence or two to the formalism section explaining that the $\pi$'s are tuned emprically; see Appendix~\ref{apdx:tuning-prior-odds}.}
 
@@
 \input{Data/results_table}
-We analyze the $60,996$ background, $5,146$ simulated, and $25$ candidate triggers reported by \pycbc's search on the data from LIGO's second observing run, restricting our analysis to the triggers that fall within our mass-space as described in Section~\ref{sec:method}.We also analyze events and candidate events reported by \GWTC and the \IAS group (note: some of these were identified as candidates by the \pycbc search).
+We analyze the $60,996$ background, $5,146$ simulated, and $25$ candidate triggers reported by \pycbc's search on the data from LIGO's second observing run, restricting our analysis to the triggers that fall within our mass-space as described in Section~\ref{sec:method}.
+We also analyze events and candidate events reported by \GWTC and the \IAS group (note: some of these were identified as candidates by the \pycbc search).
 Table~\ref{tab:results} summaries the \pastrobcr, along with the \pastro of other pipelines for comparison.
+\et{The previous text about what we analysed should go in Section III. This section is just for reporting the results.}
+
+\et{Rewrite the following text w better explanation of FAP vs p-value.}
 Although the various pipeline \pastro are not mathematically equivalent, by comparing pipeline \pastro values for a given candidate, we can compare how significant each pipeline deems various candidates.
@@
 
-Until 2016, a majority of intermediate-mass black hole candidates were from electromagnetic observations.
-The dawn of gravitational wave astronomy has provided a new lens to identify and study these massive objects -- from the mergers of heavy black holes' gravitational wave emission.
-In the future, space-based gravitational wave detectors will uncover black holes in the upper end of the intermediate-mass range.
-In the present, ground-based gravitational-wave observatories can probe the lower-end of the intermediate-mass range.
-However, many short-duration terrestrial artifacts that mimic intermediate-mass gravitational-wave signals plague ground-based detectors, making intermediate-mass detection challenging.
-
 In this paper, we demonstrate that the Bayesian Coherence Odds-Ratio \bcr~\cite{BCR1} can be used as a ranking statistic to provide a measure of significance for gravitational wave signals originating from CBCs with total masses between $55\msun$ and $400\msun$, a range that includes intermediate-mass black holes.
@@
 \begin{acknowledgments}
-
+This work is supported by the Australian Research Council (ARC) Centre of Excellence CE170100004.
 The author gratefully thank the \pycbc team for providing the gravitational-wave foreground, background and simulated triggers from \pycbc's search of O2's data.

### 2021-06-15 images/bcr_formalism.tex
submission to dcc

--- 2021-05-28 main.tex
@@
-\documentclass[%
-%reprint,
-%superscriptaddress,
-%groupedaddress,
-%unsortedaddress,
-%runinaddress,
-%frontmatterverbose, 
-% preprint,
-%preprintnumbers,
- nofootinbib,
-%nobibnotes,
-%bibnotes,
- amsmath,amssymb,
- aps,
-%pra,
-%prb,
-%rmp,
-%prstab,
-%prstper,
-%floatfix,
- twocolumn,
- superscriptaddress
-]{revtex4-2}
-
-\usepackage{aas_macros}
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage{array}
-\usepackage{color,units}
-\usepackage[dvipsnames]{xcolor} % for more colours!
-\usepackage{lineno}
-\usepackage{dcolumn}
-\usepackage{longtable}
-\usepackage[normalem]{ulem} %% for striking out text
-\usepackage{subfigure}
-\usepackage[T1]{fontenc}
-\usepackage[breaklinks]{hyperref}
-\usepackage{booktabs}
-\usepackage{xspace} 
-\usepackage{bm}% bold math
-\usepackage{graphicx} % Include figure files
-% \usepackage{authblk}
-
-\graphicspath{{images/}} %Setting the graphicspath
-
-% symbols
-\DeclareSymbolFont{extraup}{U}{zavm}{m}{n}
-\DeclareMathSymbol{\varheart}{\mathalpha}{extraup}{86}
-\DeclareMathSymbol{\vardiamond}{\mathalpha}{extraup}{87}
-
-% Keywords
-\newcommand{\bilby}{{\sc \href{https://lscsoft.docs.ligo.org/bilby/}{\texttt{Bilby}}}\xspace}
-\newcommand{\bilbypipe}{{\sc \texttt{bilby\_pipe}}\xspace}
-\newcommand{\dynesty}{{\sc \texttt{dynesty}}\xspace}
-\newcommand{\cpnest}{{\sc cpnest}\xspace}
-\newcommand{\ptemcee}{{\sc ptemcee}\xspace}
-\newcommand{\gwpy}{{\sc \href{https://gwpy.github.io/}{\texttt{GWpy}}}\xspace}
-
-\newcommand{\imrphenomp}{{\sc \texttt{IMRPhenomPv2}}\xspace}
-\newcommand{\seob}{{\sc \texttt{SEOBNRv4PHM}}\xspace}
-\newcommand{\nrsur}{{\sc \texttt{NRSur7dq4}}\xspace}
-\newcommand{\imrxhm}{{\sc \texttt{IMRPhenomXPHM}}\xspace}
-
-\newcommand{\gstlal}{{\sc GstLAL}\xspace}
-\newcommand{\cwb}{{\sc cWB}\xspace}
-\newcommand{\spiir}{{\sc SPIIR}\xspace}
-\newcommand{\mbta}{{\sc MBTAOnline}\xspace}
-\newcommand{\pycbc}{{\sc \href{https://pycbc.org/}{{PyCBC}}}\xspace}
-
-\newcommand{\GWTC}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2019PhRvX...9c1040A/abstract}{{GWTC-1}}}\xspace}
-\newcommand{\OGC}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2020ApJ...891..123N/abstract}{{2-OGC}}}\xspace}
-\newcommand{\IAS}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2020PhRvD.101h3030V/abstract}{{IAS}}}\xspace}
-
-% math keywords 
-\newcommand{\fancytext}[1]{{\relax\ifmmode#1\else $#1$\fi}\xspace}
-\newcommand{\mathcmd}[1]{{\sc \relax\ifmmode#1\else $#1$\fi}\xspace}
-\newcommand{\bcr}{\mathcmd{\rho_\text{BCR}}}
-\newcommand{\bcrodds}{\mathcmd{\mathcal{O}_{\mathrm{BCR}}}}
-\newcommand{\pycbcstat}{\mathcmd{\rho_\text{PC}}}
-\newcommand{\snr}{\mathcmd{\rho}}
-\newcommand{\psd}{\mathcmd{P(f)}}
-\newcommand{\msun}{\mathcmd{\text{M}_\odot}}
-\newcommand{\mtot}{\mathcmd{M}}
-\newcommand{\parameters}{\mathcmd{\vec{\theta}}}
-\newcommand{\prior}{\mathcmd{\pi(\parameters)}}
-\newcommand{\template}{\mathcmd{\mu(\parameters)}}
-\newcommand{\fap}{\mathcmd{\text{FAP}}}
-
-\newcommand{\pastro}{\fancytext{p_\text{astro}}}
-\newcommand{\pastrobcr}{\fancytext{p_\text{astro}^{\text{BCR}}}}
-\newcommand{\untunedpastrobcr}{\fancytext{p_\text{astro}^{\text{BCR}\prime}}}
-\newcommand{\pastroext}{\fancytext{p_\text{astro}^{\text{ext}}}}
-\newcommand{\pval}{\fancytext{\text{p-value}}}
-% Table settings
-\renewcommand{\aboverulesep}{0pt}
-\renewcommand{\belowrulesep}{0pt}
-% \setlength\cellspacetoplimit{2pt}
-% \setlength\cellspacebottomlimit{2pt}
-
-\newcolumntype{C}{>{\centering\arraybackslash}X}
-\newcolumntype{L}{>{\arraybackslash}X}
-
-% Aesthetic colours
-\definecolor{dodgerblue}{HTML}{1E90FF}
-\definecolor{viennared}{HTML}{DA0A14}
-\definecolor{ctorange}{HTML}{FF6C0C}
-\definecolor{wales}{HTML}{ff0038}
-\definecolor{benettongreen}{HTML}{009421}
-\definecolor{valenciacfred}{HTML}{ee3524}
-\definecolor{barcelonafcgold}{HTML}{edbb00}
-\definecolor{jam}{HTML}{A50B5E}
-\definecolor{austriawien}{HTML}{441678}
-\definecolor{italia90green}{HTML}{009966}
-\definecolor{ferrarired}{HTML}{ff2800}
-\definecolor{gray}{HTML}{F0F0F0}
-\definecolor{LightCyan}{rgb}{0.88,1,1}
-\newcolumntype{a}{>{\columncolor{gray}}c}
-\newcolumntype{b}{>{\columncolor{white}}c}
-
-% author comments
-\newcommand{\avi}[1]{\textcolor{orange}{[AV: #1]}}
-\newcommand{\greg}[1]{\textcolor{purple}{[Greg: #1]}}
-\newcommand{\rs}[1]{\textcolor{red}{[RS: #1]}}
-\newcommand{\et}[1]{\textcolor{blue}{[ET: #1]}}
-
-\begin{document}
-
-\title{A Bayesian ranking-statistic for binary black holes mergers in the second LIGO observing run}
-
-\input{authors}
-
-\date{\today}
-
-\begin{abstract}
-The detection of an intermediate-mass black hole population ($10^2-10^6$~\msun) will provide probes to their formation environments (e.g., disks of active galactic nuclei, globular clusters) and illuminate a potential pathway to produce supermassive black holes.
-Numerous methods to search for $10^4-10^6\ \msun$ intermediate-mass black holes exist, while the primary method to find $10^2-10^3\ \msun$ is by identifying gravitational-waves emitted from the merger of stellar binaries.
-Ground-based gravitational-wave detectors are in principle sensitive to such mergers and have found one $142^{+28}_{-16}\ \msun$ intermediate-mass black hole.
-In reality, ground-based detector data contain numerous short-duration instrumental transients that mimic the gravitational-wave signals from mergers capable of producing intermediate-mass black holes, making intermediate-mass merger detection challenging.
-Here we demonstrate a ranking statistic utilizing Bayesian inference to detect binary black hole mergers with a total mass $>55$~\msun.
-We apply this technique to candidate events with total masses $>55$~\msun during LIGO's second observing run to search for previously unresolved gravitational-wave signals from this heavy category of binary black holes.
-Our analysis does not discover new intermediate-mass black holes.
-However, we find support for some stellar-mass binary black holes unreported in GWTC-1.
-\end{abstract}
-
-% \avi{Say why it improves on prev techniques}
-
-\maketitle
-
-%%%%%%---SECTIONS---%%%%%%%%%%%%
-\section{Introduction}
-Since the 1970s, there has been a steady accumulation of evidence for stellar mass ($M_\text{BH} < 10^{2} \ \msun$) and supermassive black holes ($M_\text{BH} > 10^{6} \ \msun$)~\cite{Webster:1972:Natur, Balick:1974:ApJ, Ghez:1998:ApJ, Genzel:2010:RvMP, Abbott:2019:PhRvX, EventHorizonTelescopeCollaboration:2019:ApJL, Abbott:2020:arXiv}.
-However, there is a deficiency of observational evidence for black holes in the `intermediate-mass' range $10^{2} - 10^{6}\ \msun$.
-The discovery of an intermediate-mass black hole population will bridge this observational gap, probe intermediate-mass formation environments (e.g.
-accretion disks of active galactic nuclei~\cite{Tagawa:2021:ApJ, Li:2021:arXiv, Samsing:2020:arXiv, Tagawa:2020:ApJ, Ishibashi:2020:A&A, Grobner:2020:A&A, Yang:2019:PhRvL, McKernan:2019:ApJL, Yang:2019:ApJ, McKernan:2018:ApJ, Bellovary:2016:ApJL, McKernan:2014:MNRAS, McKernan:2012:MNRAS}, the centers of dense stellar clusters~\cite{Banerjee:2021:MNRASa, Zevin:2021:ApJ,Mapelli:2021:arXiv,Weatherford:2021:ApJL, Bouffanais:2021:arXiv, Ballone:2021:MNRAS, Kumamoto:2021:arXiv, Banerjee:2021:MNRASb, Martinez:2020:ApJ, Romero-Shaw:2020:ApJL, Anagnostou:2020:PASA}, Population-III stars~\cite{Toubiana:2021:PhRvL, Farrell:2021:MNRAS, Safarzadeh:2020:ApJL, Liu:2020:MNRAS, Inayoshi:2017:MNRAS}), and illuminate our understanding of supermassive black hole formation~\cite{Askar:2021:MNRAS, ArcaSedda:2019:arXiv, Amaro-Seoane:2007:CQGra, Gurkan:2006:ApJL}.
-A variety of techniques have been employed to search for $10^{4} - 10^{6}\ \msun$ intermediate mass candidates (reverberation mapping~\cite{Peterson:2014:SSRv}, direct kinematic measurements~\cite{Schodel:2002:Natur, Kiziltan:2017:Natur}, applying macroscopic galaxy to black hole mass scaling relations ($M_{BH}$-$\sigma$ and $M_{BH}$-L relations)~\cite{Graham:2013:ApJ, Wevers:2017:MNRAS}, studying  X-ray luminosity and spectra~\cite{Greene:2004:ApJ, Lin:2020:ApJL}, gravitational lensing of light curves~\cite{paynter_evidence_2021}, and others~\cite{Greene:2020:ARA&A, Koliopanos:2017:mbhe, Mezcua:2017:IJMPD})).
-However, these observational techniques are challenging to use for intermediate mass black holes due to their small sphere of influence compared to super-massive black holes~\cite{Mezcua:2017:IJMPD}.
-Additionally, some candidates discovered with these techniques can be attributed to sources without intermediate-mass black holes (e.g.
-clusters of stellar-mass black holes~\cite{Ridolfi:2016:MNRAS, Freire:2017:MNRAS}, anisotropic emission from neutron stars~\cite{Israel:2017:MNRAS, RodriguezCastillo:2020:ApJ}), while others have high uncertainties intrinsic to the observational techniques~\cite{Greene:2020:ARA&A}.
-
-Compact binaries coalescences (CBCs) can provide unambiguous gravitational-wave signals for intermediate-mass candidates (e.g.
-the $142^{+28}_{-16}\ \msun$ remnant observed from the gravitational wave event GW190521~\cite{Abbott:2020:PhRvL}).
-As a binary's total mass $\text{M}_{T}$ is associated with its gravitational-wave merger frequency, $f\sim \text{M}_{T}^{-1}$,  ground based gravitational wave detectors ($f\sim 10^1 - 10^3\ \text{Hz}$) are sensitive to the last milliseconds of merging systems with $100 \msun < \text{M}_{T} < 400 \msun$~\cite{LIGOScientificCollaboration:2015:CQGra, Martynov:2016:PhRvD, Moore_2014}, while space-based detectors ($f \sim 10^{-2} - 10^1\ \text{Hz}$) can study the full signals of merging systems with $10^4 \msun < \text{M}_{T} < 10^7 \msun$~\cite{ Moore_2014, Lu:2019:PhRvD}.
-Because of the short-duration of intermediate-mass gravitational-wave signals in ground-based detector data streams, handling data quality is critical to their detection.
-The low-frequency ranges of ground-based observatories data-streams have numerous non-stationary terrestrial artifacts, called \textit{glitches}~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
-Like signals from intermediate mass mergers, some glitches last for a fraction of a second, making them difficult to distinguish from the signals.
-These glitches that mimic astrophysical signals can severely decrease the confidence in detection of true gravitational-waves from black hole mergers with total masses $>55$~\msun ~\cite{pycbc_short_duration_transients}.
-
-Although a significant fraction of the glitches can be discriminated by testing them for coherence amongst various ground based detectors and performing matched-filtering, these methods are insufficient to identify all glitches~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
-One method to discriminate more glitches while searching for CBC gravitational-waves is to rely on a Bayesian odds~\cite{bci, kanner2016leveraging, BCR1, BCR2, bcr_gw151216, bayesian_odds}.
-Utilising Bayesian odds is the optimal method for discriminating glitches from signals~\cite{BCR2}.
-In this paper, we rank O2's candidate gravitational-wave signals from $55-500\ \msun$ total mass systems using a Bayesian method called the Bayesian Coherence Ratio \bcr~\cite{BCR1}.
-The \bcr used in this study is a bootstrap-Bayesian odds that estimates the true Bayesian odds.
-The \bcr is calculated using the probability of data under the hypothesis that the data contains coherent signals vs.
-incoherent glitches and empirically calculated prior-odds that describe how likely each hypothesis is.
-After computing the candidate \bcr values, we calculate the candidate's probability of astrophysical origins, \pastrobcr.
-Finally, if the candidate has a \pastro reported by the the LIGO-Virgo-KAGRA (LVK) collaboration in \GWTC~\cite{GWTC1}, the \pycbc-team~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6, pycbc_single_det, pycbc_ogc_2}, by the Institute of Advanced study's team (\IAS)~\cite{IAS0, IAS1, IAS2}, or by \citet{bayesian_odds}, we compare their \pastro with the \pastrobcr.
-We highlight several innovations unique to this work.
-First, we use our Bayesian framework to analyze all candidate signals and background triggers (incoherent signal-free data) with total masses above $> 55 \msun$ in O2.
-Second, we empirically tune prior-odds for finding a signal or a glitch in O2 using \bcr distributions for background triggers and simulated signals.
-Finally,  we use the tuned-\bcr background distribution to compute how significant candidate signals are from the background.
-
-We find that (a) high-mass events reported in the \GWTC, including GW170729 (the heaviest event in \GWTC) are very statistically significant $\pastrobcr>0.9$; (b) three out of the eight \IAS events and candidates have $\pastrobcr>0.5$, corroborating \IAS's detection claims for those events (GW170304, GW170727, GW170817A); and that (c) our ranking statistic does not identify any new intermediate-mass black holes, but does identify an unreported marginal stellar-mass binary black hole candidate, 170222 with $\pastrobcr\sim0.5$ %\avi{Need to doublecheck that this wasnt in the PyCBC sub-threshold paper}.
-
-The remainder of this paper is structured as follows.
-We outline our methods, including details of our ranking statistic and the retrieval of our candidates in Section~\ref{sec:method}.
-We present details on the implementation of our analysis in Section~\ref{sec:Analysis}.
-Finally, we present our results in Section~\ref{sec:Results}, and discuss these results in the context of the significance of gravitational-wave candidates in Section~\ref{sec:Conclusion}.
-
-\section{Method\label{sec:method}}
-
-The standard framework to identify CBC gravitational-wave signals in data is to quantify the significance of candidates with null-hypothesis significance testing~\cite{GWTC1, GWTC2}.
-In this framework, the candidates' ranking statistic is compared against a background distribution.
-The independent matched-filter searches, e.g.
-\pycbc~\cite{pycbc_og4}, \spiir~\cite{spiir} and \gstlal~\cite{sachdev2019gstlal}, and the coherent burst search \cwb~\cite{cwb} used by LVK to search for signals in gravitational-wave data all use ranking statistics in such a manner~\cite{GWTC1}.
-Both \pycbc and \gstlal's ranking statistic incorporate information of the relative likelihood that the data contains a coherent signal versus just noise.
-In contrast, \cwb's ranking statistic uses the information of coherent energy present in the network of detectors~\cite{GWTC1}.
-
-Bayesian inference offers an alternative means to rank the significance of candidate events by computing the odds that the data contain a transient gravitational-wave signal vs.
-instrumental glitches or noise~\cite{BCR1}.
-This method relies on accurate models for the signal and glitch morphologies and populations~\cite{BCR1}.
-In principle, Bayesian odds is the optimal method for hypothesis testing~\cite{BCR2}.
-Much of its power comes from the Bayesian ``evidence'': a marginalized likelihood.
-The evidence is the correct likelihood of having obtained the data given a hypothesis.
-However, due to the high computational cost to calculate the evidence, it is not explicitly used in current matched filter searches.
-Here, we explore a middle-ground hybrid between frequentist matched filtered searches and Bayesian odds.
-We compute Bayesian evidences for foreground and background data under the assumption that they either contain coherent gravitational-wave signals, noise, or glitches.
-However, instead of computing true Bayesian odds, we use the evidences to form a bootstrapped distribution for the odds of foreground and background events to form a frequentist ranking statistic.
-
-\subsection{The Bayesian Coherence Odds-Ratio}
+\subsection{Formalism}
 
@@
 \begin{equation}
-\label{eq:bcr}
+\label{eq:origbcr}
 \bcrodds = \frac{\pi^S Z^S}{\prod\limits^D_{i=1} \ [\pi^G Z^G_i + (1-\pi^G)Z^N_i]}\ ,
@@
 However, as the priors-odds are unknown, we \textit{tune} values for prior-odds, $\hat{\pi}^S$ and $\hat{\pi}^G$, to estimate \bcrodds with a ranking statistic, \bcr, given by
+\et{I would remove everything in this subsection before this point.
+Save it for your dissertation if you want, but I don't think we need to review Bayesian basics here.
+Instead, just begin by saying that we implement the BCR, which is given by Eq.~\ref{eq:bcr} with suitable references to the previous BCR papers.
+The motivation for the BCR can be summarised in a single sentence.}
 \begin{equation}
@@
 \end{equation}
-
+\et{Rewrite the remaining paragraphs to explain that how the BCR relates to the odds with just a few sentences, avoiding equations.}
 In the limit where the estimated prior-odds equal the true prior-odds, $\bcr\to\bcrodds$.
@@
 The tuning process is further described in Appendix~\ref{apdx:tuning-prior-odds}.
-
-\subsection{Estimation of astrophysical signal probability}
-Candidate \bcr-values are either statistically insignificant compared to the background \bcr distribution, implying the candidate is more probable to be an incoherent instrumental feature (the $\mathcal{H}_I$ null-hypothesis), or statistically significant relative to the background distribution, indicating the possible presence of an astrophysical signal (the $\mathcal{H}_S$ hypothesis).
-A false alarm probability with trial factors, \fap, for the candidate \bcr-value can quantify the significance.
-The \fap for a \bcr-value is the probability that a candidate originating from a non-astrophysical source can be falsely identified as a signal once in $N$ trials, and is given by
-\begin{equation}
-    \fap = 1 - (1-f)^N \ ,
-\end{equation}
-where $f$ is the probability of observing a background $\bcr'$ greater than or equal to the candidate \bcr,
-\begin{equation}
-    f = \frac{\text{Count of } \bcr' \leq \bcr}{\text{Count of } \bcr'} \ .
-\end{equation}
-
-Finally, the \fap can be used to construct a \pastro, the probability that a signal is of astrophysical origin~\cite{pastro_1,pastro_2,pastro_3}
-\begin{equation}
-    \pastro = 1 -  \fap \ .
-\end{equation}
-
-\avi{Eric, can you take a look at this section about the FAP p-astro?}
-\avi{
-The pastro calculation may need some more discussion.
-Taking pastro = 1-FAP as identifying a real signal can be hugely problematic: \url{https://en.wikipedia.org/wiki/Misuse_of_p-values}, even though its ok in this case.
-Maybe the following papers have something that can help motivate this ~\cite{Farr:2015:PhRvD, Gaebel:2019:MNRAS,Galaudage:2020:PhRvD}
-}
-
-\subsection{Data for Analysis}
-
-To rank candidate event \bcr-values we need to compute a background \bcr distribution.
-We can obtain the background data needed from the LIGO Scientific collaboration's search pipelines that scan for gravitational-waves from compact binary mergers such as \gstlal~\cite{sachdev2019gstlal}, \mbta~\cite{MBTA}, \spiir~\cite{spiir} and \pycbc~\cite{pycbc_og4}.
-The output of \pycbc's search is a list of times and their corresponding \pycbc ranking statistic \pycbcstat values.
-Whenever a local maximum of $\pycbcstat > \snr_\text{T}$, where $\snr_\text{T}$ is some predetermined threshold value, the \pycbc search pipeline produces a single-detector \textit{trigger} associated with the detector and time $t_c$ where the apparent signal in the data has its merger~\cite{pycbc_og6}.
-\pycbc produces three categories of triggers:
-\begin{itemize}
-    \item \textit{Candidate event trigger}: a trigger observed with coincident parameters amongst a network of detectors. 
-    \item \textit{Simulated trigger}: a trigger detected from an artificially manufactured signal injected into detector data.  
-    \item \textit{Background trigger}: a trigger obtained from incoherent signal-free background data (data manufactured by applying relative offsets, or time-slides, between the data of different detectors~\cite{pycbc_og6}).
-\end{itemize}
-
-After obtaining these triggers from \pycbc, we can calculate the trigger's \bcr-values and use them to measure candidate triggers' statistical significance.
-The \bcr can be a powerful ranking statistic as it incorporates information of not only all possible binary black hole systems that might have merged to produce the trigger but also the various incoherent glitches that might cause a false-detection~\cite{BCR1}.
-
-% \avi{Should I mention that we need \pycbc  as a pre-selection step to computing? }
-
-\section{Analysis}\label{sec:Analysis}
-
-\subsection{Acquisition of triggers}
-Advanced LIGO's second observing run O2 lasted $38$ weeks~\cite{GWOSC}.
-The software package, \pycbc~\cite{pycbc_code}, was used by LVK to process the O2 data in 22 time-frames (approximately 2 weeks per frame) and found several gravitational-wave events and numerous gravitational-wave candidates~\cite{pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6}.
-Some candidate events were vetoed to be glitches, while others were rejected due to their low significance.
-The data are divided into these time-frames because the detector's sensitivity does not stay constant throughout the eight-month-long observing period.
-
-In addition to finding candidate events, \pycbc also identified several million background triggers for each time-frame, by searching background data manufactured by time-sliding data within that time-frame.
-The background triggers help quantify the candidate events' significance for the respective time-frames.
-Finally, to test the search's sensitivity, \pycbc produced and searched for thousands of simulated signals.
-% \avi{Do i need to contextualize this choice more, ie talk about what would happen if I chose a narrower range?}
-
-For our study, we filter the \pycbc background, simulated and candidate triggers to include only triggers in the ranges of the parameters presented in Table~\ref{tab:parameters}.
-Filtering triggers to this region focuses our analysis to binary black hole mergers with total masses above $> 55 \msun$.
-This corresponds to binary systems with signal durations $<454 \ \text{ms}$, signals which may be mistaken for short-duration glitches.
-A plot of the \pycbc triggers from one time-frame, during April 23 - May 8, 2017, is presented in Fig.~\ref{fig:templateBank}.
-This figure also depicts the gravitational-wave templates used by \pycbc's search through this time-frame of data.
-
-\begin{table}[t]
-
-\caption[BBH parameters correspond to duration $<454\ \text{ms}$]{\label{tab:parameters}Trigger-selection parameter space (parameters correspond to signals with durations $<454 \ \text{ms}$). }
-\centering
-\begin{tabular}{lrr}
-\toprule
-  & Minimum & Maximum\\
-\midrule
-Component Mass 1 [\msun] & 31.54 & 491.68\\
-Component Mass 2 [\msun] & 1.32 & 121.01\\
-Total Mass [\msun] & 56.93 & 496.72\\
-Chirp Mass [\msun] & 8.00 & 174.56\\
-Mass Ratio & 0.01 & 0.98\\
-\end{tabular}
-\end{table}
-
-\begin{figure*}[!ht]
-
-{\centering \includegraphics[width=0.75\linewidth]{images/template_bank.png}
-
-}
-% time for chunk 14
-% 1176955218, Apr 23, 2017, 4:00 UTC
-% 1178294418, May 08, 2017, 16:00 UTC
-\caption[ BCR search space.]{The templates (pink) used by \pycbc to search a section of O2 data from $\text{April 23 - May 8, 2017}$.
-Our search is constrained to the parameter space enclosed by the dashed line.
-The candidate, background and simulated triggers detected in this region of the parameter space during this period are plotted in orange, gray and blue respectively.}\label{fig:templateBank}
-\end{figure*}
-
-\subsection{Calculating the BCR for triggers}
-To evaluate $Z^S$, $Z^G_i$ and $Z^N_i$ and calculate the \bcr Eq.~\ref{eq:bcr} for triggers, we carry out Bayesian inference with \bilby~\cite{bilby, bilby_pipe}, employing \dynesty~\cite{dynesty} as our nested sampler.
-Nested sampling, an algorithm introduced by~\citet{skilling2004, skilling2006}, provides an estimate of the Bayesian evidence and is often utilized for parameter estimation within the LIGO collaboration~\cite{bilby, bilby_paper, pbilby_paper}.
-
-The most computationally intensive step during Bayesian inference is evaluating the likelihood $\mathcal{L}(d_i|\template)$.
-To accelerate our analysis, we use a likelihood that explicitly marginalizes over coalescence time, phase at coalescence, and luminosity distance (Eq.~80 from~\citet{intro_to_gw_bayes}).
-
-We set the priors $\pi(\parameters|\mathcal{H}_S)$ and $\pi(\parameters|\mathcal{H}_G)$ to be identical which reflects our ignorance of the distribution of the population properties of signals and signal-like glitches.
-These priors restrict signals with mass parameters in the ranges presented in Table~\ref{tab:parameters}.
-The spins are aligned over a uniform range for the dimensionless spin magnitude from $\left[0,1\right]$.
-The luminosity distance prior assigns probability uniformly in comoving volume, with an upper cutoff of $5\ \text{Gpc}$.
-The full list of the priors, along with their shapes, limits and boundary conditions are documented in Table~\ref{tab:priors}.
-
-\begin{table}
-    \centering
-    \caption{
-    Prior settings for the parameters used during our parameter estimation.
-The definitions of the parameters are documented in \citet{bilby_gwtc}~Table~E1.
-The trigger time $t_c$ is obtained from the data products of \pycbc's O2 search.
-\label{tab:priors}}
-    \begin{tabular}{c c c c}
-    \hline
-    Parameter & Shape & Limits \\
-    \hline
-          $\mathcal{M}/\msun$           & Uniform & 7--180  \\
-          $q$                           & Uniform & 0.1--1  \\
-          $M/\msun$                     & Constraint & 50--500  \\
-          $d_\mathrm{L}/\mathrm{Mpc}$   & Comoving & 100--5000  \\
-          $a_1$, $a_2$                  & Uniform & 0--1  \\
-          $\theta_{JN}$                 & Sinusoidal & 0--$\pi$  \\
-          $\psi$                        & Uniform & 0--$\pi$  \\
-          $\phi$                        & Uniform & 0--$2\pi$  \\
-          ra                            & Uniform & 0--$2\pi$  \\
-          dec                           & Cosine & 0--$2\pi$  \\
-          $t_c/\mathrm{s}$              & Uniform & $t_c\pm0.1$  \\
-    \hline
-    \end{tabular}
-\end{table}
-
-The waveform template we utilize is \imrphenomp, a phenomenological waveform template constructed in the frequency domain that models the in-spiral, merger, and ring-down (IMR) of a compact binary coalescence~\citep{khan2016frequency}.
-Although there exist gravitational-wave templates such as \imrxhm~\cite{imrphenompxhm}, \nrsur~\cite{nrsur7dq4} and \seob~\cite{seobnrv4phm} which incorporate more physics, such as information on higher-order modes, we use \imrphenomp as it is computationally inexpensive compared to others.
-
-To generate the PSD, we take 31 neighboring off-source non-overlapping  4-second  segments of time-series data before the analysis data segment $d_i$.
-To suppress spectral leakage, a Tukey window with a 0.2-second roll-off is applied to each data segment .
-After this the segments are fast-Fourier transformed and median-averaged to create a PSD~\cite{ligo_psd}.
-Like other PSD estimation methods, this method adds statistical uncertainties to the PSD~\cite{psd_student_t, chatziioannou2019noise, Biscoveanu:2020:PhRvD}.
-To marginalize over the statistical uncertainty, we use the median-likelihood presented by~\citet{psd_student_t} as a post-processing step.
-We find that this post-processing step improves the search efficiency by $49.26\%$ the details of this calculation are presented in the Appendix~\ref{sec:psd-marginalization}.
-
-Finally, we acquire the foreground, background and data in which we inject simulated signals into, from from the gravitational-wave Open Science Center~\cite{GWOSC}.
-The data we use are the publicly accessible O2 strain data from the Hanford and Livingston detectors, recorded while the detectors are in ``Science Mode''.
-We obtain the data using \gwpy~\cite{gwpy}.
-
-\subsection{Assigning \pastro to candidate events}
-After calculating the \bcr for the entire set of background and simulated triggers, we calculate the background and simulated \bcr probability distributions for each 2-week time-frame of O2 data.
-These distributions are used to `tune' prior-odd $\hat{\pi}^S$ and $\hat{\pi}^G$ values as described in Appendix~\ref{apdx:tuning-prior-odds}.
-
-Using the tuned prior-odds the \bcr for the candidate events can be calculated.
-Fig.~\ref{fig:bcrCdf} shows the \bcr distributions for the background triggers, simulated triggers and candidate events.
-The bulk of the background and simulated trigger distributions are separate but slightly overlap due to some of the simulated signal's being very faint.
-The separation suggests that the \bcr can successfully distinguish signals from noise or glitches.
-The vertical lines in Fig.~\ref{fig:bcrCdf} displays the \bcr for gravitational-wave candidate events.
-On comparing the candidate event \bcr values with the background distribution, we can estimate \pastro values for the candidate events.
-
-\begin{figure}[!ht]
-{\centering \includegraphics[width=0.85\linewidth]{images/reweighted_bcr_cdf_smaller_legend.png} }
-\caption[BCR distribution example]{Histograms represent the survival function (1-CDF) from our selection of background triggers (gray) and simulated signals (blue) triggers obtained from \pycbc's search of data from $\text{August 13 - 21, 2017}$.
-Vertical lines mark the $\text{ln}\ \bcr$ of \IAS's GW170817A and \GWTC's GW170814.}\label{fig:bcrCdf}
-\end{figure}
-
-\section{\label{sec:Results}Results}
-
-\input{Data/results_table}
-We analyze the $60,996$ background, $5,146$ simulated, and $25$ candidate triggers reported by \pycbc's search on the data from LIGO's second observing run, restricting our analysis to the triggers that fall within our mass-space as described in Section~\ref{sec:method}.We also analyze events and candidate events reported by \GWTC and the \IAS group (note: some of these were identified as candidates by the \pycbc search).
-Table~\ref{tab:results} summaries the \pastrobcr, along with the \pastro of other pipelines for comparison.
-Although the various pipeline \pastro are not mathematically equivalent, by comparing pipeline \pastro values for a given candidate, we can compare how significant each pipeline deems various candidates.
-The $\hat{\pi}^S$ and $\hat{\pi}^G$ values utilized for each time-frame are reported in Appendix~\ref{apdx:alphabeta}.
-
-\subsection{GWTC-1 Events}
-All the confirmed gravitational-wave events from binary black hole mergers reported in \GWTC and within our prior space, (specifically GW170104, GW170608, GW170729, GW170809 and GW170814), have $\pastrobcr>0.9$, indicating a high probability of an astrophysical signal.
-
-In addition to the above confirmed gravitational-wave events from \GWTC, we have also analyzed several candidate events from \GWTC, most of which have low \pastrobcr.
-For example, consider the candidate event 170412, assigned a $\pastro$ of $0.06$ by \gstlal and has a $\pastrobcr$ of $0.01$.
-This candidate was reported to be excess power caused due noise appearing non-stationary between 60-200 Hz~\cite{GWTC1}.
-This candidate acts as an example of how $\pastrobcr$ may be utilized to eliminate candidates originating from terrestrial noise sources.
-
-\subsection{IAS Events}
-Our analysis of the IAS events and candidates with $M_T>55\ \msun$ in O2 has resulted in three events with disfavored $\pastrobcr<0.5$ (GWC170402, GW170403, GW170425), and four events and one candidate with $\pastrobcr\geq0.5$ (GW170121, 170302, GW170304, GW170727, GW170817A).
-While GW170727 and GW170817A's \pastrobcr are similar to the \pastro reported from IAS (the differences between the \pastro from \bcr and IAS is $|\Delta \pastro|<0.1$), the remaining candidates have opposing \pastro values (with $|\Delta \pastro| > 0.15$).
-
-GWC170402, detected by \citet{IAS2}, is reported to originate from a binary with non-zero eccentricity~\cite{IAS2}.
-Hence, we might have computed a low \pastrobcr due to our usage of \imrphenomp, a waveform that does not account for eccentricity.
-Additionally, the search conducted by \citet{IAS2} was a single-detector search.
-Our ranking statistic relies on the signal to appear coherent, even if just faintly coherent, amongst the various detectors to have a high \pastrobcr.
-The lack of coherence and the non-eccentric waveform may be the leading factors for a low \pastro.
-GW170403 and GW170425 which have $\pastrobcr<0.35$ also have low  \pastro reported by \citet{pycbc_ogc_2},  suggesting that these events may have been false alarms.
-
-From the candidates with $\pastrobcr>0.5$, GW170727 and 170302 are of particular interest, with \pastrobcr of $0.92$ and $0.63$.
-GW170727 was emitted from a black hole binary system with a source frame total mass $\approx 70\ \msun$.
-In addition to the high \pastrobcr reported by our study, \citet{IAS1} and \citet{pycbc_ogc_2} have also reported high \pastro values of 0.98 and 0.99, making it a viable gravitational-wave event candidate.
-Similarly, the sub-marginal-candidate 170302 reported by \cite{IAS1} with a \pastro of 0.45 appears to have a higher significance from our analysis, resulting in a \pastrobcr of $0.63$.
-
-\subsection{New Candidate Events}
-Although no clear detections are made with the \bcr, a marginal-candidate 170222 has been discovered with a $\pastrobcr\sim0.5$.
-This candidate has an SNR$\sim7.7$, low spin magnitudes and source-frame component masses of $({47.16}_{-5.77}^{+8.00}, {35.50}_{-6.35}^{+5.79}) \msun$, making it one of the heavier black-hole mergers from O2 and \GWTC.
-This candidate may be of interest as one component black hole may lie in the pair-instability mass gap ($55^{+10}_{-10}-148^{+13}_{-12}\msun$)~\cite{Woosley:2021:arXiv, Heger:2002:ApJ}.
-More details on the candidate are presented in Appendix~\ref{apdx:170222}.
-The remaining coherent trigger candidates all have $\pastrobcr\ll0.5$ making them unlikely to originate from astrophysical sources.
-
-\section{\label{sec:Conclusion}Conclusion}
-
-Until 2016, a majority of intermediate-mass black hole candidates were from electromagnetic observations.
-The dawn of gravitational wave astronomy has provided a new lens to identify and study these massive objects -- from the mergers of heavy black holes' gravitational wave emission.
-In the future, space-based gravitational wave detectors will uncover black holes in the upper end of the intermediate-mass range.
-In the present, ground-based gravitational-wave observatories can probe the lower-end of the intermediate-mass range.
-However, many short-duration terrestrial artifacts that mimic intermediate-mass gravitational-wave signals plague ground-based detectors, making intermediate-mass detection challenging.
-
-In this paper, we demonstrate that the Bayesian Coherence Odds-Ratio \bcr~\cite{BCR1} can be used as a ranking statistic to provide a measure of significance for gravitational wave signals originating from CBCs with total masses between $55\msun$ and $400\msun$, a range that includes intermediate-mass black holes.
-To compute the \bcr for candidates, we utilize Bayesian inference to explicitly calculate the probability of data under various hypotheses (the hypotheses that the data contains a coherent signal, just noise, or an incoherent glitch).
-This Bayesian ranking method takes a step towards building a unified Bayesian framework that provides a search-pipeline agnostic measure of significance for candidates and estimates their parameters, utilizing the same level of physical information incorporated during detected parameter estimation studies.
-
-In our study, we analyze O2 binary-black hole events and candidates with $M_T > 55 \msun$ reported by the \pycbc search~\cite{pycbc_ogc_2}, the \IAS-team~\cite{IAS1, IAS2} and those reported in \GWTC~\cite{GWTC1}.
-Using \pastrobcr, we find that the \GWTC events have high probabilities of originating from an astrophysical source.
-We also find that some of the \GWTC marginal triggers that have corroborated terrestrial sources (for example, candidate 170412) have low \pastrobcr, indicating this method's ability to discriminate between terrestrial artifacts and astrophysical signals.
-Our analysis of the \IAS events demonstrates that GW170121, GW170727, and GW170817A are likely to originate from astrophysical sources, while GWC170402, GW170402, and GW170425  are not.
-Finally, we do not identify any new gravitational-wave events, but we find a new marginal binary-black hole merger candidate, 170222.
-
-Although our analysis targets triggers with $M_T > 55 \msun$, this method can be extended to include the entire range of LIGO-detectable gravitational-wave sources.
-Additionally, to further improve the method's infrastructure, we can use more robust gravitational-wave templates (such as templates that incorporate higher-order modes and orbital precession) and sophisticated glitch models.
-Future analysis can also incorporate data from all available detectors in a network to increase the sensitivity of \pastrobcr.
-
-% \greg{can we better constraint their population properties? Do we know how much (if at all) this method outperforms current searches?}
-
-% \avi{Unlike for stellar-mass BBH, there are still alot of uncertainties for IMBH formation scenarios.
-Hence, upper limits would be challenging to calculate.
-Additionally, we would require to do more robust simulation studies to see what would fall in/outside our detection threshold, to put constraints on population properties and study the search's sensitivity
-% }
-
-%%%%%%---SECTIONS-END---%%%%%%%%%%%%
-
-%%%%%%---ACKNOWLEDGMENTS---%%%%%%%%%%%%
-\begin{acknowledgments}
-
-The author gratefully thank the \pycbc team for providing the gravitational-wave foreground, background and simulated triggers from \pycbc's search of O2's data.
-We also warmly thank Ian Harry and Thomas Dent for answering questions about the \pycbc search's data products.
-
-We thank Stuart Anderson for assistance with accommodating this analysis which was performed on the California Institute of Technology computing cluster.
-All analyses (inclusive of test and failed analyses) performed for this study used $~1.3\mathrm{M}$ core-hours, amounting to a carbon footprint of $~167\ \mathrm{t}$ of CO$^2$ (using the US average electricity source emissions of $0.429\ \text{kg/kWh}$~\cite{greenhouse} and $0.3\ \text{kWh}$ for each CPU).
-
-This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open Science Center (https://www.gw-openscience.org), a service of LIGO Laboratory, the LIGO Scientific Collaboration and the Virgo Collaboration.
-LIGO is funded by the U.S.
-National Science Foundation.
-Virgo is funded by the French Centre National de Recherche Scientifique (CNRS), the Italian Istituto Nazionale della Fisica Nucleare (INFN) and the Dutch Nikhef, with contributions by Polish and Hungarian institutes.
-
-\end{acknowledgments}
-%%%%%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
-\section{Bayesian Evidence Evaluation}\label{sec:bayesianEvidEval}
-\subsection{Noise Model}
-We assume that each detector's noise is Gaussian and stationary over the period being analyzed~\cite{ligo_psd}.
-In practice, we assume that the noise has a mean of zero that the noise variance $\sigma^2$ is proportional to the noise power spectral density (PSD) \psd of the data.
-Using the \psd, for each frequency-domain data segment $d_i$ in each of the $i$ detectors in a network of $D$ detectors, we can write
-\begin{equation}
-\label{eq:zn}
-Z^N_i = \mathcal{N}(d_i|\mu=0,\sigma^2=\psd),
-\end{equation}
-where $\mathcal{N}$ is a normal distribution.
-
-\subsection{Coherent Signal Model}
-We model coherent signals using a binary black hole waveform template \template, where the vector \parameters contains a point in the 12 dimensional space describing aligned-spin binary-black hole mergers.
-For the signal to be coherent, \parameters must be consistent in each 4-second data segment $d_i$ for a network of $D$ detectors.
-Hence, the coherent signal evidence is calculated as
-\begin{equation}
-\label{eq:zs}
-Z^S = \int\limits_{\parameters} \prod\limits^{D}_{i=1} \left[ \mathcal{L}(d_i|\template)\right] \pi(\parameters | \mathcal{H}_S)\  \text{d}\parameters \ ,
-\end{equation}
-where $\pi(\parameters| \mathcal{H}_S)$ is the prior for the parameters in the coherent signal hypothesis, and $\mathcal{L}(d_i|\template)$ is the likelihood for the coherent signal hypothesis that depends on the gravitational-wave template \template and its parameters \parameters.
-
-\subsection{Incoherent Glitch Model}
-Finally, as glitches are challenging to model and poorly understood, we follow \citet{bci} and utilize a surrogate model for glitches: the glitches are modeled using gravitational-wave templates  \template with uncorrelated  parameters amongst the different detectors such that  $\parameters_i \neq \parameters_j$ for two detectors $i$ and $j$~\cite{bci}.
-Modeling glitches with \template captures the worst case scenario: when glitches are identical to gravitational-wave signals (excluding coherent signals).
-Thus, we can write $Z^G_i$ as
-\begin{equation}
-\label{eq:zg}
-Z^G_i = \int\limits_{\parameters} \mathcal{L}(d_i|\template)\ \pi(\parameters| \mathcal{H}_G)\  \text{d}\parameters  \ ,
-\end{equation}
-where $\pi(\theta| \mathcal{H}_G)$ is the prior for the parameters in the incoherent glitch hypothesis.
-
-\section{Tuning the prior-odds}\label{apdx:tuning-prior-odds}
-
-After calculating the \bcr for a set of background triggers and simulated triggers from as stretch of detector-data (a data chunk), we can compute probability distributions for the background and simulated triggers, $p_b(\bcr)$ and $p_s(\bcr)$.
-We expect the background trigger and simulated signal \bcr values to favor the incoherent glitch and the coherent signal hypothesis, respectively.
-Ideally, these distributions representing two unique populations should be distinctly separate and have no overlap in their \bcr values.
-The prior odds parameters $\hat{\pi}^S$ and $\hat{\pi}^G$ from Eq.~\ref{eq:bcr} help separate the two distributions.
-Altering $\hat{\pi}^S$ translates the \bcr probability distributions while adjusting $\hat{\pi}^G$ spreads the distributions (refer to Appendix A of \citet{BCR1}).
-Although Bayesian hyper-parameter estimation can determine the optimal values for $\hat{\pi}^S$ and $\hat{\pi}^G$, an easier approach is to adjust the parameters for each data chunk's \bcr distribution.
-In this study, we tune $\hat{\pi}^S$ and $\hat{\pi}^G$ to maximally separate the \bcr distributions for the background and simulated triggers.
-
-To calculate the separation between $p_b(\bcr)$ and $p_s(\bcr)$, we use the Kullback--Leibler divergence (KL divergence) $D_{KL}$, given by
-\begin{equation}
-    D_{KL}(p_b | p_s) = \sum\limits_{x\in \bcr} p_b(x) \log \left( \frac{p_b(x)}{p_a(x)} \right)  \ .
-\end{equation}
-The $D_{KL}=0$ when the distributions are identical and increases as the asymmetry between the distributions increases.
-
-We limit our search for the maximum KL-divergence in the $\hat{\pi}^S$ and $\hat{\pi}^G$ ranges of $[10^{-10}, 10^0]$.
-We set our values for $\hat{\pi}^S$ and $\hat{\pi}^G$ to those which provide the highest KL-divergence and calculate the \bcr for candidate events present in this data chunk.
-Note that we conduct the analysis in data chunks of a few days rather than an entire data set of a few months as the background may be different at different points of the entire data set.
-
-\section{Marginalizing over PSD statistical uncertainties}\label{sec:psd-marginalization}
-To generate the results in Fig.~\ref{fig:bcrCdf}, we applied a post-processing step to marginalize the uncertainty in the PSD.
-In Fig.~\ref{fig:bcrCdfUnmarginalized}, we show the results if this post-processing step is not applied.
-Clearly, marginalizing over uncertainty in the PSD yields an improvement in the separation of the noise and signal distributions.
-Quantitatively, at a threshold $\bcr^T=0$ the post-processing step results in a reduction in the number of background $\bcr > \bcr^T$ from $60.7\%$ to $25.28\%$ in the August 13 - 21, 2017 time-frame of data.
-For the entirety of O2 PSD marginalization resulted in a $49.26\%$ improvement in search efficiency.
-
-\begin{figure}[!ht]
-{\centering \includegraphics[width=0.85\linewidth]{images/orig_bcr_cdf_smaller_legend.png} }
-\caption[BCR distribution example]{This plot is analogous to Fig.~\ref{fig:bcrCdf}, but without using the post-processing step to marginalize over PSD statistical uncertainties.
-Without the post-processing step, there is a greater overlap between the background (gray) and foreground (blue) survival functions.
-For more details about this plot, refer to the caption of Fig.~\ref{fig:bcrCdf}.}\label{fig:bcrCdfUnmarginalized}
-\end{figure}
-
-\section{Tuned prior odds}\label{apdx:alphabeta}
-
-O2 lasted several months over which the detector's sensitivity varied.
-Hence, a part of our analysis entailed tuning the prior odds for obtaining a signal and a glitch, $\hat{\pi}^S$ and $\hat{\pi}^G$, as described in Section~\ref{sec:method}.
-Table~\ref{tab:priorodds} presents the signal and glitch prior odds utilized for each time-frame of O2 data.
-\input{Data/alpha_beta_table}
-
-Tuning the prior odds can dramatically affect the \pastrobcr.
-For example, consider Table~\ref{tab:tuningresults}, which reports tuned \pastrobcr and un-tuned \untunedpastrobcr (where $\hat{\pi}^S=1$ and $\hat{\pi}^G=1$) for various events and candidates.
-By tuning the prior odds, the \pastrobcr for some IAS events (for example, GW170403 and GW170817A) can change by more than 0.5, resulting in the promotion/demotion of a candidate's significance.
-
-\input{Data/tuning_results_table}
-
-\section{A closer look at 170222}\label{apdx:170222}
-PyCBC found the candidate 170222 with $\mathcal{M}_c=49.46$ and $q=0.68$, values that fall within our uncertainty limits.
-Some of the posteriors that were produced as a by-product of our \bcr calculation can be viewed in Fig.~\ref{fig:170222}.
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}
-        \centering
-        \includegraphics[width=0.45\linewidth]{170222_prior_posterior.png}
-    \end{subfigure}
-    ~ 
-    \begin{subfigure}
-        \centering
-        \includegraphics[width=0.45\linewidth]{170222_source_posterior.png}
-    \end{subfigure}
-    \caption{Posterior distributions for 8 parameters of 170222. 
-    Left: Posterior probability distributions for 4 of the 12 search parameters.
-    Right: Posterior probability distributions for 4 derived parameters.
-    \label{fig:170222}}
-\end{figure*}
-
-% \section{EXTRA INTRO MATERIAL}
-
-% Given the existence of supermassive black holes detected in the early universe, it is likely for intermediate-mass black holes to have also existed~\cite{Banados:2018:Natur, Askar et al  2020,}.
-However, we only have a handful of promising candidates~\cite{Greene:2004:ApJ, Graham:2013:ApJ, Mezcua:2017:IJMPD, Koliopanos:2017:mbhe, Lin:2020:ApJL, Greene:2020:ARA&A}, and two confirmed intermediate-mass black holes, (i) the $142^{+28}_{-16}\ \msun$ remnant observed from the gravitational wave event GW190521~\cite{Abbott:2020:PhRvL}, and the $5.5^{+1.7}_{-0.9}\times10^{4}\ \msun$ black hole identified from gravitational lensing in the light curve of GRB950830~\cite{paynter_evidence_2021}.
-The concrete discovery of more intermediate-mass black holes will bridge the observational gap and illuminate our understanding of galaxy and supermassive black hole formation.
-Additionally, a catalog of observed intermediate-mass black holes can act as probes to their formation environments, such as in the accretion disks of active galactic nuclei~\cite{}, the centers of dense stellar clusters~\cite{}, and even Population-III stars~\cite{}.
-
-% However, measuring the mass of black holes can be challenging. Several observational techniques to identify intermediate mass black holes
-
-% It is possible to measure the mass of nearby supermassive black holes by directly observing the dynamic motion of stars nearby the supermassive black hole (such as Sgr A$^*$~).
-However, this dynamic measurement method is challenging to utilize for  intermediate-mass black holes as their sphere of influence is too small to resolve motions~\cite{}.
-Additionally, dynamic-measurements that have alluded to  intermediate-mass candidates, e.g.
-the candidate at the center of the globular cluster 47 Tucanae~\cite{kiziltan2017}, can also be attributed to simpler models without a central intermediate-mass black hole~\cite{freire 2017}.
-}}
-
-% \rs{\sout{In a similar vein, although the M-$\sigma$ and M-L relations (relations between the spheroidal bulge of a galaxy's velocity dispersion $\sigma$,  luminosity L, and its central black hole's mass M) can estimate the mass of supermassive black holes~\cite{Ferrarese & Merritt 2000 and Gebhardt et al.
-2000}, they cannot accurately estimate the intermediate-masses.
-The M-$\sigma$ and M-L relations are not calibrated for low-mass galaxies that might host an central intermediate-mass black hole~\cite{J.
-E.
-Greene and L.
-C.
-Ho The Mass Function of Active Black Holes in the Local Universe, E.
-C.
-Moran, K.
-Shahinyan, H.
-R.
-Sugarman, D.
-O.
-Vélez and M.
-Eracleous Black Holes At the Centers of Nearby Dwarf Galaxies}.
-Table 2 of~\citet{mercuza} displays a list of intermediate-mass candidates found with these relations.
-}}
-
-% \rs{\sout{Another method to estimate large black hole masses is with reverberation mapping, which estimates black hole virial masses by studying their nearby gasses' velocities~\cite{reverberation mapping}.
-Reverberation mapping has shown to estimate both supermassive black hole and intermediate-mass black hole virial masses successfully.
-However, this method fails to measure the systematic uncertainties on the lower-end of the intermediate-mass spectrum~\cite{}.
-Additionally, cloud-variability and the possibility of anisotropic emission deride the credibility of intermediate-mass candidates found with reverberation mapping~\cite{}.
-}}
-
-% The most promising intermediate-mass candidates found with electromagnetic-spectra are Ultra-Luminous X-ray sources with luminosities $> 10^{39} \text{erg s}^{-1}$ (e.g.
-HLX-X1)~\cite{}.
-\rs{\sout{While stellar mass black holes are too small to generate such luminosities with Eddington accretion, intermediate mass black holes can accrete at rates large enough to account for the high luminosities~\cite{}.
-However, some argue that some stellar mass black holes may exceed the Eddington limit~\cite{}, and others argue that the X-ray emission might be from a collimated jet leading to an inaccurate mass calculation~\cite{}.}}
-
-\bibliography{high_mass_bib}% Produces the bibliography via BibTeX.
-
-\end{document}
-%
-% ****** End of file apssamp.tex ******

### 2021-06-15 main.tex
submission to dcc

@@
 \newcommand{\bcr}{\mathcmd{\rho_\text{BCR}}}
+\newcommand{\bgrdbcr}{\mathcmd{\rho_\text{BCR}^\textit{b}}}
+\newcommand{\candbcr}{\mathcmd{\rho_\text{BCR}^\textit{c}}}
+
 \newcommand{\bcrodds}{\mathcmd{\mathcal{O}_{\mathrm{BCR}}}}
@@
 \newcommand{\template}{\mathcmd{\mu(\parameters)}}
-\newcommand{\fap}{\mathcmd{\text{FAP}}}
+\newcommand{\fap}{\mathcmd{p_N}}
 
 \newcommand{\pastro}{\fancytext{p_\text{astro}}}
-\newcommand{\pastrobcr}{\fancytext{p_\text{astro}^{\text{BCR}}}}
-\newcommand{\untunedpastrobcr}{\fancytext{p_\text{astro}^{\text{BCR}\prime}}}
+\newcommand{\pastrobcr}{\fancytext{p_\text{S}}}
+\newcommand{\untunedpastrobcr}{\fancytext{p_\text{S}^{\prime}}}
 \newcommand{\pastroext}{\fancytext{p_\text{astro}^{\text{ext}}}}
@@
 
-\title{A search for intermediate mass black holes mergers in the \\second LIGO--Virgo observing run with the Bayes Coherence Ratio}
+\title{A search for intermediate-mass black holes mergers in the \\second LIGO--Virgo observing run with the Bayes Coherence Ratio}
 
@@
 
-% \avi{Say why it improves on prev techniques}
-
 \maketitle
@@
 \section{Introduction}
-Since the 1970s, there has been a steady accumulation of evidence for stellar mass ($M_\text{BH} < 10^{2} \ \msun$) and supermassive black holes ($M_\text{BH} > 10^{6} \ \msun$)~\cite{Webster:1972:Natur, Balick:1974:ApJ, Ghez:1998:ApJ, Genzel:2010:RvMP, Abbott:2019:PhRvX, EventHorizonTelescopeCollaboration:2019:ApJL, Abbott:2020:arXiv}.
+
+A variety of techniques have been employed to search for $10^{4} - 10^{6}\ \msun$ intermediate-mass candidates including reverberation mapping~\cite{Peterson:2014:SSRv}, direct kinematic measurements~\cite{Schodel:2002:Natur, Kiziltan:2017:Natur}, applying macroscopic galaxy to black hole mass scaling relations ($M_{BH}$-$\sigma$ and $M_{BH}$-L relations)~\cite{Graham:2013:ApJ, Wevers:2017:MNRAS}, studying  X-ray luminosity and spectra~\cite{Greene:2004:ApJ, Lin:2020:ApJL}, gravitational lensing of gamma-ray burst light curves~\cite{paynter_evidence_2021}, and others~\cite{Greene:2020:ARA&A, Koliopanos:2017:mbhe, Mezcua:2017:IJMPD}).
+However, because intermediate-mass black holes have smaller gravitational spheres of influence than those of supermassive black holes, it is much more challenging to observe them with these observational techniques~\cite{Mezcua:2017:IJMPD}.
+Additionally, the numerous intermediate-mass black hole candidates discovered using these techniques are ambiguous as other sources can describe observations from the candidates (e.g., light sources orbiting clusters of stellar-mass black holes~\cite{Ridolfi:2016:MNRAS, Freire:2017:MNRAS}, anisotropic emission from neutron stars~\cite{Israel:2017:MNRAS, RodriguezCastillo:2020:ApJ}).
+
+Stellar mass ($M_\text{BH} < 10^{2} \ \msun$) and supermassive black holes ($M_\text{BH} > 10^{6} \ \msun$) have been observed and well studied since the 1970s~\cite{Webster:1972:Natur, Balick:1974:ApJ, Ghez:1998:ApJ, Genzel:2010:RvMP, Abbott:2019:PhRvX, EventHorizonTelescopeCollaboration:2019:ApJL, Abbott:2020:arXiv}.
 However, there is a deficiency of observational evidence for black holes in the intermediate-mass range $10^{2} - 10^{6}\ \msun$.
@@
 
-A variety of techniques have been employed to search for $10^{4} - 10^{6}\ \msun$ intermediate mass candidates including reverberation mapping~\cite{Peterson:2014:SSRv}, direct kinematic measurements~\cite{Schodel:2002:Natur, Kiziltan:2017:Natur}, applying macroscopic galaxy to black hole mass scaling relations ($M_{BH}$-$\sigma$ and $M_{BH}$-L relations)~\cite{Graham:2013:ApJ, Wevers:2017:MNRAS}, studying  X-ray luminosity and spectra~\cite{Greene:2004:ApJ, Lin:2020:ApJL}, gravitational lensing of gamma-ray burst light curves~\cite{paynter_evidence_2021}, and others~\cite{Greene:2020:ARA&A, Koliopanos:2017:mbhe, Mezcua:2017:IJMPD}).
-However, these observational techniques are challenging to use for intermediate mass black holes due to their small sphere of influence compared to super-massive black holes~\cite{Mezcua:2017:IJMPD}.
-Additionally, some IMBH candidates can be attributed to sources other than intermediate-mass black holes (e.g., clusters of stellar-mass black holes~\cite{Ridolfi:2016:MNRAS, Freire:2017:MNRAS}, anisotropic emission from neutron stars~\cite{Israel:2017:MNRAS, RodriguezCastillo:2020:ApJ}), while others have high uncertainties intrinsic to the observational techniques~\cite{Greene:2020:ARA&A}.
-\et{Consider replacing previous sentence that says none of the current IMBH candidates are widely accepted within the astronomical community as unambiguous.}
-
-Compact binary coalescences (CBCs) can provide unambiguous gravitational-wave signals for intermediate-mass candidates (e.g., the $142^{+28}_{-16}\ \msun$ remnant observed from the gravitational wave event GW190521~\cite{Abbott:2020:PhRvL}).
+Compact binary coalescences (CBCs) can provide unambiguous gravitational-wave signals for intermediate-mass candidates e.g., the $142^{+28}_{-16}\ \msun$ remnant observed from the gravitational-wave event GW190521~\cite{Abbott:2020:PhRvL} and other candidates~\cite{ligo_imbh_search, ligo_imbh_o3, pycbc_imbh}.
 As a binary's total mass $\text{M}_{T}$ is associated with its gravitational-wave merger frequency, $f\sim \text{M}_{T}^{-1}$,  ground-based gravitational-wave detectors ($f\sim 10^1 - 10^3\ \text{Hz}$) are sensitive to the last milliseconds of merging systems with $100 \msun < \text{M}_{T} < 400 \msun$~\cite{LIGOScientificCollaboration:2015:CQGra, Martynov:2016:PhRvD, Moore_2014}, while space-based detectors ($f \sim 10^{-2} - 10^1\ \text{Hz}$) can study the full signals of merging systems with $10^4 \msun < \text{M}_{T} < 10^7 \msun$~\cite{ Moore_2014, Lu:2019:PhRvD}.
@@
 One method to discriminate more glitches while searching for CBC is the Bayesian odds~\cite{bci, kanner2016leveraging, BCR1, BCR2, bcr_gw151216, bayesian_odds}.
-\et{Need sentence here saying we are inspired by the Bayesian odds to develop a ranking statistic that incorporates some of the ideas used in the odds.} In this paper, we rank O2's candidate gravitational-wave signals from $55-500\ \msun$ (\et{lab frame}) total mass systems using a ranking statistic called the Bayesian Coherence Ratio \bcr~\cite{BCR1}.
-\et{I deleted some text here going into detail about the BCR; save for method section.} For each candidate, we calculate the probability of astrophysical origin, \pastrobcr and compare to candidate events reported by other authors including the LIGO-Virgo-KAGRA (LVK) collaboration in \GWTC~\cite{GWTC1}, the \pycbc-team~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6, pycbc_single_det, pycbc_ogc_2}, by the Institute of Advanced study's team (\IAS)~\cite{IAS0, IAS1, IAS2}, or by \citet{bayesian_odds}.
-\et{Deleted several sentences here about innovations that I think are in the weeds.}
+The Bayesian Coherence Ratio \bcr~\cite{BCR1,BCR2} is a Bayesian odds comparing the probability that the data contains coherent signals vs.
+incoherent glitches.
+In this paper, we the \bcr to rank O2's candidate gravitational-wave signals from $55-500\ \msun$ (detector-frame) total mass systems.
+For each candidate, we calculate the probability of astrophysical origin, \pastrobcr and compare to candidate events reported by other authors including the LIGO-Virgo-KAGRA (LVK) collaboration in \GWTC~\cite{GWTC1}, the \pycbc-team~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6, pycbc_single_det, pycbc_ogc_2}, by the Institute of Advanced study's team (\IAS)~\cite{IAS0, IAS1, IAS2}, or by \citet{bayesian_odds}.
 
 We find that (a) high-mass events reported in the \GWTC, including GW170729 (the heaviest event in \GWTC) are very statistically significant $\pastrobcr>0.9$; (b) three out of the eight \IAS events and candidates have $\pastrobcr>0.5$, corroborating \IAS's detection claims for GW170304, GW170727, and GW170817A; and that (c) our ranking statistic does not identify any new intermediate-mass black holes, but does identify an unreported marginal stellar-mass binary black hole candidate, 170222 with $\pastrobcr\sim0.5$.
-%\avi{Need to doublecheck that this wasnt in the PyCBC sub-threshold paper}.
+%\avi{Need to doublecheck that this wasn't in the PyCBC sub-threshold paper}.
 
@@
 We present details on the implementation of our analysis in Section~\ref{sec:Analysis}.
-Finally, we present our results in Section~\ref{sec:Results}, and discuss these results in the context of the significance of gravitational-wave candidates in Section~\ref{sec:Conclusion}.
+Finally, we present our results in Section~\ref{sec:Results} and discuss these results in the context of the significance of gravitational-wave candidates in Section~\ref{sec:Conclusion}.
 
 \section{Method\label{sec:method}}
-
+\subsection{A Bayesian Ranking Statistic}
 The standard framework to identify CBC gravitational-wave signals in data is to quantify the significance of candidates with null-hypothesis significance testing~\cite{GWTC1, GWTC2}.
@@
 Here, we explore a hybrid frequentist/Bayesian ranking statistic that makes use of the Bayesian evidence.
-We compute the Bayesian evidence under the assumption that they either contain a coherent gravitational-wave signal, noise, or a glitch.
+We compute the Bayesian evidence under the assumption that they either contain a coherent gravitational-wave signal, noise, or a glitch ($Z^S, Z^N, Z^G$, defined in Appendix~\ref{sec:bayesianEvidEval}).
 However, instead of computing true Bayesian odds, we use the evidences as a ranking statistic.
@@
 
-Bayes' theorem states that the posterior probability distribution $p(\parameters|d,\mathcal{H})$ for data $d$ and a vector of parameters \parameters that describe a model which quantifies a hypothesis $\mathcal{H}$, is given by
-\begin{equation}
-p(\parameters|d,\mathcal{H}) = \frac{\mathcal{L}(d|\parameters, \mathcal{H}) \ \pi(\parameters | \mathcal{H})}{\mathcal{Z}(d|\mathcal{H})}\ , 
-\end{equation}
-where $\mathcal{L}(d|\parameters, \mathcal{H})$ is the likelihood of the data given the parameters \parameters and the hypothesis, $\pi(\parameters | \mathcal{H})$ is the prior probability of the parameters, and finally,
-\begin{equation}
-    \mathcal{Z}(d|\mathcal{H}) = \int\limits_{\parameters} \ \mathcal{L}(d|\parameters,\mathcal{H}) \ \pi(\parameters | \mathcal{H}) \ d\parameters\ ,
-\end{equation} is the likelihood after marginalizing over the parameters \parameters.
-To compare two hypotheses $\mathcal{H}_A$ and $\mathcal{H}_B$ through Bayes' theorem one can calculate an odds-ratio
-\begin{equation}
-    \mathcal{O}^A_B = \frac{\mathcal{Z}^A\ \pi^A}{\mathcal{Z}^B\ \pi^B}\ ,
-\end{equation}
-where  $\{\pi^A, \pi^B\}$ are the prior-odds for each hypothesis and $\{\mathcal{Z}^A, \mathcal{Z}^B\}$ are shorthand for the evidences $\{\mathcal{Z}(d|\mathcal{H}_A), \mathcal{Z}(d|\mathcal{H}_B)\}$.
-The odds-ratio can quantify which of the two hypotheses is more likely.
-For example, if $\mathcal{O}^A_B >> 1$, then the odds are in favor of the $\mathcal{H}_A$ hypotheses.
-
-The \bcrodds quantity is a Bayesian odds-ratio like the above, of a coherent signal hypotheses $\mathcal{H}_S$ and an incoherent instrumental feature hypothesis $\mathcal{H}_I$ (the null-hypotheses) for a network of $D$ detectors.
-$\mathcal{H_I}$ states that each detector $i$ has either pure stationary Gaussian noise $\mathcal{H}_N$ or Gaussian noise and an incoherent noise transient (glitch) $\mathcal{H}_G$.
-Taking $Z^S$, $Z^G_i$ and $Z^N_i$ as the Bayesian evidences (defined in Appendix~\ref{sec:bayesianEvidEval}) for $\mathcal{H}_S$, $\mathcal{H}_N$, and $\mathcal{H}_G$, \bcrodds is given by
+Introduced by \citet{BCR1}, the Bayesian Coherence Ratio for a candidate signal in a network of $D$ detectors is given by
 \begin{equation}
 \label{eq:bcr}
-\bcrodds = \frac{\pi^S Z^S}{\prod\limits^D_{i=1} \ [\pi^G Z^G_i + (1-\pi^G)Z^N_i]}\ ,
+\bcr = \frac{\hat{\pi}^S Z^S}{\prod\limits^D_{i=1} \ [\hat{\pi}^G Z^G_i + \hat{\pi}^N Z^N_i]}\  ,
 \end{equation}
+where $\{\hat{\pi}^S, \hat{\pi}^N, \hat{\pi}^G\}$ are estimates of the astrophysical prior-odds of obtaining a signal, noise or a glitch from a stretch of data.
+In the limit where the estimated prior-odds equal the astrophysical prior-odds, the \bcr becomes the optimal Bayesian odds described by \citet{BCR2}.
+However, as the astrophysical prior-odds are unknown, it is invalid to use the \bcr as an odds-ratio to discriminate signals from glitches.
+Instead, we use the \bcr as a ranking statistic to obtain a frequentist significance of a candidate \bcr-value, \candbcr, measured against a background \bcr distribution, \bgrdbcr.
 
-where $\pi^S$ and $\pi^G$ are the prior-odds of obtaining a signal or a glitch from a stretch of data. The prior-odds can be defined more explicitly as 
-\begin{itemize}
-    \item $\pi^S=\pi(\mathcal{H}_S)/\pi(\mathcal{H}_I)$, the prior-odds for obtaining a coherent signal versus an incoherent instrumental feature.
-    \item $\pi^G=\pi(\mathcal{H}_G| \mathcal{H}_I)$, the probability of obtaining a glitch assuming there is an incoherent instrumental feature.
-\end{itemize}
-
-When $\mathcal{H}_S$ and $\mathcal{H}_I$ are precisely described and the prior-odds represent our true beliefs, the \bcrodds is a Bayesian odds-ratio.
-As an odds-ratio, the \bcrodds is the optimal discriminator between coherent signals and incoherent instrumental features.
-However, as the priors-odds are unknown, we \textit{tune} values for prior-odds, $\hat{\pi}^S$ and $\hat{\pi}^G$, to estimate \bcrodds with a ranking statistic, \bcr, given by
-\et{I would remove everything in this subsection before this point.
-Save it for your dissertation if you want, but I don't think we need to review Bayesian basics here.
-Instead, just begin by saying that we implement the BCR, which is given by Eq.~\ref{eq:rho_bcr} with suitable references to the previous BCR papers.
-The motivation for the BCR can be summarised in a single sentence.}
+Since it is impossible to shield ground-based gravitational-wave detectors from gravitational-wave signals, the LVK empirically estimates the background by repeatedly time-shifting strain data by amounts larger than the light-travel time between the two LIGO detectors~\cite{GWTC1}.
+We use time-shifted data to generate \bgrdbcr.
+Following this, each candidate's single-event false alarm probability $p_1$ of being miss-classified as a glitch is given by
 \begin{equation}
-\label{eq:rho_bcr}
-\bcr = \frac{\hat{\pi}^S Z^S}{\prod\limits^D_{i=1} \ [\hat{\pi}^G Z^G_i + (1-\hat{\pi}^G)Z^N_i]}\ .
+    p_1 = \frac{\text{Count of } \bgrdbcr \leq \candbcr}{\text{Count of } \bgrdbcr} \ .
 \end{equation}
-\et{Rewrite the remaining paragraphs to explain that how the BCR relates to the odds with just a few sentences, avoiding equations.}
-In the limit where the estimated prior-odds equal the true prior-odds, $\bcr\to\bcrodds$.
-However, as we are uncertain what the true prior-odds are, it is invalid to use the \bcr as an odds-ratio to make an informed decision about whether a candidate is from an astrophysical or terrestrial source.
-Instead of interpreting the \bcr as a Bayesian odds-ratio, it can be used as a ranking statistic.
-Using the \bcr as a ranking statistic we can obtain a frequentist significance of a candidate \bcr-value measured against a background \bcr distribution.
-
-When using the \bcr as a detection statistic, the prior-odds are empirically tuned to maximize the separation between the \bcr distribution of the background (expected to favor the $\mathcal{H}_I$ hypothesis) and the \bcr distribution of artificially manufactured simulated signals (expected to favor the $\mathcal{H}_S$ hypothesis).
-Increasing the separation between the two distributions can improve ability of the \bcr to discriminate candidate events as coherent signals or incoherent instrumental features.
-The tuning process is further described in Appendix~\ref{apdx:tuning-prior-odds}.
-
-\subsection{Estimation of astrophysical signal probability}
-\et{Above, I propose to cut the previous subsection way back.
-I think this subsection can be cut way back too and combined with the previous subsection.
-Once we have finished talking about $\rho_\text{BCR}$, we can just state that we use time-shifted data to generate distributions of $\rho_\text{BCR}$ for noise, which we use to calculate a single-event false alarm probability = the fraction of triggers with a $\rho_\text{BCR}$ at least that big.
-(The thing we are currently calling $f$ is a single-event false alarm probability, so we should call it that and give it a better variable name like $p_1$.) Then comment that we consider $N$ triggers so we also calculate a false-alarm probability with trial factors, which is given by the current Eq.~6.
-(I suggest you call the false alarm probability with trial factors $p_N$ to avoid confusion.) The text should say how $N$ is determined.
-I agree that $p_\text{astro} = 1-p_N$ is too sloppy to do in a paper.
-(The reason we are using FAP is because there was not appetite to calculate the distribution of $\rho_\text{BCR}$ for a plausible signal distribution, which is necessary to get an actual $p_\text{astro}$.) At this late stage, I think the best thing to do is just say that we are going to report $1-p_N$ alongside $p_\text{astro}$ values even though they are apples and oranges.
-While it's sloppy to compare them directly, they \textit{are} both indicators of significance.
-Moreover, different groups make different assumptions about the signal distribution, and so the different $p_\text{astro}$ values are sort of already different fruit; see Shanika's paper.
-We can explain all this and say we're going to put everything into one table anyway.
-However, the least bad thing to do is to report $p_N$ without calling it $p_\text{astro}$.
-I think most referees can live with that.}
-Candidate \bcr-values are either statistically insignificant compared to the background \bcr distribution, implying the candidate is more probable to be an incoherent instrumental feature (the $\mathcal{H}_I$ null-hypothesis), or statistically significant relative to the background distribution, indicating the possible presence of an astrophysical signal (the $\mathcal{H}_S$ hypothesis).
-A false alarm probability with trial factors, \fap, for the candidate \bcr-value can quantify the significance.
-The \fap for a \bcr-value is the probability that a candidate originating from a non-astrophysical source can be falsely identified as a signal once in $N$ trials, and is given by
+Moreover, as we have several candidates ($N$ candidates), each with their \candbcr, we account for them by calculating a false-alarm probability with trial factors $p_N$ given by
 \begin{equation}
-    \fap = 1 - (1-f)^N \ ,
+    \fap = 1 - (1-p_1)^N \ .
 \end{equation}
-where $f$ is the probability of observing a background $\bcr'$ greater than or equal to the candidate \bcr,
+Finally, we can calculate the probability of the candidate signal event occurring from  a gravitational-wave, \pastrobcr with 
 \begin{equation}
-    f = \frac{\text{Count of } \bcr' \leq \bcr}{\text{Count of } \bcr'} \ .
+\pastrobcr = 1 - \fap \ . 
 \end{equation}
-
-Finally, the \fap can be used to construct a \pastro, the probability that a signal is of astrophysical origin~\cite{pastro_1,pastro_2,pastro_3}
-\begin{equation}
-    \pastro = 1 -  \fap \ .
-\end{equation}
-
-\avi{Eric, can you take a look at this section about the FAP p-astro?}
-\avi{
-The pastro calculation may need some more discussion.
-Taking pastro = 1-FAP as identifying a real signal can be hugely problematic: \url{https://en.wikipedia.org/wiki/Misuse_of_p-values}, even though its ok in this case.
-Maybe the following papers have something that can help motivate this ~\cite{Farr:2015:PhRvD, Gaebel:2019:MNRAS,Galaudage:2020:PhRvD}
-}
-
-\subsection{Background estimation}
-
-To rank candidate event \bcr values we compute a background \bcr distribution.
-We use time-shifted background data from \pycbc~\cite{pycbc_og4}.
-\et{Add sentence here explaining what time-shifting is and why it is used.} The output of \pycbc's search is a list of times and their corresponding \pycbc ranking statistic \pycbcstat values.
-Whenever a local maximum of $\pycbcstat > \snr_\text{T}$, where $\snr_\text{T}$ is some predetermined threshold value, the \pycbc search pipeline produces a single-detector \textit{trigger} associated with the detector and time $t_c$ where the apparent signal in the data has its merger~\cite{pycbc_og6}.
-For each \pycbc background trigger, we calculate \bcr.
-% \avi{Should I mention that we need \pycbc  as a pre-selection step to computing? }
-\et{I think this section can be cut way back too.
-(I've deleted a bunch of stuff w track changes.) I don't think we need to get into the three types of triggers; just focus on background triggers.
-I would move this discussion into a single subsection along with IIA and IIB.
-I would cover this stuff \textit{before}getting into FAP calculation.
-That way, we already have introduced the distribution of $\rho_\text{BCR}$; it will be more clear what we are talking about.}
 
@@
 
-\subsection{Acquisition of triggers}
-Advanced LIGO's second observing run O2 lasted $38$ weeks~\cite{GWOSC}.
-The software package, \pycbc~\cite{pycbc_code}, was used by LVK to process the O2 data in 22 time-frames (approximately 2 weeks per frame) and found several gravitational-wave events and numerous gravitational-wave candidates~\cite{pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6}.
-Some candidate events were vetoed to be glitches, while others were rejected due to their low significance.
-The data are divided into these time-frames because the detector's sensitivity does not stay constant throughout the eight-month-long observing period.
-
-In addition to finding candidate events, \pycbc also identified several million background triggers for each time-frame, by searching background data manufactured by time-sliding data within that time-frame.
-The background triggers help quantify the candidate events' significance for the respective time-frames.
-Finally, to test the search's sensitivity, \pycbc produced and searched for thousands of simulated signals.
-% \avi{Do i need to contextualize this choice more, ie talk about what would happen if I chose a narrower range?}
-
-For our study, we filter the \pycbc background, simulated and candidate triggers to include only triggers in the ranges of the parameters presented in Table~\ref{tab:parameters}.
-Filtering triggers to this region focuses our analysis to binary black hole mergers with total masses above $> 55 \msun$.
-This corresponds to binary systems with signal durations $<454 \ \text{ms}$, signals which may be mistaken for short-duration glitches.
-A plot of the \pycbc triggers from one time-frame, during April 23 - May 8, 2017, is presented in Fig.~\ref{fig:templateBank}.
-This figure also depicts the gravitational-wave templates used by \pycbc's search through this time-frame of data.
+We acquire O2 candidate signal triggers (times when the detector's data has a signal-to-noise ratio above a predetermined threshold) for \bcr analysis from \pycbc~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6}.
+Some of the triggers are associated with gravitational-wave events and candidates, while others are glitches.
+We also acquire background and simulated triggers from \pycbc to calculate \bgrdbcr and estimate values for $\{\hat{\pi}^S,\hat{\pi}^G\}$ (see Appendix~\ref{apdx:tuning-prior-odds} for details on the estimation process).
+Note that the triggers are divided into two week time-frames because the detector's sensitivity does not stay constant throughout the eight-month-long observing period~\cite{pycbc_og4}.
 
 \begin{table}[t]
-
 \caption[BBH parameters correspond to duration $<454\ \text{ms}$]{\label{tab:parameters}Trigger-selection parameter space (parameters correspond to signals with durations $<454 \ \text{ms}$). }
@@
 
+For our study, we filter triggers to include those in the parameter ranges presented in Table~\ref{tab:parameters}.
+This region focuses our analysis on binary black hole mergers with total masses above $> 55 \msun$, corresponding to binary systems with signal durations $<454 \ \text{ms}$.
+The filtering process leaves us with $60,996$ background, $5,146$ simulated, and $25$ candidate signal triggers.
+We also include events and candidate events reported by \GWTC and the \IAS group in our list of candidate signal triggers.
+A plot of the \pycbc triggers from April 23 - May 8, 2017, is presented in Fig.~\ref{fig:templateBank}.
+This figure also depicts the gravitational-wave templates used by \pycbc's search.
+
 \begin{figure*}[!ht]
-
 {\centering \includegraphics[width=0.75\linewidth]{images/template_bank.png}
-
 }
@@
 Our search is constrained to the parameter space enclosed by the dashed line.
-The candidate, background and simulated triggers detected in this region of the parameter space during this period are plotted in orange, gray and blue respectively.}\label{fig:templateBank}
+The candidate, background, and simulated triggers detected in this region of the parameter space during this period are plotted in orange, gray, and blue, respectively.}\label{fig:templateBank}
 \end{figure*}
 
-\subsection{Calculating the BCR for triggers}
-To evaluate $Z^S$, $Z^G_i$ and $Z^N_i$ and calculate the \bcr Eq.~\ref{eq:bcr} for triggers, we carry out Bayesian inference with \bilby~\cite{bilby, bilby_pipe}, employing \dynesty~\cite{dynesty} as our nested sampler.
+To evaluate $\{Z^S, Z^G_i, Z^N_i\}$ and calculate the \bcr Eq.~\ref{eq:bcr} for triggers, we carry out Bayesian inference with \bilby~\cite{bilby, bilby_pipe}, employing \dynesty~\cite{dynesty} as our nested sampler.
 Nested sampling, an algorithm introduced by~\citet{skilling2004, skilling2006}, provides an estimate of the Bayesian evidence and is often utilized for parameter estimation within the LIGO collaboration~\cite{bilby, bilby_paper, pbilby_paper}.
 
-The most computationally intensive step during Bayesian inference is evaluating the likelihood $\mathcal{L}(d_i|\template)$.
-To accelerate our analysis, we use a likelihood that explicitly marginalizes over coalescence time, phase at coalescence, and luminosity distance (Eq.~80 from~\citet{intro_to_gw_bayes}).
-\et{I think that IIIa and IIb should probably be shrunken and merged so that Section III does not have any subsections (IIC can be deleted; see below).
-The way to cut these sections down is to stick to just \textit{describing what was done} rather than trying to add a lot of explanation.
-(Explaining what PyCBC does and why is particularly excessive, IMO.) Just cut out anything that is not part of a recipe to reproduce the analysis.}
-
-We set the priors $\pi(\parameters|\mathcal{H}_S)$ and $\pi(\parameters|\mathcal{H}_G)$ to be identical which reflects our ignorance of the distribution of the population properties of signals and signal-like glitches.
-These priors restrict signals with mass parameters in the ranges presented in Table~\ref{tab:parameters}.
-The spins are aligned over a uniform range for the dimensionless spin magnitude from $\left[0,1\right]$.
-The luminosity distance prior assigns probability uniformly in comoving volume, with an upper cutoff of $5\ \text{Gpc}$.
-The full list of the priors, along with their shapes, limits and boundary conditions are documented in Table~\ref{tab:priors}.
+We use a likelihood that marginalizes over coalescence time, the phase at coalescence, and luminosity distance (Eq.~80 from~\citet{intro_to_gw_bayes}).
+We use identical parameter estimation priors for the glitch and signal models, reflecting our ignorance of the distribution of the population properties of signals and signal-like glitches.
+The complete list of the priors is in Table~\ref{tab:priors}.
 
@@
 To generate the PSD, we take 31 neighboring off-source non-overlapping  4-second  segments of time-series data before the analysis data segment $d_i$.
-To suppress spectral leakage, a Tukey window with a 0.2-second roll-off is applied to each data segment .
-After this the segments are fast-Fourier transformed and median-averaged to create a PSD~\cite{ligo_psd}.
+A Tukey window with a 0.2-second roll-off is applied to each data segment to suppress spectral leakage.
+After this, we fast-Fourier transform and median-average the segments to create a PSD~\cite{ligo_psd}.
 Like other PSD estimation methods, this method adds statistical uncertainties to the PSD~\cite{psd_student_t, chatziioannou2019noise, Biscoveanu:2020:PhRvD}.
 To marginalize over the statistical uncertainty, we use the median-likelihood presented by~\citet{psd_student_t} as a post-processing step.
-We find that this post-processing step improves the search efficiency by $49.26\%$ the details of this calculation are presented in the Appendix~\ref{sec:psd-marginalization}.
+We find that this post-processing step improves the search efficiency by $49.26\%$ the details of this calculation are in the Appendix~\ref{sec:psd-marginalization}.
 
-Finally, we acquire the foreground, background and data in which we inject simulated signals into, from from the gravitational-wave Open Science Center~\cite{GWOSC}.
 The data we use are the publicly accessible O2 strain data from the Hanford and Livingston detectors, recorded while the detectors are in ``Science Mode''.
-We obtain the data using \gwpy~\cite{gwpy}.
+We obtain the data from the gravitational-wave Open Science Center~\cite{GWOSC} using \gwpy~\cite{gwpy}.
 
-\subsection{Assigning \pastro to candidate events}
-After calculating the \bcr for the entire set of background and simulated triggers, we calculate the background and simulated \bcr probability distributions for each 2-week time-frame of O2 data.
-These distributions are used to `tune' prior-odd $\hat{\pi}^S$ and $\hat{\pi}^G$ values as described in Appendix~\ref{apdx:tuning-prior-odds}.
-\et{This subsection discusses formalism (how the analysis works) and so it feels out of place in Section III, which is about the details of the implementation.
-I would delete this subsection entirely and just add a sentence or two to the formalism section explaining that the $\pi$'s are tuned emprically; see Appendix~\ref{apdx:tuning-prior-odds}.}
-
-Using the tuned prior-odds the \bcr for the candidate events can be calculated.
-Fig.~\ref{fig:bcrCdf} shows the \bcr distributions for the background triggers, simulated triggers and candidate events.
-The bulk of the background and simulated trigger distributions are separate but slightly overlap due to some of the simulated signal's being very faint.
-The separation suggests that the \bcr can successfully distinguish signals from noise or glitches.
-The vertical lines in Fig.~\ref{fig:bcrCdf} displays the \bcr for gravitational-wave candidate events.
-On comparing the candidate event \bcr values with the background distribution, we can estimate \pastro values for the candidate events.
-
-\begin{figure}[!ht]
-{\centering \includegraphics[width=0.85\linewidth]{images/reweighted_bcr_cdf_smaller_legend.png} }
-\caption[BCR distribution example]{Histograms represent the survival function (1-CDF) from our selection of background triggers (gray) and simulated signals (blue) triggers obtained from \pycbc's search of data from $\text{August 13 - 21, 2017}$.
-Vertical lines mark the $\text{ln}\ \bcr$ of \IAS's GW170817A and \GWTC's GW170814.}\label{fig:bcrCdf}
-\end{figure}
+Finally, with the \candbcr and \bgrdbcr, we calculate the candidate signal's \pastrobcr. We present the \pastrobcr with \pastro of other pipelines for comparison in Table~\ref{tab:results}.
 
@@
 
+Various pipeline \pastro are not mathematically equivalent~\cite{Galaudage:2020:PhRvD}.
+However, by comparing pipeline \pastro values for a given candidate along with \pastrobcr in Table~\ref{tab:results}, we can compare how significant each pipeline deems various candidates.
+Note that the $\hat{\pi}^S$ and $\hat{\pi}^G$ values utilized for each time-frame are reported in Appendix~\ref{apdx:alphabeta}.
+
 \input{Data/results_table}
-We analyze the $60,996$ background, $5,146$ simulated, and $25$ candidate triggers reported by \pycbc's search on the data from LIGO's second observing run, restricting our analysis to the triggers that fall within our mass-space as described in Section~\ref{sec:method}.
-We also analyze events and candidate events reported by \GWTC and the \IAS group (note: some of these were identified as candidates by the \pycbc search).
-Table~\ref{tab:results} summaries the \pastrobcr, along with the \pastro of other pipelines for comparison.
-\et{The previous text about what we analysed should go in Section III. This section is just for reporting the results.}
-
-\et{Rewrite the following text w better explanation of FAP vs p-value.}
-Although the various pipeline \pastro are not mathematically equivalent, by comparing pipeline \pastro values for a given candidate, we can compare how significant each pipeline deems various candidates.
-The $\hat{\pi}^S$ and $\hat{\pi}^G$ values utilized for each time-frame are reported in Appendix~\ref{apdx:alphabeta}.
 
 \subsection{GWTC-1 Events}
-All the confirmed gravitational-wave events from binary black hole mergers reported in \GWTC and within our prior space, (specifically GW170104, GW170608, GW170729, GW170809 and GW170814), have $\pastrobcr>0.9$, indicating a high probability of an astrophysical signal.
+All the confirmed gravitational-wave events from binary black hole mergers reported in \GWTC and within our prior space (specifically GW170104, GW170608, GW170729, GW170809, and GW170814) have $\pastrobcr>0.9$, indicating a high probability of an astrophysical signal.
 
@@
 For example, consider the candidate event 170412, assigned a $\pastro$ of $0.06$ by \gstlal and has a $\pastrobcr$ of $0.01$.
-This candidate was reported to be excess power caused due noise appearing non-stationary between 60-200 Hz~\cite{GWTC1}.
+This candidate was reported to be excess power caused due to noise appearing non-stationary between 60-200 Hz~\cite{GWTC1}.
 This candidate acts as an example of how $\pastrobcr$ may be utilized to eliminate candidates originating from terrestrial noise sources.
@@
 Our analysis of the IAS events and candidates with $M_T>55\ \msun$ in O2 has resulted in three events with disfavored $\pastrobcr<0.5$ (GWC170402, GW170403, GW170425), and four events and one candidate with $\pastrobcr\geq0.5$ (GW170121, 170302, GW170304, GW170727, GW170817A).
-While GW170727 and GW170817A's \pastrobcr are similar to the \pastro reported from IAS (the differences between the \pastro from \bcr and IAS is $|\Delta \pastro|<0.1$), the remaining candidates have opposing \pastro values (with $|\Delta \pastro| > 0.15$).
+While GW170727 and GW170817A's \pastrobcr are similar to the \pastro reported from IAS (the differences between \pastrobcr and the IAS \pastro is $|\Delta p |<0.1$), the remaining candidates have contradicting \pastrobcr and  \pastro values (with $|\Delta p| > 0.15$).
 
@@
 Our ranking statistic relies on the signal to appear coherent, even if just faintly coherent, amongst the various detectors to have a high \pastrobcr.
-The lack of coherence and the non-eccentric waveform may be the leading factors for a low \pastro.
+The lack of coherence and the non-eccentric waveform may be the leading factors for a low \pastrobcr.
 GW170403 and GW170425 which have $\pastrobcr<0.35$ also have low  \pastro reported by \citet{pycbc_ogc_2},  suggesting that these events may have been false alarms.
@@
 Although no clear detections are made with the \bcr, a marginal-candidate 170222 has been discovered with a $\pastrobcr\sim0.5$.
-This candidate has an SNR$\sim7.7$, low spin magnitudes and source-frame component masses of $({47.16}_{-5.77}^{+8.00}, {35.50}_{-6.35}^{+5.79}) \msun$, making it one of the heavier black-hole mergers from O2 and \GWTC.
+This candidate has a SNR$\sim7.7$, low spin magnitudes, and source-frame component masses of $({47.16}_{-5.77}^{+8.00}, {35.50}_{-6.35}^{+5.79}) \msun$, making it one of the heavier black-hole mergers from O2 and \GWTC.
 This candidate may be of interest as one component black hole may lie in the pair-instability mass gap ($55^{+10}_{-10}-148^{+13}_{-12}\msun$)~\cite{Woosley:2021:arXiv, Heger:2002:ApJ}.
 More details on the candidate are presented in Appendix~\ref{apdx:170222}.
-The remaining coherent trigger candidates all have $\pastrobcr\ll0.5$ making them unlikely to originate from astrophysical sources.
+The remaining coherent trigger candidates all have $\pastrobcr\ll0.5$, making them unlikely to originate from astrophysical sources.
 
@@
 
-In this paper, we demonstrate that the Bayesian Coherence Odds-Ratio \bcr~\cite{BCR1} can be used as a ranking statistic to provide a measure of significance for gravitational wave signals originating from CBCs with total masses between $55\msun$ and $400\msun$, a range that includes intermediate-mass black holes.
+In this paper, we demonstrate that the Bayesian Coherence Odds-Ratio \bcr~\cite{BCR1} can be used as a ranking statistic to provide a measure of significance for gravitational-wave signals originating from CBCs with total masses between $55\msun$ and $400\msun$, a range that includes intermediate-mass black holes.
 To compute the \bcr for candidates, we utilize Bayesian inference to explicitly calculate the probability of data under various hypotheses (the hypotheses that the data contains a coherent signal, just noise, or an incoherent glitch).
@@
 
-% \avi{Unlike for stellar-mass BBH, there are still alot of uncertainties for IMBH formation scenarios.
+% \avi{Unlike for stellar-mass BBH, there are still a lot of uncertainties for IMBH formation scenarios.
 Hence, upper limits would be challenging to calculate.
-Additionally, we would require to do more robust simulation studies to see what would fall in/outside our detection threshold, to put constraints on population properties and study the search's sensitivity
+Additionally, we would require to do more robust simulation studies to see what would fall in/outside our detection threshold, to put constraints on population properties, and study the search's sensitivity.
 % }
@@
 This work is supported by the Australian Research Council (ARC) Centre of Excellence CE170100004.
-The author gratefully thank the \pycbc team for providing the gravitational-wave foreground, background and simulated triggers from \pycbc's search of O2's data.
+The authors gratefully thank the \pycbc team for providing the gravitational-wave foreground, background, and simulated triggers from \pycbc's search of O2's data.
 We also warmly thank Ian Harry and Thomas Dent for answering questions about the \pycbc search's data products.
 
-We thank Stuart Anderson for assistance with accommodating this analysis which was performed on the California Institute of Technology computing cluster.
-All analyses (inclusive of test and failed analyses) performed for this study used $~1.3\mathrm{M}$ core-hours, amounting to a carbon footprint of $~167\ \mathrm{t}$ of CO$^2$ (using the US average electricity source emissions of $0.429\ \text{kg/kWh}$~\cite{greenhouse} and $0.3\ \text{kWh}$ for each CPU).
+We thank Stuart Anderson for accommodating this analysis performed on the California Institute of Technology computing cluster.
+All analyses (inclusive of test and failed analyses) performed for this study used $~1.3\mathrm{M}$ core-hours, amounting to a carbon footprint of $~167\ \mathrm{t}$ of CO$^2$ (using the U.S.
+average electricity source emissions of $0.429\ \text{kg/kWh}$~\cite{greenhouse} and $0.3\ \text{kWh}$ for each CPU).
 
-This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open Science Center (https://www.gw-openscience.org), a service of LIGO Laboratory, the LIGO Scientific Collaboration and the Virgo Collaboration.
+This research has used data, software, and web tools obtained from the Gravitational Wave Open Science Center (https://www.gw-openscience.org), a service of LIGO Laboratory, the LIGO Scientific Collaboration, and the Virgo Collaboration.
 LIGO is funded by the U.S.
 National Science Foundation.
-Virgo is funded by the French Centre National de Recherche Scientifique (CNRS), the Italian Istituto Nazionale della Fisica Nucleare (INFN) and the Dutch Nikhef, with contributions by Polish and Hungarian institutes.
+Virgo is funded by the French Centre National de Recherche Scientifique (CNRS), the Italian Istituto Nazionale della Fisica Nucleare (INFN), and the Dutch Nikhef, with contributions by Polish and Hungarian institutes.
 
@@
 \section{Bayesian Evidence Evaluation}\label{sec:bayesianEvidEval}
+
 \subsection{Noise Model}
@@
 \subsection{Coherent Signal Model}
-We model coherent signals using a binary black hole waveform template \template, where the vector \parameters contains a point in the 12 dimensional space describing aligned-spin binary-black hole mergers.
+We model coherent signals using a binary black hole waveform template \template, where the vector \parameters contains a point in the 12-dimensional space describing aligned-spin binary-black hole mergers.
 For the signal to be coherent, \parameters must be consistent in each 4-second data segment $d_i$ for a network of $D$ detectors.
@@
 \end{equation}
-where $\pi(\parameters| \mathcal{H}_S)$ is the prior for the parameters in the coherent signal hypothesis, and $\mathcal{L}(d_i|\template)$ is the likelihood for the coherent signal hypothesis that depends on the gravitational-wave template \template and its parameters \parameters.
+where $\pi(\parameters| \mathcal{H}_S)$ is the prior for the parameters in the coherent signal hypothesis $\mathcal{H}_S$, and $\mathcal{L}(d_i|\template)$ is the likelihood for the coherent signal hypothesis that depends on the gravitational-wave template \template and its parameters \parameters.
 
 \subsection{Incoherent Glitch Model}
-Finally, as glitches are challenging to model and poorly understood, we follow \citet{bci} and utilize a surrogate model for glitches: the glitches are modeled using gravitational-wave templates  \template with uncorrelated  parameters amongst the different detectors such that  $\parameters_i \neq \parameters_j$ for two detectors $i$ and $j$~\cite{bci}.
-Modeling glitches with \template captures the worst case scenario: when glitches are identical to gravitational-wave signals (excluding coherent signals).
+Finally, as glitches are challenging to model and poorly understood, we follow \citet{bci} and utilize a surrogate model for glitches.
+The glitches are modeled using gravitational-wave templates  \template with uncorrelated parameters amongst the different detectors such that  $\parameters_i \neq \parameters_j$ for two detectors $i$ and $j$~\cite{bci}.
+Modeling glitches with \template captures the worst-case scenario: when glitches are identical to gravitational-wave signals (excluding coherent signals).
 Thus, we can write $Z^G_i$ as
@@
 \end{equation}
-where $\pi(\theta| \mathcal{H}_G)$ is the prior for the parameters in the incoherent glitch hypothesis.
+where $\pi(\theta| \mathcal{H}_G)$ is the prior for the parameters in the incoherent glitch hypothesis $\mathcal{H}_G$.
 
@@
 \end{equation}
-The $D_{KL}=0$ when the distributions are identical and increases as the asymmetry between the distributions increases.
+The $D_{K.L.}=0$ when the distributions are identical and increases as the asymmetry between the distributions increases.
 
@@
 \section{Marginalizing over PSD statistical uncertainties}\label{sec:psd-marginalization}
-To generate the results in Fig.~\ref{fig:bcrCdf}, we applied a post-processing step to marginalize the uncertainty in the PSD.
-In Fig.~\ref{fig:bcrCdfUnmarginalized}, we show the results if this post-processing step is not applied.
-Clearly, marginalizing over uncertainty in the PSD yields an improvement in the separation of the noise and signal distributions.
+To generate the results presented in Table~\ref{tab:results}, we applied a post-processing step to marginalize the uncertainty in the PSD.
+In Fig.~\ref{fig:bcrCdf}, we demonstrate the impact of the post-processing step.
+Marginalizing over uncertainty in the PSD yields an improvement in the separation of the noise and signal distributions (left plot).
 Quantitatively, at a threshold $\bcr^T=0$ the post-processing step results in a reduction in the number of background $\bcr > \bcr^T$ from $60.7\%$ to $25.28\%$ in the August 13 - 21, 2017 time-frame of data.
-For the entirety of O2 PSD marginalization resulted in a $49.26\%$ improvement in search efficiency.
+For the entirety of O2, PSD marginalization resulted in a $49.26\%$ improvement in search efficiency.
 
-\begin{figure}[!ht]
-{\centering \includegraphics[width=0.85\linewidth]{images/orig_bcr_cdf_smaller_legend.png} }
-\caption[BCR distribution example]{This plot is analogous to Fig.~\ref{fig:bcrCdf}, but without using the post-processing step to marginalize over PSD statistical uncertainties.
-Without the post-processing step, there is a greater overlap between the background (gray) and foreground (blue) survival functions.
-For more details about this plot, refer to the caption of Fig.~\ref{fig:bcrCdf}.}\label{fig:bcrCdfUnmarginalized}
-\end{figure}
+\begin{figure*}
+    \centering
+    \begin{subfigure}
+        \centering
+        \includegraphics[width=0.45\linewidth]{reweighted_bcr_cdf_smaller_legend.png}
+    \end{subfigure}
+    ~ 
+    \begin{subfigure}
+        \centering
+        \includegraphics[width=0.45\linewidth]{orig_bcr_cdf_smaller_legend.png}
+    \end{subfigure}
+    \caption{
+    Histograms represent the survival function (1-CDF) from our selection of background triggers (gray) and simulated signals (blue) triggers obtained from \pycbc's search of data from $\text{August 13 - 21, 2017}$.
+Vertical lines mark the $\text{ln}\ \bcr$ of \IAS's GW170817A and \GWTC's GW170814.
+    Left: Survival functions with using the post-processing step to marginalize over PSD statistical uncertainties.
+Right: Survival functions without the post-processing step.
+Without the post-processing step, there is a greater overlap between the background (gray) and foreground (blue) survival functions
+    \label{fig:bcrCdf}}
+\end{figure*}
 
@@
 
-O2 lasted several months over which the detector's sensitivity varied.
+O2 lasted several months, over which the detector's sensitivity varied.
 Hence, a part of our analysis entailed tuning the prior odds for obtaining a signal and a glitch, $\hat{\pi}^S$ and $\hat{\pi}^G$, as described in Section~\ref{sec:method}.
@@
 
-% \section{EXTRA INTRO MATERIAL}
-
-% Given the existence of supermassive black holes detected in the early universe, it is likely for intermediate-mass black holes to have also existed~\cite{Banados:2018:Natur, Askar et al  2020,}.
-However, we only have a handful of promising candidates~\cite{Greene:2004:ApJ, Graham:2013:ApJ, Mezcua:2017:IJMPD, Koliopanos:2017:mbhe, Lin:2020:ApJL, Greene:2020:ARA&A}, and two confirmed intermediate-mass black holes, (i) the $142^{+28}_{-16}\ \msun$ remnant observed from the gravitational wave event GW190521~\cite{Abbott:2020:PhRvL}, and the $5.5^{+1.7}_{-0.9}\times10^{4}\ \msun$ black hole identified from gravitational lensing in the light curve of GRB950830~\cite{paynter_evidence_2021}.
-The concrete discovery of more intermediate-mass black holes will bridge the observational gap and illuminate our understanding of galaxy and supermassive black hole formation.
-Additionally, a catalog of observed intermediate-mass black holes can act as probes to their formation environments, such as in the accretion disks of active galactic nuclei~\cite{}, the centers of dense stellar clusters~\cite{}, and even Population-III stars~\cite{}.
-
-% However, measuring the mass of black holes can be challenging. Several observational techniques to identify intermediate mass black holes
-
-% It is possible to measure the mass of nearby supermassive black holes by directly observing the dynamic motion of stars nearby the supermassive black hole (such as Sgr A$^*$~).
-However, this dynamic measurement method is challenging to utilize for  intermediate-mass black holes as their sphere of influence is too small to resolve motions~\cite{}.
-Additionally, dynamic-measurements that have alluded to  intermediate-mass candidates, e.g.
-the candidate at the center of the globular cluster 47 Tucanae~\cite{kiziltan2017}, can also be attributed to simpler models without a central intermediate-mass black hole~\cite{freire 2017}.
-}}
-
-% \rs{\sout{In a similar vein, although the M-$\sigma$ and M-L relations (relations between the spheroidal bulge of a galaxy's velocity dispersion $\sigma$,  luminosity L, and its central black hole's mass M) can estimate the mass of supermassive black holes~\cite{Ferrarese & Merritt 2000 and Gebhardt et al.
-2000}, they cannot accurately estimate the intermediate-masses.
-The M-$\sigma$ and M-L relations are not calibrated for low-mass galaxies that might host an central intermediate-mass black hole~\cite{J.
-E.
-Greene and L.
-C.
-Ho The Mass Function of Active Black Holes in the Local Universe, E.
-C.
-Moran, K.
-Shahinyan, H.
-R.
-Sugarman, D.
-O.
-Vélez and M.
-Eracleous Black Holes At the Centers of Nearby Dwarf Galaxies}.
-Table 2 of~\citet{mercuza} displays a list of intermediate-mass candidates found with these relations.
-}}
-
-% \rs{\sout{Another method to estimate large black hole masses is with reverberation mapping, which estimates black hole virial masses by studying their nearby gasses' velocities~\cite{reverberation mapping}.
-Reverberation mapping has shown to estimate both supermassive black hole and intermediate-mass black hole virial masses successfully.
-However, this method fails to measure the systematic uncertainties on the lower-end of the intermediate-mass spectrum~\cite{}.
-Additionally, cloud-variability and the possibility of anisotropic emission deride the credibility of intermediate-mass candidates found with reverberation mapping~\cite{}.
-}}
-
-% The most promising intermediate-mass candidates found with electromagnetic-spectra are Ultra-Luminous X-ray sources with luminosities $> 10^{39} \text{erg s}^{-1}$ (e.g.
-HLX-X1)~\cite{}.
-\rs{\sout{While stellar mass black holes are too small to generate such luminosities with Eddington accretion, intermediate mass black holes can accrete at rates large enough to account for the high luminosities~\cite{}.
-However, some argue that some stellar mass black holes may exceed the Eddington limit~\cite{}, and others argue that the X-ray emission might be from a collimated jet leading to an inaccurate mass calculation~\cite{}.}}
-
 \bibliography{high_mass_bib}% Produces the bibliography via BibTeX.

### 2021-07-06 main.tex
update tables

@@
-\documentclass[%
-%reprint,
-%superscriptaddress,
-%groupedaddress,
-%unsortedaddress,
-%runinaddress,
-%frontmatterverbose, 
+\documentclass[
 % preprint,
@@
  nofootinbib,
-%nobibnotes,
-%bibnotes,
  amsmath,amssymb,
  aps,
-%pra,
-%prb,
-%rmp,
-%prstab,
-%prstper,
-%floatfix,
  twocolumn,
@@
 \usepackage{array}
-\usepackage{color,units}
-\usepackage[dvipsnames]{xcolor} % for more colours!
+\usepackage{units}
+\usepackage{xcolor} % for more colours!
 \usepackage{lineno}
 \usepackage{dcolumn}
-\usepackage{longtable}
 \usepackage[normalem]{ulem} %% for striking out text
@@
 \usepackage[breaklinks]{hyperref}
-\usepackage{booktabs}
 \usepackage{xspace} 
@@
 \usepackage{graphicx} % Include figure files
-% \usepackage{authblk}
+
+%%% Table stuff
+\usepackage{longtable}
+\usepackage{booktabs}
+\usepackage{multirow}
+\usepackage{colortbl}
+
+\usepackage{nicematrix}
 
@@
 \newcommand{\gwpy}{{\sc \href{https://gwpy.github.io/}{\texttt{GWpy}}}\xspace}
-
 \newcommand{\imrphenomp}{{\sc \texttt{IMRPhenomPv2}}\xspace}
@@
 \newcommand{\imrxhm}{{\sc \texttt{IMRPhenomXPHM}}\xspace}
-
 \newcommand{\gstlal}{{\sc GstLAL}\xspace}
@@
 \newcommand{\pycbc}{{\sc \href{https://pycbc.org/}{{PyCBC}}}\xspace}
-
 \newcommand{\GWTC}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2019PhRvX...9c1040A/abstract}{{GWTC-1}}}\xspace}
@@
 \newcommand{\candbcr}{\mathcmd{\rho_\text{BCR}^\textit{c}}}
-
 \newcommand{\bcrodds}{\mathcmd{\mathcal{O}_{\mathrm{BCR}}}}
@@
 \newcommand{\psd}{\mathcmd{P(f)}}
-\newcommand{\msun}{\mathcmd{\text{M}_\odot}}
+\newcommand{\msun}{\mathcmd{M_\odot}}
 \newcommand{\mtot}{\mathcmd{M}}
@@
 \newcommand{\fap}{\mathcmd{p_N}}
-
+\newcommand{\totMlab}{\mathcmd{M_T^{\rm{lab}}}}
 \newcommand{\pastro}{\fancytext{p_\text{astro}}}
@@
 \newcommand{\untunedpastrobcr}{\fancytext{p_\text{S}^{\prime}}}
+\newcommand{\tunedpastrobcr}{\fancytext{p_\text{S}}}
 \newcommand{\pastroext}{\fancytext{p_\text{astro}^{\text{ext}}}}
 \newcommand{\pval}{\fancytext{\text{p-value}}}
+
+\newcommand{\pastroGwtcPycbc}{\fancytext{p_\text{astro}^{\text{pyCBC}}}}
+\newcommand{\pastroGwtcGstlal}{\fancytext{p_\text{astro}^{\text{GstLAL}}}}
+\newcommand{\pastroIas}{\fancytext{p_\text{astro}^{\text{IAS}}}}
+\newcommand{\pastroPrat}{\fancytext{P(S|\text{d})}}
+\newcommand{\pastroSing}{\fancytext{p_\text{astro}^{\text{S}}}}
+\newcommand{\pastroOgcTwo}{\fancytext{p_\text{astro}^{\text{OGC2}}}}
+\newcommand{\pastroOgcThree}{\fancytext{p_\text{astro}^{\text{OGC3}}}}
+\newcommand{\tc}{\fancytext{t_c}}
+
 % Table settings
@@
 \renewcommand{\belowrulesep}{0pt}
-% \setlength\cellspacetoplimit{2pt}
-% \setlength\cellspacebottomlimit{2pt}
-
 \newcolumntype{C}{>{\centering\arraybackslash}X}
 \newcolumntype{L}{>{\arraybackslash}X}
-
-% Aesthetic colours
-\definecolor{dodgerblue}{HTML}{1E90FF}
-\definecolor{viennared}{HTML}{DA0A14}
-\definecolor{ctorange}{HTML}{FF6C0C}
-\definecolor{wales}{HTML}{ff0038}
-\definecolor{benettongreen}{HTML}{009421}
-\definecolor{valenciacfred}{HTML}{ee3524}
-\definecolor{barcelonafcgold}{HTML}{edbb00}
-\definecolor{jam}{HTML}{A50B5E}
-\definecolor{austriawien}{HTML}{441678}
-\definecolor{italia90green}{HTML}{009966}
-\definecolor{ferrarired}{HTML}{ff2800}
-\definecolor{gray}{HTML}{F0F0F0}
-\definecolor{LightCyan}{rgb}{0.88,1,1}
 \newcolumntype{a}{>{\columncolor{gray}}c}
-\newcolumntype{b}{>{\columncolor{white}}c}
+\addtolength{\extrarowheight}{\belowrulesep}
 
@@
 The detection of an intermediate-mass black hole population ($10^2-10^6$~\msun) will provide clues to their formation environments (e.g., disks of active galactic nuclei, globular clusters) and illuminate a potential pathway to produce supermassive black holes.
-Ground-based gravitational-wave detectors are in principle sensitive to such mergers and have been used to detect one $142^{+28}_{-16}\ \msun$ intermediate-mass black hole formation event.
-Ground-based detector data contain numerous short-duration noise transients that can mimic the gravitational-wave signals from merging intermediate-mass black holes, limiting the sensitivity of searches.
-Here we demonstrate a Bayesian-inspired ranking statistic to detect binary black hole mergers with a total mass $\gtrsim55$~\msun.
-We use this statistic to identify candidate events with total masses $>55$~\msun using data from LIGO's second observing run.
+Ground-based gravitational-wave detectors are in principle sensitive to a subset of such mergers mergers and have been used to detect one $142^{+28}_{-16}~\msun$ intermediate-mass black hole formation event.
+Ground-based detector data contain numerous short duration noise transients that can mimic the gravitational-wave signals from merging intermediate-mass black holes, limiting the sensitivity of searches.
+Here we demonstrate a Bayesian-inspired ranking statistic to detect binary black hole mergers with a lab-frame total mass $\gtrsim55$~\msun.
+We use this statistic to identify candidate events with lab-frame total masses $\gtrsim55$~\msun using data from LIGO's second observing run.
 Our analysis does not yield evidence for new intermediate-mass black holes.
@@
 
-A variety of techniques have been employed to search for $10^{4} - 10^{6}\ \msun$ intermediate-mass candidates including reverberation mapping~\cite{Peterson:2014:SSRv}, direct kinematic measurements~\cite{Schodel:2002:Natur, Kiziltan:2017:Natur}, applying macroscopic galaxy to black hole mass scaling relations ($M_{BH}$-$\sigma$ and $M_{BH}$-L relations)~\cite{Graham:2013:ApJ, Wevers:2017:MNRAS}, studying  X-ray luminosity and spectra~\cite{Greene:2004:ApJ, Lin:2020:ApJL}, gravitational lensing of gamma-ray burst light curves~\cite{paynter_evidence_2021}, and others~\cite{Greene:2020:ARA&A, Koliopanos:2017:mbhe, Mezcua:2017:IJMPD}).
-However, because intermediate-mass black holes have smaller gravitational spheres of influence than those of supermassive black holes, it is much more challenging to observe them with these observational techniques~\cite{Mezcua:2017:IJMPD}.
-Additionally, the numerous intermediate-mass black hole candidates discovered using these techniques are ambiguous as other sources can describe observations from the candidates (e.g., light sources orbiting clusters of stellar-mass black holes~\cite{Ridolfi:2016:MNRAS, Freire:2017:MNRAS}, anisotropic emission from neutron stars~\cite{Israel:2017:MNRAS, RodriguezCastillo:2020:ApJ}).
+A variety of techniques have been employed to search for $10^{4} - 10^{6}~\msun$ intermediate-mass black hole (IMBH) candidates including reverberation mapping~\cite{Peterson:2014:SSRv}, direct kinematic measurements~\cite{Schodel:2002:Natur, Kiziltan:2017:Natur}, applying macroscopic galaxy to black hole mass scaling relations ($M_{BH}$-$\sigma$ and $M_{BH}$-L relations)~\cite{Graham:2013:ApJ, Wevers:2017:MNRAS}, studying  X-ray luminosity and spectra~\cite{Greene:2004:ApJ, Lin:2020:ApJL}, gravitational lensing of gamma-ray burst light curves~\cite{paynter_evidence_2021}, and others~\cite{Greene:2020:ARA&A, Koliopanos:2017:mbhe, Mezcua:2017:IJMPD}).
+However, because IMBH have smaller gravitational spheres of influence than those of supermassive black holes, it is much more challenging to observe them with these observational techniques~\cite{Mezcua:2017:IJMPD}.
+Additionally, the numerous IMBH candidates discovered using these techniques are ambiguous as other sources can describe observations from the candidates (e.g., light sources orbiting clusters of stellar-mass black holes~\cite{Ridolfi:2016:MNRAS, Freire:2017:MNRAS}, anisotropic emission from neutron stars~\cite{Israel:2017:MNRAS, RodriguezCastillo:2020:ApJ}).
 
-Stellar mass ($M_\text{BH} < 10^{2} \ \msun$) and supermassive black holes ($M_\text{BH} > 10^{6} \ \msun$) have been observed and well studied since the 1970s~\cite{Webster:1972:Natur, Balick:1974:ApJ, Ghez:1998:ApJ, Genzel:2010:RvMP, Abbott:2019:PhRvX, EventHorizonTelescopeCollaboration:2019:ApJL, Abbott:2020:arXiv}.
-However, there is a deficiency of observational evidence for black holes in the intermediate-mass range $10^{2} - 10^{6}\ \msun$.
-The discovery of an intermediate-mass black hole population will bridge this observational gap, probe intermediate-mass formation environments (e.g.
+Stellar mass ($M_\text{BH} < 10^{2}~\msun$) and supermassive black holes ($M_\text{BH} > 10^{6}~\msun$) have been observed and well studied since the 1970s~\cite{Webster:1972:Natur, Balick:1974:ApJ, Ghez:1998:ApJ, Genzel:2010:RvMP, Abbott:2019:PhRvX, EventHorizonTelescopeCollaboration:2019:ApJL, Abbott:2020:arXiv}.
+However, there is a deficiency of observational evidence for black holes in the intermediate-mass range $10^{2} - 10^{6}~\msun$.
+The discovery of an IMBH population will bridge this observational gap, probe IMBH formation environments (e.g.
 accretion disks of active galactic nuclei~\cite{Tagawa:2021:ApJ, Li:2021:arXiv, Samsing:2020:arXiv, Tagawa:2020:ApJ, Ishibashi:2020:A&A, Grobner:2020:A&A, Yang:2019:PhRvL, McKernan:2019:ApJL, Yang:2019:ApJ, McKernan:2018:ApJ, Bellovary:2016:ApJL, McKernan:2014:MNRAS, McKernan:2012:MNRAS}, the centers of dense stellar clusters~\cite{Banerjee:2021:MNRASa, Zevin:2021:ApJ,Mapelli:2021:arXiv,Weatherford:2021:ApJL, Bouffanais:2021:arXiv, Ballone:2021:MNRAS, Kumamoto:2021:arXiv, Banerjee:2021:MNRASb, Martinez:2020:ApJ, Romero-Shaw:2020:ApJL, Anagnostou:2020:PASA}, Population-III stars~\cite{Toubiana:2021:PhRvL, Farrell:2021:MNRAS, Safarzadeh:2020:ApJL, Liu:2020:MNRAS, Inayoshi:2017:MNRAS}), and illuminate our understanding of supermassive black hole formation~\cite{Askar:2021:MNRAS, ArcaSedda:2019:arXiv, Amaro-Seoane:2007:CQGra, Gurkan:2006:ApJL}.
 
-Compact binary coalescences (CBCs) can provide unambiguous gravitational-wave signals for intermediate-mass candidates e.g., the $142^{+28}_{-16}\ \msun$ remnant observed from the gravitational-wave event GW190521~\cite{Abbott:2020:PhRvL} and other candidates~\cite{ligo_imbh_search, ligo_imbh_o3, pycbc_imbh}.
-As a binary's total mass $\text{M}_{T}$ is associated with its gravitational-wave merger frequency, $f\sim \text{M}_{T}^{-1}$,  ground-based gravitational-wave detectors ($f\sim 10^1 - 10^3\ \text{Hz}$) are sensitive to the last milliseconds of merging systems with $100 \msun < \text{M}_{T} < 400 \msun$~\cite{LIGOScientificCollaboration:2015:CQGra, Martynov:2016:PhRvD, Moore_2014}, while space-based detectors ($f \sim 10^{-2} - 10^1\ \text{Hz}$) can study the full signals of merging systems with $10^4 \msun < \text{M}_{T} < 10^7 \msun$~\cite{ Moore_2014, Lu:2019:PhRvD}.
-Because of the short-duration of intermediate-mass gravitational-wave signals in ground-based detectors, data quality is critical for their detection.
+Compact binary coalescences (CBCs) can provide unambiguous gravitational-wave signals for IMBH candidates e.g., the $142^{+28}_{-16}~\msun$ ($90\%$ credible intervals) remnant observed from the gravitational-wave event GW190521~\cite{Abbott:2020:PhRvL} and other candidates~\cite{ligo_imbh_search, ligo_imbh_o3, pycbc_imbh}.
+As a binary's total mass $\text{M}_{T}$ is associated with its gravitational-wave merger frequency, $f\sim \text{M}_{T}^{-1}$,  ground-based gravitational-wave detectors ($f\sim 10^1 - 10^3\ \text{Hz}$) are sensitive to the last milliseconds of merging systems with $100~\msun < \totMlab < 400~\msun$~\cite{LIGOScientificCollaboration:2015:CQGra, Martynov:2016:PhRvD, Moore_2014, Acernese:2015:CQGra}, while space-based detectors ($f \sim 10^{-2} - 10^1\ \text{Hz}$) can study the full signals of merging systems with $10^4~\msun < \totMlab < 10^7~\msun$~\cite{ Moore_2014, Lu:2019:PhRvD}.
+Because of the short duration of IMBH gravitational-wave signals in ground-based detectors, data quality is critical for their detection.
 Gravitational-wave data is characterized by numerous non-stationary terrestrial artifacts called \textit{glitches}~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
-Like signals from intermediate mass mergers, most glitches last for a fraction of a second, making them difficult to distinguish from astrophysical signals.
-These glitches can decrease the sensitivity of searches for binary black hole mergers with total masses $>55$~\msun ~\cite{pycbc_short_duration_transients}.
+Like signals from IMBH mergers, most glitches last for a fraction of a second, making them difficult to distinguish from astrophysical signals.
+These glitches can decrease the sensitivity of searches for binary black hole mergers with $\totMlab\gtrsim55$~\msun ~\cite{pycbc_short_duration_transients}.
 
 Although a significant fraction of the glitches can be identified by testing them for coherence amongst two or more detectors and performing matched-filtering, these methods are insufficient to identify all glitches~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
-One method to discriminate more glitches while searching for CBC is the Bayesian odds~\cite{bci, kanner2016leveraging, BCR1, BCR2, bcr_gw151216, bayesian_odds}.
+One method to discriminate more glitches while searching for CBCs is the Bayesian odds~\cite{bci, kanner2016leveraging, BCR1, BCR2, bcr_gw151216, bayesian_odds}.
 The Bayesian Coherence Ratio \bcr~\cite{BCR1,BCR2} is a Bayesian odds comparing the probability that the data contains coherent signals vs.
 incoherent glitches.
-In this paper, we the \bcr to rank O2's candidate gravitational-wave signals from $55-500\ \msun$ (detector-frame) total mass systems.
-For each candidate, we calculate the probability of astrophysical origin, \pastrobcr and compare to candidate events reported by other authors including the LIGO-Virgo-KAGRA (LVK) collaboration in \GWTC~\cite{GWTC1}, the \pycbc-team~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6, pycbc_single_det, pycbc_ogc_2}, by the Institute of Advanced study's team (\IAS)~\cite{IAS0, IAS1, IAS2}, or by \citet{bayesian_odds}.
+In this paper, we use the \bcr to rank O2's candidate gravitational-wave signals from $55-500~\msun$ lab-frame total mass systems.
+For each candidate, we calculate the probability of astrophysical origin, \pastrobcr and compare to candidate events reported by the LIGO-Virgo-KAGRA (LVK) collaboration in \GWTC~\cite{GWTC1}, the \pycbc-team~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6, pycbc_single_det, pycbc_ogc_2}, by the Institute of Advanced study's team (\IAS)~\cite{IAS0, IAS1, IAS2}, or by \citet{bayesian_odds}.
 
-We find that (a) high-mass events reported in the \GWTC, including GW170729 (the heaviest event in \GWTC) are very statistically significant $\pastrobcr>0.9$; (b) three out of the eight \IAS events and candidates have $\pastrobcr>0.5$, corroborating \IAS's detection claims for GW170304, GW170727, and GW170817A; and that (c) our ranking statistic does not identify any new intermediate-mass black holes, but does identify an unreported marginal stellar-mass binary black hole candidate, 170222 with $\pastrobcr\sim0.5$.
-%\avi{Need to doublecheck that this wasn't in the PyCBC sub-threshold paper}.
+We find that (a) events reported in \GWTC, including GW170729 (likely the most massive BBH system in \GWTC) are statistically significant $\pastrobcr>0.9$; (b) three out of the eight \IAS events and candidates have $\pastrobcr>0.5$, corroborating \IAS's detection claims for GW170304, GW170727, and GW170817A; and that (c) our ranking statistic does not identify any new IMBH, but does identify an unreported marginal stellar-mass binary black hole candidate, 170222 with $\pastrobcr\sim0.5$.
 
@@
 Here, we explore a hybrid frequentist/Bayesian ranking statistic that makes use of the Bayesian evidence.
-We compute the Bayesian evidence under the assumption that they either contain a coherent gravitational-wave signal, noise, or a glitch ($Z^S, Z^N, Z^G$, defined in Appendix~\ref{sec:bayesianEvidEval}).
+We compute the Bayesian evidence under the assumption that the data either contain a coherent gravitational-wave signal, noise, or a glitch ($Z^S, Z^N, Z^G$, defined in Appendix~\ref{sec:bayesianEvidEval}).
 However, instead of computing true Bayesian odds, we use the evidences as a ranking statistic.
@@
 We also acquire background and simulated triggers from \pycbc to calculate \bgrdbcr and estimate values for $\{\hat{\pi}^S,\hat{\pi}^G\}$ (see Appendix~\ref{apdx:tuning-prior-odds} for details on the estimation process).
-Note that the triggers are divided into two week time-frames because the detector's sensitivity does not stay constant throughout the eight-month-long observing period~\cite{pycbc_og4}.
+The triggers are divided into two week time-frames because the detector's sensitivity does not stay constant throughout the eight-month-long observing period~\cite{pycbc_og4}.
 
 \begin{table}[t]
-\caption[BBH parameters correspond to duration $<454\ \text{ms}$]{\label{tab:parameters}Trigger-selection parameter space (parameters correspond to signals with durations $<454 \ \text{ms}$). }
+\caption[BBH parameters correspond to duration $<454\ \text{ms}$]{\label{tab:parameters}Trigger-selection lab-frame parameter space (parameters correspond to signals with durations $<454 \ \text{ms}$ and $q\geq0.1$).}
 \centering
@@
 Chirp Mass [\msun] & 8.00 & 174.56\\
-Mass Ratio & 0.01 & 0.98\\
+Mass Ratio & 0.1 & 0.98\\
 \end{tabular}
@@
 
-For our study, we filter triggers to include those in the parameter ranges presented in Table~\ref{tab:parameters}.
-This region focuses our analysis on binary black hole mergers with total masses above $> 55 \msun$, corresponding to binary systems with signal durations $<454 \ \text{ms}$.
+For our study, we filter \pycbc triggers to include only those in the parameter ranges presented in Table~\ref{tab:parameters}.
+This region focuses our analysis on binary black hole mergers with total masses above $\gtrsim55 \msun$, corresponding to binary systems with signal durations $<454 \ \text{ms}$ and $q\geq0.1$.
 The filtering process leaves us with $60,996$ background, $5,146$ simulated, and $25$ candidate signal triggers.
 We also include events and candidate events reported by \GWTC and the \IAS group in our list of candidate signal triggers.
-A plot of the \pycbc triggers from April 23 - May 8, 2017, is presented in Fig.~\ref{fig:templateBank}.
-This figure also depicts the gravitational-wave templates used by \pycbc's search.
+A plot of the component mass space constrained by our trigger filter is presented in Fig.~\ref{fig:templateBank}.
 
@@
 % 1178294418, May 08, 2017, 16:00 UTC
-\caption[ BCR search space.]{The templates (pink) used by \pycbc to search a section of O2 data from $\text{April 23 - May 8, 2017}$.
-Our search is constrained to the parameter space enclosed by the dashed line.
-The candidate, background, and simulated triggers detected in this region of the parameter space during this period are plotted in orange, gray, and blue, respectively.}\label{fig:templateBank}
+\caption[ BCR search space.]{Component-mass boundaries for our trigger filter and parameter estimation prior.
+Our search is constrained to the parameter space enclosed by the gold-colored hatches, while our prior is constrained to the slightly larger parameter space enclosed by the teal-colored hatches.
+The purple region labeled ``IMBH'' is the parameter space where merger remnants may be IMBHs.}\label{fig:templateBank}
 \end{figure*}
@@
     \caption{
-    Prior settings for the parameters used during our parameter estimation.
+    Prior settings for the lab-frame parameters used during our parameter estimation.
 The definitions of the parameters are documented in \citet{bilby_gwtc}~Table~E1.
@@
           $d_\mathrm{L}/\mathrm{Mpc}$   & Comoving & 100--5000  \\
-          $a_1$, $a_2$                  & Uniform & 0--1  \\
+          $\chi_1$, $\chi_2$            & Uniform & -1--1  \\
           $\theta_{JN}$                 & Sinusoidal & 0--$\pi$  \\
@@
 
-Finally, with the \candbcr and \bgrdbcr, we calculate the candidate signal's \pastrobcr. We present the \pastrobcr with \pastro of other pipelines for comparison in Table~\ref{tab:results}.
+Finally, with the \candbcr and \bgrdbcr for each time-frame of triggers, we calculate the candidate signal's \pastrobcr.
 
@@
 
-Various pipeline \pastro are not mathematically equivalent~\cite{Galaudage:2020:PhRvD}.
-However, by comparing pipeline \pastro values for a given candidate along with \pastrobcr in Table~\ref{tab:results}, we can compare how significant each pipeline deems various candidates.
-Note that the $\hat{\pi}^S$ and $\hat{\pi}^G$ values utilized for each time-frame are reported in Appendix~\ref{apdx:alphabeta}.
+We analyze the O2 candidates with $\totMlab > 55~\msun$ and report candidates with $\pastrobcr\geq0.3$ in Table~\ref{tab:results}.
+The $\hat{\pi}^S$ and $\hat{\pi}^G$ values utilized for each time-frame are reported in Appendix~\ref{apdx:alphabeta}.
+
+Various search pipeline \pastro are not mathematically equivalent~\cite{Galaudage:2020:PhRvD}.
+Moreover, \pastro is not equivalent to \pastrobcr.
+However, by comparing a candidate's pipeline \pastro with its \pastrobcr, we can compare how significant each pipeline deems the candidate.
+For comparison, in Table~\ref{tab:results} we report \pastro values from \GWTC~\cite{GWTC1}, PyCBC OGC-2~\cite{pycbc_ogc_2}, PyCBC OGC-3~\cite{pycbc_ogc_2}, PyCBC `single-search'~\cite{pycbc_single_det}, IAS~\cite{IAS1, IAS2}, and \citet{bayesian_odds}'s analyses.
 
@@
 In addition to the above confirmed gravitational-wave events from \GWTC, we have also analyzed several candidate events from \GWTC, most of which have low \pastrobcr.
-For example, consider the candidate event 170412, assigned a $\pastro$ of $0.06$ by \gstlal and has a $\pastrobcr$ of $0.01$.
+For example, consider the candidate event 170412 ($\tc = 1176047817$), assigned a $\pastro$ of $0.06$ by \gstlal and has a $\pastrobcr$ of $0.01$.
 This candidate was reported to be excess power caused due to noise appearing non-stationary between 60-200 Hz~\cite{GWTC1}.
@@
 \subsection{IAS Events}
-Our analysis of the IAS events and candidates with $M_T>55\ \msun$ in O2 has resulted in three events with disfavored $\pastrobcr<0.5$ (GWC170402, GW170403, GW170425), and four events and one candidate with $\pastrobcr\geq0.5$ (GW170121, 170302, GW170304, GW170727, GW170817A).
-While GW170727 and GW170817A's \pastrobcr are similar to the \pastro reported from IAS (the differences between \pastrobcr and the IAS \pastro is $|\Delta p |<0.1$), the remaining candidates have contradicting \pastrobcr and  \pastro values (with $|\Delta p| > 0.15$).
+Our analysis of the IAS events and candidates with $\totMlab\gtrsim55~\msun$ in O2 has resulted in one event with disfavored $\pastrobcr<0.5$ (GW170425), and five events and two candidates with $\pastrobcr\geq0.5$ (GW170121, GW170304, 170302, GWC170402, GW170403, GW170727, GW170817A).
+From this list, four events (GW170121, GW170304, GW170727, GW170817A) have $\pastrobcr>0.8$ and $\pastro>0.9$ reported from other pipelines, making them viable gravitational-wave event candidates.
 
 GWC170402, detected by \citet{IAS2}, is reported to originate from a binary with non-zero eccentricity~\cite{IAS2}.
-Hence, we might have computed a low \pastrobcr due to our usage of \imrphenomp, a waveform that does not account for eccentricity.
-Additionally, the search conducted by \citet{IAS2} was a single-detector search.
-Our ranking statistic relies on the signal to appear coherent, even if just faintly coherent, amongst the various detectors to have a high \pastrobcr.
-The lack of coherence and the non-eccentric waveform may be the leading factors for a low \pastrobcr.
-GW170403 and GW170425 which have $\pastrobcr<0.35$ also have low  \pastro reported by \citet{pycbc_ogc_2},  suggesting that these events may have been false alarms.
-
-From the candidates with $\pastrobcr>0.5$, GW170727 and 170302 are of particular interest, with \pastrobcr of $0.92$ and $0.63$.
-GW170727 was emitted from a black hole binary system with a source frame total mass $\approx 70\ \msun$.
-In addition to the high \pastrobcr reported by our study, \citet{IAS1} and \citet{pycbc_ogc_2} have also reported high \pastro values of 0.98 and 0.99, making it a viable gravitational-wave event candidate.
-Similarly, the sub-marginal-candidate 170302 reported by \cite{IAS1} with a \pastro of 0.45 appears to have a higher significance from our analysis, resulting in a \pastrobcr of $0.63$.
+As we used a non-eccentric waveform during analysis, we may be under estimating this event's significance at $\pastrobcr\leq0.6$.
+Finally, GW170425 which has $\pastrobcr<0.25$ also has low \pastro reported in OGC-2 and OGC-3 \cite{pycbc_ogc_2,pycbc_ogc_3}, suggesting that GW170425 may have been false alarm.
 
 \subsection{New Candidate Events}
-Although no clear detections are made with the \bcr, a marginal-candidate 170222 has been discovered with a $\pastrobcr\sim0.5$.
-This candidate has a SNR$\sim7.7$, low spin magnitudes, and source-frame component masses of $({47.16}_{-5.77}^{+8.00}, {35.50}_{-6.35}^{+5.79}) \msun$, making it one of the heavier black-hole mergers from O2 and \GWTC.
+Although no IMBH detections are made with the \bcr, a marginal stellar mass black hole merger candidate 170222 has been discovered with a $\pastrobcr\sim0.6$.
+This candidate has a SNR$\sim7.7$, low spin magnitudes, and source-frame component masses of $({47.16}_{-5.77}^{+8.00}, {35.50}_{-6.35}^{+5.79}) \msun$ ($90\%$ credible intervals), making it one of the heavier black-hole mergers from O2 and \GWTC.
 This candidate may be of interest as one component black hole may lie in the pair-instability mass gap ($55^{+10}_{-10}-148^{+13}_{-12}\msun$)~\cite{Woosley:2021:arXiv, Heger:2002:ApJ}.
 More details on the candidate are presented in Appendix~\ref{apdx:170222}.
-The remaining coherent trigger candidates all have $\pastrobcr\ll0.5$, making them unlikely to originate from astrophysical sources.
+The remaining coherent trigger candidates all have $\pastrobcr<0.5$, making them unlikely to originate from astrophysical sources.
 
@@
 
-In this paper, we demonstrate that the Bayesian Coherence Odds-Ratio \bcr~\cite{BCR1} can be used as a ranking statistic to provide a measure of significance for gravitational-wave signals originating from CBCs with total masses between $55\msun$ and $400\msun$, a range that includes intermediate-mass black holes.
+In this paper, we demonstrate that the Bayesian Coherence Odds-Ratio \bcr~\cite{BCR1} can be used as a ranking statistic to provide a measure of significance for gravitational-wave signals originating from CBCs with total masses between $55~\msun$ and $400~\msun$, a range that includes IMBHs.
 To compute the \bcr for candidates, we utilize Bayesian inference to explicitly calculate the probability of data under various hypotheses (the hypotheses that the data contains a coherent signal, just noise, or an incoherent glitch).
-This Bayesian ranking method takes a step towards building a unified Bayesian framework that provides a search-pipeline agnostic measure of significance for candidates and estimates their parameters, utilizing the same level of physical information incorporated during detected parameter estimation studies.
+This Bayesian ranking method takes a step towards building a unified Bayesian framework that provides a measure of significance for candidates and estimates their parameters, utilizing the same level of physical information incorporated during detected parameter estimation studies.
 
-In our study, we analyze O2 binary-black hole events and candidates with $M_T > 55 \msun$ reported by the \pycbc search~\cite{pycbc_ogc_2}, the \IAS-team~\cite{IAS1, IAS2} and those reported in \GWTC~\cite{GWTC1}.
+In our study, we analyze O2 binary-black hole events and candidates with $\totMlab > 55~\msun$ reported by the \pycbc search~\cite{pycbc_ogc_2}, the \IAS-team~\cite{IAS1, IAS2} and those reported in \GWTC~\cite{GWTC1}.
 Using \pastrobcr, we find that the \GWTC events have high probabilities of originating from an astrophysical source.
 We also find that some of the \GWTC marginal triggers that have corroborated terrestrial sources (for example, candidate 170412) have low \pastrobcr, indicating this method's ability to discriminate between terrestrial artifacts and astrophysical signals.
-Our analysis of the \IAS events demonstrates that GW170121, GW170727, and GW170817A are likely to originate from astrophysical sources, while GWC170402, GW170402, and GW170425  are not.
+Our analysis of the \IAS events demonstrates that GW170121, GW170304, GW170727, and GW170817A are likely to originate from astrophysical sources ($\pastrobcr\geq0.8$), while GW170425 is not ($\pastrobcr<0.25$).
 Finally, we do not identify any new gravitational-wave events, but we find a new marginal binary-black hole merger candidate, 170222.
 
-Although our analysis targets triggers with $M_T > 55 \msun$, this method can be extended to include the entire range of LIGO-detectable gravitational-wave sources.
+Although our analysis targets triggers with $\totMlab \gtrsim 55~\msun$, this method can be extended to include the entire range of LIGO-detectable gravitational-wave sources.
 Additionally, to further improve the method's infrastructure, we can use more robust gravitational-wave templates (such as templates that incorporate higher-order modes and orbital precession) and sophisticated glitch models.
@@
 
-% \greg{can we better constraint their population properties? Do we know how much (if at all) this method outperforms current searches?}
-
-% \avi{Unlike for stellar-mass BBH, there are still a lot of uncertainties for IMBH formation scenarios.
-Hence, upper limits would be challenging to calculate.
-Additionally, we would require to do more robust simulation studies to see what would fall in/outside our detection threshold, to put constraints on population properties, and study the search's sensitivity.
-% }
-
-%%%%%%---SECTIONS-END---%%%%%%%%%%%%
-
 %%%%%%---ACKNOWLEDGMENTS---%%%%%%%%%%%%
 \begin{acknowledgments}
-This work is supported by the Australian Research Council (ARC) Centre of Excellence CE170100004.
 The authors gratefully thank the \pycbc team for providing the gravitational-wave foreground, background, and simulated triggers from \pycbc's search of O2's data.
@@
 
-We thank Stuart Anderson for accommodating this analysis performed on the California Institute of Technology computing cluster.
-All analyses (inclusive of test and failed analyses) performed for this study used $~1.3\mathrm{M}$ core-hours, amounting to a carbon footprint of $~167\ \mathrm{t}$ of CO$^2$ (using the U.S.
+We gratefully acknowledge the computational resources provided by the LIGO Laboratory—Caltech Computing Cluster and supported by NSF grants PHY-0757058 and PHY-0823459, and thank Stuart Anderson for his assistance in resource scheduling.
+
+All analyses (inclusive of test and failed analyses) performed for this study used $~1.3\mathrm{M}$ core-hours, amounting to a carbon footprint of $~167\ \mathrm{t}$ of CO$_2$ (using the U.S.
 average electricity source emissions of $0.429\ \text{kg/kWh}$~\cite{greenhouse} and $0.3\ \text{kWh}$ for each CPU).
 
+This work is supported by the Australian Research Council (ARC) Centre of Excellence CE170100004.
+This material is based upon work supported by NSF’s LIGO Laboratory, a major facility fully funded by the National Science Foundation.
 This research has used data, software, and web tools obtained from the Gravitational Wave Open Science Center (https://www.gw-openscience.org), a service of LIGO Laboratory, the LIGO Scientific Collaboration, and the Virgo Collaboration.
-LIGO is funded by the U.S.
-National Science Foundation.
+The U.S.
+National Science Foundation funds LIGO.
 Virgo is funded by the French Centre National de Recherche Scientifique (CNRS), the Italian Istituto Nazionale della Fisica Nucleare (INFN), and the Dutch Nikhef, with contributions by Polish and Hungarian institutes.
@@
 Vertical lines mark the $\text{ln}\ \bcr$ of \IAS's GW170817A and \GWTC's GW170814.
-    Left: Survival functions with using the post-processing step to marginalize over PSD statistical uncertainties.
+    Left: Survival functions using the post-processing step to marginalize over PSD statistical uncertainties.
 Right: Survival functions without the post-processing step.
-Without the post-processing step, there is a greater overlap between the background (gray) and foreground (blue) survival functions
+Without the post-processing step, there is a greater overlap between the background (gray) and foreground (blue) survival functions.
     \label{fig:bcrCdf}}
@@
 \section{A closer look at 170222}\label{apdx:170222}
-PyCBC found the candidate 170222 with $\mathcal{M}_c=49.46$ and $q=0.68$, values that fall within our uncertainty limits.
-Some of the posteriors that were produced as a by-product of our \bcr calculation can be viewed in Fig.~\ref{fig:170222}.
+PyCBC found the candidate 170222 with $\mathcal{M}_c=49.46$ and $q=0.68$, values contained inside the $90\%$ credible intervals of our posterior probability distributions for 170222.
+Some of the posteriors produced as a by-product of our \bcr calculation can be viewed in Fig.~\ref{fig:170222}.
 
@@
 
-\bibliography{high_mass_bib}% Produces the bibliography via BibTeX.
+\bibliography{high_mass_bib}
 
 \end{document}
-%
-% ****** End of file apssamp.tex ******

### 2021-07-06 scripts/make_bcr_cdf.py
update data

@@ -42,14 +42,14 @@ DATA = dict(
 )
 
 
-def plot(data_type, add_legend=False):
+def plot(data_type, add_legend=False, alpha=1.0e-6, beta=1.0e-4, fname_label=""):
     plot_data = pack_plotting_data(
         foreground_csv=DATA[data_type][FOREGROUND],
         background_csv=DATA[data_type][BACKGROUND],
         injection_csv=DATA[data_type][INJECTION],
         rank="lnBCR",
-        alpha=1.0e-6,
-        beta=1.0e-4,
+        alpha=alpha,
+        beta=beta,
     )
     xrange = dict(min=-15, max=30)
     fig, ax_cdf = plt.subplots(nrows=1, ncols=1, figsize=(7, 5))
@@ -80,7 +80,7 @@ def plot(data_type, add_legend=False):
             fontsize="small",
             loc="lower right",
             facecolor="white",
-            framealpha=0.2,
+            framealpha=0.5,
             handlelength=0.75,
             handletextpad=0.3,
             labelspacing=0.2,
@@ -97,10 +97,10 @@ def plot(data_type, add_legend=False):
             **lg_kwargs,
         )
         frame = l.get_frame()
-        frame.set_linewidth(0)
+        frame.set_linewidth(0.2)
         bbox_extra_artists.append(l)
 
-    fname = f"images/{data_type}_bcr_cdf_smaller_legend.png"
+    fname = f"images/{data_type}_bcr_cdf_smaller_legend{fname_label}.png"
 
     ax_cdf.yaxis.set_major_formatter(FormatStrFormatter("% 1.1f"))
     fig.savefig(
@@ -113,8 +113,10 @@ def plot(data_type, add_legend=False):
 
 def main():
     print("Plotting CDFs")
+    # plot("orig", add_legend=False)
     plot("orig")
     plot("reweighted")
+    plot("reweighted", alpha=1, beta=1, fname_label="_untuned")
 
 
 if __name__ == "__main__":

### 2021-07-06 scripts/make_results_table.py

@@ -1,0 +1,219 @@
+"""
+Example table:
+\begin{table*}
+\centering
+\caption{}
+\label{tab:results}
+\def\arraystretch{1.5}
+\setlength{\tabcolsep}{0.5em}
+\begin{NiceTabular}{@{}ll!{\quad}|c|!{\quad}cc!{\quad}c!{\quad}c!{\quad}ccc!{\quad}|c@{}}
+\CodeBefore
+    \rowcolor{white}{1-3}
+    \rowcolors{2}{white}{gray!5}
+\Body
+Col1 & Col1 & AA                & b.1  & b.2                 & CC   & DD   & e.1              & e.2   & e.3   & Col4       \\
+\midrule
+dat1 & 111  & 0.00              & 1.00            & 1.00     &      & 1.00 &                  & 1.00  &       & 111111.00  \\
+dat2 & 222  & 0.00              &                 & 1.00     & 1.00 & 0.50 &                  & 1.00  & 1.00  & 222222.00  \\
+dat3 & 333  & 0.00              &                 &          &      &      &                  &       &       & 333333.00  \\
+dat4 & 444  & 0.00              &                 &          &      &      &                  &       &       & 444444.00  \\
+% \bottomrule
+\end{NiceTabular}
+\end{table*}
+
+"""
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+
+RES = "data/results.csv"
+
+MAIN_TABLE_CAPTION = """
+$\pastrobcr$ table for gravitational wave events and candidates in our search space with $\pastrobcr>0.2$.   
+Displayed for comparison are significances of events taken from: 
+GstLAL \pastroGwtcGstlal~\cite{GWTC1}, 
+PyCBC \pastroGwtcPycbc~\cite{GWTC1}, 
+IAS \pastroIas~\cite{IAS1, IAS2},  
+\pastroPrat~\cite{bayesian_odds}, 
+PyCBC `single-search' \pastroSing~\cite{pycbc_single_det}, 
+PyCBC OGC-2 \pastroOgcTwo~\cite{pycbc_ogc_2} and
+PyCBC OGC-3 \pastroOgcThree~\cite{pycbc_ogc_2}.
+The $\\tc$ column contains the `GPS' coalescence-times of the gravitational wave events. 
[…]

### 2021-07-06 scripts/make_template_plot.py

@@ -1,20 +1,144 @@
 """
 Module to plot "template_bank.png"
 """
+
 import numpy as np
 import pandas as pd
 from bilby.gw import conversion
 from matplotlib import pyplot as plt
-from settings import set_matplotlib_style_settings
+from settings import set_matplotlib_style_settings, line_annotate
+from matplotlib.patches import Polygon
+import matplotlib.patches as mpatches
 from tqdm import tqdm
-
-
+from matplotlib import rcParams
 
 BANK = "data/template_bank.csv"
 INJECTION = "data/chunk14/injection_triggers.csv"
 BACKGROUND = "data/chunk14/background_triggers.csv"
 FOREGROUND = "data/chunk14/foreground_triggers.csv"
 CATALOG = "data/catalog.csv"
+
+ZORDER = dict(
+    qline=3,
+    regions=0,
+    region_text=4,
+    upper_shade=1,
+    prior=1,
+    filter=2,
+
+)
+
+N = 1000
+PRI_COL, FILT_COL = "teal", "gold"
+
+
+def add_shaded_regions(ax):
+    xlim, ylim = ax.get_xlim()[1], ax.get_ylim()[1]
+
+    # Make the shaded region for m2 > m1
+    verts = [(0, 0), (0, 1000), (1000,1000)]
+    poly = Polygon(verts, facecolor='white', alpha=0.6, zorder=ZORDER['upper_shade'])
+    ax.add_patch(poly)
+
+    BNS = dict(min=[1,1], max=[3,3])
+    BBH = dict(min=[5,5], max=[95,95])
+    IMBH = dict(min=[5, 5], max=[1000,1000])
+    NSBH = dict(min=[5,1], max=[1000,3])
+    BNS_COL = "tab:blue"
+    GAP_COL = "tab:green"
+    BBH_COL = "tab:red"
+    IMBH_COL = "tab:purple"
+    NSBH_COL = "tab:orange"
+
+    alpha = 0.5
+    # Make the BNS region
+
+    verts = [
+        (BNS['min'][0], BNS['min'][1]),
+        (BNS['min'][0], BNS['max'][1]),
+        (BNS['max'][0], BNS['max'][1]),
+        (BNS['max'][0], BNS['min'][1])
+    ]
+    poly = Polygon(verts, facecolor=BNS_COL, alpha=alpha, zorder=ZORDER['regions'])
+    ax.add_patch(poly)
[…]

### 2021-07-06 scripts/settings.py

@@ -1,7 +1,7 @@
 from matplotlib import rcParams
 
 
-def set_matplotlib_style_settings(major=7, minor=3, linewidth=1.5, grid=False):
+def set_matplotlib_style_settings(major=7, minor=3, linewidth=1.5, grid=False, mirror=True):
     rcParams["font.size"] = 30
     rcParams["font.family"] = "serif"
     rcParams["font.sans-serif"] = ["Computer Modern Sans"]
@@ -23,7 +23,128 @@ def set_matplotlib_style_settings(major=7, minor=3, linewidth=1.5, grid=False):
     rcParams["xtick.major.width"] = linewidth
     rcParams["ytick.minor.width"] = linewidth
     rcParams["ytick.major.width"] = linewidth
-    rcParams["xtick.top"] = True
-    rcParams["ytick.right"] = True
+    if mirror:
+        rcParams["xtick.top"] = True
+        rcParams["ytick.right"] = True
     rcParams["axes.grid"] = grid
     rcParams["axes.titlepad"] = 8
+
+
+
+import numpy as np
+from matplotlib.text import Annotation
+from matplotlib.transforms import Affine2D
+
+
+class LineAnnotation(Annotation):
+    """A sloped annotation to *line* at position *x* with *text*
+    Optionally an arrow pointing from the text to the graph at *x* can be drawn.
+    Usage
+    -----
+    fig, ax = subplots()
+    x = linspace(0, 2*pi)
+    line, = ax.plot(x, sin(x))
+    ax.add_artist(LineAnnotation("text", line, 1.5))
+    """
+
+    def __init__(
+            self, text, line, x, xytext=(0, 5), textcoords="offset points", **kwargs
+    ):
+        """Annotate the point at *x* of the graph *line* with text *text*.
+
+        By default, the text is displayed with the same rotation as the slope of the
+        graph at a relative position *xytext* above it (perpendicularly above).
+
+        An arrow pointing from the text to the annotated point *xy* can
+        be added by defining *arrowprops*.
+
+        Parameters
+        ----------
+        text : str
+            The text of the annotation.
+        line : Line2D
+            Matplotlib line object to annotate
+        x : float
+            The point *x* to annotate. y is calculated from the points on the line.
+        xytext : (float, float), default: (0, 5)
+            The position *(x, y)* relative to the point *x* on the *line* to place the
+            text at. The coordinate system is determined by *textcoords*.
+        **kwargs
[…]

### 2021-07-21 main.tex
ready for submission!

@@
 \usepackage{units}
-\usepackage{xcolor} % for more colours!
+\usepackage[dvipsnames]{xcolor} % for more colours!
 \usepackage{lineno}
@@
 \usepackage[T1]{fontenc}
-\usepackage[breaklinks]{hyperref}
+% \usepackage[breaklinks]{hyperref}
 \usepackage{xspace} 
@@
 \usepackage{graphicx} % Include figure files
+\usepackage[bottom]{footmisc}
+\usepackage[colorlinks,urlcolor=NavyBlue,citecolor=NavyBlue,linkcolor=NavyBlue]{hyperref}
 
@@
 
-% symbols
-\DeclareSymbolFont{extraup}{U}{zavm}{m}{n}
-\DeclareMathSymbol{\varheart}{\mathalpha}{extraup}{86}
-\DeclareMathSymbol{\vardiamond}{\mathalpha}{extraup}{87}
+% Software
+\newcommand{\code}[1]{{\texttt{#1}}\xspace}
+\newcommand{\bilby}{\code{bilby}}
+\newcommand{\bilbypipe}{\code{bilby-pipe}}
+\newcommand{\dynesty}{\code{dynesty}}
+\newcommand{\gwpy}{\code{GWpy}}
 
 % Keywords
-\newcommand{\bilby}{{\sc \href{https://lscsoft.docs.ligo.org/bilby/}{\texttt{Bilby}}}\xspace}
-\newcommand{\bilbypipe}{{\sc \texttt{bilby\_pipe}}\xspace}
-\newcommand{\dynesty}{{\sc \texttt{dynesty}}\xspace}
-\newcommand{\cpnest}{{\sc cpnest}\xspace}
-\newcommand{\ptemcee}{{\sc ptemcee}\xspace}
-\newcommand{\gwpy}{{\sc \href{https://gwpy.github.io/}{\texttt{GWpy}}}\xspace}
 \newcommand{\imrphenomp}{{\sc \texttt{IMRPhenomPv2}}\xspace}
@@
 \newcommand{\mbta}{{\sc MBTAOnline}\xspace}
-\newcommand{\pycbc}{{\sc \href{https://pycbc.org/}{{PyCBC}}}\xspace}
-\newcommand{\GWTC}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2019PhRvX...9c1040A/abstract}{{GWTC-1}}}\xspace}
-\newcommand{\OGC}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2020ApJ...891..123N/abstract}{{2-OGC}}}\xspace}
-\newcommand{\IAS}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2020PhRvD.101h3030V/abstract}{{IAS}}}\xspace}
+
+% \newcommand{\pycbc}{{\sc \href{https://pycbc.org/}{{PyCBC}}}\xspace}
+% \newcommand{\GWTC}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2019PhRvX...9c1040A/abstract}{{GWTC-1}}}\xspace}
+% \newcommand{\OGC}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2020ApJ...891..123N/abstract}{{2-OGC}}}\xspace}
+% \newcommand{\IAS}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2020PhRvD.101h3030V/abstract}{{IAS}}}\xspace}
+
+\newcommand{\pycbc}{{\sc {{PyCBC}}}\xspace}
+\newcommand{\GWTC}{{\sc {{GWTC-1}}}\xspace}
+\newcommand{\OGC}{{\sc {{2-OGC}}}\xspace}
+\newcommand{\IAS}{{\sc {{IAS}}}\xspace}
 
@@
 
-% author comments
-\newcommand{\avi}[1]{\textcolor{orange}{[AV: #1]}}
-\newcommand{\greg}[1]{\textcolor{purple}{[Greg: #1]}}
-\newcommand{\rs}[1]{\textcolor{red}{[RS: #1]}}
-\newcommand{\et}[1]{\textcolor{blue}{[ET: #1]}}
-
 \begin{document}
@@
 The detection of an intermediate-mass black hole population ($10^2-10^6$~\msun) will provide clues to their formation environments (e.g., disks of active galactic nuclei, globular clusters) and illuminate a potential pathway to produce supermassive black holes.
-Ground-based gravitational-wave detectors are in principle sensitive to a subset of such mergers mergers and have been used to detect one $142^{+28}_{-16}~\msun$ intermediate-mass black hole formation event.
-Ground-based detector data contain numerous short duration noise transients that can mimic the gravitational-wave signals from merging intermediate-mass black holes, limiting the sensitivity of searches.
-Here we demonstrate a Bayesian-inspired ranking statistic to detect binary black hole mergers with a lab-frame total mass $\gtrsim55$~\msun.
+Ground-based gravitational-wave detectors are sensitive to a subset of such mergers and have been used to detect one $142^{+28}_{-16}~\msun$ intermediate-mass black hole formation event.
+However, ground-based detector data contain numerous incoherent short duration noise transients that can mimic the gravitational-wave signals from merging intermediate-mass black holes, limiting the sensitivity of searches.
+Here we search for binary black hole mergers using a Bayesian-inspired ranking statistic which measures the coherence or incoherence of triggers in multiple-detector data.
 We use this statistic to identify candidate events with lab-frame total masses $\gtrsim55$~\msun using data from LIGO's second observing run.
@@
 
-A variety of techniques have been employed to search for $10^{4} - 10^{6}~\msun$ intermediate-mass black hole (IMBH) candidates including reverberation mapping~\cite{Peterson:2014:SSRv}, direct kinematic measurements~\cite{Schodel:2002:Natur, Kiziltan:2017:Natur}, applying macroscopic galaxy to black hole mass scaling relations ($M_{BH}$-$\sigma$ and $M_{BH}$-L relations)~\cite{Graham:2013:ApJ, Wevers:2017:MNRAS}, studying  X-ray luminosity and spectra~\cite{Greene:2004:ApJ, Lin:2020:ApJL}, gravitational lensing of gamma-ray burst light curves~\cite{paynter_evidence_2021}, and others~\cite{Greene:2020:ARA&A, Koliopanos:2017:mbhe, Mezcua:2017:IJMPD}).
+A variety of techniques have been employed to search for ${10^{4} - 10^{6}~\msun}$ intermediate-mass black hole (IMBH) candidates including reverberation mapping~\cite{Peterson:2014:SSRv}, direct kinematic measurements~\cite{Schodel:2002:Natur, Kiziltan:2017:Natur}, applying macroscopic galaxy to black hole mass scaling relations ($M_{BH}$-$\sigma$ and $M_{BH}$-L relations)~\cite{Graham:2013:ApJ, Wevers:2017:MNRAS}, studying  X-ray luminosity and spectra~\cite{Greene:2004:ApJ, Lin:2020:ApJL}, gravitational lensing of gamma-ray burst light curves~\cite{paynter_evidence_2021}, and others~\cite{Greene:2020:ARA&A, Koliopanos:2017:mbhe, Mezcua:2017:IJMPD}).
 However, because IMBH have smaller gravitational spheres of influence than those of supermassive black holes, it is much more challenging to observe them with these observational techniques~\cite{Mezcua:2017:IJMPD}.
@@
 
-Stellar mass ($M_\text{BH} < 10^{2}~\msun$) and supermassive black holes ($M_\text{BH} > 10^{6}~\msun$) have been observed and well studied since the 1970s~\cite{Webster:1972:Natur, Balick:1974:ApJ, Ghez:1998:ApJ, Genzel:2010:RvMP, Abbott:2019:PhRvX, EventHorizonTelescopeCollaboration:2019:ApJL, Abbott:2020:arXiv}.
-However, there is a deficiency of observational evidence for black holes in the intermediate-mass range $10^{2} - 10^{6}~\msun$.
+Stellar mass (${M_\text{BH} < 10^{2}~\msun}$) and supermassive black holes (${M_\text{BH} > 10^{6}~\msun}$) have been observed and well studied since the 1970s~\cite{Webster:1972:Natur, Balick:1974:ApJ, Ghez:1998:ApJ, Genzel:2010:RvMP, Abbott:2019:PhRvX, EventHorizonTelescopeCollaboration:2019:ApJL, Abbott:2020:arXiv}.
+However, there is a deficiency of observational evidence for black holes in the intermediate-mass range ${10^{2} - 10^{6}~\msun}$.
 The discovery of an IMBH population will bridge this observational gap, probe IMBH formation environments (e.g.
@@
 
-Compact binary coalescences (CBCs) can provide unambiguous gravitational-wave signals for IMBH candidates e.g., the $142^{+28}_{-16}~\msun$ ($90\%$ credible intervals) remnant observed from the gravitational-wave event GW190521~\cite{Abbott:2020:PhRvL} and other candidates~\cite{ligo_imbh_search, ligo_imbh_o3, pycbc_imbh}.
-As a binary's total mass $\text{M}_{T}$ is associated with its gravitational-wave merger frequency, $f\sim \text{M}_{T}^{-1}$,  ground-based gravitational-wave detectors ($f\sim 10^1 - 10^3\ \text{Hz}$) are sensitive to the last milliseconds of merging systems with $100~\msun < \totMlab < 400~\msun$~\cite{LIGOScientificCollaboration:2015:CQGra, Martynov:2016:PhRvD, Moore_2014, Acernese:2015:CQGra}, while space-based detectors ($f \sim 10^{-2} - 10^1\ \text{Hz}$) can study the full signals of merging systems with $10^4~\msun < \totMlab < 10^7~\msun$~\cite{ Moore_2014, Lu:2019:PhRvD}.
+Compact binary coalescences (CBCs) can provide unambiguous gravitational-wave signals for IMBH candidates e.g., the ${142^{+28}_{-16}~\msun}$ ($90\%$ credible intervals) remnant observed from the gravitational-wave event GW190521~\cite{Abbott:2020:PhRvL} and other candidates~\cite{ligo_imbh_search, ligo_imbh_o3, pycbc_imbh}.
+As a binary's total mass $M_{T}$ is associated with its gravitational-wave merger frequency, $f\sim M_{T}^{-1}$,  ground-based gravitational-wave detectors (${f\sim 10^1 - 10^3\ \text{Hz}}$) are sensitive to the last milliseconds of merging systems with ${100~\msun < \totMlab < 400~\msun}$~\cite{LIGOScientificCollaboration:2015:CQGra, Martynov:2016:PhRvD, Moore_2014, Acernese:2015:CQGra}, while space-based detectors (${f \sim 10^{-2} - 10^1\ \text{Hz}}$) can study the full signals of merging systems with ${10^4~\msun < \totMlab < 10^7~\msun}$~\cite{ Moore_2014, Lu:2019:PhRvD}.
 Because of the short duration of IMBH gravitational-wave signals in ground-based detectors, data quality is critical for their detection.
@@
 incoherent glitches.
-In this paper, we use the \bcr to rank O2's candidate gravitational-wave signals from $55-500~\msun$ lab-frame total mass systems.
-For each candidate, we calculate the probability of astrophysical origin, \pastrobcr and compare to candidate events reported by the LIGO-Virgo-KAGRA (LVK) collaboration in \GWTC~\cite{GWTC1}, the \pycbc-team~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6, pycbc_single_det, pycbc_ogc_2}, by the Institute of Advanced study's team (\IAS)~\cite{IAS0, IAS1, IAS2}, or by \citet{bayesian_odds}.
+In this paper, we use the \bcr to rank coincident CBC candidates in Hanford and Livingston O2 data with lab-frame total masses in the range of $55-500~\msun$.
+We present the candidates' \pastrobcr, the probability that the candidate originates from a coherent gravitational-wave source.
+Additionally, for comparison, we provide the candidate's \pastro values reported by  the LIGO-Virgo-KAGRA (LVK) collaboration in \GWTC~\cite{GWTC1}, the \pycbc-team~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6, pycbc_single_det, pycbc_ogc_2}, by the Institute of Advanced study's team (\IAS)~\cite{IAS0, IAS1, IAS2}, and by \citet{bayesian_odds}.
 
-We find that (a) events reported in \GWTC, including GW170729 (likely the most massive BBH system in \GWTC) are statistically significant $\pastrobcr>0.9$; (b) three out of the eight \IAS events and candidates have $\pastrobcr>0.5$, corroborating \IAS's detection claims for GW170304, GW170727, and GW170817A; and that (c) our ranking statistic does not identify any new IMBH, but does identify an unreported marginal stellar-mass binary black hole candidate, 170222 with $\pastrobcr\sim0.5$.
+We find that (a) events reported in \GWTC, including GW170729 (likely the most massive BBH system in \GWTC) are statistically significant ${\pastrobcr>0.9}$; (b) three out of the eight \IAS events and candidates have ${\pastrobcr>0.9}$, corroborating \IAS's detection claims for GW170304, GW170727, and GW170817A; and that (c) our ranking statistic does not identify any new IMBH, but does identify an unreported marginal stellar-mass binary black hole candidate, 170222\footnote{170222 is a sub-threshold candidate detected by \pycbc (${\tc = 1171814476.97}$) with a ${\pastrobcr\sim0.6}$.
+The prefix of GW is not utilized as this is a candidate event.} with ${\pastrobcr\sim0.6}$.
 
@@
 However, instead of computing true Bayesian odds, we use the evidences as a ranking statistic.
-We form a bootstrapped distribution of the evidence for simulated foreground and background events in order to form a frequentist ranking statistic.
+We form a bootstrapped distribution of the evidence for simulated foreground and background events to form a frequentist ranking statistic.
 
@@
 \label{eq:bcr}
-\bcr = \frac{\hat{\pi}^S Z^S}{\prod\limits^D_{i=1} \ [\hat{\pi}^G Z^G_i + \hat{\pi}^N Z^N_i]}\  ,
+\bcr = \frac{\hat{\pi}^S Z^S}{\prod\limits^D_{i=1} \ [\hat{\pi}^G_i Z^G_i + \hat{\pi}^N_i Z^N_i]}\  ,
 \end{equation}
-where $\{\hat{\pi}^S, \hat{\pi}^N, \hat{\pi}^G\}$ are estimates of the astrophysical prior-odds of obtaining a signal, noise or a glitch from a stretch of data.
+where $\{\hat{\pi}^S, \hat{\pi}^N_i, \hat{\pi}^G_i\}$ are estimates of the astrophysical prior-odds that the data contain a coherent signal, incoherent noise or an incoherent glitch.
+We assume each detector has the same glitch and noise prior odds of $\{\hat{\pi}^N, \hat{\pi}^G\}$.
 In the limit where the estimated prior-odds equal the astrophysical prior-odds, the \bcr becomes the optimal Bayesian odds described by \citet{BCR2}.
@@
 Instead, we use the \bcr as a ranking statistic to obtain a frequentist significance of a candidate \bcr-value, \candbcr, measured against a background \bcr distribution, \bgrdbcr.
+
+%  $\hat{\pi}^S$ is the prior odds of detector-data containing a coherent astrophysical signal versus an incoherent instrumental-artifact (such as a glitch or noise), while $\{\hat{\pi}^N_i, \hat{\pi}^G_i\}$ are prior odds of detector-data containing a glitch or noise given an incoherent instrumental-artifact is present in the data.
 
@@
 \end{equation}
-Moreover, as we have several candidates ($N$ candidates), each with their \candbcr, we account for them by calculating a false-alarm probability with trial factors $p_N$ given by
+Moreover, as we have several candidates ($N$ candidates), each with a \candbcr, we account for them by calculating a false-alarm probability with trial factors $p_N$ given by
 \begin{equation}
@@
 
-We acquire O2 candidate signal triggers (times when the detector's data has a signal-to-noise ratio above a predetermined threshold) for \bcr analysis from \pycbc~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6}.
-Some of the triggers are associated with gravitational-wave events and candidates, while others are glitches.
-We also acquire background and simulated triggers from \pycbc to calculate \bgrdbcr and estimate values for $\{\hat{\pi}^S,\hat{\pi}^G\}$ (see Appendix~\ref{apdx:tuning-prior-odds} for details on the estimation process).
+We acquire candidate signal triggers (times when the detector's data has a signal-to-noise ratio above a predetermined threshold) for \bcr analysis from \pycbc's search in O2~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6, public_ligo_o2_triggers}.
+Some of the triggers are associated with gravitational-wave events and candidates while others are glitches.
+We also acquire background and simulated triggers from \pycbc's O2 search to calculate \bgrdbcr and estimate values for $\{\hat{\pi}^S,\hat{\pi}^G\}$ (see Appendix~\ref{apdx:tuning-prior-odds} for details on the estimation process).
 The triggers are divided into two week time-frames because the detector's sensitivity does not stay constant throughout the eight-month-long observing period~\cite{pycbc_og4}.
@@
 \begin{table}[t]
-\caption[BBH parameters correspond to duration $<454\ \text{ms}$]{\label{tab:parameters}Trigger-selection lab-frame parameter space (parameters correspond to signals with durations $<454 \ \text{ms}$ and $q\geq0.1$).}
+\caption[BBH parameters correspond to duration $\leq454\ \text{ms}$]{\label{tab:parameters}Trigger-selection lab-frame parameter space (parameters correspond to signals with durations $\leq454 \ \text{ms}$ and $q\geq0.1$).}
 \centering
@@
 For our study, we filter \pycbc triggers to include only those in the parameter ranges presented in Table~\ref{tab:parameters}.
-This region focuses our analysis on binary black hole mergers with total masses above $\gtrsim55 \msun$, corresponding to binary systems with signal durations $<454 \ \text{ms}$ and $q\geq0.1$.
+This region focuses our analysis on binary black hole mergers with lab-frame total masses above ${\gtrsim55 \msun}$, corresponding to binary systems with signal durations $<454 \ \text{ms}$ and ${q\geq0.1}$.
 The filtering process leaves us with $60,996$ background, $5,146$ simulated, and $25$ candidate signal triggers.
-We also include events and candidate events reported by \GWTC and the \IAS group in our list of candidate signal triggers.
-A plot of the component mass space constrained by our trigger filter is presented in Fig.~\ref{fig:templateBank}.
+We additionally include events and candidate events reported by \GWTC and the \IAS group in our list of candidate signal triggers.
+A plot of the lab-fame component mass space constrained by our search space is presented in Fig.~\ref{fig:templateBank}.
 
@@
 % 1178294418, May 08, 2017, 16:00 UTC
-\caption[ BCR search space.]{Component-mass boundaries for our trigger filter and parameter estimation prior.
+\caption[ BCR search space.]{Lab-frame component-mass boundaries for our search space and parameter estimation prior.
 Our search is constrained to the parameter space enclosed by the gold-colored hatches, while our prior is constrained to the slightly larger parameter space enclosed by the teal-colored hatches.
@@
 We use a likelihood that marginalizes over coalescence time, the phase at coalescence, and luminosity distance (Eq.~80 from~\citet{intro_to_gw_bayes}).
-We use identical parameter estimation priors for the glitch and signal models, reflecting our ignorance of the distribution of the population properties of signals and signal-like glitches.
+We use identical parameter estimation priors for the glitch and signal models.
+We restrict the spin priors to aligned spins to reduce the number of parameters we sample.
+We define our mass priors to be uniform in chirp mass $\mathcal{M}$ and mass ratio $q$ to avoid sampling issues that arise from sampling in thin regions of the component mass parameter space~\cite{bilby_gwtc}.
+As a post-processing step, we convert posterior samples calculated with uniform $\{\mathcal{M}, q\}$ priors to uniform component mass priors by re-sampling the posterior samples using the Jacobian given in Eq.~21 of \citet{Veitch:2015:PhRvD}.
 The complete list of the priors is in Table~\ref{tab:priors}.
@@
 
-We analyze the O2 candidates with $\totMlab > 55~\msun$ and report candidates with $\pastrobcr\geq0.3$ in Table~\ref{tab:results}.
+We analyze the O2 candidates with ${\totMlab > 55~\msun}$ and report candidates with ${\pastrobcr\geq0.2}$ in Table~\ref{tab:results}.
 The $\hat{\pi}^S$ and $\hat{\pi}^G$ values utilized for each time-frame are reported in Appendix~\ref{apdx:alphabeta}.
+By imposing a \pastrobcr threshold of 0.5, we present 13 candidate gravitational wave events.
+
+\input{Data/results_table}
 
@@
 Moreover, \pastro is not equivalent to \pastrobcr.
-However, by comparing a candidate's pipeline \pastro with its \pastrobcr, we can compare how significant each pipeline deems the candidate.
+However, by comparing candidates' various \pastro values with \pastrobcr, we can compare how significant each pipeline deems the candidate.
 For comparison, in Table~\ref{tab:results} we report \pastro values from \GWTC~\cite{GWTC1}, PyCBC OGC-2~\cite{pycbc_ogc_2}, PyCBC OGC-3~\cite{pycbc_ogc_2}, PyCBC `single-search'~\cite{pycbc_single_det}, IAS~\cite{IAS1, IAS2}, and \citet{bayesian_odds}'s analyses.
 
-\input{Data/results_table}
-
 \subsection{GWTC-1 Events}
-All the confirmed gravitational-wave events from binary black hole mergers reported in \GWTC and within our prior space (specifically GW170104, GW170608, GW170729, GW170809, and GW170814) have $\pastrobcr>0.9$, indicating a high probability of an astrophysical signal.
+All the confirmed gravitational-wave events from binary black hole mergers reported in \GWTC and within our prior space (specifically GW170104, GW170608, GW170729, GW170809, and GW170814) have ${\pastrobcr>0.9}$, indicating a high probability of an astrophysical signal.
 
 In addition to the above confirmed gravitational-wave events from \GWTC, we have also analyzed several candidate events from \GWTC, most of which have low \pastrobcr.
-For example, consider the candidate event 170412 ($\tc = 1176047817$), assigned a $\pastro$ of $0.06$ by \gstlal and has a $\pastrobcr$ of $0.01$.
-This candidate was reported to be excess power caused due to noise appearing non-stationary between 60-200 Hz~\cite{GWTC1}.
-This candidate acts as an example of how $\pastrobcr$ may be utilized to eliminate candidates originating from terrestrial noise sources.
+For example, consider the candidate event 170412 (${\tc = 1176047817}$), assigned a $\pastro$ of $0.06$ by \gstlal and has a $\pastrobcr$ of $0.01$.
+This candidate was reported to be excess power caused due to noise appearing non-stationary between ${60-200\ \text{Hz}}$~\cite{GWTC1}.
+This candidate demonstrates that $\pastrobcr$ may be utilized to eliminate candidates originating from terrestrial noise sources.
 
 \subsection{IAS Events}
-Our analysis of the IAS events and candidates with $\totMlab\gtrsim55~\msun$ in O2 has resulted in one event with disfavored $\pastrobcr<0.5$ (GW170425), and five events and two candidates with $\pastrobcr\geq0.5$ (GW170121, GW170304, 170302, GWC170402, GW170403, GW170727, GW170817A).
-From this list, four events (GW170121, GW170304, GW170727, GW170817A) have $\pastrobcr>0.8$ and $\pastro>0.9$ reported from other pipelines, making them viable gravitational-wave event candidates.
+Our analysis of the IAS events and candidates with $\totMlab\gtrsim55~\msun$ in O2 has resulted in one event with disfavored ${\pastrobcr<0.5}$ (GW170425), and five events and two candidates with $\pastrobcr\geq0.5$ (GW170121, GW170304, 170302, GWC170402, GW170403, GW170727, GW170817A).
+From this list, four events (GW170121, GW170304, GW170727, GW170817A) have ${\pastrobcr>0.8}$ and ${\pastro>0.9}$ reported from other pipelines, making them viable gravitational-wave event candidates.
 
 GWC170402, detected by \citet{IAS2}, is reported to originate from a binary with non-zero eccentricity~\cite{IAS2}.
-As we used a non-eccentric waveform during analysis, we may be under estimating this event's significance at $\pastrobcr\leq0.6$.
-Finally, GW170425 which has $\pastrobcr<0.25$ also has low \pastro reported in OGC-2 and OGC-3 \cite{pycbc_ogc_2,pycbc_ogc_3}, suggesting that GW170425 may have been false alarm.
+As we used a non-eccentric waveform during analysis, we may be under estimating this event's significance at ${\pastrobcr\leq0.6}$.
+Finally, GW170425 which has ${\pastrobcr<0.25}$ also has low \pastro reported in OGC-2 and OGC-3 \cite{pycbc_ogc_2,pycbc_ogc_3}, suggesting that GW170425 may have been false alarm.
 
 \subsection{New Candidate Events}
-Although no IMBH detections are made with the \bcr, a marginal stellar mass black hole merger candidate 170222 has been discovered with a $\pastrobcr\sim0.6$.
-This candidate has a SNR$\sim7.7$, low spin magnitudes, and source-frame component masses of $({47.16}_{-5.77}^{+8.00}, {35.50}_{-6.35}^{+5.79}) \msun$ ($90\%$ credible intervals), making it one of the heavier black-hole mergers from O2 and \GWTC.
-This candidate may be of interest as one component black hole may lie in the pair-instability mass gap ($55^{+10}_{-10}-148^{+13}_{-12}\msun$)~\cite{Woosley:2021:arXiv, Heger:2002:ApJ}.
+Although no IMBH detections are made with the \bcr, a marginal stellar mass black hole merger candidate 170222 has been discovered with a ${\pastrobcr\sim0.6}$.
+This candidate has a ${\text{SNR}\sim7.7}$, low spin magnitudes, and source-frame component masses of ${({47.16}_{-5.77}^{+8.00}, {35.50}_{-6.35}^{+5.79}) \msun}$ ($90\%$ credible intervals), making it one of the heavier black-hole mergers from O2 and \GWTC.
+This candidate may be of interest as one component black hole may lie in the pair-instability mass gap $({55^{+10}_{-10}-148^{+13}_{-12})\msun}$~\cite{Woosley:2021:arXiv, Heger:2002:ApJ}.
 More details on the candidate are presented in Appendix~\ref{apdx:170222}.
-The remaining coherent trigger candidates all have $\pastrobcr<0.5$, making them unlikely to originate from astrophysical sources.
+The remaining coherent trigger candidates all have ${\pastrobcr<0.5}$, making them unlikely to originate from astrophysical sources.
 
@@
 
-In this paper, we demonstrate that the Bayesian Coherence Odds-Ratio \bcr~\cite{BCR1} can be used as a ranking statistic to provide a measure of significance for gravitational-wave signals originating from CBCs with total masses between $55~\msun$ and $400~\msun$, a range that includes IMBHs.
-To compute the \bcr for candidates, we utilize Bayesian inference to explicitly calculate the probability of data under various hypotheses (the hypotheses that the data contains a coherent signal, just noise, or an incoherent glitch).
+In this paper, we demonstrate that the Bayesian Coherence Odds-Ratio \bcr~\cite{BCR1} can be used as a ranking statistic to provide a measure of significance for gravitational-wave signals originating from CBCs with lab-frame total masses between $55~\msun$ and $400~\msun$, a range that includes IMBHs.
+To compute the \bcr for candidates, we utilize Bayesian inference to calculate the probability of data under various hypotheses (the hypotheses that the data contains a coherent signal, just noise, or an incoherent glitch).
 This Bayesian ranking method takes a step towards building a unified Bayesian framework that provides a measure of significance for candidates and estimates their parameters, utilizing the same level of physical information incorporated during detected parameter estimation studies.
 
-In our study, we analyze O2 binary-black hole events and candidates with $\totMlab > 55~\msun$ reported by the \pycbc search~\cite{pycbc_ogc_2}, the \IAS-team~\cite{IAS1, IAS2} and those reported in \GWTC~\cite{GWTC1}.
-Using \pastrobcr, we find that the \GWTC events have high probabilities of originating from an astrophysical source.
+In our study, we analyze O2 binary-black hole events and candidates with ${\totMlab > 55~\msun}$ reported by the \pycbc search~\cite{pycbc_ogc_2}, the \IAS-team~\cite{IAS1, IAS2} and those reported in \GWTC~\cite{GWTC1}.
+Using a \pastrobcr threshold of 0.5, we find that the \GWTC events have high probabilities of originating from an astrophysical source.
 We also find that some of the \GWTC marginal triggers that have corroborated terrestrial sources (for example, candidate 170412) have low \pastrobcr, indicating this method's ability to discriminate between terrestrial artifacts and astrophysical signals.
-Our analysis of the \IAS events demonstrates that GW170121, GW170304, GW170727, and GW170817A are likely to originate from astrophysical sources ($\pastrobcr\geq0.8$), while GW170425 is not ($\pastrobcr<0.25$).
-Finally, we do not identify any new gravitational-wave events, but we find a new marginal binary-black hole merger candidate, 170222.
+Our analysis of the \IAS events demonstrates that GW170121, GW170304, GW170727, and GW170817A are likely to originate from astrophysical sources (${\pastrobcr\geq0.8}$), while GW170425 is not (${\pastrobcr<0.25}$).
+Finally, we report a new marginal binary-black hole merger candidate, 170222.
 
-Although our analysis targets triggers with $\totMlab \gtrsim 55~\msun$, this method can be extended to include the entire range of LIGO-detectable gravitational-wave sources.
-Additionally, to further improve the method's infrastructure, we can use more robust gravitational-wave templates (such as templates that incorporate higher-order modes and orbital precession) and sophisticated glitch models.
-Future analysis can also incorporate data from all available detectors in a network to increase the sensitivity of \pastrobcr.
+With the rapid rate of development in gravitational-wave Bayesian inference, we anticipate the ability to analyze longer-duration signals, utilize more advanced signal and glitch models, and incorporate data from the entire detector network.
+In a similar vein, with the accumulation of more gravitational wave events, future \bcr work may utilize astrophysically informed priors during Bayesian inference and more accurate prior odds for each detector.
 
@@
 
-All analyses (inclusive of test and failed analyses) performed for this study used $~1.3\mathrm{M}$ core-hours, amounting to a carbon footprint of $~167\ \mathrm{t}$ of CO$_2$ (using the U.S.
-average electricity source emissions of $0.429\ \text{kg/kWh}$~\cite{greenhouse} and $0.3\ \text{kWh}$ for each CPU).
+All analyses (inclusive of test and failed analyses) performed for this study used ${1.3\mathrm{M}}$ core-hours, amounting to a carbon footprint of ${\sim167\ \mathrm{t}}$ of ${\text{CO}_2}$ (using the U.S.
+average electricity source emissions of ${0.429\ \text{kg/kWh}}$~\cite{greenhouse} and ${0.3\ \text{kWh}}$ for each CPU).
 
@@
 This material is based upon work supported by NSF’s LIGO Laboratory, a major facility fully funded by the National Science Foundation.
-This research has used data, software, and web tools obtained from the Gravitational Wave Open Science Center (https://www.gw-openscience.org), a service of LIGO Laboratory, the LIGO Scientific Collaboration, and the Virgo Collaboration.
+This research has used data, software, and web tools obtained from the Gravitational Wave Open Science Center (\href{https://www.gw-openscience.org}{https://www.gw-openscience.org}), a service of LIGO Laboratory, the LIGO Scientific Collaboration, and the Virgo Collaboration.
 The U.S.
 National Science Foundation funds LIGO.
-Virgo is funded by the French Centre National de Recherche Scientifique (CNRS), the Italian Istituto Nazionale della Fisica Nucleare (INFN), and the Dutch Nikhef, with contributions by Polish and Hungarian institutes.
+Virgo is funded by the French Centre National de Recherche Scientifique (CNRS), the Italian Istituto Nazionale della Fisica Nucleare (INFN), and the Dutch Nikhef, with contributions by Polish and Hungarian institutes.\\
+
+\textit{Software:} \href{https://lscsoft.docs.ligo.org/bilby/}{\bilby} (version 1.0.0)~\cite{bilby}, \href{https://lscsoft.docs.ligo.org/bilby_pipe/master/index.html}{\bilbypipe} (version 1.0.0)~\cite{bilby_pipe}, \href{https://dynesty.readthedocs.io/}{\dynesty}~\cite{dynesty, skilling2004, skilling2006}, \href{https://gwpy.github.io/docs/stable/index.html}{\gwpy}~\cite{gwpy}, \href{https://lscsoft.docs.ligo.org/lalsuite/lalsimulation/index.html}{\code{LALSimulation}}~\cite{lalsuite}, \code{matplotlib}~\cite{matplotlib}, \code{NumPy}~\cite{NumPy}, \code{SciPy}~\cite{SciPy}, \code{pandas}~\cite{pandas}, \code{python}~\cite{pythonForScientificComputing,pythonForScientists}.
 
@@
 \subsection{Coherent Signal Model}
-We model coherent signals using a binary black hole waveform template \template, where the vector \parameters contains a point in the 12-dimensional space describing aligned-spin binary-black hole mergers.
+We model coherent signals using a binary black hole waveform template \template, where the vector \parameters contains a point in the 11-dimensional space describing aligned-spin binary-black hole mergers.
 For the signal to be coherent, \parameters must be consistent in each 4-second data segment $d_i$ for a network of $D$ detectors.

### 2021-08-04 main.tex
Pre-MNRAS conversion

@@
 \begin{abstract}
-The detection of an intermediate-mass black hole population ($10^2-10^6$~\msun) will provide clues to their formation environments (e.g., disks of active galactic nuclei, globular clusters) and illuminate a potential pathway to produce supermassive black holes.
-Ground-based gravitational-wave detectors are sensitive to a subset of such mergers and have been used to detect one $142^{+28}_{-16}~\msun$ intermediate-mass black hole formation event.
+The detection of an intermediate-mass black hole population ($10^2-10^6\ M_\odot$) will provide clues to their formation environments (e.g., disks of active galactic nuclei, globular clusters) and illuminate a potential pathway to produce supermassive black holes.
+Ground-based gravitational-wave detectors are sensitive to a subset of such mergers and have been used to detect one $142^{+28}_{-16}\ M_\odot$ intermediate-mass black hole formation event.
 However, ground-based detector data contain numerous incoherent short duration noise transients that can mimic the gravitational-wave signals from merging intermediate-mass black holes, limiting the sensitivity of searches.
 Here we search for binary black hole mergers using a Bayesian-inspired ranking statistic which measures the coherence or incoherence of triggers in multiple-detector data.
-We use this statistic to identify candidate events with lab-frame total masses $\gtrsim55$~\msun using data from LIGO's second observing run.
+We use this statistic to identify candidate events with lab-frame total masses $\gtrsim55\ M_\odot$ using data from LIGO's second observing run.
 Our analysis does not yield evidence for new intermediate-mass black holes.
@@
 Compact binary coalescences (CBCs) can provide unambiguous gravitational-wave signals for IMBH candidates e.g., the ${142^{+28}_{-16}~\msun}$ ($90\%$ credible intervals) remnant observed from the gravitational-wave event GW190521~\cite{Abbott:2020:PhRvL} and other candidates~\cite{ligo_imbh_search, ligo_imbh_o3, pycbc_imbh}.
-As a binary's total mass $M_{T}$ is associated with its gravitational-wave merger frequency, $f\sim M_{T}^{-1}$,  ground-based gravitational-wave detectors (${f\sim 10^1 - 10^3\ \text{Hz}}$) are sensitive to the last milliseconds of merging systems with ${100~\msun < \totMlab < 400~\msun}$~\cite{LIGOScientificCollaboration:2015:CQGra, Martynov:2016:PhRvD, Moore_2014, Acernese:2015:CQGra}, while space-based detectors (${f \sim 10^{-2} - 10^1\ \text{Hz}}$) can study the full signals of merging systems with ${10^4~\msun < \totMlab < 10^7~\msun}$~\cite{ Moore_2014, Lu:2019:PhRvD}.
+As a binary's total mass $M_{T}$ is associated with its gravitational-wave merger frequency, ${f\sim M_{T}^{-1}}$,  ground-based gravitational-wave detectors (${f\sim 10^1 - 10^3\ \text{Hz}}$) are sensitive to the last milliseconds of merging systems with ${100~\msun < \totMlab < 400~\msun}$~\cite{LIGOScientificCollaboration:2015:CQGra, Martynov:2016:PhRvD, Moore_2014, Acernese:2015:CQGra}, while space-based detectors (${f\sim 10^{-2}-10^1\ \text{Hz}}$) can study the full signals of merging systems with ${10^4~\msun < \totMlab < 10^7~\msun}$~\cite{ Moore_2014, Lu:2019:PhRvD}.
 Because of the short duration of IMBH gravitational-wave signals in ground-based detectors, data quality is critical for their detection.
@@
 Like signals from IMBH mergers, most glitches last for a fraction of a second, making them difficult to distinguish from astrophysical signals.
-These glitches can decrease the sensitivity of searches for binary black hole mergers with $\totMlab\gtrsim55$~\msun ~\cite{pycbc_short_duration_transients}.
+These glitches can decrease the sensitivity of searches for binary black hole mergers with ${\totMlab\gtrsim55~\msun}$ ~\cite{pycbc_short_duration_transients}.
 
@@
 incoherent glitches.
-In this paper, we use the \bcr to rank coincident CBC candidates in Hanford and Livingston O2 data with lab-frame total masses in the range of $55-500~\msun$.
+In this paper, we use the \bcr to rank O2’s coincident CBC gravitational-wave candidates with lab-frame total masses in the range of ${55-500~\msun}$.
 We present the candidates' \pastrobcr, the probability that the candidate originates from a coherent gravitational-wave source.

### 2021-08-04 main.tex
add data statement

@@
 
-%%%%%%---ACKNOWLEDGMENTS---%%%%%%%%%%%%
 \begin{acknowledgments}
@@
 This material is based upon work supported by NSF’s LIGO Laboratory, a major facility fully funded by the National Science Foundation.
-This research has used data, software, and web tools obtained from the Gravitational Wave Open Science Center (\href{https://www.gw-openscience.org}{https://www.gw-openscience.org}), a service of LIGO Laboratory, the LIGO Scientific Collaboration, and the Virgo Collaboration.
-The U.S.
-National Science Foundation funds LIGO.
-Virgo is funded by the French Centre National de Recherche Scientifique (CNRS), the Italian Istituto Nazionale della Fisica Nucleare (INFN), and the Dutch Nikhef, with contributions by Polish and Hungarian institutes.\\
+This research has used data, software, and web tools obtained from the Gravitational Wave Open Science Center (\href{https://www.gw-openscience.org}{https://www.gw-openscience.org}), a service of LIGO Laboratory, the LIGO Scientific Collaboration and the Virgo Collaboration.
+LIGO Laboratory and Advanced LIGO are funded by the United States National Science Foundation (NSF) as well as the Science and Technology Facilities Council (STFC) of the United Kingdom, the Max-Planck-Society (MPS), and the State of Niedersachsen/Germany for support of the construction of Advanced LIGO and construction and operation of the GEO600 detector.
+Additional support for Advanced LIGO was provided by the Australian Research Council.
+Virgo is funded, through the European Gravitational Observatory (EGO), by the French Centre National de Recherche Scientifique (CNRS), the Italian Istituto Nazionale di Fisica Nucleare (INFN) and the Dutch Nikhef, with contributions by institutions from Belgium, Germany, Greece, Hungary, Ireland, Japan, Monaco, Poland, Portugal, Spain.\\
+
+\end{acknowledgments}
+
+\section*{Data Availability Statement}
+{
+We analyze publicly-available gravitational wave strain data from the LIGO-Virgo-KAGRA collaboration~\cite{O2data}.
+The trigger times for analysis were provided by the \pycbc team.
+The derived data generated in this research will be shared on reasonable request to the corresponding author.
 
 \textit{Software:} \href{https://lscsoft.docs.ligo.org/bilby/}{\bilby} (version 1.0.0)~\cite{bilby}, \href{https://lscsoft.docs.ligo.org/bilby_pipe/master/index.html}{\bilbypipe} (version 1.0.0)~\cite{bilby_pipe}, \href{https://dynesty.readthedocs.io/}{\dynesty}~\cite{dynesty, skilling2004, skilling2006}, \href{https://gwpy.github.io/docs/stable/index.html}{\gwpy}~\cite{gwpy}, \href{https://lscsoft.docs.ligo.org/lalsuite/lalsimulation/index.html}{\code{LALSimulation}}~\cite{lalsuite}, \code{matplotlib}~\cite{matplotlib}, \code{NumPy}~\cite{NumPy}, \code{SciPy}~\cite{SciPy}, \code{pandas}~\cite{pandas}, \code{python}~\cite{pythonForScientificComputing,pythonForScientists}.
+}
 
-\end{acknowledgments}
 %%%%%%%%%%%%%%%%%%%%%%%%

### 2022-01-21 referee_response/review_response.tex
Added ref review

% ADAPTED FROM https://github.com/hollina/template-referee-response

\documentclass[11pt,leqno]{article}

%------------------------------------------%
%                Packages
%------------------------------------------%

\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage{microtype,xparse,tcolorbox}
\usepackage{graphicx}
\usepackage{natbib}	%Bibliography package. It handles citations and can easily change formats. This is done at the end of the document
\usepackage[utf8]{inputenx}% For proper input encoding
\usepackage{adjustbox} %Handles resizing of tables, figures, etc. Based off of page and/or line width/height 
% Packages for tables
\usepackage{booktabs}% For Pretty tables
\usepackage{threeparttable}% For Notes below table
\usepackage{rotating}% To Rotate Table
\usepackage{amsmath, amssymb,mathrsfs} %For using math
\usepackage{bm}
\usepackage{caption} 
\usepackage[list=true]{subcaption} %For having multiple figures within the same one. Figure 1, with part (a) and (b)
%\setcounter{lofdepth}{2}
\usepackage{setspace} %Single, Double Space, etc 
\usepackage[paperwidth=8.5in, paperheight=11in,margin=1in]{geometry} %For controlling the dimensions. Very useful for Posters, etc 
\usepackage{chngpage} 
\usepackage{everypage}%For page numbers on rotated pages
\usepackage[capposition=top]{floatrow}
\usepackage{accents}
\usepackage{float}
\usepackage{comment}
\usepackage{morefloats}
\usepackage{placeins}% To Create Float Barriers so the tables will stay in their sections
\usepackage{pdflscape}

\usepackage{siunitx} %This aligns tables by their decimal and handles processing of the numbers within the tables
  \sisetup{
    detect-mode,
    group-digits      = false,
    input-symbols     = {( ) [ ] - +},
    table-align-text-post = false,
    input-signs             = ,
    %parse-numbers=false,
    %scientific-notation = true,
        %round-mode              = places,
        %round-precision         = 2,
        %input-ignore={,},
    %input-decimal-markers={.},
    %group-separator={,},
        } 
\usepackage{grffile}
\usepackage{soul}
\usepackage{color}
\usepackage{caption}
%\captionsetup[figure]{justification=raggedright,singlelinecheck=off}
\sisetup{separate-uncertainty=true}
\usepackage{mathptmx}
\DeclareCaptionLabelFormat{blank}{}

%------------------------------------------%
%              Custom Commands
%------------------------------------------%
\newcommand\iid{i.i.d.} %Makes iid a command
\newcommand\pN{\mathcal{N}} %Makes the natural numbers a command

\setcounter{MaxMatrixCols}{20}

\newtheorem{theorem}{Theorem}%[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{assumption}[theorem]{Assumption}
\newenvironment{proof}{\paragraph{Proof:}}{\hfill$\square$ \\} %This fixes the problem with dynamic tables for some reason

%For Page Numbers while rotated
\newlength{\hfoot}
\newlength{\vfoot}
\AddEverypageHook{\ifdim\textwidth=\linewidth\relax
\else\setlength{\hfoot}{-\topmargin}%
\addtolength{\hfoot}{-\headheight}%
\addtolength{\hfoot}{-\headsep}%
\addtolength{\hfoot}{-.5\linewidth}%
\ifodd\value{page}\setlength{\vfoot}{\oddsidemargin}%
\else\setlength{\vfoot}{\evensidemargin}\fi%
\addtolength{\vfoot}{\textheight}%
\addtolength{\vfoot}{\footskip}%
\raisebox{\hfoot}[0pt][0pt]{\rlap{\hspace{\vfoot}\rotatebox[origin=cB]{90}{\thepage}}}\fi}
%http://tex.stackexchange.com/questions/209685/landscape-mode-and-page-numbering

%------------------------------------------%
%      Title Page Info
%------------------------------------------%
\title{Replies for MN-21-1316:\\
 ``A search for intermediate mass black holes mergers in the second LIGO-Virgo observing run with the Bayes Coherence Ratio
''}
\author{AUTHOR}
\date{\today}
\AtBeginDocument{\maketitle\thispagestyle{empty}\noindent}

\begin{document}

\onehalfspacing

\section*{Response to the referee}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Thank you for your helpful comments and guidance. We describe how we have addressed all of your concerns below. \\
\\
Your comments are below,  \fcolorbox{black}{black!10}{{\ttfamily boxed in with a gray background and different font}}. Our responses are in plain text. Any included text from the new manuscript is \fbox{boxed in with a white background and the} \\
\fbox{same font as this text} with the page number noted at the top of the quoted text. 
Any added comments or other differences from the quoted manuscript text and the text appearing in this report {\color{red} {\ttfamily[appears in brackets with a different font and a red color]}}. \\
\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Referee: Comment 1} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{tcolorbox}[left = 1em, top = 1ex, bottom = 1ex, colupper=black, colback=black!10, adjusted title = Referee: Comment 1]
    \setlength\parindent{2em}
	\noindent
	\ttfamily

	Title: black holes mergers -> black hole mergers
\end{tcolorbox}

We have adjusted the title.

\end{document}

### 2022-01-21 main.tex
Added ref review

@@
-\documentclass[
-% preprint,
-%preprintnumbers,
- nofootinbib,
- amsmath,amssymb,
- aps,
- twocolumn,
- superscriptaddress
-]{revtex4-2}
+% \documentclass[
+% % preprint,
+% %preprintnumbers,
+%  nofootinbib,
+%  amsmath,amssymb,
+%  aps,
+%  twocolumn,
+%  superscriptaddress
+% ]{revtex4-2}
+
+\documentclass[useAMS,fleqn, usenatbib, final]{mnras}
 
@@
 \usepackage{subfigure}
-\usepackage[T1]{fontenc}
-% \usepackage[breaklinks]{hyperref}
 \usepackage{xspace} 
@@
 \usepackage[bottom]{footmisc}
-\usepackage[colorlinks,urlcolor=NavyBlue,citecolor=NavyBlue,linkcolor=NavyBlue]{hyperref}
+% \usepackage[colorlinks,urlcolor=NavyBlue,citecolor=NavyBlue,linkcolor=NavyBlue]{hyperref}
+\usepackage{hyperref}
+\usepackage{color,units}
+\usepackage{aas_macros}
+\usepackage[T1]{fontenc}
+\usepackage{ae,aecompl}
+\usepackage{newtxtext,newtxmath}
 
@@
 \usepackage{colortbl}
-
 \usepackage{nicematrix}
@@
 \graphicspath{{images/}} %Setting the graphicspath
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%%
 
@@
 \newcommand{\mbta}{{\sc MBTAOnline}\xspace}
-
-% \newcommand{\pycbc}{{\sc \href{https://pycbc.org/}{{PyCBC}}}\xspace}
-% \newcommand{\GWTC}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2019PhRvX...9c1040A/abstract}{{GWTC-1}}}\xspace}
-% \newcommand{\OGC}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2020ApJ...891..123N/abstract}{{2-OGC}}}\xspace}
-% \newcommand{\IAS}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2020PhRvD.101h3030V/abstract}{{IAS}}}\xspace}
-
 \newcommand{\pycbc}{{\sc {{PyCBC}}}\xspace}
@@
 \newcommand{\fap}{\mathcmd{p_N}}
-\newcommand{\totMlab}{\mathcmd{M_T^{\rm{lab}}}}
+\newcommand{\totMlab}{\mathcmd{M}}
 \newcommand{\pastro}{\fancytext{p_\text{astro}}}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\input{titlepage_mnras}
+
+% Don't change these lines
 \begin{document}
-
-\title{A search for intermediate-mass black holes mergers in the \\second LIGO--Virgo observing run with the Bayes Coherence Ratio}
-
-\input{authors}
-
-\date{\today}
+\label{firstpage}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}}
+\maketitle
 
@@
 
-\maketitle
+% Pick six from http://astrothesaurus.org/concept-select/
+\begin{keywords}
+gravitational waves -- transients: black hole mergers -- stars: black holes -- methods: statistical -- methods: data analysis  
+\end{keywords}
 
@@
 \section{Introduction}
+\label{sec:intro}
 
-A variety of techniques have been employed to search for ${10^{4} - 10^{6}~\msun}$ intermediate-mass black hole (IMBH) candidates including reverberation mapping~\cite{Peterson:2014:SSRv}, direct kinematic measurements~\cite{Schodel:2002:Natur, Kiziltan:2017:Natur}, applying macroscopic galaxy to black hole mass scaling relations ($M_{BH}$-$\sigma$ and $M_{BH}$-L relations)~\cite{Graham:2013:ApJ, Wevers:2017:MNRAS}, studying  X-ray luminosity and spectra~\cite{Greene:2004:ApJ, Lin:2020:ApJL}, gravitational lensing of gamma-ray burst light curves~\cite{paynter_evidence_2021}, and others~\cite{Greene:2020:ARA&A, Koliopanos:2017:mbhe, Mezcua:2017:IJMPD}).
-However, because IMBH have smaller gravitational spheres of influence than those of supermassive black holes, it is much more challenging to observe them with these observational techniques~\cite{Mezcua:2017:IJMPD}.
-Additionally, the numerous IMBH candidates discovered using these techniques are ambiguous as other sources can describe observations from the candidates (e.g., light sources orbiting clusters of stellar-mass black holes~\cite{Ridolfi:2016:MNRAS, Freire:2017:MNRAS}, anisotropic emission from neutron stars~\cite{Israel:2017:MNRAS, RodriguezCastillo:2020:ApJ}).
+A variety of techniques have been employed to search for ${10^{4} - 10^{6}~\msun}$ intermediate-mass black hole (IMBH) candidates including reverberation mapping~\citep{Peterson:2014:SSRv}, direct kinematic measurements~\citep{Schodel:2002:Natur, Kiziltan:2017:Natur}, applying macroscopic galaxy to black hole mass scaling relations, $M_{BH}$-$\sigma$ and $M_{BH}$-L relations~\citep{Graham:2013:ApJ, Wevers:2017:MNRAS}, studying  X-ray luminosity and spectra~\citep{Greene:2004:ApJ, Lin:2020:ApJL}, gravitational lensing of gamma-ray burst light curves~\citep{paynter_evidence_2021}, and others~\citep[see][]{Greene:2020:ARA&A, Koliopanos:2017:mbhe, Mezcua:2017:IJMPD}.
+However, because IMBH have smaller gravitational spheres of influence than those of supermassive black holes, it is much more challenging to observe them with these observational techniques~\citep{Mezcua:2017:IJMPD}.
+Additionally, the numerous IMBH candidates discovered using these techniques are ambiguous as other sources can describe observations from the candidates (e.g., light sources orbiting clusters of stellar-mass black holes~\citealt{Ridolfi:2016:MNRAS, Freire:2017:MNRAS},  anisotropic emission from neutron stars~\citealt{Israel:2017:MNRAS, RodriguezCastillo:2020:ApJ}).
 
-Stellar mass (${M_\text{BH} < 10^{2}~\msun}$) and supermassive black holes (${M_\text{BH} > 10^{6}~\msun}$) have been observed and well studied since the 1970s~\cite{Webster:1972:Natur, Balick:1974:ApJ, Ghez:1998:ApJ, Genzel:2010:RvMP, Abbott:2019:PhRvX, EventHorizonTelescopeCollaboration:2019:ApJL, Abbott:2020:arXiv}.
+Stellar mass (${M_\text{BH} < 10^{2}~\msun}$) and supermassive black holes (${M_\text{BH} > 10^{6}~\msun}$) have been observed and well studied since the 1970s~\citep{Webster:1972:Natur, Balick:1974:ApJ, Ghez:1998:ApJ, Genzel:2010:RvMP, Abbott:2019:PhRvX, EventHorizonTelescopeCollaboration:2019:ApJL, Abbott:2020:arXiv}.
 However, there is a deficiency of observational evidence for black holes in the intermediate-mass range ${10^{2} - 10^{6}~\msun}$.
 The discovery of an IMBH population will bridge this observational gap, probe IMBH formation environments (e.g.
-accretion disks of active galactic nuclei~\cite{Tagawa:2021:ApJ, Li:2021:arXiv, Samsing:2020:arXiv, Tagawa:2020:ApJ, Ishibashi:2020:A&A, Grobner:2020:A&A, Yang:2019:PhRvL, McKernan:2019:ApJL, Yang:2019:ApJ, McKernan:2018:ApJ, Bellovary:2016:ApJL, McKernan:2014:MNRAS, McKernan:2012:MNRAS}, the centers of dense stellar clusters~\cite{Banerjee:2021:MNRASa, Zevin:2021:ApJ,Mapelli:2021:arXiv,Weatherford:2021:ApJL, Bouffanais:2021:arXiv, Ballone:2021:MNRAS, Kumamoto:2021:arXiv, Banerjee:2021:MNRASb, Martinez:2020:ApJ, Romero-Shaw:2020:ApJL, Anagnostou:2020:PASA}, Population-III stars~\cite{Toubiana:2021:PhRvL, Farrell:2021:MNRAS, Safarzadeh:2020:ApJL, Liu:2020:MNRAS, Inayoshi:2017:MNRAS}), and illuminate our understanding of supermassive black hole formation~\cite{Askar:2021:MNRAS, ArcaSedda:2019:arXiv, Amaro-Seoane:2007:CQGra, Gurkan:2006:ApJL}.
+accretion disks of active galactic nuclei~\citealt{Tagawa:2021:ApJ, Li:2021:arXiv, Samsing:2020:arXiv, Tagawa:2020:ApJ, Ishibashi:2020:A&A, Grobner:2020:A&A, Yang:2019:PhRvL, McKernan:2019:ApJL, Yang:2019:ApJ, McKernan:2018:ApJ, Bellovary:2016:ApJL, McKernan:2014:MNRAS, McKernan:2012:MNRAS}, the centers of dense stellar clusters~\citealt{Banerjee:2021:MNRASa, Zevin:2021:ApJ,Mapelli:2021:arXiv,Weatherford:2021:ApJL, Bouffanais:2021:arXiv, Ballone:2021:MNRAS, Kumamoto:2021:arXiv, Banerjee:2021:MNRASb, Martinez:2020:ApJ, Romero-Shaw:2020:ApJL, Anagnostou:2020:PASA}, Population-III stars~\citealt{Toubiana:2021:PhRvL, Farrell:2021:MNRAS, Safarzadeh:2020:ApJL, Liu:2020:MNRAS, Inayoshi:2017:MNRAS}), and illuminate our understanding of supermassive black hole formation~\citep{Askar:2021:MNRAS, ArcaSedda:2019:arXiv, Amaro-Seoane:2007:CQGra, Gurkan:2006:ApJL}.
 
-Compact binary coalescences (CBCs) can provide unambiguous gravitational-wave signals for IMBH candidates e.g., the ${142^{+28}_{-16}~\msun}$ ($90\%$ credible intervals) remnant observed from the gravitational-wave event GW190521~\cite{Abbott:2020:PhRvL} and other candidates~\cite{ligo_imbh_search, ligo_imbh_o3, pycbc_imbh}.
-As a binary's total mass $M_{T}$ is associated with its gravitational-wave merger frequency, ${f\sim M_{T}^{-1}}$,  ground-based gravitational-wave detectors (${f\sim 10^1 - 10^3\ \text{Hz}}$) are sensitive to the last milliseconds of merging systems with ${100~\msun < \totMlab < 400~\msun}$~\cite{LIGOScientificCollaboration:2015:CQGra, Martynov:2016:PhRvD, Moore_2014, Acernese:2015:CQGra}, while space-based detectors (${f\sim 10^{-2}-10^1\ \text{Hz}}$) can study the full signals of merging systems with ${10^4~\msun < \totMlab < 10^7~\msun}$~\cite{ Moore_2014, Lu:2019:PhRvD}.
+Compact binary coalescences (CBCs) can provide unambiguous gravitational-wave signals for IMBH candidates e.g., the ${142^{+28}_{-16}~\msun}$ ($90\%$ credible intervals) remnant observed from the gravitational-wave event GW190521~\citep{Abbott:2020:PhRvL} and other candidates~\citep{ligo_imbh_search, ligo_imbh_o3, pycbc_imbh}.
+As a binary's lab-frame total mass $M$ is associated with its gravitational-wave merger frequency, ${f\sim M^{-1}}$,  ground-based gravitational-wave detectors (${f\sim 10^1 - 10^3\ \text{Hz}}$) are sensitive to the last milliseconds of merging systems with ${100~\msun < \totMlab < 400~\msun}$~\citep{LIGOScientificCollaboration:2015:CQGra, Martynov:2016:PhRvD, Moore_2014, Acernese:2015:CQGra}, while space-based detectors (${f\sim 10^{-2}-10^1\ \text{Hz}}$) can study the full signals of merging systems with ${10^4~\msun < \totMlab < 10^7~\msun}$~\citep{ Moore_2014, Lu:2019:PhRvD}.
 Because of the short duration of IMBH gravitational-wave signals in ground-based detectors, data quality is critical for their detection.
-Gravitational-wave data is characterized by numerous non-stationary terrestrial artifacts called \textit{glitches}~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
+Gravitational-wave data is characterized by numerous non-stationary terrestrial artifacts called \textit{glitches}~\citep{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
 Like signals from IMBH mergers, most glitches last for a fraction of a second, making them difficult to distinguish from astrophysical signals.
-These glitches can decrease the sensitivity of searches for binary black hole mergers with ${\totMlab\gtrsim55~\msun}$ ~\cite{pycbc_short_duration_transients}.
+These glitches can decrease the sensitivity of searches for binary black hole mergers with ${\totMlab\gtrsim55~\msun}$ ~\citep{pycbc_short_duration_transients}.
 
-Although a significant fraction of the glitches can be identified by testing them for coherence amongst two or more detectors and performing matched-filtering, these methods are insufficient to identify all glitches~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
-One method to discriminate more glitches while searching for CBCs is the Bayesian odds~\cite{bci, kanner2016leveraging, BCR1, BCR2, bcr_gw151216, bayesian_odds}.
-The Bayesian Coherence Ratio \bcr~\cite{BCR1,BCR2} is a Bayesian odds comparing the probability that the data contains coherent signals vs.
+Although a significant fraction of the glitches can be identified by testing them for coherence amongst two or more detectors and performing matched-filtering, these methods are insufficient to identify all glitches~\citep{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}.
+One method to discriminate more glitches while searching for CBCs is the Bayesian odds~\citep{bci, kanner2016leveraging, BCR1, BCR2, bcr_gw151216, bayesian_odds}.
+The Bayesian Coherence Ratio \bcr~\citep{BCR1,BCR2} is a Bayesian odds comparing the probability that the data contains coherent signals vs.
 incoherent glitches.
@@
 We present the candidates' \pastrobcr, the probability that the candidate originates from a coherent gravitational-wave source.
-Additionally, for comparison, we provide the candidate's \pastro values reported by the LIGO-Virgo-KAGRA (LVK) collaboration in \GWTC~\cite{GWTC1}, the \pycbc-team~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6, pycbc_single_det, pycbc_ogc_2}, by the Institute of Advanced study's team (\IAS)~\cite{IAS0, IAS1, IAS2}, and by \citet{bayesian_odds}.
+Additionally, for comparison, we provide the candidate's \pastro values reported by the LIGO-Virgo-KAGRA (LVK) collaboration in \GWTC~\citep{GWTC1}, the \pycbc-team~\citep{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6, pycbc_single_det, pycbc_ogc_2}, by the Institute of Advanced study's team (\IAS)~\citep{IAS0, IAS1, IAS2}, and by \citet{bayesian_odds}.
 
@@
 
-\section{Method\label{sec:method}}
+\section{Method}
+\label{sec:method}
 \subsection{A Bayesian Ranking Statistic}
-The standard framework to identify CBC gravitational-wave signals in data is to quantify the significance of candidates with null-hypothesis significance testing~\cite{GWTC1, GWTC2}.
+The standard framework to identify CBC gravitational-wave signals in data is to quantify the significance of candidates with null-hypothesis significance testing~\citep{GWTC1, GWTC2}.
 In this framework, the candidates' ranking statistic is compared against a background distribution.
-The independent matched-filter searches, e.g., \pycbc~\cite{pycbc_og4}, \spiir~\cite{spiir} and \gstlal~\cite{sachdev2019gstlal}, and Coherent WaveBurst~\cite{cwb} used by LVK to search for signals in gravitational-wave data all use ranking statistics in such a manner~\cite{GWTC1}.
+The independent matched-filter searches, e.g., \pycbc~\citep{pycbc_og4}, \spiir~\citep{spiir} and \gstlal~\citep{sachdev2019gstlal}, and Coherent WaveBurst~\citep{cwb} used by LVK to search for signals in gravitational-wave data all use ranking statistics in such a manner~\citep{GWTC1}.
 Both \pycbc and \gstlal's ranking statistic incorporate information about the relative likelihood that the data contains a coherent signal versus noise.
-In contrast, \cwb's ranking statistic uses the information of coherent energy present in the network of detectors~\cite{GWTC1}.
+In contrast, \cwb's ranking statistic uses the information of coherent energy present in the network of detectors~\citep{GWTC1}.
 
-Bayesian inference offers an alternative means to rank the significance of candidate events by computing the odds that the data contain a transient gravitational-wave signal versus instrumental glitches~\cite{BCR1}.
-This method relies on accurate models for the signal and glitch morphologies~\cite{BCR1}.
-In principle, Bayesian odds is the optimal method for hypothesis testing~\cite{BCR2}.
+Bayesian inference offers an alternative means to rank the significance of candidate events by computing the odds that the data contain a transient gravitational-wave signal versus instrumental glitches~\citep{BCR1}.
+This method relies on accurate models for the signal and glitch morphologies~\citep{BCR1}.
+In principle, Bayesian odds is the optimal method for hypothesis testing~\citep{BCR2}.
 Much of its power comes from the Bayesian evidence, the likelihood of the data given a hypothesis.
@@
 However, as the astrophysical prior-odds are unknown, it is invalid to use the \bcr as an odds-ratio to discriminate signals from glitches.
-Instead, we use the \bcr as a ranking statistic to obtain a frequentist significance of a candidate \bcr-value, \candbcr, measured against a background \bcr distribution, \bgrdbcr.
+Instead, we use the \bcr as a ranking statistic to obtain a frequentist significance of a candidate \bcr-value, $\candbcr$, measured against a background \bcr distribution, $\bgrdbcr$.
 
@@
 
-Since it is impossible to shield ground-based gravitational-wave detectors from gravitational-wave signals, the LVK empirically estimates the background by repeatedly time-shifting strain data by amounts larger than the light-travel time between the two LIGO detectors~\cite{GWTC1}.
-We use time-shifted data to generate \bgrdbcr.
+Since it is impossible to shield ground-based gravitational-wave detectors from gravitational-wave signals, the LVK empirically estimates the background by repeatedly time-shifting strain data by amounts larger than the light-travel time between the two LIGO detectors~\citep{GWTC1}.
+We use time-shifted data to generate $\bgrdbcr$.
 Following this, each candidate's single-event false alarm probability $p_1$ of being miss-classified as a glitch is given by
@@
 
-\section{Analysis}\label{sec:Analysis}
+\section{Analysis}
+\label{sec:Analysis}
 
-We acquire candidate signal triggers (times when the detector's data has a signal-to-noise ratio above a predetermined threshold) for \bcr analysis from \pycbc's search in O2~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6, public_ligo_o2_triggers}.
+We acquire candidate signal triggers (times when the detector's data has a signal-to-noise ratio above a predetermined threshold) for \bcr analysis from \pycbc's search in O2~\citep{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6, public_ligo_o2_triggers}.
 Some of the triggers are associated with gravitational-wave events and candidates while others are glitches.
-We also acquire background and simulated triggers from \pycbc's O2 search to calculate \bgrdbcr and estimate values for $\{\hat{\pi}^S,\hat{\pi}^G\}$ (see Appendix~\ref{apdx:tuning-prior-odds} for details on the estimation process).
-The triggers are divided into two week time-frames because the detector's sensitivity does not stay constant throughout the eight-month-long observing period~\cite{pycbc_og4}.
+We also acquire background and simulated triggers from \pycbc's O2 search to calculate $\bgrdbcr$ and estimate values for $\{\hat{\pi}^S,\hat{\pi}^G\}$ (see Appendix~\ref{apdx:tuning-prior-odds} for details on the estimation process).
+The triggers are divided into two week time-frames because the detector's sensitivity does not stay constant throughout the eight-month-long observing period~\citep{pycbc_og4}.
 
-\begin{table}[t]
+\begin{table}
 \caption[BBH parameters correspond to duration $\leq454\ \text{ms}$]{\label{tab:parameters}Trigger-selection lab-frame parameter space (parameters correspond to signals with durations $\leq454 \ \text{ms}$ and $q\geq0.1$).}
@@
 \midrule
-Component Mass 1 [\msun] & 31.54 & 491.68\\
-Component Mass 2 [\msun] & 1.32 & 121.01\\
-Total Mass [\msun] & 56.93 & 496.72\\
-Chirp Mass [\msun] & 8.00 & 174.56\\
-Mass Ratio & 0.1 & 0.98\\
+Component Mass 1, $m_1$ [\msun] & 31.54 & 491.68\\
+Component Mass 2, $m_2$ [\msun] & 1.32 & 121.01\\
+Total Mass, $M$ [\msun] & 56.93 & 496.72\\
+Chirp Mass, $\mathcal{M}$ [\msun] & 8.00 & 174.56\\
+Mass Ratio, $q$ & 0.1 & 0.98\\
 \end{tabular}
@@
 
-\begin{figure*}[!ht]
+\begin{figure*}
 {\centering \includegraphics[width=0.75\linewidth]{images/template_bank.png}
@@
 % 1178294418, May 08, 2017, 16:00 UTC
-\caption[ BCR search space.]{Lab-frame component-mass boundaries for our search space and parameter estimation prior.
+\caption[ BCR search space.]{Lab-frame black hole component-mass boundaries for our search space and parameter estimation prior.
 Our search is constrained to the parameter space enclosed by the gold-colored hatches, while our prior is constrained to the slightly larger parameter space enclosed by the teal-colored hatches.
@@
 
-To evaluate $\{Z^S, Z^G_i, Z^N_i\}$ and calculate the \bcr Eq.~\ref{eq:bcr} for triggers, we carry out Bayesian inference with \bilby~\cite{bilby, bilby_pipe}, employing \dynesty~\cite{dynesty} as our nested sampler.
-Nested sampling, an algorithm introduced by~\citet{skilling2004, skilling2006}, provides an estimate of the Bayesian evidence and is often utilized for parameter estimation within the LIGO collaboration~\cite{bilby, bilby_paper, pbilby_paper}.
+To evaluate $\{Z^S, Z^G_i, Z^N_i\}$ and calculate the \bcr (Eq.~\ref{eq:bcr}) for triggers, we carry out Bayesian inference with \bilby~\citep{bilby, bilby_pipe}, employing \dynesty~\citep{dynesty} as our nested sampler.
+Nested sampling, an algorithm introduced by~\citet{skilling2004, skilling2006}, provides an estimate of the Bayesian evidence and is often utilized for parameter estimation within the LIGO collaboration~\citep{bilby, bilby_paper, pbilby_paper}.
 
-We use a likelihood that marginalizes over coalescence time, the phase at coalescence, and luminosity distance (Eq.~80 from~\citet{intro_to_gw_bayes}).
+We use a likelihood that marginalizes over coalescence time, the phase at coalescence, and luminosity distance~\citep[see][Eq.~80]{intro_to_gw_bayes}.
 We use identical parameter estimation priors for the glitch and signal models.
 We restrict the spin priors to aligned spins to reduce the number of parameters we sample.
-We define our mass priors to be uniform in chirp mass $\mathcal{M}$ and mass ratio $q$ to avoid sampling issues that arise from sampling in thin regions of the component mass parameter space~\cite{bilby_gwtc}.
-As a post-processing step, we convert posterior samples calculated with uniform $\{\mathcal{M}, q\}$ priors to uniform component mass priors by re-sampling the posterior samples using the Jacobian given in Eq.~21 of \citet{Veitch:2015:PhRvD}.
+We define our mass priors to be uniform in chirp mass $\mathcal{M}$ and mass ratio $q$ to avoid sampling issues that arise from sampling in thin regions of the component mass parameter space~\citep{bilby_gwtc}.
+As a post-processing step, we convert posterior samples calculated with uniform $\{\mathcal{M}, q\}$ priors to uniform component mass priors by re-sampling the posterior samples using the Jacobian given in~\citet[Eq.~21]{Veitch:2015:PhRvD}.
 The complete list of the priors is in Table~\ref{tab:priors}.
@@
     Prior settings for the lab-frame parameters used during our parameter estimation.
-The definitions of the parameters are documented in \citet{bilby_gwtc}~Table~E1.
+The definitions of the parameters are documented in \citet[Table~E1]{bilby_gwtc}.
 The trigger time $t_c$ is obtained from the data products of \pycbc's O2 search.
@@
     \hline
-          $\mathcal{M}/\msun$           & Uniform & 7--180  \\
+          $\mathcal{M}\ [\msun]$           & Uniform & 7--180  \\
           $q$                           & Uniform & 0.1--1  \\
-          $M/\msun$                     & Constraint & 50--500  \\
-          $d_\mathrm{L}/\mathrm{Mpc}$   & Comoving & 100--5000  \\
+          $M\ [\msun]$                     & Constraint & 50--500  \\
+          $d_\mathrm{L}\ [\mathrm{Mpc}]$   & Comoving & 100--5000  \\
           $\chi_1$, $\chi_2$            & Uniform & -1--1  \\
@@
           dec                           & Cosine & 0--$2\pi$  \\
-          $t_c/\mathrm{s}$              & Uniform & $t_c\pm0.1$  \\
+          $t_c\ [\mathrm{s}]$              & Uniform & $t_c\pm0.1$  \\
     \hline
@@
 The waveform template we utilize is \imrphenomp, a phenomenological waveform template constructed in the frequency domain that models the in-spiral, merger, and ring-down (IMR) of a compact binary coalescence~\citep{khan2016frequency}.
-Although there exist gravitational-wave templates such as \imrxhm~\cite{imrphenompxhm}, \nrsur~\cite{nrsur7dq4} and \seob~\cite{seobnrv4phm} which incorporate more physics, such as information on higher-order modes, we use \imrphenomp as it is computationally inexpensive compared to others.
+Although there exist gravitational-wave templates such as \imrxhm~\citep{imrphenompxhm}, \nrsur~\citep{nrsur7dq4} and \seob~\citep{seobnrv4phm} which incorporate more physics, such as information on higher-order modes, we use \imrphenomp as it is computationally inexpensive compared to others.
 
@@
 A Tukey window with a 0.2-second roll-off is applied to each data segment to suppress spectral leakage.
-After this, we fast-Fourier transform and median-average the segments to create a PSD~\cite{ligo_psd}.
-Like other PSD estimation methods, this method adds statistical uncertainties to the PSD~\cite{psd_student_t, chatziioannou2019noise, Biscoveanu:2020:PhRvD}.
+After this, we fast-Fourier transform and median-average the segments to create a PSD~\citep{ligo_psd}.
+Like other PSD estimation methods, this method adds statistical uncertainties to the PSD~\citep{psd_student_t, chatziioannou2019noise, Biscoveanu:2020:PhRvD}.
 To marginalize over the statistical uncertainty, we use the median-likelihood presented by~\citet{psd_student_t} as a post-processing step.
@@
 The data we use are the publicly accessible O2 strain data from the Hanford and Livingston detectors, recorded while the detectors are in ``Science Mode''.
-We obtain the data from the gravitational-wave Open Science Center~\cite{GWOSC} using \gwpy~\cite{gwpy}.
+We obtain the data from the gravitational-wave Open Science Center~\citep{GWOSC} using \gwpy~\citep{gwpy}.
 
-Finally, with the \candbcr and \bgrdbcr for each time-frame of triggers, we calculate the candidate signal's \pastrobcr.
+Finally, with the $\candbcr$ and $\bgrdbcr$ for each time-frame of triggers, we calculate the candidate signal's \pastrobcr.
 
-\section{\label{sec:Results}Results}
+\section{Results}
+\label{sec:Results}
 
@@
 
-Various search pipeline \pastro are not mathematically equivalent~\cite{Galaudage:2020:PhRvD}.
+Various search pipeline \pastro are not mathematically equivalent~\citep{Galaudage:2020:PhRvD}.
 Moreover, \pastro is not equivalent to \pastrobcr.
 However, by comparing candidates' various \pastro values with \pastrobcr, we can compare how significant each pipeline deems the candidate.
-For comparison, in Table~\ref{tab:results} we report \pastro values from \GWTC~\cite{GWTC1}, PyCBC OGC-2~\cite{pycbc_ogc_2}, PyCBC OGC-3~\cite{pycbc_ogc_2}, PyCBC `single-search'~\cite{pycbc_single_det}, IAS~\cite{IAS1, IAS2}, and \citet{bayesian_odds}'s analyses.
+For comparison, in Table~\ref{tab:results} we report \pastro values from \GWTC~\citep{GWTC1}, PyCBC OGC-2~\citep{pycbc_ogc_2}, PyCBC OGC-3~\citep{pycbc_ogc_2}, PyCBC `single-search'~\citep{pycbc_single_det}, IAS~\citep{IAS1, IAS2}, and \citet{bayesian_odds}'s analyses.
 
@@
 For example, consider the candidate event 170412 (${\tc = 1176047817}$), assigned a $\pastro$ of $0.06$ by \gstlal and has a $\pastrobcr$ of $0.01$.
-This candidate was reported to be excess power caused due to noise appearing non-stationary between ${60-200\ \text{Hz}}$~\cite{GWTC1}.
+This candidate was reported to be excess power caused due to noise appearing non-stationary between ${60-200\ \text{Hz}}$~\citep{GWTC1}.
 This candidate demonstrates that $\pastrobcr$ may be utilized to eliminate candidates originating from terrestrial noise sources.
@@
 
-GWC170402, detected by \citet{IAS2}, is reported to originate from a binary with non-zero eccentricity~\cite{IAS2}.
+GWC170402, detected by \citet{IAS2}, is reported to originate from a binary with non-zero eccentricity~\citep{IAS2}.
 As we used a non-eccentric waveform during analysis, we may be under estimating this event's significance at ${\pastrobcr\leq0.6}$.
-Finally, GW170425 which has ${\pastrobcr<0.25}$ also has low \pastro reported in OGC-2 and OGC-3 \cite{pycbc_ogc_2,pycbc_ogc_3}, suggesting that GW170425 may have been false alarm.
+Finally, GW170425 which has ${\pastrobcr<0.25}$ also has low \pastro reported in OGC-2 and OGC-3 \citep{pycbc_ogc_2,pycbc_ogc_3}, suggesting that GW170425 may have been false alarm.
 
@@
 This candidate has a ${\text{SNR}\sim7.7}$, low spin magnitudes, and source-frame component masses of ${({47.16}_{-5.77}^{+8.00}, {35.50}_{-6.35}^{+5.79}) \msun}$ ($90\%$ credible intervals), making it one of the heavier black-hole mergers from O2 and \GWTC.
-This candidate may be of interest as one component black hole may lie in the pair-instability mass gap $({55^{+10}_{-10}-148^{+13}_{-12})\msun}$~\cite{Woosley:2021:arXiv, Heger:2002:ApJ}.
+This candidate may be of interest as one component black hole may lie in the pair-instability mass gap $({55^{+10}_{-10}-148^{+13}_{-12})\msun}$~\citep{Woosley:2021:arXiv, Heger:2002:ApJ}.
 More details on the candidate are presented in Appendix~\ref{apdx:170222}.
@@
 
-\section{\label{sec:Conclusion}Conclusion}
+\section{Conclusion}
+\label{sec:Conclusion}
 
-In this paper, we demonstrate that the Bayesian Coherence Odds-Ratio \bcr~\cite{BCR1} can be used as a ranking statistic to provide a measure of significance for gravitational-wave signals originating from CBCs with lab-frame total masses between $55~\msun$ and $400~\msun$, a range that includes IMBHs.
+In this paper, we demonstrate that the Bayesian Coherence Odds-Ratio \bcr~\citep{BCR1} can be used as a ranking statistic to provide a measure of significance for gravitational-wave signals originating from CBCs with lab-frame total masses between $55~\msun$ and $400~\msun$, a range that includes IMBHs.
 To compute the \bcr for candidates, we utilize Bayesian inference to calculate the probability of data under various hypotheses (the hypotheses that the data contains a coherent signal, just noise, or an incoherent glitch).
@@
 
-In our study, we analyze O2 binary-black hole events and candidates with ${\totMlab > 55~\msun}$ reported by the \pycbc search~\cite{pycbc_ogc_2}, the \IAS-team~\cite{IAS1, IAS2} and those reported in \GWTC~\cite{GWTC1}.
+In our study, we analyze O2 binary-black hole events and candidates with ${\totMlab > 55~\msun}$ reported by the \pycbc search~\citep{pycbc_ogc_2}, the \IAS-team~\citep{IAS1, IAS2} and those reported in \GWTC~\citep{GWTC1}.
 Using a \pastrobcr threshold of 0.5, we find that the \GWTC events have high probabilities of originating from an astrophysical source.
@@
 
-\begin{acknowledgments}
+\section*{Acknowledgments}{
 The authors gratefully thank the \pycbc team for providing the gravitational-wave foreground, background, and simulated triggers from \pycbc's search of O2's data.
@@
 All analyses (inclusive of test and failed analyses) performed for this study used ${1.3\mathrm{M}}$ core-hours, amounting to a carbon footprint of ${\sim167\ \mathrm{t}}$ of ${\text{CO}_2}$ (using the U.S.
-average electricity source emissions of ${0.429\ \text{kg/kWh}}$~\cite{greenhouse} and ${0.3\ \text{kWh}}$ for each CPU).
+average electricity source emissions of ${0.429\ \text{kg/kWh}}$~\citep{greenhouse} and ${0.3\ \text{kWh}}$ for each CPU).
 
@@
 Additional support for Advanced LIGO was provided by the Australian Research Council.
-Virgo is funded, through the European Gravitational Observatory (EGO), by the French Centre National de Recherche Scientifique (CNRS), the Italian Istituto Nazionale di Fisica Nucleare (INFN) and the Dutch Nikhef, with contributions by institutions from Belgium, Germany, Greece, Hungary, Ireland, Japan, Monaco, Poland, Portugal, Spain.\\
-
-\end{acknowledgments}
+Virgo is funded, through the European Gravitational Observatory (EGO), by the French Centre National de Recherche Scientifique (CNRS), the Italian Istituto Nazionale di Fisica Nucleare (INFN) and the Dutch Nikhef, with contributions by institutions from Belgium, Germany, Greece, Hungary, Ireland, Japan, Monaco, Poland, Portugal, Spain.
+}
 
@@
 {
-We analyze publicly-available gravitational wave strain data from the LIGO-Virgo-KAGRA collaboration~\cite{O2data}.
-The trigger times for analysis were provided by the \pycbc team.
+We analyze publicly-available gravitational wave strain data from the LIGO-Virgo-KAGRA collaboration~\citep{dataO2}.
+The trigger times for analysis were provided by the \pycbc team~\citep{pycbc_ogc_2}.
 The derived data generated in this research will be shared on reasonable request to the corresponding author.
-
-\textit{Software:} \href{https://lscsoft.docs.ligo.org/bilby/}{\bilby} (version 1.0.0)~\cite{bilby}, \href{https://lscsoft.docs.ligo.org/bilby_pipe/master/index.html}{\bilbypipe} (version 1.0.0)~\cite{bilby_pipe}, \href{https://dynesty.readthedocs.io/}{\dynesty}~\cite{dynesty, skilling2004, skilling2006}, \href{https://gwpy.github.io/docs/stable/index.html}{\gwpy}~\cite{gwpy}, \href{https://lscsoft.docs.ligo.org/lalsuite/lalsimulation/index.html}{\code{LALSimulation}}~\cite{lalsuite}, \code{matplotlib}~\cite{matplotlib}, \code{NumPy}~\cite{NumPy}, \code{SciPy}~\cite{SciPy}, \code{pandas}~\cite{pandas}, \code{python}~\cite{pythonForScientificComputing,pythonForScientists}.
+\begin{flushleft}
+\textit{Software:} \href{https://lscsoft.docs.ligo.org/bilby/}{\bilby}~\citep[v0.6.8]{bilby}, \href{https://lscsoft.docs.ligo.org/bilby_pipe/master/index.html}{\bilbypipe}~\citep[v0.3.12]{bilby_pipe}, \href{https://dynesty.readthedocs.io/}{\dynesty}~\citep[v0.9.5.3]{dynesty}, \href{https://gwpy.github.io/docs/stable/index.html}{\gwpy}~\citep[v1.0.1]{gwpy}, \href{https://lscsoft.docs.ligo.org/lalsuite/lalsimulation/index.html}{\code{LALSimulation}}~\citep[v6.70]{lalsuite}, \code{matplotlib}~\citep[v3.2.0]{matplotlib}, \code{NumPy}~\citep[v1.8.1]{NumPy}, \code{SciPy}~\citep[v1.4.1]{SciPy}, \code{pandas}~\citep[v1.0.2]{pandas}, \code{python}~\citep[v3.7]{pythonForScientificComputing,pythonForScientists}.
+\end{flushleft}
 }
 
-%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
+
+% The best way to enter references is to use BibTeX:
+
+\bibliographystyle{mnras}
+\bibliography{high_mass_bib} % if your bibtex file is called example.bib
+
+%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
 
@@
 \subsection{Noise Model}
-We assume that each detector's noise is Gaussian and stationary over the period being analyzed~\cite{ligo_psd}.
-In practice, we assume that the noise has a mean of zero that the noise variance $\sigma^2$ is proportional to the noise power spectral density (PSD) \psd of the data.
-Using the \psd, for each frequency-domain data segment $d_i$ in each of the $i$ detectors in a network of $D$ detectors, we can write
+We assume that each detector's noise is Gaussian and stationary over the period being analyzed~\citep{ligo_psd}.
+In practice, we assume that the noise has a mean of zero that the noise variance $\sigma^2$ is proportional to the noise power spectral density \psd of the data.
+Using \psd, for each frequency-domain data segment $d_i$ in each of the $i$ detectors in a network of $D$ detectors, we can write
 \begin{equation}
@@
 Finally, as glitches are challenging to model and poorly understood, we follow \citet{bci} and utilize a surrogate model for glitches.
-The glitches are modeled using gravitational-wave templates  \template with uncorrelated parameters amongst the different detectors such that  $\parameters_i \neq \parameters_j$ for two detectors $i$ and $j$~\cite{bci}.
+The glitches are modeled using gravitational-wave templates  \template with uncorrelated parameters amongst the different detectors such that  $\parameters_i \neq \parameters_j$ for two detectors $i$ and $j$~\citep{bci}.
 Modeling glitches with \template captures the worst-case scenario: when glitches are identical to gravitational-wave signals (excluding coherent signals).
@@
 The prior odds parameters $\hat{\pi}^S$ and $\hat{\pi}^G$ from Eq.~\ref{eq:bcr} help separate the two distributions.
-Altering $\hat{\pi}^S$ translates the \bcr probability distributions while adjusting $\hat{\pi}^G$ spreads the distributions (refer to Appendix A of \citet{BCR1}).
+Altering $\hat{\pi}^S$ translates the \bcr probability distributions while adjusting $\hat{\pi}^G$ spreads the distributions~\citep[see][Appendix A]{BCR1}.
 Although Bayesian hyper-parameter estimation can determine the optimal values for $\hat{\pi}^S$ and $\hat{\pi}^G$, an easier approach is to adjust the parameters for each data chunk's \bcr distribution.
@@
 \section{A closer look at 170222}\label{apdx:170222}
-PyCBC found the candidate 170222 with $\mathcal{M}_c=49.46$ and $q=0.68$, values contained inside the $90\%$ credible intervals of our posterior probability distributions for 170222.
+PyCBC found the candidate 170222 with $\mathcal{M}=49.46\ \msun$ and $q=0.68$, values contained inside the $90\%$ credible intervals of our posterior probability distributions for 170222.
 Some of the posteriors produced as a by-product of our \bcr calculation can be viewed in Fig.~\ref{fig:170222}.
@@
 
-\bibliography{high_mass_bib}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% Don't change these lines
+\bsp	% typesetting comment
+\label{lastpage}
 

### 2022-01-21 referee_response/example.tex
Added ref review

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Referee 1: Short description of comment
\subsection*{Referee: Comment 1} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Exact comment- copied and pasted
\begin{tcolorbox}[left = 1em, top = 1ex, bottom = 1ex, colupper=black, colback=black!10, adjusted title = Referee: Comment 1]
    \setlength\parindent{2em}
	\noindent
	\ttfamily

	WORD FOR WORD COPY AND PASTE OF COMMMENT
\end{tcolorbox}

% Response

\paragraph{Short indicator of what the point is (e.g., Event study coefficients are hard to read)} Answer

\paragraph{Short indicator of what the point is (e.g., Event study should use -1 as reference category)} Answer

In response we have added the following text to the manuscript (beginning on \hl{page XX}).

% Text added to manuscript    
	\begin{tcolorbox}[left = 1em, top = 1ex, bottom = 1ex, colupper=black, colback=white, adjusted title = From page \hl{XX}]

       EXACT TEXT FROM MANUSCRIPT

        \begin{align}
            y_{it} = &~\beta X + \epsilon_{it} \notag
        \end{align}

        We report all coefficient estimates in Table~2. {\color{red} {\ttfamily[Table~\ref{tab:main_results}in this report.}} \\

        {\color{red} {\ttfamily[text continued on next page]}} \\
    \end{tcolorbox}

### 2022-01-21 titlepage_mnras.tex
Added ref review

%------ affiliation shortcuts
\newcommand{\SPA}{School of Physics and Astronomy, Monash University, Clayton VIC 3800, Australia}
\newcommand{\OzGravMonash}{OzGrav: The ARC Centre of Excellence for Gravitational Wave Discovery, Clayton VIC 3800, Australia}
\newcommand{\CIT}{LIGO Laboratory, California Institute of Technology, Pasadena, CA 91125, USA}
\newcommand{\MIT}{LIGO Laboratory, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
\newcommand{\Kavli}{Department of Physics and Kavli Institute for Astrophysics and Space Research,\\ Massachusetts Institute of Technology, 77 Massachusetts Ave, Cambridge, MA 02139, USA}
\newcommand{\Royal}{Department of Physics, Royal Holloway, University of London, TW20 0EX, United Kingdom}

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% % Title of the paper, and the short title which is used in the headers.
% % Keep the title short and informative.
% \title[MNRAS \LaTeX\ guide for authors]{\textit{Monthly Notices of the Royal Astronomical
%   Society}:  \LaTeX\ guide for authors}
\title[An IMBH search in O2 using the BCR]{A search for intermediate-mass black holes mergers in the \\second LIGO--Virgo observing run with the Bayes Coherence Ratio}

% % The list of authors, and the short list which is used in the headers.
% % If you need two or more lines of authors, add an extra line using \newauthor
% \author[K. T. Smith]{Keith T. Smith$^{1}$%
% \thanks{Contact e-mail: \href{mailto:mn@ras.ac.uk}{mn@ras.ac.uk}}%
% \thanks{Present address: Science magazine, AAAS Science International, \mbox{82-88}~Hills Road, Cambridge CB2~1LQ, UK}%
% \\
% % List of institutions
% $^{1}$Royal Astronomical Society, Burlington House, Piccadilly, London W1J 0BQ, UK}

\author[Vajpeyi et al.]{Avi~Vajpeyi$^{1,2}$\thanks{avi.vajpeyi@monash.edu},
    Rory~Smith$^{1,2}$,
    Eric~Thrane$^{1,2}$,
    Gregory~Ashton$^{1,2,3}$,
    Thomas~Alford$^{4}$,
    \newauthor
    Sierra~Garza$^{4}$,
    Maximiliano~Isi$^{5,6}$,
    Jonah~Kanner$^{4}$,
    T. J.~Massinger$^{4}$,
    Liting~Xiao$^{4}$
\\
$^{1}$ \SPA \\
$^{2}$ \OzGravMonash \\
$^{3}$ \Royal \\
$^{4}$ \CIT \\
$^{5}$ \MIT \\
$^{6}$ \Kavli 
}

% % These dates will be filled out by the publisher
\date{Last updated XXX; in original form XXX}

% % Enter the current year, for the copyright statements etc.
\pubyear{2021}

### 2022-07-20 main.tex
ref response 2

@@
 \usepackage{amssymb}
+\usepackage{widebar}
+\usepackage{ragged2e}
 \usepackage{amsmath}
@@
 
-% Software
-\newcommand{\code}[1]{{\texttt{#1}}\xspace}
-\newcommand{\bilby}{\code{bilby}}
-\newcommand{\bilbypipe}{\code{bilby-pipe}}
-\newcommand{\dynesty}{\code{dynesty}}
-\newcommand{\gwpy}{\code{GWpy}}
-
-% Keywords
-\newcommand{\imrphenomp}{{\sc \texttt{IMRPhenomPv2}}\xspace}
-\newcommand{\seob}{{\sc \texttt{SEOBNRv4PHM}}\xspace}
-\newcommand{\nrsur}{{\sc \texttt{NRSur7dq4}}\xspace}
-\newcommand{\imrxhm}{{\sc \texttt{IMRPhenomXPHM}}\xspace}
-\newcommand{\gstlal}{{\sc GstLAL}\xspace}
-\newcommand{\cwb}{{\sc cWB}\xspace}
-\newcommand{\spiir}{{\sc SPIIR}\xspace}
-\newcommand{\mbta}{{\sc MBTAOnline}\xspace}
-\newcommand{\pycbc}{{\sc {{PyCBC}}}\xspace}
-\newcommand{\GWTC}{{\sc {{GWTC-1}}}\xspace}
-\newcommand{\OGC}{{\sc {{2-OGC}}}\xspace}
-\newcommand{\IAS}{{\sc {{IAS}}}\xspace}
-
-% math keywords 
-\newcommand{\fancytext}[1]{{\relax\ifmmode#1\else $#1$\fi}\xspace}
-\newcommand{\mathcmd}[1]{{\sc \relax\ifmmode#1\else $#1$\fi}\xspace}
-\newcommand{\bcr}{\mathcmd{\rho_\text{BCR}}}
-\newcommand{\bgrdbcr}{\mathcmd{\rho_\text{BCR}^\textit{b}}}
-\newcommand{\candbcr}{\mathcmd{\rho_\text{BCR}^\textit{c}}}
-\newcommand{\bcrodds}{\mathcmd{\mathcal{O}_{\mathrm{BCR}}}}
-\newcommand{\pycbcstat}{\mathcmd{\rho_\text{PC}}}
-\newcommand{\snr}{\mathcmd{\rho}}
-\newcommand{\psd}{\mathcmd{P(f)}}
-\newcommand{\msun}{\mathcmd{M_\odot}}
-\newcommand{\mtot}{\mathcmd{M}}
-\newcommand{\parameters}{\mathcmd{\vec{\theta}}}
-\newcommand{\prior}{\mathcmd{\pi(\parameters)}}
-\newcommand{\template}{\mathcmd{\mu(\parameters)}}
-\newcommand{\fap}{\mathcmd{p_N}}
-\newcommand{\totMlab}{\mathcmd{M}}
-\newcommand{\pastro}{\fancytext{p_\text{astro}}}
-\newcommand{\pastrobcr}{\fancytext{p_\text{S}}}
-\newcommand{\untunedpastrobcr}{\fancytext{p_\text{S}^{\prime}}}
-\newcommand{\tunedpastrobcr}{\fancytext{p_\text{S}}}
-\newcommand{\pastroext}{\fancytext{p_\text{astro}^{\text{ext}}}}
-\newcommand{\pval}{\fancytext{\text{p-value}}}
-
-\newcommand{\pastroGwtcPycbc}{\fancytext{p_\text{astro}^{\text{pyCBC}}}}
-\newcommand{\pastroGwtcGstlal}{\fancytext{p_\text{astro}^{\text{GstLAL}}}}
-\newcommand{\pastroIas}{\fancytext{p_\text{astro}^{\text{IAS}}}}
-\newcommand{\pastroPrat}{\fancytext{P(S|\text{d})}}
-\newcommand{\pastroSing}{\fancytext{p_\text{astro}^{\text{S}}}}
-\newcommand{\pastroOgcTwo}{\fancytext{p_\text{astro}^{\text{OGC2}}}}
-\newcommand{\pastroOgcThree}{\fancytext{p_\text{astro}^{\text{OGC3}}}}
-\newcommand{\tc}{\fancytext{t_c}}
-
-% Table settings
-\renewcommand{\aboverulesep}{0pt}
-\renewcommand{\belowrulesep}{0pt}
-\newcolumntype{C}{>{\centering\arraybackslash}X}
-\newcolumntype{L}{>{\arraybackslash}X}
-\newcolumntype{a}{>{\columncolor{gray}}c}
-\addtolength{\extrarowheight}{\belowrulesep}
+\input{custom_commands}
 
@@
 
-% Don't change these lines
 \begin{document}
@@
 The detection of an intermediate-mass black hole population ($10^2-10^6\ M_\odot$) will provide clues to their formation environments (e.g., disks of active galactic nuclei, globular clusters) and illuminate a potential pathway to produce supermassive black holes.
-Ground-based gravitational-wave detectors are sensitive to a subset of such mergers and have been used to detect one $142^{+28}_{-16}\ M_\odot$ intermediate-mass black hole formation event.
+Ground-based gravitational-wave detectors are sensitive to mergers that can form intermediate-mass black holes weighing up to $\sim 450\ M_\odot$.
 However, ground-based detector data contain numerous incoherent short duration noise transients that can mimic the gravitational-wave signals from merging intermediate-mass black holes, limiting the sensitivity of searches.
-Here we search for binary black hole mergers using a Bayesian-inspired ranking statistic which measures the coherence or incoherence of triggers in multiple-detector data.
-We use this statistic to identify candidate events with lab-frame total masses $\gtrsim55\ M_\odot$ using data from LIGO's second observing run.
+Here we \green{follow-up on} binary black hole merger \green{candidates} using a ranking statistic that measures the coherence or incoherence of triggers in multiple-detector data. 
+We use this statistic to \green{rank} candidate events,  \green{initially identified by all-sky search pipelines,} with lab-frame total masses $\gtrsim55\ M_\odot$ using data from LIGO's second observing run.
 Our analysis does not yield evidence for new intermediate-mass black holes. 
-However, we find support for some stellar-mass binary black holes not reported in the first LIGO--Virgo gravitational-wave transient catalog, GWTC-1.
+However, we find support for eight stellar-mass binary black holes not reported in the first LIGO-Virgo gravitational wave transient catalog GWTC-1, seven of which have been previously reported by other catalogs.
 \end{abstract}
@@
 
-A variety of techniques have been employed to search for ${10^{4} - 10^{6}~\msun}$ intermediate-mass black hole (IMBH) candidates including reverberation mapping~\citep{Peterson:2014:SSRv}, direct kinematic measurements~\citep{Schodel:2002:Natur, Kiziltan:2017:Natur}, applying macroscopic galaxy to black hole mass scaling relations, $M_{BH}$-$\sigma$ and $M_{BH}$-L relations~\citep{Graham:2013:ApJ, Wevers:2017:MNRAS}, studying  X-ray luminosity and spectra~\citep{Greene:2004:ApJ, Lin:2020:ApJL}, gravitational lensing of gamma-ray burst light curves~\citep{paynter_evidence_2021}, and others~\citep[see][]{Greene:2020:ARA&A, Koliopanos:2017:mbhe, Mezcua:2017:IJMPD}.
-However, because IMBH have smaller gravitational spheres of influence than those of supermassive black holes, it is much more challenging to observe them with these observational techniques~\citep{Mezcua:2017:IJMPD}.
-Additionally, the numerous IMBH candidates discovered using these techniques are ambiguous as other sources can describe observations from the candidates (e.g., light sources orbiting clusters of stellar-mass black holes~\citealt{Ridolfi:2016:MNRAS, Freire:2017:MNRAS},  anisotropic emission from neutron stars~\citealt{Israel:2017:MNRAS, RodriguezCastillo:2020:ApJ}).
-
 Stellar mass (${M_\text{BH} < 10^{2}~\msun}$) and supermassive black holes (${M_\text{BH} > 10^{6}~\msun}$) have been observed and well studied since the 1970s~\citep{Webster:1972:Natur, Balick:1974:ApJ, Ghez:1998:ApJ, Genzel:2010:RvMP, Abbott:2019:PhRvX, EventHorizonTelescopeCollaboration:2019:ApJL, Abbott:2020:arXiv}.
 However, there is a deficiency of observational evidence for black holes in the intermediate-mass range ${10^{2} - 10^{6}~\msun}$. 
-The discovery of an IMBH population will bridge this observational gap, probe IMBH formation environments (e.g.
+A variety of techniques have been employed to search for intermediate-mass black hole (IMBH) candidates including reverberation mapping~\citep{Peterson:2014:SSRv}, direct kinematic measurements~\citep{Schodel:2002:Natur, Kiziltan:2017:Natur}, applying macroscopic galaxy to black hole mass scaling relations, $M_{BH}$-$\sigma$ and $M_{BH}$-L relations~\citep{Graham:2013:ApJ, Wevers:2017:MNRAS}, studying  X-ray luminosity and spectra~\citep{Greene:2004:ApJ, Lin:2020:ApJL}, gravitational lensing of gamma-ray burst light curves~\citep{paynter_evidence_2021}, and others~\citep[see][]{Greene:2020:ARA&A, Koliopanos:2017:mbhe, Mezcua:2017:IJMPD}.
+However, because IMBH have smaller masses than those of supermassive black holes, it is much more challenging to observe them with these observational techniques~\citep{Mezcua:2017:IJMPD}. 
+Additionally, numerous IMBH candidates discovered using these techniques are ambiguous as the observations can be attributed to other sources (e.g., light sources orbiting clusters of stellar-mass black holes~\citealt{Ridolfi:2016:MNRAS, Freire:2017:MNRAS},  anisotropic emission from neutron stars~\citealt{Israel:2017:MNRAS, RodriguezCastillo:2020:ApJ}).
+The discovery of an IMBH population will bridge the intermediate-mass observational gap, probe IMBH formation environments (e.g.
 accretion disks of active galactic nuclei~\citealt{Tagawa:2021:ApJ, Li:2021:arXiv, Samsing:2020:arXiv, Tagawa:2020:ApJ, Ishibashi:2020:A&A, Grobner:2020:A&A, Yang:2019:PhRvL, McKernan:2019:ApJL, Yang:2019:ApJ, McKernan:2018:ApJ, Bellovary:2016:ApJL, McKernan:2014:MNRAS, McKernan:2012:MNRAS}, the centers of dense stellar clusters~\citealt{Banerjee:2021:MNRASa, Zevin:2021:ApJ,Mapelli:2021:arXiv,Weatherford:2021:ApJL, Bouffanais:2021:arXiv, Ballone:2021:MNRAS, Kumamoto:2021:arXiv, Banerjee:2021:MNRASb, Martinez:2020:ApJ, Romero-Shaw:2020:ApJL, Anagnostou:2020:PASA}, Population-III stars~\citealt{Toubiana:2021:PhRvL, Farrell:2021:MNRAS, Safarzadeh:2020:ApJL, Liu:2020:MNRAS, Inayoshi:2017:MNRAS}), and illuminate our understanding of supermassive black hole formation~\citep{Askar:2021:MNRAS, ArcaSedda:2019:arXiv, Amaro-Seoane:2007:CQGra, Gurkan:2006:ApJL}.
 
-Compact binary coalescences (CBCs) can provide unambiguous gravitational-wave signals for IMBH candidates e.g., the ${142^{+28}_{-16}~\msun}$ ($90\%$ credible intervals) remnant observed from the gravitational-wave event GW190521~\citep{Abbott:2020:PhRvL} and other candidates~\citep{ligo_imbh_search, ligo_imbh_o3, pycbc_imbh}.
-As a binary's lab-frame total mass $M$ is associated with its gravitational-wave merger frequency, ${f\sim M^{-1}}$,  ground-based gravitational-wave detectors (${f\sim 10^1 - 10^3\ \text{Hz}}$) are sensitive to the last milliseconds of merging systems with ${100~\msun < \totMlab < 400~\msun}$~\citep{LIGOScientificCollaboration:2015:CQGra, Martynov:2016:PhRvD, Moore_2014, Acernese:2015:CQGra}, while space-based detectors (${f\sim 10^{-2}-10^1\ \text{Hz}}$) can study the full signals of merging systems with ${10^4~\msun < \totMlab < 10^7~\msun}$~\citep{ Moore_2014, Lu:2019:PhRvD}.
+Compact binary coalescences (CBCs) can provide gravitational-wave signals for IMBH candidates e.g., the ${142^{+28}_{-16}~\msun}$ ($90\%$ credible intervals) remnant observed from the gravitational-wave event GW190521~\citep{Abbott:2020:PhRvL} and other candidates~\citep{ligo_imbh_search, ligo_imbh_o3, pycbc_imbh}.
+As a binary's lab-frame total mass $M$ is associated with its gravitational-wave merger frequency, ${f\propto M^{-1}}$,  ground-based gravitational-wave detectors (${f\sim 10^1 - 10^3\ \text{Hz}}$) are sensitive to the last milliseconds of merging systems with ${100~\msun < \totMlab < 400~\msun}$~\citep{LIGOScientificCollaboration:2015:CQGra, Martynov:2016:PhRvD, Moore_2014, Acernese:2015:CQGra}, while space-based detectors (${f\sim 10^{-2}-10^1\ \text{Hz}}$) can study the full signals of merging systems with ${10^4~\msun < \totMlab < 10^7~\msun}$~\citep{ Moore_2014, Lu:2019:PhRvD}.
 Because of the short duration of IMBH gravitational-wave signals in ground-based detectors, data quality is critical for their detection.
@@
 In this paper, we use the \bcr to rank O2’s coincident CBC gravitational-wave candidates with lab-frame total masses in the range of ${55-500~\msun}$.
-We present the candidates' \pastrobcr, the probability that the candidate originates from a coherent gravitational-wave source.
+We present the candidates' $\pastrobcr$, the probability that the candidate is inconsistent with the background distributions of \bcr values computed from time-slid data. 
 Additionally, for comparison, we provide the candidate's \pastro values reported by the LIGO-Virgo-KAGRA (LVK) collaboration in \GWTC~\citep{GWTC1}, the \pycbc-team~\citep{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6, pycbc_single_det, pycbc_ogc_2}, by the Institute of Advanced study's team (\IAS)~\citep{IAS0, IAS1, IAS2}, and by \citet{bayesian_odds}.
 
-We find that (a) events reported in \GWTC, including GW170729 (likely the most massive BBH system in \GWTC) are statistically significant ${\pastrobcr>0.9}$; (b) three out of the eight \IAS events and candidates have ${\pastrobcr>0.9}$, corroborating \IAS's detection claims for GW170304, GW170727, and GW170817A; and that (c) our ranking statistic does not identify any new IMBH, but does identify an unreported marginal stellar-mass binary black hole candidate, 170222\footnote{170222 is a sub-threshold candidate detected by \pycbc (${\tc = 1171814476.97}$) with a ${\pastrobcr\sim0.6}$.
-The prefix of GW is not utilized as this is a candidate event.} with ${\pastrobcr\sim0.6}$.
+We find that (a) events reported in \GWTC, including GW170729 (likely the most massive BBH system in \GWTC) are statistically significant ${\pastrobcr>0.9}$; (b) three out of the eight \IAS events and candidates have ${\pastrobcr>0.9}$, corroborating \IAS's detection claims for GW170304, GW170727, and GW170817A; and that (c) our ranking statistic does not identify any new IMBH, but does identify an unreported marginal stellar-mass binary black hole candidate, 170222 with ${\pastrobcr\sim0.6}$.\footnote{
+\RaggedRight
+170222 is a sub-threshold candidate detected by \pycbc (${{\rm SNR}\sim7.7}$). The prefix of GW is not utilized as this is a candidate event.
+}
 
@@
 We compute the Bayesian evidence under the assumption that the data either contain a coherent gravitational-wave signal, noise, or a glitch ($Z^S, Z^N, Z^G$, defined in Appendix~\ref{sec:bayesianEvidEval}).
-However, instead of computing true Bayesian odds, we use the evidences as a ranking statistic.
+However, because we do not have at our disposal a set of PyCBC triggers generated for simulated signals from a realistic population, we use the evidences as a ranking statistic, instead of computing true Bayesian odds.
 We form a bootstrapped distribution of the evidence for simulated foreground and background events to form a frequentist ranking statistic.
+Our work highlights the importance of an astrophysically realistic injection set for calculating $p_\text{astro}$.
 
@@
 
-Introduced by \citet{BCR1}, the Bayesian Coherence Ratio for a candidate signal in a network of $D$ detectors is given by
+Introduced by \citet{BCR1}, the Bayesian Coherence Ratio for a signal in a network of $D$ detectors is given by
 \begin{equation}
@@
 \end{equation}
-where $\{\hat{\pi}^S, \hat{\pi}^N_i, \hat{\pi}^G_i\}$ are estimates of the astrophysical prior-odds that the data contain a coherent signal, incoherent noise or an incoherent glitch.
-We assume each detector has the same glitch and noise prior odds of $\{\hat{\pi}^N, \hat{\pi}^G\}$.
-In the limit where the estimated prior-odds equal the astrophysical prior-odds, the \bcr becomes the optimal Bayesian odds described by \citet{BCR2}.
-However, as the astrophysical prior-odds are unknown, it is invalid to use the \bcr as an odds-ratio to discriminate signals from glitches.
-Instead, we use the \bcr as a ranking statistic to obtain a frequentist significance of a candidate \bcr-value, $\candbcr$, measured against a background \bcr distribution, $\bgrdbcr$.
+where $\{\hat{\pi}^S, \hat{\pi}^N_i, \hat{\pi}^G_i\}$ are ``pseudo prior probabilities'' that the data contain a coherent signal, incoherent noise or an incoherent glitch.
+These factors are not true prior probabilities because they are not chosen a priori.
+Rather, these factors are obtained by minimizing the overlap between a signal and background distribution (see Appendix D). 
+We assume each detector has the same glitch and noise prior probabilities of $\{\hat{\pi}^N, \hat{\pi}^G\}$.
+In the limit where our pseudo prior probabilities equal the actual prior probabilities, the \bcr becomes the optimal Bayesian odds described by \citet{BCR2}.
+However, as we do not (in this work) have a reliable estimate for the prior probabilities, we cannot interpret the \bcr as a Bayesian odds to discriminate signals from glitches.
+Instead, we use the \bcr as a ranking statistic to obtain a frequentist significance of \bcr.
 
@@
 Since it is impossible to shield ground-based gravitational-wave detectors from gravitational-wave signals, the LVK empirically estimates the background by repeatedly time-shifting strain data by amounts larger than the light-travel time between the two LIGO detectors~\citep{GWTC1}.
-We use time-shifted data to generate $\bgrdbcr$.
-Following this, each candidate's single-event false alarm probability $p_1$ of being miss-classified as a glitch is given by
+We use time-shifted data to generate $\bgrdbcr$, \green{the background ranking statistic}.
+Following this, we calculate the \green{fraction of $\bgrdbcr$ greater than or equal to a $\candbcr$, the candidate ranking statistic}:
 \begin{equation}
-    p_1 = \frac{\text{Count of } \bgrdbcr \leq \candbcr}{\text{Count of } \bgrdbcr} \ .
+    p_1^b = \frac{\text{Count of } \bgrdbcr \leq \candbcr}{\text{Count of } \bgrdbcr} \ .
 \end{equation}
-Moreover, as we have several candidates ($N$ candidates), each with a \candbcr, we account for them by calculating a false-alarm probability with trial factors $p_N$ given by
+Given a set of simulated signals \green{and their ranking statistic $\injbcr$, one may calculate the fraction of $\injbcr$ greater than or equal to a $\candbcr$}: 
 \begin{equation}
-    \fap = 1 - (1-p_1)^N \ .
+    p_1^s = \frac{\text{Count of } \injbcr \leq \candbcr}{\text{Count of } \injbcr} \ .
 \end{equation}
-Finally, we can calculate the probability of the candidate signal event occurring from  a gravitational-wave, \pastrobcr with 
+\green{With $p_1^b$ and $p_1^s$ it is possible to compute a candidate’s 
+\pastro, the probability that a candidate is of astrophysical origin:}
+\begin{equation}
+    \pastro = \frac{p_1^s}{p_1^s + p_1^b}\ .
+\end{equation}
+However, for this study we do not have an astrophysical distribution of simulated signals and so we cannot compute $p_1^s$ \green{or consequently $\pastro$}. 
+Instead we opt for a frequentist $p$-value probability that a candidate is inconsistent with the background. 
+As we have $k$ candidates, each with a \candbcr, we calculate a false-alarm probability \fap that accounts for trial factors given by
+\begin{equation}
+    \fap = 1 - (1-p_1^b)^k \ .
+\end{equation}
+Finally, we compute the probability that a candidate is inconsistent with the background:
 \begin{equation}
@@
 \end{equation}
+When $\pastrobcr \ll 1$, the event is consistent with the background distribution. 
+Conversely, when $\pastrobcr \approx 1$ the event is inconsistent with the background distribution, and is therefore a promising gravitational-wave candidate.
+
+\green{It is important to note that 
+$\pastrobcr$ (the probability that an event is not part of the background distribution) is not the same as $\pastro$, which requires an astrophysical set of simulated signals.}
 
@@
 Some of the triggers are associated with gravitational-wave events and candidates while others are glitches.
-We also acquire background and simulated triggers from \pycbc's O2 search to calculate $\bgrdbcr$ and estimate values for $\{\hat{\pi}^S,\hat{\pi}^G\}$ (see Appendix~\ref{apdx:tuning-prior-odds} for details on the estimation process).
+We also acquire background time-slid triggers and simulated triggers from \pycbc's O2 search to calculate $\bgrdbcr$ and estimate values for $\{\hat{\pi}^S,\hat{\pi}^G\}$ (see Appendix~\ref{apdx:tuning-prior-odds} for details on the estimation process).
 The triggers are divided into two week time-frames because the detector's sensitivity does not stay constant throughout the eight-month-long observing period~\citep{pycbc_og4}.
@@
 This region focuses our analysis on binary black hole mergers with lab-frame total masses above ${\gtrsim55 \msun}$, corresponding to binary systems with signal durations $<454 \ \text{ms}$ and ${q\geq0.1}$.
-The filtering process leaves us with $60,996$ background, $5,146$ simulated, and $25$ candidate signal triggers.
+The filtering process leaves us with ${{\sim}70{,}000}$ background, ${\sim}5{,}000$ simulated, and $25$ candidate signal triggers.
 We additionally include events and candidate events reported by \GWTC and the \IAS group in our list of candidate signal triggers.
@@
 To marginalize over the statistical uncertainty, we use the median-likelihood presented by~\citet{psd_student_t} as a post-processing step.
-We find that this post-processing step improves the search efficiency by $49.26\%$ the details of this calculation are in the Appendix~\ref{sec:psd-marginalization}.
+\green{This post-processing step reduces the percentage of background $\bgrdbcr>0$ by $\sim49\%$.} The details of this calculation are in the Appendix~\ref{sec:psd-marginalization}.
 
@@
 
-Finally, with the $\candbcr$ and $\bgrdbcr$ for each time-frame of triggers, we calculate the candidate signal's \pastrobcr.
+Finally, with the $\candbcr$ and $\bgrdbcr$ for each time-frame of triggers, we calculate the candidate signal's $\pastrobcr$.
 
@@
 The $\hat{\pi}^S$ and $\hat{\pi}^G$ values utilized for each time-frame are reported in Appendix~\ref{apdx:alphabeta}.
-By imposing a \pastrobcr threshold of 0.5, we present 13 candidate gravitational wave events.
+By imposing a $\pastrobcr$ threshold of 0.5, we present 13 candidate gravitational wave events.
 
@@
 Various search pipeline \pastro are not mathematically equivalent~\citep{Galaudage:2020:PhRvD}.
-Moreover, \pastro is not equivalent to \pastrobcr.
-However, by comparing candidates' various \pastro values with \pastrobcr, we can compare how significant each pipeline deems the candidate.
-For comparison, in Table~\ref{tab:results} we report \pastro values from \GWTC~\citep{GWTC1}, PyCBC OGC-2~\citep{pycbc_ogc_2}, PyCBC OGC-3~\citep{pycbc_ogc_2}, PyCBC `single-search'~\citep{pycbc_single_det}, IAS~\citep{IAS1, IAS2}, and \citet{bayesian_odds}'s analyses.
+Moreover, \pastro is not equivalent to $\pastrobcr$.
+However, by comparing candidates' various \pastro values with $\pastrobcr$, we can compare how significant each pipeline deems the candidate.
+For comparison, in Table~\ref{tab:results} we report \pastro values from \GWTC~\citep{GWTC1}, PyCBC OGC-2~\citep{pycbc_ogc_2}, PyCBC OGC-3~\citep{pycbc_ogc_2}, IAS~\citep{IAS1, IAS2}, and \citet{bayesian_odds}'s analyses.
 
@@
 
-In addition to the above confirmed gravitational-wave events from \GWTC, we have also analyzed several candidate events from \GWTC, most of which have low \pastrobcr.
+In addition to the above confirmed gravitational-wave events from \GWTC, we have also analyzed several candidate events from \GWTC, most of which have low $\pastrobcr$.
 For example, consider the candidate event 170412 (${\tc = 1176047817}$), assigned a $\pastro$ of $0.06$ by \gstlal and has a $\pastrobcr$ of $0.01$.
@@
 
-In this paper, we demonstrate that the Bayesian Coherence Odds-Ratio \bcr~\citep{BCR1} can be used as a ranking statistic to provide a measure of significance for gravitational-wave signals originating from CBCs with lab-frame total masses between $55~\msun$ and $400~\msun$, a range that includes IMBHs.
+In this paper, we demonstrate that the Bayesian Coherence Ratio \bcr~\citep{BCR1} can be used as a ranking statistic to provide a measure of significance for gravitational-wave signals originating from CBCs with lab-frame total masses between $55~\msun$ and $400~\msun$, a range that includes IMBHs.
 To compute the \bcr for candidates, we utilize Bayesian inference to calculate the probability of data under various hypotheses (the hypotheses that the data contains a coherent signal, just noise, or an incoherent glitch).
@@
 In our study, we analyze O2 binary-black hole events and candidates with ${\totMlab > 55~\msun}$ reported by the \pycbc search~\citep{pycbc_ogc_2}, the \IAS-team~\citep{IAS1, IAS2} and those reported in \GWTC~\citep{GWTC1}.
-Using a \pastrobcr threshold of 0.5, we find that the \GWTC events have high probabilities of originating from an astrophysical source.
-We also find that some of the \GWTC marginal triggers that have corroborated terrestrial sources (for example, candidate 170412) have low \pastrobcr, indicating this method's ability to discriminate between terrestrial artifacts and astrophysical signals.
+Using a $\pastrobcr$ threshold of 0.5, we find that the \GWTC events have high probabilities of originating from an astrophysical source.
+We also find that some of the \GWTC marginal triggers that have corroborated terrestrial sources (for example, candidate 170412) have low $\pastrobcr$, indicating this method's ability to discriminate between terrestrial artifacts and astrophysical signals.
 Our analysis of the \IAS events demonstrates that GW170121, GW170304, GW170727, and GW170817A are likely to originate from astrophysical sources (${\pastrobcr\geq0.8}$), while GW170425 is not (${\pastrobcr<0.25}$).
@@
 With the rapid rate of development in gravitational-wave Bayesian inference, we anticipate the ability to analyze longer-duration signals, utilize more advanced signal and glitch models, and incorporate data from the entire detector network.
-In a similar vein, with the accumulation of more gravitational wave events, future \bcr work may utilize astrophysically informed priors during Bayesian inference and more accurate prior odds for each detector.
+In a similar vein, with the accumulation of more gravitational wave events, future \bcr work may utilize astrophysically informed priors during Bayesian inference and more accurate prior probabilities for each detector.
 
@@
 
-All analyses (inclusive of test and failed analyses) performed for this study used ${1.3\mathrm{M}}$ core-hours, amounting to a carbon footprint of ${\sim167\ \mathrm{t}}$ of ${\text{CO}_2}$ (using the U.S.
+All analyses (inclusive of test and failed analyses) performed for this study used ${1.3\mathrm{M}}$ core-hours, amounting to a carbon footprint of ${\sim1.67\ \mathrm{t}}$ of ${\text{CO}_2}$ (using the U.S.
 average electricity source emissions of ${0.429\ \text{kg/kWh}}$~\citep{greenhouse} and ${0.3\ \text{kWh}}$ for each CPU).
 
-This work is supported by the Australian Research Council (ARC) Centre of Excellence CE170100004.
 This material is based upon work supported by NSF’s LIGO Laboratory, a major facility fully funded by the National Science Foundation.
@@
 Virgo is funded, through the European Gravitational Observatory (EGO), by the French Centre National de Recherche Scientifique (CNRS), the Italian Istituto Nazionale di Fisica Nucleare (INFN) and the Dutch Nikhef, with contributions by institutions from Belgium, Germany, Greece, Hungary, Ireland, Japan, Monaco, Poland, Portugal, Spain.
+
 }
 
-\section*{Data Availability Statement}
+\section*{Data Availability}
 {
@@
 
-\section{Tuning the prior-odds}\label{apdx:tuning-prior-odds}
+\section{Tuning the prior probabilities}\label{apdx:tuning-prior-odds}
 
-After calculating the \bcr for a set of background triggers and simulated triggers from as stretch of detector-data (a data chunk), we can compute probability distributions for the background and simulated triggers, $p_b(\bcr)$ and $p_s(\bcr)$.
+After calculating the \bcr for a set of background triggers and simulated triggers from a stretch of detector-data (a data chunk), we can compute probability distributions for the background and simulated triggers, $p_b(\bcr)$ and $p_s(\bcr)$.
 We expect the background trigger and simulated signal \bcr values to favor the incoherent glitch and the coherent signal hypothesis, respectively.
 Ideally, these distributions representing two unique populations should be distinctly separate and have no overlap in their \bcr values.
-The prior odds parameters $\hat{\pi}^S$ and $\hat{\pi}^G$ from Eq.~\ref{eq:bcr} help separate the two distributions.
+The prior probability parameters $\hat{\pi}^S$ and $\hat{\pi}^G$ from Eq.~\ref{eq:bcr} help separate the two distributions.
 Altering $\hat{\pi}^S$ translates the \bcr probability distributions while adjusting $\hat{\pi}^G$ spreads the distributions~\citep[see][Appendix A]{BCR1}.
@@
 \begin{equation}
-    D_{KL}(p_b | p_s) = \sum\limits_{x\in \bcr} p_b(x) \log \left( \frac{p_b(x)}{p_a(x)} \right)  \ .
+    D_{KL}(p_b | p_s) = \sum\limits_{x\in \bcr} p_b(x) \log \left( \frac{p_b(x)}{p_s(x)} \right)  \ .
 \end{equation}
@@
 We set our values for $\hat{\pi}^S$ and $\hat{\pi}^G$ to those which provide the highest KL-divergence and calculate the \bcr for candidate events present in this data chunk.
-Note that we conduct the analysis in data chunks of a few days rather than an entire data set of a few months as the background may be different at different points of the entire data set.
+Note that we conduct the analysis in data chunks of two weeks rather than an entire data set of a few months as the background may be different at different points of the entire data set.
 
@@
 Marginalizing over uncertainty in the PSD yields an improvement in the separation of the noise and signal distributions (left plot).
-Quantitatively, at a threshold $\bcr^T=0$ the post-processing step results in a reduction in the number of background $\bcr > \bcr^T$ from $60.7\%$ to $25.28\%$ in the August 13 - 21, 2017 time-frame of data.
-For the entirety of O2, PSD marginalization resulted in a $49.26\%$ improvement in search efficiency.
+Quantitatively, at a threshold $\bcr^T=0$ the post-processing step \green{reduces the percentage of} background $\bcr > \bcr^T$ from $60\%$ to $25\%$ \green{(a $58\%$ improvement)} in the August 13 - 21, 2017 time-frame of data.
+\green{For the entirety of O2, PSD marginalization reduces the percentage of $\bcr > \bcr^T$ from $64\%$ to $33\%$ (a $\sim49\%$ improvement).
+}
 
@@
 
-\section{Tuned prior odds}\label{apdx:alphabeta}
+\section{Tuned prior probabilities}\label{apdx:alphabeta}
 
 O2 lasted several months, over which the detector's sensitivity varied.
-Hence, a part of our analysis entailed tuning the prior odds for obtaining a signal and a glitch, $\hat{\pi}^S$ and $\hat{\pi}^G$, as described in Section~\ref{sec:method}.
-Table~\ref{tab:priorodds} presents the signal and glitch prior odds utilized for each time-frame of O2 data.
+Hence, a part of our analysis entailed tuning the prior probabilities for obtaining a signal and a glitch, $\hat{\pi}^S$ and $\hat{\pi}^G$, as described in Section~\ref{sec:method}.
+Table~\ref{tab:priorodds} presents the signal and glitch prior probabilities utilized for each time-frame of O2 data.
 \input{Data/alpha_beta_table}
 
-Tuning the prior odds can dramatically affect the \pastrobcr.
-For example, consider Table~\ref{tab:tuningresults}, which reports tuned \pastrobcr and un-tuned \untunedpastrobcr (where $\hat{\pi}^S=1$ and $\hat{\pi}^G=1$) for various events and candidates.
-By tuning the prior odds, the \pastrobcr for some IAS events (for example, GW170403 and GW170817A) can change by more than 0.5, resulting in the promotion/demotion of a candidate's significance.
+Tuning the prior probabilities can dramatically affect the $\pastrobcr$.
+For example, consider Table~\ref{tab:tuningresults}, which reports tuned $\pastrobcr$ and un-tuned \untunedpastrobcr (where $\hat{\pi}^S=1$ and $\hat{\pi}^G=1$) for various events and candidates.
+By tuning the prior probabilities, the $\pastrobcr$ for some IAS events (for example, GW170403 and GW170817A) can change by more than 0.5, resulting in the promotion/demotion of a candidate's significance.
 

### 2022-07-20 referee_response/main.tex
ref response 2

% ADAPTED FROM https://github.com/hollina/template-referee-response

\documentclass[11pt,leqno]{article}

%------------------------------------------%
%                Packages
%------------------------------------------%

\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage{microtype,xparse,tcolorbox}
\usepackage{graphicx}
\usepackage{natbib}	%Bibliography package. It handles citations and can easily change formats. This is done at the end of the document
\usepackage[utf8]{inputenx}% For proper input encoding
\usepackage{adjustbox} %Handles resizing of tables, figures, etc. Based off of page and/or line width/height 
% Packages for tables
\usepackage{booktabs}% For Pretty tables
\usepackage{threeparttable}% For Notes below table
\usepackage{rotating}% To Rotate Table
\usepackage{amsmath, amssymb,mathrsfs} %For using math
\usepackage{bm}
\usepackage{caption} 
\usepackage[list=true]{subcaption} %For having multiple figures within the same one. Figure 1, with part (a) and (b)
%\setcounter{lofdepth}{2}
\usepackage{setspace} %Single, Double Space, etc 
\usepackage[paperwidth=8.5in, paperheight=11in,margin=1in]{geometry} %For controlling the dimensions. Very useful for Posters, etc 
\usepackage{chngpage} 
\usepackage{everypage}%For page numbers on rotated pages
\usepackage[capposition=top]{floatrow}
\usepackage{accents}
\usepackage{float}
\usepackage{comment}
\usepackage{morefloats}
\usepackage{placeins}% To Create Float Barriers so the tables will stay in their sections
\usepackage{pdflscape}

\usepackage{siunitx} %This aligns tables by their decimal and handles processing of the numbers within the tables
  \sisetup{
    detect-mode,
    group-digits      = false,
    input-symbols     = {( ) [ ] - +},
    table-align-text-post = false,
    input-signs             = ,
    %parse-numbers=false,
    %scientific-notation = true,
        %round-mode              = places,
        %round-precision         = 2,
        %input-ignore={,},
    %input-decimal-markers={.},
    %group-separator={,},
        } 
\usepackage{grffile}
\usepackage{soul}
\usepackage{color}
\usepackage{caption}
%\captionsetup[figure]{justification=raggedright,singlelinecheck=off}
\sisetup{separate-uncertainty=true}
\usepackage{mathptmx}
\DeclareCaptionLabelFormat{blank}{}

%------------------------------------------%
%              Custom Commands
%------------------------------------------%
\newcommand\iid{i.i.d.} %Makes iid a command
\newcommand\pN{\mathcal{N}} %Makes the natural numbers a command

\setcounter{MaxMatrixCols}{20}

\newtheorem{theorem}{Theorem}%[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{assumption}[theorem]{Assumption}
\newenvironment{proof}{\paragraph{Proof:}}{\hfill$\square$ \\} %This fixes the problem with dynamic tables for some reason

%For Page Numbers while rotated
\newlength{\hfoot}
\newlength{\vfoot}
\AddEverypageHook{\ifdim\textwidth=\linewidth\relax
\else\setlength{\hfoot}{-\topmargin}%
\addtolength{\hfoot}{-\headheight}%
\addtolength{\hfoot}{-\headsep}%
\addtolength{\hfoot}{-.5\linewidth}%
\ifodd\value{page}\setlength{\vfoot}{\oddsidemargin}%
\else\setlength{\vfoot}{\evensidemargin}\fi%
\addtolength{\vfoot}{\textheight}%
\addtolength{\vfoot}{\footskip}%
\raisebox{\hfoot}[0pt][0pt]{\rlap{\hspace{\vfoot}\rotatebox[origin=cB]{90}{\thepage}}}\fi}
%http://tex.stackexchange.com/questions/209685/landscape-mode-and-page-numbering

%------------------------------------------%
%      Title Page Info
%------------------------------------------%
\title{Replies for MN-21-1316:\\
 ``A search for intermediate mass black holes mergers in the second LIGO-Virgo observing run with the Bayes Coherence Ratio
''}
\author{AUTHOR}
\date{\today}
\AtBeginDocument{\maketitle\thispagestyle{empty}\noindent}

\begin{document}

\onehalfspacing

\section*{Response to the referee}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Thank you for your helpful comments and guidance. We describe how we have addressed all of your concerns below. \\
\begin{itemize}
    \item Your comments are \fcolorbox{black}{black!10}{{\ttfamily boxed in gray a different font}}. 
    \item Our responses are in plain text. 
    \item Any included text from the new manuscript is \fbox{boxed in white} with the page number noted at the top of the quoted text. 
    \item Any added comments or other differences from the quoted manuscript text and the text appearing in this report {\color{red} {\ttfamily[appears in brackets with a different font and a red color]}}. 
\end{itemize}

\subsection*{Title Comment} 
\begin{tcolorbox}[left = 1em, top = 1ex, bottom = 1ex, colupper=black, colback=black!10, adjusted title =  Comment 1]
    \setlength\parindent{2em}
	\noindent
	\ttfamily
	Title: black holes mergers -> black hole mergers
\end{tcolorbox}
We have adjusted the title.

\subsection*{Abstract Comments} 
\begin{tcolorbox}[left = 1em, top = 1ex, bottom = 1ex, colupper=black, colback=black!10, adjusted title = Comment 1]
    \setlength\parindent{2em}
	\noindent
	\ttfamily
	2nd sentence "such mergers": what mergers? they haven't been mentioned yet "Bayesian-inspired": this is a bit sneaky, if you aren't doing a full bayesian analysis then don't insinuate that you are.
\end{tcolorbox}

%% what have we done

\begin{tcolorbox}[left = 1em, top = 1ex, bottom = 1ex, colupper=black, colback=black!10, adjusted title = Comment 2]
    \setlength\parindent{2em}
	\noindent
	\ttfamily
    "We find support for some stellar-mass binary black holes not reported in the first LIGO-Virgo gravitational wave transient catalog GWTC-1": This includes events previously reported by the IAS group. Be specific here: you find support for three previously unreported candidates.
\end{tcolorbox}

%% what have we done

%% what have we done

\subsection*{Introduction Comments} 
\begin{tcolorbox}[left = 1em, top = 1ex, bottom = 1ex, colupper=black, colback=black!10, adjusted title =  Comment 1]
    \setlength\parindent{2em}
	\noindent
	\ttfamily
    Abrupt start: There is no motivation given for the searches for IMBHs, you jump right in to previous searches. Why should we expect to find IMBHs? Can you provide some more justification here. Maybe rearrange with the next paragraph.
\end{tcolorbox}

\begin{tcolorbox}[left = 1em, top = 1ex, bottom = 1ex, colupper=black, colback=black!10, adjusted title =  Comment 2]
    \setlength\parindent{2em}
	\noindent
	\ttfamily
    "smaller gravitational spheres of influence" -> too informal. Gravitation has an infinite range so all "spheres of influence" are commensurate. You mean "smaller masses", "smaller Einstein radii", "smaller lensing cross-section" or similar?
\end{tcolorbox}

\begin{tcolorbox}[left = 1em, top = 1ex, bottom = 1ex, colupper=black, colback=black!10, adjusted title =  Comment 3]
    \setlength\parindent{2em}
	\noindent
	\ttfamily
    "other sources can describe observations" the sources do not describe the observations. 
\end{tcolorbox}

Additionally, the numerous IMBH candidates discovered using these techniques are ambiguous as other sources can describe observations from the candidates (e.g., light sources orbiting clusters of stellar-mass black holes

Change to

Additionally, numerous IMBH candidates discovered using these techniques are ambiguous as

other sources can describe observations from the candidates (e.g., light sources orbiting clusters of stellar-mass black holes

\subsection*{Left Side Page 2} 
\begin{tcolorbox}[left = 1em, top = 1ex, bottom = 1ex, colupper=black, colback=black!10, adjusted title =  Comment 1]
    \setlength\parindent{2em}
	\noindent
	\ttfamily
    line 9 "unambiguous": I wouldn't say this - there have been other models proposed to explain GW190521.
\end{tcolorbox}

\begin{tcolorbox}[left = 1em, top = 1ex, bottom = 1ex, colupper=black, colback=black!10, adjusted title =  Comment 2]
    \setlength\parindent{2em}
	\noindent
	\ttfamily
    line 16: $f \sim M^{-1}$: what does ~ mean here? Shouldn't this be $\propto$?
\end{tcolorbox}

\begin{tcolorbox}[left = 1em, top = 1ex, bottom = 1ex, colupper=black, colback=black!10, adjusted title =  Comment 3]
    \setlength\parindent{2em}
	\noindent
	\ttfamily
    lines 42: "We present the candidates' $p_S$, the probability that the candidate originates from a coherent gravitational-wave source". I have several problems with this statement. Firstly, you don't say what the probability is conditioned on, i.e. P(what $|$ what assumptions)? secondly, $P_S$ isn't actually a probability of the candidate, it's more like a P-value, as defined in eqns 2 and 3. The statement is misleading, a $P_S$=0.9 does not mean that a particular source has a probability of 0.9 of being a coherent source.
\end{tcolorbox}

% p1b = p1 = function of BCR <------- background probability
% p1s = another function of the BCR <------  signal probability (you need astrophysical distribution of injections to do this one)
% p_astro = p1s / (p1s + p1b)
% our hack:
% let's pretend
% p_notb = p1s = 1 - 1pb (edited)

not the prob of candidate signal event

its the prob of event not being from the background

we dont have p1s

strictly this is not correct

in the paper we show how strickly speaking how to calculate pastro

but we use a hack

\subsection*{Right Side Page 2} 
\begin{tcolorbox}[left = 1em, top = 1ex, bottom = 1ex, colupper=black, colback=black!10, adjusted title =  Comment 1]
    \setlength\parindent{2em}
	\noindent
	\ttfamily
    End of sec 2.1. You should justify why you go for a frequentist ranking statistic rather than a bayesian odds ratio.
\end{tcolorbox}

we dnt have prior odds, see greg's BCR2 paper

\begin{tcolorbox}[left = 1em, top = 1ex, bottom = 1ex, colupper=black, colback=black!10, adjusted title =  Comment 2]
    \setlength\parindent{2em}
	\noindent
	\ttfamily
    2.2: Text is misleading: The pi terms in eqn 1 are not astrophysical (or intrumental) prior odds. They are adjusted to maximise search sensitivity to an injection dataset on a chunk-by-chunk basis. You also say that $\pi^G$ is equal for all signals but this contradicts table D1.
\end{tcolorbox}

this is not a actual prior -- but emperical one

form of equatin 1 is similar to bayesian odds ratio.

we should not call it a prior

this functions like a prior

these are not chosen apriori

future iterations it may be possible to chose apriori

\subsection*{Left Side Page 3 Comments} 
\begin{tcolorbox}[left = 1em, top = 1ex, bottom = 1ex, colupper=black, colback=black!10, adjusted title =  Comment 1]
    \setlength\parindent{2em}
	\noindent
	\ttfamily
    I think the discussion before and around eqn 2 is wrong. $p_1$, as defined in eqn 2, is not the probability of a particular event being mis-classified as a glitch, as the text states. It is the p- value using the BCR as a ranking statistic. This is related to the comment above about the description of $P_S$. The p-value would be something like the probability of getting a BCR value greater than or equal to the candidate's value given purely noise. However, I'm not even sure if this is true, because the text doesn't say how the background time-slides are chosen: are they from the time-slide triggers from the matched filter search or chosen at random over the entire O2 data?
\end{tcolorbox}

first part is answered before

mention that we get the timeslid triggers

\begin{tcolorbox}[left = 1em, top = 1ex, bottom = 1ex, colupper=black, colback=black!10, adjusted title =  Comment 2]
    \setlength\parindent{2em}
	\noindent
	\ttfamily
    The definition of $p_S$ in eqn 4 is also not what is described in the text, as you are manipulating p- values not probabilities. This paragraph needs to be rewritten and checked for accuracy.
\end{tcolorbox}

\begin{tcolorbox}[left = 1em, top = 1ex, bottom = 1ex, colupper=black, colback=black!10, adjusted title =  Comment 3]
    \setlength\parindent{2em}
	\noindent
	\ttfamily
    line 53: the numbers are badly formatted after the commas
\end{tcolorbox}

\subsection*{Right Side Page 3} 
\begin{tcolorbox}[left = 1em, top = 1ex, bottom = 1ex, colupper=black, colback=black!10, adjusted title =  Comment 1]
    \setlength\parindent{2em}
	\noindent
	\ttfamily
    line 42: IMRPhenomPv2 may be relatively cheap but IMRPhenomX is even cheaper. However I don't suggest you re-run the entire analysis - but bear this in mind in future.
\end{tcolorbox}

\begin{tcolorbox}[left = 1em, top = 1ex, bottom = 1ex, colupper=black, colback=black!10, adjusted title =  Comment 2]
    \setlength\parindent{2em}
	\noindent
	\ttfamily
    line 54: post-processing improves the search efficiency: the search efficiency has not been defined yet. Reading on, it appears to be the sensitivity to the injection dataset, i.e. the number of detected signals above a given false alarm probability.
\end{tcolorbox}

sorry my bad, not serach efficency but resolving power.

\subsection*{Appendix Comments} 
\begin{tcolorbox}[left = 1em, top = 1ex, bottom = 1ex, colupper=black, colback=black!10, adjusted title =  Apdx B: Comment 1]
    \setlength\parindent{2em}
	\noindent
	\ttfamily
     "as stretch" -> "a stretch"
\end{tcolorbox}

\begin{tcolorbox}[left = 1em, top = 1ex, bottom = 1ex, colupper=black, colback=black!10, adjusted title =  Apdx B: Comment 2]
    \setlength\parindent{2em}
	\noindent
	\ttfamily
     "a few days" is this the two weeks mentioned in section 3?
\end{tcolorbox}

\begin{tcolorbox}[left = 1em, top = 1ex, bottom = 1ex, colupper=black, colback=black!10, adjusted title =  Apdx C Comment]
    \setlength\parindent{2em}
	\noindent
	\ttfamily
     Normally I would expect to see search performance presented as an ROQ curve. Can you provide this? Does it depend on which matched filter pipeline provides the upstream triggers?
\end{tcolorbox}

We made a mistake -- not efficency but resolving power

\begin{tcolorbox}[left = 1em, top = 1ex, bottom = 1ex, colupper=black, colback=black!10, adjusted title =  Apdx D Comment]
    \setlength\parindent{2em}
	\noindent
	\ttfamily
     The $P_S$ varies enormously, so it is not a surprise that it has a large effect on the results. It should be made much clearer in the main text that these prior odds are tuned from the data, so they are not the astrophysical prior odds as stated below eqn 1.
\end{tcolorbox}

\end{document}

### 2022-07-20 titlepage_mnras.tex
ref response 2

@@
 %   Society}:  \LaTeX\ guide for authors}
-\title[An IMBH search in O2 using the BCR]{A search for intermediate-mass black holes mergers in the \\second LIGO--Virgo observing run with the Bayes Coherence Ratio}
+\title[\green{An IMBH candidate follow-up in O2 using the BCR}]{\green{A follow-up on intermediate-mass black hole candidates in the second LIGO--Virgo observing run with the Bayes Coherence Ratio}}
 

### 2022-08-03 main.tex
Final version

@@
 However, ground-based detector data contain numerous incoherent short duration noise transients that can mimic the gravitational-wave signals from merging intermediate-mass black holes, limiting the sensitivity of searches.
-Here we \green{follow-up on} binary black hole merger \green{candidates} using a ranking statistic that measures the coherence or incoherence of triggers in multiple-detector data. 
-We use this statistic to \green{rank} candidate events,  \green{initially identified by all-sky search pipelines,} with lab-frame total masses $\gtrsim55\ M_\odot$ using data from LIGO's second observing run.
+Here we follow-up on binary black hole merger candidates using a ranking statistic that measures the coherence or incoherence of triggers in multiple-detector data. 
+We use this statistic to rank candidate events,  initially identified by all-sky search pipelines, with lab-frame total masses $\gtrsim55\ M_\odot$ using data from LIGO's second observing run. 
 Our analysis does not yield evidence for new intermediate-mass black holes. 
@@
 Since it is impossible to shield ground-based gravitational-wave detectors from gravitational-wave signals, the LVK empirically estimates the background by repeatedly time-shifting strain data by amounts larger than the light-travel time between the two LIGO detectors~\citep{GWTC1}.
-We use time-shifted data to generate $\bgrdbcr$, \green{the background ranking statistic}.
-Following this, we calculate the \green{fraction of $\bgrdbcr$ greater than or equal to a $\candbcr$, the candidate ranking statistic}:
+We use time-shifted data to generate $\bgrdbcr$, the background ranking statistic.
+Following this, we calculate the fraction of $\bgrdbcr$ greater than or equal to a $\candbcr$, the candidate ranking statistic:
 \begin{equation}
@@
 \end{equation}
-Given a set of simulated signals \green{and their ranking statistic $\injbcr$, one may calculate the fraction of $\injbcr$ greater than or equal to a $\candbcr$}: 
+Given a set of simulated signals and their ranking statistic $\injbcr$, one may calculate the fraction of $\injbcr$ greater than or equal to a $\candbcr$: 
 \begin{equation}
@@
 \end{equation}
-\green{With $p_1^b$ and $p_1^s$ it is possible to compute a candidate’s 
-\pastro, the probability that a candidate is of astrophysical origin:}
+With $p_1^b$ and $p_1^s$ it is possible to compute a candidate’s 
+\pastro, the probability that a candidate is of astrophysical origin:
 \begin{equation}
@@
 \end{equation}
-However, for this study we do not have an astrophysical distribution of simulated signals and so we cannot compute $p_1^s$ \green{or consequently $\pastro$}. 
+However, for this study we do not have an astrophysical distribution of simulated signals and so we cannot compute $p_1^s$ or consequently $\pastro$. 
 Instead we opt for a frequentist $p$-value probability that a candidate is inconsistent with the background. 
@@
 
-\green{It is important to note that 
-$\pastrobcr$ (the probability that an event is not part of the background distribution) is not the same as $\pastro$, which requires an astrophysical set of simulated signals.}
+It is important to note that 
+$\pastrobcr$ (the probability that an event is not part of the background distribution) is not the same as $\pastro$, which requires an astrophysical set of simulated signals.
 
@@
 To marginalize over the statistical uncertainty, we use the median-likelihood presented by~\citet{psd_student_t} as a post-processing step.
-\green{This post-processing step reduces the percentage of background $\bgrdbcr>0$ by $\sim49\%$.} The details of this calculation are in the Appendix~\ref{sec:psd-marginalization}.
+This post-processing step reduces the percentage of background $\bgrdbcr>0$ by $\sim49\%$.
+The details of this calculation are in the Appendix~\ref{sec:psd-marginalization}.
 
@@
 
-All analyses (inclusive of test and failed analyses) performed for this study used ${1.3\mathrm{M}}$ core-hours, amounting to a carbon footprint of ${\sim1.67\ \mathrm{t}}$ of ${\text{CO}_2}$ (using the U.S.
-average electricity source emissions of ${0.429\ \text{kg/kWh}}$~\citep{greenhouse} and ${0.3\ \text{kWh}}$ for each CPU).
+All analyses (inclusive of test and failed analyses) performed for this study used ${0.6\mathrm{M}}$ core-hours, amounting to a carbon footprint of ${\sim77\ \mathrm{t}}$ of ${\text{CO}_2}$ (using the U.S.
+average electricity source emissions of ${0.371\ \text{kg/kWh}}$~\citep{greenhouse} and ${0.3\ \text{kWh}}$ for each CPU).
 
@@
 Marginalizing over uncertainty in the PSD yields an improvement in the separation of the noise and signal distributions (left plot).
-Quantitatively, at a threshold $\bcr^T=0$ the post-processing step \green{reduces the percentage of} background $\bcr > \bcr^T$ from $60\%$ to $25\%$ \green{(a $58\%$ improvement)} in the August 13 - 21, 2017 time-frame of data.
-\green{For the entirety of O2, PSD marginalization reduces the percentage of $\bcr > \bcr^T$ from $64\%$ to $33\%$ (a $\sim49\%$ improvement).
-}
+Quantitatively, at a threshold $\bcr^T=0$ the post-processing step reduces the percentage of background $\bcr > \bcr^T$ from $60\%$ to $25\%$ (a $58\%$ improvement) in the August 13 - 21, 2017 time-frame of data.
+For the entirety of O2, PSD marginalization reduces the percentage of $\bcr > \bcr^T$ from $64\%$ to $33\%$ (a $\sim49\%$ improvement).
 

### 2022-08-03 titlepage_mnras.tex
Final version

--- 2022-01-21 titlepage_mnras.tex
@@
 %   Society}:  \LaTeX\ guide for authors}
-\title[An IMBH search in O2 using the BCR]{A search for intermediate-mass black holes mergers in the \\second LIGO--Virgo observing run with the Bayes Coherence Ratio}
+\title[An IMBH candidate follow-up in O2 using the BCR]{A follow-up on intermediate-mass black hole candidates in the second LIGO--Virgo observing run with the Bayes Coherence Ratio}
 

### 2022-08-03 Data/corner_data/download_data.sh
remove data dir

@@ -1,2 +1,0 @@
-scp avi.vajpeyi@ldas-pcdev3.ligo.caltech.edu:/hdfs/user/avi.vajpeyi/out_O2_BCRs/chunk7/pe_outdir/out_foreground/result/bcr_O2_chunk7_foreground_data1_1171814476-971924_analysis_H1L1_dynesty_result.json data/corner_data/170222_result.json
-scp avi.vajpeyi@ldas-pcdev3.ligo.caltech.edu:/home/avi.vajpeyi/projects/bcr_pipeline/bcr_pipeline/priors/454ns.prior data/corner_data/454ns.prior
